### 2014-07-02 Abstract.tex
Initial

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax

\pdfbookmark[1]{Abstract}{Abstract}

\section*{Abstract}

This dissertation presents a method for modelling disclosure behaviour
by treating the interaction as paired signalling games played by decision
theoretic agents. Two theories of decision making - Bayesian risk
minimisation, and \ac{CPT} - are investigated, and a simulation developed
using Python.

The feasibility of the method is examined through a case study, which
considers the disclosure of the drinking behaviour of pregnant women
to their midwives.

The essence of the scenario is that there is considered to be a long
term benefit to disclosure - common in the healthcare arena, but an
opportunity cost associated with disclosure. In the case study, this
is conceptualised as arising from the perceived undesirability of
drinking while pregnant. More generally this could derive from any
imbalance in the long term benefit and the opportunity cost, for example
the subjective benefit of a cigarette in the near future, versus the
discounted benefit of better health later.

Theories of decision are driven by the weighing of probabilities and
subjective gains or losses. In this case, the probabilities are generated
by individual agents based on their initial preconceptions and their
experiences across the simulation, using Bayesian inference.

The Bayesian risk minimising model is able to reproduce qualitative
trends around increased honesty over appointments, and a negative
impact of harsh judgement of drinkers on disclosure. The \ac{CPT}
model is less successful, which may be a result of improper, or excessively
homogenous parameters, in combination with unrealistic payoffs.

A global sensitivity analysis is also conducted using Gaussian Emulation
Machines, and finally recommendations for further work are dervived, along
with a few key recommendations for practice - assume people are being honest,
and be non-judgemental.

\vfill{}

\endgroup

### 2014-07-02 Background.tex
Initial

\section{Background}

\label{ch:lit_review}

This chapter presents an overview of literature focusing on the impact
of drinking behaviour in pregnancy, and factors affecting disclosure
behaviour in the midwifery context. This is followed by a review of
literature supporting the theoretical underpinning of the modelling
approach, with particular reference to statistical decision theory.

\subsection{Alcohol, and Disclosure in the Maternity Setting}

\subsubsection{Impact of Alcohol\label{sub:Impact-of-Alcohol}}

Distinct from stigma attached to alcohol consumption in pregnancy,
is the question of the real impact on woman and baby both in the \gls{antenatal}
period, and beyond. While the canonical example of alcohol linked
disorders is \ac{FAS}, and others on that spectrum, heavy drinking
during pregnancy has been mooted as a factor in a variety of negative
health outcomes.

The impact of moderate alcohol consumption in pregnancy is more contested.
For example, \citet{Andersen2012} examined moderate drinking in a
large Danish cohort study, finding a significant increase in the risk
of spontaneous abortion at low levels of consumption early in pregnancy.
\citet{Savitz2012} questioned the extent to which this can be interpreted
as a causal connection, noting that there is a known relationship
between absence of morning sickness, and spontaneous abortion, and
suggesting that this may explain much of the difference in risk. \citet{Kesmodel2002}
examined the relationship between alcohol consumption and still-birth,
finding that increased consumption lead to an increase in risk to
the baby, but in contrast to \citet{Andersen2012} this was significant
at \gls{term}.

Considering longer term negative outcomes, a metastudy by \citet{Latino-Martel2010}
examined the potential for maternal alcohol consumption in pregnancy
to feature as a risk factor for onset of childhood leukaemia, finding
that any alcohol consumption was associated with an increased risk
of childhood \ac{AML}, but note the rarity of the condition as a
limitation.

\citet{Huizink2006} reviewed literature looking at the impact of
moderate consumption on neurodevelopmental and cognitive outcomes,
concluding that maternal consumption can be a contributing factor
to \ac{ADHD}, and impairments to learning and memory. They subsequently
suggest that the underlying mechanism is not specific to alcohol consumption,
but a more general phenomena arising from perturbations to foetal
conditions \citep{Huizink2009}, but caution that methodological issues
in many of the studies reviewed may undermine this hypothesis.

Contrary to this, a meta-study by \citet{Gray2006} found there was
insufficient evidence to suggest any harm arising from moderate (under
1.5 UK units per day) alcohol consumption. This ties to the current
guidance from the \ac{NICE} \citep{NICE2010a}, advising that women
should avoid drinking at all in at least the first three months of
pregnancy, and no more than 1-2 units once or twice a week if they
do. In giving this advice, \ac{NICE} acknowledge that the risks to
the foetus from alcohol are a somewhat contentious subject, concluding
that the evidence of harm is inconclusive, but that this is not sufficient
to rule out the risk of negative outcomes. This tension is reflected
by earlier guidance from the \ac{RCOG} \citep{Gynecologists1996}
suggesting no evidence of harm below 15 units per week, and subsequent
criticism by \citet{Guerri1999}, who suggest that this might be interpreted
as legitimising \gls{binge}, while noting several studies indicating
adverse affects linked to even a single drink per day (e.g. \citet{Day1990}).
A subsequent \ac{RCOG} statement \citep{RoyalCollegeofObstetriciansandGynaecologists2006}
revised the recommendations to incorporate newer findings, advising
that there is no known safe threshold for drinking in pregnancy, and
highlighting binge drinking as of particular concern.

There has recently been an increased interest in the impact of binge
drinking, as a distinct pattern of consumption, with a wide variety
of negative outcomes reported by \citet{Maier2001}, although a significant
portion of their evidence base is drawn from animal studies which
augers for caution in generalising findings to humans. \citet{Strandberg-larsen2008}
explored links between binge drinking, and stillbirth, reporting a
statistically significant increase in risk associated with more than
three antenatal binge episodes. \citet{Sun2009} looked at seizure
disorders in children whose mothers binged during pregnancy. They
reported significantly greater risk of both neonatal seizures (\textasciitilde{}3
fold) and epilepsy (1.81 fold) associated with binge drinking between
11 and 16 weeks, but emphasised the exploratory nature of the results,
and need for replication. In terms of neurodevelopmental outcomes,
\citet{Streissguth1994} found a dose dependent association with scores
on timed word, and arithmetic tests in fourteen year olds with a stronger
association where bingeing occurred. A review by \citet{Henderson2007}
cautiously supports the contention that binge drinking has a neurodevelopmental
impact, but found no consistent support for adverse outcomes in pregnancy
(e.g. stillbirth, miscarriage, etc.) and note a paucity of studies
in the area. \citet{Meyer-Leu2011} considered the neonatal period,
finding that both moderate and binge drinking were associated with
an increased trend towards neonatal asphyxia. They also noted a large
number of contradictory findings and raising methodological concerns
about the studies reviewed by \citeauthor{Henderson2007}. \citet{Barr2006}
contend that binge drinking may also contribute to psychiatric issues
in the later life of offspring, although in this case their findings
are confined to individuals with \ac{FAS}, which may in itself be
a confounding factor, rather than indicating a directly causative
relationship between antenatal binge drinking and subsequent psychiatric
disorder in offspring.

Overall, there is a distinct lack of consensus on what, and how extensive,
the effects of drinking on the immediate and long term health outcomes
are for the child.

\subsubsection{Disclosure}

The issue of disclosure is central to the model presented here, in
particular self-report by women of information that might disadvantage
them, or be expected to do so in the immediate term. In general, the
consensus is that alcohol self-reports have acceptable validity in
the research context \citep{DelBoca2000}, but do not correspond perfectly
to alternative methods. \citet{DelBoca2003} claim that the validity
is generally accepted, and suggest that the current focus lies on
what factors and processes underlie the discrepancies rather than
questioning determining their existence. In this instance, the conjecture
is that the information is in some way stigmatising; that, following
\citet{Goffman1999}, disclosure equates to revelation of the mark.
This is not immediately contentious, for example \citet{Gomberg1988}
identified stigma surrounding alcohol abusing women in particular,
an issue also highlighted by \ac{IAPT} guidance \citep{IAPT2012},
as well as a number of other studies relating response effects to
perceived negative consequences \citep{Langenbucher2001,DelBoca2000,Blair1977}.
In the maternity context, \citet{Radcliffe2011} identifies stigma
pertaining to substance misusing women amongst staff, and suggests
that this may represent a barrier to appropriate treatment; similarly,
\ac{NICE} guidance on pregnancy and complex social factors \citep{NICE2010}
recognises concern about the attitude of staff as a source of anxiety
in pregnant women who misuse substances.

Stigma, or fear of a judgemental response on the part of the practitioner
should not however be taken uncritically to explain inaccurate reporting
by patients. While recent \ac{NICE} public health guidance advocates
routine alcohol misuse screening as a part of all practice \citep{NationalInstituteforHealthandCareExcellence2010},
there is no specific policy for routine antenatal care beyond providing
information on possible impacts of alcohol consumption \citep{NICE2010a}.
\ac{NICE} guidance on pregnancy and complex social factors \citep{NICE2010}
does specifically address women who misuse alcohol, but presupposes
knowledge of the problem through medical history, or via other services.
Taken in concert with the potential for harm from even moderate alcohol
use (section \ref{sub:Impact-of-Alcohol}), this suggests that much
of the onus is on the patient to volunteer information.

Where screening is used, \citet{Kaskutas2000} note that the most
basic method, i.e. number of standard drinks consumed, can lead to
inaccurate estimates of consumption arising from inability to relate
the concept of a standard drink, to actual consumption. This is compounded
by the impact of memory effects on recall over a number of days \citep{Stockwell2004},
and a lack of consistency in the standard drink measure \citep{Turner1990}.
Alternative screening tools, for example \acs{AUDIT}, and \acs{T-ACE}
are available and have been shown to perform well in identifying problematic
levels of drinking \citep{Piccinelli1997,Bradley1998,Russell1994,Russell1996},
although the emphasis in these cases is on consumption at disordered
levels.

\citet{Prior2003} considered a different health arena (mental health
problems and GPs), with similar characteristics in terms of concealment
of medically relevant information. The central finding in this case
is that non-disclosure is not a result of stigma, but of mismatched
ontologies surrounding mental illness. Work by \citet{Alvik2005},
where the relationship between anonymity and reporting of alcohol
consumption by pregnant women was investigated, found no significant
relationship, suggesting that a fear of social judgement may not be
a dominant factor. This draws an interesting contrast with a study
by \citet{Alvik2006}, which found that contemporaneous reports of
consumption were significantly lower than those postpartum. Logistic
regression results suggest that this trend is amplified by a number
of factors, including level of alcohol consumption preceding conception,
while anxiety about foetal wellbeing during pregnancy was associated
with lower retrospective reports. Taken together with \citep{Alvik2005},
these results could be seen as conflicting, but may suggest self-stigmatisation
\citep{Watson2007}, or reflect a lack of distinction between anonymity,
and confidentiality \citep{Malvin1983}.

In summation then, there is a consensus that alcohol consumption is
generally underreported in the pregnant population, with some support
for the idea that concern about social judgement associated with stigmatisation
may be a contributing factor. Of particular interest in the wider
context of this work, is the relationship between underreporting and
consumption, i.e. that heavier drinking is associated with a greater
tendency to understate intake.

\subsubsection{Practice Implications}

Given that alcohol consumption is thought to be underreported some
consideration must be given to the implications for midwifery practice,
in terms of eliciting more accurate self-reporting. \citet{Phillips2007}
present a qualitative account of factors influencing the disclosure
of substance misuse to midwives, identifying particularly the need
to build up a rapport, potentially over a number of appointments.
This was related to continuity of care, seen as necessary by both
midwives and women for building up a trust relationship, itself a
key component of facilitating disclosure. \citet{Stevens2002} looked
specifically at the process of transitioning to a caseloading model
of care provision in one midwifery practice, reporting that both practitioners
and women felt that this offered advantages in terms of long term
relationship building. Relationship building was also highlighted
by \citet{Kennedy2004} in a narrative investigation of midwifery
practice, where the subjects interpreted the midwife-woman dynamic
as about mutuality. \citeauthor{Kennedy2004} suggest that this arises
from a recognition that interactions in this context are about information
exchange, with the knowledge base of the woman as significant as that
of the midwife, rather than simply a unidirectionally didactic relationship.

\citet{Hunter2006} also focuses on much of midwifery as about relationship
building, suggesting that there is an insufficiently recognised emotional
labour component to practice. Observation and interview of a number
of midwives as they practiced suggested that many midwives effectively
took a mother type role to their patients, with implications around
the nature of information exchange that was able to take place. The
emotional labour component was also reported by \citeauthor{Stevens2002},
who suggest that this is more evident under a caseloading system, particularly
with challenging patients with complex needs. \citet{Todd1998} surveyed
midwives working in a hospital environment, as well as those working
in the community in a caseloading context, finding that community
practice appeared to provide more job satisfaction, but was challenging
to implement effectively because of limited resources. Community midwives
suggested that larger team sizes, and smaller caseloads would contribute
to a better realisation of the model. \citet{Farquhar2000} approached
the same question from the perspective of women, also finding that
faulty implementation hampered the expected benefits. They found that
those cared for under a team scheme, with much higher continuity of
care, reported that they had a better relationship with their midwives,
but were not more satisfied in general with their care. In contrast,
\citet{Biro2003} looked at a \ac{RCT} of team midwifery care versus
hospital care in Australia, finding a significantly higher level of
satisfaction under the team model, the distinction in this case may
lie in the different balance of team size to caseload size.

In terms of the impact of continuity of care on health, rather than
experiential outcomes, research is relatively sparse. \citet{Marks2003}
examined the impact of continuity of care on \ac{PND}, which has
similar features to alcohol in that it carries an associated stigma
that can act as a barrier to help seeking \citep{Dennis2006}. Based
on the results of a \ac{RCT}, they conclude that continuity of care
is not protective, in the sense of reducing rates or impacting onset,
but was very successful in supporting engagement with treatment. Echoing
this, a 2009 Cochrane Review by \citet{Hatem2009} found no significant
difference in incidence of \ac{PND}, but reported benefits in terms
of lower rates of \gls{episiotomies}, anaesthesia, and shorter hospital
stays, with higher satisfaction as found by \citeauthor{Biro2003}.
While research in this area does not specifically pertain to disclosure,
the general trend in results are suggestive when taken in concert
with studies emphasising the importance of relationship building as
key in fostering a disclosure friendly environment. Continuity of
care is generally regarded as improving patient experience, and leading
to better health outcomes in the wider medical arena \citep{VanWalraven2010},
but is clearly not a cost free endeavour, with particular concern
arising from the emotional cost \citep{Todd1998}, and increased rates
of `\gls{burnout}' in practitioners \citep{Sandall1997}.

\subsection{Games, Signals, and Decisions}

\subsubsection{Signalling Games}

Game theory generally deals with strategic decision making in the
unusual circumstance of complete information, that is, every player
has at least complete knowledge of all possible outcomes, who their
opponents are, and so forth. Arguably more generally applicable is
the incomplete information scenario, where players lack information
about the rules of play in some fashion. \citet{Harsanyi1967} proposed
a method for effectively transforming such games into games of complete
information by treating the possible variations on the rules as subgames.
To determine which subgame is to be played, an additional player -
nature - is introduced to make the first move, where nature conducts
a lottery according to some probability distribution. If it is assumed
that the underlying probability distribution is known to all players,
the game is then one of complete information.

Perhaps the best known example of Bayesian games, are the signalling
games codified by \citet{Kreps1987}, after initially being framed
by \citet{Spence1973} in the context of employment markets. The general
form of such a game is that one player holds information known only
to them, on the basis of which they send a signal to the other player(s),
which the other player(s) then act upon. Much of the interest in signalling
games turns on what conditions are necessary for honest signalling
to be a Nash equilibrium, or in the context of evolutionary game theory,
an \ac{ESS} .

One approach to this requires that signalling is a costly exercise,
as proposed by \citet{Grafen1990} in examining biological signals
(for example, the eye-catching but unwieldy peacock tail). \citeauthor{Grafen1990}
demonstrated that an earlier suggestion by \citet{Zahavi1975}, who
proposed that such signals were in effect a handicap demonstrating
fitness, would lead to an \ac{ESS} because of the costly nature of
the signalling. This solution is also noted by \citet{Spence1973},
who showed that a separating equilibrium exists%
\footnote{In fact, an infinite number of them.%
} contingent on signals being more costly for some types.

Costly signalling has been applied to explain a variety of apparently
contradictory behaviours, for example \citet{Godfray1991} in the
context of offspring soliciting food from parents, where the key question
is why a behaviour with potentially very high costs (namely, being
eaten) would be preferred to a less risky method. In a social context,
costly signalling has been proposed as an explanation for religion
in human societies. \citet{Sosis2003} developed a model of religious
ritual as an exercise in costly signalling, showing that higher costs
to engagement in rituals for skeptics maintains the stability of religious
groups and the presumed benefits that membership confers. \citet{Henrich2009}
extended this idea, and developed an evolutionary model combining
cultural transmission with costly signalling in a population, finding
that for even modest costs the system moved towards universal belief.
\citet{Wildman2011} subsequently extended the model, to address the
fact that both stable equilibria are binary states, finding that the
incorporation of group differentiation allowed subgroups to persist.

Signalling games have also been extended to provide models of other
observed human behaviour, for example \citet{Austen-Smith2005} attempted
to explain the observed poor academic attainment of some social groups
by positing a multiple audience signalling game. They found that the
introduction of a secondary signalling game with a peer audience,
alongside the prototypical \citeauthor{Spence1973} model introduced
a pooling equilibrium. Subsequent empirical work by \citet{Jr2010}
has provided some support for this idea. Along similar lines, \citet{Feltovich2002}
examine an observed failure by high quality types to signal as would
be anticipated, introducing the concept of countersignaling in scenarios
where there is noisy leakage of type information. They found that
where there is added noisy type information available, separating
equilibriums exist where high quality senders signal either as low
quality, or not at all.

\subsubsection{Bayesian Decision Theory and Expected Utility}

Decision theory is the theory of rational decision making \citep{Peterson2009},
this contrasts with game theory which is concerned with strategic
decision making. In the broadest sense, the field can be divided into
two types of theories: normative, and descriptive. Normative theories
are those which attempt to give the rational answer to a decision
problem, descriptive or behavioural theories focus instead on characterising
the process of human decision making. In this instance, the particular
concern is with theories of decision making under uncertainty.

Underpinning almost all theories of decision making, and much of economic
theory in general is the concept of expected utility, originally proposed
by \citet{Bernoulli1954}. This casts decisions as choices between
lotteries or gambles, with differing payoffs and probabilities.

Under this model, the expected utility of any gamble is a function
of the probability of the outcomes, their utility to the gambler,
and the gambler's risk aversion. Essentially this is an extension
of the expected value criterion, which assumes that the expected value
is based only on the probability and objective value of outcomes.
By contrast, the utility framing is a subjective measure, allowing
differing preferences between gamblers. \citet{Neumann1953} later
formalised the theory, defining rational decision as acting to maximise
expected utility, where an individual's preferences are shown to fulfil
four axioms, namely completeness, transitivity, independence, and
continuity. Completeness requires that for any two lotteries A and
B, the decision maker prefers one to the other, or is indifferent.
Transitivity requires that if A is preferred to B, and B is preferred
to C, then A is also preferred to C. Continuity states that given
a scenario as in the transitivity axiom, there is some combination
of lotteries A and C where the decision maker is indifferent between
that combined lottery and B. Finally, independence maintains that
if one were to prefer gamble A to B, that preference holds if both
are combined with lottery C.

While vastly influential, the expected utility theory has been substantially
criticised, generally for failing to predict real behaviour. \citet{Society2013}
attacked the independence axiom in particular, suggesting that in
some scenarios people's choices would be inconsistent where expected
utility implies otherwise. A number of studies (e.g. \citep{Oliver2003,Burke1996})
have since supported the intuition to some extent.

More recently, support for some aspects of the expected utility theory,
particularly the concept of utility as a common currency for comparison,
has come from neurology, for example following work by \citet{Platt1999},
\citet{Padoa-Schioppa2006,Padoa-Schioppa2008} report neuronal firing
corresponding to economic value in decision making tasks undertaken
by monkeys, while \citet{Christopoulos2009} found similarly indicative
results for risk aversion. The suggestion implicit in the model proposed
here, that this also applies to social judgements, is less investigated,
although both \citet{Watson2012}, and \citet{Willis2010} found that
lesions in the brain area%
\footnote{The orbitofrontal cortex.%
} identified by \citeauthor{Padoa-Schioppa2006} lead to abnormal social
judgements in humans and primates.

Bayesian decision theory, as expounded by \citet{Robbins1964} applies
Bayesian inference to the process of decision making under some degree
of uncertainty, on the basis that the decision is a repeated one.
The central idea is relatively straightforward, and assumes that the
loss or gain of some action to resolve a decision is contingent on
an unknown parameter. To solve the problem, the decision maker chooses
whichever action will minimise the risk, where the risk of an action
is $\underset{i}{\sum}\lambda(a_{j}|w_{i})P(w_{i}|x)$, i.e. the loss
incurred for taking action $a_{j}$ given that the true state of the
world is $w_{i}$, multiplied by the belief that this is the true
state of world given evidence $x$, summed across all possible worlds.
Essentially this is identical with expected value, with Bayesian style
probabilities. This allows an additional process of inference to progressively
update the distribution from which $P(w_{i}|x)$ derives, as new evidence
is obtained after each decision.

This approach has been used in a wide variety of scenarios, for example
\citet{McNamara1980} have applied statistical decision theory as
a framework for understanding animal learning%
\footnote{Although they note that this is in the sense of how animals `should'
learn, rather than how they do learn%
}, while \citet{Harsanyi1978} has derived an ethical framework from
the principles. Less controversially, in contexts where optimality
is desirable as an outcome, \citet{Survey2003} have used Bayesian
decision methods in combination with \ac{MCMC} to solve complex waterfowl
habitat management problems, and \citet{Kristensen1997} has developed
robots which utilise Bayesian decision analysis to plan sensor operations.

As with standard expected utility, the Bayesian approach can be criticised,
in this case on the grounds of plausibility. The question of plausibility
arises from the suggestion that Bayesian inference is in some way
a model of human inductive reasoning, as argued by some branches of
cognitive science. For example, \citeauthor{Tenenbaum2006} argue
for the Bayesian approach as a top-down model of inductive reasoning
in humans \citep{Tenenbaum2006,Griffiths2010}, a general approach
criticised by \citet{Bowers2012} as unfalsifiable, overcomplicated,
and relying on an unrealistic conceptualisation of the brain as optimal.
\citet{Miller2012} also applied similar criticism to claims by \citet{Gallistel2012}
that Bayesian inference better characterises learning as opposed to
associative conditioning type models, suggesting that this relies
on an assumption of optimality which is unfounded.

\subsubsection{Descriptive Decision Theory}

Arguably the most significant criticism of theories of decision making,
is their failure to correspond to empirically observed decision making
\footnote{This critique is not unique to decision theory, and has also been
levelled at game theory (e.g. \citet{Fehr2003} on the irrational
altruism of humans playing the prisoners' dilemma).%
}. This was probably first raised by \citet{Simon1956}, who proposed that the
apparent divergence derived from a tendency to satisfice, rather than
optimise. This suggestion rests on the not unreasonable assumption
that people do not have unlimited cognitive capacity (i.e. bounded
rationality \citep{Simon2000}), and hence use heuristic means to
make decisions, namely by choosing the first `good enough' option.
\citeauthor{Simon1956} suggests that this process nevertheless leads
to the optimal solution is most cases.

Subsequent work on descriptive theories largely follows the same framework
in assuming that in reality, human decision making is a heuristic
process. \citet{Tversky1974} developed three heuristics to explain
observed systematic errors in reasoning - representativeness, availability,
and anchoring. Representativeness suggests that when asked to judge
how related one object or event is to another, they do this based
on the extent to which they resemble one another - crucially they
will ignore additional, better information when available. Availability
claims that when tasked with estimating probabilities, people will
rely on the ease with which they can call examples to mind (note that
this might be considered an example of satisficing). Finally, anchoring
proposes that when estimating, people start with some initial value
and progressively update from there, i.e. they will tend to overweight
prior evidence at the expense of new information.

Subsequently, \citet{Kahneman1984,Tversky1986} also identified framing
effects, which imply that the decisions people make are impacted by
the fashion in which the problem is presented. The essential outcome
from these findings is that people are risk seeking when faced with
outcomes framed as losses, but risk averse towards gains, and regard
any loss as greater than an equivalent gain. The impact of framing
in itself has been shown to be significant, for example \citet{Toll2007}
found improved abstinence rates in smoking cessation where quitting
was framed as a gain, and \ac{NICE} recommend considering the framing
of treatment outcomes when presenting options to patients \citep{NICE2007}.

\ac{PT} \citep{Kahneman1979} attempts to provide a decision rule
accounting for the heuristic nature of decision making and incorporate
framing effects, which successfully explains many perceived failures
of rationality. A revised version, \ac{CPT} \citep{Tversky1992}
addressing a violation of first order stochastic dominance possible
under the original formulation, extends the theory to allow decisions
with more than two options, but sacrifices the editing phase. \citet{Camerer2004a}
reviews a number of successes in explaining apparent anomalies with
\ac{CPT}, and argues that should replace expected utility in general
usage. \citet{Thaler2000} regards the theory as promising, but points
out that it is in many ways incomplete, citing the lack of explanation
as to how people construct frames as an example of this.

A significant weakness of \ac{CPT} as a general theory of decision
making is that it fails to account for behaviour under intertemporal
choice, or rather does not attempt to address it. Generally, intertemporal
choice is assumed to be underpinned by the \ac{DU} model of \citet{Samuelson1937},
which proposes that the value of a thing right now is greater than
the value of it at some point in the future (jam today has more utility
than jam tomorrow), following an exponential relationship. A more
nuanced view of this has been proposed by \citet{Ainslie1991}, suggesting
that the relationship is hyperbolic rather than exponential. Both
models however fail to explain several inconsistencies, for example
\citet{Thaler1981} found that discounting rates were different between
gains and losses. \citet{Loewenstein1992} report a number of additional
inconsistencies that are not adequately resolved by \ac{DU} models,
and propose an alternative along the lines of \ac{CPT} to resolve
them while retaining the capabilities of Kahneman and Tversky's model
in immediate term choices.

### 2014-07-02 disclosure_game.tex
Initial

\documentclass{article}
\usepackage{ifthen}
\newboolean{enable-backrefs} % enable backrefs in the bibliography
\setboolean{enable-backrefs}{true} % true false
\newcommand{\backrefnotcitedstring}{\relax}%(Not cited.)
\newcommand{\backrefcitedsinglestring}[1]{(Cited on page~#1.)}
\newcommand{\backrefcitedmultistring}[1]{(Cited on pages~#1.)}
\ifthenelse{\boolean{enable-backrefs}}%
{%
		\PassOptionsToPackage{hyperpageref}{backref}
		\usepackage{backref} % to be loaded after hyperref package
		   \renewcommand{\backreftwosep}{ and~} % separate 2 pages
		   \renewcommand{\backreflastsep}{, and~} % separate last of longer list
		   \renewcommand*{\backref}[1]{}  % disable standard
		   \renewcommand*{\backrefalt}[4]{% detailed backref
		      \ifcase #1 %
		         \backrefnotcitedstring%
		      \or%
		         \backrefcitedsinglestring{#2}%
		      \else%
		         \backrefcitedmultistring{#2}%
		      \fi}%
}{\relax}
\usepackage{fullpage}
\usepackage{comment}
\usepackage[square, numbers]{natbib}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[subrefformat=parens,labelformat=parens]{subfig}
\usepackage{acronym}
\usepackage{nomencl}
\usepackage[style=long,nolist]{glossaries}
% the following is useful when we have the old nomencl.sty package
\providecommand{\printnomenclature}{\printglossary}
\providecommand{\makenomenclature}{\makeglossary}
\title{Deciding to Disclose: Pregnancy and Alcohol Misuse}
\author{Jonathan Gray \and Jakub Bijak \and Seth Bullock\\
University of Southampton, Southampton, SO17 1BJ, United Kingdom\\
E-mail: \texttt{j.gray@soton.ac.uk}}
\date{\vspace{-5ex}}
\begin{document}
\maketitle

%*************************
% Acronyms
%*************************
%\phantomsection
%\refstepcounter{dummy}
\pdfbookmark[1]{Acronyms}{acronyms}
%\markboth{\spacedlowsmallcaps{Acronyms}}{\spacedlowsmallcaps{Acronyms}}
\section*{Acronyms}
\begin{acronym}[UML]
  \acro{FAS}{Foetal Alcohol Syndrome}
  \acro{CPT}{Cumulative Prospect Theory}
  \acro{PT}{Prospect Theory}
  \acro{NICE}{National Institute for Health and Care Excellence}
  \acro{IAPT}{Improving Access to Psychological Therapies}
  \acro{CMACE}{Centre for Maternal and Child Enquiries}
  \acroindefinite{CMACE}{the}{the}
  \acro{AUDIT}{Alcohol Use Disorders Identification Test}
  \acro{T-ACE}{Tolerance, Annoyance, Cut down, Eye-opener}
  \acro{RCOG}{Royal College of Obstetricians and Gynecologists}
  \acroindefinite{RCOG}{the}{the}
  \acro{AML}{acute myeloid leukemia}
  \acro{ADHD}{Attention Defecit Hyperactivity Disorder}
  \acro{PND}{Postnatal Depression}
  \acro{RCT}{randomised control trial}
  \acro{WHO}{the World Health Organisation}
  \acro{ESS}{Evolutionarily Stable Strategy}
  \acro{MCMC}{Markov chain monte carlo methods}
  \acro{DU}{Discounted Utility}
  \acro{AIC}{Akaike information criterion}
  \acro{ANOVA}{analysis of variance}
  \acro{ALSPAC}{Avon Longitudinal Study of Parents and Children}
  \acro{GEM}{Gaussian Emulation Machine}
  \acrodefplural{GEM}{Gaussian Emulation Machines}
  \acro{GEM-SA}{Gaussian Emulation Machine for Sensitivity Analysis}
  \acro{JIT}{Just-in-time}
  \acro{ABM}{Agent Based Model}
  \acro{CPT}{Cumulative Prospect Theory}
\end{acronym}

\newglossaryentry{gravid}{name={gravid}, description={Pregnant}}
\newglossaryentry{term}{name={term}, description={Gestation of 37-42 weeks, 40 weeks is considered full term}}
\newglossaryentry{binge}{name={binge drinking}, description={Drinking with the express purpose of becoming drunk}}
\newglossaryentry{burnout}{name={burnout}, description={Lasting physical and emotional exhaustion, and disillusionment}}
\newglossaryentry{antenatal}{name={antenatal},description={The time period covering the pregnancy, prior to birth}}
\newglossaryentry{episiotomies}{name={episiotomies}, description={An episiotomy is a common procedure where an incision is made in the perineum to facilitate delivery, and attempt to reduce the risk of vaginal tearing}}
\newglossaryentry{neonatal asphyxia}{name={antenatal},description={The time period covering the pregnancy, prior to birth}}

%\refstepcounter{dummy}
\pdfbookmark[1]{Glossary}{glossary}
\printglossary[type=main]

\printnomenclature{}

\include{Abstract}

\section{Introduction} %(half page)

\include{Background}

\section{Model}

\subsection{Disclosure Game}

\subsection{Agent Models}

\section{Method}
\subsection{Qualitative Trends}
\subsection{Sensitivity Analysis}

\section{Results}
\subsection{}

\section{Discussion and Conclusions}

\bibliographystyle{plainnat}
\bibliography{library}
\end{document}

### 2014-07-03 Introduction.tex
Making the sections, slowly

\section{Introduction}
\label{sec:intro}
%CONTRIBUTION, FUCKER!
%Also, remember to say what you're going to do for the rest of the article?

### 2014-07-03 Methods.tex
Making the sections, slowly

\section{Method}
\label{sec:method}
%Lay out the design of experiments, harking back to things we're looking for
%from the real world.
%explicit subsection on the SA.
\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}

### 2014-07-03 Model.tex
Making the sections, slowly

\section{Model}
\label{sec:model}
%Start this off with a brief description of our fictional scenario.

\subsection{Disclosure Game}
\label{sub:the_game}
%Outline how the scenario translates into a game.

\subsection{Agent Models}
\label{sub:the_agents}
%Outline basic structure, then specifics on each one.
%This should probably go lexic -> bayes payoff -> bayes -> CPT in order
% of complexity.

### 2014-07-03 Conclusion.tex
Moar sections

--- 2014-07-02 disclosure_game.tex
@@
-\documentclass{article}
-\usepackage{ifthen}
-\newboolean{enable-backrefs} % enable backrefs in the bibliography
-\setboolean{enable-backrefs}{true} % true false
-\newcommand{\backrefnotcitedstring}{\relax}%(Not cited.)
-\newcommand{\backrefcitedsinglestring}[1]{(Cited on page~#1.)}
-\newcommand{\backrefcitedmultistring}[1]{(Cited on pages~#1.)}
-\ifthenelse{\boolean{enable-backrefs}}%
-{%
-		\PassOptionsToPackage{hyperpageref}{backref}
-		\usepackage{backref} % to be loaded after hyperref package
-		   \renewcommand{\backreftwosep}{ and~} % separate 2 pages
-		   \renewcommand{\backreflastsep}{, and~} % separate last of longer list
-		   \renewcommand*{\backref}[1]{}  % disable standard
-		   \renewcommand*{\backrefalt}[4]{% detailed backref
-		      \ifcase #1 %
-		         \backrefnotcitedstring%
-		      \or%
-		         \backrefcitedsinglestring{#2}%
-		      \else%
-		         \backrefcitedmultistring{#2}%
-		      \fi}%
-}{\relax}
-\usepackage{fullpage}
-\usepackage{comment}
-\usepackage[square, numbers]{natbib}
-\usepackage{hyperref}
-\usepackage{graphicx}
-\usepackage[subrefformat=parens,labelformat=parens]{subfig}
-\usepackage{acronym}
-\usepackage{nomencl}
-\usepackage[style=long,nolist]{glossaries}
-% the following is useful when we have the old nomencl.sty package
-\providecommand{\printnomenclature}{\printglossary}
-\providecommand{\makenomenclature}{\makeglossary}
-\title{Deciding to Disclose: Pregnancy and Alcohol Misuse}
-\author{Jonathan Gray \and Jakub Bijak \and Seth Bullock\\
-University of Southampton, Southampton, SO17 1BJ, United Kingdom\\
-E-mail: \texttt{j.gray@soton.ac.uk}}
-\date{\vspace{-5ex}}
-\begin{document}
-\maketitle
-
-%*************************
-% Acronyms
-%*************************
-%\phantomsection
-%\refstepcounter{dummy}
-\pdfbookmark[1]{Acronyms}{acronyms}
-%\markboth{\spacedlowsmallcaps{Acronyms}}{\spacedlowsmallcaps{Acronyms}}
-\section*{Acronyms}
-\begin{acronym}[UML]
-  \acro{FAS}{Foetal Alcohol Syndrome}
-  \acro{CPT}{Cumulative Prospect Theory}
-  \acro{PT}{Prospect Theory}
-  \acro{NICE}{National Institute for Health and Care Excellence}
-  \acro{IAPT}{Improving Access to Psychological Therapies}
-  \acro{CMACE}{Centre for Maternal and Child Enquiries}
-  \acroindefinite{CMACE}{the}{the}
-  \acro{AUDIT}{Alcohol Use Disorders Identification Test}
-  \acro{T-ACE}{Tolerance, Annoyance, Cut down, Eye-opener}
-  \acro{RCOG}{Royal College of Obstetricians and Gynecologists}
-  \acroindefinite{RCOG}{the}{the}
-  \acro{AML}{acute myeloid leukemia}
-  \acro{ADHD}{Attention Defecit Hyperactivity Disorder}
-  \acro{PND}{Postnatal Depression}
-  \acro{RCT}{randomised control trial}
-  \acro{WHO}{the World Health Organisation}
-  \acro{ESS}{Evolutionarily Stable Strategy}
-  \acro{MCMC}{Markov chain monte carlo methods}
-  \acro{DU}{Discounted Utility}
-  \acro{AIC}{Akaike information criterion}
-  \acro{ANOVA}{analysis of variance}
-  \acro{ALSPAC}{Avon Longitudinal Study of Parents and Children}
-  \acro{GEM}{Gaussian Emulation Machine}
-  \acrodefplural{GEM}{Gaussian Emulation Machines}
-  \acro{GEM-SA}{Gaussian Emulation Machine for Sensitivity Analysis}
-  \acro{JIT}{Just-in-time}
-  \acro{ABM}{Agent Based Model}
-  \acro{CPT}{Cumulative Prospect Theory}
-\end{acronym}
-
-\newglossaryentry{gravid}{name={gravid}, description={Pregnant}}
-\newglossaryentry{term}{name={term}, description={Gestation of 37-42 weeks, 40 weeks is considered full term}}
-\newglossaryentry{binge}{name={binge drinking}, description={Drinking with the express purpose of becoming drunk}}
-\newglossaryentry{burnout}{name={burnout}, description={Lasting physical and emotional exhaustion, and disillusionment}}
-\newglossaryentry{antenatal}{name={antenatal},description={The time period covering the pregnancy, prior to birth}}
-\newglossaryentry{episiotomies}{name={episiotomies}, description={An episiotomy is a common procedure where an incision is made in the perineum to facilitate delivery, and attempt to reduce the risk of vaginal tearing}}
-\newglossaryentry{neonatal asphyxia}{name={antenatal},description={The time period covering the pregnancy, prior to birth}}
-
-%\refstepcounter{dummy}
-\pdfbookmark[1]{Glossary}{glossary}
-\printglossary[type=main]
-
-\printnomenclature{}
-
-\include{Abstract}
-
-\section{Introduction} %(half page)
-
-\include{Background}
-
-\section{Model}
-
-\subsection{Disclosure Game}
-
-\subsection{Agent Models}
-
-\section{Method}
-\subsection{Qualitative Trends}
-\subsection{Sensitivity Analysis}
-
-\section{Results}
-\subsection{}
-
 \section{Discussion and Conclusions}
-
-\bibliographystyle{plainnat}
-\bibliography{library}
-\end{document}
+\label{sec:conclusion}

### 2014-07-04 Abstract.tex
Added acknowledgements
Added tex  root for easier building
Sketching abstract

@@
+%!TEX root = disclosure_game.tex
 \begingroup
@@
 \section*{Abstract}
+
+Background:
+Roots in agents, decision theory, game theory.
+We draw together methodologies from game theory, agent based modelling, and decision theory to explore the process of decision making around disclosure.
+This is framed in the context of pregnant women disclosing their drinking behaviour to their midwives.
+
+Objective: 
+To pimp out this method, and maybe get some insight into reality.
+Address the perceived ad hoc character with strongly theoretically underpinned agents.
+
+Methods: 
+Made a game, made a simulation, did a sensitivity analysis.
+
+Results: 
+Look! Chaos! Look! Qualitative trends! Look! More data needed.
+
+Conclusions:
+This.. might actually kind of work??
+
+Comments: 
+Lesson learned: data should drive modelling.
 

### 2014-07-05 Abstract.tex
Sketching out

--- 2014-07-02 Abstract.tex
@@
 
-This dissertation presents a method for modelling disclosure behaviour
-by treating the interaction as paired signalling games played by decision
-theoretic agents. Two theories of decision making - Bayesian risk
-minimisation, and \ac{CPT} - are investigated, and a simulation developed
-using Python.
+\subsection*{Background}
 
-The feasibility of the method is examined through a case study, which
-considers the disclosure of the drinking behaviour of pregnant women
-to their midwives.
+We draw together methodologies from game theory, agent based modelling, and decision theory to explore the process of decision making around disclosure.
+This is framed in the context of pregnant women disclosing their drinking behaviour to their midwives.
 
-The essence of the scenario is that there is considered to be a long
-term benefit to disclosure - common in the healthcare arena, but an
-opportunity cost associated with disclosure. In the case study, this
-is conceptualised as arising from the perceived undesirability of
-drinking while pregnant. More generally this could derive from any
-imbalance in the long term benefit and the opportunity cost, for example
-the subjective benefit of a cigarette in the near future, versus the
-discounted benefit of better health later.
+\subsection*{Objective}
 
-Theories of decision are driven by the weighing of probabilities and
-subjective gains or losses. In this case, the probabilities are generated
-by individual agents based on their initial preconceptions and their
-experiences across the simulation, using Bayesian inference.
+The primary purpose it to demonstrate the potential utility of an approach which it is hoped goes some way towards addressing concerns about the ad hoc character of \ac{ABM}, by providing a strong theoretical grounding for the reasoning processes of individual agents.
+To this end we hope to show that these simple rules, operating in an inescapably artificial scenario are nonetheless capable of producing trends from the literature.
+We also seek to demonstrate the significance of precisely how the decision making process is formulated, by contrasting four distinct decision rules against one another and exploring a simple form of information sharing, supported by the use of statistical emulators for a full exploration of the parameter space.
 
-The Bayesian risk minimising model is able to reproduce qualitative
-trends around increased honesty over appointments, and a negative
-impact of harsh judgement of drinkers on disclosure. The \ac{CPT}
-model is less successful, which may be a result of improper, or excessively
-homogenous parameters, in combination with unrealistic payoffs.
+\subsection*{Methods}
 
-A global sensitivity analysis is also conducted using Gaussian Emulation
-Machines, and finally recommendations for further work are dervived, along
-with a few key recommendations for practice - assume people are being honest,
-and be non-judgemental.
+We employ game theory to define a signalling game representative of a scenario where pregnant women decide how far to disclose their drinking behaviours to their midwives, and midwives employ the information provided to decide whether a costly referral should be made.
+This game is then recast as two games taking play against nature, to permit the use of a decision theoretic approach where both classes of agent use simple rules to decide their moves.
+Four decision rules are explored - a lexicographic heuristic which considers only the link between moves and payoffs, a Bayesian risk minimisation agent that uses the same information, a more complex Bayesian risk minimiser, and a \ac{CPT} type.
 
-\vfill{}
+Using a simulator we have developed in Python, we recreate two key qualitative trends described in the Midwifery literature for all the decision models, and investigate the impact of introducing a simple form of information sharing within agent groups.
+Finally a global sensitivity analysis using \acp{GEM} was conducted, to compare the response surfaces of the different decision rules in the game.
 
-\endgroup
+\subsection*{Results}
+
+Selected results showing the ability of all decision rules to reproduce qualitative trends noted in the literature are provided, together with a sensitivity analysis, and comparitive heat maps produced using \acp{GEM} demonstrating the significance of the precise implementation of the decision making.
+
+\subsection*{Conclusions}
+
+The ability of all the decision rules to show the qualitative trends suggests that there is some utility associated with this approach.
+
+\subsection*{Comments}
+
+We note that the scenario omits the overwhelming complexity of the reality, and is presented largely in the spirit of a convenient demonstration of the methodology.
+Clearly a domain where there is sufficient data to permit a more comprehensive approach to validation of model outcomes is desirable, and will form the basis of our future work.

### 2014-07-05 Introduction.tex
Added tex  root for easier building
Making notes
Sketching out

@@
+%!TEX root = disclosure_game.tex
 \section{Introduction}
@@
 %Also, remember to say what you're going to do for the rest of the article?
+%CONTRIBUTION
+%	Agents are awesome
+%	Decision theory is super awesome
+%	'nice story to hang it on'
+
+The case in favour of \ac{ABM} as an approach has been made numerously, and elegantly REFS.
+As such we will not belabour the point, and instead turn to addressing some of the concerns often expressed about the method.
+In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, tending to be a reflection of the assumptions of the modeller rather than empirically or theoretically grounded.
+
+%Finishing up
+
+The remainder of this paper proceeds to provide small reviews of alcohol and disclosure in the maternity setting (\ref{sub:alcohol_disclosure}), and the methodological context (\ref{sub:games_signals}), before outlining the model (\ref{sec:model}), and experiments (\ref{sec:method}), with selected results (\ref{sec:results}), then closing with a discussion contrasting the decision models (\ref{sec:conclusion}).

### 2014-07-05 Model.tex
Added tex  root for easier building
Making notes
Sketching out

@@
+%!TEX root = disclosure_game.tex
 \section{Model}
@@
 %Start this off with a brief description of our fictional scenario.
+% Whole section ~ 1.5K
 
@@
 %Outline how the scenario translates into a game.
+%Brief mention of the game theoretic solution
+
+In order to translate the scenario sketched above into a more abstract, tractable form, we cast it as a signalling game, and assume that women's disclosures (or not), are signals.
+We also make the simplifying assumption that a woman may have one of only three drinking patterns - light, moderate, or heavy.
+Correspondingly, they are limited in what signals they may send to claiming to be one of these three types.
+
+Midwives are treated in a similar fashion, where their type corresponds to how negatively they regard a drinking pattern - non-judgemental, moderately judgemental, and harshly judgemental.
+The expression of this judgement is not a matter of choice on their part, and is assumed not to impact on their choice of response, which is either to refer the woman for specialist treatment, or to do nothing.
+
+At the end of a game, each player receives a payoff dependent on the actions and types of both players, which has a partially common interest component.
+Women receive a payoff based on the health of their eventual baby, with a social cost dependent on the signal they sent and the midwife's reaction to it.
+Midwives receive the same health payoff as the women, but pay a cost for referring to a specialist, mirroring the organisational cost of non-routine care.
+
+Agents treat this two player game as taking place against nature, along the lines of adversial risk analysis \citep{THINGY}.
+
+%Might belong in a more methody bit? Read some stuff to check..
+Women are drawn in order from a queue, and play against a midwife chosen at random.
+They play for a maximum of 12 rounds (following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred.
+At which point a new player is drawn from the same distribution that produced the original players to replace them.
+If they are not referred, they rejoin the back of the queue after their appointment.
+In either case, they are informed of their payoff after each round and update their beliefs accordingly.
+
+Midwives play for \(k\) rounds (\(k=1000\) in all experiments), and conduct appointments in parallel.
+Unlike women, midwives are only informed of their payoff if they choose to make a referral.
+Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.
 
@@
 % of complexity.
+%suggest there are added shells of complexity
+%		mention the info sharing because homophilly
+%			related - the enhancement to the bayes/cpt agents is that they personalise, as much as anything.
+%		properly explain dirichlet priors
+% How about comparing the decision problem representation for the agent types?
+
+While in principle a wide variety of agent models, given that decision rules operate on essentially the same information, and produce the same outputs, we limit ourselves here to four.
+The simplest is a lexicographic rule (1), motivated as in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; a Bayesian risk minimisation rule using the same information (2); a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \cite{Hau2008} agent (4) which is identical with 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}.
+
+As noted in section \ref{sub:the_game}, agents have perfect recall, and recognise individual opponents if they encounter them subsequently.
+While agents recall perfectly and make use of the new information for retrospective updates, their decisions are made \'as-if\' they were facing a new opponent.
+
+\subsubsection{Payoff Reasoning}
+
+Both payoff reasoners assume a simplified decision problem, as in figure \ref{fig:payoff_problem}, where an action is a choice between lotteries.
+The lexicographic heuristic (algorithm \ref{alg:lexicographic}) maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e.
+one reason decision making.
+The Bayesian risk minimisation agent uses the same subset of information, but updates beliefs on the link between actions and payoffs using Bayes rule, and attempts to choose the action which minimises risk.
+
+\subsubsection{Bayesian Risk Minimisation}
+
+Aside from the heuristic agent, the remaining three agent types use Bayesian updating to attempt to improve
+the accuracy of their beliefs. Given the discrete nature of agent
+types, and actions, coupled with a desire for tractability of the
+simulation, the Dirichlet distribution is employed. The probability
+density function takes the form -
+
+\[
+D(\Theta|\alpha)=\frac{\Gamma(\sum_{i=1}^{k}\alpha_{i})}{\prod_{i=1}^{k}\Gamma(\alpha_{i})}\overset{k}{\underset{i=1}{\prod}\Theta_{i}^{\alpha_{i-1}}}
+\]
+
+Where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\)is the number
+of discrete types, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
+more than zero and summing to less than 1, and \(\alpha_{i}\) is the
+psuedo-count of prior observations for type \(i\).
+
+The distribution is particularly convenient, in that to infer the
+probability of a new observation being of some particular type becomes
+simply -
+
+\begin{equation}
+P(x=j|D,\alpha)=\frac{\alpha_{j}+n_{j}}{\sum_{j}(\alpha_{j}+n_{j})}\label{eq:posterior}
+\end{equation}
+
+Where \(n_{j}\) is simply the count of occurrences of type \(j\), so
+that the belief that a new observation is of type \(j\) the number
+of times that type has been observed (including the pseudo-count),
+over the total number of observations thus far. This makes computation
+of beliefs fast, and simple, since all that must be maintained is
+a count of observations with no particular concern as to their order.
+
+\subsubsection{Descriptive Decision Theory}
+
+\subsection{Information Sharing}
+\label{sub:info_sharing}
+
+It would seem unreasonable to suppose that neither party recounts their experiences to their peers, and to explore the impact of this we also modify the game to introduce a simple form of information sharing within agent groups.
+This takes the form of having each agent share their memories with their colleagues with some probability \(p\).
+Individuals then incorporate shared information into their beliefs using weighted updates, such that a shared observation of a low type signal contributes to their beliefs by \(q\), and \(0\leq q\leq 1\).
+Women share only when they have finished play, and provide their complete history of games, because they have accurate information about the outcomes.
+By the same rationale, midwives share only their history with the most recent woman they referred.
+Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{Memories of games remain, but the assumption is that only current news is relevant.}
+
+Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this outside information differently.
+The simple payoff based rule relys on a belief structure relating actions directly to rewards.
+Because payoffs differ by the agent's private type, the information shared may not correspond to the experience of the listening agent in the same scenario.
+As a result, payoff reasoners have a belief bias towards the most common player type, and can believe in outcomes that are, for them, impossible.
+
+By contrast, representing the problem in terms of the probabilities of the individual lotteries yields a structure that generalises the new information.
+
+\subsection{Model Implementation}
+\label{sub:the_code}
+% Use this bit to talk about the practical version of the game and where info is revealed?
+The model itself is implemented as a Python module, and is freely available under the Mozilla Public License from \url{https://github.com/greenape/disclosure-game}, together with full parameter sets, raw data, and all other code used in producing this paper.

### 2014-07-07 Background.tex
Making the sections, slowly
Added tex  root for easier building
Sketching out
Fleshing out
Beginning to flesh out, added a stub for a decision problem figure.

@@
+%!TEX root = disclosure_game.tex
 \section{Background}
 
-\label{ch:lit_review}
+\label{sec:lit_review}
 
-This chapter presents an overview of literature focusing on the impact
+This section presents a brief overview of literature focusing on the impact
 of drinking behaviour in pregnancy, and factors affecting disclosure
@@
 \subsection{Alcohol, and Disclosure in the Maternity Setting}
+\label{sub:alcohol_disclosure}
 
@@
 \subsection{Games, Signals, and Decisions}
+\label{sub:games_signals}
 
@@
 Bayesian inference to the process of decision making under some degree
-of uncertainty, on the basis that the decision is a repeated one.
+of uncertainty, where decisions may be one-shot, or repeated.
 The central idea is relatively straightforward, and assumes that the

### 2014-07-07 Introduction.tex
Fleshing out
Beginning to flesh out, added a stub for a decision problem figure.

@@
 
-The remainder of this paper proceeds to provide small reviews of alcohol and disclosure in the maternity setting (\ref{sub:alcohol_disclosure}), and the methodological context (\ref{sub:games_signals}), before outlining the model (\ref{sec:model}), and experiments (\ref{sec:method}), with selected results (\ref{sec:results}), then closing with a discussion contrasting the decision models (\ref{sec:conclusion}).
+The remainder of this paper proceeds to provide brief reviews of alcohol and disclosure in the maternity setting (\ref{sub:alcohol_disclosure}), and the methodological context (\ref{sub:games_signals}), before outlining the model (\ref{sec:model}), and experiments (\ref{sec:method}), with selected results (\ref{sec:results}), then closing with a discussion contrasting the decision models (\ref{sec:conclusion}).

### 2014-07-07 Methods.tex
Added tex  root for easier building
Fleshing out
Beginning to flesh out, added a stub for a decision problem figure.

@@
+%!TEX root = disclosure_game.tex
 \section{Method}
@@
 %from the real world.
+
+This section provides details of experiments conducted to examine the ability of the model to reproduce qualitative trends reported in the midwifery literature by \cite{Alvik2006}, and \cite{Phillips2007}; as well as a global sensitivity analysis and construction of statistical emulators to explore, and contrast the response surfaces of the four decision rules.
+
+\subsection{Qualitative Trends}
+\label{sub:qt}
 %explicit subsection on the SA.
+
+Throughout this paper, parameters for the \ac{CPT} model were as used in \cite{Tversky1992} (table \ref{tab:qt_params}).
+While there has been significant work on determining appropriate parameterisation for the model (e.g.
+\cite{Neilson2002}, \cite{Glockner2012}, \cite{Nilsson2011}), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work.
+
+Two key measures were used - the fraction of the subpopulation who had ever signalled honestly, and the proportion referred.
+Both measures were taken after every round of play, and were taken relative to the agent's position in their sequence of appointments giving the probability of signalling honestly, or being referred having had a given number of appointments.
+
+\begin{table}
+\center
+\begin{tabular} {l | c}
+Name & Value \\
+
+\end{tabular}
+\caption[Table caption text]{Model parameters. \label{tab:qt_params}}
+\end{table}
 \subsection{Global Sensitivity Analysis}
 \label{sub:sensitivity}
+%Maxmin latin hypercube -> remember to cite the r package used.
+%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
+ \cite{Bijak2013b}
+
+Parameters for training were generated in R \citep{RTeam2014} using Latin Hypercube Sampling \citep{Carnell2012} over the space of inputs given in table \ref{tab:sa_params}.
+Initially a unit hypercube was generated, then the margins transformed appropriately to cover those regions where the inputs are not bounded between 0 and 1, and for proportions of agent types which necessarily sum to one across the three parameters.
+Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each.
+A fixed set of 100 random seeds was used, such that each parameter set was run once with each seed, for every decision rule.
+
+To better capture the response characteristics for the model, we employ three - (1) the interquartile range of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3) the standard deviation of that average signal between simulation runs.
+Together these three metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the stability of the system in the face of the stochastic elements.
+
+Measurements were taken at the end of 1000 rounds of play, and for 1 and 2, 400 results were selected covering the full hypercube with each chosen randomly from the runs for that design point.
+This approach, rather than averaging across runs, was taken to avoid obscuring the high degree of variability evident in the output of the payoff reasoning agents in some areas of the parameter space.
+
+Twelve emulators were built, covering each of the three output on all four decision models.
+These emulators were used to conduct a probabalistic sensitivity analysis using \ac{GEM-SA} to assess the impact of parameters individually, and in combination.
+In addition, the trained emulators were used to explore novel areas of the parameter space.?????????????
+
+\begin{table}
+\center
+\begin{tabular} {l | c}
+Name & Value \\
+
+\end{tabular}
+\caption[Table caption text]{Parameter ranges. \label{tab:sa_params}}
+\end{table}
+
+\begin{table}
+\center
+\begin{tabular} {l | c}
+Name & Value \\
+
+\end{tabular}
+\caption[Table caption text]{Output measures. \label{tab:sa_measures}}
+\end{table}

### 2014-07-07 Model.tex
Fleshing out
Beginning to flesh out, added a stub for a decision problem figure.

@@
 % Whole section ~ 1.5K
+
+In this section we outline the disclosure game model, and give details of the four decision rules.
+
+A brief sketch of a pregnancy in terms of encounters between a woman and a midwife is instructive at this juncture.
+Typically women will have 12 appointments with a midwife during the antenatal period.
+Outside of caseloading teams, a woman does not generally have a named midwife, and may see a different practitioner at each appointment.
+In the UK, and unlike most healthcare scenarios, maternity notes are patient held, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously.
+Maternity notes are not generally linked to extra-departmental records, meaning that a history of alcohol related admissions to another service may remain unknown unless revealed by the woman.
+
+According to NICE guidance \citep{NICE2010a,NICE2010} substance misuse should be raised at the initial booking appointment, and subsequent action if a concern is raised is at the discretion of the midwife.
+This may take the form of specific guidance to reduce intake, or if deemed necessary a referral to a specialist midwife and relevant interdisciplinary team.
+On alcohol consumption, policy regarding how to determine the level of consumption is generally at the trust level, or according to the best judgement of the individual midwife, with no guidance provided by NICE.
+This commonly takes the form of average units per week, but may include \ac{T-ACE} and similar measures.
+
+Beyond the booking appointment, the onus is on women to raise concerns about their drinking behaviour, or the midwife to probe further if they feel it is warranted.
 
@@
 Midwives are treated in a similar fashion, where their type corresponds to how negatively they regard a drinking pattern - non-judgemental, moderately judgemental, and harshly judgemental.
-The expression of this judgement is not a matter of choice on their part, and is assumed not to impact on their choice of response, which is either to refer the woman for specialist treatment, or to do nothing.
+The expression of this judgement is not a matter of choice on their part, and is assumed to have no impact on their response, which is to either refer the woman for specialist treatment, or do nothing.
 
@@
 
-Agents treat this two player game as taking place against nature, along the lines of adversial risk analysis \citep{THINGY}.
+Taken together, this leads to a game tree that is relatively complex even at the subgame level (figure \ref{fig:subgame_tree} shows the subgame tree, with information sets). 
+%The subgame has a large number of pure Nash equilibria, and solution using Gambit \citep{Gambit13}
+Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversial risk analysis \citep{RiosInsua2009}.
+This effectively translates the game to a pair of decision problems, which agents attempt to resolve at each turn using a simple decision rule.
 
@@
 
-While in principle a wide variety of agent models, given that decision rules operate on essentially the same information, and produce the same outputs, we limit ourselves here to four.
+While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same outputs, we limit ourselves here to four.
 The simplest is a lexicographic rule (1), motivated as in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; a Bayesian risk minimisation rule using the same information (2); a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \cite{Hau2008} agent (4) which is identical with 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}.
+Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-ouput characteristics.
 
@@
 While agents recall perfectly and make use of the new information for retrospective updates, their decisions are made \'as-if\' they were facing a new opponent.
+
+A simplifying assumption is made that all midwives have just qualified, with identical training and as a result have entirely homogenous beliefs about their women.
+It is assumed in general that they have not been trained by Dr.
+House, and as a result have been taught that people will generally tell the truth.
+Women are heterogenous in their prior observations, which are assigned stochastically and constrained such that they have encountered each scenario possible at least once, with exactly \(k\) encounters overall.
 
@@
 
+The most complex decision rule used is \ac{CPT}, which attempts to reproduce a number of systematic deviations from rationality observed in humans.
+While \ac{CPT} has primarily been applied in the context of decisions from description, it has been modified to deal with decisions from experience by incorporating a first stage where probabilities are estimates from observations as in \cite{Hau2008}.
+In this instance we replace the frequentist first stage with the equivalent Bayesian inference process.
+
 \subsection{Information Sharing}
@@
 By the same rationale, midwives share only their history with the most recent woman they referred.
-Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{Memories of games remain, but the assumption is that only current news is relevant.}
+Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{Memories of games remain, but it is assumed that only current news is relevant.}
 
@@
 
-By contrast, representing the problem in terms of the probabilities of the individual lotteries yields a structure that generalises the new information.
+By contrast, representing the problem in terms of the probabilities of the individual lotteries yields a structure that abstracts the new information from payoffs, and allows the agent discount implausible outcomes.
 

### 2014-07-07 Model.tex
Filler
Filler text to be rewritten

@@
 
-In this section we outline the disclosure game model, and give details of the four decision rules.
-
-A brief sketch of a pregnancy in terms of encounters between a woman and a midwife is instructive at this juncture.
+In this section we outline the disclosure game model, and give details of the four decision rules, but begin with a brief sketch of a pregnancy in terms of encounters between a woman and a midwife. 
 Typically women will have 12 appointments with a midwife during the antenatal period.
@@
 Beyond the booking appointment, the onus is on women to raise concerns about their drinking behaviour, or the midwife to probe further if they feel it is warranted.
+In either case, once a concern has been raised the midwife must respond clinically, and inevitably personally, to the information.
+
+In an ideal world, all interactions with healthcare providers would be immediately and fully disclosive, with no repercussions for the patient.
+However even when considering less emotive topics, this is not the case.
 
@@
 Women receive a payoff based on the health of their eventual baby, with a social cost dependent on the signal they sent and the midwife's reaction to it.
-Midwives receive the same health payoff as the women, but pay a cost for referring to a specialist, mirroring the organisational cost of non-routine care.
+Midwives receive the same health payoff as the women, but pay a cost for referring to a specialist, mirroring the organisational cost of non-routine care (table \ref{tab:Payoff-matrix}).
 
-Taken together, this leads to a game tree that is relatively complex even at the subgame level (figure \ref{fig:subgame_tree} shows the subgame tree, with information sets). 
+Taken together, this leads to a game tree that is relatively complex even at the subgame level (figure \ref{fig:subgame_tree} shows the extensive form for a subgame, with information sets). 
 %The subgame has a large number of pure Nash equilibria, and solution using Gambit \citep{Gambit13}
 Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversial risk analysis \citep{RiosInsua2009}.
-This effectively translates the game to a pair of decision problems, which agents attempt to resolve at each turn using a simple decision rule.
+This effectively translates the game to a pair of decision problems, which agents attempt to resolve at each turn using a simple decision rule, given their prior beliefs and experience of play.
 
@@
 
-Midwives play for \(k\) rounds (\(k=1000\) in all experiments), and conduct appointments in parallel.
+Midwives play for \(k\) rounds (\(k=1000\) in all experiments), and conduct appointments in parallel, i.e.
+if there are 5 midwives, then five women are drawn from the queue and assigned at random to the midwives.
 Unlike women, midwives are only informed of their payoff if they choose to make a referral.
 Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.
+
+\begin{table}
+\center
+\subfloat[Social cost\label{tab:Social-cost-matrix}]{%
+\begin{tabular}{|c|c|c|c|c|}
+\cline{3-5} 
+\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
+
+\hline
+\multirow{4}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
+\cline{2-5} 
+ & Harsh & 0, -2 & 0, -1 & 0, 0\tabularnewline
+\cline{2-5} 
+ & Medium & 0, -1 & 0, 0 & 0, 0\tabularnewline
+\cline{2-5} 
+ & Low & 0, 0 & 0, 0 & 0, 0\tabularnewline
+\hline 
+\end{tabular}
+
+}
+
+\subfloat[Health outcome\label{tab:Referral-payoff-matrix}]{%
+\begin{tabular}{|c|c|c|c|c|}
+\cline{3-5} 
+\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
+
+\hline 
+\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
+\cline{2-5} 
+ & Refer & 10, 10 & 10, 10 & 10, 10\tabularnewline
+\cline{2-5} 
+ & Don't refer & -2, -2 & -1, -1 & 10, 10\tabularnewline
+\hline 
+\end{tabular}
+
+}
+
+\subfloat[Referral cost\label{tab:inst_cost_matrix}]{%
+\begin{tabular}{|c|c|c|c|c|}
+\cline{3-5}  
+\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
+\hline 
+\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
+\cline{2-5} 
+ & Refer & -9, 0 & -9, 0 & -9, 0\tabularnewline
+\cline{2-5} 
+ & Don't refer & 0, 0 & 0, 0 & 0, 0\tabularnewline
+\hline 
+\end{tabular}
+
+}
+
+\caption{Payoff matrices\label{tab:Payoff-matrix}}
+\end{table}
 
@@
 As noted in section \ref{sub:the_game}, agents have perfect recall, and recognise individual opponents if they encounter them subsequently.
-While agents recall perfectly and make use of the new information for retrospective updates, their decisions are made \'as-if\' they were facing a new opponent.
+While agents recall perfectly and make use of the new information for retrospective updates, all four agent models make decisions `as-if' they were always facing a new opponent.
 
@@
 types, and actions, coupled with a desire for tractability of the
-simulation, the Dirichlet distribution is employed. The probability
+simulation, the Dirichlet distribution is employed to represent these beliefs. The probability
 density function takes the form -
@@
 
-Where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\)is the number
+Where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\) is the number
 of discrete types, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
-more than zero and summing to less than 1, and \(\alpha_{i}\) is the
+more than zero and summing to less than 1, and \(\alpha_{i}\) is the integer
 psuedo-count of prior observations for type \(i\).
@@
 over the total number of observations thus far. This makes computation
-of beliefs fast, and simple, since all that must be maintained is
+of beliefs fast and simple, since all that must be maintained is
 a count of observations with no particular concern as to their order.
@@
 
+Rather than the psychologically more interesting \ac{PT}, the \ac{CPT}
+decision rule is used in this instance, because of the requirement
+for women to evaluate more than two `prospects'.\footnote{A prospect in this instance is a paired outcome and probability, and the set of prospects
+for an action hence define the outcome space.} \ac{CPT} introduces
+the concept of a probability weighting function, which underweights
+small probabilities, and overweights large ones in an effort to capture
+the tendency of humans to treat high probability events as sure things,
+and small probabilities as `never going to happen'. A number of different
+weighting functions have been proposed, but in this instance the original
+formulation by \citet{Tversky1992} is used. This distinguishes between
+weighting for gains, and losses -
+
+\begin{eqnarray*}
+w^{+}(p) & = & \frac{p^{\gamma}}{(p^{\gamma}+(1-p)^{\gamma})^{\frac{1}{\gamma}}}\\
+w^{-}(p) & = & \frac{p^{\delta}}{(p^{\delta}+(1-p)^{\delta})^{\frac{1}{\delta}}}
+\end{eqnarray*}
+
+Where $p$ is the unweighted probability, and $\gamma$ and $\delta$
+are the weights for gain and loss probabilities respectively. Humans
+have also been observed to value gains and losses differently, with
+a loss being `worse' than the equivalent gain is `good'. This
+entails a transformed value function -
+
+\[
+v(x)=\begin{cases}
+f(x) & if\, x>0\\
+0 & if\, x=0\\
+g(x) & if\, x<0
+\end{cases}
+\]
+
+Where,
+
+\[
+f(x)=\begin{cases}
+x^{\alpha} & if\,\alpha>0\\
+ln(x) & if\,\alpha=0\\
+1-(1+x)^{\alpha} & if\,\alpha<0
+\end{cases}
+\]
+\[
+g(x)=\begin{cases}
+-(-x)^{\beta} & if\,\beta>0\\
+-ln(-x) & if\,\beta=0\\
+(1-x)^{\beta}-1 & if\,\beta<0
+\end{cases}
+\]
+
+And $\alpha$, and $\beta$ are respectively the power of a gain,
+and a loss. The \ac{CPT} value of outcome $x$ is $v(x)w^{+}(x)$
+if $x\geq0$, and $v(x)w^{-}(x)$ otherwise. For an action the \ac{CPT}
+value is the sum of the value of the prospects of that action, as
+in the Bayesian risk model. The decision rule then requires the agent
+to choose the action which maximises the prospect theory value.
+
 \subsection{Information Sharing}
@@
 This takes the form of having each agent share their memories with their colleagues with some probability \(p\).
-Individuals then incorporate shared information into their beliefs using weighted updates, such that a shared observation of a low type signal contributes to their beliefs by \(q\), and \(0\leq q\leq 1\).
+Individuals then incorporate shared information into their beliefs using weighted updates, such that a shared observation of a low type signal contributes to their beliefs by \(q\), and \(0\leq q\leq 1\) (i.e.
+\(n_{j} = n_{j} + q\)).
 Women share only when they have finished play, and provide their complete history of games, because they have accurate information about the outcomes.
@@
 
-Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this outside information differently.
+Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this exogenous information differently.
 The simple payoff based rule relys on a belief structure relating actions directly to rewards.
@@
 By contrast, representing the problem in terms of the probabilities of the individual lotteries yields a structure that abstracts the new information from payoffs, and allows the agent discount implausible outcomes.
-
-\subsection{Model Implementation}
-\label{sub:the_code}
-% Use this bit to talk about the practical version of the game and where info is revealed?
-The model itself is implemented as a Python module, and is freely available under the Mozilla Public License from \url{https://github.com/greenape/disclosure-game}, together with full parameter sets, raw data, and all other code used in producing this paper.

### 2014-07-08 Methods.tex
MOAR TABLES!

@@
 \center
-\begin{tabular} {l | c}
-Name & Value \\
-
+\begin{tabular} {|l | c | r|}
+\hline
+Name & Description & Value \\ \hline
+\(N_{w}\) & Number of women & 1000 \\ \hline
+\(N_{m}\) & Number of midwives & 100 \\ \hline
+k & Number of appointments per midwive & 1000 \\ \hline
+A & Maximum number of appointments per woman & 12 \\ \hline
+R & Runs & 1000 \\ \hline
+\(P_{h,w}\) & Proportion of heavy drinkers & \(1/3\) \\ \hline
+\(P_{m,w}\) & Proportion of moderate drinkers & \(1/3\) \\ \hline
+\(P_{l,w}\) & Proportion of light drinkers & \(1/3\) \\ \hline
+\(P_{h,m}\) & Proportion of harsh midwives & \(5/100\) \\ \hline
+\(P_{m,m}\) & Proportion of moderate midwives & \(10/100\) \\ \hline
+\(P_{l,m}\) & Proportion of non-judgemental midwives & \(85/100\) \\ \hline
+\(p_{w}\) & Probability of women sharing & 0. \\ \hline
+\(q_{w}\) & Weight of shared information for women & 0. \\ \hline
+\(p_{m}\) & Probability of midwives sharing & 0. \\ \hline
+\(q_{m}\) & Weight of shared information for midwives & 0. \\ \hline
+\(s_{i}[a_{i}]\) & Psuedo-count favouring honesty & 10 \\ \hline
 \end{tabular}
@@
 \center
-\begin{tabular} {l | c}
-Name & Value \\
-
+\begin{tabular} {|l | l | l| l|}
+\hline
+Name & Description & Min & Max \\ \hline
+\(P_{h,w}\) & Proportion of heavy drinkers & 0 & 1 \\ \hline
+\(P_{m,w}\) & Proportion of moderate drinkers & 0 & 1 \\ \hline
+\(P_{l,w}\) & Proportion of light drinkers & 0 & 1 \\ \hline
+\(P_{h,m}\) & Proportion of harsh midwives & 0 & 1 \\ \hline
+\(P_{m,m}\) & Proportion of moderate midwives & 0 & 1 \\ \hline
+\(P_{l,m}\) & Proportion of non-judgemental midwives & 0 & 1 \\ \hline
+\(p_{w}\) & Probability of women sharing & 0 & 1 \\ \hline
+\(q_{w}\) & Weight of shared information for women & 0 & 1 \\ \hline
+\(p_{m}\) & Probability of midwives sharing & 0 & 1 \\ \hline
+\(q_{m}\) & Weight of shared information for midwives & 0 & 1 \\ \hline
+\(Payoff_{baby}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
+\(Payoff_{referral}\) & Cost for referral & \multicolumn{2}{l|}{\(Payoff_{baby} - 1\)} \\ \hline
+\(s_{i}[a_{i}]\) & Psuedo-count favouring honesty & 1 & 100 \\ \hline
 \end{tabular}
@@
 \center
-\begin{tabular} {l | c}
-Name & Value \\
+\begin{tabular} {| l | l |}
+Name & Description \\ \hline
 

### 2014-07-08 Methods.tex
Adding algorithms

@@
 \(N_{m}\) & Number of midwives & 100 \\ \hline
-k & Number of appointments per midwive & 1000 \\ \hline
-A & Maximum number of appointments per woman & 12 \\ \hline
+\(A_{m}\) & Number of appointments per midwive & 1000 \\ \hline
+\(A_{w}\) & Maximum number of appointments per woman & 12 \\ \hline
 R & Runs & 1000 \\ \hline
@@
 
-Parameters for training were generated in R \citep{RTeam2014} using Latin Hypercube Sampling \citep{Carnell2012} over the space of inputs given in table \ref{tab:sa_params}.
+Parameters for training were generated in R \citep{RTeam2014} using Latin Hypercube Sampling \citep{Carnell2012} over the space of inputs given in table \ref{tab:sa_params}, giving 10 free parameters.
 Initially a unit hypercube was generated, then the margins transformed appropriately to cover those regions where the inputs are not bounded between 0 and 1, and for proportions of agent types which necessarily sum to one across the three parameters.
@@
 
-To better capture the response characteristics for the model, we employ three - (1) the interquartile range of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3) the standard deviation of that average signal between simulation runs.
+To better capture the response characteristics for the model, we measure three outcome variables - (1) the interquartile range of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3) the standard deviation of that average signal between simulation runs.
 Together these three metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the stability of the system in the face of the stochastic elements.
@@
 These emulators were used to conduct a probabalistic sensitivity analysis using \ac{GEM-SA} to assess the impact of parameters individually, and in combination.
-In addition, the trained emulators were used to explore novel areas of the parameter space.?????????????
 
@@
 \(Payoff_{baby}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
-\(Payoff_{referral}\) & Cost for referral & \multicolumn{2}{l|}{\(Payoff_{baby} - 1\)} \\ \hline
+\(Payoff_{referral}\) & Cost for referral & \multicolumn{2}{l|}{\(-(Payoff_{baby} - 1)\)} \\ \hline
 \(s_{i}[a_{i}]\) & Psuedo-count favouring honesty & 1 & 100 \\ \hline

### 2014-07-08 Model.tex
Adding algorithms

@@
 
-Midwives play for \(k\) rounds (\(k=1000\) in all experiments), and conduct appointments in parallel, i.e.
+Midwives play for \(A_{m}\) rounds (\(A_{m}=1000\) in all experiments), and conduct appointments in parallel, i.e.
 if there are 5 midwives, then five women are drawn from the queue and assigned at random to the midwives.
@@
 \center
-\subfloat[Social cost\label{tab:Social-cost-matrix}]{%
+\subfloat[Social cost, \(P_{s}\)\label{tab:Social-cost-matrix}]{%
 \begin{tabular}{|c|c|c|c|c|}
@@
 
-\subfloat[Health outcome\label{tab:Referral-payoff-matrix}]{%
+\subfloat[Health outcome, \(P_{h}\)\label{tab:Referral-payoff-matrix}]{%
 \begin{tabular}{|c|c|c|c|c|}
@@
 
-\subfloat[Referral cost\label{tab:inst_cost_matrix}]{%
+\subfloat[Referral cost, \(P_{c}\)\label{tab:inst_cost_matrix}]{%
 \begin{tabular}{|c|c|c|c|c|}
@@
 
-A simplifying assumption is made that all midwives have just qualified, with identical training and as a result have entirely homogenous beliefs about their women.
-It is assumed in general that they have not been trained by Dr.
-House, and as a result have been taught that people will generally tell the truth.
+A simplifying assumption is made that all midwives have just qualified after receiving identical training.
+As a result, they have homogenous beliefs about their women and assume to some extent that they are honest.
 Women are heterogenous in their prior observations, which are assigned stochastically and constrained such that they have encountered each scenario possible at least once, with exactly \(k\) encounters overall.
 
-\subsubsection{Payoff Reasoning}
+Formally we let \(S\) be the set of signals \(\{l, m, h\}\), \(T_{w}\) be the set of drinking types \(\{l, m, h\}\), \(T_{m}\) the set of midwife types \(\{l, m, h\}\), and \(J=\{r,n\}\) the actions available to midwives.
+The set of all payoffs shall be denoted \(P\), where \(P_{w}\) are the payoffs for all women\footnote{While it is assumed that \(P_{w}\) for an individual of type \(a\) is constrained such that \(T=\{a\}\), this can change under the modified game described in subsection \ref{sub:info_sharing}} defined by \(P_{w}=\{x | x=P_{h, b, c} + P_{s, a, d}\wedge b \in J\wedge c \in T\wedge d \in M\}\), and equivalently for midwives \(P_{m}=\{x | x=P_{h, b, c} + P_{c, b}\}\).
 
-Both payoff reasoners assume a simplified decision problem, as in figure \ref{fig:payoff_problem}, where an action is a choice between lotteries.
-The lexicographic heuristic (algorithm \ref{alg:lexicographic}) maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e.
+\subsection{Lexicographic Heuristic}
+\label{sub:lexico}
+
+The lexicographic heuristic (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified decision problem, as in figure \ref{fig:payoff_problem}, where an action is a choice between combined lotteries.
+Functionally, the heuristic maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e.
 one reason decision making.
-The Bayesian risk minimisation agent uses the same subset of information, but updates beliefs on the link between actions and payoffs using Bayes rule, and attempts to choose the action which minimises risk.
+This approach requires minimal computation, and does not assume that all payoffs are known, or static.
 
-\subsubsection{Bayesian Risk Minimisation}
+Women maintain a count, \(n\) for each of the \(k\) payoffs in \(P_{w, a},a\in k\), an individual payoff paired with a signal, such that \(n_{i}=\{n_{i,1}\ldots n_{i,k}\}\).
 
-Aside from the heuristic agent, the remaining three agent types use Bayesian updating to attempt to improve
-the accuracy of their beliefs. Given the discrete nature of agent
-types, and actions, coupled with a desire for tractability of the
+Midwives solve a slightly different problem, where the signal received may convey useful information.
+This is resolved by maintaining a separate count for each signal, i.e.
+\(n_{i,j}=\{n_{i,j,1}\ldots n_{i, j, k}\}\), and otherwise follow the same algorithm.
+
+\begin{algorithm}
+\begin{algorithmic}
+\State n=1, action=none
+\While{action is none}
+\State Calculate the nth most common outcome following each action.
+\State Sort actions by the value of the nth most common outcome.
+\If{clear winner} \State action = best \EndIf
+\State n = n + 1
+\EndWhile
+\State \Return action
+\end{algorithmic}
+\caption{Lexicographic heuristic\label{alg:lexico}}
+\end{algorithm}
+
+\subsubsection{Bayesian Payoff Heuristic}
+
+The Bayesian payoff agent uses the same subset of information as the lexicographic method, but updates beliefs on the link between actions and payoffs using Bayes rule, and attempts to choose the action which minimises risk.
+
+Given the discrete nature of actions and payoffs, coupled with a desire for tractability of the
 simulation, the Dirichlet distribution is employed to represent these beliefs. The probability
@@
 Where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\) is the number
-of discrete types, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
+of signal-payoff pairs, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
 more than zero and summing to less than 1, and \(\alpha_{i}\) is the integer
-psuedo-count of prior observations for type \(i\).
+psuedo-count of prior observations for a pair \(i\).
 
 The distribution is particularly convenient, in that to infer the
-probability of a new observation being of some particular type becomes
+probability of a signal implying a payoff becomes
 simply -
@@
 
-Where \(n_{j}\) is simply the count of occurrences of type \(j\), so
-that the belief that a new observation is of type \(j\) the number
+Where \(n_{j}\) is simply the count of occurrences of pair \(j\), so
+that the belief that a signal \(j\) the number
 of times that type has been observed (including the pseudo-count),
@@
 
+As before, midwives follow a similar pattern but per signal.
+
+\subsubsection{Bayesian Risk Minimisation}
+
+The second Bayesian agent augments the payoff reasoning version by separating the two lotteries and assuming that \(P\) is a static, and known set of payoffs possible for the agent.
+For women, this means that they maintain two sets of beliefs: a Dirichlet mixture which represents the believed distribution of midwife types, and a second set linking signals to referrals.
+
+Formally, let \(D=\{D_{h}, D_{s}\}\), \(\alpha=\{\alpha_{h},\alpha_{s}\}\), and \(n=\{n_{h},n_{s}\}\). The quantity to be minimised then becomes -
+
+\begin{equation}
+R(i)= \sum_{z=1}\sum_{j=1}-P_{w, i, z, j}P(x=l|D_{s},\alpha_{s})P(x=j|D_{h},\alpha_{h})\label{eq:risk}
+\end{equation}
+
+So that the risk of a signal, \(i\) is the sum of all possible payoffs multiplied by the probability of that payoff occurring.
+
+Midwives reasoning centers determing the meaning of signals, since given the knowledge of what some signal \(i\) conveys about the true type of the sender, the payoff for an action is known.
+As such, their inference process is the same as for the simple Bayesian agent but over signal-type pairs, and they attempt to minimise -
+
+\begin{equation}
+R(i, j)= \sum_{z=1}\sum_{j=1}-P_{m, i, z, j}P(x=l|D_{s},\alpha_{s})P(x=j|D_{h},\alpha_{h})\label{eq:mw_risk}
+\end{equation}
+
 \subsubsection{Descriptive Decision Theory}
@@
 The most complex decision rule used is \ac{CPT}, which attempts to reproduce a number of systematic deviations from rationality observed in humans.
-While \ac{CPT} has primarily been applied in the context of decisions from description, it has been modified to deal with decisions from experience by incorporating a first stage where probabilities are estimates from observations as in \cite{Hau2008}.
+While \ac{CPT} has primarily been applied in the context of decisions from description, it has been modified to deal with decisions from experience by incorporating a first stage where probabilities are estimates from observations as in \cite{FoxCPT}.
 In this instance we replace the frequentist first stage with the equivalent Bayesian inference process.
@@
 By contrast, representing the problem in terms of the probabilities of the individual lotteries yields a structure that abstracts the new information from payoffs, and allows the agent discount implausible outcomes.
+This stronger assumption as to the static and known qualities of payoffs does however reduce the flexibility of the decision rule.

### 2014-07-09 Methods.tex
Trying to clear up the notation

@@
 \center
-\begin{tabular} {|l | c | r|}
+\begin{tabular} {|l | l | c|}
 \hline
@@
 \(N_{m}\) & Number of midwives & 100 \\ \hline
-\(A_{m}\) & Number of appointments per midwive & 1000 \\ \hline
-\(A_{w}\) & Maximum number of appointments per woman & 12 \\ \hline
-R & Runs & 1000 \\ \hline
+\(R_{m}\) & Number of appointments per midwive & 1000 \\ \hline
+\(R_{w}\) & Maximum number of appointments per woman & 12 \\ \hline
+Runs & Simulation runs & 1000 \\ \hline
 \(P_{h,w}\) & Proportion of heavy drinkers & \(1/3\) \\ \hline
@@
 \(q_{m}\) & Weight of shared information for midwives & 0. \\ \hline
-\(s_{i}[a_{i}]\) & Psuedo-count favouring honesty & 10 \\ \hline
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 10:1 \\ \hline
 \end{tabular}
@@
 %Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
- \cite{Bijak2013b}
+In general, we follow the procedure outlined in \cite{Bijak2013b} for stochastic
 
@@
 \(q_{m}\) & Weight of shared information for midwives & 0 & 1 \\ \hline
-\(Payoff_{baby}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
-\(Payoff_{referral}\) & Cost for referral & \multicolumn{2}{l|}{\(-(Payoff_{baby} - 1)\)} \\ \hline
-\(s_{i}[a_{i}]\) & Psuedo-count favouring honesty & 1 & 100 \\ \hline
+\(P_{h,}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
+\(P_{c, r}\) & Cost for referral & \multicolumn{2}{l|}{\(-(Payoff_{baby} - 1)\)} \\ \hline
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 1:1 & 100:1 \\ \hline
 \end{tabular}

### 2014-07-09 Model.tex
Trying to clear up the notation

@@
 Women receive a payoff based on the health of their eventual baby, with a social cost dependent on the signal they sent and the midwife's reaction to it.
-Midwives receive the same health payoff as the women, but pay a cost for referring to a specialist, mirroring the organisational cost of non-routine care (table \ref{tab:Payoff-matrix}).
+Midwives receive the same health payoff as the women, but pay a cost for referring to a specialist, mirroring the organisational cost of non-routine care.
+Table \ref{tab:Payoff-matrix} shows the three payoff matrices which together describe the game.
 
@@
 
-Midwives play for \(A_{m}\) rounds (\(A_{m}=1000\) in all experiments), and conduct appointments in parallel, i.e.
+Midwives play for \(R_{m}\) rounds (\(R_{m}=1000\) in all experiments), and conduct appointments in parallel, i.e.
 if there are 5 midwives, then five women are drawn from the queue and assigned at random to the midwives.
@@
 Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.
+
+Formally then, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\).
+Additionally define a utility function \(u_{i}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=P_{s, s_{w}, \theta_{m}} + P_{h, \theta_{w}, s_{m}} + P_{c, \theta_{w}, s_{m}}\), and distributions over types \(p_{w}(l, m, h), p_{m}(l, m, h)\).
 
@@
 
-Formally we let \(S\) be the set of signals \(\{l, m, h\}\), \(T_{w}\) be the set of drinking types \(\{l, m, h\}\), \(T_{m}\) the set of midwife types \(\{l, m, h\}\), and \(J=\{r,n\}\) the actions available to midwives.
-The set of all payoffs shall be denoted \(P\), where \(P_{w}\) are the payoffs for all women\footnote{While it is assumed that \(P_{w}\) for an individual of type \(a\) is constrained such that \(T=\{a\}\), this can change under the modified game described in subsection \ref{sub:info_sharing}} defined by \(P_{w}=\{x | x=P_{h, b, c} + P_{s, a, d}\wedge b \in J\wedge c \in T\wedge d \in M\}\), and equivalently for midwives \(P_{m}=\{x | x=P_{h, b, c} + P_{c, b}\}\).
-
 \subsection{Lexicographic Heuristic}
@@
 one reason decision making.
-This approach requires minimal computation, and does not assume that all payoffs are known, or static.
+This approach requires minimal computation, and does not assume that \(u_{i}\) is static, or known.
 
-Women maintain a count, \(n\) for each of the \(k\) payoffs in \(P_{w, a},a\in k\), an individual payoff paired with a signal, such that \(n_{i}=\{n_{i,1}\ldots n_{i,k}\}\).
+Women resolve this by approximating the utility function, as a function \(f(s_{w}, \sigma)\) on their choice of signal and an unknown distribution, which maps to \(u_{w}\) - i.e.
+\(s_{w}\) is a choice between simple lotteries.
+The algorithm maintains a count, \(n\), of the number of occurrences of each outcome given the choice from \(s_{w}\).
 
-Midwives solve a slightly different problem, where the signal received may convey useful information.
-This is resolved by maintaining a separate count for each signal, i.e.
-\(n_{i,j}=\{n_{i,j,1}\ldots n_{i, j, k}\}\), and otherwise follow the same algorithm.
+Midwives solve a slightly different problem with more information, where \(s_{w}\) is known, and \(s_{m}\) is the lottery choice - \(f(s_{w}, s_{m},\sigma)\).
+This is resolved by maintaining a separate count for each signal (i.e.
+\(n_{s_{w},s_{m}}\)), and otherwise following the same algorithm.
 
@@
 
-The second Bayesian agent augments the payoff reasoning version by separating the two lotteries and assuming that \(P\) is a static, and known set of payoffs possible for the agent.
+The second Bayesian agent augments the reasoning of the simple payoff model, approximating \(u_{w}\) with a more complex function - \(f(s_{w}, \theta_{w}, \sigma_{s}, \sigma_{r})=g(s_{w}, \theta_{w}, \sigma_{s}) + h(s_{w}, \theta_{w}, \sigma_{r})\).
 For women, this means that they maintain two sets of beliefs: a Dirichlet mixture which represents the believed distribution of midwife types, and a second set linking signals to referrals.
@@
 
-Midwives reasoning centers determing the meaning of signals, since given the knowledge of what some signal \(i\) conveys about the true type of the sender, the payoff for an action is known.
+Midwives reasoning centers on determining the meaning of signals, since given the knowledge of what some signal \(i\) conveys about the true type of the sender, the payoff for an action is known.
 As such, their inference process is the same as for the simple Bayesian agent but over signal-type pairs, and they attempt to minimise -

### 2014-07-09 Model.tex
More notation fiddling

@@
 Formally then, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\).
-Additionally define a utility function \(u_{i}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=P_{s, s_{w}, \theta_{m}} + P_{h, \theta_{w}, s_{m}} + P_{c, \theta_{w}, s_{m}}\), and distributions over types \(p_{w}(l, m, h), p_{m}(l, m, h)\).
+Additionally define a utility function \(u_{i}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}}\), and distributions over types \(p_{w}(l, m, h), p_{m}(l, m, h)\).
 
@@
 \center
-\subfloat[Social cost, \(P_{s}\)\label{tab:Social-cost-matrix}]{%
+\subfloat[Social cost, \(X_{s}\)\label{tab:Social-cost-matrix}]{%
 \begin{tabular}{|c|c|c|c|c|}
@@
 
-\subfloat[Health outcome, \(P_{h}\)\label{tab:Referral-payoff-matrix}]{%
+\subfloat[Health outcome, \(X_{h}\)\label{tab:Referral-payoff-matrix}]{%
 \begin{tabular}{|c|c|c|c|c|}
@@
 
-\subfloat[Referral cost, \(P_{c}\)\label{tab:inst_cost_matrix}]{%
+\subfloat[Referral cost, \(X_{c}\)\label{tab:inst_cost_matrix}]{%
 \begin{tabular}{|c|c|c|c|c|}
@@
 a count of observations with no particular concern as to their order.
+As before, midwives follow a similar pattern but per signal.
 
-As before, midwives follow a similar pattern but per signal.
+\begin{equation}
+R_{w}(s_{w}) = \sum_{x\in \Theta} -xp(x | s_{w})
+\end{equation}
+\begin{equation}
+R_{m}(s_{w}, s_{m}) = \sum_{x\in \Theta} -xp(x | s_{w}\wedge s_{m})
+\end{equation}
 
@@
 The second Bayesian agent augments the reasoning of the simple payoff model, approximating \(u_{w}\) with a more complex function - \(f(s_{w}, \theta_{w}, \sigma_{s}, \sigma_{r})=g(s_{w}, \theta_{w}, \sigma_{s}) + h(s_{w}, \theta_{w}, \sigma_{r})\).
-For women, this means that they maintain two sets of beliefs: a Dirichlet mixture which represents the believed distribution of midwife types, and a second set linking signals to referrals.
-
-Formally, let \(D=\{D_{h}, D_{s}\}\), \(\alpha=\{\alpha_{h},\alpha_{s}\}\), and \(n=\{n_{h},n_{s}\}\). The quantity to be minimised then becomes -
+Women maintain two sets of beliefs, one each for \(g\) and \(h\), corresponding respectively to \(p_{m}\), and the probability of referral.
+This leads to the risk function -
 
 \begin{equation}
-R(i)= \sum_{z=1}\sum_{j=1}-P_{w, i, z, j}P(x=l|D_{s},\alpha_{s})P(x=j|D_{h},\alpha_{h})\label{eq:risk}
+R(s_{w}) = \sum_{i\in s_{m}}\sum_{j\in \theta_{m}} -u_{w}(s_{w}, s_{m, i}, \theta_{w}, \theta_{m, j})p(j)p(i | s_{w})
 \end{equation}
 
-So that the risk of a signal, \(i\) is the sum of all possible payoffs multiplied by the probability of that payoff occurring.
+So that the risk of a signal is the sum of the products of all payoffs with the probabilities of their entailed midwife types and responses.
 
@@
 \begin{equation}
-R(i, j)= \sum_{z=1}\sum_{j=1}-P_{m, i, z, j}P(x=l|D_{s},\alpha_{s})P(x=j|D_{h},\alpha_{h})\label{eq:mw_risk}
+R(s_{w}, s_{m}) = \sum_{i\in \theta_{w}} -u_{w}(s_{w}, s_{m}, \theta_{w, i}, \theta_{m})p(i | s_{w})
 \end{equation}

### 2014-07-09 Model.tex
Subsections

@@
 
-\subsection{Lexicographic Heuristic}
+\subsubsection{Lexicographic Heuristic}
 \label{sub:lexico}
@@
 
-\subsubsection{Bayesian Payoff Heuristic}
+\subsubsection{Bayesian Payoff}
 
@@
 
+Agents then choose $s_{i}$ to minimise $R_{i}$, which is simply - 
 \begin{equation}
@@
 
-The second Bayesian agent augments the reasoning of the simple payoff model, approximating \(u_{w}\) with a more complex function - \(f(s_{w}, \theta_{w}, \sigma_{s}, \sigma_{r})=g(s_{w}, \theta_{w}, \sigma_{s}) + h(s_{w}, \theta_{w}, \sigma_{r})\).
+The second Bayesian agent augments the reasoning of the simple payoff model, making the stronger assumption that the utility function is static, and known.
 Women maintain two sets of beliefs, one each for \(g\) and \(h\), corresponding respectively to \(p_{m}\), and the probability of referral.
@@
 \begin{equation}
-R(s_{w}) = \sum_{i\in s_{m}}\sum_{j\in \theta_{m}} -u_{w}(s_{w}, s_{m, i}, \theta_{w}, \theta_{m, j})p(j)p(i | s_{w})
+R_{w}(s_{w}) = \sum_{i\in s_{m}}\sum_{j\in \theta_{m}} -u_{w}(s_{w}, s_{m, i}, \theta_{w}, \theta_{m, j})p(j)p(i | s_{w})
 \end{equation}
@@
 \begin{equation}
-R(s_{w}, s_{m}) = \sum_{i\in \theta_{w}} -u_{w}(s_{w}, s_{m}, \theta_{w, i}, \theta_{m})p(i | s_{w})
+R_{m}(s_{w}, s_{m}) = \sum_{i\in \theta_{w}} -u_{w}(s_{w}, s_{m}, \theta_{w, i}, \theta_{m})p(i | s_{w})
 \end{equation}
@@
 And $\alpha$, and $\beta$ are respectively the power of a gain,
-and a loss. The \ac{CPT} value of outcome $x$ is $v(x)w^{+}(x)$
+and a loss, and \(x=u_{i}\). The \ac{CPT} value of outcome $x$ is $v(x)w^{+}(x)$
 if $x\geq0$, and $v(x)w^{-}(x)$ otherwise. For an action the \ac{CPT}

### 2014-07-09 Methods.tex
Match up notations, remove occlusions.

@@
 Name & Description & Value \\ \hline
-\(N_{w}\) & Number of women & 1000 \\ \hline
-\(N_{m}\) & Number of midwives & 100 \\ \hline
-\(R_{m}\) & Number of appointments per midwive & 1000 \\ \hline
-\(R_{w}\) & Maximum number of appointments per woman & 12 \\ \hline
+\(n_{w}\) & Number of women & 1000 \\ \hline
+\(n_{m}\) & Number of midwives & 100 \\ \hline
+\(r_{m}\) & Number of appointments per midwive & 1000 \\ \hline
+\(r_{w}\) & Maximum number of appointments per woman & 12 \\ \hline
 Runs & Simulation runs & 1000 \\ \hline
-\(P_{h,w}\) & Proportion of heavy drinkers & \(1/3\) \\ \hline
-\(P_{m,w}\) & Proportion of moderate drinkers & \(1/3\) \\ \hline
-\(P_{l,w}\) & Proportion of light drinkers & \(1/3\) \\ \hline
-\(P_{h,m}\) & Proportion of harsh midwives & \(5/100\) \\ \hline
-\(P_{m,m}\) & Proportion of moderate midwives & \(10/100\) \\ \hline
-\(P_{l,m}\) & Proportion of non-judgemental midwives & \(85/100\) \\ \hline
-\(p_{w}\) & Probability of women sharing & 0. \\ \hline
-\(q_{w}\) & Weight of shared information for women & 0. \\ \hline
-\(p_{m}\) & Probability of midwives sharing & 0. \\ \hline
-\(q_{m}\) & Weight of shared information for midwives & 0. \\ \hline
+\(p_{w}(h)\) & Proportion of heavy drinkers & \(1/3\) \\ \hline
+\(p_{w}(m)\) & Proportion of moderate drinkers & \(1/3\) \\ \hline
+\(p_{w}(l)\) & Proportion of light drinkers & \(1/3\) \\ \hline
+\(p_{m}(h)\) & Proportion of harsh midwives & \(5/100\) \\ \hline
+\(p_{m}(m)\) & Proportion of moderate midwives & \(10/100\) \\ \hline
+\(p_{m}(l)\) & Proportion of non-judgemental midwives & \(85/100\) \\ \hline
+\(q_{w}\) & Probability of women sharing & 0. \\ \hline
+\(w_{w}\) & Weight of shared information for women & 0. \\ \hline
+\(q_{m}\) & Probability of midwives sharing & 0. \\ \hline
+\(w_{m}\) & Weight of shared information for midwives & 0. \\ \hline
 \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 10:1 \\ \hline
@@
 Name & Description & Min & Max \\ \hline
-\(P_{h,w}\) & Proportion of heavy drinkers & 0 & 1 \\ \hline
-\(P_{m,w}\) & Proportion of moderate drinkers & 0 & 1 \\ \hline
-\(P_{l,w}\) & Proportion of light drinkers & 0 & 1 \\ \hline
-\(P_{h,m}\) & Proportion of harsh midwives & 0 & 1 \\ \hline
-\(P_{m,m}\) & Proportion of moderate midwives & 0 & 1 \\ \hline
-\(P_{l,m}\) & Proportion of non-judgemental midwives & 0 & 1 \\ \hline
-\(p_{w}\) & Probability of women sharing & 0 & 1 \\ \hline
-\(q_{w}\) & Weight of shared information for women & 0 & 1 \\ \hline
-\(p_{m}\) & Probability of midwives sharing & 0 & 1 \\ \hline
-\(q_{m}\) & Weight of shared information for midwives & 0 & 1 \\ \hline
-\(P_{h,}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
-\(P_{c, r}\) & Cost for referral & \multicolumn{2}{l|}{\(-(Payoff_{baby} - 1)\)} \\ \hline
+\(p_{w}(h)\) & Proportion of heavy drinkers & 0 & 1 \\ \hline
+\(p_{w}(m)\) & Proportion of moderate drinkers & 0 & 1 \\ \hline
+\(p_{w}(l)\) & Proportion of light drinkers & 0 & 1 \\ \hline
+\(p_{m}(h)\) & Proportion of harsh midwives & 0 & 1 \\ \hline
+\(p_{m}(m)\) & Proportion of moderate midwives & 0 & 1 \\ \hline
+\(p_{m}(l)\) & Proportion of non-judgemental midwives & 0 & 1 \\ \hline
+\(q_{w}\) & Probability of women sharing & 0 & 1 \\ \hline
+\(w_{w}\) & Weight of shared information for women & 0 & 1 \\ \hline
+\(q_{m}\) & Probability of midwives sharing & 0 & 1 \\ \hline
+\(w_{m}\) & Weight of shared information for midwives & 0 & 1 \\ \hline
+\(X_{h,}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
+\(X_{c, r}\) & Cost for referral & \multicolumn{2}{l|}{\(-(X_{h} - 1)\)} \\ \hline
 \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 1:1 & 100:1 \\ \hline

### 2014-07-09 Model.tex
Match up notations, remove occlusions.

@@
 Women are drawn in order from a queue, and play against a midwife chosen at random.
-They play for a maximum of 12 rounds (following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred.
+They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred.
 At which point a new player is drawn from the same distribution that produced the original players to replace them.
@@
 
-Midwives play for \(R_{m}\) rounds (\(R_{m}=1000\) in all experiments), and conduct appointments in parallel, i.e.
+Midwives play for \(r_{m}\) rounds (\(r_{m}=1000\) in all experiments), and conduct appointments in parallel, i.e.
 if there are 5 midwives, then five women are drawn from the queue and assigned at random to the midwives.
@@
 Formally then, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\).
-Additionally define a utility function \(u_{i}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}}\), and distributions over types \(p_{w}(l, m, h), p_{m}(l, m, h)\).
+Additionally define a utility function \(u_{i}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}}\), and distributions over types \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\).
 
@@
 of signal-payoff pairs, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
-more than zero and summing to less than 1, and \(\alpha_{i}\) is the integer
+more than zero and summing to less than 1, and \(\alpha_{i}\) is the 
 psuedo-count of prior observations for a pair \(i\).
@@
 \begin{equation}
-R_{w}(s_{w}) = \sum_{x\in \Theta} -xp(x | s_{w})
+R_{w}(s_{w}) = \sum_{x \in X} -xp(x | s_{w})
 \end{equation}
 \begin{equation}
-R_{m}(s_{w}, s_{m}) = \sum_{x\in \Theta} -xp(x | s_{w}\wedge s_{m})
+R_{m}(s_{w}, s_{m}) = \sum_{x \in X} -xp(x | s_{w}\wedge s_{m})
 \end{equation}
+
+Where $X$ is set of payoffs the agent has observed to follow $s$.
 
@@
 The second Bayesian agent augments the reasoning of the simple payoff model, making the stronger assumption that the utility function is static, and known.
-Women maintain two sets of beliefs, one each for \(g\) and \(h\), corresponding respectively to \(p_{m}\), and the probability of referral.
+Women maintain two sets of beliefs, corresponding respectively to \(p_{m}\), and the probability of referral given signal choice.
 This leads to the risk function -
@@
 It would seem unreasonable to suppose that neither party recounts their experiences to their peers, and to explore the impact of this we also modify the game to introduce a simple form of information sharing within agent groups.
-This takes the form of having each agent share their memories with their colleagues with some probability \(p\).
-Individuals then incorporate shared information into their beliefs using weighted updates, such that a shared observation of a low type signal contributes to their beliefs by \(q\), and \(0\leq q\leq 1\) (i.e.
-\(n_{j} = n_{j} + q\)).
+This takes the form of having each agent share their memories with their colleagues with some probability \(q\).
+Individuals then incorporate shared information into their beliefs using weighted updates, such that a shared observation of a low type signal contributes to their beliefs by \(w\), and \(0\leq w\leq 1\) (i.e.
+\(n_{j} = n_{j} + w\)).
 Women share only when they have finished play, and provide their complete history of games, because they have accurate information about the outcomes.

### 2014-07-11 Background.tex
Pruning background

@@
 highlighting binge drinking as of particular concern.
-
-There has recently been an increased interest in the impact of binge
-drinking, as a distinct pattern of consumption, with a wide variety
-of negative outcomes reported by \citet{Maier2001}, although a significant
-portion of their evidence base is drawn from animal studies which
-augers for caution in generalising findings to humans. \citet{Strandberg-larsen2008}
-explored links between binge drinking, and stillbirth, reporting a
-statistically significant increase in risk associated with more than
-three antenatal binge episodes. \citet{Sun2009} looked at seizure
-disorders in children whose mothers binged during pregnancy. They
-reported significantly greater risk of both neonatal seizures (\textasciitilde{}3
-fold) and epilepsy (1.81 fold) associated with binge drinking between
-11 and 16 weeks, but emphasised the exploratory nature of the results,
-and need for replication. In terms of neurodevelopmental outcomes,
-\citet{Streissguth1994} found a dose dependent association with scores
-on timed word, and arithmetic tests in fourteen year olds with a stronger
-association where bingeing occurred. A review by \citet{Henderson2007}
-cautiously supports the contention that binge drinking has a neurodevelopmental
-impact, but found no consistent support for adverse outcomes in pregnancy
-(e.g. stillbirth, miscarriage, etc.) and note a paucity of studies
-in the area. \citet{Meyer-Leu2011} considered the neonatal period,
-finding that both moderate and binge drinking were associated with
-an increased trend towards neonatal asphyxia. They also noted a large
-number of contradictory findings and raising methodological concerns
-about the studies reviewed by \citeauthor{Henderson2007}. \citet{Barr2006}
-contend that binge drinking may also contribute to psychiatric issues
-in the later life of offspring, although in this case their findings
-are confined to individuals with \ac{FAS}, which may in itself be
-a confounding factor, rather than indicating a directly causative
-relationship between antenatal binge drinking and subsequent psychiatric
-disorder in offspring.
 
@@
 midwives and women for building up a trust relationship, itself a
-key component of facilitating disclosure. \citet{Stevens2002} looked
-specifically at the process of transitioning to a caseloading model
-of care provision in one midwifery practice, reporting that both practitioners
-and women felt that this offered advantages in terms of long term
-relationship building. Relationship building was also highlighted
-by \citet{Kennedy2004} in a narrative investigation of midwifery
-practice, where the subjects interpreted the midwife-woman dynamic
-as about mutuality. \citeauthor{Kennedy2004} suggest that this arises
-from a recognition that interactions in this context are about information
-exchange, with the knowledge base of the woman as significant as that
-of the midwife, rather than simply a unidirectionally didactic relationship.
-
-\citet{Hunter2006} also focuses on much of midwifery as about relationship
-building, suggesting that there is an insufficiently recognised emotional
-labour component to practice. Observation and interview of a number
-of midwives as they practiced suggested that many midwives effectively
-took a mother type role to their patients, with implications around
-the nature of information exchange that was able to take place. The
-emotional labour component was also reported by \citeauthor{Stevens2002},
-who suggest that this is more evident under a caseloading system, particularly
-with challenging patients with complex needs. \citet{Todd1998} surveyed
-midwives working in a hospital environment, as well as those working
-in the community in a caseloading context, finding that community
-practice appeared to provide more job satisfaction, but was challenging
-to implement effectively because of limited resources. Community midwives
-suggested that larger team sizes, and smaller caseloads would contribute
-to a better realisation of the model. \citet{Farquhar2000} approached
-the same question from the perspective of women, also finding that
-faulty implementation hampered the expected benefits. They found that
-those cared for under a team scheme, with much higher continuity of
-care, reported that they had a better relationship with their midwives,
-but were not more satisfied in general with their care. In contrast,
-\citet{Biro2003} looked at a \ac{RCT} of team midwifery care versus
-hospital care in Australia, finding a significantly higher level of
-satisfaction under the team model, the distinction in this case may
-lie in the different balance of team size to caseload size.
-
-In terms of the impact of continuity of care on health, rather than
-experiential outcomes, research is relatively sparse. \citet{Marks2003}
-examined the impact of continuity of care on \ac{PND}, which has
-similar features to alcohol in that it carries an associated stigma
-that can act as a barrier to help seeking \citep{Dennis2006}. Based
-on the results of a \ac{RCT}, they conclude that continuity of care
-is not protective, in the sense of reducing rates or impacting onset,
-but was very successful in supporting engagement with treatment. Echoing
-this, a 2009 Cochrane Review by \citet{Hatem2009} found no significant
-difference in incidence of \ac{PND}, but reported benefits in terms
-of lower rates of \gls{episiotomies}, anaesthesia, and shorter hospital
-stays, with higher satisfaction as found by \citeauthor{Biro2003}.
-While research in this area does not specifically pertain to disclosure,
-the general trend in results are suggestive when taken in concert
-with studies emphasising the importance of relationship building as
-key in fostering a disclosure friendly environment. Continuity of
-care is generally regarded as improving patient experience, and leading
-to better health outcomes in the wider medical arena \citep{VanWalraven2010},
-but is clearly not a cost free endeavour, with particular concern
-arising from the emotional cost \citep{Todd1998}, and increased rates
-of `\gls{burnout}' in practitioners \citep{Sandall1997}.
+key component of facilitating disclosure.
 

### 2014-07-16 Background.tex
Working on introduction

@@
 %!TEX root = disclosure_game.tex
+%Rewrite all of this, ditch the alcohol stuff altogether. Any really key can be woven in elsewhere (discussion)
 \section{Background}
@@
 
-This section presents a brief overview of literature focusing on the impact
-of drinking behaviour in pregnancy, and factors affecting disclosure
-behaviour in the midwifery context. This is followed by a review of
-literature supporting the theoretical underpinning of the modelling
+This section presents a brief overview of literature focusing on the theoretical underpinning of the modelling
 approach, with particular reference to statistical decision theory.
-
-\subsection{Alcohol, and Disclosure in the Maternity Setting}
-\label{sub:alcohol_disclosure}
-
-\subsubsection{Impact of Alcohol\label{sub:Impact-of-Alcohol}}
-
-Distinct from stigma attached to alcohol consumption in pregnancy,
-is the question of the real impact on woman and baby both in the \gls{antenatal}
-period, and beyond. While the canonical example of alcohol linked
-disorders is \ac{FAS}, and others on that spectrum, heavy drinking
-during pregnancy has been mooted as a factor in a variety of negative
-health outcomes.
-
-The impact of moderate alcohol consumption in pregnancy is more contested.
-For example, \citet{Andersen2012} examined moderate drinking in a
-large Danish cohort study, finding a significant increase in the risk
-of spontaneous abortion at low levels of consumption early in pregnancy.
-\citet{Savitz2012} questioned the extent to which this can be interpreted
-as a causal connection, noting that there is a known relationship
-between absence of morning sickness, and spontaneous abortion, and
-suggesting that this may explain much of the difference in risk. \citet{Kesmodel2002}
-examined the relationship between alcohol consumption and still-birth,
-finding that increased consumption lead to an increase in risk to
-the baby, but in contrast to \citet{Andersen2012} this was significant
-at \gls{term}.
-
-Considering longer term negative outcomes, a metastudy by \citet{Latino-Martel2010}
-examined the potential for maternal alcohol consumption in pregnancy
-to feature as a risk factor for onset of childhood leukaemia, finding
-that any alcohol consumption was associated with an increased risk
-of childhood \ac{AML}, but note the rarity of the condition as a
-limitation.
-
-\citet{Huizink2006} reviewed literature looking at the impact of
-moderate consumption on neurodevelopmental and cognitive outcomes,
-concluding that maternal consumption can be a contributing factor
-to \ac{ADHD}, and impairments to learning and memory. They subsequently
-suggest that the underlying mechanism is not specific to alcohol consumption,
-but a more general phenomena arising from perturbations to foetal
-conditions \citep{Huizink2009}, but caution that methodological issues
-in many of the studies reviewed may undermine this hypothesis.
-
-Contrary to this, a meta-study by \citet{Gray2006} found there was
-insufficient evidence to suggest any harm arising from moderate (under
-1.5 UK units per day) alcohol consumption. This ties to the current
-guidance from the \ac{NICE} \citep{NICE2010a}, advising that women
-should avoid drinking at all in at least the first three months of
-pregnancy, and no more than 1-2 units once or twice a week if they
-do. In giving this advice, \ac{NICE} acknowledge that the risks to
-the foetus from alcohol are a somewhat contentious subject, concluding
-that the evidence of harm is inconclusive, but that this is not sufficient
-to rule out the risk of negative outcomes. This tension is reflected
-by earlier guidance from the \ac{RCOG} \citep{Gynecologists1996}
-suggesting no evidence of harm below 15 units per week, and subsequent
-criticism by \citet{Guerri1999}, who suggest that this might be interpreted
-as legitimising \gls{binge}, while noting several studies indicating
-adverse affects linked to even a single drink per day (e.g. \citet{Day1990}).
-A subsequent \ac{RCOG} statement \citep{RoyalCollegeofObstetriciansandGynaecologists2006}
-revised the recommendations to incorporate newer findings, advising
-that there is no known safe threshold for drinking in pregnancy, and
-highlighting binge drinking as of particular concern.
-
-Overall, there is a distinct lack of consensus on what, and how extensive,
-the effects of drinking on the immediate and long term health outcomes
-are for the child.
-
-\subsubsection{Disclosure}
-
-The issue of disclosure is central to the model presented here, in
-particular self-report by women of information that might disadvantage
-them, or be expected to do so in the immediate term. In general, the
-consensus is that alcohol self-reports have acceptable validity in
-the research context \citep{DelBoca2000}, but do not correspond perfectly
-to alternative methods. \citet{DelBoca2003} claim that the validity
-is generally accepted, and suggest that the current focus lies on
-what factors and processes underlie the discrepancies rather than
-questioning determining their existence. In this instance, the conjecture
-is that the information is in some way stigmatising; that, following
-\citet{Goffman1999}, disclosure equates to revelation of the mark.
-This is not immediately contentious, for example \citet{Gomberg1988}
-identified stigma surrounding alcohol abusing women in particular,
-an issue also highlighted by \ac{IAPT} guidance \citep{IAPT2012},
-as well as a number of other studies relating response effects to
-perceived negative consequences \citep{Langenbucher2001,DelBoca2000,Blair1977}.
-In the maternity context, \citet{Radcliffe2011} identifies stigma
-pertaining to substance misusing women amongst staff, and suggests
-that this may represent a barrier to appropriate treatment; similarly,
-\ac{NICE} guidance on pregnancy and complex social factors \citep{NICE2010}
-recognises concern about the attitude of staff as a source of anxiety
-in pregnant women who misuse substances.
-
-Stigma, or fear of a judgemental response on the part of the practitioner
-should not however be taken uncritically to explain inaccurate reporting
-by patients. While recent \ac{NICE} public health guidance advocates
-routine alcohol misuse screening as a part of all practice \citep{NationalInstituteforHealthandCareExcellence2010},
-there is no specific policy for routine antenatal care beyond providing
-information on possible impacts of alcohol consumption \citep{NICE2010a}.
-\ac{NICE} guidance on pregnancy and complex social factors \citep{NICE2010}
-does specifically address women who misuse alcohol, but presupposes
-knowledge of the problem through medical history, or via other services.
-Taken in concert with the potential for harm from even moderate alcohol
-use (section \ref{sub:Impact-of-Alcohol}), this suggests that much
-of the onus is on the patient to volunteer information.
-
-Where screening is used, \citet{Kaskutas2000} note that the most
-basic method, i.e. number of standard drinks consumed, can lead to
-inaccurate estimates of consumption arising from inability to relate
-the concept of a standard drink, to actual consumption. This is compounded
-by the impact of memory effects on recall over a number of days \citep{Stockwell2004},
-and a lack of consistency in the standard drink measure \citep{Turner1990}.
-Alternative screening tools, for example \acs{AUDIT}, and \acs{T-ACE}
-are available and have been shown to perform well in identifying problematic
-levels of drinking \citep{Piccinelli1997,Bradley1998,Russell1994,Russell1996},
-although the emphasis in these cases is on consumption at disordered
-levels.
-
-\citet{Prior2003} considered a different health arena (mental health
-problems and GPs), with similar characteristics in terms of concealment
-of medically relevant information. The central finding in this case
-is that non-disclosure is not a result of stigma, but of mismatched
-ontologies surrounding mental illness. Work by \citet{Alvik2005},
-where the relationship between anonymity and reporting of alcohol
-consumption by pregnant women was investigated, found no significant
-relationship, suggesting that a fear of social judgement may not be
-a dominant factor. This draws an interesting contrast with a study
-by \citet{Alvik2006}, which found that contemporaneous reports of
-consumption were significantly lower than those postpartum. Logistic
-regression results suggest that this trend is amplified by a number
-of factors, including level of alcohol consumption preceding conception,
-while anxiety about foetal wellbeing during pregnancy was associated
-with lower retrospective reports. Taken together with \citep{Alvik2005},
-these results could be seen as conflicting, but may suggest self-stigmatisation
-\citep{Watson2007}, or reflect a lack of distinction between anonymity,
-and confidentiality \citep{Malvin1983}.
-
-In summation then, there is a consensus that alcohol consumption is
-generally underreported in the pregnant population, with some support
-for the idea that concern about social judgement associated with stigmatisation
-may be a contributing factor. Of particular interest in the wider
-context of this work, is the relationship between underreporting and
-consumption, i.e. that heavier drinking is associated with a greater
-tendency to understate intake.
-
-\subsubsection{Practice Implications}
-
-Given that alcohol consumption is thought to be underreported some
-consideration must be given to the implications for midwifery practice,
-in terms of eliciting more accurate self-reporting. \citet{Phillips2007}
-present a qualitative account of factors influencing the disclosure
-of substance misuse to midwives, identifying particularly the need
-to build up a rapport, potentially over a number of appointments.
-This was related to continuity of care, seen as necessary by both
-midwives and women for building up a trust relationship, itself a
-key component of facilitating disclosure.
 

### 2014-07-16 Introduction.tex
Working on introduction

--- 2014-07-03 Introduction.tex
@@
 %Also, remember to say what you're going to do for the rest of the article?
+%CONTRIBUTION
+%	Agents are awesome
+%	Decision theory is super awesome
+%	'nice story to hang it on'
+% 	mention the importance of behaviour change
+
+In this paper we extend previous work by \cite{GrayDissert}.
+
+The case in favour of \ac{ABM} as a general approach has been made numerously, and elegantly REFS.
+As such we will not belabour the point, and instead turn to addressing some of the concerns expressed about the method.
+In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, tending to be a reflection of the assumptions of the modeller rather than empirically or theoretically grounded \citep{Waldherr2013}.
+To ameliorate this concern, we draw on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game \citep{Kreps1987} with a basic form of intragroup information sharing.
+Four decision models of varying complexity, and behavioural plausibility are contrasted, by way of demonstrating the significance of the operationalisation of decision making in \ac{ABM}.
+
+This is framed in the context of disclosure decisions, and a scenario examining drinking patterns in pregnant women which is presented in the spirit of a motivating example, rather than claimed as an accurate representation of reality.
+Alcohol consumption in the ante natal period is a significant issue in itself, and has been associated with many potentially negative consequences.
+For example, \citet{Andersen2012} report results from a large scale Danish cohort study suggesting that even low levels of consumption in early pregnancy increase the risk of spontaneous abortion, although \citet{Savitz2012} has suggested this may be attributable to a previously known link to absence of mornining sickness.
+Risk continues to the point of birth - \citet{Kesmodel2002} found a heightened risk to the infant - into childhood, with a metastudy by \citet{Latino-Martel2010} finding evidence on an increased risk of childhood \ac{AML} (although they suggest that the rarity of the condition is a limitation).
+Harm may also extend even further, and a review by \citet{Huizink2006} concluded that maternal alcohol consumption could be a contributing factor to \ac{ADHD}, and other learning impairments, but note methodological issues in a number of the papers.
+There is not, however, a clear consensus, with \citet{Gray2006} finding no evidence of harm below 1.5 UK units per day.
+In terms of official guidance, \ac{NICE} acknowledge that evidence of harm to the fetus is less than conclusive, but advise not drinking at all, or significant moderation \citep{NICE2010a}, with similar advice from the \cite{DepartmentofHealth2008}.
+
+Turning more specifically to disclosure of alcohol use during pregnance, research is relatively sparce, although qualitative trends are reported by \citet{Phillips2007}, and \citet{Alvik2006}.
+The former explored factors impacting disclosure through a small case study, highlighting the need to build up rapport over several appointments; the latter compared post partum reports of consumption with contemporaneous accounts, finding apparent underreporting during pregnancy which was amplified by increased drinking.
+The simulation model described in this paper is able to replicate both qualitative trends, i.e.
+an increase in disclosure over appointments, and more honest behaviour by moderate as compared to heavier drinkers.
+
+This scenario is of substantial independent interest, and shows the potential utility of a simulation approach in arenas where \ac{RCT} are not viable for ethical, or financial reasons.
+With this said, the lack of a strong quantitative evidence base against which to validate the behaviour of the model augers for caution in interpreting the results, and a necessary reminder that in this instance the focus is primarily methodological.
+
+two fold appeal. cognitive plausibility - neuroec. inaccessible systems (litigation, concealment). fast. cheap. portable. theoretical grounding. rigor.
+
+A game theoretic approach to generating an abstract form of the problem gives a convenient, and well known framework to reason about the processes involved in the scenario.
+While scenarios may well map to a plurality of games, this still allows for a principled comparison between interpretations and enforces explicit assumptions.
+Relating this to decision theory shifts the emphasis away from analytical equilibrium-seeking, and heightens the importance of behaviour change.
+Where the focus is on the behavioural processes driving a system in motion, and how they change in response to that movement, this is clearly desirable.
+Fundamentally, the shift of emphasis is from the process of acquiring and inferring the information needed to make choices, to the process of decision.
+Naturally, this does not preclude the incorporation of strategic refinement, since decision rules are to a great extent modular, and as demonstrated in this paper can be exchanged without altering the underpinning decision problem.
+In addition, rules are agnostic as to where the information used derives from, suggesting room for multi-stage processes.
+As a corollary, the decision problem agents attempt to answer can change, allowing agents' behaviour in novel problems to be informed by beliefs derived under other conditions.
+
+A key motivation for decision rules is their claim to provide an account of decision making that is behaviourally and cognitively plausible.
+Their mooted capability in this regard is to some extent supported by work from neuroeconomics, which aims to empirically test theories of decision making \citep{Rustichini2009}.
+Many key aspects common to decision rules, for example the idea that a common currency is used by the brain to compare outcomes \citep{Padoa-Schioppa2006,Padoa-Schioppa2008}, are supported by neurological findings.
+
+Given these features, the application of decision, and game theory to \ac{ABM} is an attractive approach to computational social science, where the locus of interest is decision making.
+Taking a balance between the strongly biological, e.g.
+neural networks, and the more abstract threshold, or microsimulation like models yields a computationally tractable approach.
+Despite the relative simplicity, it nonetheless captures some of the nuance and sophistication of human decisions.
+
+%Finishing up
+
+The remainder of this paper proceeds to provide a brief review of the methodological context (\ref{sub:games_signals}), before outlining the model (\ref{sec:model}), and experiments (\ref{sec:method}), with selected results (\ref{sec:results}), then closing with a discussion contrasting the decision models (\ref{sec:conclusion}).

### 2014-07-16 Model.tex
Remove implicit insult to frequentist approach
Tweak notation to make Risk calculation clearer
Working on introduction

@@
 While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same outputs, we limit ourselves here to four.
-The simplest is a lexicographic rule (1), motivated as in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; a Bayesian risk minimisation rule using the same information (2); a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \cite{Hau2008} agent (4) which is identical with 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}.
+The simplest is a lexicographic rule (1), motivated as in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; a Bayesian risk minimisation rule using the same information (2); a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical with 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}.
 Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-ouput characteristics.
@@
 \begin{equation}
-R_{w}(s_{w}) = \sum_{i\in s_{m}}\sum_{j\in \theta_{m}} -u_{w}(s_{w}, s_{m, i}, \theta_{w}, \theta_{m, j})p(j)p(i | s_{w})
+R_{w}(s_{w}) = \sum_{i\in s_{m}}\sum_{j\in \theta_{m}} -u_{w}(s_{w}, s_{m, i}, \theta_{w}, \theta_{m, j})p(s_{m,i})p(i | s_{w})
 \end{equation}
@@
 While \ac{CPT} has primarily been applied in the context of decisions from description, it has been modified to deal with decisions from experience by incorporating a first stage where probabilities are estimates from observations as in \cite{FoxCPT}.
-In this instance we replace the frequentist first stage with the equivalent Bayesian inference process.
+In this instance the Bayesian inference process fills the first stage role.
 
+%Maybe cut this bit and make explanation richer?
 Rather than the psychologically more interesting \ac{PT}, the \ac{CPT}

### 2014-07-16 Background.tex
Rewriting background

@@
 %Rewrite all of this, ditch the alcohol stuff altogether. Any really key can be woven in elsewhere (discussion)
-\section{Background}
+\section{Previous Research}
 
@@
 
-This section presents a brief overview of literature focusing on the theoretical underpinning of the modelling
-approach, with particular reference to statistical decision theory.
+This section presents a brief overview of previous research, addressing in turn signalling games, normative decision theory, heuristic decision making, and descriptive decision theory.
 
-\subsection{Games, Signals, and Decisions}
-\label{sub:games_signals}
+\subsection{Signalling Games}
 
-\subsubsection{Signalling Games}
+The preponderance of classical game theory focuses on strategic decision making, in scenarios where all players have complete information about all aspects of the game.
+An alternative, perhaps more common situation, is that players have incomplete information, i.e.
+their knowledge of the rules of play is in some way deficient.
+\citet{Harsanyi1967} introduced the concept of a Bayesian game, resolving the problems introduced by the incomplete information scenario by allowing the possible variations on the rules to be treated as subgames.
+This adds an additional player - nature, to the game, where nature takes the first move thereby deciding which subgame is played.
+Nature is assumed to make their move by lottery, and where the probability distribution governing the lottery is known to all players this permits the game to be formulated as one of complete information.
+Here, we are specifically interested in signalling games \citep{Kreps1987,Spence1973}, where one player holds some private information which may be communicated (or not) by means of a signal.
 
-Game theory generally deals with strategic decision making in the
-unusual circumstance of complete information, that is, every player
-has at least complete knowledge of all possible outcomes, who their
-opponents are, and so forth. Arguably more generally applicable is
-the incomplete information scenario, where players lack information
-about the rules of play in some fashion. \citet{Harsanyi1967} proposed
-a method for effectively transforming such games into games of complete
-information by treating the possible variations on the rules as subgames.
-To determine which subgame is to be played, an additional player -
-nature - is introduced to make the first move, where nature conducts
-a lottery according to some probability distribution. If it is assumed
-that the underlying probability distribution is known to all players,
-the game is then one of complete information.
+This basic form has been widely applied, with substantial interest in what conditions permit honest signalling as Nash equilibria or \ac{ESS}.
+\citet{Grafen1990}, following from a suggestion by \citet{Zahavi1975}, proposed that if signals intended to indicate mate quality exacted a cost on the signaller (e.g.
+peacock tail feathers), then honest signalling would constitute an \ac{ESS}.
+\citet{Spence1973} demonstrated similar results in a game of job market signalling, where signal cost was differentiated by type.
+Costly signalling has also been suggested as an explaination of behaviour that at first gasp appears counter intuitive, for example \citet{Godfray1991} applied the idea to the food solicitation behaviour of chicks, where a stronger signal carries a risk of being eaten.
+Moving beyond animal behaviour, \citet{Sosis2003} considered the implications if ritual behaviour, in the context of religion, represented a costly signal, an idea subsequently extended by \citet{Henrich2009} to include cultural transmission, and \citet{Wildman2011} to introduce group differentiation.
 
-Perhaps the best known example of Bayesian games, are the signalling
-games codified by \citet{Kreps1987}, after initially being framed
-by \citet{Spence1973} in the context of employment markets. The general
-form of such a game is that one player holds information known only
-to them, on the basis of which they send a signal to the other player(s),
-which the other player(s) then act upon. Much of the interest in signalling
-games turns on what conditions are necessary for honest signalling
-to be a Nash equilibrium, or in the context of evolutionary game theory,
-an \ac{ESS} .
+Other work augments the signalling game model, for example \citet{Austen-Smith2005} adds a second `peer group' audience signalling game to the original \citeauthor{Spence1973} game in an effort to explain poor academic performance in some social groups, with some subseqent empirical support for the idea from \citet{Jr2010}.
+On a similar tack, \citet{Feltovich2002} introduced additional noisy type information, finding that this effectively explained counterintuitive observed behaviour where actors with every right to boast of their quality faail to do so.
 
-One approach to this requires that signalling is a costly exercise,
-as proposed by \citet{Grafen1990} in examining biological signals
-(for example, the eye-catching but unwieldy peacock tail). \citeauthor{Grafen1990}
-demonstrated that an earlier suggestion by \citet{Zahavi1975}, who
-proposed that such signals were in effect a handicap demonstrating
-fitness, would lead to an \ac{ESS} because of the costly nature of
-the signalling. This solution is also noted by \citet{Spence1973},
-who showed that a separating equilibrium exists%
-\footnote{In fact, an infinite number of them.%
-} contingent on signals being more costly for some types.
+\subsection{Normative Decision Theory}
 
-Costly signalling has been applied to explain a variety of apparently
-contradictory behaviours, for example \citet{Godfray1991} in the
-context of offspring soliciting food from parents, where the key question
-is why a behaviour with potentially very high costs (namely, being
-eaten) would be preferred to a less risky method. In a social context,
-costly signalling has been proposed as an explanation for religion
-in human societies. \citet{Sosis2003} developed a model of religious
-ritual as an exercise in costly signalling, showing that higher costs
-to engagement in rituals for skeptics maintains the stability of religious
-groups and the presumed benefits that membership confers. \citet{Henrich2009}
-extended this idea, and developed an evolutionary model combining
-cultural transmission with costly signalling in a population, finding
-that for even modest costs the system moved towards universal belief.
-\citet{Wildman2011} subsequently extended the model, to address the
-fact that both stable equilibria are binary states, finding that the
-incorporation of group differentiation allowed subgroups to persist.
+Where game theory addresses strategic decision making, decision theory deals instead with rational decision making \citep{Peterson2009}.
+Taken literally, this leads to normative decision theory, where the focus is on giving the rational answer to a decision problem.
+An alternative view - descriptive, or behavioural decisin theory, holds that the focus should instead be on giving an account of human decision making, complete with observed deviations from perfect rationality, which we address in section \ref{sub:descriptive_theories}.
+Finally a third perspective, which to some extent overlaps this division, suggests that decisions are heuristic in nature and rational in ecological context (section \ref{sub:heuristic_theories}).
 
-Signalling games have also been extended to provide models of other
-observed human behaviour, for example \citet{Austen-Smith2005} attempted
-to explain the observed poor academic attainment of some social groups
-by positing a multiple audience signalling game. They found that the
-introduction of a secondary signalling game with a peer audience,
-alongside the prototypical \citeauthor{Spence1973} model introduced
-a pooling equilibrium. Subsequent empirical work by \citet{Jr2010}
-has provided some support for this idea. Along similar lines, \citet{Feltovich2002}
-examine an observed failure by high quality types to signal as would
-be anticipated, introducing the concept of countersignaling in scenarios
-where there is noisy leakage of type information. They found that
-where there is added noisy type information available, separating
-equilibriums exist where high quality senders signal either as low
-quality, or not at all.
+The conceptual underpinning of all of these is the central idea of expected utility, originated by \citet{Bernoulli1954} and later formalised by \citet{Neumann1953}, which treats all decisions as gambles defined in terms of payoffs and probabilities.
 
-\subsubsection{Bayesian Decision Theory and Expected Utility}
+\subsection{Heuristic Decision Making}\label{sub:heuristic_theories}
 
-Decision theory is the theory of rational decision making \citep{Peterson2009},
-this contrasts with game theory which is concerned with strategic
-decision making. In the broadest sense, the field can be divided into
-two types of theories: normative, and descriptive. Normative theories
-are those which attempt to give the rational answer to a decision
-problem, descriptive or behavioural theories focus instead on characterising
-the process of human decision making. In this instance, the particular
-concern is with theories of decision making under uncertainty.
+As noted, heuristic decision making stems from a contention that \citeauthor{Neumann1953} type rationality ignores the context of decision making.
 
-Underpinning almost all theories of decision making, and much of economic
-theory in general is the concept of expected utility, originally proposed
-by \citet{Bernoulli1954}. This casts decisions as choices between
-lotteries or gambles, with differing payoffs and probabilities.
+\subsection{Descriptive Decision Theory}\label{sub:descriptive_theories}
+
+While normative theories are concerned with how decisions should be made, descriptive theories instead focus on how decisions are made.
 

### 2014-07-16 Background.tex
Heuristics & descriptive

@@
 
-As noted, heuristic decision making stems from a contention that \citeauthor{Neumann1953} type rationality ignores the context of decision making.
+As noted, heuristic decision making stems from a contention that \citeauthor{Neumann1953} type rationality ignores the both context of decision making, and a lack of correspondence between predicted and actual human decisions (see, for example the Allais paradox \citep{Society2013}, and subsequent empirical support \citep{Oliver2003,Burke1996}).
+Arguably, this begins with \citet{Simon1956}, who suggested that humans do not attempt to make optimal choices, but to satisfice and choose the first `good enough' option.
+While noting that this will often achieve the same result, the claim is that humans exhibit bounded rationality \citep{Simon2000} arising from inherent limits to cognition.
+
+\citet{Gigerenzer1996} take the concept of bounded rationality further, and argue for what they term \ac{FFH}.
+This recasts rationality as bound to the context of the behaviour - a rational approach to choosing the right mate might well require checking every possible partner, but given finite time, memory, and so on rapidly becomes nonsensical.
 
@@
 
-While normative theories are concerned with how decisions should be made, descriptive theories instead focus on how decisions are made.
+While heuristic theories arguably fall under the purview of the descriptive, the wider tendency is towards what are in essence patches to normative models.
+The most influential models in this class derive from \ac{PT} \citep{Kahneman1979}, which combines a set of heuristics based on observed decision behaviour, with distortions to the perception of probability, and the value of outcomes.
+\citet{Tversky1992} subsequently addressed key issues present in their original formulation by introducing \ac{CPT}, which allows for non-binary decisions, at the expense of the heuristics.
+The essence then, is that high and low probabilities are treated differently, and the subjective value of a loss differs from the equivalent gain (losing your shirt is worse than winning a shirt is good).
 

### 2014-07-16 Background.tex
Neural correlates of decisions

@@
 
+Recently, several studies have explored biological correlates to aspects of expected utility.
+The fundamental concept, that all outcomes are comparable in a universal currency has been supported by evidence of neural correlates of decision variables \citep{Platt1999}, and following from this results from \citet{Padoa-Schioppa2006,Padoa-Schioppa2008} showing neuronal firing in the \ac{OFC} corresponding to revealed preferences in monkeys.
+Additionally, some support for neural representation of value, and risk aversion was found by \citet{Christopoulos2009}.
+The model presented in this paper makes an explicit assumption that social decisions utilise the same process, and while this is less well supported there is some evidence to suggest involvement by the same brain region, since damage to the \ac{OFC} has been shown to impair social judgements in both primates \citep{Watson2012}, and humans \citep{Willis2010}.
+
 \subsection{Heuristic Decision Making}\label{sub:heuristic_theories}
@@
 This recasts rationality as bound to the context of the behaviour - a rational approach to choosing the right mate might well require checking every possible partner, but given finite time, memory, and so on rapidly becomes nonsensical.
+On this basis, they contend that the rationality of any given decision rule can only be determined in the context of the environment, which implies that heuristics are task specific.
 
@@
 \citet{Tversky1992} subsequently addressed key issues present in their original formulation by introducing \ac{CPT}, which allows for non-binary decisions, at the expense of the heuristics.
-The essence then, is that high and low probabilities are treated differently, and the subjective value of a loss differs from the equivalent gain (losing your shirt is worse than winning a shirt is good).
+The essence then, is that high and low probabilities are treated differently, and the subjective value of a loss differs from the equivalent gain (losing your shirt is perceived as more of a loss than winning a shirt is a gain).
 
@@
 are combined with lottery C.
-
-While vastly influential, the expected utility theory has been substantially
-criticised, generally for failing to predict real behaviour. \citet{Society2013}
-attacked the independence axiom in particular, suggesting that in
-some scenarios people's choices would be inconsistent where expected
-utility implies otherwise. A number of studies (e.g. \citep{Oliver2003,Burke1996})
-have since supported the intuition to some extent.
-
-More recently, support for some aspects of the expected utility theory,
-particularly the concept of utility as a common currency for comparison,
-has come from neurology, for example following work by \citet{Platt1999},
-\citet{Padoa-Schioppa2006,Padoa-Schioppa2008} report neuronal firing
-corresponding to economic value in decision making tasks undertaken
-by monkeys, while \citet{Christopoulos2009} found similarly indicative
-results for risk aversion. The suggestion implicit in the model proposed
-here, that this also applies to social judgements, is less investigated,
-although both \citet{Watson2012}, and \citet{Willis2010} found that
-lesions in the brain area%
-\footnote{The orbitofrontal cortex.%
-} identified by \citeauthor{Padoa-Schioppa2006} lead to abnormal social
-judgements in humans and primates.
 

### 2014-07-17 Background.tex
Progress!

@@
 
+An alternative normative model of decision making is Bayesian decision theory, proposed by \citet{Robbins1964}, which is essentially the application of Bayesian style probabilities to the expected utility model.
+This allows probabilities used in reasoning to be subjective, which may allow for a better account of decisions from experience (see \citet{Hau2008,Hertwig2004} for results elucidating the distinction, and comparing the performance of several non-Bayesian models).
+This model has seen notable successes in practical problems \citep{McNamara1980,Survey2003,Kristensen1997}, but suggestions by several authors  that it could constitute an effective (top-down) model of learning \citep{Tenenbaum2006,Griffiths2010}, or induction \citep{Gallistel2012} in the brain have attracted substantil criticism, e.g.
+\citet{Bowers2012}, and \citet{Miller2012} responding to \citeauthor{Tenenbaum2006,Griffiths2010}, and \citeauthor{Gallistel2012} respectively.
+
 \subsection{Heuristic Decision Making}\label{sub:heuristic_theories}
@@
 While heuristic theories arguably fall under the purview of the descriptive, the wider tendency is towards what are in essence patches to normative models.
-The most influential models in this class derive from \ac{PT} \citep{Kahneman1979}, which combines a set of heuristics based on observed decision behaviour, with distortions to the perception of probability, and the value of outcomes.
-\citet{Tversky1992} subsequently addressed key issues present in their original formulation by introducing \ac{CPT}, which allows for non-binary decisions, at the expense of the heuristics.
+The most influential models in this class derive from \ac{PT} \citep{Kahneman1979}, which combines a set of heuristics based on observed decision behaviour \citep{Tversky1974}, with distortions to the perception of probability, and the value of outcomes \citep{Kahneman1984,Tversky1986} .
+\citet{Tversky1992} subsequently addressed issues present in their original formulation by introducing \ac{CPT}, which allows for non-binary decisions, at the expense of the heuristics.
 The essence then, is that high and low probabilities are treated differently, and the subjective value of a loss differs from the equivalent gain (losing your shirt is perceived as more of a loss than winning a shirt is a gain).
+This last, known as the framing effect is particularly significant, see for example work by \citet{Toll2007} examining the relationship between loss and gain framings and success rates in giving up smoking, and \ac{NICE} guidance on framing of treatment options \citep{NICE2007}.
 
-Under this model, the expected utility of any gamble is a function
+\ac{CPT} has been successful in explaining a number of anomalous results in decision tasks (see \citet{Camerer2004a} for a review), and \citet{Thaler2000} comments to the effect that the theory is promising, albeit incomplete, lacking for example any explanation of how frames are constructed.
+While an effective account of decision behaviour under risk, the theory does not attempt to resolve apparent inconsistencies that arise when outcomes are delayed, i.e.
+in situations of intertemporal choice.
+Historically, \ac{DU} \citep{Samuelson1937}, which effectively claims that the value of a thing now is exponentially greater than the promise of the same thing at some future date, has been applied to explain this.
+More recently, \citet{Ainslie1991} has suggested that discounting of future outcomes is hyperbolic, rather than exponential, although neither model is complete - both fail to account for results from \citet{Thaler1981} showing differing temporal discounting rates for losses and gains.
+\citet{Loewenstein1992} report additional failings in classic \ac{DU} models, and propose a modified form of \ac{CPT} which they suggest is able to handle both immediate, and intertemporal choice.
+
+\begin{comment}Under this model, the expected utility of any gamble is a function
 of the probability of the outcomes, their utility to the gambler,
@@
 in immediate term choices.
+\end{comment}

### 2014-07-17 Introduction.tex
Progress!

@@
 
-In this paper we extend previous work by \cite{GrayDissert}.
-
 The case in favour of \ac{ABM} as a general approach has been made numerously, and elegantly REFS.
@@
 In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, tending to be a reflection of the assumptions of the modeller rather than empirically or theoretically grounded \citep{Waldherr2013}.
-To ameliorate this concern, we draw on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game \citep{Kreps1987} with a basic form of intragroup information sharing.
+To ameliorate this concern, we extend previous work by \cite{GrayDissert} drawing on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game \citep{Kreps1987} with a basic form of intragroup information sharing.
 Four decision models of varying complexity, and behavioural plausibility are contrasted, by way of demonstrating the significance of the operationalisation of decision making in \ac{ABM}.
@@
 
-The remainder of this paper proceeds to provide a brief review of the methodological context (\ref{sub:games_signals}), before outlining the model (\ref{sec:model}), and experiments (\ref{sec:method}), with selected results (\ref{sec:results}), then closing with a discussion contrasting the decision models (\ref{sec:conclusion}).
+The remainder of this paper proceeds to provide a brief review of the methodological context (\ref{sec:lit_review}), before outlining the model (\ref{sec:model}), and experiments (\ref{sec:method}), with selected results (\ref{sec:results}), then closing with a discussion contrasting the decision models (\ref{sec:conclusion}).

### 2014-07-17 Methods.tex
Working on introduction
Progress!

@@
 \end{table}
+
+\subsection{Information Sharing}
+
+In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examine the impact of simple information sharing (section \ref{sub:info_sharing}) on the robustness of these trends.
+Table \ref{tab:sharing_params} gives the parameters explored, with a more complete exploration of the effects on the system as a whole performed as part of the global sensitivity analysis.
+
+\begin{table}
+\center
+\begin{tabular} {|l | l | l| l| l|}
+\hline
+Name & Description & Min & Max & Step Size \\ \hline
+\(q_{w}\) & Probability of women sharing & 0 & 1 & 0.25 \\ \hline
+\(w_{w}\) & Weight of shared information for women & 0 & 1 & 0.25 \\ \hline
+\(q_{m}\) & Probability of midwives sharing & 0 & 1 & 0.25 \\ \hline
+\(w_{m}\) & Weight of shared information for midwives & 0 & 1 & 0.25 \\ \hline
+\end{tabular}
+\caption[Table caption text]{Information sharing parameter ranges. \label{tab:sharing_params}}
+\end{table}
+
 \subsection{Global Sensitivity Analysis}
@@
 %Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
-In general, we follow the procedure outlined in \cite{Bijak2013b} for stochastic
+In general, we follow the procedure outlined in \cite{Bijak2013b} for stochastic \acp{ABMs}, although see \citet{Thiele2014} for a review of alternative techniques.
 

### 2014-07-17 Results.tex
Added tex  root for easier building
Fleshing out
Beginning to flesh out, added a stub for a decision problem figure.
Filler
Filler text to be rewritten
Working on introduction
Progress!

--- 2014-07-03 Conclusion.tex
@@
-\section{Discussion and Conclusions}
-\label{sec:conclusion}
+%!TEX root = disclosure_game.tex
+%Include the descent into chaos bit
+\section{Results}
+\label{sec:results}
+
+LOOK AT MAH GRAFS!
+
+\subsection{Qualitative Trends}
+\label{sub:qt_results}
+
+As shown in figure \ref{fig:qt_honesty}, all four decision rules were able to reproduce both qualitative trends towards more disclosure as women experience more appointments \citep{Phillips2007}, and a greater tendency towards underreporting of consumption by heavier drinkers \citep{Alvik2006}.
+Trends for all four rules are broadly similar, exhibiting a gradual increase across appointments which subsequently levels off.
+This levelling can in part be explained by the referral results (figure \ref{fig:qt_ref}), which show that the majority of drinkers are referred, despite substantial concealment.
+Referrals continue to occur, in the absence of honest signals, because drinkers are able to achieve a referral by pooling with higher or lower types, dependent on how their initial beliefs are biased.
+
+\begin{figure}[h!]
+\caption{Average fraction of population signalling honestly over appointments, across 100 runs.}
+\label{fig:qt_honesty}
+\end{figure}
+
+\begin{figure}[h!]
+\caption{Average fraction of population referred over appointments, across 100 runs.}
+\label{fig:qt_ref}
+\end{figure}
+
+\subsection{Information Sharing}
+\label{sub:sharing_results}
+
+\subsection{Sensitivity Analysis}
+\label{sub:sa_results}
+
+The full results for the sensitivity analysis covering all twelve emulators are available in appendix \ref{}, and in this section we present selected results highlighting......

### 2014-07-19 Methods.tex
Acronym twiddling

@@
 %Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
-In general, we follow the procedure outlined in \cite{Bijak2013b} for stochastic \acp{ABMs}, although see \citet{Thiele2014} for a review of alternative techniques.
+In general, we follow the procedure outlined in \cite{Bijak2013b} for stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques.
 
@@
 \(w_{m}\) & Weight of shared information for midwives & 0 & 1 \\ \hline
-\(X_{h,}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
-\(X_{c, r}\) & Cost for referral & \multicolumn{2}{l|}{\(-(X_{h} - 1)\)} \\ \hline
+\(x_{h}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
+\(x_{r}\) & Cost for referral & \multicolumn{2}{l|}{\(-(X_{h} - 1)\)} \\ \hline
 \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 1:1 & 100:1 \\ \hline

### 2014-07-21 Background.tex
Stigma, notation
More commentary in methods

@@
 peacock tail feathers), then honest signalling would constitute an \ac{ESS}.
-\citet{Spence1973} demonstrated similar results in a game of job market signalling, where signal cost was differentiated by type.
+Similar results have also been demonstrated in a game of job market signalling, where signal cost was differentiated by type \citep{Spence1973}.
 Costly signalling has also been suggested as an explaination of behaviour that at first gasp appears counter intuitive, for example \citet{Godfray1991} applied the idea to the food solicitation behaviour of chicks, where a stronger signal carries a risk of being eaten.
@@
 Other work augments the signalling game model, for example \citet{Austen-Smith2005} adds a second `peer group' audience signalling game to the original \citeauthor{Spence1973} game in an effort to explain poor academic performance in some social groups, with some subseqent empirical support for the idea from \citet{Jr2010}.
-On a similar tack, \citet{Feltovich2002} introduced additional noisy type information, finding that this effectively explained counterintuitive observed behaviour where actors with every right to boast of their quality faail to do so.
+On a similar tack, \citet{Feltovich2002} introduced additional noisy type information, finding that this effectively explained counterintuitive observed behaviour where actors with every right to boast of their quality fail to do so.
 
@@
 \citet{Loewenstein1992} report additional failings in classic \ac{DU} models, and propose a modified form of \ac{CPT} which they suggest is able to handle both immediate, and intertemporal choice.
-
-\begin{comment}Under this model, the expected utility of any gamble is a function
-of the probability of the outcomes, their utility to the gambler,
-and the gambler's risk aversion. Essentially this is an extension
-of the expected value criterion, which assumes that the expected value
-is based only on the probability and objective value of outcomes.
-By contrast, the utility framing is a subjective measure, allowing
-differing preferences between gamblers. \citet{Neumann1953} later
-formalised the theory, defining rational decision as acting to maximise
-expected utility, where an individual's preferences are shown to fulfil
-four axioms, namely completeness, transitivity, independence, and
-continuity. Completeness requires that for any two lotteries A and
-B, the decision maker prefers one to the other, or is indifferent.
-Transitivity requires that if A is preferred to B, and B is preferred
-to C, then A is also preferred to C. Continuity states that given
-a scenario as in the transitivity axiom, there is some combination
-of lotteries A and C where the decision maker is indifferent between
-that combined lottery and B. Finally, independence maintains that
-if one were to prefer gamble A to B, that preference holds if both
-are combined with lottery C.
-
-Bayesian decision theory, as expounded by \citet{Robbins1964} applies
-Bayesian inference to the process of decision making under some degree
-of uncertainty, where decisions may be one-shot, or repeated.
-The central idea is relatively straightforward, and assumes that the
-loss or gain of some action to resolve a decision is contingent on
-an unknown parameter. To solve the problem, the decision maker chooses
-whichever action will minimise the risk, where the risk of an action
-is $\underset{i}{\sum}\lambda(a_{j}|w_{i})P(w_{i}|x)$, i.e. the loss
-incurred for taking action $a_{j}$ given that the true state of the
-world is $w_{i}$, multiplied by the belief that this is the true
-state of world given evidence $x$, summed across all possible worlds.
-Essentially this is identical with expected value, with Bayesian style
-probabilities. This allows an additional process of inference to progressively
-update the distribution from which $P(w_{i}|x)$ derives, as new evidence
-is obtained after each decision.
-
-This approach has been used in a wide variety of scenarios, for example
-\citet{McNamara1980} have applied statistical decision theory as
-a framework for understanding animal learning%
-\footnote{Although they note that this is in the sense of how animals `should'
-learn, rather than how they do learn%
-}, while \citet{Harsanyi1978} has derived an ethical framework from
-the principles. Less controversially, in contexts where optimality
-is desirable as an outcome, \citet{Survey2003} have used Bayesian
-decision methods in combination with \ac{MCMC} to solve complex waterfowl
-habitat management problems, and \citet{Kristensen1997} has developed
-robots which utilise Bayesian decision analysis to plan sensor operations.
-
-As with standard expected utility, the Bayesian approach can be criticised,
-in this case on the grounds of plausibility. The question of plausibility
-arises from the suggestion that Bayesian inference is in some way
-a model of human inductive reasoning, as argued by some branches of
-cognitive science. For example, \citeauthor{Tenenbaum2006} argue
-for the Bayesian approach as a top-down model of inductive reasoning
-in humans \citep{Tenenbaum2006,Griffiths2010}, a general approach
-criticised by \citet{Bowers2012} as unfalsifiable, overcomplicated,
-and relying on an unrealistic conceptualisation of the brain as optimal.
-\citet{Miller2012} also applied similar criticism to claims by \citet{Gallistel2012}
-that Bayesian inference better characterises learning as opposed to
-associative conditioning type models, suggesting that this relies
-on an assumption of optimality which is unfounded.
-
-\subsubsection{Descriptive Decision Theory}
-
-Arguably the most significant criticism of theories of decision making,
-is their failure to correspond to empirically observed decision making
-\footnote{This critique is not unique to decision theory, and has also been
-levelled at game theory (e.g. \citet{Fehr2003} on the irrational
-altruism of humans playing the prisoners' dilemma).%
-}. This was probably first raised by \citet{Simon1956}, who proposed that the
-apparent divergence derived from a tendency to satisfice, rather than
-optimise. This suggestion rests on the not unreasonable assumption
-that people do not have unlimited cognitive capacity (i.e. bounded
-rationality \citep{Simon2000}), and hence use heuristic means to
-make decisions, namely by choosing the first `good enough' option.
-\citeauthor{Simon1956} suggests that this process nevertheless leads
-to the optimal solution is most cases.
-
-Subsequent work on descriptive theories largely follows the same framework
-in assuming that in reality, human decision making is a heuristic
-process. \citet{Tversky1974} developed three heuristics to explain
-observed systematic errors in reasoning - representativeness, availability,
-and anchoring. Representativeness suggests that when asked to judge
-how related one object or event is to another, they do this based
-on the extent to which they resemble one another - crucially they
-will ignore additional, better information when available. Availability
-claims that when tasked with estimating probabilities, people will
-rely on the ease with which they can call examples to mind (note that
-this might be considered an example of satisficing). Finally, anchoring
-proposes that when estimating, people start with some initial value
-and progressively update from there, i.e. they will tend to overweight
-prior evidence at the expense of new information.
-
-Subsequently, \citet{Kahneman1984,Tversky1986} also identified framing
-effects, which imply that the decisions people make are impacted by
-the fashion in which the problem is presented. The essential outcome
-from these findings is that people are risk seeking when faced with
-outcomes framed as losses, but risk averse towards gains, and regard
-any loss as greater than an equivalent gain. The impact of framing
-in itself has been shown to be significant, for example \citet{Toll2007}
-found improved abstinence rates in smoking cessation where quitting
-was framed as a gain, and \ac{NICE} recommend considering the framing
-of treatment outcomes when presenting options to patients \citep{NICE2007}.
-
-\ac{PT} \citep{Kahneman1979} attempts to provide a decision rule
-accounting for the heuristic nature of decision making and incorporate
-framing effects, which successfully explains many perceived failures
-of rationality. A revised version, \ac{CPT} \citep{Tversky1992}
-addressing a violation of first order stochastic dominance possible
-under the original formulation, extends the theory to allow decisions
-with more than two options, but sacrifices the editing phase. \citet{Camerer2004a}
-reviews a number of successes in explaining apparent anomalies with
-\ac{CPT}, and argues that should replace expected utility in general
-usage. \citet{Thaler2000} regards the theory as promising, but points
-out that it is in many ways incomplete, citing the lack of explanation
-as to how people construct frames as an example of this.
-
-A significant weakness of \ac{CPT} as a general theory of decision
-making is that it fails to account for behaviour under intertemporal
-choice, or rather does not attempt to address it. Generally, intertemporal
-choice is assumed to be underpinned by the \ac{DU} model of \citet{Samuelson1937},
-which proposes that the value of a thing right now is greater than
-the value of it at some point in the future (jam today has more utility
-than jam tomorrow), following an exponential relationship. A more
-nuanced view of this has been proposed by \citet{Ainslie1991}, suggesting
-that the relationship is hyperbolic rather than exponential. Both
-models however fail to explain several inconsistencies, for example
-\citet{Thaler1981} found that discounting rates were different between
-gains and losses. \citet{Loewenstein1992} report a number of additional
-inconsistencies that are not adequately resolved by \ac{DU} models,
-and propose an alternative along the lines of \ac{CPT} to resolve
-them while retaining the capabilities of Kahneman and Tversky's model
-in immediate term choices.
-\end{comment}

### 2014-07-21 Introduction.tex
More commentary in methods

@@
 
-Turning more specifically to disclosure of alcohol use during pregnance, research is relatively sparce, although qualitative trends are reported by \citet{Phillips2007}, and \citet{Alvik2006}.
+Turning more specifically to disclosure of alcohol use during pregnancy, research is relatively sparce, although qualitative trends are reported by \citet{Phillips2007}, and \citet{Alvik2006}.
 The former explored factors impacting disclosure through a small case study, highlighting the need to build up rapport over several appointments; the latter compared post partum reports of consumption with contemporaneous accounts, finding apparent underreporting during pregnancy which was amplified by increased drinking.
@@
 
-two fold appeal. cognitive plausibility - neuroec. inaccessible systems (litigation, concealment). fast. cheap. portable. theoretical grounding. rigor.
+%two fold appeal. cognitive plausibility - neuroec. inaccessible systems (litigation, concealment). fast. cheap. portable. theoretical grounding. rigor.
 

### 2014-07-21 Methods.tex
More commentary in methods

@@
 While there has been significant work on determining appropriate parameterisation for the model (e.g.
-\cite{Neilson2002}, \cite{Glockner2012}, \cite{Nilsson2011}), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work.
+\cite{Neilson2002,Glockner2012,Nilsson2011}, and particularly \citet{Byrnes1999,Booij2009} addressing risk aversion and gender), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work.
+For simplicity, it is assumed that all three drinking types are equally prevalent within the population, although results derived from \ac{ALSPAC} suggest that the reality is far more positive \citep{Humphriss2013}.
+The scenario is biased towards disclosure as the better option by presuming a distribution of midwives strongly skewed towards non-judgemental types, with beliefs initially favouring honesty.
+Payoffs were as in table \ref{tab:Payoff-matrix}, which ensure that it is always strictly preferable to refer drinkers, and together with the initial belief that signals will be honest, not refer those claiming otherwise.
 
@@
 
-\begin{table}
+\begin{table}[h!]
 \center
@@
 \(x_{h}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
-\(x_{r}\) & Cost for referral & \multicolumn{2}{l|}{\(-(X_{h} - 1)\)} \\ \hline
+\(x_{r}\) & Cost for referral & \multicolumn{2}{l|}{\(-(x_{h} - 1)\)} \\ \hline
 \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 1:1 & 100:1 \\ \hline

### 2014-07-22 Background.tex
Wordings

@@
 
-\citet{Gigerenzer1996} take the concept of bounded rationality further, and argue for what they term \ac{FFH}.
-This recasts rationality as bound to the context of the behaviour - a rational approach to choosing the right mate might well require checking every possible partner, but given finite time, memory, and so on rapidly becomes nonsensical.
-On this basis, they contend that the rationality of any given decision rule can only be determined in the context of the environment, which implies that heuristics are task specific.
+\citet{Gigerenzer1996} take the concept of bounded rationality further, and argue for what they term \acp{FFH}.
+This recasts rationality as bound to the context of the behaviour: a rational approach to choosing the right mate might well require checking every possible partner, but given finite time, memory, and so on rapidly becomes nonsensical.
+On this basis, they contend that the rationality of any given decision rule can only be determined in the context of the environment \citep{Todd2003}, which implies that heuristics are task specific.
+They provide a number of heuristics for varying decision problems, e.g.
+recognition \citep{Goldstein2002}, cue ordering \citep{Gigerenzer1999,Todd2004}, and binary decisions \citep{Brandstatter2006}.
 
@@
 While heuristic theories arguably fall under the purview of the descriptive, the wider tendency is towards what are in essence patches to normative models.
-The most influential models in this class derive from \ac{PT} \citep{Kahneman1979}, which combines a set of heuristics based on observed decision behaviour \citep{Tversky1974}, with distortions to the perception of probability, and the value of outcomes \citep{Kahneman1984,Tversky1986} .
+The most influential models in this class derive from \ac{PT} \citep{Kahneman1979}, which combines a set of heuristics based on observed decision behaviour \citep{Tversky1974}, with distortions to the perception of probability, and the value of outcomes \citep{Kahneman1984,Tversky1986}.
 \citet{Tversky1992} subsequently addressed issues present in their original formulation by introducing \ac{CPT}, which allows for non-binary decisions, at the expense of the heuristics.
@@
 Historically, \ac{DU} \citep{Samuelson1937}, which effectively claims that the value of a thing now is exponentially greater than the promise of the same thing at some future date, has been applied to explain this.
-More recently, \citet{Ainslie1991} has suggested that discounting of future outcomes is hyperbolic, rather than exponential, although neither model is complete - both fail to account for results from \citet{Thaler1981} showing differing temporal discounting rates for losses and gains.
+More recently, \citet{Ainslie1991} has suggested that discounting of future outcomes is hyperbolic, rather than exponential.
+However neither model is complete, in that both fail to account for results from \citet{Thaler1981} showing differing temporal discounting rates for losses and gains.
 \citet{Loewenstein1992} report additional failings in classic \ac{DU} models, and propose a modified form of \ac{CPT} which they suggest is able to handle both immediate, and intertemporal choice.

### 2014-07-22 Introduction.tex
Wordings

@@
 
-This scenario is of substantial independent interest, and shows the potential utility of a simulation approach in arenas where \ac{RCT} are not viable for ethical, or financial reasons.
+This scenario is of substantial independent interest, and shows the potential utility of a simulation approach in arenas where \acp{RCT} are not viable for ethical, or financial reasons.
 With this said, the lack of a strong quantitative evidence base against which to validate the behaviour of the model augers for caution in interpreting the results, and a necessary reminder that in this instance the focus is primarily methodological.

### 2014-07-22 Methods.tex
Wordings

@@
 %Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
-In general, we follow the procedure outlined in \cite{Bijak2013b} for stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques.
+In general, we follow the procedure outlined in \cite{Bijak2013b} for global sensitivity analysis of stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques.
+This employs the \ac{GEM-SA} software \citep{Kennedy}, which draws on the theoretical framework developed by \citeauthor{Oakley2004} \citep{Oakley2002,Oakley2004,Dorresteijn2010}.
 

### 2014-07-24 Methods.tex
Starting in on results

@@
 
-In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examine the impact of simple information sharing (section \ref{sub:info_sharing}) on the robustness of these trends.
-Table \ref{tab:sharing_params} gives the parameters explored, with a more complete exploration of the effects on the system as a whole performed as part of the global sensitivity analysis.
-
-\begin{table}
-\center
-\begin{tabular} {|l | l | l| l| l|}
-\hline
-Name & Description & Min & Max & Step Size \\ \hline
-\(q_{w}\) & Probability of women sharing & 0 & 1 & 0.25 \\ \hline
-\(w_{w}\) & Weight of shared information for women & 0 & 1 & 0.25 \\ \hline
-\(q_{m}\) & Probability of midwives sharing & 0 & 1 & 0.25 \\ \hline
-\(w_{m}\) & Weight of shared information for midwives & 0 & 1 & 0.25 \\ \hline
-\end{tabular}
-\caption[Table caption text]{Information sharing parameter ranges. \label{tab:sharing_params}}
-\end{table}
+In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examine the impact of simple information sharing within the population of women (section \ref{sub:info_sharing}) on the robustness of these trends.
+The original experiment was repeated at \(q_{w}\,\&\,w_{w}={0.25, 0.5, 0.75, 1}\).
 

### 2014-07-24 Model.tex
Progress!
Stigma, notation
Wordings
Starting in on results

@@
 %!TEX root = disclosure_game.tex
-\section{Model}
+\section{Disclosure Game Model}
 \label{sec:model}
@@
 In this section we outline the disclosure game model, and give details of the four decision rules, but begin with a brief sketch of a pregnancy in terms of encounters between a woman and a midwife.
+
 Typically women will have 12 appointments with a midwife during the antenatal period.
@@
 In an ideal world, all interactions with healthcare providers would be immediately and fully disclosive, with no repercussions for the patient.
-However even when considering less emotive topics, this is not the case.
+However, alcohol misuse by women is known to attract stigma \citep{Gomberg1988}, and is a recognised barrier to appropriate treatment in the maternity context \citep{Radcliffe2011,NICE2010}.
 
@@
 
-Where $X$ is set of payoffs the agent has observed to follow $s$.
+Where $X$ is the set of payoffs the agent has observed to follow $s$.
 
@@
 \begin{equation}
-R_{w}(s_{w}) = \sum_{i\in s_{m}}\sum_{j\in \theta_{m}} -u_{w}(s_{w}, s_{m, i}, \theta_{w}, \theta_{m, j})p(s_{m,i})p(i | s_{w})
+R_{w}(s_{w}, \theta_{w}) = \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, \theta_{w}, j)p(j)p(i | s_{w})
 \end{equation}
@@
 \begin{equation}
-R_{m}(s_{w}, s_{m}) = \sum_{i\in \theta_{w}} -u_{w}(s_{w}, s_{m}, \theta_{w, i}, \theta_{m})p(i | s_{w})
+R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{w}(s_{w}, s_{m}, i, \theta_{m})p(i | s_{w})
 \end{equation}

### 2014-07-24 Results.tex
Starting in on results

@@
 
-LOOK AT MAH GRAFS!
-
 \subsection{Qualitative Trends}
@@
 
-As shown in figure \ref{fig:qt_honesty}, all four decision rules were able to reproduce both qualitative trends towards more disclosure as women experience more appointments \citep{Phillips2007}, and a greater tendency towards underreporting of consumption by heavier drinkers \citep{Alvik2006}.
+As shown in figure \ref{fig:honest_signals}, all four decision rules were able to reproduce both qualitative trends towards more disclosure as women experience more appointments \citep{Phillips2007}, and a greater tendency towards underreporting of consumption by heavier drinkers \citep{Alvik2006}.
 Trends for all four rules are broadly similar, exhibiting a gradual increase across appointments which subsequently levels off.
-This levelling can in part be explained by the referral results (figure \ref{fig:qt_ref}), which show that the majority of drinkers are referred, despite substantial concealment.
+This levelling can in part be explained by the referral results (figure \ref{fig:referrals}), which show that the majority of drinkers are referred, despite substantial concealment.
 Referrals continue to occur, in the absence of honest signals, because drinkers are able to achieve a referral by pooling with higher or lower types, dependent on how their initial beliefs are biased.
+Despite this the results suggest that a minority of drinkers will evade detection altogether, with no notable distinction between heavy and moderate types.
+Under these parameters, light drinkers always signal honestly and are never referred since there is no perceived advantage in doing so, and the evidence of deceptive signalling is insufficient to outweigh the biased priors of the midwives.
 
 \begin{figure}[h!]
-\caption{Average fraction of population signalling honestly over appointments, across 100 runs.}
-\label{fig:qt_honesty}
-\end{figure}
+\begin{adjustbox}{center}\subfloat[Average fraction of population signalling honestly\label{fig:honest_signals}]{\includegraphics[width=0.43\paperwidth]{figures/honesty_plot.png}
 
-\begin{figure}[h!]
-\caption{Average fraction of population referred over appointments, across 100 runs.}
-\label{fig:qt_ref}
+}\subfloat[Average fraction of population referred\label{fig:referrals}]{\includegraphics[width=0.43\paperwidth]{figures/ref_plot.png}}\end{adjustbox}
+\caption{Qualitative trends after 1000 rounds, mean with 95\% confidence limit over 1000 runs.}
+\label{fig:qt_trends}
 \end{figure}

### 2014-08-07 Introduction.tex
Figures & text
Obviously

@@
 Relating this to decision theory shifts the emphasis away from analytical equilibrium-seeking, and heightens the importance of behaviour change.
-Where the focus is on the behavioural processes driving a system in motion, and how they change in response to that movement, this is clearly desirable.
+This is clearly desirable where the focus is on the behavioural processes driving a system in motion, and how they change in response to that movement.
 Fundamentally, the shift of emphasis is from the process of acquiring and inferring the information needed to make choices, to the process of decision.

### 2014-08-07 Methods.tex
Figures & text
Obviously

@@
 
-Two key measures were used - the fraction of the subpopulation who had ever signalled honestly, and the proportion referred.
+Two key measures were used: the fraction of the subpopulation who had ever signalled honestly, and the proportion referred.
 Both measures were taken after every round of play, and were taken relative to the agent's position in their sequence of appointments giving the probability of signalling honestly, or being referred having had a given number of appointments.
@@
 In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examine the impact of simple information sharing within the population of women (section \ref{sub:info_sharing}) on the robustness of these trends.
-The original experiment was repeated at \(q_{w}\,\&\,w_{w}={0.25, 0.5, 0.75, 1}\).
+The original experiment was repeated at \(q_{w}=w_{w}={0.25, 0.5, 0.75, 1}\), with 100 runs under each condition.
 
@@
 This employs the \ac{GEM-SA} software \citep{Kennedy}, which draws on the theoretical framework developed by \citeauthor{Oakley2004} \citep{Oakley2002,Oakley2004,Dorresteijn2010}.
+Under this method...
 
@@
 
-To better capture the response characteristics for the model, we measure three outcome variables - (1) the interquartile range of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3) the standard deviation of that average signal between simulation runs.
-Together these three metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the stability of the system in the face of the stochastic elements.
+To better capture the response characteristics for the model, we measure four outcome variables - (1) the interquartile range of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3, 4) the interquartile range of the average signal, and interquartile range between simulation runs.
+Together these four metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the variability in the system in response to changes to the parameters (3 \& 4).
 
-Measurements were taken at the end of 1000 rounds of play, and for 1 and 2, 400 results were selected covering the full hypercube with each chosen randomly from the runs for that design point.
-This approach, rather than averaging across runs, was taken to avoid obscuring the high degree of variability evident in the output of the payoff reasoning agents in some areas of the parameter space.
+Measurements were taken at the end of 1000 rounds of play, and emulators were built against the mean, and interquartile range of each measure to assess both the overall trend, and the extent to which the parameters contribute to variance between runs.
 
-Twelve emulators were built, covering each of the three output on all four decision models.
+Twelve emulators were built, covering each of the four output on all four decision models.
 These emulators were used to conduct a probabalistic sensitivity analysis using \ac{GEM-SA} to assess the impact of parameters individually, and in combination.
@@
 \end{table}
-
-\begin{table}
-\center
-\begin{tabular} {| l | l |}
-Name & Description \\ \hline
-
-\end{tabular}
-\caption[Table caption text]{Output measures. \label{tab:sa_measures}}
-\end{table}

### 2014-08-07 Results.tex
Figures & text
Obviously

@@
 
-\begin{figure}[h!]
-\begin{adjustbox}{center}\subfloat[Average fraction of population signalling honestly\label{fig:honest_signals}]{\includegraphics[width=0.43\paperwidth]{figures/honesty_plot.png}
+\begin{figure}[H]
+\begin{adjustbox}{center}\subfloat[Average fraction of population signalling honestly\label{fig:honest_signals}]{\includegraphics[width=0.43\paperwidth]{figures/honesty_plot}
 
-}\subfloat[Average fraction of population referred\label{fig:referrals}]{\includegraphics[width=0.43\paperwidth]{figures/ref_plot.png}}\end{adjustbox}
+}\subfloat[Average fraction of population referred\label{fig:referrals}]{\includegraphics[width=0.43\paperwidth]{figures/ref_plot}}\end{adjustbox}
 \caption{Qualitative trends after 1000 rounds, mean with 95\% confidence limit over 1000 runs.}
@@
 
+Introducing information sharing amongst women leads the behaviour of the decision rules to diverge markedly.
+Figure \ref{fig:honest_sharing} shows the proportion of women who have signalled honestly at least once by their final appointment, under four sharing conditions.
+Aside from the lexicographic decision rule, the general tendency is towards less honest signalling by heavy drinkers, but \ref{fig:ref_sharing} shows a slight increase in referrals for the Bayesian, and \ac{CPT} rules.
+For these decision models, this is because information sharing exacerbates the existing tendency to pool with moderate drinkers, who behave more honestly as heavy drinkers become less so.
+
+Particularly notable, is the decline in honest signalling by light drinkers visible in both heuristic type rules at the .25 level, and the associated increase in false positives.
+This arises because of the lack of homophilly in information sharing, as light drinkers become informed about negative outcomes associated with concealment, despite having nothing to conceal.
+The relatively high referral rates of drinkers heighten the effect further, because shared information becomes dominated by their experiences.
+
+The relationship is not, however entirely that simple, in that increasing information sharing leads to greater variance between runs.
+A linear model was was used to predict the standard deviation between runs of the average signal sent by moderate drinkers, with decision rule, and level of information sharing, together with the interaction between the two as predictors.
+The regression results were significant (\(F_{7,12}=25,p<2.9\times10^{-6}\)) with \(R^2=94\%\), and intercept 0.07.
+The only significant coefficients were for the interaction terms, which were 0.44 (\(p<0.05\)) for the Bayesian payoff rule, and 0.69 (\(p<0.005\)) for the lexicographic.
+This suggests that information sharing, for the heuristic style decision rules introduces considerable uncertainty to the model, which is explored further in the sensitivity analysis.
+
+\begin{figure}[H]
+\begin{adjustbox}{center}\subfloat[Honest signalling\label{fig:honest_sharing}]{\includegraphics[width=0.43\paperwidth]{figures/honesty_sharing}
+
+}\subfloat[Referrals\label{fig:ref_sharing}]{\includegraphics[width=0.43\paperwidth]{figures/ref_sharing}}\end{adjustbox}
+\caption{Impact of information sharing on qualitative trends after 1000 rounds, mean with 95\% confidence interval over 100 runs.}
+\label{fig:sharing_trends}
+\end{figure}
+
 \subsection{Sensitivity Analysis}
@@
 
-The full results for the sensitivity analysis covering all twelve emulators are available in appendix \ref{}, and in this section we present selected results highlighting......
+In this section we present selected results highlighting the global effect of changes to perceived payoffs and degree of bias towards honesty, as well as information sharing within women.
+The full results for the sensitivity analysis covering all sixteen emulators are available in appendix \ref{}
+
+\begin{figure}[h!]
+\begin{adjustbox}{center}\includegraphics[width=0.8\paperwidth]{figures/sharing_emulated_simulated}\end{adjustbox}
+\caption{Mean moderate drinker signal vs mean between drinking type IQR for all decision rules.}
+\label{fig:outcome_plots}
+\end{figure}

### 2014-08-07 build.sh

@@ -1,0 +1,6 @@
+#!/bin/sh
+pdflatex -interaction=batchmode disclosure_game
+makeglossaries disclosure_game
+bibtex disclosure_game
+pdflatex -interaction=batchmode disclosure_game
+pdflatex -interaction=batchmode disclosure_game

### 2014-08-13 Methods.tex
Medians

@@
 
-Measurements were taken at the end of 1000 rounds of play, and emulators were built against the mean, and interquartile range of each measure to assess both the overall trend, and the extent to which the parameters contribute to variance between runs.
+Measurements were taken at the end of 1000 rounds of play, and emulators were built against the median, and interquartile range of each measure to assess both the overall trend, and the extent to which the parameters contribute to variance between runs.
 
-Twelve emulators were built, covering each of the four output on all four decision models.
+Sixteen emulators were built, covering each of the four outputs on all four decision models.
 These emulators were used to conduct a probabalistic sensitivity analysis using \ac{GEM-SA} to assess the impact of parameters individually, and in combination.

### 2014-08-26 Results.tex
Figures!

@@
 Trends for all four rules are broadly similar, exhibiting a gradual increase across appointments which subsequently levels off.
-This levelling can in part be explained by the referral results (figure \ref{fig:referrals}), which show that the majority of drinkers are referred, despite substantial concealment.
+This levelling can in part be explained by the referral results (figure \ref{fig:referrals}), which show that the majority of drinkers are referred, even with substantial concealment.
 Referrals continue to occur, in the absence of honest signals, because drinkers are able to achieve a referral by pooling with higher or lower types, dependent on how their initial beliefs are biased.
-Despite this the results suggest that a minority of drinkers will evade detection altogether, with no notable distinction between heavy and moderate types.
+Despite this the results suggest that a minority of risky drinkers will evade detection altogether, with no notable distinction between heavy and moderate types.
 Under these parameters, light drinkers always signal honestly and are never referred since there is no perceived advantage in doing so, and the evidence of deceptive signalling is insufficient to outweigh the biased priors of the midwives.
@@
 Figure \ref{fig:honest_sharing} shows the proportion of women who have signalled honestly at least once by their final appointment, under four sharing conditions.
-Aside from the lexicographic decision rule, the general tendency is towards less honest signalling by heavy drinkers, but \ref{fig:ref_sharing} shows a slight increase in referrals for the Bayesian, and \ac{CPT} rules.
+Aside from the lexicographic decision rule, the general tendency is towards less honest signalling by heavy drinkers, but figure \ref{fig:ref_sharing} shows a slight increase in referrals for the Bayesian, and \ac{CPT} rules.
 For these decision models, this is because information sharing exacerbates the existing tendency to pool with moderate drinkers, who behave more honestly as heavy drinkers become less so.
@@
 In this section we present selected results highlighting the global effect of changes to perceived payoffs and degree of bias towards honesty, as well as information sharing within women.
-The full results for the sensitivity analysis covering all sixteen emulators are available in appendix \ref{}
+The full results for the sensitivity analysis covering all sixteen emulators are available in appendix \ref{app:sensitivity_results}.
 
@@
 \begin{adjustbox}{center}\includegraphics[width=0.8\paperwidth]{figures/sharing_emulated_simulated}\end{adjustbox}
-\caption{Mean moderate drinker signal vs mean between drinking type IQR for all decision rules.}
+\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules.}
 \label{fig:outcome_plots}
 \end{figure}
+
+Figure \ref{fig:outcome_plots} gives a qualitative picture of both emulator quality, and the divergent response surfaces of the decision rules in response to variations in information sharing parameters.
+Emulator fit is clearly imperfect, but overall behaviour is qualitatively similar, with both emulated and simulated plots demonstrating separation in outcome space for the decision rules.
+
+\begin{figure}[h!]
+\begin{adjustbox}{center}\includegraphics[width=0.8\paperwidth]{figures/unfixed_emu_sig_iqr}\end{adjustbox}
+\caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\).}
+\label{fig:emulated_sharing_iqr}
+\end{figure}
+
+Following from the suggestive results for information sharing introducing uncertainty (section \ref{sub:info_sharing}), figure \ref{fig:emulated_sharing_iqr} shows emulated points covering the parameter space in high resolution.
+These plots reflect the increase in uncertainty of outcome shown for the heuristic type rules.
+They also suggest that the Bayesian decision rule is less stable under conditions where the weight of shared information is substantially higher than the probability of sharing.
+Also of interest is the large region of instability that can be discerned for the Bayesian rule under modest probability of information sharing and higher weights.
+
+For the \ac{CPT}, and Bayesian decision models, the interaction of bias towards honesty, and distinction between payoffs has a significant, and non-linear effect on instability, and separability of groups.
+Figure \ref{fig:emulated_payoff_group_iqr} shows the effects, and also highlights the tendency towards poor separability of groups for both the heuristic type decision rules.
+The response surface of the Bayesian payoff rule is slightly more nuanced than the simple Lexicographic rule, showing better separation close to partial pooling at high payoff distinction, with relatively modest honesty bias.
+For the more complex rules, the general tendency is towards less pooling for higher values of both, but with pockets where full pooling occurs.
+The plots also suggest that the sensitivity of the \ac{CPT} rule is marginally greater, which reflects the distorted utility function.
+
+\begin{figure}[h!]
+\begin{adjustbox}{center}\includegraphics[width=0.8\paperwidth]{figures/unfixed_emu_payoff_honesty_group_iqr}\end{adjustbox}
+\caption{Emulated between groups IQR in response to varying \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\), and \(x_{h}\).}
+\label{fig:emulated_payoff_group_iqr}
+\end{figure}

### 2014-08-26 SensitivityAnalysis.tex
Figures!

%!TEX root = disclosure_game.tex
%Include the descent into chaos bit
\section{Sensitivity Analysis}
\label{app:sensitivity_results}

\subsection{Lexicographic}

\subsubsection{Median Moderate Drinker Signalling}

\subsubsection{Median Between Groups IQR}

\subsubsection{Median Moderate Drinker Signalling IQR}

\subsubsection{Between Groups IQR IQR}

### 2014-08-28 Abstract.tex
Filler
Filler text to be rewritten
Writing, updated figures.

@@
 
-Selected results showing the ability of all decision rules to reproduce qualitative trends noted in the literature are provided, together with a sensitivity analysis, and comparitive heat maps produced using \acp{GEM} demonstrating the significance of the precise implementation of the decision making.
-
-\subsection*{Conclusions}
-
-The ability of all the decision rules to show the qualitative trends suggests that there is some utility associated with this approach.
+Selected results showing the ability of all decision rules to reproduce qualitative trends noted in the literature are provided, together with a sensitivity analysis, and comparative heat maps produced using \acp{GEM} demonstrating the significance of the precise implementation of the decision making.
 
@@
 Clearly a domain where there is sufficient data to permit a more comprehensive approach to validation of model outcomes is desirable, and will form the basis of our future work.
+
+To aid in replication and extension, the model has been implemented as a Python module, and is freely available under the Mozilla Public License from \url{https://github.com/greenape/disclosure-game}, together with full parameter sets, raw data, and all other code used in producing this paper.

### 2014-08-28 Conclusion.tex
Added tex  root for easier building
Making notes
Figures!
Writing, updated figures.

@@
+%!TEX root = disclosure_game.tex
 \section{Discussion and Conclusions}
 \label{sec:conclusion}
+%reiterate contribution
+%	bring up the simplicity -> chaos thing, talk about homophily
+%	talk up the good (trends! yay!) and intro the bad -> no data
+%
+%	emphasise the 'nice story' -> future work
+% ~ 1,500 words.
+
+From a pragmatic perspective, the differing response characteristics of the decision rules are substantial and significant.
+The lack of a mechanism of homophily in the very simple rules leads to a high level of uncertainty in the overall dynamics, since even irrelevant information is taken at face value and to be equally valuable.
+By contrast, the belief structure of the \ac{CPT}, and Bayesian models represents a useful abstraction which allows the use of the relevant aspects of the information.
+Naturally, incorporating homophily, by, for example weighting shared information by the type of the sharer, would represent a relatively trivial modification to the heuristic models.
+While to some extent this highlights the flexibility of the decision rule approach, it would of course sacrifice the parsimony of the model to a degree.
+This is an important consideration, given that part of the argument in favour of a decision theoretic approach to agent building lies in the minimal nature of the behavioural rules, which can be seen as occupying a middle ground between parameter and model.
+
+One of the notable features of the results is the similarity in behaviour of the two classes of decision rule.
+To some extent this reflects poorly on the most complex rule, \ac{CPT}, which diverges only relatively minorly in behaviour from the Bayesian model.
+To some extent this might be anticipated, in that the payoffs are clearly unrealistic, which limits the utility of the \ac{CPT} approach.
+Additionally, work by \citet{Glockner2012} has shown that there is considerable variation in individual parameters for the decision model, whereas we have let them remain homogenous here.
+In the vein, utility functions should arguably vary between individual agents, which could potentially be addressed by replacing the fixed payoffs used here with a distribution.
+With this said, the significant increase in complexity, which entails both additional parameters and increases to simulation time may auger for a middle ground, particularly where elicitation of payoffs is impractical.
+This, together with the variablility associated with the heuristic type decision rules speaks to a tradeoff between capturing reality, and replicating it.
+
+Continuing the discussion of the issues raised by the representation of payoffs, the temporal aspect is significant, in that there is clearly a timing difference in payoffs, since while the potential social pain of disclosure is immediate, the health outcome comes only later.
+In light of this, that there is a known impact of time on perceived utility \citet{Thaler1981} suggests that incorporating some form of temporal discounting (e.g.
+exponential \citep{Samuelson1937}, or hyperbolic \citep{Ainslie1991}), or a decision model which explicitly treats intertemporal choice, such as the \ac{CPT} like model of \citet{Loewenstein1992}, is warranted.
+
+More broadly, the results demonstrate the logistical feasibility, and utility as a `tool for thinking', of an agent model grounded in decision theory.
+The results also make clear that deciding the operationalisation of the decision making is of key significance.
+
+The conclusions that can be drawn about the behaviours of real life women, and their midwives, are necessarily limited by the paucity of data available to validate the model.
+While qualitative trends offer a some indication, they are clearly very limited in scope, and do not permit strong claims about the drivers of disclosure, and auger for a sceptical eye as to any recommendations targetted at improving outcomes.
+With this said, the trends reported by \citet{Alvik2006}, and \citet{Phillips2007} are bourne out by the model, and predictions from the two more complex rules suggest that encouraging information sharing between women may encourage disclosure, but at the expense of reducing accuracy.
+
+Further work will focus on applying the model to domains where validation data is more available, which will support a more comprehensive evaluation of the model discrepancy.
+Disclosure is a widely applicable issue in health and social care and beyond, with examples ranging from a lack of help seeking behaviour noted in older men \citep{Smith2007a}, to the inverse scenario of innapropriate disclosure in social media \citep{christofides2009information}.

### 2014-08-28 Introduction.tex
Writing, updated figures.

@@
 % 	mention the importance of behaviour change
+% tool for thinking
+% theoretical vacuum at the middle
+% under what scenarios does an as if explanation break down
 
-The case in favour of \ac{ABM} as a general approach has been made numerously, and elegantly REFS.
+The case in favour of \ac{ABM} as a general approach has been made numerously, and elegantly \citep{Silverman2011,Silverman2013,Resnick,gilbert1999simulation,epstein1994growing,Macy2002a,Axelrod1997}.
 As such we will not belabour the point, and instead turn to addressing some of the concerns expressed about the method.
@@
 This scenario is of substantial independent interest, and shows the potential utility of a simulation approach in arenas where \acp{RCT} are not viable for ethical, or financial reasons.
-With this said, the lack of a strong quantitative evidence base against which to validate the behaviour of the model augers for caution in interpreting the results, and a necessary reminder that in this instance the focus is primarily methodological.
+With this said, the lack of a strong quantitative evidence base against which to validate the behaviour of the model augers for caution in interpreting the results, and a necessary reminder that in this instance the model is primarily a tool for thinking, rather than a machine for predicting.
 
@@
 
-A key motivation for decision rules is their claim to provide an account of decision making that is behaviourally and cognitively plausible.
+While there is no universal theory of human behaviour to sit at the center of \ac{ABM} as a method,a key motivation for decision rules is their claim to provide an account of decision making that is behaviourally and cognitively plausible.
 Their mooted capability in this regard is to some extent supported by work from neuroeconomics, which aims to empirically test theories of decision making \citep{Rustichini2009}.
 Many key aspects common to decision rules, for example the idea that a common currency is used by the brain to compare outcomes \citep{Padoa-Schioppa2006,Padoa-Schioppa2008}, are supported by neurological findings.
+In addition, decision rules represent a pleasingly parsimonious alternative to explicit behavioural rules covering all possible eventualities.
 

### 2014-08-28 Methods.tex
Figures!
Writing, updated figures.

@@
 %Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
-In general, we follow the procedure outlined in \cite{Bijak2013b} for global sensitivity analysis of stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques.
-This employs the \ac{GEM-SA} software \citep{Kennedy}, which draws on the theoretical framework developed by \citeauthor{Oakley2004} \citep{Oakley2002,Oakley2004,Dorresteijn2010}.
-Under this method...
+In general, we follow the example of \cite{Bijak2013b} for global sensitivity analysis of stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques.
+For this purpose the \ac{GEM-SA} software \citep{Kennedy} was used, which implements the \ac{BACCO} method developed by \citeauthor{Oakley2004} \citep{Oakley2002,Oakley2004,Dorresteijn2010}.
+This is a form of variance based sensitivity analysis, which assumes that the model output is an unknown, smooth function of the inputs.
+The unknown function can then be approximated as a Gaussian Process, which is fitted to the training data using Bayes' Theorem.
+The emulator is then able to provide an indication about the extent to which uncertainty in a parameter propogates to uncertainty in the output, and how sharply the output responds to change in each input.
 
-Parameters for training were generated in R \citep{RTeam2014} using Latin Hypercube Sampling \citep{Carnell2012} over the space of inputs given in table \ref{tab:sa_params}, giving 10 free parameters.
+\begin{comment}
+
+Justification for doing SA, point out the wide variety of places this gets used. Talk about uncertainty, briefly raise model discrepancy.
+
+\end{comment}
+
+Parameters for training were generated in R \citep{RTeam2014} using Latin Hypercube Sampling \citep{Carnell2012} over the space of inputs given in table \ref{tab:sa_params}, giving 10 free parameters which were treated as uniformly distrubuted in the range given.
 Initially a unit hypercube was generated, then the margins transformed appropriately to cover those regions where the inputs are not bounded between 0 and 1, and for proportions of agent types which necessarily sum to one across the three parameters.
-Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each.
+Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each, with emulator quality assessed by leave-one-out.
 A fixed set of 100 random seeds was used, such that each parameter set was run once with each seed, for every decision rule.
@@
 These emulators were used to conduct a probabalistic sensitivity analysis using \ac{GEM-SA} to assess the impact of parameters individually, and in combination.
+
+In addition to the sensitivity analysis, we also employed the resulting emulators to rapidly\footnote{Once constructed, the emulator is sufficiently quick that results requiring several days of runtime on an HPC can be generated in minutes on a desktop computer.} explore the parameter space.
+While emulated results are subject to innaccuracy, they do provide an indication of the interest, and plausibility, of regions of the parameter space.
+Results for the outcomes of the interactions of \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) with \(x_{h}\), and \(q_{w}\) with \(w_{w}\) are given in section \ref{sub:sa_results}.
 

### 2014-08-28 Model.tex
Writing, updated figures.

@@
 
-Taken together, this leads to a game tree that is relatively complex even at the subgame level (figure \ref{fig:subgame_tree} shows the extensive form for a subgame, with information sets). 
-%The subgame has a large number of pure Nash equilibria, and solution using Gambit \citep{Gambit13}
+Taken together, this leads to a game tree that is relatively complex even at the subgame level.
 Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversial risk analysis \citep{RiosInsua2009}.
-This effectively translates the game to a pair of decision problems, which agents attempt to resolve at each turn using a simple decision rule, given their prior beliefs and experience of play.
+This effectively translates the game to a pair of decision problems (figure \ref{fig:decision_probs}), which agents attempt to resolve at each turn using a simple decision rule, given their prior beliefs and experience of play.
+
+\begin{figure}[H]
+\begin{adjustbox}{center}\subfloat[Women]{\includegraphics[width=0.43\paperwidth]{figures/women_influence}
+
+}\subfloat[Midwives]{\includegraphics[width=0.43\paperwidth]{figures/mw_influence}}\end{adjustbox}
+\caption{Influence diagrams, showing the game broken into two decision problems.}
+
+\label{fig:decision_problems}
+\end{figure}
 

### 2014-08-28 Results.tex
Writing, updated figures.

@@
 
-The relationship is not, however entirely that simple, in that increasing information sharing leads to greater variance between runs.
+The relationship is not, however, entirely that simple, in that increasing information sharing leads to greater variance between runs.
 A linear model was was used to predict the standard deviation between runs of the average signal sent by moderate drinkers, with decision rule, and level of information sharing, together with the interaction between the two as predictors.
@@
 
-\begin{figure}[h!]
-\begin{adjustbox}{center}\includegraphics[width=0.8\paperwidth]{figures/sharing_emulated_simulated}\end{adjustbox}
+\begin{figure}[H]
+\begin{adjustbox}{center}\includegraphics[width=0.8\linewidth]{figures/sharing_emulated_simulated}\end{adjustbox}
 \caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules.}
@@
 
-\begin{figure}[h!]
-\begin{adjustbox}{center}\includegraphics[width=0.8\paperwidth]{figures/unfixed_emu_sig_iqr}\end{adjustbox}
+\begin{figure}[H]
+\begin{adjustbox}{center}\includegraphics[width=0.8\linewidth]{figures/unfixed_emu_sig_iqr}\end{adjustbox}
 \caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\).}
@@
 Following from the suggestive results for information sharing introducing uncertainty (section \ref{sub:info_sharing}), figure \ref{fig:emulated_sharing_iqr} shows emulated points covering the parameter space in high resolution.
-These plots reflect the increase in uncertainty of outcome shown for the heuristic type rules.
+These plots reflect the increase in uncertainty of outcome shown for the heuristic type rules, which is especially severe for the Bayesian payoff rule.
 They also suggest that the Bayesian decision rule is less stable under conditions where the weight of shared information is substantially higher than the probability of sharing.
 Also of interest is the large region of instability that can be discerned for the Bayesian rule under modest probability of information sharing and higher weights.
+This suggests that, perhaps unsurprisingly, that what information is shared is significant to outcomes.
 
@@
 
-\begin{figure}[h!]
-\begin{adjustbox}{center}\includegraphics[width=0.8\paperwidth]{figures/unfixed_emu_payoff_honesty_group_iqr}\end{adjustbox}
+\begin{figure}[H]
+\begin{adjustbox}{center}\includegraphics[width=0.8\linewidth]{figures/unfixed_emu_payoff_honesty_group_iqr}\end{adjustbox}
 \caption{Emulated between groups IQR in response to varying \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\), and \(x_{h}\).}

### 2014-08-28 disclosure_game.tex
Making the sections, slowly
Moar sections
Fiddling with natbib
Added acknowledgements
Fleshing out
Beginning to flesh out, added a stub for a decision problem figure.
Filler
Filler text to be rewritten
Adding algorithms
Progress!
Acronym twiddling
More commentary in methods
Starting in on results
Figures & text
Obviously
Figures!
Writing, updated figures.

@@
 \documentclass{article}
+\usepackage{tikz}
+\usepackage{adjustbox}
+\usepackage{multirow}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 \usepackage{ifthen}
@@
 \usepackage{comment}
-\usepackage[square, numbers]{natbib}
+\usepackage{natbib}
+\setcitestyle{authoryear,round,aysep={,}}
 \usepackage{hyperref}
@@
 \usepackage[subrefformat=parens,labelformat=parens]{subfig}
-\usepackage{acronym}
+\usepackage[nolist,smaller]{acronym}
 \usepackage{nomencl}
 \usepackage[style=long,nolist]{glossaries}
-% the following is useful when we have the old nomencl.sty package
-\providecommand{\printnomenclature}{\printglossary}
-\providecommand{\makenomenclature}{\makeglossary}
+
 \title{Deciding to Disclose: Pregnancy and Alcohol Misuse}
@@
 %\markboth{\spacedlowsmallcaps{Acronyms}}{\spacedlowsmallcaps{Acronyms}}
-\section*{Acronyms}
+%\section*{Acronyms}
 \begin{acronym}[UML]
@@
   \acro{ANOVA}{analysis of variance}
-  \acro{ALSPAC}{Avon Longitudinal Study of Parents and Children}
+  \acro{ALSPAC}{the Avon Longitudinal Study of Parents and Children}
   \acro{GEM}{Gaussian Emulation Machine}
@@
   \acro{JIT}{Just-in-time}
-  \acro{ABM}{Agent Based Model}
+  \acro{ABM}{Agent Based Modelling}
+  \acro{ABMs}{Agent Based Models}
   \acro{CPT}{Cumulative Prospect Theory}
+  \acro{FFH}{Fast and Frugal Heuristic}
+  \acro{OFC}{orbito-frontal cortex}
+  \acro{BACCO}{Bayesian Analysis of Computer Code Outputs}
 \end{acronym}
@@
 \newglossaryentry{episiotomies}{name={episiotomies}, description={An episiotomy is a common procedure where an incision is made in the perineum to facilitate delivery, and attempt to reduce the risk of vaginal tearing}}
-\newglossaryentry{neonatal asphyxia}{name={antenatal},description={The time period covering the pregnancy, prior to birth}}
+%\newglossaryentry{neonatal asphyxia}{name={antenatal},description={The time period covering the pregnancy, prior to birth}}
 
@@
 
+%Assuming this is for JASSS.. Need to make background shorter.
+%Aim for ~ 7-8,000 words overall.
+
 \include{Abstract}
+\acresetall
 
-\section{Introduction} %(half page)
+\include{Introduction} %(half page)
 
@@
 
-\section{Model}
+\include{Model}
 
-\subsection{Disclosure Game}
+\include{Methods}
 
-\subsection{Agent Models}
+\include{Results}
 
-\section{Method}
-\subsection{Qualitative Trends}
-\subsection{Sensitivity Analysis}
+\include{Conclusion}
+\include{Acknowledgements}
 
-\section{Results}
-\subsection{}
+\bibliography{library,library_addendum}
+\bibliographystyle{myplainnat}
 
-\section{Discussion and Conclusions}
+\appendix
 
-\bibliographystyle{plainnat}
-\bibliography{library}
+\include{SensitivityAnalysis}
 \end{document}

### 2014-08-30 Conclusion.tex
Appendix

@@
 
+The conclusions that can be drawn about the behaviours of real life women, and their midwives, are necessarily limited by the paucity of data available to validate the model.
+While qualitative trends offer a some indication, they are clearly very limited in scope, and do not permit strong claims about the drivers of disclosure, and auger for a sceptical eye as to any recommendations targetted at improving outcomes.
+With this said, the trends reported by \citet{Alvik2006}, and \citet{Phillips2007} are bourne out by the model, and predictions from the two more complex rules suggest that encouraging information sharing between women may encourage disclosure, but at the expense of reducing accuracy.
+As such, further work will focus on applying the model to domains where validation data is more available, which will support a more comprehensive evaluation of the model discrepancy.
+
 More broadly, the results demonstrate the logistical feasibility, and utility as a `tool for thinking', of an agent model grounded in decision theory.
@@
 
-The conclusions that can be drawn about the behaviours of real life women, and their midwives, are necessarily limited by the paucity of data available to validate the model.
-While qualitative trends offer a some indication, they are clearly very limited in scope, and do not permit strong claims about the drivers of disclosure, and auger for a sceptical eye as to any recommendations targetted at improving outcomes.
-With this said, the trends reported by \citet{Alvik2006}, and \citet{Phillips2007} are bourne out by the model, and predictions from the two more complex rules suggest that encouraging information sharing between women may encourage disclosure, but at the expense of reducing accuracy.
-
-Further work will focus on applying the model to domains where validation data is more available, which will support a more comprehensive evaluation of the model discrepancy.
-Disclosure is a widely applicable issue in health and social care and beyond, with examples ranging from a lack of help seeking behaviour noted in older men \citep{Smith2007a}, to the inverse scenario of innapropriate disclosure in social media \citep{christofides2009information}.
+ % Disclosure is a widely applicable issue in health and social care and beyond, with examples ranging from a lack of help seeking behaviour noted in older men \citep{Smith2007a}, to the inverse scenario of innapropriate disclosure in social media \citep{christofides2009information}.

### 2014-08-30 SensitivityAnalysis.tex
Appendix

@@
 
-\subsection{Lexicographic}
+\subsubsection{Median Moderate Drinker Signalling}
 
-\subsubsection{Median Moderate Drinker Signalling}
+\begin{table}[h!]
+\center
+\begin{tabular} {|l | l | l | l | l | l |}
+\hline
+Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac(CPT) \\ \hline
+\(p_{w}(m)\) & Proportion of moderate drinkers & 0.367 & 1.145 \\ \hline
+\(p_{w}(l)\) & Proportion of light drinkers & 10.080 & 37.750 \\ \hline
+\(p_{m}(m)\) & Proportion of moderate midwives & 6.715 & 13.017\\ \hline
+\(p_{m}(l)\) & Proportion of non-judgemental midwives & 43.942 & 1.655 \\ \hline
+\(q_{w}\) & Probability of women sharing & 0.198 & 5.527 \\ \hline
+\(w_{w}\) & Weight of shared information for women & 0.355 & 13.025 \\ \hline
+\(q_{m}\) & Probability of midwives sharing & 0.145 & 0.667 \\ \hline
+\(w_{m}\) & Weight of shared information for midwives & 0.118 & 0.376 \\ \hline
+\(x_{h}\) & Health payoff for healthy delivery & 0.457 & 9.618 \\ \hline
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.140 & 7.537 \\ \hline
+\end{tabular}
+\caption[Table caption text]{Median moderate drinker signalling parameter sensitivity. \label{tab:sa_results_sig}}
+\end{table}
+
+\begin{table}[h!]
+\center
+\begin{tabular} {|l | l | l | l | l | l |}
+\hline
+Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
+Lexicographic & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
+Bayesian Payoff & 1.667 & 0.475 &  0.662 & 0.003 & 0.181 & 3.12 \\ \hline
+Bayesian & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
+\ac{CPT} & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
+\end{tabular}
+\caption[Table caption text]{Median moderate drinker signalling emulator statistics. \label{tab:sa_emulator_sig}}
+\end{table}
 
@@
 
+\begin{table}[h!]
+\center
+\begin{tabular} {|l | l | l | l | l | l |}
+\hline
+Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac(CPT) \\ \hline
+\(p_{w}(m)\) & Proportion of moderate drinkers & 0.367 & 1 \\ \hline
+\(p_{w}(l)\) & Proportion of light drinkers & 10.080 & 1 \\ \hline
+\(p_{m}(m)\) & Proportion of moderate midwives & 6.715 & 1 \\ \hline
+\(p_{m}(l)\) & Proportion of non-judgemental midwives & 43.942 & 1 \\ \hline
+\(q_{w}\) & Probability of women sharing & 0.198 & 1 \\ \hline
+\(w_{w}\) & Weight of shared information for women & 0.355 & 1 \\ \hline
+\(q_{m}\) & Probability of midwives sharing & 0.145 & 1 \\ \hline
+\(w_{m}\) & Weight of shared information for midwives & 0.118 & 1 \\ \hline
+\(x_{h}\) & Health payoff for healthy delivery & 0.457 & 100 \\ \hline
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.140 & 100:1 \\ \hline
+\end{tabular}
+\caption[Table caption text]{Median between groups IQR parameter sensitivity. \label{tab:sa_results_iqr}}
+\end{table}
+
+\begin{table}[h!]
+\center
+\begin{tabular} {|l | l | l | l | l | l |}
+\hline
+Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
+Lexicographic & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
+Bayesian Payoff & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
+Bayesian & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
+\ac{CPT} & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
+\end{tabular}
+\caption[Table caption text]{Median between groups IQR emulator statistics. \label{tab:sa_emulator_iqr}}
+\end{table}
+
 \subsubsection{Median Moderate Drinker Signalling IQR}
 
+\begin{table}[h!]
+\center
+\begin{tabular} {|l | l | l | l | l | l |}
+\hline
+Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac(CPT) \\ \hline
+\(p_{w}(m)\) & Proportion of moderate drinkers & 0.367 & 1 \\ \hline
+\(p_{w}(l)\) & Proportion of light drinkers & 10.080 & 1 \\ \hline
+\(p_{m}(m)\) & Proportion of moderate midwives & 6.715 & 1 \\ \hline
+\(p_{m}(l)\) & Proportion of non-judgemental midwives & 43.942 & 1 \\ \hline
+\(q_{w}\) & Probability of women sharing & 0.198 & 1 \\ \hline
+\(w_{w}\) & Weight of shared information for women & 0.355 & 1 \\ \hline
+\(q_{m}\) & Probability of midwives sharing & 0.145 & 1 \\ \hline
+\(w_{m}\) & Weight of shared information for midwives & 0.118 & 1 \\ \hline
+\(x_{h}\) & Health payoff for healthy delivery & 0.457 & 100 \\ \hline
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.140 & 100:1 \\ \hline
+\end{tabular}
+\caption[Table caption text]{IQR of median moderate drinker signalling parameter sensitivity. \label{tab:sa_results_sig_iqr}}
+\end{table}
+
+\begin{table}[h!]
+\center
+\begin{tabular} {|l | l | l | l | l | l |}
+\hline
+Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
+Lexicographic & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
+Bayesian Payoff & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
+Bayesian & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
+\ac{CPT} & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
+\end{tabular}
+\caption[Table caption text]{IQR of median between groups IQR emulator statistics. \label{tab:sa_emulator_sig_iqr}}
+\end{table}
+
 \subsubsection{Between Groups IQR IQR}
+
+\begin{table}[h!]
+\center
+\begin{tabular} {|l | l | l | l | l | l |}
+\hline
+Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac(CPT) \\ \hline
+\(p_{w}(m)\) & Proportion of moderate drinkers & 0.367 & 1 \\ \hline
+\(p_{w}(l)\) & Proportion of light drinkers & 10.080 & 1 \\ \hline
+\(p_{m}(m)\) & Proportion of moderate midwives & 6.715 & 1 \\ \hline
+\(p_{m}(l)\) & Proportion of non-judgemental midwives & 43.942 & 1 \\ \hline
+\(q_{w}\) & Probability of women sharing & 0.198 & 1 \\ \hline
+\(w_{w}\) & Weight of shared information for women & 0.355 & 1 \\ \hline
+\(q_{m}\) & Probability of midwives sharing & 0.145 & 1 \\ \hline
+\(w_{m}\) & Weight of shared information for midwives & 0.118 & 1 \\ \hline
+\(x_{h}\) & Health payoff for healthy delivery & 0.457 & 100 \\ \hline
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.140 & 100:1 \\ \hline
+\end{tabular}
+\caption[Table caption text]{IQR of median between groups IQR parameter sensitivity. \label{tab:sa_results_iqr_iqr}}
+\end{table}
+
+\begin{table}[h!]
+\center
+\begin{tabular} {|l | l | l | l | l | l |}
+\hline
+Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
+Lexicographic & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
+Bayesian Payoff & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
+Bayesian & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
+\ac{CPT} & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
+\end{tabular}
+\caption[Table caption text]{IQR of median between groups IQR emulator statistics. \label{tab:sa_emulator_iqr_iqr}}
+\end{table}

### 2014-08-30 SensitivityAnalysis.tex
Emulator tables

--- 2014-08-26 SensitivityAnalysis.tex
@@
 
-\subsection{Lexicographic}
+\subsubsection{Median Moderate Drinker Signalling}
 
-\subsubsection{Median Moderate Drinker Signalling}
+\begin{table}[h!]
+\center
+\begin{tabular} {|l | l | l | l | l | l |}
+\hline
+Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac(CPT) \\ \hline
+\(p_{w}(m)\) & Proportion of moderate drinkers & 0.367 & 1.145 & 0.801 & 0.614 \\ \hline
+\(p_{w}(l)\) & Proportion of light drinkers & 10.080 & 37.750 & 23.968  & 5.137\\ \hline
+\(p_{m}(m)\) & Proportion of moderate midwives & 6.715 & 13.017 & 0.894 & 1.485\\ \hline
+\(p_{m}(l)\) & Proportion of non-judgemental midwives & 43.942 & 1.655 & 1.602 & 2.618 \\ \hline
+\(q_{w}\) & Probability of women sharing & 0.198 & 5.527 & 4.460 & 1.159 \\ \hline
+\(w_{w}\) & Weight of shared information for women & 0.355 & 13.025 & 2.716 & 0.888 \\ \hline
+\(q_{m}\) & Probability of midwives sharing & 0.145 & 0.667 & 0.368 & 0.157 \\ \hline
+\(w_{m}\) & Weight of shared information for midwives & 0.118 & 0.376 & 0.176 & 0.200 \\ \hline
+\(x_{h}\) & Health payoff for healthy delivery & 0.457 & 9.618 & 1.912 & 15.355 \\ \hline
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.140 & 7.537 & 10.427 & 7.795 \\ \hline
+\end{tabular}
+\caption[Table caption text]{Median moderate drinker signalling parameter sensitivity. \label{tab:sa_results_sig}}
+\end{table}
+
+\begin{table}[h!]
+\center
+\begin{tabular} {|l | l | l | l | l | l |}
+\hline
+Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
+Lexicographic & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
+Bayesian Payoff & 1.667 & 0.475 &  0.662 & 0.003 & 0.181 & 3.12 \\ \hline
+Bayesian & 3.352 & 0.534 & 1.160 & 0.001 & 0.068 & 2.423 \\ \hline
+\ac{CPT} & 1.503 & 0.331 & 1.241 & 0.002 & 0.101 & 1.842 \\ \hline
+\end{tabular}
+\caption[Table caption text]{Median moderate drinker signalling emulator statistics. \label{tab:sa_emulator_sig}}
+\end{table}
 
@@
 
+\begin{table}[h!]
+\center
+\begin{tabular} {|l | l | l | l | l | l |}
+\hline
+Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac(CPT) \\ \hline
+\(p_{w}(m)\) & Proportion of moderate drinkers & 0.327 & 0.688 & 0.457 & 0.586 \\ \hline
+\(p_{w}(l)\) & Proportion of light drinkers & 11.223 & 20.123 & 11.046 & 4.081 \\ \hline
+\(p_{m}(m)\) & Proportion of moderate midwives & 36.630 & 1.160 & 0.364 & 1.945 \\ \hline
+\(p_{m}(l)\) & Proportion of non-judgemental midwives & 6.228 & 4.487 & 0.0964 & 2.627\\ \hline
+\(q_{w}\) & Probability of women sharing & 0.498 & 0.235 & 2.537 & 1.812 \\ \hline
+\(w_{w}\) & Weight of shared information for women & 1.018 & 2.307 & 1.889 & 0.740 \\ \hline
+\(q_{m}\) & Probability of midwives sharing & 0.158 & 0.343 & 0.387 & 0.156 \\ \hline
+\(w_{m}\) & Weight of shared information for midwives & 0.076 & 0.973 & 0.125 & 0.213 \\ \hline
+\(x_{h}\) & Health payoff for healthy delivery & 0.317 & 10.960 & 3.305 & 16.493 \\ \hline
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 1.107 & 8.411 & 2.890 & 6.729 \\ \hline
+\end{tabular}
+\caption[Table caption text]{Median between groups IQR parameter sensitivity. \label{tab:sa_results_iqr}}
+\end{table}
+
+\begin{table}[h!]
+\center
+\begin{tabular} {|l | l | l | l | l | l |}
+\hline
+Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
+Lexicographic & 0.930 & 0.240 & 0.249 & 0.002 & 0.040 & 1.832 \\ \hline
+Bayesian Payoff & 1.242 & 0.417 & 0.232 & 0.001 & 0.0034 & 2.308 \\ \hline
+Bayesian & 1.254 & 0.131 & 0.644 & 0.000 & 0.019 & 1.167 \\ \hline
+\ac{CPT} & 1.190 & 0.313 & 0.659 & 0.000 & 0.024 & 1.701 \\ \hline
+\end{tabular}
+\caption[Table caption text]{Median between groups IQR emulator statistics. \label{tab:sa_emulator_iqr}}
+\end{table}
+
 \subsubsection{Median Moderate Drinker Signalling IQR}
 
+\begin{table}[h!]
+\center
+\begin{tabular} {|l | l | l | l | l | l |}
+\hline
+Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac(CPT) \\ \hline
+\(p_{w}(m)\) & Proportion of moderate drinkers & 0.428 & 9.828 & 3.816 & 2.068 \\ \hline
+\(p_{w}(l)\) & Proportion of light drinkers & 8.369 & 13.791 & 4.045 & 2.400 \\ \hline
+\(p_{m}(m)\) & Proportion of moderate midwives & 13.416 & 0.712 & 0.676 & 0.583 \\ \hline
+\(p_{m}(l)\) & Proportion of non-judgemental midwives & 21.079 & 0.648 & 0.659 & 0.373 \\ \hline
+\(q_{w}\) & Probability of women sharing & 2.307 & 3.481 & 0.891 & 0.600 \\ \hline
+\(w_{w}\) & Weight of shared information for women & 6.021 & 6.009 & 0.562 & 0.937 \\ \hline
+\(q_{m}\) & Probability of midwives sharing & 0.315 & 1.829 & 0.114 & 0.117 \\ \hline
+\(w_{m}\) & Weight of shared information for midwives & 1.652 & 1.354 & 0.260 & 0.0.139 \\ \hline
+\(x_{h}\) & Health payoff for healthy delivery & 0.253 & 0.612 & 4.889 & 15.146 \\ \hline
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.504 & 3.096 & 19.863 & 25.999 \\ \hline
+\end{tabular}
+\caption[Table caption text]{IQR of median moderate drinker signalling parameter sensitivity. \label{tab:sa_results_sig_iqr}}
+\end{table}
+
+\begin{table}[h!]
+\center
+\begin{tabular} {|l | l | l | l | l | l |}
+\hline
+Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
+Lexicographic & 1.425 & 0.436 & 0.549 & 0.008 & 0.114 & 2.719 \\ \hline
+Bayesian Payoff & 1.223 & 0.496 & 0.747 & 0.012 & 0.207 & 2.034 \\ \hline
+Bayesian &  1.065 & 0.000 & 0.230 & 0.002 & 0.088 & 1.015 \\ \hline
+\ac{CPT} & 0.874 & 0.213 & 0.233 & 0.001 & 0.066 & 1.806 \\ \hline
+\end{tabular}
+\caption[Table caption text]{IQR of median between groups IQR emulator statistics. \label{tab:sa_emulator_sig_iqr}}
+\end{table}
+
 \subsubsection{Between Groups IQR IQR}
+
+\begin{table}[h!]
+\center
+\begin{tabular} {|l | l | l | l | l | l |}
+\hline
+Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac(CPT) \\ \hline
+\(p_{w}(m)\) & Proportion of moderate drinkers & 0.691 & 5.926 & 1.053 & 1.265 \\ \hline
+\(p_{w}(l)\) & Proportion of light drinkers & 3.664 & 17.047 & 4.877 & 3.656 \\ \hline
+\(p_{m}(m)\) & Proportion of moderate midwives & 41.369 & 1.124 & 0.814 & 0.591 \\ \hline
+\(p_{m}(l)\) & Proportion of non-judgemental midwives & 7.109 & 0.739 & 0.496 & 0.378 \\ \hline
+\(q_{w}\) & Probability of women sharing & 1.963 & 2.038 & 0.733 & 0.589 \\ \hline
+\(w_{w}\) & Weight of shared information for women & 7.932 & 11.193 & 2.289 & 1.960 \\ \hline
+\(q_{m}\) & Probability of midwives sharing & 0.413 & 1.972 & 0.267 & 0.069\\ \hline
+\(w_{m}\) & Weight of shared information for midwives & 0.120 & 2.902 & 0.150 & 0.123 \\ \hline
+\(x_{h}\) & Health payoff for healthy delivery & 0.228 & 3.190 & 6.308 & 14.777 \\ \hline
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.673 & 10.411 & 22.901 & 26.340 \\ \hline
+\end{tabular}
+\caption[Table caption text]{IQR of median between groups IQR parameter sensitivity. \label{tab:sa_results_iqr_iqr}}
+\end{table}
+
+\begin{table}[h!]
+\center
+\begin{tabular} {|l | l | l | l | l | l |}
+\hline
+Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
+Lexicographic & 0.826 & 0.409 & 0.259 & 0.002 & 0.034 & 2.364 \\ \hline
+Bayesian Payoff & 3.202 & 0.520 & 0.328 & 0.002 & 0.032 & 2.452 \\ \hline
+Bayesian & 1.177 & 0.041 & 0.133 & 0.000 & 0.018 & 1.152 \\ \hline
+\ac{CPT} & 0.874 & 0.118 & 0.126 & 0.000 & 0.017 & 1.570 \\ \hline
+\end{tabular}
+\caption[Table caption text]{IQR of median between groups IQR emulator statistics. \label{tab:sa_emulator_iqr_iqr}}
+\end{table}

### 2014-08-30 Methods.tex
Appendix
Tables, switched to input rather than include
Because nesting

@@
 \(n_{m}\) & Number of midwives & 100 \\ \hline
-\(r_{m}\) & Number of appointments per midwive & 1000 \\ \hline
+\(r_{m}\) & Number of appointments per midwife & 1000 \\ \hline
 \(r_{w}\) & Maximum number of appointments per woman & 12 \\ \hline
@@
 Initially a unit hypercube was generated, then the margins transformed appropriately to cover those regions where the inputs are not bounded between 0 and 1, and for proportions of agent types which necessarily sum to one across the three parameters.
-Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each, with emulator quality assessed by leave-one-out.
+Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each, with emulator quality assessed by leave-one-out cross validation.
 A fixed set of 100 random seeds was used, such that each parameter set was run once with each seed, for every decision rule.
 
-To better capture the response characteristics for the model, we measure four outcome variables - (1) the interquartile range of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3, 4) the interquartile range of the average signal, and interquartile range between simulation runs.
+To capture the response characteristics for the model, we measure four outcome variables - (1) the interquartile range of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3, 4) the interquartile range of the average signal, and interquartile range between simulation runs.
 Together these four metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the variability in the system in response to changes to the parameters (3 \& 4).

### 2014-08-30 SensitivityAnalysis.tex
Wrong brackets
Fixed number of columns
Tables, switched to input rather than include
Because nesting

@@
 
-\subsubsection{Median Moderate Drinker Signalling}
+\subsection{Median Moderate Drinker Signalling}
 
-\begin{table}[h!]
+\begin{table}[H]
 \center
@@
 \hline
-Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac(CPT) \\ \hline
+Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\ \hline
 \(p_{w}(m)\) & Proportion of moderate drinkers & 0.367 & 1.145 & 0.801 & 0.614 \\ \hline
@@
 \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.140 & 7.537 & 10.427 & 7.795 \\ \hline
+Total & All parameters and two way interactions & 86.777 & 96.527 & 85.529 & 74.123 \\ \hline
 \end{tabular}
@@
 
-\begin{table}[h!]
+\begin{table}[H]
 \center
-\begin{tabular} {|l | l | l | l | l | l |}
+\begin{tabular} {|l | l | l | l | l | l | l |}
 \hline
@@
 
-\subsubsection{Median Between Groups IQR}
+\input{top_5_table_sig}
 
-\begin{table}[h!]
+\subsection{Median Between Groups IQR}
+
+\begin{table}[H]
 \center
@@
 \hline
-Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac(CPT) \\ \hline
+Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\ \hline
 \(p_{w}(m)\) & Proportion of moderate drinkers & 0.327 & 0.688 & 0.457 & 0.586 \\ \hline
@@
 \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 1.107 & 8.411 & 2.890 & 6.729 \\ \hline
+Total & All parameters and two way interactions & 81.702 & 83.693 & 47.449 & 71.032 \\ \hline
 \end{tabular}
@@
 
-\subsubsection{Median Moderate Drinker Signalling IQR}
+\input{top_5_table_group_iqr}
 
-\begin{table}[h!]
+\subsection{Median Moderate Drinker Signalling IQR}
+
+\begin{table}[H]
 \center
@@
 \hline
-Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac(CPT) \\ \hline
+Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\ \hline
 \(p_{w}(m)\) & Proportion of moderate drinkers & 0.428 & 9.828 & 3.816 & 2.068 \\ \hline
@@
 \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.504 & 3.096 & 19.863 & 25.999 \\ \hline
+Total & All parameters and two way interactions & 84.9968 & 77.413 & 57.125 & 83.322 \\ \hline
 \end{tabular}
@@
 
-\subsubsection{Between Groups IQR IQR}
+\input{top_5_table_sig_iqr}
 
-\begin{table}[h!]
+\subsection{Between Groups IQR IQR}
+
+\begin{table}[H]
 \center
@@
 \hline
-Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac(CPT) \\ \hline
+Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\ \hline
 \(p_{w}(m)\) & Proportion of moderate drinkers & 0.691 & 5.926 & 1.053 & 1.265 \\ \hline
@@
 \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.673 & 10.411 & 22.901 & 26.340 \\ \hline
+Total & All parameters and two way interactions & 85.740 & 88.611 & 68.640 & 84.210 \\ \hline
 \end{tabular}
@@
 \end{table}
+
+\input{top_5_table_group_iqr_iqr}

### 2014-08-30 Abstract.tex
Bit more on results

@@
 
-To aid in replication and extension, the model has been implemented as a Python module, and is freely available under the Mozilla Public License from \url{https://github.com/greenape/disclosure-game}, together with full parameter sets, raw data, and all other code used in producing this paper.
+To aid in replication and extension, the model has been implemented as a Python module, and is freely available under the Mozilla Public License from \url{https://github.com/greenape/disclosure-game-module}.

### 2014-08-30 Conclusion.tex
Bit more on results

@@
 
+As noted in section \ref{sub:sensitivity}, the impact of information sharing between midwives is surprisingly minimal, where it might be expected to play a more significant role in reality.
+A possible explanation for this lies in the implementation, which may place an excessive constraint on how much information midwives can share.
+The restriction to sharing only after a referral, together with the disparity in population sizes, and random allocation of appointments leads to midwives rarely having more than a single interaction with woman to pass on to their colleagues.
+In reality it might be anticipated that midwives would not withhold judgement so completely, and would concerns about particular women to their colleagues.
+This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared.
+This also highlights an advantage of the \ac{BACCO} approach, in that it aids in diagnosing issues with model design by giving insight into parameters which are contributing innapropriately to variance in output.
+
 The conclusions that can be drawn about the behaviours of real life women, and their midwives, are necessarily limited by the paucity of data available to validate the model.
 While qualitative trends offer a some indication, they are clearly very limited in scope, and do not permit strong claims about the drivers of disclosure, and auger for a sceptical eye as to any recommendations targetted at improving outcomes.
+As such, further work will focus on applying the model to domains where validation data is more available, which will support a more comprehensive evaluation of the model discrepancy.
 With this said, the trends reported by \citet{Alvik2006}, and \citet{Phillips2007} are bourne out by the model, and predictions from the two more complex rules suggest that encouraging information sharing between women may encourage disclosure, but at the expense of reducing accuracy.
-As such, further work will focus on applying the model to domains where validation data is more available, which will support a more comprehensive evaluation of the model discrepancy.
+By contrast, if one takes the view that a Lexicographic model is a better approximation of real behaviour, then outcomes can best be influenced by controlling how far midwives punish their women socially.
+We would however suggest that there are better reasons than the outputs of a simulation for doing so.
 

### 2014-08-30 Methods.tex
Bit more on results

@@
 \cite{Neilson2002,Glockner2012,Nilsson2011}, and particularly \citet{Byrnes1999,Booij2009} addressing risk aversion and gender), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work.
-For simplicity, it is assumed that all three drinking types are equally prevalent within the population, although results derived from \ac{ALSPAC} suggest that the reality is far more positive \citep{Humphriss2013}.
-The scenario is biased towards disclosure as the better option by presuming a distribution of midwives strongly skewed towards non-judgemental types, with beliefs initially favouring honesty.
+For simplicity, it was assumed that all three drinking types are equally prevalent within the population, although results derived from \ac{ALSPAC} suggest that the reality is far more positive \citep{Humphriss2013}.
+The scenario was biased towards disclosure as the better option by presuming a distribution of midwives strongly skewed towards non-judgemental types, with beliefs initially favouring honesty.
 Payoffs were as in table \ref{tab:Payoff-matrix}, which ensure that it is always strictly preferable to refer drinkers, and together with the initial belief that signals will be honest, not refer those claiming otherwise.
@@
 
-In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examine the impact of simple information sharing within the population of women (section \ref{sub:info_sharing}) on the robustness of these trends.
+In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examined the impact of simple information sharing within the population of women (section \ref{sub:info_sharing}) on the robustness of these trends.
 The original experiment was repeated at \(q_{w}=w_{w}={0.25, 0.5, 0.75, 1}\), with 100 runs under each condition.
@@
 %Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
-In general, we follow the example of \cite{Bijak2013b} for global sensitivity analysis of stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques.
+In general, we have followed the example of \cite{Bijak2013b} for global sensitivity analysis of stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques.
 For this purpose the \ac{GEM-SA} software \citep{Kennedy} was used, which implements the \ac{BACCO} method developed by \citeauthor{Oakley2004} \citep{Oakley2002,Oakley2004,Dorresteijn2010}.
@@
 
-To capture the response characteristics for the model, we measure four outcome variables - (1) the interquartile range of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3, 4) the interquartile range of the average signal, and interquartile range between simulation runs.
+To capture the response characteristics for the model, we measured four outcome variables - (1) the interquartile range of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3, 4) the interquartile range of the average signal, and interquartile range between simulation runs.
 Together these four metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the variability in the system in response to changes to the parameters (3 \& 4).
@@
 Name & Description & Min & Max \\ \hline
-\(p_{w}(h)\) & Proportion of heavy drinkers & 0 & 1 \\ \hline
 \(p_{w}(m)\) & Proportion of moderate drinkers & 0 & 1 \\ \hline
 \(p_{w}(l)\) & Proportion of light drinkers & 0 & 1 \\ \hline
-\(p_{m}(h)\) & Proportion of harsh midwives & 0 & 1 \\ \hline
 \(p_{m}(m)\) & Proportion of moderate midwives & 0 & 1 \\ \hline

### 2014-08-30 Results.tex
Bit more on results

@@
 The relationship is not, however, entirely that simple, in that increasing information sharing leads to greater variance between runs.
-A linear model was was used to predict the standard deviation between runs of the average signal sent by moderate drinkers, with decision rule, and level of information sharing, together with the interaction between the two as predictors.
+A linear model was was used to predict the between runs interquartile range of the average signal sent by moderate drinkers, with decision rule, and level of information sharing, together with the interaction between the two as predictors.
 The regression results were significant (\(F_{7,12}=25,p<2.9\times10^{-6}\)) with \(R^2=94\%\), and intercept 0.07.
@@
 
-In this section we present selected results highlighting the global effect of changes to perceived payoffs and degree of bias towards honesty, as well as information sharing within women.
+In this section we present a brief overview of the sensitivity analysis, followed by selected results highlighting the global effect of changes to perceived payoffs and degree of bias towards honesty, as well as information sharing within women.
 The full results for the sensitivity analysis covering all sixteen emulators are available in appendix \ref{app:sensitivity_results}.
+
+For the median signal choice of moderate drinkers, the emulator results suggest that the proportion of light drinkers has a significant effect for all decision rules, accounting for 10\%, 38\%, 24\%, and 5\% of the variance in output for the Lexicographic, Bayesian Payoff, Bayesian, and \ac{CPT} rules respectively.
+For the Lexicographic rule, the overwhelming majority of variance in signalling behaviour is attributable to the proportions of midwives (44\% \(p_{m}(m)\), 7\% \(p_{l}(m)\), and a further 15\% for their interaction).
+The proportions of midwives are also key drivers in group separation, and the between run IQR of both measures for this rule.
+
+Perhaps surprisingly, variance attributable to information sharing between midwives is relatively low, with neither the weight nor probability accounting for more than 5\% of variance in any measure.
+While there are small contributions to variance in interaction with other parameters (e.g.
+4\% to between groups IQR, for the interaction with the proportion of light drinkers under the Bayesian rule), this may suggest that the implementation is lacking, which we touch on in section \ref{sec:conclusion}.
 

### 2014-08-30 build.sh

@@ -4,3 +4,4 @@ makeglossaries disclosure_game
 bibtex disclosure_game
 pdflatex -interaction=batchmode disclosure_game
 pdflatex -interaction=batchmode disclosure_game
+pdflatex -interaction=batchmode disclosure_game

### 2014-10-29 Abstract.tex
Ammendments

@@
 
-We draw together methodologies from game theory, agent based modelling, and decision theory to explore the process of decision making around disclosure.
-This is framed in the context of pregnant women disclosing their drinking behaviour to their midwives.
+We draw together methodologies from game theory, agent based modelling, decision theory, and uncertainty analysis to explore the process of decision making in the context of pregnant women disclosing their drinking behaviour to their midwives.
 
@@
 
-The primary purpose it to demonstrate the potential utility of an approach which it is hoped goes some way towards addressing concerns about the ad hoc character of \ac{ABM}, by providing a strong theoretical grounding for the reasoning processes of individual agents.
-To this end we hope to show that these simple rules, operating in an inescapably artificial scenario are nonetheless capable of producing trends from the literature.
-We also seek to demonstrate the significance of precisely how the decision making process is formulated, by contrasting four distinct decision rules against one another and exploring a simple form of information sharing, supported by the use of statistical emulators for a full exploration of the parameter space.
+The primary purpose of this work is to demonstrate the significance of precisely how the decision making process is formulated, by contrasting four distinct decision rules against one another and exploring a simple form of information sharing, supported by the use of statistical emulators for a full exploration of the parameter space.
+We also demonstrate the utility of an approach which it is hoped goes some way towards addressing concerns about the ad hoc character of \ac{ABM}, by providing a strong theoretical grounding for the reasoning processes of individual agents.
+To this end we hope to show that these simple rules, operating in an inescapably artificial scenario are nonetheless capable of reproducing trends from the literature.
 
@@
 
-We employ game theory to define a signalling game representative of a scenario where pregnant women decide how far to disclose their drinking behaviours to their midwives, and midwives employ the information provided to decide whether a costly referral should be made.
-This game is then recast as two games taking play against nature, to permit the use of a decision theoretic approach where both classes of agent use simple rules to decide their moves.
-Four decision rules are explored - a lexicographic heuristic which considers only the link between moves and payoffs, a Bayesian risk minimisation agent that uses the same information, a more complex Bayesian risk minimiser, and a \ac{CPT} type.
+We employ game theory to define a signalling game representative of a scenario where pregnant women decide the extent to which they disclose their drinking behaviours to their midwives, and midwives employ the information provided to decide whether to refer their patients for costly specialist treatment.
+This game is then recast as two games played against nature, to permit the use of a decision theoretic approach where both classes of agent use simple rules to decide their moves.
+Four decision rules are explored - a lexicographic heuristic which considers only the link between moves and payoffs, a Bayesian risk minimisation agent that uses the same information, a more complex Bayesian risk minimiser with full access to the structure of the decision problem, and a \ac{CPT} rule.
 
-Using a simulator we have developed in Python, we recreate two key qualitative trends described in the Midwifery literature for all the decision models, and investigate the impact of introducing a simple form of information sharing within agent groups.
+In simulation, we recreate two key qualitative trends described in the Midwifery literature for all the decision models, and investigate the impact of introducing a simple form of information sharing within agent groups.
 Finally a global sensitivity analysis using \acp{GEM} was conducted, to compare the response surfaces of the different decision rules in the game.
@@
 
-We note that the scenario omits the overwhelming complexity of the reality, and is presented largely in the spirit of a convenient demonstration of the methodology.
+We note that the model omits the overwhelming complexity of the real disclosure scenario, and is presented largely in the spirit of a convenient demonstration of the methodology.
 Clearly a domain where there is sufficient data to permit a more comprehensive approach to validation of model outcomes is desirable, and will form the basis of our future work.

### 2014-10-29 Background.tex
Ammendments

@@
 
-This basic form has been widely applied, with substantial interest in what conditions permit honest signalling as Nash equilibria or \ac{ESS}.
+This basic form has been widely applied, with substantial interest in what conditions permit honest signalling as Nash equilibria or \acp{ESS}.
 \citet{Grafen1990}, following from a suggestion by \citet{Zahavi1975}, proposed that if signals intended to indicate mate quality exacted a cost on the signaller (e.g.
@@
 This model has seen notable successes in practical problems \citep{McNamara1980,Survey2003,Kristensen1997}, but suggestions by several authors  that it could constitute an effective (top-down) model of learning \citep{Tenenbaum2006,Griffiths2010}, or induction \citep{Gallistel2012} in the brain have attracted substantil criticism, e.g.
-\citet{Bowers2012}, and \citet{Miller2012} responding to \citeauthor{Tenenbaum2006,Griffiths2010}, and \citeauthor{Gallistel2012} respectively.
+\citet{Bowers2012} responding to \citeauthor{Tenenbaum2006}, and \citeauthor{Griffiths2010}; and \citet{Miller2012} addressing \citeauthor{Gallistel2012}.
 

### 2014-10-29 Conclusion.tex
Ammendments

@@
 The restriction to sharing only after a referral, together with the disparity in population sizes, and random allocation of appointments leads to midwives rarely having more than a single interaction with woman to pass on to their colleagues.
-In reality it might be anticipated that midwives would not withhold judgement so completely, and would concerns about particular women to their colleagues.
-This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared.
+Furthermore, because midwives are only informed of the true type if a referral occurs, they have an inherent myopia, since until they have evidence of deception they will not refer, with said evidence difficult to obtain without a referral.
+
+In reality it might be anticipated that midwives would not withhold judgement so completely, and would pass on concerns about particular women to their colleagues, or that particularly dramatic stories would persist and be passed.
+This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared and more sophisticated model of information transmission in general.
 This also highlights an advantage of the \ac{BACCO} approach, in that it aids in diagnosing issues with model design by giving insight into parameters which are contributing innapropriately to variance in output.

### 2014-10-29 Introduction.tex
Ammendments

@@
 
-The case in favour of \ac{ABM} as a general approach has been made numerously, and elegantly \citep{Silverman2011,Silverman2013,Resnick,gilbert1999simulation,epstein1994growing,Macy2002a,Axelrod1997}.
+The case in favour of \ac{ABM} as a general approach has been made numerously, and elegantly (e.g.
+\citet{Silverman2011,Silverman2013,Resnick,gilbert1999simulation,epstein1994growing,Macy2002a,Axelrod1997}, amongst others).
 As such we will not belabour the point, and instead turn to addressing some of the concerns expressed about the method.
@@
 For example, \citet{Andersen2012} report results from a large scale Danish cohort study suggesting that even low levels of consumption in early pregnancy increase the risk of spontaneous abortion, although \citet{Savitz2012} has suggested this may be attributable to a previously known link to absence of mornining sickness.
-Risk continues to the point of birth - \citet{Kesmodel2002} found a heightened risk to the infant - into childhood, with a metastudy by \citet{Latino-Martel2010} finding evidence on an increased risk of childhood \ac{AML} (although they suggest that the rarity of the condition is a limitation).
+Risk continues to the point of birth - \citet{Kesmodel2002} found a heightened risk to the infant - into childhood, with a metastudy by \citet{Latino-Martel2010} finding evidence on an increased risk of childhood \ac{AML}.
 Harm may also extend even further, and a review by \citet{Huizink2006} concluded that maternal alcohol consumption could be a contributing factor to \ac{ADHD}, and other learning impairments, but note methodological issues in a number of the papers.

### 2014-10-29 Model.tex
Ammendments

@@
 
-Taken together, this leads to a game tree that is relatively complex even at the subgame level.
+Taken together, this leads to a game tree that is relatively complex (figure \ref{fig:simple_tree} shows a simplified representation) even at the subgame level.
 Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversial risk analysis \citep{RiosInsua2009}.
-This effectively translates the game to a pair of decision problems (figure \ref{fig:decision_probs}), which agents attempt to resolve at each turn using a simple decision rule, given their prior beliefs and experience of play.
+This effectively translates the game to a pair of decision problems (figure \ref{fig:decision_problems}), which agents attempt to resolve at each turn using a simple decision rule, given their prior beliefs and experience of play.
+
+\begin{figure}[H]
+\begin{adjustbox}{center}
+\subfloat[Women]{\includegraphics[width=0.43\paperwidth]{figures/simple_game_tree}}
+\end{adjustbox}
+\caption{Simmplified game tree.}
+
+\label{fig:simple_tree}
+\end{figure}
 
@@
 
-As noted in section \ref{sub:the_game}, agents have perfect recall, and recognise individual opponents if they encounter them subsequently.
+As noted in section \ref{sub:the_game}, agents have perfect recall, and midwives recognise women if they encounter them subsequently.
 While agents recall perfectly and make use of the new information for retrospective updates, all four agent models make decisions `as-if' they were always facing a new opponent.
@@
 
-The lexicographic heuristic (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified decision problem, as in figure \ref{fig:payoff_problem}, where an action is a choice between combined lotteries.
+The lexicographic heuristic (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified, where an action is a choice between combined lotteries.
 Functionally, the heuristic maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e.
@@
 decision rule is used in this instance, because of the requirement
-for women to evaluate more than two `prospects'.\footnote{A prospect in this instance is a paired outcome and probability, and the set of prospects
-for an action hence define the outcome space.} \ac{CPT} introduces
-the concept of a probability weighting function, which underweights
-small probabilities, and overweights large ones in an effort to capture
-the tendency of humans to treat high probability events as sure things,
-and small probabilities as `never going to happen'. A number of different
-weighting functions have been proposed, but in this instance the original
-formulation by \citet{Tversky1992} is used. This distinguishes between
-weighting for gains, and losses -
+for women to evaluate more than two `prospects'.\footnote{Where a prospect is a payoff-probability pair, with the set of prospects for an action defining the possible outcomes for it.} \ac{CPT} uses transformed probabilities, underweighting
+small probabilities, and overweighting large ones.
+This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and contrastingly low probabilities as impossible.
+The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains and losses -
 
@@
 Where $p$ is the unweighted probability, and $\gamma$ and $\delta$
-are the weights for gain and loss probabilities respectively. Humans
-have also been observed to value gains and losses differently, with
-a loss being `worse' than the equivalent gain is `good'. This
-entails a transformed value function -
+are the weights for gain and loss probabilities respectively.
+Along similar lines, the values of losses and gains are transformed to reflect a tendency to regard a loss as more significant than a gain  -
 
@@
 value is the sum of the value of the prospects of that action, as
-in the Bayesian risk model. The decision rule then requires the agent
-to choose the action which maximises the prospect theory value.
+in the Bayesian risk model, and the agent chooses the option which maximises this quantity.
 

### 2014-10-29 Results.tex
Ammendments

@@
 \begin{figure}[H]
-\begin{adjustbox}{center}\subfloat[Average fraction of population signalling honestly\label{fig:honest_signals}]{\includegraphics[width=0.43\paperwidth]{figures/honesty_plot}
+\begin{adjustbox}{center}\subfloat[Average fraction of population ever signalled honestly\label{fig:honest_signals}]{\includegraphics[width=0.43\paperwidth]{figures/honesty_plot}
 
@@
 
-The relationship is not, however, entirely that simple, in that increasing information sharing leads to greater variance between runs.
+The relationship is not, however, entirely straighforward, in that increasing information sharing leads to greater variance between runs.
 A linear model was was used to predict the between runs interquartile range of the average signal sent by moderate drinkers, with decision rule, and level of information sharing, together with the interaction between the two as predictors.
@@
 Figure \ref{fig:emulated_payoff_group_iqr} shows the effects, and also highlights the tendency towards poor separability of groups for both the heuristic type decision rules.
-The response surface of the Bayesian payoff rule is slightly more nuanced than the simple Lexicographic rule, showing better separation close to partial pooling at high payoff distinction, with relatively modest honesty bias.
+The response surface of the Bayesian payoff rule is slightly more nuanced than the simple Lexicographic rule.
+Figure \ref{fig:emulated_payoff_group_iqr} shows better separation close to partial pooling at high payoff distinction, with relatively modest honesty bias, which is reflected by the variance contributions of 11\% and 8\% respectively.
 For the more complex rules, the general tendency is towards less pooling for higher values of both, but with pockets where full pooling occurs.
-The plots also suggest that the sensitivity of the \ac{CPT} rule is marginally greater, which reflects the distorted utility function.
+The plots also suggest that the sensitivity of the \ac{CPT} rule is marginally greater, which is supported by the significant contribution to variance of close to 15\% for all measures of \(x_{h}\).
 

### 2014-12-17 Model.tex
Game tree diagrams
Clearer emulated-simulated figure

@@
 
-Taken together, this leads to a game tree that is relatively complex (figure \ref{fig:simple_tree} shows a simplified representation) even at the subgame level.
+Taken together, this leads to a game tree that is relatively complex (figure \ref{fig:simple_tree} shows a simplified representation, with a detailed view of one branch in figure \ref{fig:zoom_tree}) even at the subgame level.
 Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversial risk analysis \citep{RiosInsua2009}.
@@
 \begin{adjustbox}{center}
-\subfloat[Women]{\includegraphics[width=0.43\paperwidth]{figures/simple_game_tree}}
+\includegraphics[width=0.43\paperwidth]{figures/rounded_clover_infosets}
 \end{adjustbox}
-\caption{Simmplified game tree.}
+\caption{Simplified game tree.}
 
 \label{fig:simple_tree}
+\end{figure}
+
+\begin{figure}[H]
+\begin{adjustbox}{center}
+\includegraphics[width=0.43\paperwidth]{figures/tree_zoom}
+\end{adjustbox}
+\caption{Detail view of a single game tree branch.}
+
+\label{fig:zoom_tree}
 \end{figure}

### 2014-12-18 Introduction.tex
Less equivocation

@@
 
-This is framed in the context of disclosure decisions, and a scenario examining drinking patterns in pregnant women which is presented in the spirit of a motivating example, rather than claimed as an accurate representation of reality.
+This is framed in the context of disclosure decisions, taking drinking patterns in pregnant women as a motivating example.
 Alcohol consumption in the ante natal period is a significant issue in itself, and has been associated with many potentially negative consequences.

### 2014-12-18 Abstract.tex
Incorporating Seth & Jakub's comments

@@
 
-We note that the model omits the overwhelming complexity of the real disclosure scenario, and is presented largely in the spirit of a convenient demonstration of the methodology.
+We note that the model omits the overwhelming complexity of the real disclosure scenario where hardly any quantitative data are available, and is presented largely in the spirit of a convenient demonstration of the methodology.
 Clearly a domain where there is sufficient data to permit a more comprehensive approach to validation of model outcomes is desirable, and will form the basis of our future work.

### 2014-12-18 Background.tex
Incorporating Seth & Jakub's comments

@@
 
-The preponderance of classical game theory focuses on strategic decision making, in scenarios where all players have complete information about all aspects of the game.
+The majority of classical game theory focuses on strategic decision making, in scenarios where all players have complete information about all aspects of the game.
 An alternative, perhaps more common situation, is that players have incomplete information, i.e.
-their knowledge of the rules of play is in some way deficient.
+their knowledge of the state of the world is in some way deficient.
 \citet{Harsanyi1967} introduced the concept of a Bayesian game, resolving the problems introduced by the incomplete information scenario by allowing the possible variations on the rules to be treated as subgames.
@@
 Nature is assumed to make their move by lottery, and where the probability distribution governing the lottery is known to all players this permits the game to be formulated as one of complete information.
+
 Here, we are specifically interested in signalling games \citep{Kreps1987,Spence1973}, where one player holds some private information which may be communicated (or not) by means of a signal.
-
 This basic form has been widely applied, with substantial interest in what conditions permit honest signalling as Nash equilibria or \acp{ESS}.
@@
 Similar results have also been demonstrated in a game of job market signalling, where signal cost was differentiated by type \citep{Spence1973}.
-Costly signalling has also been suggested as an explaination of behaviour that at first gasp appears counter intuitive, for example \citet{Godfray1991} applied the idea to the food solicitation behaviour of chicks, where a stronger signal carries a risk of being eaten.
-Moving beyond animal behaviour, \citet{Sosis2003} considered the implications if ritual behaviour, in the context of religion, represented a costly signal, an idea subsequently extended by \citet{Henrich2009} to include cultural transmission, and \citet{Wildman2011} to introduce group differentiation.
+Costly signalling has also been suggested as an explaination of behaviour that at first glance appears counter intuitive, for example \citet{Godfray1991} applied the idea to the food solicitation behaviour of chicks, where a stronger signal carries a risk of being eaten.
+Moving beyond animal behaviour, \citet{Sosis2003} considered the implications of ritual behaviour, in the context of religion, represented a costly signal, an idea subsequently extended by \citet{Henrich2009} to include cultural transmission, and \citet{Wildman2011} to introduce group differentiation.
 
-Other work augments the signalling game model, for example \citet{Austen-Smith2005} adds a second `peer group' audience signalling game to the original \citeauthor{Spence1973} game in an effort to explain poor academic performance in some social groups, with some subseqent empirical support for the idea from \citet{Jr2010}.
-On a similar tack, \citet{Feltovich2002} introduced additional noisy type information, finding that this effectively explained counterintuitive observed behaviour where actors with every right to boast of their quality fail to do so.
+Other work augments the signalling game model, for example \citet{Austen-Smith2005} add a second `peer group' audience signalling game to the original \citeauthor{Spence1973} game in an effort to explain poor academic performance in some social groups, with some subseqent empirical support for the idea from \citet{Jr2010}.
+On a similar tack, \citet{Feltovich2002} introduce additional noisy type information, finding that this effectively explained counterintuitive observed behaviour where actors with every right to boast of their quality fail to do so.
 
@@
 
-Where game theory addresses strategic decision making, decision theory deals instead with rational decision making \citep{Peterson2009}.
+While game theory addresses rational strategic decision making, decision theory deals instead with rational decision making \citep{Peterson2009}.
 Taken literally, this leads to normative decision theory, where the focus is on giving the rational answer to a decision problem.
-An alternative view - descriptive, or behavioural decisin theory, holds that the focus should instead be on giving an account of human decision making, complete with observed deviations from perfect rationality, which we address in section \ref{sub:descriptive_theories}.
-Finally a third perspective, which to some extent overlaps this division, suggests that decisions are heuristic in nature and rational in ecological context (section \ref{sub:heuristic_theories}).
+An alternative view - descriptive, or behavioural decision theory, holds that the focus should instead be on giving an account of human decision making performance, complete with observed deviations from perfect rationality, which we address in section \ref{sub:descriptive_theories}.
+Finally a third perspective, which to some extent overlaps this division, suggests that decisions are heuristic in nature and rational in ecological context \citep{Gigerenzer1996} (section \ref{sub:heuristic_theories}).
 
@@
 This allows probabilities used in reasoning to be subjective, which may allow for a better account of decisions from experience (see \citet{Hau2008,Hertwig2004} for results elucidating the distinction, and comparing the performance of several non-Bayesian models).
-This model has seen notable successes in practical problems \citep{McNamara1980,Survey2003,Kristensen1997}, but suggestions by several authors  that it could constitute an effective (top-down) model of learning \citep{Tenenbaum2006,Griffiths2010}, or induction \citep{Gallistel2012} in the brain have attracted substantil criticism, e.g.
-\citet{Bowers2012} responding to \citeauthor{Tenenbaum2006}, and \citeauthor{Griffiths2010}; and \citet{Miller2012} addressing \citeauthor{Gallistel2012}.
+This model has seen notable successes in practical problems \citep{McNamara1980,Survey2003,Kristensen1997}, but suggestions by several authors  that it could constitute an effective (top-down) model of learning \citep{Tenenbaum2006,Griffiths2010}, or induction \citep{Gallistel2012} in the brain have attracted substantial criticism\footnote{For example \citet{Bowers2012} responding to \citet{Tenenbaum2006}, and \citet{Griffiths2010}; and \citet{Miller2012} addressing \citet{Gallistel2012}.}.
 
@@
 
-As noted, heuristic decision making stems from a contention that \citeauthor{Neumann1953} type rationality ignores the both context of decision making, and a lack of correspondence between predicted and actual human decisions (see, for example the Allais paradox \citep{Society2013}, and subsequent empirical support \citep{Oliver2003,Burke1996}).
-Arguably, this begins with \citet{Simon1956}, who suggested that humans do not attempt to make optimal choices, but to satisfice and choose the first `good enough' option.
+As noted, heuristic decision making stems from a contention that \citeauthor{Neumann1953} type rationality ignores the context of decision making, and a lack of correspondence between predicted and actual human decisions (see, for example the Allais paradox \citep{Society2013}, and subsequent empirical support \citep{Oliver2003,Burke1996}).
+Arguably, this notion begins with \citet{Simon1956}, who suggested that humans do not attempt to make optimal choices, but to satisfice and choose the first `good enough' option.
 While noting that this will often achieve the same result, the claim is that humans exhibit bounded rationality \citep{Simon2000} arising from inherent limits to cognition.
@@
 \citet{Gigerenzer1996} take the concept of bounded rationality further, and argue for what they term \acp{FFH}.
-This recasts rationality as bound to the context of the behaviour: a rational approach to choosing the right mate might well require checking every possible partner, but given finite time, memory, and so on rapidly becomes nonsensical.
+This recasts rationality as bound to the context of the behaviour: a rational approach to choosing the right mate might well require checking every possible partner, but given finite time, memory, and so on rapidly becomes unachievable.
 On this basis, they contend that the rationality of any given decision rule can only be determined in the context of the environment \citep{Todd2003}, which implies that heuristics are task specific.
@@
 
-While heuristic theories arguably fall under the purview of the descriptive, the wider tendency is towards what are in essence patches to normative models.
+While heuristic theories arguably fall under the purview of the descriptive, the wider tendency is towards what are in essence \enquote{patches} to normative models.
 The most influential models in this class derive from \ac{PT} \citep{Kahneman1979}, which combines a set of heuristics based on observed decision behaviour \citep{Tversky1974}, with distortions to the perception of probability, and the value of outcomes \citep{Kahneman1984,Tversky1986}.
-\citet{Tversky1992} subsequently addressed issues present in their original formulation by introducing \ac{CPT}, which allows for non-binary decisions, at the expense of the heuristics.
+\citet{Tversky1992} subsequently addressed issues present in their original formulation by introducing \ac{CPT}, which allows for non-binary decisions, but dispenses with the heuristic aspects of the original formulation.
 The essence then, is that high and low probabilities are treated differently, and the subjective value of a loss differs from the equivalent gain (losing your shirt is perceived as more of a loss than winning a shirt is a gain).
-This last, known as the framing effect is particularly significant, see for example work by \citet{Toll2007} examining the relationship between loss and gain framings and success rates in giving up smoking, and \ac{NICE} guidance on framing of treatment options \citep{NICE2007}.
+This last effect, known as the framing effect is particularly significant, see for example work by \citet{Toll2007} examining the relationship between loss and gain framings and success rates in giving up smoking, and \ac{NICE} guidance on framing of treatment options \citep{NICE2007}.
 
 \ac{CPT} has been successful in explaining a number of anomalous results in decision tasks (see \citet{Camerer2004a} for a review), and \citet{Thaler2000} comments to the effect that the theory is promising, albeit incomplete, lacking for example any explanation of how frames are constructed.
-While an effective account of decision behaviour under risk, the theory does not attempt to resolve apparent inconsistencies that arise when outcomes are delayed, i.e.
+While remaining an effective account of decision behaviour under risk, the theory does not attempt to resolve apparent inconsistencies that arise when outcomes are delayed, i.e.
 in situations of intertemporal choice.

### 2014-12-18 Introduction.tex
Incorporating Seth & Jakub's comments

@@
 The case in favour of \ac{ABM} as a general approach has been made numerously, and elegantly (e.g.
-\citet{Silverman2011,Silverman2013,Resnick,gilbert1999simulation,epstein1994growing,Macy2002a,Axelrod1997}, amongst others).
-As such we will not belabour the point, and instead turn to addressing some of the concerns expressed about the method.
+\citet{epstein1994growing,Resnick,Axelrod1997,gilbert1999simulation,Macy2002a,Silverman2011,Silverman2013,epstein2014agent_zero}, amongst others).
+As such we will not belabour the point, and instead turn to addressing some of the concerns expressed about the approach.
 In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, tending to be a reflection of the assumptions of the modeller rather than empirically or theoretically grounded \citep{Waldherr2013}.
-To ameliorate this concern, we extend previous work by \cite{GrayDissert} drawing on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game \citep{Kreps1987} with a basic form of intragroup information sharing.
+To ameliorate this concern, we draw on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game \citep{Kreps1987} with a basic form of intragroup information sharing.
 Four decision models of varying complexity, and behavioural plausibility are contrasted, by way of demonstrating the significance of the operationalisation of decision making in \ac{ABM}.
 
-This is framed in the context of disclosure decisions, taking drinking patterns in pregnant women as a motivating example.
-Alcohol consumption in the ante natal period is a significant issue in itself, and has been associated with many potentially negative consequences.
+This exercise is framed in the context of disclosure decisions, taking drinking patterns in pregnant women as a motivating example.
+Alcohol consumption in the antenatal period is a significant issue in itself, and has been associated with many potentially negative consequences.
 For example, \citet{Andersen2012} report results from a large scale Danish cohort study suggesting that even low levels of consumption in early pregnancy increase the risk of spontaneous abortion, although \citet{Savitz2012} has suggested this may be attributable to a previously known link to absence of mornining sickness.
@@
 Harm may also extend even further, and a review by \citet{Huizink2006} concluded that maternal alcohol consumption could be a contributing factor to \ac{ADHD}, and other learning impairments, but note methodological issues in a number of the papers.
-There is not, however, a clear consensus, with \citet{Gray2006} finding no evidence of harm below 1.5 UK units per day.
-In terms of official guidance, \ac{NICE} acknowledge that evidence of harm to the fetus is less than conclusive, but advise not drinking at all, or significant moderation \citep{NICE2010a}, with similar advice from the \cite{DepartmentofHealth2008}.
+There is not, however, a clear consensus, with \citet{Gray2006} finding no evidence of harm below 1.5 UK units\footnote{Roughly half a pint of beer, a single 25ml measure of spirits, or one 175ml glass of wine.} per day.
+In terms of official guidance in the UK, \ac{NICE} acknowledge that evidence of harm to the fetus is less than conclusive, but advise not drinking at all, or significant moderation \citep{NICE2010a}, with similar advice from the UK \cite{DepartmentofHealth2008}.
 
-Turning more specifically to disclosure of alcohol use during pregnancy, research is relatively sparce, although qualitative trends are reported by \citet{Phillips2007}, and \citet{Alvik2006}.
+Turning more specifically to disclosure of alcohol use during pregnancy, research is relatively sparse, although qualitative trends are reported by \citet{Phillips2007} and \citet{Alvik2006}.
 The former explored factors impacting disclosure through a small case study, highlighting the need to build up rapport over several appointments; the latter compared post partum reports of consumption with contemporaneous accounts, finding apparent underreporting during pregnancy which was amplified by increased drinking.
@@
 
-This scenario is of substantial independent interest, and shows the potential utility of a simulation approach in arenas where \acp{RCT} are not viable for ethical, or financial reasons.
-With this said, the lack of a strong quantitative evidence base against which to validate the behaviour of the model augers for caution in interpreting the results, and a necessary reminder that in this instance the model is primarily a tool for thinking, rather than a machine for predicting.
+The resulting scenario is of substantial independent interest, and shows the potential utility of a simulation approach in arenas where \acp{RCT} are not viable for ethical, or financial reasons.
+With this said, the lack of a strong quantitative evidence base against which to validate the behaviour of the model augers for caution in interpreting the results, and a necessary reminder that in this instance the model is primarily a tool for formalisation of the thought process \citep{epstein2008}, rather than a machine for predicting.
 
@@
 A game theoretic approach to generating an abstract form of the problem gives a convenient, and well known framework to reason about the processes involved in the scenario.
-While scenarios may well map to a plurality of games, this still allows for a principled comparison between interpretations and enforces explicit assumptions.
+While scenarios may well map to a number of games, exploring one candidate game still allows for a principled comparison between interpretations, and enforces explicit assumptions.
 Relating this to decision theory shifts the emphasis away from analytical equilibrium-seeking, and heightens the importance of behaviour change.
@@
 
-While there is no universal theory of human behaviour to sit at the center of \ac{ABM} as a method,a key motivation for decision rules is their claim to provide an account of decision making that is behaviourally and cognitively plausible.
+While there is no universal theory of human behaviour to sit at the center of \ac{ABM} as a method, a key motivation for decision rules is their claim to provide an account of decision making that is behaviourally and cognitively plausible.
 Their mooted capability in this regard is to some extent supported by work from neuroeconomics, which aims to empirically test theories of decision making \citep{Rustichini2009}.

### 2014-12-18 Model.tex
Incorporating Seth & Jakub's comments

@@
 
-In this section we outline the disclosure game model, and give details of the four decision rules, but begin with a brief sketch of a pregnancy in terms of encounters between a woman and a midwife.
+In this section we outline the disclosure game model, and give details of the four decision rules that will be examined in this paper, but begin with a brief sketch of a pregnancy in terms of encounters between a pregnant woman and a midwife.
 
-Typically women will have 12 appointments with a midwife during the antenatal period.
-Outside of caseloading teams, a woman does not generally have a named midwife, and may see a different practitioner at each appointment.
-In the UK, and unlike most healthcare scenarios, maternity notes are patient held, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously.
+Typically in the UK, a women will have 12 appointments with a midwife during the antenatal period.
+Outside of caseloading\footnote{Under a caseloading system, women are allocated an individual, or small group of midwives who deal with their care throughout pregnancy, and birth.} teams, a woman does not generally have a named midwife, and may see a different practitioner at each appointment.
+In the UK, and unlike most healthcare scenarios, maternity notes are held by the patient, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously.
 Maternity notes are not generally linked to extra-departmental records, meaning that a history of alcohol related admissions to another service may remain unknown unless revealed by the woman.
 
-According to NICE guidance \citep{NICE2010a,NICE2010} substance misuse should be raised at the initial booking appointment, and subsequent action if a concern is raised is at the discretion of the midwife.
+According to NICE guidance \citep{NICE2010a,NICE2010} the issue of substance misuse should be raised at the initial booking appointment, follwed by subsequent action if a concern is raised is at the discretion of the midwife.
 This may take the form of specific guidance to reduce intake, or if deemed necessary a referral to a specialist midwife and relevant interdisciplinary team.
-On alcohol consumption, policy regarding how to determine the level of consumption is generally at the trust level, or according to the best judgement of the individual midwife, with no guidance provided by NICE.
-This commonly takes the form of average units per week, but may include \ac{T-ACE} and similar measures.
+On alcohol consumption, policy regarding how to determine the level of consumption is generally at the level of local health authority, hospital trust, or according to the best judgement of the individual midwife, with no guidance provided by NICE.
+This commonly takes the form of average units per week, but may include \ac{T-ACE}\footnote{The \ac{T-ACE} is a four question screening test intended specifically for use with pregnant women.} \citep{Sokol1989863} and similar measures.
 
-Beyond the booking appointment, the onus is on women to raise concerns about their drinking behaviour, or the midwife to probe further if they feel it is warranted.
+Beyond the \enquote{booking} appointment, the onus is on women to raise concerns about their drinking behaviour, or the midwife to probe further if they feel it is warranted.
 In either case, once a concern has been raised the midwife must respond clinically, and inevitably personally, to the information.
@@
 We also make the simplifying assumption that a woman may have one of only three drinking patterns - light, moderate, or heavy.
-Correspondingly, they are limited in what signals they may send to claiming to be one of these three types.
+Correspondingly, they are limited in what signals they may send when claiming to be one of these three types.
 
 Midwives are treated in a similar fashion, where their type corresponds to how negatively they regard a drinking pattern - non-judgemental, moderately judgemental, and harshly judgemental.
-The expression of this judgement is not a matter of choice on their part, and is assumed to have no impact on their response, which is to either refer the woman for specialist treatment, or do nothing.
+The expression of this judgement is not a matter of choice on their part, and is assumed to have no impact on their clinical response, which is to either refer the woman for specialist treatment, or do nothing.
 

### 2014-12-18 Conclusion.tex
More comments

@@
 %!TEX root = disclosure_game.tex
-\section{Discussion and Conclusions}
-\label{sec:conclusion}
+\section{Discussion}
+\label{sec:discussion}
 %reiterate contribution
@@
 One of the notable features of the results is the similarity in behaviour of the two classes of decision rule.
-To some extent this reflects poorly on the most complex rule, \ac{CPT}, which diverges only relatively minorly in behaviour from the Bayesian model.
+To some extent this reflects poorly on the most complex rule, \ac{CPT}, which diverges only minimally in behaviour from the Bayesian model.
 To some extent this might be anticipated, in that the payoffs are clearly unrealistic, which limits the utility of the \ac{CPT} approach.
 Additionally, work by \citet{Glockner2012} has shown that there is considerable variation in individual parameters for the decision model, whereas we have let them remain homogenous here.
-In the vein, utility functions should arguably vary between individual agents, which could potentially be addressed by replacing the fixed payoffs used here with a distribution.
+In the same vein, utility functions should arguably vary between individual agents, which could potentially be addressed by replacing the fixed payoffs used here with a distribution.
 With this said, the significant increase in complexity, which entails both additional parameters and increases to simulation time may auger for a middle ground, particularly where elicitation of payoffs is impractical.
@@
 
+\section{Conclusion}
+\label{sec:conclusion}
+
 The conclusions that can be drawn about the behaviours of real life women, and their midwives, are necessarily limited by the paucity of data available to validate the model.
-While qualitative trends offer a some indication, they are clearly very limited in scope, and do not permit strong claims about the drivers of disclosure, and auger for a sceptical eye as to any recommendations targetted at improving outcomes.
+While qualitative trends offer some indication, they are clearly very limited in scope, and do not permit strong claims about the drivers of disclosure.
 As such, further work will focus on applying the model to domains where validation data is more available, which will support a more comprehensive evaluation of the model discrepancy.
-With this said, the trends reported by \citet{Alvik2006}, and \citet{Phillips2007} are bourne out by the model, and predictions from the two more complex rules suggest that encouraging information sharing between women may encourage disclosure, but at the expense of reducing accuracy.
+With this said, the trends reported by \citet{Alvik2006}, and \citet{Phillips2007} are borne out by the model, and predictions from the two more complex rules suggest that encouraging information sharing between women may encourage disclosure, but at the expense of reducing accuracy.
 By contrast, if one takes the view that a Lexicographic model is a better approximation of real behaviour, then outcomes can best be influenced by controlling how far midwives punish their women socially.
@@
 
-More broadly, the results demonstrate the logistical feasibility, and utility as a `tool for thinking', of an agent model grounded in decision theory.
+More broadly, the results demonstrate the logistical feasibility, and its utility as a `tool for thinking', of an agent model grounded in decision theory.
 The results also make clear that deciding the operationalisation of the decision making is of key significance.

### 2014-12-18 Introduction.tex
More comments

@@
 
-The remainder of this paper proceeds to provide a brief review of the methodological context (\ref{sec:lit_review}), before outlining the model (\ref{sec:model}), and experiments (\ref{sec:method}), with selected results (\ref{sec:results}), then closing with a discussion contrasting the decision models (\ref{sec:conclusion}).
+The remainder of this paper proceeds to provide a brief review of the methodological context (section \ref{sec:lit_review}), before outlining the model (section \ref{sec:model}), and experiments (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}).

### 2014-12-18 Methods.tex
More comments

@@
 While there has been significant work on determining appropriate parameterisation for the model (e.g.
-\cite{Neilson2002,Glockner2012,Nilsson2011}, and particularly \citet{Byrnes1999,Booij2009} addressing risk aversion and gender), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work.
+\cite{Neilson2002,Glockner2012,Nilsson2011}, and particularly \citet{Byrnes1999} and \citet{Booij2009} addressing risk aversion and gender), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work.
 For simplicity, it was assumed that all three drinking types are equally prevalent within the population, although results derived from \ac{ALSPAC} suggest that the reality is far more positive \citep{Humphriss2013}.
@@
 \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 10:1 \\ \hline
+\(\gamma\) & Probability weighting for gains  & 0.61 \\ \hline
+\(\delta\) & Probability weighting for losses &  0.69\\ \hline
+\(\alpha\) & Power for gains  & 0.88 \\ \hline
+\(\beta\) & Power for losses & 0.88 \\ \hline
+\(\lambda\) & Loss aversion &  2.25 \\ \hline
 \end{tabular}
@@
 
-\subsection{Information Sharing}
-
 In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examined the impact of simple information sharing within the population of women (section \ref{sub:info_sharing}) on the robustness of these trends.
-The original experiment was repeated at \(q_{w}=w_{w}={0.25, 0.5, 0.75, 1}\), with 100 runs under each condition.
+The original experiment was repeated at \(q_{w},w_{w}\in \{0.25, 0.5, 0.75, 1\}\), with 100 runs under each condition.
 
@@
 For this purpose the \ac{GEM-SA} software \citep{Kennedy} was used, which implements the \ac{BACCO} method developed by \citeauthor{Oakley2004} \citep{Oakley2002,Oakley2004,Dorresteijn2010}.
-This is a form of variance based sensitivity analysis, which assumes that the model output is an unknown, smooth function of the inputs.
+This is a form of variance-based sensitivity analysis, which assumes that the model output is an unknown, smooth function of the inputs.
 The unknown function can then be approximated as a Gaussian Process, which is fitted to the training data using Bayes' Theorem.
-The emulator is then able to provide an indication about the extent to which uncertainty in a parameter propogates to uncertainty in the output, and how sharply the output responds to change in each input.
+The emulator is then able to provide an indication about the extent to which uncertainty in a parameter propogates to uncertainty in the output, and how sharply the output responds to change in each parameter.
 
@@
 
-Parameters for training were generated in R \citep{RTeam2014} using Latin Hypercube Sampling \citep{Carnell2012} over the space of inputs given in table \ref{tab:sa_params}, giving 10 free parameters which were treated as uniformly distrubuted in the range given.
+Parameters for training were generated in R \citep{RTeam2014} using Latin Hypercube Sampling \citep{Carnell2012} over the space of parameters given in table \ref{tab:sa_params}, giving then free parameters which were treated as uniformly distributed in the range given.
 Initially a unit hypercube was generated, then the margins transformed appropriately to cover those regions where the inputs are not bounded between 0 and 1, and for proportions of agent types which necessarily sum to one across the three parameters.
@@
 
-To capture the response characteristics for the model, we measured four outcome variables - (1) the interquartile range of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3, 4) the interquartile range of the average signal, and interquartile range between simulation runs.
+To capture the response characteristics for the model, we measured four outcome variables - (1) the interquartile range of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3, 4) the interquartile range of the average signal, and \ac{IQR} between simulation runs.
 Together these four metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the variability in the system in response to changes to the parameters (3 \& 4).
@@
 
-In addition to the sensitivity analysis, we also employed the resulting emulators to rapidly\footnote{Once constructed, the emulator is sufficiently quick that results requiring several days of runtime on an HPC can be generated in minutes on a desktop computer.} explore the parameter space.
-While emulated results are subject to innaccuracy, they do provide an indication of the interest, and plausibility, of regions of the parameter space.
+In addition to the sensitivity analysis, we also employed the resulting emulators to rapidly\footnote{Once constructed, the emulator has an analytical solution conditional on the roughness parameters, which obviates the need to use MCMC.} explore the parameter space.
+While emulated results are subject to inaccuracy, they do provide an indication of the interest, and plausibility, of regions of the parameter space.
 Results for the outcomes of the interactions of \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) with \(x_{h}\), and \(q_{w}\) with \(w_{w}\) are given in section \ref{sub:sa_results}.

### 2014-12-18 Model.tex
More comments

@@
 %Might belong in a more methody bit? Read some stuff to check..
-Women are drawn in order from a queue, and play against a midwife chosen at random.
-They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred.
-At which point a new player is drawn from the same distribution that produced the original players to replace them.
+Women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)).
+They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred, and a new player is drawn from the same distribution that produced the original players to replace them.
 If they are not referred, they rejoin the back of the queue after their appointment.
-In either case, they are informed of their payoff after each round and update their beliefs accordingly.
+In either case, they are informed of their payoff after each round and update their beliefs accordingly using the rules described in section \ref{sub:the_agents}.
 
@@
 \center
-\subfloat[Social cost, \(X_{s}\)\label{tab:Social-cost-matrix}]{%
+\subfloat[Social cost, \(X_{s}\), for women\label{tab:Social-cost-matrix}]{%
 \begin{tabular}{|c|c|c|c|c|}
@@
 \cline{2-5} 
- & Harsh & 0, -2 & 0, -1 & 0, 0\tabularnewline
+ & Harsh & -2 & -1 & 0\tabularnewline
 \cline{2-5} 
- & Medium & 0, -1 & 0, 0 & 0, 0\tabularnewline
+ & Medium & -1 & 0 & 0\tabularnewline
 \cline{2-5} 
- & Low & 0, 0 & 0, 0 & 0, 0\tabularnewline
+ & Low & 0 & 0 & 0\tabularnewline
 \hline 
@@
 
-\subfloat[Health outcome, \(X_{h}\)\label{tab:Referral-payoff-matrix}]{%
+\subfloat[Health outcome, \(X_{h}\), for women and midwives\label{tab:Referral-payoff-matrix}]{%
 \begin{tabular}{|c|c|c|c|c|}
@@
 
-\subfloat[Referral cost, \(X_{c}\)\label{tab:inst_cost_matrix}]{%
+\subfloat[Referral cost, \(X_{c}\), for midwife\label{tab:inst_cost_matrix}]{%
 \begin{tabular}{|c|c|c|c|c|}
@@
 \cline{2-5} 
- & Refer & -9, 0 & -9, 0 & -9, 0\tabularnewline
+ & Refer & -9 & -9 & -9 \tabularnewline
 \cline{2-5} 
- & Don't refer & 0, 0 & 0, 0 & 0, 0\tabularnewline
+ & Don't refer & 0 & 0 & 0\tabularnewline
 \hline 
@@
 While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same outputs, we limit ourselves here to four.
-The simplest is a lexicographic rule (1), motivated as in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; a Bayesian risk minimisation rule using the same information (2); a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical with 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}.
+The simplest is a lexicographic rule (1), in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}.
 Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-ouput characteristics.
 
-As noted in section \ref{sub:the_game}, agents have perfect recall, and midwives recognise women if they encounter them subsequently.
-While agents recall perfectly and make use of the new information for retrospective updates, all four agent models make decisions `as-if' they were always facing a new opponent.
+As noted in section \ref{sub:the_game}, agents have perfect recall, and midwives recognise women if they repeatedly encounter them.
+While agents recall perfectly and make use of the new information for retrospective updates, all four agent models make decisions `as-if' they were always facing a new \enquote{opponent}.
 
 A simplifying assumption is made that all midwives have just qualified after receiving identical training.
-As a result, they have homogenous beliefs about their women and assume to some extent that they are honest.
+As a result, they have homogenous beliefs about  women and assume to some extent that they are honest.
 Women are heterogenous in their prior observations, which are assigned stochastically and constrained such that they have encountered each scenario possible at least once, with exactly \(k\) encounters overall.
@@
 
-The lexicographic heuristic (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified, where an action is a choice between combined lotteries.
+The lexicographic heuristic (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified problem representation, where an action is a choice between combined lotteries.
 Functionally, the heuristic maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e.
 one reason decision making.
+Where there is no clear best action, but one or more is clearly worse, a choice must be made as to whether to discard the poorer action; in this case we have elected to retain it.
 This approach requires minimal computation, and does not assume that \(u_{i}\) is static, or known.
@@
 This is resolved by maintaining a separate count for each signal (i.e.
-\(n_{s_{w},s_{m}}\)), and otherwise following the same algorithm.
+\(n_{s_{w},s_{m}}\)), and otherwise following the same algorithm, presented below.
 
@@
 
-The Bayesian payoff agent uses the same subset of information as the lexicographic method, but updates beliefs on the link between actions and payoffs using Bayes rule, and attempts to choose the action which minimises risk.
+The Bayesian payoff agent uses the same subset of information as the lexicographic method, but updates beliefs on the link between actions and payoffs using the Bayes rule, and attempts to choose the action which minimises risk.
 
 Given the discrete nature of actions and payoffs, coupled with a desire for tractability of the
-simulation, the Dirichlet distribution is employed to represent these beliefs. The probability
+simulation, the Dirichlet distribution is employed as a prior to represent these beliefs. The probability
 density function takes the form -
@@
 
-Where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\) is the number
+where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\) is the number
 of signal-payoff pairs, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
@@
 
-Agents then choose $s_{i}$ to minimise $R_{i}$, which is simply - 
+Agents then choose the strategy $s_{i}$ to minimise risk $R_{i}$, which is simply defined as - 
 \begin{equation}
@@
 
-Where $X$ is the set of payoffs the agent has observed to follow $s$.
+where $X$ is the set of payoffs the agent has observed to follow $s$.
 
@@
 Women maintain two sets of beliefs, corresponding respectively to \(p_{m}\), and the probability of referral given signal choice.
-This leads to the risk function -
+This leads to the risk function, minimised with respect to \(s_{w}\) -
 
@@
 
-So that the risk of a signal is the sum of the products of all payoffs with the probabilities of their entailed midwife types and responses.
+so that the risk of a signal is the sum of the products of all payoffs with the probabilities of their entailed midwife types and responses.
 
 Midwives reasoning centers on determining the meaning of signals, since given the knowledge of what some signal \(i\) conveys about the true type of the sender, the payoff for an action is known.
-As such, their inference process is the same as for the simple Bayesian agent but over signal-type pairs, and they attempt to minimise -
+As such, their inference process is the same as for the simple Bayesian agent but over signal-type pairs, and they attempt to minimise the following risk function, minimised with respect to \(s_{m}\) -
 
@@
 
-\begin{eqnarray*}
+\begin{eqnarray}
 w^{+}(p) & = & \frac{p^{\gamma}}{(p^{\gamma}+(1-p)^{\gamma})^{\frac{1}{\gamma}}}\\
 w^{-}(p) & = & \frac{p^{\delta}}{(p^{\delta}+(1-p)^{\delta})^{\frac{1}{\delta}}}
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 
-\[
-v(x)=\begin{cases}
-f(x) & if\, x>0\\
-0 & if\, x=0\\
-g(x) & if\, x<0
+\begin{equation}
+v(u_{i})=\begin{cases}
+f(u_{i}) & \text{if}\, u_{i}>0\\
+0 & \text{if}\, u_{i}=0\\
+\lambda g(u_{i}) & \text{if}\, x<0
 \end{cases}
-\]
+\end{equation}
 
-Where,
+where,
 
-\[
-f(x)=\begin{cases}
-x^{\alpha} & if\,\alpha>0\\
-ln(x) & if\,\alpha=0\\
-1-(1+x)^{\alpha} & if\,\alpha<0
+\begin{equation}
+f(u_{i})=\begin{cases}
+u_{i}^{\alpha} & \text{if}\,\alpha>0\\
+\ln(u_{i}) & \text{if}\,\alpha=0\\
+1-(1+u_{i})^{\alpha} & \text{if}\,\alpha<0
 \end{cases}
-\]
-\[
-g(x)=\begin{cases}
--(-x)^{\beta} & if\,\beta>0\\
--ln(-x) & if\,\beta=0\\
-(1-x)^{\beta}-1 & if\,\beta<0
+\end{equation}
+\begin{equation}
+g(u_{i})=\begin{cases}
+-(-u_{i})^{\beta} & \text{if}\,\beta>0\\
+-\ln(-u_{i}) & \text{if}\,\beta=0\\
+(1-u_{i})^{\beta}-1 & \text{if}\,\beta<0
 \end{cases}
-\]
+\end{equation}
 
-And $\alpha$, and $\beta$ are respectively the power of a gain,
-and a loss, and \(x=u_{i}\). The \ac{CPT} value of outcome $x$ is $v(x)w^{+}(x)$
-if $x\geq0$, and $v(x)w^{-}(x)$ otherwise. For an action the \ac{CPT}
+and $\alpha$, and $\beta$ are respectively the power of a gain,
+and a loss, and \(\lambda\) is a multiplier giving the aversion to loss. The \ac{CPT} value of outcome $u_{i}$, occurring with probability \(p\) is $v(u_{i})w^{+}(p)$
+if $u_{i}\geq0$, and $v(u_{i})w^{-}(p)$ otherwise. For any given action the \ac{CPT}
 value is the sum of the value of the prospects of that action, as
@@
 By the same rationale, midwives share only their history with the most recent woman they referred.
-Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{Memories of games remain, but it is assumed that only current news is relevant.}
+Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{More precisely, memories of games remain, but it is assumed that only the most current information is relevant enough to be shared.}
 
@@
 
-By contrast, representing the problem in terms of the probabilities of the individual lotteries yields a structure that abstracts the new information from payoffs, and allows the agent discount implausible outcomes.
+By contrast, representing the problem in terms of the probabilities of the individual lotteries yields a structure that abstracts the new information from payoffs, and allows the agent to discard implausible outcomes.
 This stronger assumption as to the static and known qualities of payoffs does however reduce the flexibility of the decision rule.

### 2014-12-18 Results.tex
More comments

@@
 This levelling can in part be explained by the referral results (figure \ref{fig:referrals}), which show that the majority of drinkers are referred, even with substantial concealment.
-Referrals continue to occur, in the absence of honest signals, because drinkers are able to achieve a referral by pooling with higher or lower types, dependent on how their initial beliefs are biased.
+Referrals continue to occur, in the absence of honest signals, because drinkers are able to achieve a referral by masquerading as higher or lower types, dependent on how their initial beliefs are biased.
 Despite this the results suggest that a minority of risky drinkers will evade detection altogether, with no notable distinction between heavy and moderate types.
@@
 Aside from the lexicographic decision rule, the general tendency is towards less honest signalling by heavy drinkers, but figure \ref{fig:ref_sharing} shows a slight increase in referrals for the Bayesian, and \ac{CPT} rules.
-For these decision models, this is because information sharing exacerbates the existing tendency to pool with moderate drinkers, who behave more honestly as heavy drinkers become less so.
+For these decision models, this is because information sharing exacerbates the existing tendency of heavy drinkers to impersonate moderate drinkers, who behave more honestly as heavy drinkers become less so.
 
-Particularly notable, is the decline in honest signalling by light drinkers visible in both heuristic type rules at the .25 level, and the associated increase in false positives.
+Particularly notable, is the decline in honest signalling by light drinkers visible in both heuristic type rules at the 0.25 level of \(q_{w}\) \& \(w_{w}\), and the associated increase in false positives.
 This arises because of the lack of homophilly in information sharing, as light drinkers become informed about negative outcomes associated with concealment, despite having nothing to conceal.
@@
 The relationship is not, however, entirely straighforward, in that increasing information sharing leads to greater variance between runs.
-A linear model was was used to predict the between runs interquartile range of the average signal sent by moderate drinkers, with decision rule, and level of information sharing, together with the interaction between the two as predictors.
+A linear model was used to predict the between runs interquartile range of the average signal sent by moderate drinkers, with decision rule, and level of information sharing, together with the interaction between the two as predictors.
 The regression results were significant (\(F_{7,12}=25,p<2.9\times10^{-6}\)) with \(R^2=94\%\), and intercept 0.07.
 The only significant coefficients were for the interaction terms, which were 0.44 (\(p<0.05\)) for the Bayesian payoff rule, and 0.69 (\(p<0.005\)) for the lexicographic.
-This suggests that information sharing, for the heuristic style decision rules introduces considerable uncertainty to the model, which is explored further in the sensitivity analysis.
+This suggests that information sharing, for the heuristic style decision rules introduces considerable uncertainty to the model, which is explored further in the sensitivity analysis below.
 
@@
 
-For the median signal choice of moderate drinkers, the emulator results suggest that the proportion of light drinkers has a significant effect for all decision rules, accounting for 10\%, 38\%, 24\%, and 5\% of the variance in output for the Lexicographic, Bayesian Payoff, Bayesian, and \ac{CPT} rules respectively.
-For the Lexicographic rule, the overwhelming majority of variance in signalling behaviour is attributable to the proportions of midwives (44\% \(p_{m}(m)\), 7\% \(p_{l}(m)\), and a further 15\% for their interaction).
+For the median signal choice of moderate drinkers, the results of the sensitivity analysis suggest that the proportion of light drinkers has a significant effect for all decision rules, accounting for 10\%, 38\%, 24\%, and 5\% of the variance in output for the Lexicographic, Bayesian Payoff, Bayesian, and \ac{CPT} rules respectively.
+For the Lexicographic rule, the overwhelming majority of variance in signalling behaviour is reflective of the prevalence of stigmatisation by midwives (44\% \(p_{m}(m)\), 7\% \(p_{l}(m)\), and a further 15\% for their interaction).
 The proportions of midwives are also key drivers in group separation, and the between run IQR of both measures for this rule.

### 2014-12-19 Abstract.tex
Tweaking figures

@@
 We also demonstrate the utility of an approach which it is hoped goes some way towards addressing concerns about the ad hoc character of \ac{ABM}, by providing a strong theoretical grounding for the reasoning processes of individual agents.
-To this end we hope to show that these simple rules, operating in an inescapably artificial scenario are nonetheless capable of reproducing trends from the literature.
+To this end we hope to show that these simple rules, operating in an inescapably artificial scenario are nonetheless capable of reproducing trends reported in the literature.
 
@@
 We employ game theory to define a signalling game representative of a scenario where pregnant women decide the extent to which they disclose their drinking behaviours to their midwives, and midwives employ the information provided to decide whether to refer their patients for costly specialist treatment.
-This game is then recast as two games played against nature, to permit the use of a decision theoretic approach where both classes of agent use simple rules to decide their moves.
+This game is then recast as two games played against \enquote{nature}, to permit the use of a decision theoretic approach where both classes of agent use simple rules to decide their moves.
 Four decision rules are explored - a lexicographic heuristic which considers only the link between moves and payoffs, a Bayesian risk minimisation agent that uses the same information, a more complex Bayesian risk minimiser with full access to the structure of the decision problem, and a \ac{CPT} rule.
@@
 
-Selected results showing the ability of all decision rules to reproduce qualitative trends noted in the literature are provided, together with a sensitivity analysis, and comparative heat maps produced using \acp{GEM} demonstrating the significance of the precise implementation of the decision making.
+Selected results showing the ability of all decision rules to reproduce qualitative trends noted in the literature are provided, together with a sensitivity analysis, and comparative heat maps produced using \acp{GEM} demonstrating the significance of the precise implementation of the decision making framework.
 

### 2014-12-31 Background.tex
PDF figures

@@
 
-This section presents a brief overview of previous research, addressing in turn signalling games, normative decision theory, heuristic decision making, and descriptive decision theory.
+This section presents a brief overview of previous work relating to the theoretical backdrop to this approach, addressing in turn signalling games, normative decision theory, heuristic decision making, and descriptive decision theory.
 

### 2014-12-31 Methods.tex
PDF figures

@@
 
-Parameters for training were generated in R \citep{RTeam2014} using Latin Hypercube Sampling \citep{Carnell2012} over the space of parameters given in table \ref{tab:sa_params}, giving then free parameters which were treated as uniformly distributed in the range given.
+Parameters for training were generated in R \citep{RTeam2014} using Latin Hypercube Sampling \citep{Carnell2012} over the space of parameters given in table \ref{tab:sa_params}, giving eleven free parameters which were treated as uniformly distributed in the range given.
 Initially a unit hypercube was generated, then the margins transformed appropriately to cover those regions where the inputs are not bounded between 0 and 1, and for proportions of agent types which necessarily sum to one across the three parameters.

### 2014-12-31 Model.tex
PDF figures

@@
 \begin{adjustbox}{center}
-\includegraphics[width=0.43\paperwidth]{figures/rounded_clover_infosets}
+\includegraphics[width=\textwidth]{figures/rounded_clover_infosets}
 \end{adjustbox}
-\caption{Simplified game tree.}
+\caption{Simplified game tree.
+Green, blue, and orange arrows correspond to moves by nature, women, and midwives, respectively.
+Green terminal nodes indicate that the game may repeat from that point, and black nodes are exits.}
 
@@
 \end{adjustbox}
-\caption{Detail view of a single game tree branch.}
+\caption{Detail view of a single game tree branch, showing the possible moves by each player, with information sets for midwives.}
 
@@
 %Might belong in a more methody bit? Read some stuff to check..
-Women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)).
+To formally define the game, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\).
+Additionally define two utility functions \(u_{w}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}}\), \(u_{m}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}}\), with $X_{c}$, $X_{h}$, and $X_{s}$ being the payoff matrices as in table \ref{tab:Payoff-matrix}; and distributions over types \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\).
+
+As noted, rather than solve the game, we allow populations of agents to play it, and hence stipulate further that women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)).
 They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred, and a new player is drawn from the same distribution that produced the original players to replace them.
@@
 Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.
-
-Formally then, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\).
-Additionally define a utility function \(u_{i}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}}\), and distributions over types \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\).
 
@@
 As a result, they have homogenous beliefs about  women and assume to some extent that they are honest.
-Women are heterogenous in their prior observations, which are assigned stochastically and constrained such that they have encountered each scenario possible at least once, with exactly \(k\) encounters overall.
+Women are heterogenous in their prior observations, which are assigned stochastically and constrained such that they have encountered each scenario possible for their type at least once, with exactly \(k\) encounters overall.
 
@@
 
-Women resolve this by approximating the utility function, as a function \(f(s_{w}, \sigma)\) on their choice of signal and an unknown distribution, which maps to \(u_{w}\) - i.e.
+Women resolve this by approximating the utility function, as a function \(f(s_{w}, \sigma)\) on their choice of signal and an unknown distribution $\sigma$, which maps to \(u_{w}\) - i.e.
 \(s_{w}\) is a choice between simple lotteries.
@@
 Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this exogenous information differently.
-The simple payoff based rule relys on a belief structure relating actions directly to rewards.
+The simple payoff based rule relys on a belief structure relating actions directly to rewards which is essentially model free.
 Because payoffs differ by the agent's private type, the information shared may not correspond to the experience of the listening agent in the same scenario.
@@
 
-By contrast, representing the problem in terms of the probabilities of the individual lotteries yields a structure that abstracts the new information from payoffs, and allows the agent to discard implausible outcomes.
+By contrast, representing the problem in terms of the probabilities of the individual lotteries imposes a model that abstracts the new information from payoffs, and allows the agent to discard implausible outcomes.
 This stronger assumption as to the static and known qualities of payoffs does however reduce the flexibility of the decision rule.

### 2014-12-31 Results.tex
PDF figures

@@
 \begin{figure}[H]
-\begin{adjustbox}{center}\subfloat[Honest signalling\label{fig:honest_sharing}]{\includegraphics[width=0.43\paperwidth]{figures/honesty_sharing}
+\begin{adjustbox}{center}
+\includegraphics[width=0.8\textwidth]{figures/honesty_sharing}
+\end{adjustbox}
+\caption{Impact of information sharing on trends in honest signalling after 1000 rounds, mean with 95\% confidence interval over 100 runs.}
+\label{fig:honest_sharing}
+\end{figure}
 
-}\subfloat[Referrals\label{fig:ref_sharing}]{\includegraphics[width=0.43\paperwidth]{figures/ref_sharing}}\end{adjustbox}
-\caption{Impact of information sharing on qualitative trends after 1000 rounds, mean with 95\% confidence interval over 100 runs.}
-\label{fig:sharing_trends}
+\begin{figure}[H]
+\begin{adjustbox}{center}
+\includegraphics[width=0.8\textwidth]{figures/ref_sharing}
+\end{adjustbox}
+\caption{Impact of information sharing on referral trends after 1000 rounds, mean with 95\% confidence interval over 100 runs.}
+\label{fig:ref_sharing}
 \end{figure}
@@
 \begin{figure}[H]
-\begin{adjustbox}{center}\includegraphics[width=0.8\linewidth]{figures/sharing_emulated_simulated}\end{adjustbox}
+\begin{adjustbox}{center}\includegraphics[width=0.8\textwidth]{figures/sharing_emulated_simulated}\end{adjustbox}
 \caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules.}
@@
 \begin{figure}[H]
-\begin{adjustbox}{center}\includegraphics[width=0.8\linewidth]{figures/unfixed_emu_sig_iqr}\end{adjustbox}
+\begin{adjustbox}{center}\includegraphics[width=0.8\textwidth]{figures/unfixed_emu_sig_iqr}\end{adjustbox}
 \caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\).}
@@
 The response surface of the Bayesian payoff rule is slightly more nuanced than the simple Lexicographic rule.
-Figure \ref{fig:emulated_payoff_group_iqr} shows better separation close to partial pooling at high payoff distinction, with relatively modest honesty bias, which is reflected by the variance contributions of 11\% and 8\% respectively.
-For the more complex rules, the general tendency is towards less pooling for higher values of both, but with pockets where full pooling occurs.
+Figure \ref{fig:emulated_payoff_group_iqr} shows better separation, close to partial pooling\footnote{Pooling occurs when signallers of different types `pool' their signals, and one adopts the signals of another.} at high payoff distinction, with relatively modest honesty bias, which is reflected by the variance contributions of 11\% and 8\% respectively.
+For the more complex rules, the general tendency is towards less pooling for higher values of both, but with pockets where full pooling\footnote{Indicating that all signallers types are using a single signal.} occurs.
 The plots also suggest that the sensitivity of the \ac{CPT} rule is marginally greater, which is supported by the significant contribution to variance of close to 15\% for all measures of \(x_{h}\).

### 2014-12-31 Model.tex
Springer styles

@@
 \begin{adjustbox}{center}
-\includegraphics[width=\textwidth]{figures/rounded_clover_infosets}
+\includegraphics[width=119mm]{figures/rounded_clover_infosets}
 \end{adjustbox}
 \caption{Simplified game tree.
-Green, blue, and orange arrows correspond to moves by nature, women, and midwives, respectively.
-Green terminal nodes indicate that the game may repeat from that point, and black nodes are exits.}
+Arrows correspond to two moves by nature, followed by women, and midwives respectively.
+Light terminal nodes indicate that the game may repeat from that point, and black nodes are exits.}
 
@@
 \begin{adjustbox}{center}
-\includegraphics[width=0.43\paperwidth]{figures/tree_zoom}
+\includegraphics[width=119mm]{figures/tree_zoom}
 \end{adjustbox}
@@
 \begin{figure}[H]
-\begin{adjustbox}{center}\subfloat[Women]{\includegraphics[width=0.43\paperwidth]{figures/women_influence}
-
-}\subfloat[Midwives]{\includegraphics[width=0.43\paperwidth]{figures/mw_influence}}\end{adjustbox}
+\begin{adjustbox}{center}\subfloat[Women]{\includegraphics[width=119mm]{figures/women_influence}}\end{adjustbox}
+\vskip
+\begin{adjustbox}{center}\subfloat[Midwives]{\includegraphics[width=119mm]{figures/mw_influence}}\end{adjustbox}
 \caption{Influence diagrams, showing the game broken into two decision problems.}

### 2014-12-31 disclosure_game.tex
Tables, switched to input rather than include
Because nesting
Bit more on results
Ammendments
Incorporating Seth & Jakub's comments
More comments
PDF figures
Springer styles

@@
-\documentclass{article}
+% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass[graybox]{svmult}
+
+% choose options for [] as required from the list
+% in the Reference Guide
+
+\usepackage{mathptmx}       % selects Times Roman as basic font
+\usepackage{helvet}         % selects Helvetica as sans-serif font
+\usepackage{courier}        % selects Courier as typewriter font
+\usepackage{type1cm}        % activate if the above 3 fonts are
+                            % not available on your system
+%
+\usepackage{makeidx}         % allows index generation
+\usepackage{graphicx}        % standard LaTeX graphics tool
+                             % when including figure files
+\usepackage{multicol}        % used for the two-column index
+\usepackage[bottom]{footmisc}% places footnotes at page bottom
+
+% see the list of further useful packages
+% in the Reference Guide
+
+\makeindex             % used for the subject index
+                       % please use the style svind.ist with
+                       % your makeindex program
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \usepackage{tikz}
@@
 \usepackage{ifthen}
+\usepackage{csquotes}
 \newboolean{enable-backrefs} % enable backrefs in the bibliography
@@
 
-\title{Deciding to Disclose: Pregnancy and Alcohol Misuse}
+\title*{Deciding to Disclose: A Decision Theoretic Agent Model of Pregnancy and Alcohol Misuse}
 \author{Jonathan Gray \and Jakub Bijak \and Seth Bullock\\
@@
 %\refstepcounter{dummy}
-\pdfbookmark[1]{Acronyms}{acronyms}
+%\pdfbookmark[1]{Acronyms}{acronyms}
 %\markboth{\spacedlowsmallcaps{Acronyms}}{\spacedlowsmallcaps{Acronyms}}
@@
   \acro{ESS}{Evolutionarily Stable Strategy}
+  \acrodefplural{ESS}[ESS]{Evolutionarily Stable Strategies}
   \acro{MCMC}{Markov chain monte carlo methods}
@@
   \acro{BACCO}{Bayesian Analysis of Computer Code Outputs}
+  \acro{IQR}{interquartile range}
 \end{acronym}
@@
 %\refstepcounter{dummy}
-\pdfbookmark[1]{Glossary}{glossary}
-\printglossary[type=main]
+%\pdfbookmark[1]{Glossary}{glossary}
+%\printglossary[type=main]
 
-\printnomenclature{}
+%\printnomenclature{}
 
@@
 
-\include{Abstract}
+\input{Abstract}
 \acresetall
 
-\include{Introduction} %(half page)
+\input{Introduction} %(half page)
 
-\include{Background}
+\input{Background}
 
-\include{Model}
+\input{Model}
 
-\include{Methods}
+\input{Methods}
 
-\include{Results}
+\input{Results}
 
-\include{Conclusion}
-\include{Acknowledgements}
+\input{Conclusion}
+\input{Acknowledgements}
 
 \bibliography{library,library_addendum}
-\bibliographystyle{myplainnat}
+\bibliographystyle{spbasic}
 
 \appendix
-
-\include{SensitivityAnalysis}
+\setcounter{table}{0}
+\renewcommand{\thetable}{A\arabic{table}}
+\input{SensitivityAnalysis}
 \end{document}

### 2014-12-31 Model.tex
More Springer jazz

@@
 Arrows correspond to two moves by nature, followed by women, and midwives respectively.
-Light terminal nodes indicate that the game may repeat from that point, and black nodes are exits.}
+Light terminal nodes indicate that the game may repeat from that point, and black nodes are exits}
 
@@
 \end{adjustbox}
-\caption{Detail view of a single game tree branch, showing the possible moves by each player, with information sets for midwives.}
+\caption{Detail view of a single game tree branch, showing the possible moves by each player, with information sets for midwives}
 
@@
 \begin{adjustbox}{center}\subfloat[Midwives]{\includegraphics[width=119mm]{figures/mw_influence}}\end{adjustbox}
-\caption{Influence diagrams, showing the game broken into two decision problems.}
+\caption{Influence diagrams, showing the game broken into two decision problems}
 
@@
 \cline{2-5} 
- & Refer & 10, 10 & 10, 10 & 10, 10\tabularnewline
+ & Refer & 10 & 10 & 10\tabularnewline
 \cline{2-5} 
- & Don't refer & -2, -2 & -1, -1 & 10, 10\tabularnewline
+ & Don't refer & -2 & -1 & 10\tabularnewline
 \hline 

### 2014-12-31 Results.tex
More Springer jazz

@@
 
-\begin{figure}[H]
-\begin{adjustbox}{center}\subfloat[Average fraction of population ever signalled honestly\label{fig:honest_signals}]{\includegraphics[width=0.43\paperwidth]{figures/honesty_plot}
-
-}\subfloat[Average fraction of population referred\label{fig:referrals}]{\includegraphics[width=0.43\paperwidth]{figures/ref_plot}}\end{adjustbox}
-\caption{Qualitative trends after 1000 rounds, mean with 95\% confidence limit over 1000 runs.}
+\begin{SCfigure}[H]
+\begin{adjustbox}{center}\subfloat[Average fraction of population ever signalled honestly\label{fig:honest_signals}]{\includegraphics[width=78mm]{figures/honesty_plot}\end{adjustbox}{center}
+}
+\vskip
+\begin{adjustbox}{center}\subfloat[Average fraction of population referred\label{fig:referrals}]{\includegraphics[width=78mm]{figures/ref_plot}}\end{adjustbox}
+\caption{Qualitative trends after 1000 rounds, mean with 95\% confidence limit over 1000 runs}
 \label{fig:qt_trends}
-\end{figure}
+\end{SCfigure}
 
@@
 \begin{adjustbox}{center}
-\includegraphics[width=0.8\textwidth]{figures/honesty_sharing}
+\includegraphics[width=119mm]{figures/honesty_sharing}
 \end{adjustbox}
-\caption{Impact of information sharing on trends in honest signalling after 1000 rounds, mean with 95\% confidence interval over 100 runs.}
+\caption{Impact of information sharing on trends in honest signalling after 1000 rounds, mean with 95\% confidence interval over 100 runs}
 \label{fig:honest_sharing}
@@
 \begin{adjustbox}{center}
-\includegraphics[width=0.8\textwidth]{figures/ref_sharing}
+\includegraphics[width=119mm]{figures/ref_sharing}
 \end{adjustbox}
-\caption{Impact of information sharing on referral trends after 1000 rounds, mean with 95\% confidence interval over 100 runs.}
+\caption{Impact of information sharing on referral trends after 1000 rounds, mean with 95\% confidence interval over 100 runs}
 \label{fig:ref_sharing}
@@
 \begin{figure}[H]
-\begin{adjustbox}{center}\includegraphics[width=0.8\textwidth]{figures/sharing_emulated_simulated}\end{adjustbox}
-\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules.}
+\begin{adjustbox}{center}\includegraphics[width=119mm]{figures/sharing_emulated_simulated}\end{adjustbox}
+\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules}
 \label{fig:outcome_plots}
@@
 \begin{figure}[H]
-\begin{adjustbox}{center}\includegraphics[width=0.8\textwidth]{figures/unfixed_emu_sig_iqr}\end{adjustbox}
-\caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\).}
+\begin{adjustbox}{center}\includegraphics[width=119mm]{figures/unfixed_emu_sig_iqr}\end{adjustbox}
+\caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\)}
 \label{fig:emulated_sharing_iqr}
@@
 \begin{figure}[H]
-\begin{adjustbox}{center}\includegraphics[width=0.8\linewidth]{figures/unfixed_emu_payoff_honesty_group_iqr}\end{adjustbox}
-\caption{Emulated between groups IQR in response to varying \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\), and \(x_{h}\).}
+\begin{adjustbox}{center}\includegraphics[width=119mm]{figures/unfixed_emu_payoff_honesty_group_iqr}\end{adjustbox}
+\caption{Emulated between groups IQR in response to varying \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\), and \(x_{h}\)}
 \label{fig:emulated_payoff_group_iqr}

### 2014-12-31 disclosure_game.tex
More Springer jazz

@@
 % RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[graybox]{svmult}
+\documentclass{svmult}
 
@@
 \usepackage[bottom]{footmisc}% places footnotes at page bottom
-
-% see the list of further useful packages
-% in the Reference Guide
-
-\makeindex             % used for the subject index
-                       % please use the style svind.ist with
-                       % your makeindex program
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{tikz}
+%\documentclass{article}
+% \usepackage{tikz}
  \usepackage{adjustbox}
@@
 }{\relax}
-\usepackage{fullpage}
 \usepackage{comment}
@@
  \setcitestyle{authoryear,round,aysep={,}}
-\usepackage{hyperref}
+% \usepackage{hyperref}
  \usepackage{graphicx}
-\usepackage[subrefformat=parens,labelformat=parens]{subfig}
+ \usepackage[subrefformat=parens,labelformat=simple,caption=false,labelfont={bf}]{subfig}
  \usepackage[nolist,smaller]{acronym}
-\usepackage{nomencl}
-\usepackage[style=long,nolist]{glossaries}
+ \usepackage{sidecap}
+% \usepackage{nomencl}
 
-\title*{Deciding to Disclose: A Decision Theoretic Agent Model of Pregnancy and Alcohol Misuse}
-\author{Jonathan Gray \and Jakub Bijak \and Seth Bullock\\
-University of Southampton, Southampton, SO17 1BJ, United Kingdom\\
-E-mail: \texttt{j.gray@soton.ac.uk}}
-\date{\vspace{-5ex}}
+\makeindex
+
 \begin{document}
-\maketitle
-
-%*************************
-% Acronyms
-%*************************
-%\phantomsection
-%\refstepcounter{dummy}
-%\pdfbookmark[1]{Acronyms}{acronyms}
-%\markboth{\spacedlowsmallcaps{Acronyms}}{\spacedlowsmallcaps{Acronyms}}
-%\section*{Acronyms}
-\begin{acronym}[UML]
+\begin{acronym}[ALSPAC]
   \acro{FAS}{Foetal Alcohol Syndrome}
@@
 
-\newglossaryentry{gravid}{name={gravid}, description={Pregnant}}
-\newglossaryentry{term}{name={term}, description={Gestation of 37-42 weeks, 40 weeks is considered full term}}
-\newglossaryentry{binge}{name={binge drinking}, description={Drinking with the express purpose of becoming drunk}}
-\newglossaryentry{burnout}{name={burnout}, description={Lasting physical and emotional exhaustion, and disillusionment}}
-\newglossaryentry{antenatal}{name={antenatal},description={The time period covering the pregnancy, prior to birth}}
-\newglossaryentry{episiotomies}{name={episiotomies}, description={An episiotomy is a common procedure where an incision is made in the perineum to facilitate delivery, and attempt to reduce the risk of vaginal tearing}}
-%\newglossaryentry{neonatal asphyxia}{name={antenatal},description={The time period covering the pregnancy, prior to birth}}
+\title*{Deciding to Disclose: A Decision Theoretic Agent Model of Pregnancy and Alcohol Misuse}
+
+\author{Jonathan Gray \and Jakub Bijak \and Seth Bullock}
+% Use \authorrunning{Short Title} for an abbreviated version of
+% your contribution title if the original one is too long
+\institute{Jonathan Gray \at University of Southampton, Southampton, SO17 1BJ, United Kingdom \email{j.gray@soton.ac.uk}
+\and Jakub Bijak \at University of Southampton, Southampton, SO17 1BJ, United Kingdom \email{j.bijak@soton.ac.uk}}
+
+\maketitle
+
+%*************************
+% Acronyms
+%*************************
+%\phantomsection
+%\refstepcounter{dummy}
+%\pdfbookmark[1]{Acronyms}{acronyms}
+%\markboth{\spacedlowsmallcaps{Acronyms}}{\spacedlowsmallcaps{Acronyms}}
+%\section*{Acronyms}
 

### 2014-12-31 build.sh

@@ -1,5 +1,12 @@
 #!/bin/sh
-pdflatex -interaction=batchmode disclosure_game
+rm disclosure_game.aux
+rm disclosure_game.bbl
+rm disclosure_game.blg
+rm disclosure_game.idx
+rm disclosure_game.log
+rm disclosure_game.out
+rm disclosure_game.pdf
+latex -interaction=batchmode disclosure_game
 makeglossaries disclosure_game
 bibtex disclosure_game
 pdflatex -interaction=batchmode disclosure_game

### 2014-12-31 Background.tex
Visual formatting

@@
 
-Here, we are specifically interested in signalling games \citep{Kreps1987,Spence1973}, where one player holds some private information which may be communicated (or not) by means of a signal.
+Here, we are specifically interested in signalling games \citep{Spence1973,Kreps1987}, where one player holds some private information which may be communicated (or not) by means of a signal.
 This basic form has been widely applied, with substantial interest in what conditions permit honest signalling as Nash equilibria or \acp{ESS}.
@@
 An alternative normative model of decision making is Bayesian decision theory, proposed by \citet{Robbins1964}, which is essentially the application of Bayesian style probabilities to the expected utility model.
-This allows probabilities used in reasoning to be subjective, which may allow for a better account of decisions from experience (see \citet{Hau2008,Hertwig2004} for results elucidating the distinction, and comparing the performance of several non-Bayesian models).
-This model has seen notable successes in practical problems \citep{McNamara1980,Survey2003,Kristensen1997}, but suggestions by several authors  that it could constitute an effective (top-down) model of learning \citep{Tenenbaum2006,Griffiths2010}, or induction \citep{Gallistel2012} in the brain have attracted substantial criticism\footnote{For example \citet{Bowers2012} responding to \citet{Tenenbaum2006}, and \citet{Griffiths2010}; and \citet{Miller2012} addressing \citet{Gallistel2012}.}.
+This allows probabilities used in reasoning to be subjective, which may allow for a better account of decisions from experience (see \citet{Hertwig2004,Hau2008} for results elucidating the distinction, and comparing the performance of several non-Bayesian models).
+This model has seen notable successes in practical problems \citep{McNamara1980,Kristensen1997,Survey2003}, but suggestions by several authors  that it could constitute an effective (top-down) model of learning \citep{Tenenbaum2006,Griffiths2010}, or induction \citep{Gallistel2012} in the brain have attracted substantial criticism\footnote{For example \citet{Bowers2012} responding to \citet{Tenenbaum2006}, and \citet{Griffiths2010}; and \citet{Miller2012} addressing \citet{Gallistel2012}.}.
 
@@
 
-As noted, heuristic decision making stems from a contention that \citeauthor{Neumann1953} type rationality ignores the context of decision making, and a lack of correspondence between predicted and actual human decisions (see, for example the Allais paradox \citep{Society2013}, and subsequent empirical support \citep{Oliver2003,Burke1996}).
+As noted, heuristic decision making stems from a contention that \citeauthor{Neumann1953} type rationality ignores the context of decision making, and a lack of correspondence between predicted and actual human decisions (see, for example the Allais paradox \citep{Society2013}, and subsequent empirical support \citep{Burke1996,Oliver2003}).
 Arguably, this notion begins with \citet{Simon1956}, who suggested that humans do not attempt to make optimal choices, but to satisfice and choose the first `good enough' option.

### 2014-12-31 Methods.tex
Visual formatting

@@
 While there has been significant work on determining appropriate parameterisation for the model (e.g.
-\cite{Neilson2002,Glockner2012,Nilsson2011}, and particularly \citet{Byrnes1999} and \citet{Booij2009} addressing risk aversion and gender), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work.
+\cite{Neilson2002,Nilsson2011,Glockner2012}, and particularly \citet{Byrnes1999} and \citet{Booij2009} addressing risk aversion and gender), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work.
 For simplicity, it was assumed that all three drinking types are equally prevalent within the population, although results derived from \ac{ALSPAC} suggest that the reality is far more positive \citep{Humphriss2013}.

### 2014-12-31 Model.tex
Visual formatting

@@
 In an ideal world, all interactions with healthcare providers would be immediately and fully disclosive, with no repercussions for the patient.
-However, alcohol misuse by women is known to attract stigma \citep{Gomberg1988}, and is a recognised barrier to appropriate treatment in the maternity context \citep{Radcliffe2011,NICE2010}.
+However, alcohol misuse by women is known to attract stigma \citep{Gomberg1988}, and is a recognised barrier to appropriate treatment in the maternity context \citep{NICE2010,Radcliffe2011}.
 

### 2014-12-31 Results.tex
Visual formatting

@@
 
-\begin{SCfigure}[H]
-\begin{adjustbox}{center}\subfloat[Average fraction of population ever signalled honestly\label{fig:honest_signals}]{\includegraphics[width=78mm]{figures/honesty_plot}\end{adjustbox}{center}
-}
-\vskip
-\begin{adjustbox}{center}\subfloat[Average fraction of population referred\label{fig:referrals}]{\includegraphics[width=78mm]{figures/ref_plot}}\end{adjustbox}
-\caption{Qualitative trends after 1000 rounds, mean with 95\% confidence limit over 1000 runs}
-\label{fig:qt_trends}
-\end{SCfigure}
+\begin{figure}[H]
+\includegraphics[width=119mm]{figures/honesty_plot}
+\caption{Average fraction of population ever signalled honestly after 1000 rounds, mean with 95\% confidence limit over 1000 runs\label{fig:honest_signals}}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[width=119mm]{figures/ref_plot}
+\caption{Average fraction of population referred after 1000 rounds, mean with 95\% confidence limit over 1000 runs\label{fig:qt_trends}}
+\end{figure}
 

### 2014-12-31 disclosure_game.tex
Visual formatting

@@
 
-\title*{Deciding to Disclose: A Decision Theoretic Agent Model of Pregnancy and Alcohol Misuse}
+\title*{Deciding to Disclose}
+\subtitle{A Decision Theoretic Agent Model of Pregnancy and Alcohol Misuse}
 
@@
 % your contribution title if the original one is too long
-\institute{Jonathan Gray \at University of Southampton, Southampton, SO17 1BJ, United Kingdom \email{j.gray@soton.ac.uk}
-\and Jakub Bijak \at University of Southampton, Southampton, SO17 1BJ, United Kingdom \email{j.bijak@soton.ac.uk}}
+\institute{Jonathan Gray \at University of Southampton, Southampton, United Kingdom \email{j.gray@soton.ac.uk}
+\and Jakub Bijak \at University of Southampton, Southampton, United Kingdom \email{j.bijak@soton.ac.uk}
+\and Seth Bullock \at University of Southampton, Southampton, United Kingdom \email{sgb@ecs.soton.ac.uk}}
 

### 2015-01-07 Abstract.tex
More Springer jazz
Grayscale friendliness, spelling

@@
 \let\cleardoublepage\relax
-
-\pdfbookmark[1]{Abstract}{Abstract}
 
@@
 
-The primary purpose of this work is to demonstrate the significance of precisely how the decision making process is formulated, by contrasting four distinct decision rules against one another and exploring a simple form of information sharing, supported by the use of statistical emulators for a full exploration of the parameter space.
-We also demonstrate the utility of an approach which it is hoped goes some way towards addressing concerns about the ad hoc character of \ac{ABM}, by providing a strong theoretical grounding for the reasoning processes of individual agents.
-To this end we hope to show that these simple rules, operating in an inescapably artificial scenario are nonetheless capable of reproducing trends reported in the literature.
+The primary purpose of this work is to demonstrate the significance of how the decision making process is formulated, by contrasting four distinct decision rules against one another and exploring a simple form of information sharing, the analysis is supported by the use of statistical emulators for a full exploration of the parameter space.
+We also demonstrate the utility of an approach which it is hoped contributes towards addressing concerns about the ad hoc character of \ac{ABM}, by providing a strong theoretical grounding for the reasoning processes of individual agents.
+To this end we aim to show that these simple rules, operating in an inescapably artificial scenario are nonetheless capable of reproducing trends reported in the literature.
 
@@
 
-We employ game theory to define a signalling game representative of a scenario where pregnant women decide the extent to which they disclose their drinking behaviours to their midwives, and midwives employ the information provided to decide whether to refer their patients for costly specialist treatment.
+We employ a game theoretic framework to define a signalling game.
+The game represents a scenario where pregnant women decide the extent to which they disclose their drinking behaviours to their midwives, and midwives employ the information provided to decide whether to refer their patients for costly specialist treatment.
 This game is then recast as two games played against \enquote{nature}, to permit the use of a decision theoretic approach where both classes of agent use simple rules to decide their moves.
@@
 
-In simulation, we recreate two key qualitative trends described in the Midwifery literature for all the decision models, and investigate the impact of introducing a simple form of information sharing within agent groups.
-Finally a global sensitivity analysis using \acp{GEM} was conducted, to compare the response surfaces of the different decision rules in the game.
+In simulation, we recreate two key qualitative trends described in the midwifery literature for all the decision models, and investigate the impact of introducing a simple form of information sharing within agent groups.
+Finally a global sensitivity analysis using \acp{GEM} is conducted, to compare the response surfaces of the different decision rules in the game.
 

### 2015-01-07 Background.tex
Grayscale friendliness, spelling

@@
 Similar results have also been demonstrated in a game of job market signalling, where signal cost was differentiated by type \citep{Spence1973}.
-Costly signalling has also been suggested as an explaination of behaviour that at first glance appears counter intuitive, for example \citet{Godfray1991} applied the idea to the food solicitation behaviour of chicks, where a stronger signal carries a risk of being eaten.
+Costly signalling has also been suggested as an explanation of behaviour that at first glance appears counter intuitive, for example \citet{Godfray1991} applied the idea to the food solicitation behaviour of chicks, where a stronger signal (i.e.
+more, or louder chirping) carries a risk of being eaten by predators.
 Moving beyond animal behaviour, \citet{Sosis2003} considered the implications of ritual behaviour, in the context of religion, represented a costly signal, an idea subsequently extended by \citet{Henrich2009} to include cultural transmission, and \citet{Wildman2011} to introduce group differentiation.
 
-Other work augments the signalling game model, for example \citet{Austen-Smith2005} add a second `peer group' audience signalling game to the original \citeauthor{Spence1973} game in an effort to explain poor academic performance in some social groups, with some subseqent empirical support for the idea from \citet{Jr2010}.
-On a similar tack, \citet{Feltovich2002} introduce additional noisy type information, finding that this effectively explained counterintuitive observed behaviour where actors with every right to boast of their quality fail to do so.
+Other work augments the signalling game model, for example \citet{Austen-Smith2005} add a second `peer group' audience signalling game to the original \citeauthor{Spence1973} game in an effort to explain poor academic performance in some social groups, with some subsequent empirical support for the idea from \citet{Jr2010}.
+On a similar tack, \citet{Feltovich2002} introduce additional noisy type information, finding that this effectively explained counter-intuitive observed behaviour where actors with every right to boast of their quality fail to do so.
 
@@
 Taken literally, this leads to normative decision theory, where the focus is on giving the rational answer to a decision problem.
-An alternative view - descriptive, or behavioural decision theory, holds that the focus should instead be on giving an account of human decision making performance, complete with observed deviations from perfect rationality, which we address in section \ref{sub:descriptive_theories}.
+An complementary view - descriptive, or behavioural decision theory, holds that the focus should instead be on giving an account of human decision making performance, complete with observed deviations from perfect rationality, which we address in section \ref{sub:descriptive_theories}.
 Finally a third perspective, which to some extent overlaps this division, suggests that decisions are heuristic in nature and rational in ecological context \citep{Gigerenzer1996} (section \ref{sub:heuristic_theories}).

### 2015-01-07 Conclusion.tex
Grayscale friendliness, spelling

@@
 To some extent this reflects poorly on the most complex rule, \ac{CPT}, which diverges only minimally in behaviour from the Bayesian model.
-To some extent this might be anticipated, in that the payoffs are clearly unrealistic, which limits the utility of the \ac{CPT} approach.
-Additionally, work by \citet{Glockner2012} has shown that there is considerable variation in individual parameters for the decision model, whereas we have let them remain homogenous here.
+This might be to a degree anticipated, in that the payoffs are unrealistic, which limits the utility of the \ac{CPT} approach.
+Additionally, work by \citet{Glockner2012} has shown that there is considerable variation in individual parameters for the decision model, whereas we have let them remain homogeneous here.
 In the same vein, utility functions should arguably vary between individual agents, which could potentially be addressed by replacing the fixed payoffs used here with a distribution.
 With this said, the significant increase in complexity, which entails both additional parameters and increases to simulation time may auger for a middle ground, particularly where elicitation of payoffs is impractical.
-This, together with the variablility associated with the heuristic type decision rules speaks to a tradeoff between capturing reality, and replicating it.
+This, together with the variability associated with the heuristic type decision rules speaks to a trade off between capturing reality, and replicating it.
 
-Continuing the discussion of the issues raised by the representation of payoffs, the temporal aspect is significant, in that there is clearly a timing difference in payoffs, since while the potential social pain of disclosure is immediate, the health outcome comes only later.
+Continuing the discussion of the issues raised by the representation of payoffs, the temporal aspect is significant, in that there is a timing difference in payoffs, since while the potential social pain of disclosure is immediate, the health outcome comes only later.
 In light of this, that there is a known impact of time on perceived utility \citet{Thaler1981} suggests that incorporating some form of temporal discounting (e.g.
@@
 The restriction to sharing only after a referral, together with the disparity in population sizes, and random allocation of appointments leads to midwives rarely having more than a single interaction with woman to pass on to their colleagues.
-Furthermore, because midwives are only informed of the true type if a referral occurs, they have an inherent myopia, since until they have evidence of deception they will not refer, with said evidence difficult to obtain without a referral.
+Furthermore, because midwives are only informed of the true type if a referral occurs, they have an inherent myopia since until they have evidence of deception they will not refer, with said evidence difficult to obtain without a referral.
 
@@
 This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared and more sophisticated model of information transmission in general.
-This also highlights an advantage of the \ac{BACCO} approach, in that it aids in diagnosing issues with model design by giving insight into parameters which are contributing innapropriately to variance in output.
+This also highlights an advantage of the \ac{BACCO} approach, in that it aids in diagnosing issues with model design by giving insight into parameters which are contributing inappropriately to variance in output.
+Coupled with the ability of emulators to rapidly explore parameter space, this clearly suggests that statistical emulation is a powerful tool to support simulation based approaches.
 
@@
 The conclusions that can be drawn about the behaviours of real life women, and their midwives, are necessarily limited by the paucity of data available to validate the model.
-While qualitative trends offer some indication, they are clearly very limited in scope, and do not permit strong claims about the drivers of disclosure.
+While qualitative trends offer some indication, they are limited in scope, and do not permit strong claims about the drivers of disclosure.
 As such, further work will focus on applying the model to domains where validation data is more available, which will support a more comprehensive evaluation of the model discrepancy.

### 2015-01-07 Introduction.tex
Grayscale friendliness, spelling

@@
 
-The case in favour of \ac{ABM} as a general approach has been made numerously, and elegantly (e.g.
+The case in favour of \ac{ABM} as a general analytical approach has been made numerously, and elegantly (e.g.
 \citet{epstein1994growing,Resnick,Axelrod1997,gilbert1999simulation,Macy2002a,Silverman2011,Silverman2013,epstein2014agent_zero}, amongst others).
@@
 
-While there is no universal theory of human behaviour to sit at the center of \ac{ABM} as a method, a key motivation for decision rules is their claim to provide an account of decision making that is behaviourally and cognitively plausible.
+While there is no universal theory of human behaviour to sit at the centre of \ac{ABM}ing as a method, a key motivation for decision rules is their claim to provide an account of decision making that is behaviourally and cognitively plausible.
 Their mooted capability in this regard is to some extent supported by work from neuroeconomics, which aims to empirically test theories of decision making \citep{Rustichini2009}.
@@
 Given these features, the application of decision, and game theory to \ac{ABM} is an attractive approach to computational social science, where the locus of interest is decision making.
-Taking a balance between the strongly biological, e.g.
-neural networks, and the more abstract threshold, or microsimulation like models yields a computationally tractable approach.
+Taking a balance between models focused on replication of low level neurological mechanics, and those with a higher level emphasis where individual behaviours are abstracted away yields a computationally tractable approach.
 Despite the relative simplicity, it nonetheless captures some of the nuance and sophistication of human decisions.

### 2015-01-07 Methods.tex
Grayscale friendliness, spelling

@@
 Throughout this paper, parameters for the \ac{CPT} model were as used in \cite{Tversky1992} (table \ref{tab:qt_params}).
-While there has been significant work on determining appropriate parameterisation for the model (e.g.
+While there has been significant work on determining appropriate parametrisation for the model (e.g.
 \cite{Neilson2002,Nilsson2011,Glockner2012}, and particularly \citet{Byrnes1999} and \citet{Booij2009} addressing risk aversion and gender), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work.
@@
 \(w_{m}\) & Weight of shared information for midwives & 0. \\ \hline
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 10:1 \\ \hline
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 10:1 \\ \hline
 \(\gamma\) & Probability weighting for gains  & 0.61 \\ \hline
@@
 In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examined the impact of simple information sharing within the population of women (section \ref{sub:info_sharing}) on the robustness of these trends.
-The original experiment was repeated at \(q_{w},w_{w}\in \{0.25, 0.5, 0.75, 1\}\), with 100 runs under each condition.
+The original experiment was repeated at \(q_{w},w_{w}\in \{0.25, 0.5, 0.75, 1 | q_{w}=w_{w}\}\), with 100 runs under each condition.
 
@@
 This is a form of variance-based sensitivity analysis, which assumes that the model output is an unknown, smooth function of the inputs.
-The unknown function can then be approximated as a Gaussian Process, which is fitted to the training data using Bayes' Theorem.
-The emulator is then able to provide an indication about the extent to which uncertainty in a parameter propogates to uncertainty in the output, and how sharply the output responds to change in each parameter.
+The unknown function can then be approximated as a Gaussian Process, which is fitted to the training data using Bayes' Theorem and then serves as an emulator for the simulator.
+The emulator is then able to provide an indication about the extent to which uncertainty in a parameter propagates to uncertainty in the output, and how sharply the output responds to change in each parameter.
 
@@
 Sixteen emulators were built, covering each of the four outputs on all four decision models.
-These emulators were used to conduct a probabalistic sensitivity analysis using \ac{GEM-SA} to assess the impact of parameters individually, and in combination.
+These emulators were used to conduct a probabilistic sensitivity analysis using \ac{GEM-SA} to assess the impact of parameters individually, and in combination.
 
@@
 \(x_{r}\) & Cost for referral & \multicolumn{2}{l|}{\(-(x_{h} - 1)\)} \\ \hline
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 1:1 & 100:1 \\ \hline
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 1:1 & 100:1 \\ \hline
 \end{tabular}

### 2015-01-07 Model.tex
Grayscale friendliness, spelling

@@
 
-According to NICE guidance \citep{NICE2010a,NICE2010} the issue of substance misuse should be raised at the initial booking appointment, follwed by subsequent action if a concern is raised is at the discretion of the midwife.
+According to NICE guidance \citep{NICE2010a,NICE2010} the issue of substance misuse should be raised at the initial booking appointment, followed by subsequent action if a concern is raised is at the discretion of the midwife.
 This may take the form of specific guidance to reduce intake, or if deemed necessary a referral to a specialist midwife and relevant interdisciplinary team.
-On alcohol consumption, policy regarding how to determine the level of consumption is generally at the level of local health authority, hospital trust, or according to the best judgement of the individual midwife, with no guidance provided by NICE.
-This commonly takes the form of average units per week, but may include \ac{T-ACE}\footnote{The \ac{T-ACE} is a four question screening test intended specifically for use with pregnant women.} \citep{Sokol1989863} and similar measures.
+On alcohol consumption, policy regarding how to determine the level of consumption is at the time of writing generally at the level of local health authority, hospital trust, or according to the best judgement of the individual midwife, with no guidance provided by NICE.
+This commonly takes the form of average units per week, but may include \ac{T-ACE}\footnote{The \ac{T-ACE} is a four question screening test for alcohol misuse intended specifically for use with pregnant women.} \citep{Sokol1989863} and similar measures.
 
@@
 Taken together, this leads to a game tree that is relatively complex (figure \ref{fig:simple_tree} shows a simplified representation, with a detailed view of one branch in figure \ref{fig:zoom_tree}) even at the subgame level.
-Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversial risk analysis \citep{RiosInsua2009}.
+Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversarial risk analysis \citep{RiosInsua2009}.
 This effectively translates the game to a pair of decision problems (figure \ref{fig:decision_problems}), which agents attempt to resolve at each turn using a simple decision rule, given their prior beliefs and experience of play.
@@
 \begin{figure}[H]
-\begin{adjustbox}{center}\subfloat[Women]{\includegraphics[width=119mm]{figures/women_influence}}\end{adjustbox}
+\begin{adjustbox}{center}\subfloat[Women (heavy drinkers)]{\includegraphics[width=119mm]{figures/women_influence}}\end{adjustbox}
 \vskip
 \begin{adjustbox}{center}\subfloat[Midwives]{\includegraphics[width=119mm]{figures/mw_influence}}\end{adjustbox}
-\caption{Influence diagrams, showing the game broken into two decision problems}
+\caption{Influence diagrams, showing the game broken into two decision problems. Squares indicate a decision node, while circles are (from the perspective of the agent) chance nodes}
 
@@
 To formally define the game, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\).
-Additionally define two utility functions \(u_{w}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}}\), \(u_{m}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}}\), with $X_{c}$, $X_{h}$, and $X_{s}$ being the payoff matrices as in table \ref{tab:Payoff-matrix}; and distributions over types \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\).
+Here, \(\{l, m, h\}\) correspond to light, moderate, and heavy alcohol consumption for women, and non-judgemental, moderately judgemental, and harshly judgemental for midwives.
+Midwives' pure strategies \(\{r,n\}\) are to refer, or do nothing, and those for women are to signal that they have one of the possible drinking patterns.
+Additionally define two utility functions \(u_{w}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}}\), \(u_{m}(s_{w}, s_{m}, \theta_{w})=X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}}\), with $X_{c}$, $X_{h}$, and $X_{s}$ being the payoff matrices as in table \ref{tab:Payoff-matrix}, with $s_{w}$ and $s_{m}$ denoting a specific signal by a woman, and referral response by a midwife.
+Lastly let \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\) be distributions over types of women, and midwives respectively.
 
@@
 \center
-\subfloat[Social cost, \(X_{s}\), for women\label{tab:Social-cost-matrix}]{%
+\subfloat[Social cost, \(X_{s}\), for women, given their signal, and the midwife's type\label{tab:Social-cost-matrix}]{%
 \begin{tabular}{|c|c|c|c|c|}
@@
 \cline{2-5} 
- & Medium & -1 & 0 & 0\tabularnewline
+ & Moderate & -1 & 0 & 0\tabularnewline
 \cline{2-5} 
- & Low & 0 & 0 & 0\tabularnewline
+ & Non & 0 & 0 & 0\tabularnewline
 \hline 
@@
 
-\subfloat[Health outcome, \(X_{h}\), for women and midwives\label{tab:Referral-payoff-matrix}]{%
+\subfloat[Health outcome, \(X_{h}\), for women and midwives, given the midwife's action, and woman's type\label{tab:Referral-payoff-matrix}]{%
 \begin{tabular}{|c|c|c|c|c|}
@@
 
-\subfloat[Referral cost, \(X_{c}\), for midwife\label{tab:inst_cost_matrix}]{%
+\subfloat[Referral cost, \(X_{c}\), for midwife, given their action and the woman's type\label{tab:inst_cost_matrix}]{%
 \begin{tabular}{|c|c|c|c|c|}
@@
 The simplest is a lexicographic rule (1), in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}.
-Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-ouput characteristics.
+Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-output characteristics.
 
@@
 A simplifying assumption is made that all midwives have just qualified after receiving identical training.
-As a result, they have homogenous beliefs about  women and assume to some extent that they are honest.
-Women are heterogenous in their prior observations, which are assigned stochastically and constrained such that they have encountered each scenario possible for their type at least once, with exactly \(k\) encounters overall.
+As a result, they have homogeneous beliefs about  women and assume to some extent that they are honest.
+Women are heterogeneous in their prior observations, which are assigned stochastically and constrained such that they have encountered each scenario possible for their type at least once, with exactly \(k\) encounters overall.
 
@@
 one reason decision making.
-Where there is no clear best action, but one or more is clearly worse, a choice must be made as to whether to discard the poorer action; in this case we have elected to retain it.
+Where there is no clear best action, but one or more is evidently worse, a choice must be made as to whether to discard the poorer action; in this case we have elected to retain it.
 This approach requires minimal computation, and does not assume that \(u_{i}\) is static, or known.
@@
 more than zero and summing to less than 1, and \(\alpha_{i}\) is the 
-psuedo-count of prior observations for a pair \(i\).
+pseudo-count of prior observations for a pair \(i\).
 
@@
 \begin{equation}
-P(x=j|D,\alpha)=\frac{\alpha_{j}+n_{j}}{\sum_{j}(\alpha_{j}+n_{j})}\label{eq:posterior}
+p(x=j|D,\alpha)=\frac{\alpha_{j}+n_{j}}{\sum_{j}(\alpha_{j}+n_{j})}\label{eq:posterior}
 \end{equation}
 
-Where \(n_{j}\) is simply the count of occurrences of pair \(j\), so
-that the belief that a signal \(j\) the number
-of times that type has been observed (including the pseudo-count),
+Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), so
+that the belief that a signal will lead to a payoff is the number
+of times that pairing has been observed (including the pseudo-count),
 over the total number of observations thus far. This makes computation
@@
 a count of observations with no particular concern as to their order.
-As before, midwives follow a similar pattern but per signal.
+As before, midwives follow a similar pattern but maintain \(n_{s_{w}}\) independent counts of pairings between referral choice and payoff, updating their beliefs about the relationship between the choice to refer and payoff given the signal they have received.
 
@@
 \begin{equation}
-R_{m}(s_{w}, s_{m}) = \sum_{x \in X} -xp(x | s_{w}\wedge s_{m})
+R_{m}(s_{w}, s_{m}) = \sum_{x \in X} -xp(x | s_{w}\wedge s_{m}),
 \end{equation}
 
-where $X$ is the set of payoffs the agent has observed to follow $s$.
+where $X$ is the set of payoffs the agent has observed to follow $s_{i}$.
 
@@
 \begin{equation}
-R_{w}(s_{w}, \theta_{w}) = \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, \theta_{w}, j)p(j)p(i | s_{w})
+R_{w}(s_{w}, \theta_{w}) = \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, \theta_{w}, j)p(j)p(i | s_{w}),
 \end{equation}
@@
 
-Midwives reasoning centers on determining the meaning of signals, since given the knowledge of what some signal \(i\) conveys about the true type of the sender, the payoff for an action is known.
+Midwives reasoning centres on determining the meaning of signals, since given the knowledge of what some signal \(s_{w}\) conveys about the true type of the sender, the payoff for an action is known.
 As such, their inference process is the same as for the simple Bayesian agent but over signal-type pairs, and they attempt to minimise the following risk function, minimised with respect to \(s_{m}\) -
@@
 \begin{equation}
-R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{w}(s_{w}, s_{m}, i, \theta_{m})p(i | s_{w})
+R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{w}(s_{w}, s_{m}, i)p(i | s_{w})
 \end{equation}
@@
 This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and contrastingly low probabilities as impossible.
-The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains and losses -
+The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains (eqn \ref{eqn:cpt_p_pos}) and losses (eqn \ref{eqn:cpt_p_neg}) -
 
-\begin{eqnarray}
-w^{+}(p) & = & \frac{p^{\gamma}}{(p^{\gamma}+(1-p)^{\gamma})^{\frac{1}{\gamma}}}\\
-w^{-}(p) & = & \frac{p^{\delta}}{(p^{\delta}+(1-p)^{\delta})^{\frac{1}{\delta}}}
-\end{eqnarray}
+\begin{align}
+w^{+}(p) & = & \frac{p^{\gamma}}{(p^{\gamma}+(1-p)^{\gamma})^{\frac{1}{\gamma}}}\label{eqn:cpt_p_pos}\\
+w^{-}(p) & = & \frac{p^{\delta}}{(p^{\delta}+(1-p)^{\delta})^{\frac{1}{\delta}}}\label{eqn:cpt_p_neg},
+\end{align}
 
-Where $p$ is the unweighted probability, and $\gamma$ and $\delta$
+where $p$ is the unweighted probability, and $\gamma$ and $\delta$
 are the weights for gain and loss probabilities respectively.
@@
 v(u_{i})=\begin{cases}
-f(u_{i}) & \text{if}\, u_{i}>0\\
-0 & \text{if}\, u_{i}=0\\
-\lambda g(u_{i}) & \text{if}\, x<0
-\end{cases}
+f(u_{i}),& \text{if}\, u_{i}>0\\
+0,& \text{if}\, u_{i}=0\\
+\lambda g(u_{i}),& \text{if}\, x<0
+\end{cases},
 \end{equation}
@@
 f(u_{i})=\begin{cases}
-u_{i}^{\alpha} & \text{if}\,\alpha>0\\
-\ln(u_{i}) & \text{if}\,\alpha=0\\
-1-(1+u_{i})^{\alpha} & \text{if}\,\alpha<0
+u_{i}^{\alpha},& \text{if}\,\alpha>0\\
+\ln(u_{i}),& \text{if}\,\alpha=0\\
+1-(1+u_{i})^{\alpha},& \text{if}\,\alpha<0
 \end{cases}
@@
 g(u_{i})=\begin{cases}
--(-u_{i})^{\beta} & \text{if}\,\beta>0\\
--\ln(-u_{i}) & \text{if}\,\beta=0\\
-(1-u_{i})^{\beta}-1 & \text{if}\,\beta<0
-\end{cases}
+-(-u_{i})^{\beta},& \text{if}\,\beta>0\\
+-\ln(-u_{i}),& \text{if}\,\beta=0\\
+(1-u_{i})^{\beta}-1,& \text{if}\,\beta<0
+\end{cases},
 \end{equation}
@@
 Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this exogenous information differently.
-The simple payoff based rule relys on a belief structure relating actions directly to rewards which is essentially model free.
+The simple payoff based rule relies on a belief structure relating actions directly to rewards which is essentially model free.
 Because payoffs differ by the agent's private type, the information shared may not correspond to the experience of the listening agent in the same scenario.

### 2015-01-07 Results.tex
Grayscale friendliness, spelling

@@
 \includegraphics[width=119mm]{figures/ref_plot}
-\caption{Average fraction of population referred after 1000 rounds, mean with 95\% confidence limit over 1000 runs\label{fig:qt_trends}}
+\caption{Average fraction of population referred after 1000 rounds, mean with 95\% confidence limit over 1000 runs\label{fig:referrals}}
 \end{figure}
@@
 Particularly notable, is the decline in honest signalling by light drinkers visible in both heuristic type rules at the 0.25 level of \(q_{w}\) \& \(w_{w}\), and the associated increase in false positives.
-This arises because of the lack of homophilly in information sharing, as light drinkers become informed about negative outcomes associated with concealment, despite having nothing to conceal.
+This arises because of the lack of homophily in information sharing, as light drinkers become informed about negative outcomes associated with concealment, despite having nothing to conceal.
 The relatively high referral rates of drinkers heighten the effect further, because shared information becomes dominated by their experiences.
 
-The relationship is not, however, entirely straighforward, in that increasing information sharing leads to greater variance between runs.
-A linear model was used to predict the between runs interquartile range of the average signal sent by moderate drinkers, with decision rule, and level of information sharing, together with the interaction between the two as predictors.
+The relationship is not, however, entirely straightforward, in that increasing information sharing leads to greater variance between runs.
+A linear model was used to predict the between-runs interquartile range of the average signal sent by moderate drinkers.
+The predictors used were decision rule, and level of information sharing, together with the interaction between the two.
 The regression results were significant (\(F_{7,12}=25,p<2.9\times10^{-6}\)) with \(R^2=94\%\), and intercept 0.07.
@@
 They also suggest that the Bayesian decision rule is less stable under conditions where the weight of shared information is substantially higher than the probability of sharing.
-Also of interest is the large region of instability that can be discerned for the Bayesian rule under modest probability of information sharing and higher weights.
 This suggests that, perhaps unsurprisingly, that what information is shared is significant to outcomes.

### 2015-01-07 SensitivityAnalysis.tex
Grayscale friendliness, spelling

@@
 \(x_{h}\) & Health payoff for healthy delivery & 0.457 & 9.618 & 1.912 & 15.355 \\ \hline
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.140 & 7.537 & 10.427 & 7.795 \\ \hline
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.140 & 7.537 & 10.427 & 7.795 \\ \hline
 Total & All parameters and two way interactions & 86.777 & 96.527 & 85.529 & 74.123 \\ \hline
@@
 \(x_{h}\) & Health payoff for healthy delivery & 0.317 & 10.960 & 3.305 & 16.493 \\ \hline
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 1.107 & 8.411 & 2.890 & 6.729 \\ \hline
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 1.107 & 8.411 & 2.890 & 6.729 \\ \hline
 Total & All parameters and two way interactions & 81.702 & 83.693 & 47.449 & 71.032 \\ \hline
@@
 \(x_{h}\) & Health payoff for healthy delivery & 0.253 & 0.612 & 4.889 & 15.146 \\ \hline
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.504 & 3.096 & 19.863 & 25.999 \\ \hline
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.504 & 3.096 & 19.863 & 25.999 \\ \hline
 Total & All parameters and two way interactions & 84.9968 & 77.413 & 57.125 & 83.322 \\ \hline
@@
 \(x_{h}\) & Health payoff for healthy delivery & 0.228 & 3.190 & 6.308 & 14.777 \\ \hline
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Psuedo-count favouring honesty & 0.673 & 10.411 & 22.901 & 26.340 \\ \hline
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.673 & 10.411 & 22.901 & 26.340 \\ \hline
 Total & All parameters and two way interactions & 85.740 & 88.611 & 68.640 & 84.210 \\ \hline

### 2015-01-07 Results.tex
More explanation for simplified tree

@@
 Figure \ref{fig:emulated_payoff_group_iqr} shows better separation, close to partial pooling\footnote{Pooling occurs when signallers of different types `pool' their signals, and one adopts the signals of another.} at high payoff distinction, with relatively modest honesty bias, which is reflected by the variance contributions of 11\% and 8\% respectively.
-For the more complex rules, the general tendency is towards less pooling for higher values of both, but with pockets where full pooling\footnote{Indicating that all signallers types are using a single signal.} occurs.
+For the more complex rules, the general tendency is towards less pooling for higher values of both, but with pockets where full pooling\footnote{Indicating that all signaller types are using a single signal.} occurs.
 The plots also suggest that the sensitivity of the \ac{CPT} rule is marginally greater, which is supported by the significant contribution to variance of close to 15\% for all measures of \(x_{h}\).

### 2015-01-08 Background.tex
Minor tweaks

@@
 more, or louder chirping) carries a risk of being eaten by predators.
-Moving beyond animal behaviour, \citet{Sosis2003} considered the implications of ritual behaviour, in the context of religion, represented a costly signal, an idea subsequently extended by \citet{Henrich2009} to include cultural transmission, and \citet{Wildman2011} to introduce group differentiation.
+Moving beyond animal behaviour, \citet{Sosis2003} considered the implications of ritual behaviour, in the context of religion, representing a costly signal, an idea subsequently extended by \citet{Henrich2009} to include cultural transmission, and \citet{Wildman2011} to introduce group differentiation.
 
@@
 
-While game theory addresses rational strategic decision making, decision theory deals instead with rational decision making \citep{Peterson2009}.
+While game theory addresses rational \emph{strategic} decision making, decision theory deals instead with rational decision making \citep{Peterson2009}.
 Taken literally, this leads to normative decision theory, where the focus is on giving the rational answer to a decision problem.
@@
 
-As noted, heuristic decision making stems from a contention that \citeauthor{Neumann1953} type rationality ignores the context of decision making, and a lack of correspondence between predicted and actual human decisions (see, for example the Allais paradox \citep{Society2013}, and subsequent empirical support \citep{Burke1996,Oliver2003}).
+As noted, heuristic decision making stems from a contention that \citeauthor{Neumann1953} type rationality ignores the context of decision making, and a lack of correspondence between predicted and actual human decisions (see, for example the Allais paradox \citep{Society2013}, and subsequent empirical support from \citet{Burke1996} and \citet{Oliver2003}).
 Arguably, this notion begins with \citet{Simon1956}, who suggested that humans do not attempt to make optimal choices, but to satisfice and choose the first `good enough' option.

### 2015-01-08 Conclusion.tex
Minor tweaks

@@
 
-In reality it might be anticipated that midwives would not withhold judgement so completely, and would pass on concerns about particular women to their colleagues, or that particularly dramatic stories would persist and be passed.
+In reality it might be anticipated that midwives would not withhold judgement so completely, and would pass on concerns about specific women to their colleagues, or that particularly dramatic stories would persist and be passed.
 This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared and more sophisticated model of information transmission in general.

### 2015-01-08 Introduction.tex
Minor tweaks

@@
 A game theoretic approach to generating an abstract form of the problem gives a convenient, and well known framework to reason about the processes involved in the scenario.
-While scenarios may well map to a number of games, exploring one candidate game still allows for a principled comparison between interpretations, and enforces explicit assumptions.
+While scenarios may map to a number of games, exploring one candidate game still allows for a principled comparison between interpretations, and enforces explicit assumptions.
 Relating this to decision theory shifts the emphasis away from analytical equilibrium-seeking, and heightens the importance of behaviour change.

### 2015-01-08 Model.tex
More explanation for simplified tree
Minor tweaks

@@
 Arrows correspond to two moves by nature, followed by women, and midwives respectively.
+Line weight distinguishes between information sets, and possible moves, corresponding to ascending player types.
+For midwives, referral is shown by a heavier arrow.
 Light terminal nodes indicate that the game may repeat from that point, and black nodes are exits}
@@
 Midwives' pure strategies \(\{r,n\}\) are to refer, or do nothing, and those for women are to signal that they have one of the possible drinking patterns.
-Additionally define two utility functions \(u_{w}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}}\), \(u_{m}(s_{w}, s_{m}, \theta_{w})=X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}}\), with $X_{c}$, $X_{h}$, and $X_{s}$ being the payoff matrices as in table \ref{tab:Payoff-matrix}, with $s_{w}$ and $s_{m}$ denoting a specific signal by a woman, and referral response by a midwife.
+Additionally define two utility functions - 
+\begin{equation}
+u_{w}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}},
+\end{equation} 
+\begin{equation}
+u_{m}(s_{w}, s_{m}, \theta_{w})=X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}},
+\end{equation} with $X_{c}$, $X_{h}$, and $X_{s}$ being the payoff matrices as in table \ref{tab:Payoff-matrix}, $s_{w}$ and $s_{m}$ denoting a specific signal by a woman, and referral response by a midwife.
 Lastly let \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\) be distributions over types of women, and midwives respectively.
@@
 If they are not referred, they rejoin the back of the queue after their appointment.
-In either case, they are informed of their payoff after each round and update their beliefs accordingly using the rules described in section \ref{sub:the_agents}.
+In either case, they are informed of their payoff after each round and update their beliefs accordingly using one of the rules described in section \ref{sub:the_agents}.
 
@@
 
-\[
+\begin{equation}
 D(\Theta|\alpha)=\frac{\Gamma(\sum_{i=1}^{k}\alpha_{i})}{\prod_{i=1}^{k}\Gamma(\alpha_{i})}\overset{k}{\underset{i=1}{\prod}\Theta_{i}^{\alpha_{i-1}}}
-\]
+\end{equation}
 
@@
 decision rule is used in this instance, because of the requirement
-for women to evaluate more than two `prospects'.\footnote{Where a prospect is a payoff-probability pair, with the set of prospects for an action defining the possible outcomes for it.} \ac{CPT} uses transformed probabilities, underweighting
+for women to evaluate the `prospects'\footnote{Where a prospect is a payoff-probability pair, with the set of prospects for an action defining the possible outcomes for it.} of more than two actions.
+\ac{CPT} uses transformed probabilities, underweighting
 small probabilities, and overweighting large ones.

### 2015-01-08 SensitivityAnalysis.tex
Minor tweaks

@@
 \end{tabular}
-\caption[Table caption text]{Median moderate drinker signalling parameter sensitivity. \label{tab:sa_results_sig}}
+\caption[Table caption text]{Median moderate drinker signalling parameter sensitivity \label{tab:sa_results_sig}}
 \end{table}
@@
 \end{tabular}
-\caption[Table caption text]{Median moderate drinker signalling emulator statistics. \label{tab:sa_emulator_sig}}
+\caption[Table caption text]{Median moderate drinker signalling emulator statistics \label{tab:sa_emulator_sig}}
 \end{table}
@@
 \end{tabular}
-\caption[Table caption text]{Median between groups IQR parameter sensitivity. \label{tab:sa_results_iqr}}
+\caption[Table caption text]{Median between groups IQR parameter sensitivity \label{tab:sa_results_iqr}}
 \end{table}
@@
 \end{tabular}
-\caption[Table caption text]{Median between groups IQR emulator statistics. \label{tab:sa_emulator_iqr}}
+\caption[Table caption text]{Median between groups IQR emulator statistics \label{tab:sa_emulator_iqr}}
 \end{table}
@@
 \end{tabular}
-\caption[Table caption text]{IQR of median moderate drinker signalling parameter sensitivity. \label{tab:sa_results_sig_iqr}}
+\caption[Table caption text]{IQR of median moderate drinker signalling parameter sensitivity \label{tab:sa_results_sig_iqr}}
 \end{table}
@@
 \end{tabular}
-\caption[Table caption text]{IQR of median between groups IQR emulator statistics. \label{tab:sa_emulator_sig_iqr}}
+\caption[Table caption text]{IQR of median between groups IQR emulator statistics \label{tab:sa_emulator_sig_iqr}}
 \end{table}
@@
 \end{tabular}
-\caption[Table caption text]{IQR of median between groups IQR parameter sensitivity. \label{tab:sa_results_iqr_iqr}}
+\caption[Table caption text]{IQR of median between groups IQR parameter sensitivity \label{tab:sa_results_iqr_iqr}}
 \end{table}
@@
 \end{tabular}
-\caption[Table caption text]{IQR of median between groups IQR emulator statistics. \label{tab:sa_emulator_iqr_iqr}}
+\caption[Table caption text]{IQR of median between groups IQR emulator statistics \label{tab:sa_emulator_iqr_iqr}}
 \end{table}

### 2015-02-23 Methods.tex
Footnote, formula typo

@@
 \cite{Neilson2002,Nilsson2011,Glockner2012}, and particularly \citet{Byrnes1999} and \citet{Booij2009} addressing risk aversion and gender), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work.
-For simplicity, it was assumed that all three drinking types are equally prevalent within the population, although results derived from \ac{ALSPAC} suggest that the reality is far more positive \citep{Humphriss2013}.
+For simplicity, it was assumed that all three drinking types are equally prevalent within the population, although results derived from \ac{ALSPAC} suggest that the reality is far more positive\footnote{95.5\% of women in the sample reported consumption at, or below, \ac{NICE} recommended safe levels.} \citep{Humphriss2013}.
 The scenario was biased towards disclosure as the better option by presuming a distribution of midwives strongly skewed towards non-judgemental types, with beliefs initially favouring honesty.

### 2015-06-02 Background.tex
Reflecting reviewers comments

@@
 Taken literally, this leads to normative decision theory, where the focus is on giving the rational answer to a decision problem.
-An complementary view - descriptive, or behavioural decision theory, holds that the focus should instead be on giving an account of human decision making performance, complete with observed deviations from perfect rationality, which we address in section \ref{sub:descriptive_theories}.
+A complementary view - descriptive, or behavioural decision theory, holds that the focus should instead be on giving an account of human decision making performance, complete with observed deviations from perfect rationality, which we address in section \ref{sub:descriptive_theories}.
 Finally a third perspective, which to some extent overlaps this division, suggests that decisions are heuristic in nature and rational in ecological context \citep{Gigerenzer1996} (section \ref{sub:heuristic_theories}).

### 2015-06-02 Introduction.tex
Reflecting reviewers comments

@@
 
-Turning more specifically to disclosure of alcohol use during pregnancy, research is relatively sparse, although qualitative trends are reported by \citet{Phillips2007} and \citet{Alvik2006}.
-The former explored factors impacting disclosure through a small case study, highlighting the need to build up rapport over several appointments; the latter compared post partum reports of consumption with contemporaneous accounts, finding apparent underreporting during pregnancy which was amplified by increased drinking.
+Turning more specifically to disclosure of alcohol use by women during their pregnancy, research is relatively sparse, although qualitative trends are reported by \citet{Phillips2007} and \citet{Alvik2006}.
+The former explored factors impacting disclosure through a small case study, highlighting the need to build up rapport between woman and midwife over several appointments; the latter compared post partum reports of consumption with contemporaneous accounts, finding apparent underreporting during pregnancy which was amplified by increased drinking.
 The simulation model described in this paper is able to replicate both qualitative trends, i.e.
@@
 
-The resulting scenario is of substantial independent interest, and shows the potential utility of a simulation approach in arenas where \acp{RCT} are not viable for ethical, or financial reasons.
+The resulting scenario is of substantial independent interest, and shows the potential utility of a simulation approach in arenas where randomized control trials are not viable for ethical, or financial reasons.
 With this said, the lack of a strong quantitative evidence base against which to validate the behaviour of the model augers for caution in interpreting the results, and a necessary reminder that in this instance the model is primarily a tool for formalisation of the thought process \citep{epstein2008}, rather than a machine for predicting.
@@
 Many key aspects common to decision rules, for example the idea that a common currency is used by the brain to compare outcomes \citep{Padoa-Schioppa2006,Padoa-Schioppa2008}, are supported by neurological findings.
-In addition, decision rules represent a pleasingly parsimonious alternative to explicit behavioural rules covering all possible eventualities.
+In addition, a single decision rule represents a pleasingly parsimonious alternative to numerous case specific production rules.
 

### 2015-06-02 Model.tex
Footnote, formula typo
Reflecting reviewers comments

@@
 
-Typically in the UK, a women will have 12 appointments with a midwife during the antenatal period.
-Outside of caseloading\footnote{Under a caseloading system, women are allocated an individual, or small group of midwives who deal with their care throughout pregnancy, and birth.} teams, a woman does not generally have a named midwife, and may see a different practitioner at each appointment.
+Typically in the UK, a women will have 12 appointments with a midwife during the antenatal period, and in the majority of cases will encounter several different midwives \citep{Redshaw2014} in the course of their care.
 In the UK, and unlike most healthcare scenarios, maternity notes are held by the patient, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously.
@@
 In order to translate the scenario sketched above into a more abstract, tractable form, we cast it as a signalling game, and assume that women's disclosures (or not), are signals.
-We also make the simplifying assumption that a woman may have one of only three drinking patterns - light, moderate, or heavy.
+We also make the simplifying assumption that a woman may have one of only three drinking patterns - light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy.
 Correspondingly, they are limited in what signals they may send when claiming to be one of these three types.
@@
 Table \ref{tab:Payoff-matrix} shows the three payoff matrices which together describe the game.
-
-Taken together, this leads to a game tree that is relatively complex (figure \ref{fig:simple_tree} shows a simplified representation, with a detailed view of one branch in figure \ref{fig:zoom_tree}) even at the subgame level.
-Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversarial risk analysis \citep{RiosInsua2009}.
-This effectively translates the game to a pair of decision problems (figure \ref{fig:decision_problems}), which agents attempt to resolve at each turn using a simple decision rule, given their prior beliefs and experience of play.
-
-\begin{figure}[H]
-\begin{adjustbox}{center}
-\includegraphics[width=119mm]{figures/rounded_clover_infosets}
-\end{adjustbox}
-\caption{Simplified game tree.
-Arrows correspond to two moves by nature, followed by women, and midwives respectively.
-Line weight distinguishes between information sets, and possible moves, corresponding to ascending player types.
-For midwives, referral is shown by a heavier arrow.
-Light terminal nodes indicate that the game may repeat from that point, and black nodes are exits}
-
-\label{fig:simple_tree}
-\end{figure}
-
-\begin{figure}[H]
-\begin{adjustbox}{center}
-\includegraphics[width=119mm]{figures/tree_zoom}
-\end{adjustbox}
-\caption{Detail view of a single game tree branch, showing the possible moves by each player, with information sets for midwives}
-
-\label{fig:zoom_tree}
-\end{figure}
-
-\begin{figure}[H]
-\begin{adjustbox}{center}\subfloat[Women (heavy drinkers)]{\includegraphics[width=119mm]{figures/women_influence}}\end{adjustbox}
-\vskip
-\begin{adjustbox}{center}\subfloat[Midwives]{\includegraphics[width=119mm]{figures/mw_influence}}\end{adjustbox}
-\caption{Influence diagrams, showing the game broken into two decision problems. Squares indicate a decision node, while circles are (from the perspective of the agent) chance nodes}
-
-\label{fig:decision_problems}
-\end{figure}
-
-%Might belong in a more methody bit? Read some stuff to check..
-To formally define the game, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\).
-Here, \(\{l, m, h\}\) correspond to light, moderate, and heavy alcohol consumption for women, and non-judgemental, moderately judgemental, and harshly judgemental for midwives.
-Midwives' pure strategies \(\{r,n\}\) are to refer, or do nothing, and those for women are to signal that they have one of the possible drinking patterns.
-Additionally define two utility functions - 
-\begin{equation}
-u_{w}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}},
-\end{equation} 
-\begin{equation}
-u_{m}(s_{w}, s_{m}, \theta_{w})=X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}},
-\end{equation} with $X_{c}$, $X_{h}$, and $X_{s}$ being the payoff matrices as in table \ref{tab:Payoff-matrix}, $s_{w}$ and $s_{m}$ denoting a specific signal by a woman, and referral response by a midwife.
-Lastly let \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\) be distributions over types of women, and midwives respectively.
-
-As noted, rather than solve the game, we allow populations of agents to play it, and hence stipulate further that women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)).
-They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred, and a new player is drawn from the same distribution that produced the original players to replace them.
-If they are not referred, they rejoin the back of the queue after their appointment.
-In either case, they are informed of their payoff after each round and update their beliefs accordingly using one of the rules described in section \ref{sub:the_agents}.
-
-Midwives play for \(r_{m}\) rounds (\(r_{m}=1000\) in all experiments), and conduct appointments in parallel, i.e.
-if there are 5 midwives, then five women are drawn from the queue and assigned at random to the midwives.
-Unlike women, midwives are only informed of their payoff if they choose to make a referral.
-Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.
 
@@
 \end{table}
+
+Taken together, this leads to a game tree that is relatively complex (figure \ref{fig:simple_tree} shows a simplified representation, with a detailed view of one branch in figure \ref{fig:zoom_tree}) even at the subgame level.
+Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversarial risk analysis \citep{RiosInsua2009}.
+This effectively translates the game to a pair of decision problems (figure \ref{fig:decision_problems}), which agents attempt to resolve at each turn using a simple decision rule, given their prior beliefs and experience of play.
+
+\begin{figure}[H]
+\begin{adjustbox}{center}
+\includegraphics[width=119mm]{figures/rounded_clover_infosets}
+\end{adjustbox}
+\caption{Simplified game tree.
+Arrows correspond to two moves by nature, followed by women, and midwives respectively.
+Line weight distinguishes between information sets, and possible moves, corresponding to ascending player types.
+For midwives, referral is shown by a heavier arrow.
+Light terminal nodes indicate that the game may repeat from that point, and black nodes are exits}
+
+\label{fig:simple_tree}
+\end{figure}
+
+\begin{figure}[H]
+\begin{adjustbox}{center}
+\includegraphics[width=119mm]{figures/tree_zoom}
+\end{adjustbox}
+\caption{Detail view of a single game tree branch, showing the possible moves by each player, with information sets for midwives}
+
+\label{fig:zoom_tree}
+\end{figure}
+
+\begin{figure}[H]
+\begin{adjustbox}{center}\subfloat[Women (heavy drinkers)]{\includegraphics[width=119mm]{figures/women_influence}}\end{adjustbox}
+\vskip
+\begin{adjustbox}{center}\subfloat[Midwives]{\includegraphics[width=119mm]{figures/mw_influence}}\end{adjustbox}
+\caption{Influence diagrams, showing the game broken into two decision problems. Squares indicate a decision node, while circles are (from the perspective of the agent) chance nodes}
+
+\label{fig:decision_problems}
+\end{figure}
+
+%Might belong in a more methody bit? Read some stuff to check..
+To formally define the game, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\).
+Here, \(\{l, m, h\}\) correspond to light, moderate, and heavy alcohol consumption for women, and non-judgemental, moderately judgemental, and harshly judgemental for midwives.
+Midwives' pure strategies \(\{r,n\}\) are to refer, or do nothing, and those for women are to signal that they have one of the possible drinking patterns.
+Additionally define two utility functions - 
+\begin{equation}
+u_{w}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}}
+\end{equation} 
+\begin{equation}
+u_{m}(s_{w}, s_{m}, \theta_{w})=X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}},
+\end{equation} with $X_{c}$, $X_{h}$, and $X_{s}$ being the payoff matrices as in table \ref{tab:Payoff-matrix}, $s_{w}$ and $s_{m}$ denoting a specific signal by a woman, and referral response by a midwife.
+Lastly let \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\) be distributions over types of women, and midwives respectively.
+
+As noted, rather than solve the game, we allow populations of agents to play it, and hence stipulate further that women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)).
+They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred, and a new player is drawn from the same distribution that produced the original players to replace them.
+If they are not referred, they rejoin the back of the queue after their appointment.
+In either case, they are informed of their payoff after each round and update their beliefs accordingly using one of the rules described in section \ref{sub:the_agents}.
+
+Midwives play for \(r_{m}\) rounds (\(r_{m}=1000\) in all experiments), and conduct appointments in parallel, i.e.
+if there are 5 midwives, then five women are drawn from the queue and assigned at random to the midwives.
+Unlike women, midwives are only informed of their payoff if they choose to make a referral.
+Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.
 

### 2015-06-02 Model.tex
Make it clearer that the 'health payoff' is common interest
And hopefully why

@@
 
-At the end of a game, each player receives a payoff dependent on the actions and types of both players, which has a partially common interest component.
-Women receive a payoff based on the health of their eventual baby, with a social cost dependent on the signal they sent and the midwife's reaction to it.
-Midwives receive the same health payoff as the women, but pay a cost for referring to a specialist, mirroring the organisational cost of non-routine care.
+At the end of a game, each player receives a payoff dependent on the actions and types of both players.
+Because both women and midwives have an interest in the outcome of the pregnancy, and would prefer a healthy baby, the payoff has a common interest component.
+Hence, both players receive a payoff based on the health of their eventual baby, but women bear a social cost dependent on the signal they sent and the midwife's reaction to it.
+Similarly, midwives pay a cost if they refer to a specialist, mirroring the organisational cost of non-routine care.
 Table \ref{tab:Payoff-matrix} shows the three payoff matrices which together describe the game.

### 2015-06-02 Model.tex
Make women's beliefs clearer

@@
 Because both women and midwives have an interest in the outcome of the pregnancy, and would prefer a healthy baby, the payoff has a common interest component.
-Hence, both players receive a payoff based on the health of their eventual baby, but women bear a social cost dependent on the signal they sent and the midwife's reaction to it.
+Hence, both players receive a payoff based on the outcome of pregnancy, but women bear a social cost dependent on the signal they sent and the midwife's reaction to it.
 Similarly, midwives pay a cost if they refer to a specialist, mirroring the organisational cost of non-routine care.
@@
 As a result, they have homogeneous beliefs about  women and assume to some extent that they are honest.
-Women are heterogeneous in their prior observations, which are assigned stochastically and constrained such that they have encountered each scenario possible for their type at least once, with exactly \(k\) encounters overall.
+Women have heterogeneous beliefs, which correspond to experiencing \(k\) randomly chosen paths through the game, and following each path at least once.
 

### 2015-06-02 Introduction.tex
Added a footnote to intro explaining signalling games

@@
 In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, tending to be a reflection of the assumptions of the modeller rather than empirically or theoretically grounded \citep{Waldherr2013}.
-To ameliorate this concern, we draw on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game \citep{Kreps1987} with a basic form of intragroup information sharing.
+To ameliorate this concern, we draw on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game\footnote{In a signalling game, on player, the signaller, has some piece of information that is known only to them which affects the outcome of the game for both players.
+The signaller has a choice as to what they tell the other player about this hidden information, and the responding player as to what they believe the information to be.} \citep{Kreps1987} with a basic form of intragroup information sharing.
 Four decision models of varying complexity, and behavioural plausibility are contrasted, by way of demonstrating the significance of the operationalisation of decision making in \ac{ABM}.

### 2015-06-02 Model.tex
Added an example of the strategic difficulty

@@
 Taken together, this leads to a game tree that is relatively complex (figure \ref{fig:simple_tree} shows a simplified representation, with a detailed view of one branch in figure \ref{fig:zoom_tree}) even at the subgame level.
+
+As an example, consider the challenge faced by an agent of the heavy drinking type.
+In order to get the best health outcome, they must be referred and would ideally achieve this without paying any social cost at all.
+The best move depends on the type, and beliefs of the midwife.
+For example, a particularly unlucky scenario might be for the midwife to not only be of a harshly judgemental disposition, but to believe that no women really need to be referred.
+
 Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversarial risk analysis \citep{RiosInsua2009}.

### 2015-06-02 Model.tex
Add lexicographic eg

@@
 For example, a particularly unlucky scenario might be for the midwife to not only be of a harshly judgemental disposition, but to believe that no women really need to be referred.
+Even a relatively weak belief in this possibility can make the honest signal look like an unwarranted risk.
 
@@
 \end{algorithm}
+
+As an example, take a light drinker who has played three rounds, signalling honestly in two and claiming to be a moderate drinker in one, where they encountered a particularly judgemental midwife.
+The most common outcome of the honest signal was a payoff of 10, which is clearly preferable to the 9 gained by claiming to be moderate.
+On that basis, they choose to signal honestly.
 

### 2015-06-02 Model.tex
Add simple bayes e.g.

@@
 
+If we take our light drinker from the lexicographic case, and assume that they began with an uninformative prior.
+The 6 possible signal-payoffs pairings are then \([(l,10),(m,10),(h,10),(m,9),(h,9),(h,8)]\), with \(\alpha_{i}=1\) for all \(i\).
+After playing the three rounds, \(n_{l,10}=2\), and \(n_{m,9}=1\).
+
+The agent then evaluates \(R_{w}\) for each signal, e.g. for the light signal:
+
+\begin{equation*}
+\begin{align*}
+X &= \{10\}\\
+R_{w}(l) &= \sum_{x \in X} -xp(x | l) &= -10p(10 | l)\\
+R_{w}(l) &= -10(\frac{\alpha_{l,10}+n_{l,10}}{\sum_{j}(\alpha_{j}+n_{j})}) &= -10(\frac{1+2}{1+2})\\
+R_{w}(l) &= -10(\frac{3}{3}) &= -10
+\end{align}
+\end{equation}
+
+and by the same method, \(R_{w}(m)=-7\), and \(R_{w}(h)=-9\), concluding that signalling honestly is the best move.
+
 \subsubsection{Bayesian Risk Minimisation}
@@
 \begin{equation}
-R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{w}(s_{w}, s_{m}, i)p(i | s_{w})
+R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{m}(s_{w}, s_{m}, i)p(i | s_{w})
+\end{equation}
+
+Returning to our example agent, we now add slightly more information, and stipulate that they have in fact encountered a harshly judgemental midwife in all three rounds, hence \(n_{h}=3\).
+Their prior beliefs remain uninformative, i.e.
+\(\alpha_{j} = 1, j \in \{l,m,h\}\), \(\alpha_{i}=1,i \in \{r,n\}\).
+As before, the agent evaluates \(R_{w}\) for the three signals, and the process for the light signal is given below -
+
+\begin{equation*}
+\begin{align*}
+R_{w}(s_{w}, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, l, j)p(j)p(i | s_{w}),
+R_{w}(s_{w}, l) &= 
+\end{align}
 \end{equation}

### 2015-06-02 Model.tex
Add bayes e.g.

@@
 
-As an example, take a light drinker who has played three rounds, signalling honestly in two and claiming to be a moderate drinker in one, where they encountered a particularly judgemental midwife.
+As an example, take a light drinker who has played three rounds with a succession of particularly judgemental midwives, signalling honestly in two and claiming to be a moderate drinker in one.
 The most common outcome of the honest signal was a payoff of 10, which is clearly preferable to the 9 gained by claiming to be moderate.
@@
 
-Returning to our example agent, we now add slightly more information, and stipulate that they have in fact encountered a harshly judgemental midwife in all three rounds, hence \(n_{h}=3\).
+Returning to our example agent, under this model the type of the midwife becomes salient, hence \(n_{h}=3\).
 Their prior beliefs remain uninformative, i.e.
@@
 \begin{align*}
-R_{w}(s_{w}, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, l, j)p(j)p(i | s_{w}),
-R_{w}(s_{w}, l) &= 
+R_{w}(l, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(l, i, l, j)p(j)p(i | l)\\
+R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l) \\- u_{w}(l, r, l, m)p(m)p(r | l) - u_{w}(l, n, l, m)p(m)p(n | l) \\- u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
+R_{w}(l, l) &= -10p(l)p(r | l) - 10p(l)p(n | l) \\- 10p(m)p(r | l) - 10p(m)p(n | l) \\- 10p(h)p(r | l) - 10p(h)p(n | l)\\
+p(l) &= \frac{1 + 0}{1 + 1 + 1 + 3} &= \frac{1}{6}\\
+p(m) &= \frac{1 + 0}{1 + 1 + 1 + 3} &= \frac{1}{6}\\
+p(h) &= \frac{1 + 3}{1 + 1 + 1 + 3} &= \frac{2}{3}\\
+p(r | l) &= \frac{1 + 0}{1 + 1 + 2} &= \frac{1}{4}\\
+p(n | l) &= \frac{1 + 2}{1 + 1 + 2} &= \frac{3}{4}\\
+WRONGWRONGWRONGWRONGWRONGR_{w}(l, l) &= -\frac{1}{3} - \frac{4}{3} - \frac{1}{3} - \frac{4}{3} - \frac{4}{3} - \frac{16}{3}\\
+R_{w}(l, l) &= -10
 \end{align}
 \end{equation}
+
+and similarly for moderate (\(R_{w}(m,l)=-9\frac{1}{3}\)), and heavy (\(R_{w}(h,l)=-\frac{1}{2}\)) signals, once again concluding that honesty is the better option.
 

### 2015-06-02 Model.tex
Correct Bayes eg

--- 2015-06-02 Model.tex
@@
 
-Returning to our example agent, we now add slightly more information, and stipulate that they have in fact encountered a harshly judgemental midwife in all three rounds, hence \(n_{h}=3\).
+Returning to our example agent, under this model the type of the midwife becomes salient, hence \(n_{h}=3\), and \(n_{l,n}=2\), \(n_{m,n}=1\).
 Their prior beliefs remain uninformative, i.e.
-\(\alpha_{j} = 1, j \in \{l,m,h\}\), \(\alpha_{i}=1,i \in \{r,n\}\).
+\(\alpha_{j} = 1, j \in \{l,m,h\}\), \(\alpha_{i,j}=1,i \in \{r,n\}, j \in \{l,m,h\}\).
 As before, the agent evaluates \(R_{w}\) for the three signals, and the process for the light signal is given below -
@@
 \begin{align*}
-R_{w}(s_{w}, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, l, j)p(j)p(i | s_{w}),
-R_{w}(s_{w}, l) &= 
+R_{w}(l, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(l, i, l, j)p(j)p(i | l)\\
+R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l) - u_{w}(l, r, l, m)p(m)p(r | l) - u_{w}(l, n, l, m)p(m)p(n | l) - u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
+R_{w}(l, l) &= -10p(l)p(r | l) - 10p(l)p(n | l) - 10p(m)p(r | l) - 10p(m)p(n | l) - 10p(h)p(r | l) - 10p(h)p(n | l)\\
+p(l) &= \frac{1 + 0}{1 + 1 + 1 + 3} &= \frac{1}{6}\\
+p(m) &= \frac{1 + 0}{1 + 1 + 1 + 3} &= \frac{1}{6}\\
+p(h) &= \frac{1 + 3}{1 + 1 + 1 + 3} &= \frac{2}{3}\\
+p(r | l) &= \frac{1 + 0}{1 + 1 + 2} &= \frac{1}{4}\\
+p(n | l) &= \frac{1 + 2}{1 + 1 + 2} &= \frac{3}{4}\\
+R_{w}(l, l) &= -10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} 10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{2}{3} \cdot \frac{1}{4} - 10\cdot \frac{2}{3} \cdot \frac{3}{4}\\
+R_{w}(l, l) &= -10
 \end{align}
 \end{equation}
+
+and similarly for moderate (\(R_{w}(m,l)=-9\frac{1}{3}\)), and heavy (\(R_{w}(h,l)=-\frac{1}{2}\)) signals, once again concluding that honesty is the better option.
 

### 2015-06-04 Model.tex
Bayes eg final
Fix eqn endings
Added CPT eg

@@
 R_{w}(l) &= -10(\frac{3}{3}) &= -10
-\end{align}
-\end{equation}
+\end{align*}
+\end{equation*}
 
@@
 R_{w}(l, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(l, i, l, j)p(j)p(i | l)\\
-R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l) - u_{w}(l, r, l, m)p(m)p(r | l) - u_{w}(l, n, l, m)p(m)p(n | l) - u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
+R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l) - u_{w}(l, r, l, m)p(m)p(r | l) - u_{w}(l, n, l, m)p(m)p(n | l) \\
+&\phantom{{}=1}- u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
+u_{w}(l, i, l, j) &= 10\\
 R_{w}(l, l) &= -10p(l)p(r | l) - 10p(l)p(n | l) - 10p(m)p(r | l) - 10p(m)p(n | l) - 10p(h)p(r | l) - 10p(h)p(n | l)\\
@@
 p(n | l) &= \frac{1 + 2}{1 + 1 + 2} &= \frac{3}{4}\\
-R_{w}(l, l) &= -10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} 10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{2}{3} \cdot \frac{1}{4} - 10\cdot \frac{2}{3} \cdot \frac{3}{4}\\
+R_{w}(l, l) &= -10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{2}{3} \cdot \frac{1}{4} - 10\cdot \frac{2}{3} \cdot \frac{3}{4}\\
 R_{w}(l, l) &= -10
-\end{align}
-\end{equation}
+\end{align*}
+\end{equation*}
 
@@
 
+Once again, we return to the light drinker example.
+The inferential aspects are identical with the more complex Bayesian risk minimisation algorithm, hence \(p(j)p(i | l)\), and \(u_{w}(l, i, l, j)\) remain the same, but the agent additionally calculates $v(u_{w}(l, i, l, j))w^{+}(p(j)p(i | l))$.
+For the \ac{CPT} parameters, the values are those originally given by \citet{Tversky1992} and used in the actual simulations which are given fully in table \ref{tab:qt_params}.
+
+\begin{equation*}
+\begin{align*}
+\alpha &= 0.88\\
+\gamma &= 0.61\\
+p(l) &= \frac{1}{6}\\
+p(m) &= \frac{1}{6}\\
+p(h) &= \frac{2}{3}\\
+p(r | l) &= \frac{1}{4}\\
+p(n | l) &= \frac{3}{4}\\
+u_{w}(l, i, l, j) &= 10\\
+v(u_{w}) &= f(u_{w}) &= u_{w}^\alpha\\
+v(u_{w}) &= 10^{0.88} &= 7.59\\
+w^{+}(p(l)p(r | l))  &= \frac{(p(l)p(r | l))^\gamma}{[(p(l)p(r | l))^\gamma + (1-(p(l)p(r | l)))^\gamma]^\frac{1}{\gamma}}\\
+w^{+}(p(l)p(r | l))  &= \frac{\frac{1}{24}^{0.61}}{[\frac{1}{24}^{0.61} + (1-\frac{1}{24})^{0.61}]^\frac{1}{0.61}} &= 0.12\\
+w^{+}(p(l)p(n | l)) &= \frac{\frac{1}{8}^{0.61}}{[\frac{1}{8}^{0.61} + (1-\frac{1}{8})^{0.61}]^\frac{1}{0.61}} &= 0.21\\
+w^{+}(p(m)p(r | l)) &= 0.12
+w^{+}(p(m)p(n | l)) &= 0.21
+w^{+}(p(h)p(r | l)) &= 0.24
+w^{+}(p(h)p(n | l)) &= 0.42
+V(l) &= 0.12\cdot7.59 + 0.21\cdot7.59 + 0.12\cdot7.59 + 0.21\cdot7.59 + 0.24\cdot7.59 + 0.42\cdot7.59 &= 10.02
+\end{align*}
+\end{equation*}
+
 \subsection{Information Sharing}

### 2015-06-04 Model.tex
Add CPT eg to ipython
And start correcting missing part of CPT in paper

--- 2015-06-02 Model.tex
@@
 R_{w}(l, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(l, i, l, j)p(j)p(i | l)\\
-R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l) - u_{w}(l, r, l, m)p(m)p(r | l) - u_{w}(l, n, l, m)p(m)p(n | l) - u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
+R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l) - u_{w}(l, r, l, m)p(m)p(r | l) - u_{w}(l, n, l, m)p(m)p(n | l) \\
+&\phantom{{}=1}- u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
+u_{w}(l, i, l, j) &= 10\\
 R_{w}(l, l) &= -10p(l)p(r | l) - 10p(l)p(n | l) - 10p(m)p(r | l) - 10p(m)p(n | l) - 10p(h)p(r | l) - 10p(h)p(n | l)\\
-p(l) &= \frac{1 + 0}{1 + 1 + 1 + 3} &= \frac{1}{6}\\
-p(m) &= \frac{1 + 0}{1 + 1 + 1 + 3} &= \frac{1}{6}\\
-p(h) &= \frac{1 + 3}{1 + 1 + 1 + 3} &= \frac{2}{3}\\
-p(r | l) &= \frac{1 + 0}{1 + 1 + 2} &= \frac{1}{4}\\
-p(n | l) &= \frac{1 + 2}{1 + 1 + 2} &= \frac{3}{4}\\
-R_{w}(l, l) &= -10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} 10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{2}{3} \cdot \frac{1}{4} - 10\cdot \frac{2}{3} \cdot \frac{3}{4}\\
+p(l) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
+p(m) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
+p(h) &= \frac{1 + 3}{1 + 1 + 1 + 3} = \frac{2}{3}\\
+p(r | l) &= \frac{1 + 0}{1 + 1 + 2} = \frac{1}{4}\\
+p(n | l) &= \frac{1 + 2}{1 + 1 + 2} = \frac{3}{4}\\
+R_{w}(l, l) &= -10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{2}{3} \cdot \frac{1}{4} - 10\cdot \frac{2}{3} \cdot \frac{3}{4}\\
 R_{w}(l, l) &= -10
-\end{align}
-\end{equation}
+\end{align*}
+\end{equation*}
 
@@
 decision rule is used in this instance, because of the requirement
-for women to evaluate the `prospects'\footnote{Where a prospect is a payoff-probability pair, with the set of prospects for an action defining the possible outcomes for it.} of more than two actions.
+for women to evaluate the `prospects'\footnote{Where a prospect is a sequence of payoff-probability pairings in ascending order of payoff, associated with an action.} of more than two actions.
 \ac{CPT} uses transformed probabilities, underweighting
@@
 and $\alpha$, and $\beta$ are respectively the power of a gain,
-and a loss, and \(\lambda\) is a multiplier giving the aversion to loss. The \ac{CPT} value of outcome $u_{i}$, occurring with probability \(p\) is $v(u_{i})w^{+}(p)$
-if $u_{i}\geq0$, and $v(u_{i})w^{-}(p)$ otherwise. For any given action the \ac{CPT}
+and a loss, and \(\lambda\) is a multiplier giving the aversion to loss.
+
+Finally, the transformed probabilities are used to construct decision weights, \(\pi^{+},\pi^{-}\) for losses and gains, where,
+
+\begin{equation}
+\pi_{n}^{+}=w^{+}(p_{n})
+\end{equation}
+\begin{equation}
+\pi_{-m}^{-}=w^{-}(p_{-m})
+\end{equation}
+\begin{equation}
+\pi_{i}^{+}=w^{+}(p_{i}+\ldots+p_{n}) - w^{+}(p_{i+1}+\ldots+p_{n}),0\leq i \leq n - 1
+\end{equation}
+\begin{equation}
+\pi_{i}^{-}=w^{-}(p_{-m}+\ldots+p_{i}) - w^{-}(p_{-m}+\ldots+p_{i-1}),1-m\leq i \leq 0
+\end{equation}
+
+The \ac{CPT} value of outcome $u_{i}$, occurring with probability \(p\) is $v(u_{i})\pi^{+}(p_{i})$
+if $u_{i}\geq0$, and $v(u_{i})\pi^{-}(p_{i})$ otherwise. For any given action the \ac{CPT}
 value is the sum of the value of the prospects of that action, as
 in the Bayesian risk model, and the agent chooses the option which maximises this quantity.
+
+Once again, we return to the light drinker example.
+The inferential aspects are identical with the more complex Bayesian risk minimisation algorithm, hence \(p(j)p(i | l)\), and \(u_{w}(l, i, l, j)\) remain the same, but the agent additionally calculates $v(u_{w}(l, i, l, j))w^{+}(p(j))w^{+}(p(i | l))$.
+For the \ac{CPT} parameters, the values are those originally given by \citet{Tversky1992} and used in the actual simulations which are given fully in table \ref{tab:qt_params}.
+
+\begin{equation*}
+\begin{align*}
+\alpha &= 0.88\\
+\gamma &= 0.61\\
+p(l) &= \frac{1}{6}\\
+p(m) &= \frac{1}{6}\\
+p(h) &= \frac{2}{3}\\
+p(r | l) &= \frac{1}{4}\\
+p(n | l) &= \frac{3}{4}\\
+u_{w}(l, i, l, j) &= 10\\
+v(u_{w}) &= f(u_{w}) = u_{w}^\alpha\\
+v(u_{w}) &= 10^{0.88} = 7.59\\
+w^{+}(p(l)p(r | l))  &= \frac{(p(l)p(r | l))^\gamma}{[(p(l)p(r | l))^\gamma + (1-(p(l)p(r | l)))^\gamma]^\frac{1}{\gamma}}\\
+w^{+}(p(l)p(r | l))  &= \frac{\frac{1}{24}^{0.61}}{[\frac{1}{24}^{0.61} + (1-\frac{1}{24})^{0.61}]^\frac{1}{0.61}} = 0.12\\
+w^{+}(p(l)p(n | l)) &= \frac{\frac{1}{8}^{0.61}}{[\frac{1}{8}^{0.61} + (1-\frac{1}{8})^{0.61}]^\frac{1}{0.61}} = 0.21\\
+w^{+}(p(m)p(r | l)) &= 0.12\\
+w^{+}(p(m)p(n | l)) &= 0.21\\
+w^{+}(p(h)p(r | l)) &= 0.24\\
+w^{+}(p(h)p(n | l)) &= 0.42\\
+V(l) &= 0.12\cdot7.59 + 0.21\cdot7.59 + 0.12\cdot7.59 + 0.21\cdot7.59 + 0.24\cdot7.59 + 0.42\cdot7.59 &= 10.02
+\end{align*}
+\end{equation*}
 

### 2015-06-04 Model.tex
Corrected CPT forumulas and e.g.

@@
 
-The \ac{CPT} value of outcome $u_{i}$, occurring with probability \(p\) is $v(u_{i})\pi^{+}(p_{i})$
+The \ac{CPT} value of a single outcome prospect \(f=(u_{i};p_{i})\), is $v(u_{i})\pi^{+}(p_{i})$
 if $u_{i}\geq0$, and $v(u_{i})\pi^{-}(p_{i})$ otherwise. For any given action the \ac{CPT}
-value is the sum of the value of the prospects of that action, as
+value, \(V\) is the sum of the value of the prospects of that action, as
 in the Bayesian risk model, and the agent chooses the option which maximises this quantity.
@@
 u_{w}(l, i, l, j) &= 10\\
+f&=(10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{6},10;\frac{1}{2})\\
+f^{+}&=f,f^{-}=()\\
+n &= 5\\
 v(u_{w}) &= f(u_{w}) = u_{w}^\alpha\\
 v(u_{w}) &= 10^{0.88} = 7.59\\
-w^{+}(p(l)p(r | l))  &= \frac{(p(l)p(r | l))^\gamma}{[(p(l)p(r | l))^\gamma + (1-(p(l)p(r | l)))^\gamma]^\frac{1}{\gamma}}\\
-w^{+}(p(l)p(r | l))  &= \frac{\frac{1}{24}^{0.61}}{[\frac{1}{24}^{0.61} + (1-\frac{1}{24})^{0.61}]^\frac{1}{0.61}} = 0.12\\
-w^{+}(p(l)p(n | l)) &= \frac{\frac{1}{8}^{0.61}}{[\frac{1}{8}^{0.61} + (1-\frac{1}{8})^{0.61}]^\frac{1}{0.61}} = 0.21\\
-w^{+}(p(m)p(r | l)) &= 0.12\\
-w^{+}(p(m)p(n | l)) &= 0.21\\
-w^{+}(p(h)p(r | l)) &= 0.24\\
-w^{+}(p(h)p(n | l)) &= 0.42\\
-V(l) &= 0.12\cdot7.59 + 0.21\cdot7.59 + 0.12\cdot7.59 + 0.21\cdot7.59 + 0.24\cdot7.59 + 0.42\cdot7.59 &= 10.02
+\pi_{0}^{+}&=w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(1) - w^{+}(\frac{23}{24})\\
+&=0.19\\
+\pi_{1}^{+}&=w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(\frac{23}{24}) - w^{+}(\frac{5}{6})\\
+&= 0.17\\
+\pi_{2}^{+}&=w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(\frac{5}{6}) - w^{+}(\frac{19}{24})\\
+&= 0.04\\
+\pi_{3}^{+}&=w^{+}(\frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{6} + \frac{1}{2})=w^{+}(\frac{19}{24}) - w^{+}(\frac{2}{3})\\
+&= 0.09\\
+\pi_{4}^{+}&=w^{+}(\frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{2})=w^{+}(\frac{2}{3}) - w^{+}(\frac{1}{2})\\
+&= 0.09\\
+\pi_{5}^{+}&=w^{+}(\frac{1}{2})\\
+&= 0.42\\
+V(f) &= V(f^{+}) + V(f^{-}) = V(f^{+}) + 0\\
+V(f^{+}) &= \sum_{i\leqn}\pi_{i}^{+}(f^{+})v_{i}^{+}(f^{+}) = 7.59
 \end{align*}
 \end{equation*}
+
+And as before, following the same process for moderate, and heavy signals which yields respectively 7.14, and 6.22, the agent chooses the higher valued action and sends an honest signal.
 

### 2015-06-04 Background.tex
Explain expected utility in background

@@
 
-The conceptual underpinning of all of these is the central idea of expected utility, originated by \citet{Bernoulli1954} and later formalised by \citet{Neumann1953}, which treats all decisions as gambles defined in terms of payoffs and probabilities.
+The conceptual underpinning of all of these is the central idea of expected utility, originated by \citet{Bernoulli1954} and later formalised by \citet{Neumann1953}, which simply put, states that the worth of an action is the probability of each outcome, multiplied by the subjective gain or loss it delivers.
 

### 2015-06-04 Model.tex
Fix sum notation in CPT eg
Explain expected utility in background

@@
 X &= \{10\}\\
-R_{w}(l) &= \sum_{x \in X} -xp(x | l) &= -10p(10 | l)\\
-R_{w}(l) &= -10(\frac{\alpha_{l,10}+n_{l,10}}{\sum_{j}(\alpha_{j}+n_{j})}) &= -10(\frac{1+2}{1+2})\\
-R_{w}(l) &= -10(\frac{3}{3}) &= -10
+R_{w}(l) &= \sum_{x \in X} -xp(x | l) = -10p(10 | l)\\
+R_{w}(l) &= -10(\frac{\alpha_{l,10}+n_{l,10}}{\sum_{j}(\alpha_{j}+n_{j})}) = -10(\frac{1+2}{1+2})\\
+R_{w}(l) &= -10(\frac{3}{3}) = -10
 \end{align*}
@@
 R_{w}(l, l) &= -10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{2}{3} \cdot \frac{1}{4} - 10\cdot \frac{2}{3} \cdot \frac{3}{4}\\
-R_{w}(l, l) &= -10
+&= -10
 \end{align*}
@@
 \begin{align}
-w^{+}(p) & = & \frac{p^{\gamma}}{(p^{\gamma}+(1-p)^{\gamma})^{\frac{1}{\gamma}}}\label{eqn:cpt_p_pos}\\
-w^{-}(p) & = & \frac{p^{\delta}}{(p^{\delta}+(1-p)^{\delta})^{\frac{1}{\delta}}}\label{eqn:cpt_p_neg},
+w^{+}(p) & = \frac{p^{\gamma}}{(p^{\gamma}+(1-p)^{\gamma})^{\frac{1}{\gamma}}}\label{eqn:cpt_p_pos}\\
+w^{-}(p) & = \frac{p^{\delta}}{(p^{\delta}+(1-p)^{\delta})^{\frac{1}{\delta}}}\label{eqn:cpt_p_neg},
 \end{align}
@@
 V(f) &= V(f^{+}) + V(f^{-}) = V(f^{+}) + 0\\
-V(f^{+}) &= \sum_{i\leqn}\pi_{i}^{+}(f^{+})v_{i}^{+}(f^{+}) = 7.59
+V(f^{+}) &= \sum_{i}^{n}\pi_{i}^{+}(f^{+})v_{i}^{+}(f^{+}) = 7.59
 \end{align*}

### 2015-06-04 Background.tex
Clarify GT -> BGT -> SG in bg

@@
 
-The majority of classical game theory focuses on strategic decision making, in scenarios where all players have complete information about all aspects of the game.
-An alternative, perhaps more common situation, is that players have incomplete information, i.e.
-their knowledge of the state of the world is in some way deficient.
-\citet{Harsanyi1967} introduced the concept of a Bayesian game, resolving the problems introduced by the incomplete information scenario by allowing the possible variations on the rules to be treated as subgames.
+The majority of classical game theory focuses on strategic decision making, in scenarios where all players have complete information about all aspects of the game and their opponents.
+Moves by players are assumed to be perfectly rational, and account for the equally rational moves of their opponents.
+An alternative, perhaps more common situation, is that players have incomplete information, whether about the actions available to their opponents or themselves, or concerning the possible payoffs for the players.
+This second case was essentially unexplored, until \citet{Harsanyi1967} introduced the concept of a Bayesian game, which treats incomplete information scenarios by allowing the possible variations on the rules to be treated as subgames.
 This adds an additional player - nature, to the game, where nature takes the first move thereby deciding which subgame is played.
@@
 
-Here, we are specifically interested in signalling games \citep{Spence1973,Kreps1987}, where one player holds some private information which may be communicated (or not) by means of a signal.
+Here, we are specifically interested in signalling games \citep{Spence1973,Kreps1987}, a type of Bayesian game where one player holds some private information which may be communicated (or not) by means of a signal.
 This basic form has been widely applied, with substantial interest in what conditions permit honest signalling as Nash equilibria or \acp{ESS}.

### 2015-06-12 Model.tex
Typos

@@
 
-and by the same method, \(R_{w}(m)=-7\), and \(R_{w}(h)=-9\), concluding that signalling honestly is the best move.
+and by the same method, \(R_{w}(m)=-9\frac{1}{3}\), and \(R_{w}(h)=-9\), concluding that signalling honestly is the best move.
 
@@
 
-and similarly for moderate (\(R_{w}(m,l)=-9\frac{1}{3}\)), and heavy (\(R_{w}(h,l)=-\frac{1}{2}\)) signals, once again concluding that honesty is the better option.
+and similarly for moderate (\(R_{w}(m,l)=-9\frac{1}{3}\)), and heavy (\(R_{w}(h,l)=-8\frac{1}{2}\)) signals, once again concluding that honesty is the better option.
 

### 2015-06-15 Conclusion.tex
Change info sharing to social learning
Begin moving model description to appendix. Also add an explanation of
pseudo-counts vs priors.

@@
 
-As noted in section \ref{sub:sensitivity}, the impact of information sharing between midwives is surprisingly minimal, where it might be expected to play a more significant role in reality.
+As noted in section \ref{sub:sensitivity}, the impact of social learning in midwives is surprisingly minimal, where it might be expected to play a more significant role in reality.
 A possible explanation for this lies in the implementation, which may place an excessive constraint on how much information midwives can share.

### 2015-06-15 Introduction.tex
Change info sharing to social learning
Begin moving model description to appendix. Also add an explanation of
pseudo-counts vs priors.

@@
 To ameliorate this concern, we draw on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game\footnote{In a signalling game, on player, the signaller, has some piece of information that is known only to them which affects the outcome of the game for both players.
-The signaller has a choice as to what they tell the other player about this hidden information, and the responding player as to what they believe the information to be.} \citep{Kreps1987} with a basic form of intragroup information sharing.
+The signaller has a choice as to what they tell the other player about this hidden information, and the responding player as to what they believe the information to be.} \citep{Kreps1987} with a basic form of intragroup social learning.
 Four decision models of varying complexity, and behavioural plausibility are contrasted, by way of demonstrating the significance of the operationalisation of decision making in \ac{ABM}.
@@
 
-The remainder of this paper proceeds to provide a brief review of the methodological context (section \ref{sec:lit_review}), before outlining the model (section \ref{sec:model}), and experiments (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}).
+The remainder of this paper proceeds to provide a brief review of the methodological context (section \ref{sec:lit_review}), before outlining the proposed approach to model development (section \ref{sec:model}), and experiments (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}).

### 2015-06-15 Methods.tex
Change info sharing to social learning
Begin moving model description to appendix. Also add an explanation of
pseudo-counts vs priors.

@@
 
-In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examined the impact of simple information sharing within the population of women (section \ref{sub:info_sharing}) on the robustness of these trends.
+In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examined the impact of simple social learning within the population of women (section \ref{sub:info_sharing}) on the robustness of these trends.
 The original experiment was repeated at \(q_{w},w_{w}\in \{0.25, 0.5, 0.75, 1 | q_{w}=w_{w}\}\), with 100 runs under each condition.

### 2015-06-15 Results.tex
Change info sharing to social learning
Begin moving model description to appendix. Also add an explanation of
pseudo-counts vs priors.

@@
 
-\subsection{Information Sharing}
+\subsection{Social Learning}
 \label{sub:sharing_results}
 
-Introducing information sharing amongst women leads the behaviour of the decision rules to diverge markedly.
+Introducing social learning amongst women leads the behaviour of the decision rules to diverge markedly.
 Figure \ref{fig:honest_sharing} shows the proportion of women who have signalled honestly at least once by their final appointment, under four sharing conditions.
 Aside from the lexicographic decision rule, the general tendency is towards less honest signalling by heavy drinkers, but figure \ref{fig:ref_sharing} shows a slight increase in referrals for the Bayesian, and \ac{CPT} rules.
-For these decision models, this is because information sharing exacerbates the existing tendency of heavy drinkers to impersonate moderate drinkers, who behave more honestly as heavy drinkers become less so.
+For these decision models, this is because social learning exacerbates the existing tendency of heavy drinkers to impersonate moderate drinkers, who behave more honestly as heavy drinkers become less so.
 
 Particularly notable, is the decline in honest signalling by light drinkers visible in both heuristic type rules at the 0.25 level of \(q_{w}\) \& \(w_{w}\), and the associated increase in false positives.
-This arises because of the lack of homophily in information sharing, as light drinkers become informed about negative outcomes associated with concealment, despite having nothing to conceal.
+This arises because of the lack of homophily in social learning, as light drinkers become informed about negative outcomes associated with concealment, despite having nothing to conceal.
 The relatively high referral rates of drinkers heighten the effect further, because shared information becomes dominated by their experiences.
 
-The relationship is not, however, entirely straightforward, in that increasing information sharing leads to greater variance between runs.
+The relationship is not, however, entirely straightforward, in that increasing social learning leads to greater variance between runs.
 A linear model was used to predict the between-runs interquartile range of the average signal sent by moderate drinkers.
-The predictors used were decision rule, and level of information sharing, together with the interaction between the two.
+The predictors used were decision rule, and level of social learning, together with the interaction between the two.
 The regression results were significant (\(F_{7,12}=25,p<2.9\times10^{-6}\)) with \(R^2=94\%\), and intercept 0.07.
 The only significant coefficients were for the interaction terms, which were 0.44 (\(p<0.05\)) for the Bayesian payoff rule, and 0.69 (\(p<0.005\)) for the lexicographic.
-This suggests that information sharing, for the heuristic style decision rules introduces considerable uncertainty to the model, which is explored further in the sensitivity analysis below.
+This suggests that social learning, for the heuristic style decision rules introduces considerable uncertainty to the model, which is explored further in the sensitivity analysis below.
 
@@
 \end{adjustbox}
-\caption{Impact of information sharing on trends in honest signalling after 1000 rounds, mean with 95\% confidence interval over 100 runs}
+\caption{Impact of social learning on trends in honest signalling after 1000 rounds, mean with 95\% confidence interval over 100 runs}
 \label{fig:honest_sharing}
@@
 \end{adjustbox}
-\caption{Impact of information sharing on referral trends after 1000 rounds, mean with 95\% confidence interval over 100 runs}
+\caption{Impact of social learning on referral trends after 1000 rounds, mean with 95\% confidence interval over 100 runs}
 \label{fig:ref_sharing}
@@
 
-In this section we present a brief overview of the sensitivity analysis, followed by selected results highlighting the global effect of changes to perceived payoffs and degree of bias towards honesty, as well as information sharing within women.
+In this section we present a brief overview of the sensitivity analysis, followed by selected results highlighting the global effect of changes to perceived payoffs and degree of bias towards honesty, as well as social learning within women.
 The full results for the sensitivity analysis covering all sixteen emulators are available in appendix \ref{app:sensitivity_results}.
@@
 
-Perhaps surprisingly, variance attributable to information sharing between midwives is relatively low, with neither the weight nor probability accounting for more than 5\% of variance in any measure.
+Perhaps surprisingly, variance attributable to social learning between midwives is relatively low, with neither the weight nor probability accounting for more than 5\% of variance in any measure.
 While there are small contributions to variance in interaction with other parameters (e.g.
@@
 
-Figure \ref{fig:outcome_plots} gives a qualitative picture of both emulator quality, and the divergent response surfaces of the decision rules in response to variations in information sharing parameters.
+Figure \ref{fig:outcome_plots} gives a qualitative picture of both emulator quality, and the divergent response surfaces of the decision rules in response to variations in social learning parameters.
 Emulator fit is clearly imperfect, but overall behaviour is qualitatively similar, with both emulated and simulated plots demonstrating separation in outcome space for the decision rules.
@@
 
-Following from the suggestive results for information sharing introducing uncertainty (section \ref{sub:info_sharing}), figure \ref{fig:emulated_sharing_iqr} shows emulated points covering the parameter space in high resolution.
+Following from the suggestive results for social learning introducing uncertainty (section \ref{sub:info_sharing}), figure \ref{fig:emulated_sharing_iqr} shows emulated points covering the parameter space in high resolution.
 These plots reflect the increase in uncertainty of outcome shown for the heuristic type rules, which is especially severe for the Bayesian payoff rule.
 They also suggest that the Bayesian decision rule is less stable under conditions where the weight of shared information is substantially higher than the probability of sharing.
-This suggests that, perhaps unsurprisingly, that what information is shared is significant to outcomes.
+This suggests, perhaps unsurprisingly, that what information is shared is significant to outcomes.
 

### 2015-06-15 model_description.tex
Change info sharing to social learning
Begin moving model description to appendix. Also add an explanation of
pseudo-counts vs priors.

--- 2015-06-12 Model.tex
@@
-%!TEX root = disclosure_game.tex
-\section{Disclosure Game Model}
-\label{sec:model}
-%Start this off with a brief description of our fictional scenario.
-% Whole section ~ 1.5K
+\section{Model Description}
+\label{app:model_description}
 
-In this section we outline the disclosure game model, and give details of the four decision rules that will be examined in this paper, but begin with a brief sketch of a pregnancy in terms of encounters between a pregnant woman and a midwife.
+In this section we sketch the process of moving from a real world scenario, to a minimal game which sufficiently captures reality. For a
 

### 2015-06-15 Background.tex
Simulation schedule

@@
 
-The conceptual underpinning of all of these is the central idea of expected utility, originated by \citet{Bernoulli1954} and later formalised by \citet{Neumann1953}, which simply put, states that the worth of an action is the probability of each outcome, multiplied by the subjective gain or loss it delivers.
+The conceptual underpinning of all of these is the central idea of expected utility, originated by \citet{Bernoulli1954} and later formalised by \citet{Neumann1953}.
+Utility in this sense is the subjective value of an outcome, often expressed in monetary terms, and expected utility incorporates the uncertainty of obtaining that outcome.
+This is expressed by taking the expected utility of an outcome to be the probability of the outcome occurring, multiplied by the subjective value of it.
 

### 2015-06-15 Model.tex
Simulation schedule

@@
 
-In this section we outline the disclosure game model, and give details of the four decision rules that will be examined in this paper, but begin with a brief sketch of a pregnancy in terms of encounters between a pregnant woman and a midwife.
+In this section we sketch\footnote{A complete example of this for the alcohol misuse in pregnancy model is given in appendix \ref{app:model_description}, with simulation psuedocode in appendix \ref{app:sim_schedule}} the process of moving from a real world scenario to a minimal game which sufficiently captures reality, expressing the result as a decision problem representation, and finally translating this to a simulation model, and then outline four possible decision rules.
 
-Typically in the UK, a women will have 12 appointments with a midwife during the antenatal period, and in the majority of cases will encounter several different midwives \citep{Redshaw2014} in the course of their care.
-In the UK, and unlike most healthcare scenarios, maternity notes are held by the patient, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously.
-Maternity notes are not generally linked to extra-departmental records, meaning that a history of alcohol related admissions to another service may remain unknown unless revealed by the woman.
+\subsection{Model Construction Approach}
+\label{sec:model_design}
 
-According to NICE guidance \citep{NICE2010a,NICE2010} the issue of substance misuse should be raised at the initial booking appointment, followed by subsequent action if a concern is raised is at the discretion of the midwife.
-This may take the form of specific guidance to reduce intake, or if deemed necessary a referral to a specialist midwife and relevant interdisciplinary team.
-On alcohol consumption, policy regarding how to determine the level of consumption is at the time of writing generally at the level of local health authority, hospital trust, or according to the best judgement of the individual midwife, with no guidance provided by NICE.
-This commonly takes the form of average units per week, but may include \ac{T-ACE}\footnote{The \ac{T-ACE} is a four question screening test for alcohol misuse intended specifically for use with pregnant women.} \citep{Sokol1989863} and similar measures.
+The appropriate game representative of the scenario of interest, which captures the desired strategic dynamics may not be immediately obvious.
+There will almost invariably be many possible alternatives, of which some are isomorphisms, and others fundamentally different conjectures about the data generating process.
+We suggest that an iterative process is beneficial, beginning from the simplest possible game, and progressively augmenting it.
 
-Beyond the \enquote{booking} appointment, the onus is on women to raise concerns about their drinking behaviour, or the midwife to probe further if they feel it is warranted.
-In either case, once a concern has been raised the midwife must respond clinically, and inevitably personally, to the information.
+Transitioning from the resulting game, to a set of decision problems is a relatively simple task.
+We treat the $n$ player game as $n$ one-player games \citep{RiosInsua2009}, where the moves of other players are drawn from a probability distribution - nature, in game theoretic parlance.
+As with the game, the decision problem representation admits a degree of variation, and may need to be adjusted to reflect the decision rules that will be used.
 
-In an ideal world, all interactions with healthcare providers would be immediately and fully disclosive, with no repercussions for the patient.
-However, alcohol misuse by women is known to attract stigma \citep{Gomberg1988}, and is a recognised barrier to appropriate treatment in the maternity context \citep{NICE2010,Radcliffe2011}.
+These decision problems may then form the basis of an agent model, where agents use learning, and decision rules to play out the game.
+Simulation can then support features which are not readily representable within an analytic framework, for example, populations of heterogeneous players, individual and social learning, or network effects.
+In addition, the ability to observe the system in a state of flux rather than at equilibrium is desirable, since even where a social system reaches a stable state, the process by which we arrive at it is significant.
 
@@
 
-\begin{table}
-\center
-\subfloat[Social cost, \(X_{s}\), for women, given their signal, and the midwife's type\label{tab:Social-cost-matrix}]{%
-\begin{tabular}{|c|c|c|c|c|}
-\cline{3-5} 
-\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
-
-\hline
-\multirow{4}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
-\cline{2-5} 
- & Harsh & -2 & -1 & 0\tabularnewline
-\cline{2-5} 
- & Moderate & -1 & 0 & 0\tabularnewline
-\cline{2-5} 
- & Non & 0 & 0 & 0\tabularnewline
-\hline 
-\end{tabular}
-
-}
-
-\subfloat[Health outcome, \(X_{h}\), for women and midwives, given the midwife's action, and woman's type\label{tab:Referral-payoff-matrix}]{%
-\begin{tabular}{|c|c|c|c|c|}
-\cline{3-5} 
-\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
-
-\hline 
-\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
-\cline{2-5} 
- & Refer & 10 & 10 & 10\tabularnewline
-\cline{2-5} 
- & Don't refer & -2 & -1 & 10\tabularnewline
-\hline 
-\end{tabular}
-
-}
-
-\subfloat[Referral cost, \(X_{c}\), for midwife, given their action and the woman's type\label{tab:inst_cost_matrix}]{%
-\begin{tabular}{|c|c|c|c|c|}
-\cline{3-5}  
-\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
-\hline 
-\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
-\cline{2-5} 
- & Refer & -9 & -9 & -9 \tabularnewline
-\cline{2-5} 
- & Don't refer & 0 & 0 & 0\tabularnewline
-\hline 
-\end{tabular}
-
-}
-
-\caption{Payoff matrices\label{tab:Payoff-matrix}}
-\end{table}
-
-Taken together, this leads to a game tree that is relatively complex (figure \ref{fig:simple_tree} shows a simplified representation, with a detailed view of one branch in figure \ref{fig:zoom_tree}) even at the subgame level.
-
 As an example, consider the challenge faced by an agent of the heavy drinking type.
@@
 Even a relatively weak belief in this possibility can make the honest signal look like an unwarranted risk.
-
-Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversarial risk analysis \citep{RiosInsua2009}.
-This effectively translates the game to a pair of decision problems (figure \ref{fig:decision_problems}), which agents attempt to resolve at each turn using a simple decision rule, given their prior beliefs and experience of play.
-
-\begin{figure}[H]
-\begin{adjustbox}{center}
-\includegraphics[width=119mm]{figures/rounded_clover_infosets}
-\end{adjustbox}
-\caption{Simplified game tree.
-Arrows correspond to two moves by nature, followed by women, and midwives respectively.
-Line weight distinguishes between information sets, and possible moves, corresponding to ascending player types.
-For midwives, referral is shown by a heavier arrow.
-Light terminal nodes indicate that the game may repeat from that point, and black nodes are exits}
-
-\label{fig:simple_tree}
-\end{figure}
-
-\begin{figure}[H]
-\begin{adjustbox}{center}
-\includegraphics[width=119mm]{figures/tree_zoom}
-\end{adjustbox}
-\caption{Detail view of a single game tree branch, showing the possible moves by each player, with information sets for midwives}
-
-\label{fig:zoom_tree}
-\end{figure}
-
-\begin{figure}[H]
-\begin{adjustbox}{center}\subfloat[Women (heavy drinkers)]{\includegraphics[width=119mm]{figures/women_influence}}\end{adjustbox}
-\vskip
-\begin{adjustbox}{center}\subfloat[Midwives]{\includegraphics[width=119mm]{figures/mw_influence}}\end{adjustbox}
-\caption{Influence diagrams, showing the game broken into two decision problems. Squares indicate a decision node, while circles are (from the perspective of the agent) chance nodes}
-
-\label{fig:decision_problems}
-\end{figure}
 
@@
 \begin{algorithmic}
-\State n=1, action=none
-\While{action is none}
-\State Calculate the nth most common outcome following each action.
-\State Sort actions by the value of the nth most common outcome.
-\If{clear winner} \State action = best \EndIf
-\State n = n + 1
+\State $n \gets 1, action \gets none$
+\While{$action = none$}
+\State Calculate the $n$th most common outcome following each action.
+\State Sort actions by the value of the $n$th most common outcome.
+\If{clear winner} \State $action \gets best$ \EndIf
+\State $n \gets n + 1$
 \EndWhile
@@
 Given the discrete nature of actions and payoffs, coupled with a desire for tractability of the
-simulation, the Dirichlet distribution is employed as a prior to represent these beliefs. The probability
-density function takes the form -
+simulation, the Dirichlet distribution is employed as a prior to represent these beliefs. The probability density function takes the form -
 
@@
 more than zero and summing to less than 1, and \(\alpha_{i}\) is the 
-pseudo-count of prior observations for a pair \(i\).
+pseudo-count of prior observations\footnote{Psuedo-counts are related to, but distinct from prior beliefs.
+Here, the psuedo-count is a parameter to the prior belief distribution and is nothing more than a hypothetical count of prior observations.} for a pair \(i\).
 
@@
 
-\subsection{Information Sharing}
+\subsection{Social Learning}
 \label{sub:info_sharing}

### 2015-06-15 simulation_schedule.tex
Simulation schedule

%!TEX root = disclosure_game.tex

\section{Simulation Schedule}
\label{app:sim_schedule}

In this section we provide psuedocode for a single simulation, which encompasses several games.

\begin{algorithm}
\begin{algorithmic}
\State $rounds \gets 1000, appointments \gets 12$
\State women \gets enqueue([], $w_{1},\ldots,w_{1000}$), midwives \gets [$m_{1},\ldots,m_{100}$]
\While{$rounds > 0$}
	\State players $\gets$ dequeue first 100 women
	\State referred $\gets$ []
	\State $i $\gets$ 1$
	\While{$i < 100$}
		\State woman $\gets$ players[i], midwife $\gets$ midwives[i]
		\State signal $\gets$ signal(woman)
		\State response $\gets$ respond(midwife)
		\State midwife's memory $\gets$ woman, signal, response
		\State woman's memory $\gets$ type(midwife), signal, response, $X_{w, s, r, type(woman), type(midwife)}$
		\State update woman's beliefs
		\If{$response = refer$}
			\State midwife's memory $\gets$ type(woman), $X_{m, s, r, type(woman)}$
			\State retrospectively update midwife's beliefs
			\State women $\gets$ enqueue(women, new woman)
			\State Add woman to referred
		\Else
			women $\gets$ enqueue(women, woman)
		\EndIf
	\EndWhile
	\For{woman in referred}
		\If{$random \lt p$}
			\For{player in women}

			\EndFor
		\EndIf
	\EndFor
\State $rounds \gets rounds - 1$
\EndWhile
\end{algorithmic}
\caption{Simulation schedule\label{alg:sim}}
\end{algorithm}

### 2015-06-17 Introduction.tex
Reducing the pagecount
Substantially.

@@
 In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, tending to be a reflection of the assumptions of the modeller rather than empirically or theoretically grounded \citep{Waldherr2013}.
-To ameliorate this concern, we draw on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game\footnote{In a signalling game, on player, the signaller, has some piece of information that is known only to them which affects the outcome of the game for both players.
+To ameliorate this concern, we draw on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game\footnote{In a signalling game, one player (the signaller), has some piece of information that is known only to them which affects the outcome of the game for both players.
 The signaller has a choice as to what they tell the other player about this hidden information, and the responding player as to what they believe the information to be.} \citep{Kreps1987} with a basic form of intragroup social learning.
@@
 As a corollary, the decision problem agents attempt to answer can change, allowing agents' behaviour in novel problems to be informed by beliefs derived under other conditions.
+This is also indicative of the broader benefits to \ac{ABM} as an approach.
+Embedding these abstract rules in a simulated environment allows for mechanics which cannot be readily explored using purely analytic, or predictive approaches, for example, the social learning dynamic of the disclosure game model.
 
-While there is no universal theory of human behaviour to sit at the centre of \ac{ABM}ing as a method, a key motivation for decision rules is their claim to provide an account of decision making that is behaviourally and cognitively plausible.
+While there is no universal theory of human behaviour to sit at the centre of \ac{ABM} as a method, a key motivation for decision rules is their claim to provide an account of decision making that is behaviourally and cognitively plausible.
 Their mooted capability in this regard is to some extent supported by work from neuroeconomics, which aims to empirically test theories of decision making \citep{Rustichini2009}.

### 2015-06-17 Model.tex
Reducing the pagecount
Substantially.

@@
 
-In this section we sketch\footnote{A complete example of this for the alcohol misuse in pregnancy model is given in appendix \ref{app:model_description}, with simulation psuedocode in appendix \ref{app:sim_schedule}} the process of moving from a real world scenario to a minimal game which sufficiently captures reality, expressing the result as a decision problem representation, and finally translating this to a simulation model, and then outline four possible decision rules.
+In this section we sketch\footnote{A complete example of this for the alcohol misuse in pregnancy model is given in appendix \ref{app:model_description}, with a schedule of simulation provided in appendix \ref{app:sim_schedule}} the process of moving from a real world scenario to a minimal game which sufficiently captures reality, expressing the result as a decision problem representation, and finally translating this to a simulation model, and then outline four possible decision rules.
 
@@
 In addition, the ability to observe the system in a state of flux rather than at equilibrium is desirable, since even where a social system reaches a stable state, the process by which we arrive at it is significant.
-
-\subsection{Disclosure Game}
-\label{sub:the_game}
-%Outline how the scenario translates into a game.
-%Brief mention of the game theoretic solution
-
-In order to translate the scenario sketched above into a more abstract, tractable form, we cast it as a signalling game, and assume that women's disclosures (or not), are signals.
-We also make the simplifying assumption that a woman may have one of only three drinking patterns - light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy.
-Correspondingly, they are limited in what signals they may send when claiming to be one of these three types.
-
-Midwives are treated in a similar fashion, where their type corresponds to how negatively they regard a drinking pattern - non-judgemental, moderately judgemental, and harshly judgemental.
-The expression of this judgement is not a matter of choice on their part, and is assumed to have no impact on their clinical response, which is to either refer the woman for specialist treatment, or do nothing.
-
-At the end of a game, each player receives a payoff dependent on the actions and types of both players.
-Because both women and midwives have an interest in the outcome of the pregnancy, and would prefer a healthy baby, the payoff has a common interest component.
-Hence, both players receive a payoff based on the outcome of pregnancy, but women bear a social cost dependent on the signal they sent and the midwife's reaction to it.
-Similarly, midwives pay a cost if they refer to a specialist, mirroring the organisational cost of non-routine care.
-Table \ref{tab:Payoff-matrix} shows the three payoff matrices which together describe the game.
-
-As an example, consider the challenge faced by an agent of the heavy drinking type.
-In order to get the best health outcome, they must be referred and would ideally achieve this without paying any social cost at all.
-The best move depends on the type, and beliefs of the midwife.
-For example, a particularly unlucky scenario might be for the midwife to not only be of a harshly judgemental disposition, but to believe that no women really need to be referred.
-Even a relatively weak belief in this possibility can make the honest signal look like an unwarranted risk.
-
-%Might belong in a more methody bit? Read some stuff to check..
-To formally define the game, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\).
-Here, \(\{l, m, h\}\) correspond to light, moderate, and heavy alcohol consumption for women, and non-judgemental, moderately judgemental, and harshly judgemental for midwives.
-Midwives' pure strategies \(\{r,n\}\) are to refer, or do nothing, and those for women are to signal that they have one of the possible drinking patterns.
-Additionally define two utility functions - 
-\begin{equation}
-u_{w}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}}
-\end{equation} 
-\begin{equation}
-u_{m}(s_{w}, s_{m}, \theta_{w})=X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}},
-\end{equation} with $X_{c}$, $X_{h}$, and $X_{s}$ being the payoff matrices as in table \ref{tab:Payoff-matrix}, $s_{w}$ and $s_{m}$ denoting a specific signal by a woman, and referral response by a midwife.
-Lastly let \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\) be distributions over types of women, and midwives respectively.
-
-As noted, rather than solve the game, we allow populations of agents to play it, and hence stipulate further that women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)).
-They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred, and a new player is drawn from the same distribution that produced the original players to replace them.
-If they are not referred, they rejoin the back of the queue after their appointment.
-In either case, they are informed of their payoff after each round and update their beliefs accordingly using one of the rules described in section \ref{sub:the_agents}.
-
-Midwives play for \(r_{m}\) rounds (\(r_{m}=1000\) in all experiments), and conduct appointments in parallel, i.e.
-if there are 5 midwives, then five women are drawn from the queue and assigned at random to the midwives.
-Unlike women, midwives are only informed of their payoff if they choose to make a referral.
-Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.
-
-\subsection{Agent Models}
-\label{sub:the_agents}
-%Outline basic structure, then specifics on each one.
-%This should probably go lexic -> bayes payoff -> bayes -> CPT in order
-% of complexity.
-%suggest there are added shells of complexity
-%		mention the info sharing because homophilly
-%			related - the enhancement to the bayes/cpt agents is that they personalise, as much as anything.
-%		properly explain dirichlet priors
-% How about comparing the decision problem representation for the agent types?
-
-While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same outputs, we limit ourselves here to four.
-The simplest is a lexicographic rule (1), in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}.
-Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-output characteristics.
-
-As noted in section \ref{sub:the_game}, agents have perfect recall, and midwives recognise women if they repeatedly encounter them.
-While agents recall perfectly and make use of the new information for retrospective updates, all four agent models make decisions `as-if' they were always facing a new \enquote{opponent}.
-
-A simplifying assumption is made that all midwives have just qualified after receiving identical training.
-As a result, they have homogeneous beliefs about  women and assume to some extent that they are honest.
-Women have heterogeneous beliefs, which correspond to experiencing \(k\) randomly chosen paths through the game, and following each path at least once.
-
-\subsubsection{Lexicographic Heuristic}
-\label{sub:lexico}
-
-The lexicographic heuristic (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified problem representation, where an action is a choice between combined lotteries.
-Functionally, the heuristic maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e.
-one reason decision making.
-Where there is no clear best action, but one or more is evidently worse, a choice must be made as to whether to discard the poorer action; in this case we have elected to retain it.
-This approach requires minimal computation, and does not assume that \(u_{i}\) is static, or known.
-
-Women resolve this by approximating the utility function, as a function \(f(s_{w}, \sigma)\) on their choice of signal and an unknown distribution $\sigma$, which maps to \(u_{w}\) - i.e.
-\(s_{w}\) is a choice between simple lotteries.
-The algorithm maintains a count, \(n\), of the number of occurrences of each outcome given the choice from \(s_{w}\).
-
-Midwives solve a slightly different problem with more information, where \(s_{w}\) is known, and \(s_{m}\) is the lottery choice - \(f(s_{w}, s_{m},\sigma)\).
-This is resolved by maintaining a separate count for each signal (i.e.
-\(n_{s_{w},s_{m}}\)), and otherwise following the same algorithm, presented below.
-
-\begin{algorithm}
-\begin{algorithmic}
-\State $n \gets 1, action \gets none$
-\While{$action = none$}
-\State Calculate the $n$th most common outcome following each action.
-\State Sort actions by the value of the $n$th most common outcome.
-\If{clear winner} \State $action \gets best$ \EndIf
-\State $n \gets n + 1$
-\EndWhile
-\State \Return action
-\end{algorithmic}
-\caption{Lexicographic heuristic\label{alg:lexico}}
-\end{algorithm}
-
-As an example, take a light drinker who has played three rounds with a succession of particularly judgemental midwives, signalling honestly in two and claiming to be a moderate drinker in one.
-The most common outcome of the honest signal was a payoff of 10, which is clearly preferable to the 9 gained by claiming to be moderate.
-On that basis, they choose to signal honestly.
-
-\subsubsection{Bayesian Payoff}
-
-The Bayesian payoff agent uses the same subset of information as the lexicographic method, but updates beliefs on the link between actions and payoffs using the Bayes rule, and attempts to choose the action which minimises risk.
-
-Given the discrete nature of actions and payoffs, coupled with a desire for tractability of the
-simulation, the Dirichlet distribution is employed as a prior to represent these beliefs. The probability density function takes the form -
-
-\begin{equation}
-D(\Theta|\alpha)=\frac{\Gamma(\sum_{i=1}^{k}\alpha_{i})}{\prod_{i=1}^{k}\Gamma(\alpha_{i})}\overset{k}{\underset{i=1}{\prod}\Theta_{i}^{\alpha_{i-1}}}
-\end{equation}
-
-where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\) is the number
-of signal-payoff pairs, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
-more than zero and summing to less than 1, and \(\alpha_{i}\) is the 
-pseudo-count of prior observations\footnote{Psuedo-counts are related to, but distinct from prior beliefs.
-Here, the psuedo-count is a parameter to the prior belief distribution and is nothing more than a hypothetical count of prior observations.} for a pair \(i\).
-
-The distribution is particularly convenient, in that to infer the
-probability of a signal implying a payoff becomes
-simply -
-
-\begin{equation}
-p(x=j|D,\alpha)=\frac{\alpha_{j}+n_{j}}{\sum_{j}(\alpha_{j}+n_{j})}\label{eq:posterior}
-\end{equation}
-
-Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), so
-that the belief that a signal will lead to a payoff is the number
-of times that pairing has been observed (including the pseudo-count),
-over the total number of observations thus far. This makes computation
-of beliefs fast and simple, since all that must be maintained is
-a count of observations with no particular concern as to their order.
-As before, midwives follow a similar pattern but maintain \(n_{s_{w}}\) independent counts of pairings between referral choice and payoff, updating their beliefs about the relationship between the choice to refer and payoff given the signal they have received.
-
-Agents then choose the strategy $s_{i}$ to minimise risk $R_{i}$, which is simply defined as - 
-\begin{equation}
-R_{w}(s_{w}) = \sum_{x \in X} -xp(x | s_{w})
-\end{equation}
-\begin{equation}
-R_{m}(s_{w}, s_{m}) = \sum_{x \in X} -xp(x | s_{w}\wedge s_{m}),
-\end{equation}
-
-where $X$ is the set of payoffs the agent has observed to follow $s_{i}$.
-
-If we take our light drinker from the lexicographic case, and assume that they began with an uninformative prior.
-The 6 possible signal-payoffs pairings are then \([(l,10),(m,10),(h,10),(m,9),(h,9),(h,8)]\), with \(\alpha_{i}=1\) for all \(i\).
-After playing the three rounds, \(n_{l,10}=2\), and \(n_{m,9}=1\).
-
-The agent then evaluates \(R_{w}\) for each signal, e.g. for the light signal:
-
-\begin{equation*}
-\begin{align*}
-X &= \{10\}\\
-R_{w}(l) &= \sum_{x \in X} -xp(x | l) = -10p(10 | l)\\
-R_{w}(l) &= -10(\frac{\alpha_{l,10}+n_{l,10}}{\sum_{j}(\alpha_{j}+n_{j})}) = -10(\frac{1+2}{1+2})\\
-R_{w}(l) &= -10(\frac{3}{3}) = -10
-\end{align*}
-\end{equation*}
-
-and by the same method, \(R_{w}(m)=-9\frac{1}{3}\), and \(R_{w}(h)=-9\), concluding that signalling honestly is the best move.
-
-\subsubsection{Bayesian Risk Minimisation}
-
-The second Bayesian agent augments the reasoning of the simple payoff model, making the stronger assumption that the utility function is static, and known.
-Women maintain two sets of beliefs, corresponding respectively to \(p_{m}\), and the probability of referral given signal choice.
-This leads to the risk function, minimised with respect to \(s_{w}\) -
-
-\begin{equation}
-R_{w}(s_{w}, \theta_{w}) = \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, \theta_{w}, j)p(j)p(i | s_{w}),
-\end{equation}
-
-so that the risk of a signal is the sum of the products of all payoffs with the probabilities of their entailed midwife types and responses.
-
-Midwives reasoning centres on determining the meaning of signals, since given the knowledge of what some signal \(s_{w}\) conveys about the true type of the sender, the payoff for an action is known.
-As such, their inference process is the same as for the simple Bayesian agent but over signal-type pairs, and they attempt to minimise the following risk function, minimised with respect to \(s_{m}\) -
-
-\begin{equation}
-R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{m}(s_{w}, s_{m}, i)p(i | s_{w})
-\end{equation}
-
-Returning to our example agent, under this model the type of the midwife becomes salient, hence \(n_{h}=3\), and \(n_{l,n}=2\), \(n_{m,n}=1\).
-Their prior beliefs remain uninformative, i.e.
-\(\alpha_{j} = 1, j \in \{l,m,h\}\), \(\alpha_{i,j}=1,i \in \{r,n\}, j \in \{l,m,h\}\).
-As before, the agent evaluates \(R_{w}\) for the three signals, and the process for the light signal is given below -
-
-\begin{equation*}
-\begin{align*}
-R_{w}(l, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(l, i, l, j)p(j)p(i | l)\\
-R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l) - u_{w}(l, r, l, m)p(m)p(r | l) - u_{w}(l, n, l, m)p(m)p(n | l) \\
-&\phantom{{}=1}- u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
-u_{w}(l, i, l, j) &= 10\\
-R_{w}(l, l) &= -10p(l)p(r | l) - 10p(l)p(n | l) - 10p(m)p(r | l) - 10p(m)p(n | l) - 10p(h)p(r | l) - 10p(h)p(n | l)\\
-p(l) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
-p(m) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
-p(h) &= \frac{1 + 3}{1 + 1 + 1 + 3} = \frac{2}{3}\\
-p(r | l) &= \frac{1 + 0}{1 + 1 + 2} = \frac{1}{4}\\
-p(n | l) &= \frac{1 + 2}{1 + 1 + 2} = \frac{3}{4}\\
-R_{w}(l, l) &= -10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{2}{3} \cdot \frac{1}{4} - 10\cdot \frac{2}{3} \cdot \frac{3}{4}\\
-&= -10
-\end{align*}
-\end{equation*}
-
-and similarly for moderate (\(R_{w}(m,l)=-9\frac{1}{3}\)), and heavy (\(R_{w}(h,l)=-8\frac{1}{2}\)) signals, once again concluding that honesty is the better option.
-
-\subsubsection{Descriptive Decision Theory}
-
-The most complex decision rule used is \ac{CPT}, which attempts to reproduce a number of systematic deviations from rationality observed in humans.
-While \ac{CPT} has primarily been applied in the context of decisions from description, it has been modified to deal with decisions from experience by incorporating a first stage where probabilities are estimates from observations as in \cite{FoxCPT}.
-In this instance the Bayesian inference process fills the first stage role.
-
-%Maybe cut this bit and make explanation richer?
-Rather than the psychologically more interesting \ac{PT}, the \ac{CPT}
-decision rule is used in this instance, because of the requirement
-for women to evaluate the `prospects'\footnote{Where a prospect is a sequence of payoff-probability pairings in ascending order of payoff, associated with an action.} of more than two actions.
-\ac{CPT} uses transformed probabilities, underweighting
-small probabilities, and overweighting large ones.
-This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and contrastingly low probabilities as impossible.
-The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains (eqn \ref{eqn:cpt_p_pos}) and losses (eqn \ref{eqn:cpt_p_neg}) -
-
-\begin{align}
-w^{+}(p) & = \frac{p^{\gamma}}{(p^{\gamma}+(1-p)^{\gamma})^{\frac{1}{\gamma}}}\label{eqn:cpt_p_pos}\\
-w^{-}(p) & = \frac{p^{\delta}}{(p^{\delta}+(1-p)^{\delta})^{\frac{1}{\delta}}}\label{eqn:cpt_p_neg},
-\end{align}
-
-where $p$ is the unweighted probability, and $\gamma$ and $\delta$
-are the weights for gain and loss probabilities respectively.
-Along similar lines, the values of losses and gains are transformed to reflect a tendency to regard a loss as more significant than a gain  -
-
-\begin{equation}
-v(u_{i})=\begin{cases}
-f(u_{i}),& \text{if}\, u_{i}>0\\
-0,& \text{if}\, u_{i}=0\\
-\lambda g(u_{i}),& \text{if}\, x<0
-\end{cases},
-\end{equation}
-
-where,
-
-\begin{equation}
-f(u_{i})=\begin{cases}
-u_{i}^{\alpha},& \text{if}\,\alpha>0\\
-\ln(u_{i}),& \text{if}\,\alpha=0\\
-1-(1+u_{i})^{\alpha},& \text{if}\,\alpha<0
-\end{cases}
-\end{equation}
-\begin{equation}
-g(u_{i})=\begin{cases}
--(-u_{i})^{\beta},& \text{if}\,\beta>0\\
--\ln(-u_{i}),& \text{if}\,\beta=0\\
-(1-u_{i})^{\beta}-1,& \text{if}\,\beta<0
-\end{cases},
-\end{equation}
-
-and $\alpha$, and $\beta$ are respectively the power of a gain,
-and a loss, and \(\lambda\) is a multiplier giving the aversion to loss.
-
-Finally, the transformed probabilities are used to construct decision weights, \(\pi^{+},\pi^{-}\) for losses and gains, where,
-
-\begin{equation}
-\pi_{n}^{+}=w^{+}(p_{n})
-\end{equation}
-\begin{equation}
-\pi_{-m}^{-}=w^{-}(p_{-m})
-\end{equation}
-\begin{equation}
-\pi_{i}^{+}=w^{+}(p_{i}+\ldots+p_{n}) - w^{+}(p_{i+1}+\ldots+p_{n}),0\leq i \leq n - 1
-\end{equation}
-\begin{equation}
-\pi_{i}^{-}=w^{-}(p_{-m}+\ldots+p_{i}) - w^{-}(p_{-m}+\ldots+p_{i-1}),1-m\leq i \leq 0
-\end{equation}
-
-The \ac{CPT} value of a single outcome prospect \(f=(u_{i};p_{i})\), is $v(u_{i})\pi^{+}(p_{i})$
-if $u_{i}\geq0$, and $v(u_{i})\pi^{-}(p_{i})$ otherwise. For any given action the \ac{CPT}
-value, \(V\) is the sum of the value of the prospects of that action, as
-in the Bayesian risk model, and the agent chooses the option which maximises this quantity.
-
-Once again, we return to the light drinker example.
-The inferential aspects are identical with the more complex Bayesian risk minimisation algorithm, hence \(p(j)p(i | l)\), and \(u_{w}(l, i, l, j)\) remain the same, but the agent additionally calculates $v(u_{w}(l, i, l, j))w^{+}(p(j))w^{+}(p(i | l))$.
-For the \ac{CPT} parameters, the values are those originally given by \citet{Tversky1992} and used in the actual simulations which are given fully in table \ref{tab:qt_params}.
-
-\begin{equation*}
-\begin{align*}
-\alpha &= 0.88\\
-\gamma &= 0.61\\
-p(l) &= \frac{1}{6}\\
-p(m) &= \frac{1}{6}\\
-p(h) &= \frac{2}{3}\\
-p(r | l) &= \frac{1}{4}\\
-p(n | l) &= \frac{3}{4}\\
-u_{w}(l, i, l, j) &= 10\\
-f&=(10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{6},10;\frac{1}{2})\\
-f^{+}&=f,f^{-}=()\\
-n &= 5\\
-v(u_{w}) &= f(u_{w}) = u_{w}^\alpha\\
-v(u_{w}) &= 10^{0.88} = 7.59\\
-\pi_{0}^{+}&=w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(1) - w^{+}(\frac{23}{24})\\
-&=0.19\\
-\pi_{1}^{+}&=w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(\frac{23}{24}) - w^{+}(\frac{5}{6})\\
-&= 0.17\\
-\pi_{2}^{+}&=w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(\frac{5}{6}) - w^{+}(\frac{19}{24})\\
-&= 0.04\\
-\pi_{3}^{+}&=w^{+}(\frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{6} + \frac{1}{2})=w^{+}(\frac{19}{24}) - w^{+}(\frac{2}{3})\\
-&= 0.09\\
-\pi_{4}^{+}&=w^{+}(\frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{2})=w^{+}(\frac{2}{3}) - w^{+}(\frac{1}{2})\\
-&= 0.09\\
-\pi_{5}^{+}&=w^{+}(\frac{1}{2})\\
-&= 0.42\\
-V(f) &= V(f^{+}) + V(f^{-}) = V(f^{+}) + 0\\
-V(f^{+}) &= \sum_{i}^{n}\pi_{i}^{+}(f^{+})v_{i}^{+}(f^{+}) = 7.59
-\end{align*}
-\end{equation*}
-
-And as before, following the same process for moderate, and heavy signals which yields respectively 7.14, and 6.22, the agent chooses the higher valued action and sends an honest signal.
-
-\subsection{Social Learning}
-\label{sub:info_sharing}
-
-It would seem unreasonable to suppose that neither party recounts their experiences to their peers, and to explore the impact of this we also modify the game to introduce a simple form of information sharing within agent groups.
-This takes the form of having each agent share their memories with their colleagues with some probability \(q\).
-Individuals then incorporate shared information into their beliefs using weighted updates, such that a shared observation of a low type signal contributes to their beliefs by \(w\), and \(0\leq w\leq 1\) (i.e.
-\(n_{j} = n_{j} + w\)).
-Women share only when they have finished play, and provide their complete history of games, because they have accurate information about the outcomes.
-By the same rationale, midwives share only their history with the most recent woman they referred.
-Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{More precisely, memories of games remain, but it is assumed that only the most current information is relevant enough to be shared.}
-
-Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this exogenous information differently.
-The simple payoff based rule relies on a belief structure relating actions directly to rewards which is essentially model free.
-Because payoffs differ by the agent's private type, the information shared may not correspond to the experience of the listening agent in the same scenario.
-As a result, payoff reasoners have a belief bias towards the most common player type, and can believe in outcomes that are, for them, impossible.
-
-By contrast, representing the problem in terms of the probabilities of the individual lotteries imposes a model that abstracts the new information from payoffs, and allows the agent to discard implausible outcomes.
-This stronger assumption as to the static and known qualities of payoffs does however reduce the flexibility of the decision rule.

### 2015-06-17 SensitivityAnalysis.tex
Reducing the pagecount
Substantially.

@@
 \label{app:sensitivity_results}
+
+This section provides complete variance based sensitivity analysis results for the disclosure game model.
+Each subsection gives results for one simulation output under all four decision rules, with tables providing the percentage of overall variance attributable to the individual parameters, emulator quality statistics, and the 5 most significant interaction contributions to variance in the output.
 

### 2015-06-17 abstract_short.tex
Reducing the pagecount
Substantially.

--- 2015-01-07 Abstract.tex
@@
 
-\subsection*{Background}
-
 We draw together methodologies from game theory, agent based modelling, decision theory, and uncertainty analysis to explore the process of decision making in the context of pregnant women disclosing their drinking behaviour to their midwives.
-
-\subsection*{Objective}
-
-The primary purpose of this work is to demonstrate the significance of how the decision making process is formulated, by contrasting four distinct decision rules against one another and exploring a simple form of information sharing, the analysis is supported by the use of statistical emulators for a full exploration of the parameter space.
-We also demonstrate the utility of an approach which it is hoped contributes towards addressing concerns about the ad hoc character of \ac{ABM}, by providing a strong theoretical grounding for the reasoning processes of individual agents.
-To this end we aim to show that these simple rules, operating in an inescapably artificial scenario are nonetheless capable of reproducing trends reported in the literature.
-
-\subsection*{Methods}
 
@@
 Finally a global sensitivity analysis using \acp{GEM} is conducted, to compare the response surfaces of the different decision rules in the game.
-
-\subsection*{Results}
-
-Selected results showing the ability of all decision rules to reproduce qualitative trends noted in the literature are provided, together with a sensitivity analysis, and comparative heat maps produced using \acp{GEM} demonstrating the significance of the precise implementation of the decision making framework.
-
-\subsection*{Comments}
-
-We note that the model omits the overwhelming complexity of the real disclosure scenario where hardly any quantitative data are available, and is presented largely in the spirit of a convenient demonstration of the methodology.
-Clearly a domain where there is sufficient data to permit a more comprehensive approach to validation of model outcomes is desirable, and will form the basis of our future work.
-
-To aid in replication and extension, the model has been implemented as a Python module, and is freely available under the Mozilla Public License from \url{https://github.com/greenape/disclosure-game-module}.

### 2015-06-17 model_description.tex
Reducing the pagecount
Substantially.

@@
 \section{Model Description}
-\label{app:model_description}
+\label{app:detail_model_description}
 
@@
 
-\subsection{Agent Models}
-\label{sub:the_agents}
-%Outline basic structure, then specifics on each one.
-%This should probably go lexic -> bayes payoff -> bayes -> CPT in order
-% of complexity.
-%suggest there are added shells of complexity
-%		mention the info sharing because homophilly
-%			related - the enhancement to the bayes/cpt agents is that they personalise, as much as anything.
-%		properly explain dirichlet priors
-% How about comparing the decision problem representation for the agent types?
-
-While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same outputs, we limit ourselves here to four.
-The simplest is a lexicographic rule (1), in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}.
-Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-output characteristics.
-
-As noted in section \ref{sub:the_game}, agents have perfect recall, and midwives recognise women if they repeatedly encounter them.
-While agents recall perfectly and make use of the new information for retrospective updates, all four agent models make decisions `as-if' they were always facing a new \enquote{opponent}.
-
-A simplifying assumption is made that all midwives have just qualified after receiving identical training.
-As a result, they have homogeneous beliefs about  women and assume to some extent that they are honest.
-Women have heterogeneous beliefs, which correspond to experiencing \(k\) randomly chosen paths through the game, and following each path at least once.
-
-\subsubsection{Lexicographic Heuristic}
-\label{sub:lexico}
-
-The lexicographic heuristic (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified problem representation, where an action is a choice between combined lotteries.
-Functionally, the heuristic maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e.
-one reason decision making.
-Where there is no clear best action, but one or more is evidently worse, a choice must be made as to whether to discard the poorer action; in this case we have elected to retain it.
-This approach requires minimal computation, and does not assume that \(u_{i}\) is static, or known.
-
-Women resolve this by approximating the utility function, as a function \(f(s_{w}, \sigma)\) on their choice of signal and an unknown distribution $\sigma$, which maps to \(u_{w}\) - i.e.
-\(s_{w}\) is a choice between simple lotteries.
-The algorithm maintains a count, \(n\), of the number of occurrences of each outcome given the choice from \(s_{w}\).
-
-Midwives solve a slightly different problem with more information, where \(s_{w}\) is known, and \(s_{m}\) is the lottery choice - \(f(s_{w}, s_{m},\sigma)\).
-This is resolved by maintaining a separate count for each signal (i.e.
-\(n_{s_{w},s_{m}}\)), and otherwise following the same algorithm, presented below.
-
-\begin{algorithm}
-\begin{algorithmic}
-\State n=1, action=none
-\While{action is none}
-\State Calculate the nth most common outcome following each action.
-\State Sort actions by the value of the nth most common outcome.
-\If{clear winner} \State action = best \EndIf
-\State n = n + 1
-\EndWhile
-\State \Return action
-\end{algorithmic}
-\caption{Lexicographic heuristic\label{alg:lexico}}
-\end{algorithm}
-
-As an example, take a light drinker who has played three rounds with a succession of particularly judgemental midwives, signalling honestly in two and claiming to be a moderate drinker in one.
-The most common outcome of the honest signal was a payoff of 10, which is clearly preferable to the 9 gained by claiming to be moderate.
-On that basis, they choose to signal honestly.
-
-\subsubsection{Bayesian Payoff}
-
-The Bayesian payoff agent uses the same subset of information as the lexicographic method, but updates beliefs on the link between actions and payoffs using the Bayes rule, and attempts to choose the action which minimises risk.
-
-Given the discrete nature of actions and payoffs, coupled with a desire for tractability of the
-simulation, the Dirichlet distribution is employed as a prior to represent these beliefs. The probability
-density function takes the form -
-
-\begin{equation}
-D(\Theta|\alpha)=\frac{\Gamma(\sum_{i=1}^{k}\alpha_{i})}{\prod_{i=1}^{k}\Gamma(\alpha_{i})}\overset{k}{\underset{i=1}{\prod}\Theta_{i}^{\alpha_{i-1}}}
-\end{equation}
-
-where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\) is the number
-of signal-payoff pairs, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
-more than zero and summing to less than 1, and \(\alpha_{i}\) is the 
-pseudo-count of prior observations for a pair \(i\).
-
-The distribution is particularly convenient, in that to infer the
-probability of a signal implying a payoff becomes
-simply -
-
-\begin{equation}
-p(x=j|D,\alpha)=\frac{\alpha_{j}+n_{j}}{\sum_{j}(\alpha_{j}+n_{j})}\label{eq:posterior}
-\end{equation}
-
-Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), so
-that the belief that a signal will lead to a payoff is the number
-of times that pairing has been observed (including the pseudo-count),
-over the total number of observations thus far. This makes computation
-of beliefs fast and simple, since all that must be maintained is
-a count of observations with no particular concern as to their order.
-As before, midwives follow a similar pattern but maintain \(n_{s_{w}}\) independent counts of pairings between referral choice and payoff, updating their beliefs about the relationship between the choice to refer and payoff given the signal they have received.
-
-Agents then choose the strategy $s_{i}$ to minimise risk $R_{i}$, which is simply defined as - 
-\begin{equation}
-R_{w}(s_{w}) = \sum_{x \in X} -xp(x | s_{w})
-\end{equation}
-\begin{equation}
-R_{m}(s_{w}, s_{m}) = \sum_{x \in X} -xp(x | s_{w}\wedge s_{m}),
-\end{equation}
-
-where $X$ is the set of payoffs the agent has observed to follow $s_{i}$.
-
-If we take our light drinker from the lexicographic case, and assume that they began with an uninformative prior.
-The 6 possible signal-payoffs pairings are then \([(l,10),(m,10),(h,10),(m,9),(h,9),(h,8)]\), with \(\alpha_{i}=1\) for all \(i\).
-After playing the three rounds, \(n_{l,10}=2\), and \(n_{m,9}=1\).
-
-The agent then evaluates \(R_{w}\) for each signal, e.g. for the light signal:
-
-\begin{equation*}
-\begin{align*}
-X &= \{10\}\\
-R_{w}(l) &= \sum_{x \in X} -xp(x | l) = -10p(10 | l)\\
-R_{w}(l) &= -10(\frac{\alpha_{l,10}+n_{l,10}}{\sum_{j}(\alpha_{j}+n_{j})}) = -10(\frac{1+2}{1+2})\\
-R_{w}(l) &= -10(\frac{3}{3}) = -10
-\end{align*}
-\end{equation*}
-
-and by the same method, \(R_{w}(m)=-9\frac{1}{3}\), and \(R_{w}(h)=-9\), concluding that signalling honestly is the best move.
-
-\subsubsection{Bayesian Risk Minimisation}
-
-The second Bayesian agent augments the reasoning of the simple payoff model, making the stronger assumption that the utility function is static, and known.
-Women maintain two sets of beliefs, corresponding respectively to \(p_{m}\), and the probability of referral given signal choice.
-This leads to the risk function, minimised with respect to \(s_{w}\) -
-
-\begin{equation}
-R_{w}(s_{w}, \theta_{w}) = \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, \theta_{w}, j)p(j)p(i | s_{w}),
-\end{equation}
-
-so that the risk of a signal is the sum of the products of all payoffs with the probabilities of their entailed midwife types and responses.
-
-Midwives reasoning centres on determining the meaning of signals, since given the knowledge of what some signal \(s_{w}\) conveys about the true type of the sender, the payoff for an action is known.
-As such, their inference process is the same as for the simple Bayesian agent but over signal-type pairs, and they attempt to minimise the following risk function, minimised with respect to \(s_{m}\) -
-
-\begin{equation}
-R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{m}(s_{w}, s_{m}, i)p(i | s_{w})
-\end{equation}
-
-Returning to our example agent, under this model the type of the midwife becomes salient, hence \(n_{h}=3\), and \(n_{l,n}=2\), \(n_{m,n}=1\).
-Their prior beliefs remain uninformative, i.e.
-\(\alpha_{j} = 1, j \in \{l,m,h\}\), \(\alpha_{i,j}=1,i \in \{r,n\}, j \in \{l,m,h\}\).
-As before, the agent evaluates \(R_{w}\) for the three signals, and the process for the light signal is given below -
-
-\begin{equation*}
-\begin{align*}
-R_{w}(l, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(l, i, l, j)p(j)p(i | l)\\
-R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l) - u_{w}(l, r, l, m)p(m)p(r | l) - u_{w}(l, n, l, m)p(m)p(n | l) \\
-&\phantom{{}=1}- u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
-u_{w}(l, i, l, j) &= 10\\
-R_{w}(l, l) &= -10p(l)p(r | l) - 10p(l)p(n | l) - 10p(m)p(r | l) - 10p(m)p(n | l) - 10p(h)p(r | l) - 10p(h)p(n | l)\\
-p(l) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
-p(m) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
-p(h) &= \frac{1 + 3}{1 + 1 + 1 + 3} = \frac{2}{3}\\
-p(r | l) &= \frac{1 + 0}{1 + 1 + 2} = \frac{1}{4}\\
-p(n | l) &= \frac{1 + 2}{1 + 1 + 2} = \frac{3}{4}\\
-R_{w}(l, l) &= -10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{2}{3} \cdot \frac{1}{4} - 10\cdot \frac{2}{3} \cdot \frac{3}{4}\\
-&= -10
-\end{align*}
-\end{equation*}
-
-and similarly for moderate (\(R_{w}(m,l)=-9\frac{1}{3}\)), and heavy (\(R_{w}(h,l)=-8\frac{1}{2}\)) signals, once again concluding that honesty is the better option.
-
-\subsubsection{Descriptive Decision Theory}
-
-The most complex decision rule used is \ac{CPT}, which attempts to reproduce a number of systematic deviations from rationality observed in humans.
-While \ac{CPT} has primarily been applied in the context of decisions from description, it has been modified to deal with decisions from experience by incorporating a first stage where probabilities are estimates from observations as in \cite{FoxCPT}.
-In this instance the Bayesian inference process fills the first stage role.
-
-%Maybe cut this bit and make explanation richer?
-Rather than the psychologically more interesting \ac{PT}, the \ac{CPT}
-decision rule is used in this instance, because of the requirement
-for women to evaluate the `prospects'\footnote{Where a prospect is a sequence of payoff-probability pairings in ascending order of payoff, associated with an action.} of more than two actions.
-\ac{CPT} uses transformed probabilities, underweighting
-small probabilities, and overweighting large ones.
-This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and contrastingly low probabilities as impossible.
-The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains (eqn \ref{eqn:cpt_p_pos}) and losses (eqn \ref{eqn:cpt_p_neg}) -
-
-\begin{align}
-w^{+}(p) & = \frac{p^{\gamma}}{(p^{\gamma}+(1-p)^{\gamma})^{\frac{1}{\gamma}}}\label{eqn:cpt_p_pos}\\
-w^{-}(p) & = \frac{p^{\delta}}{(p^{\delta}+(1-p)^{\delta})^{\frac{1}{\delta}}}\label{eqn:cpt_p_neg},
-\end{align}
-
-where $p$ is the unweighted probability, and $\gamma$ and $\delta$
-are the weights for gain and loss probabilities respectively.
-Along similar lines, the values of losses and gains are transformed to reflect a tendency to regard a loss as more significant than a gain  -
-
-\begin{equation}
-v(u_{i})=\begin{cases}
-f(u_{i}),& \text{if}\, u_{i}>0\\
-0,& \text{if}\, u_{i}=0\\
-\lambda g(u_{i}),& \text{if}\, x<0
-\end{cases},
-\end{equation}
-
-where,
-
-\begin{equation}
-f(u_{i})=\begin{cases}
-u_{i}^{\alpha},& \text{if}\,\alpha>0\\
-\ln(u_{i}),& \text{if}\,\alpha=0\\
-1-(1+u_{i})^{\alpha},& \text{if}\,\alpha<0
-\end{cases}
-\end{equation}
-\begin{equation}
-g(u_{i})=\begin{cases}
--(-u_{i})^{\beta},& \text{if}\,\beta>0\\
--\ln(-u_{i}),& \text{if}\,\beta=0\\
-(1-u_{i})^{\beta}-1,& \text{if}\,\beta<0
-\end{cases},
-\end{equation}
-
-and $\alpha$, and $\beta$ are respectively the power of a gain,
-and a loss, and \(\lambda\) is a multiplier giving the aversion to loss.
-
-Finally, the transformed probabilities are used to construct decision weights, \(\pi^{+},\pi^{-}\) for losses and gains, where,
-
-\begin{equation}
-\pi_{n}^{+}=w^{+}(p_{n})
-\end{equation}
-\begin{equation}
-\pi_{-m}^{-}=w^{-}(p_{-m})
-\end{equation}
-\begin{equation}
-\pi_{i}^{+}=w^{+}(p_{i}+\ldots+p_{n}) - w^{+}(p_{i+1}+\ldots+p_{n}),0\leq i \leq n - 1
-\end{equation}
-\begin{equation}
-\pi_{i}^{-}=w^{-}(p_{-m}+\ldots+p_{i}) - w^{-}(p_{-m}+\ldots+p_{i-1}),1-m\leq i \leq 0
-\end{equation}
-
-The \ac{CPT} value of a single outcome prospect \(f=(u_{i};p_{i})\), is $v(u_{i})\pi^{+}(p_{i})$
-if $u_{i}\geq0$, and $v(u_{i})\pi^{-}(p_{i})$ otherwise. For any given action the \ac{CPT}
-value, \(V\) is the sum of the value of the prospects of that action, as
-in the Bayesian risk model, and the agent chooses the option which maximises this quantity.
-
-Once again, we return to the light drinker example.
-The inferential aspects are identical with the more complex Bayesian risk minimisation algorithm, hence \(p(j)p(i | l)\), and \(u_{w}(l, i, l, j)\) remain the same, but the agent additionally calculates $v(u_{w}(l, i, l, j))w^{+}(p(j))w^{+}(p(i | l))$.
-For the \ac{CPT} parameters, the values are those originally given by \citet{Tversky1992} and used in the actual simulations which are given fully in table \ref{tab:qt_params}.
-
-\begin{equation*}
-\begin{align*}
-\alpha &= 0.88\\
-\gamma &= 0.61\\
-p(l) &= \frac{1}{6}\\
-p(m) &= \frac{1}{6}\\
-p(h) &= \frac{2}{3}\\
-p(r | l) &= \frac{1}{4}\\
-p(n | l) &= \frac{3}{4}\\
-u_{w}(l, i, l, j) &= 10\\
-f&=(10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{6},10;\frac{1}{2})\\
-f^{+}&=f,f^{-}=()\\
-n &= 5\\
-v(u_{w}) &= f(u_{w}) = u_{w}^\alpha\\
-v(u_{w}) &= 10^{0.88} = 7.59\\
-\pi_{0}^{+}&=w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(1) - w^{+}(\frac{23}{24})\\
-&=0.19\\
-\pi_{1}^{+}&=w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(\frac{23}{24}) - w^{+}(\frac{5}{6})\\
-&= 0.17\\
-\pi_{2}^{+}&=w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(\frac{5}{6}) - w^{+}(\frac{19}{24})\\
-&= 0.04\\
-\pi_{3}^{+}&=w^{+}(\frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{6} + \frac{1}{2})=w^{+}(\frac{19}{24}) - w^{+}(\frac{2}{3})\\
-&= 0.09\\
-\pi_{4}^{+}&=w^{+}(\frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{2})=w^{+}(\frac{2}{3}) - w^{+}(\frac{1}{2})\\
-&= 0.09\\
-\pi_{5}^{+}&=w^{+}(\frac{1}{2})\\
-&= 0.42\\
-V(f) &= V(f^{+}) + V(f^{-}) = V(f^{+}) + 0\\
-V(f^{+}) &= \sum_{i}^{n}\pi_{i}^{+}(f^{+})v_{i}^{+}(f^{+}) = 7.59
-\end{align*}
-\end{equation*}
-
-And as before, following the same process for moderate, and heavy signals which yields respectively 7.14, and 6.22, the agent chooses the higher valued action and sends an honest signal.
-
 \subsection{Information Sharing}

### 2015-06-17 simulation_schedule.tex
Reducing the pagecount
Substantially.

@@
 
-In this section we provide psuedocode for a single simulation, which encompasses several games.
+In this section we give the step by step process for a single run of the disclosure game simulation.
 
-\begin{algorithm}
-\begin{algorithmic}
-\State $rounds \gets 1000, appointments \gets 12$
-\State women \gets enqueue([], $w_{1},\ldots,w_{1000}$), midwives \gets [$m_{1},\ldots,m_{100}$]
-\While{$rounds > 0$}
-	\State players $\gets$ dequeue first 100 women
-	\State referred $\gets$ []
-	\State $i $\gets$ 1$
-	\While{$i < 100$}
-		\State woman $\gets$ players[i], midwife $\gets$ midwives[i]
-		\State signal $\gets$ signal(woman)
-		\State response $\gets$ respond(midwife)
-		\State midwife's memory $\gets$ woman, signal, response
-		\State woman's memory $\gets$ type(midwife), signal, response, $X_{w, s, r, type(woman), type(midwife)}$
-		\State update woman's beliefs
-		\If{$response = refer$}
-			\State midwife's memory $\gets$ type(woman), $X_{m, s, r, type(woman)}$
-			\State retrospectively update midwife's beliefs
-			\State women $\gets$ enqueue(women, new woman)
-			\State Add woman to referred
-		\Else
-			women $\gets$ enqueue(women, woman)
-		\EndIf
-	\EndWhile
-	\For{woman in referred}
-		\If{$random \lt p$}
-			\For{player in women}
-
-			\EndFor
-		\EndIf
-	\EndFor
-\State $rounds \gets rounds - 1$
-\EndWhile
-\end{algorithmic}
-\caption{Simulation schedule\label{alg:sim}}
-\end{algorithm}
+\begin{itemize}
+\item Generate 1000 women, and place them in a queue
+\item Generate 100 midwives.
+\item For each round of the game
+\begin{itemize}
+\item Take 100 women from the queue
+\item Pair each one with a random midwife
+\item For each pair
+\begin{itemize}
+\item Woman sends a signal
+\item Midwife refers or not based on the signal
+\item Woman is informed of their payoff, the midwife's type, and whether they are referred
+\item If the woman is referred
+\begin{itemize}
+\item The midwife is informed of the woman's true type
+\item The midwife retrospectively updates their beliefs using the true type, and memories of any games with this woman
+\item The midwife is now eligible to share their memories of games with this woman
+\end{itemize}
+\end{itemize}
+\item Women who have not been referred, or had their baby join the back of the queue
+\item Generate new women to replace those referred, or delivered
+\item Add new women to the back of the queue
+\item For each referred or birthed woman
+\begin{itemize}
+\item With probability p, their memory of games is shared with the active women
+\item They are removed from simulation
+\end{itemize}
+\item For each midwife with information to share
+\begin{itemize}
+\item With probability p, their memory of games with the referred woman is shared
+\item The memory is no longer eligible to be shared
+\end{itemize}
+\end{itemize}
+\end{itemize}

### 2015-06-18 Conclusion.tex
Trimming length

@@
 By contrast, the belief structure of the \ac{CPT}, and Bayesian models represents a useful abstraction which allows the use of the relevant aspects of the information.
-Naturally, incorporating homophily, by, for example weighting shared information by the type of the sharer, would represent a relatively trivial modification to the heuristic models.
-While to some extent this highlights the flexibility of the decision rule approach, it would of course sacrifice the parsimony of the model to a degree.
-This is an important consideration, given that part of the argument in favour of a decision theoretic approach to agent building lies in the minimal nature of the behavioural rules, which can be seen as occupying a middle ground between parameter and model.
+Naturally, incorporating homophily, by, for example weighting shared information by the type of the sharer, would represent a trivial modification to the heuristic models.
+While to some extent this highlights the flexibility of the decision rule approach, it would of course sacrifice the parsimony of the model.
+This is an important consideration, given that part of the argument in favour of a decision theoretic approach lies in the minimal nature of the behavioural rules, which can be seen as occupying a middle ground between parameter and model.
 
@@
 
-In reality it might be anticipated that midwives would not withhold judgement so completely, and would pass on concerns about specific women to their colleagues, or that particularly dramatic stories would persist and be passed.
+In reality it might be anticipated that midwives would not withhold judgement, and would pass on concerns about specific women to their colleagues, or that particularly dramatic stories would persist and be passed.
 This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared and more sophisticated model of information transmission in general.
-This also highlights an advantage of the \ac{BACCO} approach, in that it aids in diagnosing issues with model design by giving insight into parameters which are contributing inappropriately to variance in output.
+This also highlights an advantage of the \ac{BACCO} approach, in diagnosing issues with model design by giving insight into parameters which are contributing inappropriately to variance in output.
 Coupled with the ability of emulators to rapidly explore parameter space, this clearly suggests that statistical emulation is a powerful tool to support simulation based approaches.

### 2015-06-18 Introduction.tex
Trimming length

@@
 The case in favour of \ac{ABM} as a general analytical approach has been made numerously, and elegantly (e.g.
-\citet{epstein1994growing,Resnick,Axelrod1997,gilbert1999simulation,Macy2002a,Silverman2011,Silverman2013,epstein2014agent_zero}, amongst others).
+\cite{epstein1994growing,Resnick,Axelrod1997,gilbert1999simulation,Macy2002a,Silverman2011,Silverman2013,epstein2014agent_zero}, amongst others).
 As such we will not belabour the point, and instead turn to addressing some of the concerns expressed about the approach.
-In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, tending to be a reflection of the assumptions of the modeller rather than empirically or theoretically grounded \citep{Waldherr2013}.
+In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, reflecting the assumptions of the modeller rather than empirically or theoretically grounded \citep{Waldherr2013}.
 To ameliorate this concern, we draw on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game\footnote{In a signalling game, one player (the signaller), has some piece of information that is known only to them which affects the outcome of the game for both players.
@@
 This exercise is framed in the context of disclosure decisions, taking drinking patterns in pregnant women as a motivating example.
-Alcohol consumption in the antenatal period is a significant issue in itself, and has been associated with many potentially negative consequences.
-For example, \citet{Andersen2012} report results from a large scale Danish cohort study suggesting that even low levels of consumption in early pregnancy increase the risk of spontaneous abortion, although \citet{Savitz2012} has suggested this may be attributable to a previously known link to absence of mornining sickness.
-Risk continues to the point of birth - \citet{Kesmodel2002} found a heightened risk to the infant - into childhood, with a metastudy by \citet{Latino-Martel2010} finding evidence on an increased risk of childhood \ac{AML}.
-Harm may also extend even further, and a review by \citet{Huizink2006} concluded that maternal alcohol consumption could be a contributing factor to \ac{ADHD}, and other learning impairments, but note methodological issues in a number of the papers.
-There is not, however, a clear consensus, with \citet{Gray2006} finding no evidence of harm below 1.5 UK units\footnote{Roughly half a pint of beer, a single 25ml measure of spirits, or one 175ml glass of wine.} per day.
+Alcohol consumption in the antenatal period is a significant issue in itself, although there is not, a clear consensus, with \citet{Gray2006} finding no evidence of harm below 1.5 UK units\footnote{Roughly half a pint of beer, a single 25ml measure of spirits, or one 175ml glass of wine.} per day.
 In terms of official guidance in the UK, \ac{NICE} acknowledge that evidence of harm to the fetus is less than conclusive, but advise not drinking at all, or significant moderation \citep{NICE2010a}, with similar advice from the UK \cite{DepartmentofHealth2008}.
@@
 Fundamentally, the shift of emphasis is from the process of acquiring and inferring the information needed to make choices, to the process of decision.
-Naturally, this does not preclude the incorporation of strategic refinement, since decision rules are to a great extent modular, and as demonstrated in this paper can be exchanged without altering the underpinning decision problem.
-In addition, rules are agnostic as to where the information used derives from, suggesting room for multi-stage processes.
-As a corollary, the decision problem agents attempt to answer can change, allowing agents' behaviour in novel problems to be informed by beliefs derived under other conditions.
+This does not preclude a strategic dimension, since decision rules are to a great extent modular, and as demonstrated in this paper can be exchanged without altering the decision problem.
+In addition, rules are agnostic as to where the source of information, suggesting room for multi-stage processes.
+As a corollary, the decision problem agents attempt to answer can change, allowing behaviour in novel problems to be informed by beliefs derived under other conditions.
 This is also indicative of the broader benefits to \ac{ABM} as an approach.
@@
 Many key aspects common to decision rules, for example the idea that a common currency is used by the brain to compare outcomes \citep{Padoa-Schioppa2006,Padoa-Schioppa2008}, are supported by neurological findings.
-In addition, a single decision rule represents a pleasingly parsimonious alternative to numerous case specific production rules.
+In addition, a single decision rule represents a parsimonious alternative to numerous case specific production rules.
 

### 2015-06-18 Methods.tex
Trimming length

@@
 
-Parameters for training were generated in R \citep{RTeam2014} using Latin Hypercube Sampling \citep{Carnell2012} over the space of parameters given in table \ref{tab:sa_params}, giving eleven free parameters which were treated as uniformly distributed in the range given.
-Initially a unit hypercube was generated, then the margins transformed appropriately to cover those regions where the inputs are not bounded between 0 and 1, and for proportions of agent types which necessarily sum to one across the three parameters.
+Parameters for training were generated in R \citep{RTeam2014} using and appropriately transformed Latin Hypercube Sample \citep{Carnell2012} over the space of parameters given in table \ref{tab:sa_params}, giving eleven free parameters which were treated as uniformly distributed in the range given.
 Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each, with emulator quality assessed by leave-one-out cross validation.
@@
 
-Measurements were taken at the end of 1000 rounds of play, and emulators were built against the median, and interquartile range of each measure to assess both the overall trend, and the extent to which the parameters contribute to variance between runs.
+Measurements were taken at the end of 1000 rounds of play, and emulators were built against the median, and \ac{IQR} of each measure to assess both the overall trend, and the extent to which the parameters contribute to variance between runs.
 
-Sixteen emulators were built, covering each of the four outputs on all four decision models.
-These emulators were used to conduct a probabilistic sensitivity analysis using \ac{GEM-SA} to assess the impact of parameters individually, and in combination.
+Sixteen emulators were built, covering each of the four outputs on all decision models and used to conduct a probabilistic sensitivity analysis to assess the impact of parameters and interactions.
 

### 2015-06-18 Results.tex
Trimming length

@@
 Trends for all four rules are broadly similar, exhibiting a gradual increase across appointments which subsequently levels off.
-This levelling can in part be explained by the referral results (figure \ref{fig:referrals}), which show that the majority of drinkers are referred, even with substantial concealment.
+This levelling can in part be explained by the referral results, which show that the majority of drinkers are referred, even with substantial concealment.
 Referrals continue to occur, in the absence of honest signals, because drinkers are able to achieve a referral by masquerading as higher or lower types, dependent on how their initial beliefs are biased.
@@
 
-\begin{figure}[H]
-\includegraphics[width=119mm]{figures/ref_plot}
-\caption{Average fraction of population referred after 1000 rounds, mean with 95\% confidence limit over 1000 runs\label{fig:referrals}}
-\end{figure}
-
 \subsection{Social Learning}
@@
 Figure \ref{fig:honest_sharing} shows the proportion of women who have signalled honestly at least once by their final appointment, under four sharing conditions.
-Aside from the lexicographic decision rule, the general tendency is towards less honest signalling by heavy drinkers, but figure \ref{fig:ref_sharing} shows a slight increase in referrals for the Bayesian, and \ac{CPT} rules.
+Aside from the lexicographic decision rule, the general tendency is towards less honest signalling by heavy drinkers, which is accompanied by a slight increase in referrals for the Bayesian, and \ac{CPT} rules.
 For these decision models, this is because social learning exacerbates the existing tendency of heavy drinkers to impersonate moderate drinkers, who behave more honestly as heavy drinkers become less so.
@@
 \label{fig:honest_sharing}
-\end{figure}
-
-\begin{figure}[H]
-\begin{adjustbox}{center}
-\includegraphics[width=119mm]{figures/ref_sharing}
-\end{adjustbox}
-\caption{Impact of social learning on referral trends after 1000 rounds, mean with 95\% confidence interval over 100 runs}
-\label{fig:ref_sharing}
 \end{figure}
@@
 
-Following from the suggestive results for social learning introducing uncertainty (section \ref{sub:info_sharing}), figure \ref{fig:emulated_sharing_iqr} shows emulated points covering the parameter space in high resolution.
+Following from the suggestive results for social learning introducing uncertainty (section \ref{sub:sharing_results}), figure \ref{fig:emulated_sharing_iqr} shows emulated points covering the parameter space in high resolution.
 These plots reflect the increase in uncertainty of outcome shown for the heuristic type rules, which is especially severe for the Bayesian payoff rule.

### 2015-06-18 abstract_short.tex
Trimming length

@@
 
-In simulation, we recreate two key qualitative trends described in the midwifery literature for all the decision models, and investigate the impact of introducing a simple form of information sharing within agent groups.
+In simulation, we recreate two key qualitative trends described in the midwifery literature for all the decision models, and investigate the impact of introducing a simple form of social learning within agent groups.
 Finally a global sensitivity analysis using \acp{GEM} is conducted, to compare the response surfaces of the different decision rules in the game.

### 2015-06-18 Model.tex
Rejigging btw appendices and body

@@
 In addition, the ability to observe the system in a state of flux rather than at equilibrium is desirable, since even where a social system reaches a stable state, the process by which we arrive at it is significant.
+
+\subsection{Disclosure Game}
+\label{sub:the_game}
+%Outline how the scenario translates into a game.
+%Brief mention of the game theoretic solution
+
+In order to translate the scenario sketched above into a more abstract, tractable form, we cast it as a signalling game, and assume that women's disclosures (or not), are signals.
+We also make the simplifying assumption that a woman may have one of only three drinking patterns - light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy.
+Correspondingly, they are limited in what signals they may send when claiming to be one of these three types.
+
+Midwives are treated in a similar fashion, where their type corresponds to how negatively they regard a drinking pattern - non-judgemental, moderately judgemental, and harshly judgemental.
+The expression of this judgement is not a matter of choice on their part, and is assumed to have no impact on their clinical response, which is to either refer the woman for specialist treatment, or do nothing.
+
+At the end of a game, each player receives a payoff dependent on the actions and types of both players.
+Because both women and midwives have an interest in the outcome of the pregnancy, and would prefer a healthy baby, the payoff has a common interest component.
+Hence, both players receive a payoff based on the outcome of pregnancy, but women bear a social cost dependent on the signal they sent and the midwife's reaction to it.
+Similarly, midwives pay a cost if they refer to a specialist, mirroring the organisational cost of non-routine care.
+Table \ref{tab:Payoff-matrix} shows the three payoff matrices which together describe the game.
+
+As an example, consider the challenge faced by an agent of the heavy drinking type.
+In order to get the best health outcome, they must be referred and would ideally achieve this without paying any social cost at all.
+The best move depends on the type, and beliefs of the midwife.
+For example, a particularly unlucky scenario might be for the midwife to not only be of a harshly judgemental disposition, but to believe that no women really need to be referred.
+Even a relatively weak belief in this possibility can make the honest signal look like an unwarranted risk.
+
+%Might belong in a more methody bit? Read some stuff to check..
+To formally define the game, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\).
+Here, \(\{l, m, h\}\) correspond to light, moderate, and heavy alcohol consumption for women, and non-judgemental, moderately judgemental, and harshly judgemental for midwives.
+Midwives' pure strategies \(\{r,n\}\) are to refer, or do nothing, and those for women are to signal that they have one of the possible drinking patterns.
+Additionally define two utility functions - 
+\begin{equation}
+u_{w}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}}
+\end{equation} 
+\begin{equation}
+u_{m}(s_{w}, s_{m}, \theta_{w})=X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}},
+\end{equation} with $X_{c}$, $X_{h}$, and $X_{s}$ being the payoff matrices as in table \ref{tab:Payoff-matrix}, $s_{w}$ and $s_{m}$ denoting a specific signal by a woman, and referral response by a midwife.
+Lastly let \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\) be distributions over types of women, and midwives respectively.
+
+As noted, rather than solve the game, we allow populations of agents to play it, and hence stipulate further that women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)).
+They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred, and a new player is drawn from the same distribution that produced the original players to replace them.
+If they are not referred, they rejoin the back of the queue after their appointment.
+In either case, they are informed of their payoff after each round and update their beliefs accordingly using one of the rules described in section \ref{sub:the_agents}.
+
+Midwives play for \(r_{m}\) rounds (\(r_{m}=1000\) in all experiments), and conduct appointments in parallel, i.e.
+if there are 5 midwives, then five women are drawn from the queue and assigned at random to the midwives.
+Unlike women, midwives are only informed of their payoff if they choose to make a referral.
+Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.
+
+\subsection{Social Learning}
+\label{sub:info_sharing}
+
+It would seem unreasonable to suppose that neither party recounts their experiences to their peers, and to explore the impact of this we also modify the game to introduce a simple form of information sharing within agent groups.
+This takes the form of having each agent share their memories with their colleagues with some probability \(q\).
+Individuals then incorporate shared information into their beliefs using weighted updates, such that a shared observation of a low type signal contributes to their beliefs by \(w\), and \(0\leq w\leq 1\) (i.e.
+\(n_{j} = n_{j} + w\)).
+Women share only when they have finished play, and provide their complete history of games, because they have accurate information about the outcomes.
+By the same rationale, midwives share only their history with the most recent woman they referred.
+Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{More precisely, memories of games remain, but it is assumed that only the most current information is relevant enough to be shared.}
+
+Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this exogenous information differently.
+The simple payoff based rule relies on a belief structure relating actions directly to rewards which is essentially model free.
+Because payoffs differ by the agent's private type, the information shared may not correspond to the experience of the listening agent in the same scenario.
+As a result, payoff reasoners have a belief bias towards the most common player type, and can believe in outcomes that are, for them, impossible.
+
+By contrast, representing the problem in terms of the probabilities of the individual lotteries imposes a model that abstracts the new information from payoffs, and allows the agent to discard implausible outcomes.
+This stronger assumption as to the static and known qualities of payoffs does however reduce the flexibility of the decision rule.

### 2015-06-18 agent_examples.tex
Rejigging btw appendices and body

\section{Agent Examples}
\label{sec:agent_eg}

This section provides a worked example for the learning and decision process of each agent model, focusing on the behaviour of the signalling agent.

\subsubsection{Lexicographic Heuristic}
\label{sub:lexico_eg}

As an example, take a light drinker who has played three rounds with a succession of particularly judgemental midwives, signalling honestly in two and claiming to be a moderate drinker in one. The most common outcome of the honest signal was a payoff of 10, which is clearly preferable to the 9 gained by claiming to be moderate. On that basis, they choose to signal honestly.

\subsubsection{Bayesian Payoff}
\label{sub:payoff_eg}

If we take our light drinker from the lexicographic case, and assume that they began with an uninformative prior. The 6 possible signal-payoffs pairings are then \([(l,10),(m,10),(h,10),(m,9),(h,9),(h,8)]\), with \(\alpha_{i}=1\) for all \(i\). After playing the three rounds, \(n_{l,10}=2\), and \(n_{m,9}=1\).

The agent then evaluates \(R_{w}\) for each signal, e.g. for the light signal:

\begin{equation*}
\begin{align*}
X &= \{10\}\\
R_{w}(l) &= \sum_{x \in X} -xp(x | l) = -10p(10 | l)\\
R_{w}(l) &= -10(\frac{\alpha_{l,10}+n_{l,10}}{\sum_{j}(\alpha_{j}+n_{j})}) = -10(\frac{1+2}{1+2})\\
R_{w}(l) &= -10(\frac{3}{3}) = -10
\end{align*}
\end{equation*}

and by the same method, \(R_{w}(m)=-9\frac{1}{3}\), and \(R_{w}(h)=-9\), concluding that signalling honestly is the best move.

\subsection{Bayesian Risk Minimisation}
\label{sub:bayes_eg}

Returning to our example agent, under this model the type of the midwife becomes salient, hence \(n_{h}=3\), and \(n_{l,n}=2\), \(n_{m,n}=1\). Their prior beliefs remain uninformative, i.e. \(\alpha_{j} = 1, j \in \{l,m,h\}\), \(\alpha_{i,j}=1,i \in \{r,n\}, j \in \{l,m,h\}\). As before, the agent evaluates \(R_{w}\) for the three signals, and the process for the light signal is given below -

\begin{equation*}
\begin{align*}
R_{w}(l, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(l, i, l, j)p(j)p(i | l)\\
R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l) - u_{w}(l, r, l, m)p(m)p(r | l) - u_{w}(l, n, l, m)p(m)p(n | l) \\
&\phantom{{}=1}- u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
u_{w}(l, i, l, j) &= 10\\
R_{w}(l, l) &= -10p(l)p(r | l) - 10p(l)p(n | l) - 10p(m)p(r | l) - 10p(m)p(n | l) - 10p(h)p(r | l) - 10p(h)p(n | l)\\
p(l) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
p(m) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
p(h) &= \frac{1 + 3}{1 + 1 + 1 + 3} = \frac{2}{3}\\
p(r | l) &= \frac{1 + 0}{1 + 1 + 2} = \frac{1}{4}\\
p(n | l) &= \frac{1 + 2}{1 + 1 + 2} = \frac{3}{4}\\
R_{w}(l, l) &= -10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{2}{3} \cdot \frac{1}{4} - 10\cdot \frac{2}{3} \cdot \frac{3}{4}\\
&= -10
\end{align*}
\end{equation*}

and similarly for moderate (\(R_{w}(m,l)=-9\frac{1}{3}\)), and heavy (\(R_{w}(h,l)=-8\frac{1}{2}\)) signals, once again concluding that honesty is the better option.

\subsection{Descriptive Decision Theory}
\label{sub:cpt_eg}

Once again, we return to the light drinker example.  The inferential aspects are identical with the more complex Bayesian risk minimisation algorithm, hence \(p(j)p(i | l)\), and \(u_{w}(l, i, l, j)\) remain the same, but the agent additionally calculates $v(u_{w}(l, i, l, j))w^{+}(p(j))w^{+}(p(i | l))$. For the \ac{CPT} parameters, the values are those originally given by \citet{Tversky1992} and used in the actual simulations which are given fully in table \ref{tab:qt_params}.

\begin{equation*}
\begin{align*}
\alpha &= 0.88\\
\gamma &= 0.61\\
p(l) &= \frac{1}{6}\\
p(m) &= \frac{1}{6}\\
p(h) &= \frac{2}{3}\\
p(r | l) &= \frac{1}{4}\\
p(n | l) &= \frac{3}{4}\\
u_{w}(l, i, l, j) &= 10\\
f&=(10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{6},10;\frac{1}{2})\\
f^{+}&=f,f^{-}=()\\
n &= 5\\
v(u_{w}) &= f(u_{w}) = u_{w}^\alpha\\
v(u_{w}) &= 10^{0.88} = 7.59\\
\pi_{0}^{+}&=w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(1) - w^{+}(\frac{23}{24})\\
&=0.19\\
\pi_{1}^{+}&=w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(\frac{23}{24}) - w^{+}(\frac{5}{6})\\
&= 0.17\\
\pi_{2}^{+}&=w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(\frac{5}{6}) - w^{+}(\frac{19}{24})\\
&= 0.04\\
\pi_{3}^{+}&=w^{+}(\frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{6} + \frac{1}{2})=w^{+}(\frac{19}{24}) - w^{+}(\frac{2}{3})\\
&= 0.09\\
\pi_{4}^{+}&=w^{+}(\frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{2})=w^{+}(\frac{2}{3}) - w^{+}(\frac{1}{2})\\
&= 0.09\\
\pi_{5}^{+}&=w^{+}(\frac{1}{2})\\
&= 0.42\\
V(f) &= V(f^{+}) + V(f^{-}) = V(f^{+}) + 0\\
V(f^{+}) &= \sum_{i}^{n}\pi_{i}^{+}(f^{+})v_{i}^{+}(f^{+}) = 7.59
\end{align*}
\end{equation*}

And as before, following the same process for moderate, and heavy signals which yields respectively 7.14, and 6.22, the agent chooses the higher valued action and sends an honest signal.

### 2015-06-18 agent_models.tex
Rejigging btw appendices and body

\subsection{Agent Models}
\label{sub:the_agents}
%Outline basic structure, then specifics on each one.
%This should probably go lexic -> bayes payoff -> bayes -> CPT in order
% of complexity.
%suggest there are added shells of complexity
%		mention the info sharing because homophilly
%			related - the enhancement to the bayes/cpt agents is that they personalise, as much as anything.
%		properly explain dirichlet priors
% How about comparing the decision problem representation for the agent types?

While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same outputs, we limit ourselves here to four. The simplest is a lexicographic rule (1), in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}. Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-output characteristics.

As noted in section \ref{sub:the_game}, agents have perfect recall, and midwives recognise women if they repeatedly encounter them. While agents recall perfectly and make use of the new information for retrospective updates, all four agent models make decisions `as-if' they were always facing a new \enquote{opponent}.

A simplifying assumption is made that all midwives have just qualified after receiving identical training. As a result, they have homogeneous beliefs about  women and assume to some extent that they are honest.
Women have heterogeneous beliefs, which correspond to experiencing \(k\) randomly chosen paths through the game, and following each path at least once.

\subsubsection{Lexicographic Heuristic}
\label{sub:lexico}

The lexicographic heuristic (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified problem representation, where an action is a choice between combined lotteries. Functionally, the heuristic maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e. one reason decision making. Where there is no clear best action, but one or more is evidently worse, a choice must be made as to whether to discard the poorer action; in this case we have elected to retain it.
This approach requires minimal computation, and does not assume that \(u_{i}\) is static, or known.

Women resolve this by approximating the utility function, as a function \(f(s_{w}, \sigma)\) on their choice of signal and an unknown distribution $\sigma$, which maps to \(u_{w}\) - i.e. \(s_{w}\) is a choice between simple lotteries. The algorithm maintains a count, \(n\), of the number of occurrences of each outcome given the choice from \(s_{w}\).

Midwives solve a slightly different problem with more information, where \(s_{w}\) is known, and \(s_{m}\) is the lottery choice - \(f(s_{w}, s_{m},\sigma)\). This is resolved by maintaining a separate count for each signal (i.e. \(n_{s_{w},s_{m}}\)), and otherwise following the same algorithm, presented below.

\begin{algorithm}
\begin{algorithmic}
\State $n \gets 1, action \gets none$
\While{$action = none$}
\State Calculate the $n$th most common outcome following each action.
\State Sort actions by the value of the $n$th most common outcome.
\If{clear winner} \State $action \gets best$ \EndIf
\State $n \gets n + 1$
\EndWhile
\State \Return action
\end{algorithmic}
\caption{Lexicographic heuristic\label{alg:lexico}}
\end{algorithm}

\subsubsection{Bayesian Payoff}

The Bayesian payoff agent uses the same subset of information as the lexicographic method, but updates beliefs on the link between actions and payoffs using the Bayes rule, and attempts to choose the action which minimises risk.

Given the discrete nature of actions and payoffs, coupled with a desire for tractability of the
simulation, the Dirichlet distribution is employed as a prior to represent these beliefs. The probability density function takes the form -

\begin{equation}
D(\Theta|\alpha)=\frac{\Gamma(\sum_{i=1}^{k}\alpha_{i})}{\prod_{i=1}^{k}\Gamma(\alpha_{i})}\overset{k}{\underset{i=1}{\prod}\Theta_{i}^{\alpha_{i-1}}}
\end{equation}

where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\) is the number
of signal-payoff pairs, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
more than zero and summing to less than 1, and \(\alpha_{i}\) is the 
pseudo-count of prior observations\footnote{Psuedo-counts are related to, but distinct from prior beliefs. Here, the psuedo-count is a parameter to the prior belief distribution and is nothing more than a hypothetical count of prior observations.} for a pair \(i\).

The distribution is particularly convenient, in that to infer the
probability of a signal implying a payoff becomes
simply -

\begin{equation}
p(x=j|D,\alpha)=\frac{\alpha_{j}+n_{j}}{\sum_{j}(\alpha_{j}+n_{j})}\label{eq:posterior}
\end{equation}

Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), so
that the belief that a signal will lead to a payoff is the number
of times that pairing has been observed (including the pseudo-count),
over the total number of observations thus far. This makes computation
of beliefs fast and simple, since all that must be maintained is
a count of observations with no particular concern as to their order.
As before, midwives follow a similar pattern but maintain \(n_{s_{w}}\) independent counts of pairings between referral choice and payoff, updating their beliefs about the relationship between the choice to refer and payoff given the signal they have received.

Agents then choose the strategy $s_{i}$ to minimise risk $R_{i}$, which is simply defined as - 
\begin{equation}
R_{w}(s_{w}) = \sum_{x \in X} -xp(x | s_{w})
\end{equation}
\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{x \in X} -xp(x | s_{w}\wedge s_{m}),
\end{equation}

where $X$ is the set of payoffs the agent has observed to follow $s_{i}$.

\subsubsection{Bayesian Risk Minimisation}

The second Bayesian agent augments the reasoning of the simple payoff model, making the stronger assumption that the utility function is static, and known. Women maintain two sets of beliefs, corresponding respectively to \(p_{m}\), and the probability of referral given signal choice. This leads to the risk function, minimised with respect to \(s_{w}\) -

\begin{equation}
R_{w}(s_{w}, \theta_{w}) = \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, \theta_{w}, j)p(j)p(i | s_{w}),
\end{equation}

so that the risk of a signal is the sum of the products of all payoffs with the probabilities of their entailed midwife types and responses.

Midwives reasoning centres on determining the meaning of signals, since given the knowledge of what some signal \(s_{w}\) conveys about the true type of the sender, the payoff for an action is known. As such, their inference process is the same as for the simple Bayesian agent but over signal-type pairs, and they attempt to minimise the following risk function, minimised with respect to \(s_{m}\) -

\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{m}(s_{w}, s_{m}, i)p(i | s_{w})
\end{equation}

\subsubsection{Descriptive Decision Theory}

The most complex decision rule used is \ac{CPT}, which attempts to reproduce a number of systematic deviations from rationality observed in humans. While \ac{CPT} has primarily been applied in the context of decisions from description, it has been modified to deal with decisions from experience by incorporating a first stage where probabilities are estimates from observations as in \cite{FoxCPT}. In this instance the Bayesian inference process fills the first stage role.

%Maybe cut this bit and make explanation richer?
Rather than the psychologically more interesting \ac{PT}, the \ac{CPT}
decision rule is used in this instance, because of the requirement
for women to evaluate the `prospects'\footnote{Where a prospect is a sequence of payoff-probability pairings in ascending order of payoff, associated with an action.} of more than two actions. \ac{CPT} uses transformed probabilities, underweighting
small probabilities, and overweighting large ones. This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and contrastingly low probabilities as impossible. The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains (eqn \ref{eqn:cpt_p_pos}) and losses (eqn \ref{eqn:cpt_p_neg}) -

\begin{align}
w^{+}(p) & = \frac{p^{\gamma}}{(p^{\gamma}+(1-p)^{\gamma})^{\frac{1}{\gamma}}}\label{eqn:cpt_p_pos}\\
w^{-}(p) & = \frac{p^{\delta}}{(p^{\delta}+(1-p)^{\delta})^{\frac{1}{\delta}}}\label{eqn:cpt_p_neg},
\end{align}

where $p$ is the unweighted probability, and $\gamma$ and $\delta$
are the weights for gain and loss probabilities respectively. Along similar lines, the values of losses and gains are transformed to reflect a tendency to regard a loss as more significant than a gain  -

\begin{equation}
v(u_{i})=\begin{cases}
f(u_{i}),& \text{if}\, u_{i}>0\\
0,& \text{if}\, u_{i}=0\\
\lambda g(u_{i}),& \text{if}\, x<0
\end{cases},
\end{equation}

where,

\begin{equation}
f(u_{i})=\begin{cases}
u_{i}^{\alpha},& \text{if}\,\alpha>0\\
\ln(u_{i}),& \text{if}\,\alpha=0\\
1-(1+u_{i})^{\alpha},& \text{if}\,\alpha<0
\end{cases}
\end{equation}
\begin{equation}
g(u_{i})=\begin{cases}
-(-u_{i})^{\beta},& \text{if}\,\beta>0\\
-\ln(-u_{i}),& \text{if}\,\beta=0\\
(1-u_{i})^{\beta}-1,& \text{if}\,\beta<0
\end{cases},
\end{equation}

and $\alpha$, and $\beta$ are respectively the power of a gain,
and a loss, and \(\lambda\) is a multiplier giving the aversion to loss.

Finally, the transformed probabilities are used to construct decision weights, \(\pi^{+},\pi^{-}\) for losses and gains, where,

\begin{equation}
\pi_{n}^{+}=w^{+}(p_{n})
\end{equation}
\begin{equation}
\pi_{-m}^{-}=w^{-}(p_{-m})
\end{equation}
\begin{equation}
\pi_{i}^{+}=w^{+}(p_{i}+\ldots+p_{n}) - w^{+}(p_{i+1}+\ldots+p_{n}),0\leq i \leq n - 1
\end{equation}
\begin{equation}
\pi_{i}^{-}=w^{-}(p_{-m}+\ldots+p_{i}) - w^{-}(p_{-m}+\ldots+p_{i-1}),1-m\leq i \leq 0
\end{equation}

The \ac{CPT} value of a single outcome prospect \(f=(u_{i};p_{i})\), is $v(u_{i})\pi^{+}(p_{i})$
if $u_{i}\geq0$, and $v(u_{i})\pi^{-}(p_{i})$ otherwise. For any given action the \ac{CPT}
value, \(V\) is the sum of the value of the prospects of that action, as
in the Bayesian risk model, and the agent chooses the option which maximises this quantity.

### 2015-06-18 model_description.tex
Rejigging btw appendices and body

@@
 Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.
-
-\subsection{Information Sharing}
-\label{sub:info_sharing}
-
-It would seem unreasonable to suppose that neither party recounts their experiences to their peers, and to explore the impact of this we also modify the game to introduce a simple form of information sharing within agent groups.
-This takes the form of having each agent share their memories with their colleagues with some probability \(q\).
-Individuals then incorporate shared information into their beliefs using weighted updates, such that a shared observation of a low type signal contributes to their beliefs by \(w\), and \(0\leq w\leq 1\) (i.e.
-\(n_{j} = n_{j} + w\)).
-Women share only when they have finished play, and provide their complete history of games, because they have accurate information about the outcomes.
-By the same rationale, midwives share only their history with the most recent woman they referred.
-Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{More precisely, memories of games remain, but it is assumed that only the most current information is relevant enough to be shared.}
-
-Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this exogenous information differently.
-The simple payoff based rule relies on a belief structure relating actions directly to rewards which is essentially model free.
-Because payoffs differ by the agent's private type, the information shared may not correspond to the experience of the listening agent in the same scenario.
-As a result, payoff reasoners have a belief bias towards the most common player type, and can believe in outcomes that are, for them, impossible.
-
-By contrast, representing the problem in terms of the probabilities of the individual lotteries imposes a model that abstracts the new information from payoffs, and allows the agent to discard implausible outcomes.
-This stronger assumption as to the static and known qualities of payoffs does however reduce the flexibility of the decision rule.

### 2015-06-18 Conclusion.tex
More reorganisation

@@
 In light of this, that there is a known impact of time on perceived utility \citet{Thaler1981} suggests that incorporating some form of temporal discounting (e.g.
-exponential \citep{Samuelson1937}, or hyperbolic \citep{Ainslie1991}), or a decision model which explicitly treats intertemporal choice, such as the \ac{CPT} like model of \citet{Loewenstein1992}, is warranted.
+exponential \citep{Samuelson1937}, or hyperbolic \citep{Ainslie1991}), or a decision model which explicitly treats intertemporal choice, such as the \ac{CPT}-like model of \citet{Loewenstein1992}, is warranted.
 

### 2015-06-18 Introduction.tex
More reorganisation

@@
 This exercise is framed in the context of disclosure decisions, taking drinking patterns in pregnant women as a motivating example.
-Alcohol consumption in the antenatal period is a significant issue in itself, although there is not, a clear consensus, with \citet{Gray2006} finding no evidence of harm below 1.5 UK units\footnote{Roughly half a pint of beer, a single 25ml measure of spirits, or one 175ml glass of wine.} per day.
+Alcohol consumption in the antenatal period is a significant issue in itself, although there is not a clear consensus on associated risk.
 In terms of official guidance in the UK, \ac{NICE} acknowledge that evidence of harm to the fetus is less than conclusive, but advise not drinking at all, or significant moderation \citep{NICE2010a}, with similar advice from the UK \cite{DepartmentofHealth2008}.

### 2015-06-18 Methods.tex
More reorganisation

@@
 \cite{Neilson2002,Nilsson2011,Glockner2012}, and particularly \citet{Byrnes1999} and \citet{Booij2009} addressing risk aversion and gender), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work.
-For simplicity, it was assumed that all three drinking types are equally prevalent within the population, although results derived from \ac{ALSPAC} suggest that the reality is far more positive\footnote{95.5\% of women in the sample reported consumption at, or below, \ac{NICE} recommended safe levels.} \citep{Humphriss2013}.
+For simplicity, it was assumed that all three drinking types are equally prevalent within the population, although results derived from \acl{ALSPAC} suggest that the reality is far more positive\footnote{95.5\% of women in the sample reported consumption at, or below, \ac{NICE} recommended safe levels.} \citep{Humphriss2013}.
 The scenario was biased towards disclosure as the better option by presuming a distribution of midwives strongly skewed towards non-judgemental types, with beliefs initially favouring honesty.

### 2015-06-18 agent_examples.tex
More reorganisation

@@
 
-\subsubsection{Lexicographic Heuristic}
+\subsection{Lexicographic Heuristic}
 \label{sub:lexico_eg}
@@
 
-\subsubsection{Bayesian Payoff}
+\subsection{Bayesian Payoff}
 \label{sub:payoff_eg}
@@
 The inferential aspects are identical with the more complex Bayesian risk minimisation algorithm, hence \(p(j)p(i | l)\), and \(u_{w}(l, i, l, j)\) remain the same, but the agent additionally calculates $v(u_{w}(l, i, l, j))w^{+}(p(j))w^{+}(p(i | l))$.
-For the \ac{CPT} parameters, the values are those originally given by \citet{Tversky1992} and used in the actual simulations which are given fully in table \ref{tab:qt_params}.
+For the \ac{CPT} parameters, the values are those originally given by \citet{Tversky1992} and used in the actual simulations which are given fully in table \ref{tab:cpt_params}.
+
+\begin{table}
+\begin{tabular}{|l | l | c|}
+\hline
+Name & Description & Value \\ \hline
+\(\gamma\) & Probability weighting for gains  & 0.61 \\ \hline
+\(\delta\) & Probability weighting for losses &  0.69\\ \hline
+\(\alpha\) & Power for gains  & 0.88 \\ \hline
+\(\beta\) & Power for losses & 0.88 \\ \hline
+\(\lambda\) & Loss aversion &  2.25 \\ \hline
+\end{tabular}
+\caption[Table caption text]{Model parameters. \label{tab:cpt_params}}
+\end{table}
 

### 2015-06-18 agent_models.tex
More reorganisation

@@
 
-As noted in section \ref{sub:the_game}, agents have perfect recall, and midwives recognise women if they repeatedly encounter them.
-While agents recall perfectly and make use of the new information for retrospective updates, all four agent models make decisions `as-if' they were always facing a new \enquote{opponent}.
+Agents have perfect recall, midwives recognise women if they repeatedly encounter them, making use of new information for retrospective updates.
+However, all four agent models make decisions `as-if' they were always facing a new \enquote{opponent}.
 
@@
 This is resolved by maintaining a separate count for each signal (i.e.
-\(n_{s_{w},s_{m}}\)), and otherwise following the same algorithm, presented below.
+\(n_{s_{w},s_{m}}\)), and otherwise following the same algorithm (\ref{alg:lexico}).
 
@@
 The most complex decision rule used is \ac{CPT}, which attempts to reproduce a number of systematic deviations from rationality observed in humans.
-While \ac{CPT} has primarily been applied in the context of decisions from description, it has been modified to deal with decisions from experience by incorporating a first stage where probabilities are estimates from observations as in \cite{FoxCPT}.
+Rather than risk, `prospects', the sequence of payoff-probability pairings in ascending order of payoff, associated with an action  are used as decision criteria.
+While \ac{CPT} has primarily been applied in the context of decisions from description, it has been modified to deal with decisions from experience by incorporating a first stage where probabilities are estimates from observations \cite{FoxCPT}.
 In this instance the Bayesian inference process fills the first stage role.
@@
 %Maybe cut this bit and make explanation richer?
-Rather than the psychologically more interesting \ac{PT}, the \ac{CPT}
-decision rule is used in this instance, because of the requirement
-for women to evaluate the `prospects'\footnote{Where a prospect is a sequence of payoff-probability pairings in ascending order of payoff, associated with an action.} of more than two actions.
-\ac{CPT} uses transformed probabilities, underweighting
-small probabilities, and overweighting large ones.
+\ac{CPT} uses transformed probabilities, underweighting small probabilities, and overweighting large ones.
 This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and contrastingly low probabilities as impossible.

### 2015-06-18 build.sh
More trimming

@@ -1,11 +1,4 @@
 #!/bin/sh
-rm disclosure_game.aux
-rm disclosure_game.bbl
-rm disclosure_game.blg
-rm disclosure_game.idx
-rm disclosure_game.log
-rm disclosure_game.out
-rm disclosure_game.pdf
 latex -interaction=batchmode disclosure_game
 makeglossaries disclosure_game
 bibtex disclosure_game

### 2015-06-19 agent_examples.tex
More trimming
Placement juggling

@@
+%!TEX root = disclosure_game.tex
 \section{Agent Examples}
@@
 \begin{equation*}
-\begin{align*}
+\begin{aligned}
 X &= \{10\}\\
@@
 R_{w}(l) &= -10(\frac{3}{3}) = -10
-\end{align*}
+\end{aligned}
 \end{equation*}
@@
 \(\alpha_{j} = 1, j \in \{l,m,h\}\), \(\alpha_{i,j}=1,i \in \{r,n\}, j \in \{l,m,h\}\).
-As before, the agent evaluates \(R_{w}\) for the three signals, and the process for the light signal is given below -
+As before, the agent evaluates \(R_{w}\) for the three signals, and the process for the light signal is given below.
 
 \begin{equation*}
-\begin{align*}
+\begin{aligned}
 R_{w}(l, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(l, i, l, j)p(j)p(i | l)\\
-R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l) - u_{w}(l, r, l, m)p(m)p(r | l) - u_{w}(l, n, l, m)p(m)p(n | l) \\
-&\phantom{{}=1}- u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
+R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l) - u_{w}(l, r, l, m)p(m)p(r | l)\\
+&\phantom{{}=1}- u_{w}(l, n, l, m)p(m)p(n | l) - u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
 u_{w}(l, i, l, j) &= 10\\
-R_{w}(l, l) &= -10p(l)p(r | l) - 10p(l)p(n | l) - 10p(m)p(r | l) - 10p(m)p(n | l) - 10p(h)p(r | l) - 10p(h)p(n | l)\\
+R_{w}(l, l) &= -10p(l)p(r | l) - 10p(l)p(n | l) - 10p(m)p(r | l) - 10p(m)p(n | l)\\
+&\phantom{{}=1} - 10p(h)p(r | l) - 10p(h)p(n | l)\\
 p(l) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
@@
 &= -10
-\end{align*}
+\end{aligned}
 \end{equation*}
@@
 The inferential aspects are identical with the more complex Bayesian risk minimisation algorithm, hence \(p(j)p(i | l)\), and \(u_{w}(l, i, l, j)\) remain the same, but the agent additionally calculates $v(u_{w}(l, i, l, j))w^{+}(p(j))w^{+}(p(i | l))$.
-For the \ac{CPT} parameters, the values are those originally given by \citet{Tversky1992} and used in the actual simulations which are given fully in table \ref{tab:cpt_params}.
+For the \ac{CPT} parameters, the values are those originally given by \citet{Tversky1992} and used in the actual simulations which are given in table \ref{tab:cpt_params}.
 
@@
 \end{tabular}
-\caption[Table caption text]{Model parameters. \label{tab:cpt_params}}
+\caption[Table caption text]{\ac{CPT} parameters. \label{tab:cpt_params}}
 \end{table}
@@
 \begin{equation*}
-\begin{align*}
+\begin{aligned}
 \alpha &= 0.88\\
@@
 V(f^{+}) &= \sum_{i}^{n}\pi_{i}^{+}(f^{+})v_{i}^{+}(f^{+}) = 7.59
-\end{align*}
+\end{aligned}
 \end{equation*}

### 2015-06-19 disclosure_game.tex
Grayscale friendliness, spelling
Change info sharing to social learning
Begin moving model description to appendix. Also add an explanation of
pseudo-counts vs priors.
Simulation schedule
Reducing the pagecount
Substantially.
Trimming length
More reorganisation
Placement juggling

@@
 % RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass{svmult}
-
+\documentclass[graybox]{svmult}
+\usepackage[hyperfootnotes=false]{hyperref}
+\hypersetup{bookmarksdepth=3}
 % choose options for [] as required from the list
@@
  \usepackage{csquotes}
-\newboolean{enable-backrefs} % enable backrefs in the bibliography
-\setboolean{enable-backrefs}{true} % true false
-\newcommand{\backrefnotcitedstring}{\relax}%(Not cited.)
-\newcommand{\backrefcitedsinglestring}[1]{(Cited on page~#1.)}
-\newcommand{\backrefcitedmultistring}[1]{(Cited on pages~#1.)}
-\ifthenelse{\boolean{enable-backrefs}}%
-{%
-		\PassOptionsToPackage{hyperpageref}{backref}
-		\usepackage{backref} % to be loaded after hyperref package
-		   \renewcommand{\backreftwosep}{ and~} % separate 2 pages
-		   \renewcommand{\backreflastsep}{, and~} % separate last of longer list
-		   \renewcommand*{\backref}[1]{}  % disable standard
-		   \renewcommand*{\backrefalt}[4]{% detailed backref
-		      \ifcase #1 %
-		         \backrefnotcitedstring%
-		      \or%
-		         \backrefcitedsinglestring{#2}%
-		      \else%
-		         \backrefcitedmultistring{#2}%
-		      \fi}%
-}{\relax}
+ \usepackage{amsmath}
+
 \usepackage{comment}
  \usepackage{natbib}
- \setcitestyle{authoryear,round,aysep={,}}
+ \setcitestyle{numbers,square}
 % \usepackage{hyperref}
@@
 % \usepackage{nomencl}
-
 \makeindex
@@
 
-\author{Jonathan Gray \and Jakub Bijak \and Seth Bullock}
+\author{Jonathan Gray, Jakub Bijak, and Seth Bullock}
 % Use \authorrunning{Short Title} for an abbreviated version of
@@
 
-\input{Abstract}
+\input{abstract_short}
 \acresetall
@@
 
-\input{Background}
+%\input{Background}
 
 \input{Model}
+\input{agent_models}
 
@@
 \bibliographystyle{spbasic}
-
-\appendix
-\setcounter{table}{0}
-\renewcommand{\thetable}{A\arabic{table}}
 \input{SensitivityAnalysis}
+\input{model_description}
+\input{simulation_schedule}
+\input{agent_examples}
 \end{document}

### 2015-06-19 model_description.tex
Placement juggling

@@
+%!TEX root = disclosure_game.tex
 \section{Model Description}
-\label{app:detail_model_description}
+\label{app:model_description}
 
@@
 \begin{figure}[H]
-\begin{adjustbox}{center}\subfloat[Women (heavy drinkers)]{\includegraphics[width=119mm]{figures/women_influence}}\end{adjustbox}
-\vskip
-\begin{adjustbox}{center}\subfloat[Midwives]{\includegraphics[width=119mm]{figures/mw_influence}}\end{adjustbox}
+\centering
+\subfloat[Women (heavy drinkers)]{\includegraphics[width=119mm]{figures/women_influence}}
+\vskip\baselineskip
+\subfloat[Midwives]{\includegraphics[width=119mm]{figures/mw_influence}}
 \caption{Influence diagrams, showing the game broken into two decision problems. Squares indicate a decision node, while circles are (from the perspective of the agent) chance nodes}

### 2015-06-22 Model.tex
Move payoff matrices back to main body

@@
 
+\begin{table}
+\center
+\subfloat[Social cost, \(X_{s}\), for women, given their signal, and the midwife's type\label{tab:Social-cost-matrix}]{%
+\begin{tabular}{|c|c|c|c|c|}
+\cline{3-5} 
+\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
+
+\hline
+\multirow{4}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
+\cline{2-5} 
+ & Harsh & -2 & -1 & 0\tabularnewline
+\cline{2-5} 
+ & Moderate & -1 & 0 & 0\tabularnewline
+\cline{2-5} 
+ & Non & 0 & 0 & 0\tabularnewline
+\hline 
+\end{tabular}
+
+}
+
+\subfloat[Health outcome, \(X_{h}\), for women and midwives, given the midwife's action, and woman's type\label{tab:Referral-payoff-matrix}]{%
+\begin{tabular}{|c|c|c|c|c|}
+\cline{3-5} 
+\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
+
+\hline 
+\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
+\cline{2-5} 
+ & Refer & 10 & 10 & 10\tabularnewline
+\cline{2-5} 
+ & Don't refer & -2 & -1 & 10\tabularnewline
+\hline 
+\end{tabular}
+
+}
+
+\subfloat[Referral cost, \(X_{c}\), for midwife, given their action and the woman's type\label{tab:inst_cost_matrix}]{%
+\begin{tabular}{|c|c|c|c|c|}
+\cline{3-5}  
+\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
+\hline 
+\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
+\cline{2-5} 
+ & Refer & -9 & -9 & -9 \tabularnewline
+\cline{2-5} 
+ & Don't refer & 0 & 0 & 0\tabularnewline
+\hline 
+\end{tabular}
+
+}
+
+\caption{Payoff matrices\label{tab:Payoff-matrix}}
+\end{table}
+
 As an example, consider the challenge faced by an agent of the heavy drinking type.
@@
 
-It would seem unreasonable to suppose that neither party recounts their experiences to their peers, and to explore the impact of this we also modify the game to introduce a simple form of information sharing within agent groups.
-This takes the form of having each agent share their memories with their colleagues with some probability \(q\).
+In reality, learning is not exclusively from personal experience, and social learning plays an important role.
+In the disclosure game model, this takes the form of having each agent recount their play history to their colleagues with some probability \(q\).
 Individuals then incorporate shared information into their beliefs using weighted updates, such that a shared observation of a low type signal contributes to their beliefs by \(w\), and \(0\leq w\leq 1\) (i.e.

### 2015-06-22 model_description.tex
Move payoff matrices back to main body

@@
 Table \ref{tab:Payoff-matrix} shows the three payoff matrices which together describe the game.
-
-\begin{table}
-\center
-\subfloat[Social cost, \(X_{s}\), for women, given their signal, and the midwife's type\label{tab:Social-cost-matrix}]{%
-\begin{tabular}{|c|c|c|c|c|}
-\cline{3-5} 
-\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
-
-\hline
-\multirow{4}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
-\cline{2-5} 
- & Harsh & -2 & -1 & 0\tabularnewline
-\cline{2-5} 
- & Moderate & -1 & 0 & 0\tabularnewline
-\cline{2-5} 
- & Non & 0 & 0 & 0\tabularnewline
-\hline 
-\end{tabular}
-
-}
-
-\subfloat[Health outcome, \(X_{h}\), for women and midwives, given the midwife's action, and woman's type\label{tab:Referral-payoff-matrix}]{%
-\begin{tabular}{|c|c|c|c|c|}
-\cline{3-5} 
-\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
-
-\hline 
-\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
-\cline{2-5} 
- & Refer & 10 & 10 & 10\tabularnewline
-\cline{2-5} 
- & Don't refer & -2 & -1 & 10\tabularnewline
-\hline 
-\end{tabular}
-
-}
-
-\subfloat[Referral cost, \(X_{c}\), for midwife, given their action and the woman's type\label{tab:inst_cost_matrix}]{%
-\begin{tabular}{|c|c|c|c|c|}
-\cline{3-5}  
-\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
-\hline 
-\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
-\cline{2-5} 
- & Refer & -9 & -9 & -9 \tabularnewline
-\cline{2-5} 
- & Don't refer & 0 & 0 & 0\tabularnewline
-\hline 
-\end{tabular}
-
-}
-
-\caption{Payoff matrices\label{tab:Payoff-matrix}}
-\end{table}
 

### 2015-06-22 Introduction.tex
Remove bg from intro

@@
 
-The remainder of this paper proceeds to provide a brief review of the methodological context (section \ref{sec:lit_review}), before outlining the proposed approach to model development (section \ref{sec:model}), and experiments (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}).
+The remainder of this paper proceeds to outline the proposed approach to model development (section \ref{sec:model}), and experiments (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}).

### 2015-06-22 Results.tex
More trimming
Remove bg from intro

@@
 
-\begin{figure}[H]
+\begin{figure}[h]
 \includegraphics[width=119mm]{figures/honesty_plot}
@@
 Figure \ref{fig:honest_sharing} shows the proportion of women who have signalled honestly at least once by their final appointment, under four sharing conditions.
+
+\begin{figure}
+\begin{adjustbox}{center}
+\includegraphics[width=119mm]{figures/honesty_sharing}
+\end{adjustbox}
+\caption{Impact of social learning on trends in honest signalling after 1000 rounds, mean with 95\% confidence interval over 100 runs}
+\label{fig:honest_sharing}
+\end{figure}
+
 Aside from the lexicographic decision rule, the general tendency is towards less honest signalling by heavy drinkers, which is accompanied by a slight increase in referrals for the Bayesian, and \ac{CPT} rules.
@@
 
-Particularly notable, is the decline in honest signalling by light drinkers visible in both heuristic type rules at the 0.25 level of \(q_{w}\) \& \(w_{w}\), and the associated increase in false positives.
+Particularly notable, is the decline in honest signalling by light drinkers visible in both heuristic type rules at the 0.25 level of \(q_{w}\) \& \(w_{w}\), which is associated with an increase in false positives.
 This arises because of the lack of homophily in social learning, as light drinkers become informed about negative outcomes associated with concealment, despite having nothing to conceal.
@@
 This suggests that social learning, for the heuristic style decision rules introduces considerable uncertainty to the model, which is explored further in the sensitivity analysis below.
-
-\begin{figure}[H]
-\begin{adjustbox}{center}
-\includegraphics[width=119mm]{figures/honesty_sharing}
-\end{adjustbox}
-\caption{Impact of social learning on trends in honest signalling after 1000 rounds, mean with 95\% confidence interval over 100 runs}
-\label{fig:honest_sharing}
-\end{figure}
 
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
 \begin{adjustbox}{center}\includegraphics[width=119mm]{figures/sharing_emulated_simulated}\end{adjustbox}
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
 \begin{adjustbox}{center}\includegraphics[width=119mm]{figures/unfixed_emu_sig_iqr}\end{adjustbox}

### 2015-06-22 model_description.tex
Expanding the model build process

@@
 \label{app:model_description}
-
-In this section we sketch the process of moving from a real world scenario, to a minimal game which sufficiently captures reality. For a
 
@@
 
-In order to translate the scenario sketched above into a more abstract, tractable form, we cast it as a signalling game, and assume that women's disclosures (or not), are signals.
-We also make the simplifying assumption that a woman may have one of only three drinking patterns - light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy.
+In order to translate the scenario sketched above into a more abstract, tractable form, we can treat it as a game.
+A game, in the game theoretic sense, this can be any interaction where the result for one person is dependent on the actions of another.
+In this scenario, the result for the woman would seem dependent on whether the midwife chooses to refer them for specialist support (although naturally the reality can only be thought of in terms of risk mitigation), and conversely, the right choice for the midwife is somewhat contingent on what the woman is willing to tell them.
+
+A very simple way to represent this would be a game with two players, who both have two possible moves - ask for help, or not; and refer, or not (fig \ref{fig:simplest_game}).
+Since both parties are invested in the outcome of the pregnancy, we might allow them to share the same payoff if everything ends well.
+The only time things in this very restricted world obviously end poorly, is if the woman asks for help but does not get any.
+This implies that a rational player would always refer if asked for help, and is indifferent otherwise - in other words, there are three possible Nash equilibriums.
+
+\begin{figure}[H]
+\begin{adjustbox}{center}
+\includegraphics[width=119mm]{figures/simplest_game}
+\end{adjustbox}
+\caption{A very simple two player game.}
+
+\label{fig:simplest_game}
+\end{figure}
+
+The first complication, is that there should be differentiation between referring, and doing nothing because specialist treatment incurs a cost.
+We can modify the payoffs to reflect this, by reducing the midwife's payoffs when they refer.
+If the cost of referring is less than the value of a good outcome, then the effect of this is to make the only rational choice when not asked for help is to do nothing.
+
+This simple game is, however not very informative and clearly neglects much of the nuance of the scenario.
+The wider difficulty here is that the real outcome depends on an attribute of one of the players, rather than their moves.
+In this case, we would expect the right choices to depend on the alcohol consumption of the woman, rather than entirely on what they have claimed about it.
+To reflect this, we would need different variations on the same game to reflect this attribute.
+
+To resolve this, we can do exactly that, and cast it as a signalling game.
+We make the simplifying assumption that a woman may have one of only three drinking patterns - light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy.
+Each of these types of player, will play a different game.
+This also introduces a third player, who we will call nature.
+Nature takes the first move, and decides the type of the woman according to some probability distribution; in this case we will allow the probability of types to be uniform.
+This changes the dynamics of play substantially, since the midwife can no longer be certain of which game they are playing, and hence which move yields the best outcome.
+We must also amend the moves, and payoffs slightly.
+The woman now claims to be one of the types, and may send a signal to say, for example, that they are a heavy drinker.
+We will also modify the common payoffs to allow light drinkers to get the best outcome no matter what, and moderate and heavy types to get the best outcome only if referred.
+We can also differentiate between the consequences of not getting help for these types by letting heavy drinkers have a very negative outcome, and moderate drinkers a slight one (fig \ref{fig:less_simple}).
+
+\begin{figure}[H]
+\begin{adjustbox}{center}
+\includegraphics[width=119mm]{figures/less_simple_game}
+\end{adjustbox}
+\caption{A less simple two player game.}
+
+\label{fig:less_simple}
+\end{figure}
+
 Correspondingly, they are limited in what signals they may send when claiming to be one of these three types.

### 2015-06-22 model_description.tex
Adding to the construction

@@
 
-Correspondingly, they are limited in what signals they may send when claiming to be one of these three types.
+At this point, the game becomes challenging to analyse from a Nash equilibrium perspective (there are several hundred).
+But, having raised to issue of stigma, we would also like incorporate this in the game.
+A possible approach to this is similar to the drinking behaviour of the women, and lets midwives have a type as well, corresponding to how judgemental they are when receiving signals: non-judgemental, moderately judgemental, and harshly judgemental.
+The expression of this judgement is not a matter of choice on their part, and is assumed to have no impact on their clinical response.
+Nature now has an additional move, to choose the type of the midwife, and we add costs for sending moderate and heavy signals.
+A heavy signal to a harshly judgemental midwife adds a heavy cost, and a moderate cost from a moderate midwife.
+The resulting game might reasonably be said to be intractable.
 
-Midwives are treated in a similar fashion, where their type corresponds to how negatively they regard a drinking pattern - non-judgemental, moderately judgemental, and harshly judgemental.
-The expression of this judgement is not a matter of choice on their part, and is assumed to have no impact on their clinical response, which is to either refer the woman for specialist treatment, or do nothing.
+At this juncture, we do not gain much further from the game representation, and instead separate it into multiple decision problems.
 

### 2015-06-29 motivation.tex
Motivation & methods mini lit review
+ finish sim schedule

--- 2015-06-17 Model.tex
@@
-%!TEX root = disclosure_game.tex
-\section{Disclosure Game Model}
-\label{sec:model}
-%Start this off with a brief description of our fictional scenario.
-% Whole section ~ 1.5K
-
-In this section we sketch\footnote{A complete example of this for the alcohol misuse in pregnancy model is given in appendix \ref{app:model_description}, with a schedule of simulation provided in appendix \ref{app:sim_schedule}} the process of moving from a real world scenario to a minimal game which sufficiently captures reality, expressing the result as a decision problem representation, and finally translating this to a simulation model, and then outline four possible decision rules.
-
-\subsection{Model Construction Approach}
+\section{Methods and Motivation}
 \label{sec:model_design}

### 2015-07-03 Methods.tex
Cleaning up

@@
 \label{sec:method}
-%Lay out the design of experiments, harking back to things we're looking for
-%from the real world.
 
-This section provides details of experiments conducted to examine the ability of the model to reproduce qualitative trends reported in the midwifery literature by \cite{Alvik2006}, and \cite{Phillips2007}; as well as a global sensitivity analysis and construction of statistical emulators to explore, and contrast the response surfaces of the four decision rules.
+This section provides details of experiments conducted to examine the ability of the model to reproduce qualitative trends reported in the midwifery literature by \citet{Alvik2006}, and \citet{Phillips2007}; as well as a global sensitivity analysis and construction of statistical emulators to explore, and contrast the response surfaces of the four decision rules.
 
@@
 \label{sub:qt}
-%explicit subsection on the SA.
 
@@
 \label{sub:sensitivity}
-%Maxmin latin hypercube -> remember to cite the r package used.
-%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
+
 In general, we have followed the example of \cite{Bijak2013b} for global sensitivity analysis of stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques.

### 2015-07-03 Model.tex
Cleaning up

@@
 \label{sec:model}
-%Start this off with a brief description of our fictional scenario.
-% Whole section ~ 1.5K
 
-In this section we sketch\footnote{A complete example of this for the alcohol misuse in pregnancy model is given in appendix \ref{app:model_description}, with a schedule of simulation provided in appendix \ref{app:sim_schedule}} the process of moving from a real world scenario to a minimal game which sufficiently captures reality, expressing the result as a decision problem representation, and finally translating this to a simulation model, and then outline four possible decision rules.
+In this section we sketch\footnote{A complete example of this for the alcohol misuse in pregnancy model is given in appendix \ref{app:model_description}, with a schedule of simulation provided in appendix \ref{app:sim_schedule}} the process of moving from a real world scenario to a minimal game which sufficiently captures reality, expressing the result as a decision problem representation, and translating this to a simulation model.
+We then outline four possible decision rules, and as an example of additional flexibility of process models and simulation in contrast to purely predictive or analytical approaches, extend the model to allow a simple form of social learning.
 
-\subsection{Model Construction Approach}
+\subsection{Modelling Approach}
 \label{sec:model_design}
 
+To model a scenario, we take the approach of first creating a formal game to represent it, capturing the key features as far as possible in the structure of that game.
+This game is in essence a conjecture about the real data generating process, which can be played out it in simulation.
+
 The appropriate game representative of the scenario of interest, which captures the desired strategic dynamics may not be immediately obvious.
-There will almost invariably be many possible alternatives, of which some are isomorphisms, and others fundamentally different conjectures about the data generating process.
 We suggest that an iterative process is beneficial, beginning from the simplest possible game, and progressively augmenting it.
@@
 
+\subsection{Scenario}
+\label{sec:scenario}
+
+Typically in the UK, a women will have 12 appointments with a midwife during the antenatal period, and in the majority of cases will encounter several different midwives \citep{Redshaw2014} in the course of their care.
+In the UK, and unlike most healthcare scenarios, maternity notes are held by the patient, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously.
+Maternity notes are not generally linked to extra-departmental records, meaning that a history of alcohol related admissions to another service may remain unknown unless revealed by the woman.
+
+According to NICE guidance \citep{NICE2010a,NICE2010} the issue of substance misuse should be raised at the initial booking appointment, followed by subsequent action if a concern is raised is at the discretion of the midwife.
+This may take the form of specific guidance to reduce intake, or if deemed necessary a referral to a specialist midwife and relevant interdisciplinary team.
+On alcohol consumption, policy regarding how to determine the level of consumption is at the time of writing generally at the level of local health authority, hospital trust, or according to the best judgement of the individual midwife, with no guidance provided by NICE.
+This commonly takes the form of average units per week, but may include \ac{T-ACE}\footnote{The \ac{T-ACE} is a four question screening test for alcohol misuse intended specifically for use with pregnant women.} \citep{Sokol1989863} and similar measures.
+
+Beyond the \enquote{booking} appointment, the onus is on women to raise concerns about their drinking behaviour, or the midwife to probe further if they feel it is warranted.
+In either case, once a concern has been raised the midwife must respond clinically, and inevitably personally, to the information.
+
+In an ideal world, all interactions with healthcare providers would be immediately and fully disclosive, with no repercussions for the patient.
+However, alcohol misuse by women is known to attract stigma \citep{Gomberg1988}, and is a recognised barrier to appropriate treatment in the maternity context \citep{NICE2010,Radcliffe2011}.
+
 \subsection{Disclosure Game}
 \label{sub:the_game}
-%Outline how the scenario translates into a game.
-%Brief mention of the game theoretic solution
 

### 2015-07-03 model_description.tex
Cleaning up

@@
 %!TEX root = disclosure_game.tex
-\section{Model Description}
+\section{Disclosure Game Model Development}
 \label{app:model_description}
 
-Typically in the UK, a women will have 12 appointments with a midwife during the antenatal period, and in the majority of cases will encounter several different midwives \citep{Redshaw2014} in the course of their care.
-In the UK, and unlike most healthcare scenarios, maternity notes are held by the patient, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously.
-Maternity notes are not generally linked to extra-departmental records, meaning that a history of alcohol related admissions to another service may remain unknown unless revealed by the woman.
+This appendix provides a more in depth exploration of the model development process, beginning by deriving a game to serve as the basis for the model, and decision problems.
 
-According to NICE guidance \citep{NICE2010a,NICE2010} the issue of substance misuse should be raised at the initial booking appointment, followed by subsequent action if a concern is raised is at the discretion of the midwife.
-This may take the form of specific guidance to reduce intake, or if deemed necessary a referral to a specialist midwife and relevant interdisciplinary team.
-On alcohol consumption, policy regarding how to determine the level of consumption is at the time of writing generally at the level of local health authority, hospital trust, or according to the best judgement of the individual midwife, with no guidance provided by NICE.
-This commonly takes the form of average units per week, but may include \ac{T-ACE}\footnote{The \ac{T-ACE} is a four question screening test for alcohol misuse intended specifically for use with pregnant women.} \citep{Sokol1989863} and similar measures.
-
-Beyond the \enquote{booking} appointment, the onus is on women to raise concerns about their drinking behaviour, or the midwife to probe further if they feel it is warranted.
-In either case, once a concern has been raised the midwife must respond clinically, and inevitably personally, to the information.
-
-In an ideal world, all interactions with healthcare providers would be immediately and fully disclosive, with no repercussions for the patient.
-However, alcohol misuse by women is known to attract stigma \citep{Gomberg1988}, and is a recognised barrier to appropriate treatment in the maternity context \citep{NICE2010,Radcliffe2011}.
-
-\subsection{Disclosure Game}
-\label{sub:the_game}
-%Outline how the scenario translates into a game.
-%Brief mention of the game theoretic solution
-
-In order to translate the scenario sketched above into a more abstract, tractable form, we can treat it as a game.
 A game, in the game theoretic sense, this can be any interaction where the result for one person is dependent on the actions of another.
@@
 
-This simple game is, however not very informative and clearly neglects much of the nuance of the scenario.
+This simple game is however not very informative, and clearly neglects much of the nuance of the scenario.
 The wider difficulty here is that the real outcome depends on an attribute of one of the players, rather than their moves.
@@
 
+Breaking the game down into separate decision problems can be achieved by treating the moves of the other players as a chance node, and omitting moves by nature that are known to them.
+For women, there are two such nodes, corresponding to the move by nature determining the type of midwife they play against, and the midwife's action.
+Midwives have simpler problem with only a single chance node, because the woman's move is known to them.
+Figure \ref{fig:decision_problems} shows the structure of the resulting decision problems.
+Note that there are in fact three distinct decision problems for the three types of woman, since the move by nature determining their type is known to them.
+
+\begin{figure}[H]
+\centering
+\subfloat[Women (heavy drinkers)]{\includegraphics[width=119mm]{figures/women_influence}}
+\vskip\baselineskip
+\subfloat[Midwives]{\includegraphics[width=119mm]{figures/mw_influence}}
+\caption{Influence diagrams, showing the game broken into two decision problems. Squares indicate a decision node, while circles are (from the perspective of the agent) chance nodes}
+
+\label{fig:decision_problems}
+\end{figure}
+
+The precise structure of the decision problem is to some extent dependent on the decision rule in use, for example the Lexicographic heuristic rule is concerned only with a direct relationship between action and consequence.
+However, the literal translation from game to decision problem for women yields two chance nodes.
+As a result, solving this using the heuristic approach requires that the nodes be combined.
+By the same token, an arbitrarily complex problem could be resolved by rules without this limitation.
+This is significant, in that the decision problem is an individual agent's model of the situation, which might not be expected to correspond perfectly with the true situation.
+
+From this position, simulating play, and augmenting the basic conjecture is easily achievable, since together the game, and the decision rules specify the basis for a simulation model.
+In the disclosure game case, we make additional stipulations on how many games agents play, order of play, the circumstances under which agents observe true types, and the structure of agent populations amongst others.
+
+\begin{comment}
 At the end of a game, each player receives a payoff dependent on the actions and types of both players.
@@
 
-\begin{figure}[H]
-\centering
-\subfloat[Women (heavy drinkers)]{\includegraphics[width=119mm]{figures/women_influence}}
-\vskip\baselineskip
-\subfloat[Midwives]{\includegraphics[width=119mm]{figures/mw_influence}}
-\caption{Influence diagrams, showing the game broken into two decision problems. Squares indicate a decision node, while circles are (from the perspective of the agent) chance nodes}
-
-\label{fig:decision_problems}
-\end{figure}
-
 %Might belong in a more methody bit? Read some stuff to check..
@@
 Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.
+\end{comment}

### 2015-07-06 model_description.tex
Moving table caps

@@
 Since both parties are invested in the outcome of the pregnancy, we might allow them to share the same payoff if everything ends well.
-The only time things in this very restricted world obviously end poorly, is if the woman asks for help but does not get any.
-This implies that a rational player would always refer if asked for help, and is indifferent otherwise - in other words, there are three possible Nash equilibriums.
 
 \begin{figure}[H]
-\begin{adjustbox}{center}
-\includegraphics[width=119mm]{figures/simplest_game}
-\end{adjustbox}
-\caption{A very simple two player game.}
-
+\sidecaption
+\includegraphics[width=7cm]{figures/simplest_game}
+\caption{A very simple two player game.
+The only time things in this very restricted world obviously end poorly, is if the woman asks for help but does not get any.
+This implies that a rational player would always refer if asked for help, and is indifferent otherwise - in other words, there are three possible Nash equilibriums.}
 \label{fig:simplest_game}
@@
 \begin{adjustbox}{center}
-\includegraphics[width=119mm]{figures/less_simple_game}
+\includegraphics[width=78mm]{figures/less_simple_game}
 \end{adjustbox}
-\caption{A less simple two player game.}
+\sidecaption{A less simple two player game.}
 

### 2015-07-06 SensitivityAnalysis.tex
Table captions

@@
 \end{tabular}
-\caption[Table caption text]{Median moderate drinker signalling parameter sensitivity \label{tab:sa_results_sig}}
+\caption{Median moderate drinker signalling parameter sensitivity \label{tab:sa_results_sig}}
 \end{table}
@@
 \end{tabular}
-\caption[Table caption text]{Median moderate drinker signalling emulator statistics \label{tab:sa_emulator_sig}}
+\caption{Median moderate drinker signalling emulator statistics \label{tab:sa_emulator_sig}}
 \end{table}
@@
 \end{tabular}
-\caption[Table caption text]{Median between groups IQR parameter sensitivity \label{tab:sa_results_iqr}}
+\caption{Median between groups IQR parameter sensitivity \label{tab:sa_results_iqr}}
 \end{table}
@@
 \end{tabular}
-\caption[Table caption text]{Median between groups IQR emulator statistics \label{tab:sa_emulator_iqr}}
+\caption{Median between groups IQR emulator statistics \label{tab:sa_emulator_iqr}}
 \end{table}
@@
 \end{tabular}
-\caption[Table caption text]{IQR of median moderate drinker signalling parameter sensitivity \label{tab:sa_results_sig_iqr}}
+\caption{IQR of median moderate drinker signalling parameter sensitivity \label{tab:sa_results_sig_iqr}}
 \end{table}
@@
 \end{tabular}
-\caption[Table caption text]{IQR of median between groups IQR emulator statistics \label{tab:sa_emulator_sig_iqr}}
+\caption{IQR of median between groups IQR emulator statistics \label{tab:sa_emulator_sig_iqr}}
 \end{table}
@@
 \end{tabular}
-\caption[Table caption text]{IQR of median between groups IQR parameter sensitivity \label{tab:sa_results_iqr_iqr}}
+\caption{IQR of median between groups IQR parameter sensitivity \label{tab:sa_results_iqr_iqr}}
 \end{table}
@@
 \end{tabular}
-\caption[Table caption text]{IQR of median between groups IQR emulator statistics \label{tab:sa_emulator_iqr_iqr}}
+\caption{IQR of median between groups IQR emulator statistics \label{tab:sa_emulator_iqr_iqr}}
 \end{table}

### 2015-07-06 Results.tex
Finally fixed the tables

@@
 \begin{figure}
-\begin{adjustbox}{center}
 \includegraphics[width=119mm]{figures/honesty_sharing}
-\end{adjustbox}
 \caption{Impact of social learning on trends in honest signalling after 1000 rounds, mean with 95\% confidence interval over 100 runs}
@@
 \begin{figure}[h]
-\begin{adjustbox}{center}\includegraphics[width=119mm]{figures/sharing_emulated_simulated}\end{adjustbox}
+\includegraphics[width=119mm]{figures/sharing_emulated_simulated}
 \caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules}
@@
 \begin{figure}[h]
-\begin{adjustbox}{center}\includegraphics[width=119mm]{figures/unfixed_emu_sig_iqr}\end{adjustbox}
+\includegraphics[width=119mm]{figures/unfixed_emu_sig_iqr}
 \caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\)}
@@
 \begin{figure}[H]
-\begin{adjustbox}{center}\includegraphics[width=119mm]{figures/unfixed_emu_payoff_honesty_group_iqr}\end{adjustbox}
+\includegraphics[width=119mm]{figures/unfixed_emu_payoff_honesty_group_iqr}
 \caption{Emulated between groups IQR in response to varying \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\), and \(x_{h}\)}

### 2015-07-06 agent_models.tex
More trimming
Finally fixed the tables

@@
 While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same outputs, we limit ourselves here to four.
-The simplest is a lexicographic rule (1), in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}.
+The simplest is a lexicographic rule (1), in the spirit of a \acl{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}.
 Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-output characteristics.
@@
 Given the discrete nature of actions and payoffs, coupled with a desire for tractability of the
-simulation, the Dirichlet distribution is employed as a prior to represent these beliefs. The probability density function takes the form -
-
-\begin{equation}
-D(\Theta|\alpha)=\frac{\Gamma(\sum_{i=1}^{k}\alpha_{i})}{\prod_{i=1}^{k}\Gamma(\alpha_{i})}\overset{k}{\underset{i=1}{\prod}\Theta_{i}^{\alpha_{i-1}}}
-\end{equation}
-
-where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\) is the number
-of signal-payoff pairs, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
-more than zero and summing to less than 1, and \(\alpha_{i}\) is the 
-pseudo-count of prior observations\footnote{Psuedo-counts are related to, but distinct from prior beliefs.
-Here, the psuedo-count is a parameter to the prior belief distribution and is nothing more than a hypothetical count of prior observations.} for a pair \(i\).
-
+simulation, the Dirichlet distribution is employed as a prior to represent these beliefs. 
 The distribution is particularly convenient, in that to infer the
-probability of a signal implying a payoff becomes
+probability of a signal implying a payoff is
 simply -
@@
 
-Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), so
-that the belief that a signal will lead to a payoff is the number
+Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), and \(\alpha_{i}\) is the pseudo-count of prior observations\footnote{Psuedo-counts are related to, but distinct from prior beliefs.
+Here, the psuedo-count is a parameter to the prior belief distribution and is nothing more than a hypothetical count of prior observations.} for a pair \(i\).
+Hence,
+the belief that a signal will lead to a payoff is the number
 of times that pairing has been observed (including the pseudo-count),
@@
 of beliefs fast and simple, since all that must be maintained is
-a count of observations with no particular concern as to their order.
+a count of observations.
 As before, midwives follow a similar pattern but maintain \(n_{s_{w}}\) independent counts of pairings between referral choice and payoff, updating their beliefs about the relationship between the choice to refer and payoff given the signal they have received.

### 2015-07-06 model_description.tex
Add less simple game

@@
 
-To resolve this, we can do exactly that, and cast it as a signalling game.
+To resolve this, we can do exactly that, and cast it as a signalling game (fig \ref{fig:less_simple}).
 We make the simplifying assumption that a woman may have one of only three drinking patterns - light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy.
@@
 We will also modify the common payoffs to allow light drinkers to get the best outcome no matter what, and moderate and heavy types to get the best outcome only if referred.
-We can also differentiate between the consequences of not getting help for these types by letting heavy drinkers have a very negative outcome, and moderate drinkers a slight one (fig \ref{fig:less_simple}).
+We can also differentiate between the consequences of not getting help for these types by letting heavy drinkers have a very negative outcome, and moderate drinkers a slight one.
 
 \begin{figure}[H]
-\begin{adjustbox}{center}
-\includegraphics[width=78mm]{figures/less_simple_game}
-\end{adjustbox}
-\sidecaption{A less simple two player game.}
+\includegraphics[width=\textwidth]{figures/less_simplest_game}
+\caption{A less simple two player signalling game. }
 
@@
 \begin{figure}[H]
-\centering
-\subfloat[Women (heavy drinkers)]{\includegraphics[width=119mm]{figures/women_influence}}
+\subfloat[Women (heavy drinkers)]{\includegraphics[width=11.9cm]{figures/women_influence}}
 \vskip\baselineskip
-\subfloat[Midwives]{\includegraphics[width=119mm]{figures/mw_influence}}
+\subfloat[Midwives]{\includegraphics[width=11.9cm]{figures/mw_influence}}
 \caption{Influence diagrams, showing the game broken into two decision problems. Squares indicate a decision node, while circles are (from the perspective of the agent) chance nodes}

### 2015-07-09 model_description.tex
Rephrase

@@
 By the same token, an arbitrarily complex problem could be resolved by rules without this limitation.
-This is significant, in that the decision problem is an individual agent's model of the situation, which might not be expected to correspond perfectly with the true situation.
+This is significant, in that the decision problem is an individual agent's model of the situation, which might not be expected to correspond perfectly with the true sequence of events.
 
@@
 In the disclosure game case, we make additional stipulations on how many games agents play, order of play, the circumstances under which agents observe true types, and the structure of agent populations amongst others.
-
-\begin{comment}
-At the end of a game, each player receives a payoff dependent on the actions and types of both players.
-Because both women and midwives have an interest in the outcome of the pregnancy, and would prefer a healthy baby, the payoff has a common interest component.
-Hence, both players receive a payoff based on the outcome of pregnancy, but women bear a social cost dependent on the signal they sent and the midwife's reaction to it.
-Similarly, midwives pay a cost if they refer to a specialist, mirroring the organisational cost of non-routine care.
-Table \ref{tab:Payoff-matrix} shows the three payoff matrices which together describe the game.
-
-Taken together, this leads to a game tree that is relatively complex (figure \ref{fig:simple_tree} shows a simplified representation, with a detailed view of one branch in figure \ref{fig:zoom_tree}) even at the subgame level.
-
-As an example, consider the challenge faced by an agent of the heavy drinking type.
-In order to get the best health outcome, they must be referred and would ideally achieve this without paying any social cost at all.
-The best move depends on the type, and beliefs of the midwife.
-For example, a particularly unlucky scenario might be for the midwife to not only be of a harshly judgemental disposition, but to believe that no women really need to be referred.
-Even a relatively weak belief in this possibility can make the honest signal look like an unwarranted risk.
-
-Rather than attempt to solve for equilibria, agents treat this two player game as taking place against nature, along the lines of adversarial risk analysis \citep{RiosInsua2009}.
-This effectively translates the game to a pair of decision problems (figure \ref{fig:decision_problems}), which agents attempt to resolve at each turn using a simple decision rule, given their prior beliefs and experience of play.
-
-\begin{figure}[H]
-\begin{adjustbox}{center}
-\includegraphics[width=119mm]{figures/rounded_clover_infosets}
-\end{adjustbox}
-\caption{Simplified game tree.
-Arrows correspond to two moves by nature, followed by women, and midwives respectively.
-Line weight distinguishes between information sets, and possible moves, corresponding to ascending player types.
-For midwives, referral is shown by a heavier arrow.
-Light terminal nodes indicate that the game may repeat from that point, and black nodes are exits}
-
-\label{fig:simple_tree}
-\end{figure}
-
-\begin{figure}[H]
-\begin{adjustbox}{center}
-\includegraphics[width=119mm]{figures/tree_zoom}
-\end{adjustbox}
-\caption{Detail view of a single game tree branch, showing the possible moves by each player, with information sets for midwives}
-
-\label{fig:zoom_tree}
-\end{figure}
-
-%Might belong in a more methody bit? Read some stuff to check..
-To formally define the game, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\).
-Here, \(\{l, m, h\}\) correspond to light, moderate, and heavy alcohol consumption for women, and non-judgemental, moderately judgemental, and harshly judgemental for midwives.
-Midwives' pure strategies \(\{r,n\}\) are to refer, or do nothing, and those for women are to signal that they have one of the possible drinking patterns.
-Additionally define two utility functions - 
-\begin{equation}
-u_{w}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}}
-\end{equation} 
-\begin{equation}
-u_{m}(s_{w}, s_{m}, \theta_{w})=X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}},
-\end{equation} with $X_{c}$, $X_{h}$, and $X_{s}$ being the payoff matrices as in table \ref{tab:Payoff-matrix}, $s_{w}$ and $s_{m}$ denoting a specific signal by a woman, and referral response by a midwife.
-Lastly let \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\) be distributions over types of women, and midwives respectively.
-
-As noted, rather than solve the game, we allow populations of agents to play it, and hence stipulate further that women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)).
-They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred, and a new player is drawn from the same distribution that produced the original players to replace them.
-If they are not referred, they rejoin the back of the queue after their appointment.
-In either case, they are informed of their payoff after each round and update their beliefs accordingly using one of the rules described in section \ref{sub:the_agents}.
-
-Midwives play for \(r_{m}\) rounds (\(r_{m}=1000\) in all experiments), and conduct appointments in parallel, i.e.
-if there are 5 midwives, then five women are drawn from the queue and assigned at random to the midwives.
-Unlike women, midwives are only informed of their payoff if they choose to make a referral.
-Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.
-\end{comment}

### 2015-07-13 Introduction.tex
Cleaning up
Table formatting

@@
 \label{sec:intro}
-%CONTRIBUTION, FUCKER!
-%Also, remember to say what you're going to do for the rest of the article?
-%CONTRIBUTION
-%	Agents are awesome
-%	Decision theory is super awesome
-%	'nice story to hang it on'
-% 	mention the importance of behaviour change
-% tool for thinking
-% theoretical vacuum at the middle
-% under what scenarios does an as if explanation break down
 
@@
 
-Turning more specifically to disclosure of alcohol use by women during their pregnancy, research is relatively sparse, although qualitative trends are reported by \citet{Phillips2007} and \citet{Alvik2006}.
+Turning more specifically to disclosure of alcohol use by women to healthcare professionals during their pregnancy, research is relatively sparse, although qualitative trends are reported by \citet{Phillips2007} and \citet{Alvik2006}.
 The former explored factors impacting disclosure through a small case study, highlighting the need to build up rapport between woman and midwife over several appointments; the latter compared post partum reports of consumption with contemporaneous accounts, finding apparent underreporting during pregnancy which was amplified by increased drinking.
@@
 
-The resulting scenario is of substantial independent interest, and shows the potential utility of a simulation approach in arenas where randomized control trials are not viable for ethical, or financial reasons.
+The resulting scenario is of substantial independent interest, and shows the potential utility of a simulation approach in domains where process is opaque, here both because of the interest in concealment, and obvious ethical concerns.
 With this said, the lack of a strong quantitative evidence base against which to validate the behaviour of the model augers for caution in interpreting the results, and a necessary reminder that in this instance the model is primarily a tool for formalisation of the thought process \citep{epstein2008}, rather than a machine for predicting.
-
-%two fold appeal. cognitive plausibility - neuroec. inaccessible systems (litigation, concealment). fast. cheap. portable. theoretical grounding. rigor.
 
@@
 
-Given these features, the application of decision, and game theory to \ac{ABM} is an attractive approach to computational social science, where the locus of interest is decision making.
+Given these features, the application of decision, and game theory to \ac{ABM} is an attractive approach to computational social science, where the locus of interest is process, and decision making.
 Taking a balance between models focused on replication of low level neurological mechanics, and those with a higher level emphasis where individual behaviours are abstracted away yields a computationally tractable approach.
@@
 
-%Finishing up
-
 The remainder of this paper proceeds to outline the proposed approach to model development (section \ref{sec:model}), and experiments (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}).

### 2015-07-13 Methods.tex
Table captions
Finally fixed the tables
Table formatting

@@
 \begin{table}[h!]
-\center
-\begin{tabular} {|l | l | c|}
-\hline
-Name & Description & Value \\ \hline
-\(n_{w}\) & Number of women & 1000 \\ \hline
-\(n_{m}\) & Number of midwives & 100 \\ \hline
-\(r_{m}\) & Number of appointments per midwife & 1000 \\ \hline
-\(r_{w}\) & Maximum number of appointments per woman & 12 \\ \hline
-Runs & Simulation runs & 1000 \\ \hline
-\(p_{w}(h)\) & Proportion of heavy drinkers & \(1/3\) \\ \hline
-\(p_{w}(m)\) & Proportion of moderate drinkers & \(1/3\) \\ \hline
-\(p_{w}(l)\) & Proportion of light drinkers & \(1/3\) \\ \hline
-\(p_{m}(h)\) & Proportion of harsh midwives & \(5/100\) \\ \hline
-\(p_{m}(m)\) & Proportion of moderate midwives & \(10/100\) \\ \hline
-\(p_{m}(l)\) & Proportion of non-judgemental midwives & \(85/100\) \\ \hline
-\(q_{w}\) & Probability of women sharing & 0. \\ \hline
-\(w_{w}\) & Weight of shared information for women & 0. \\ \hline
-\(q_{m}\) & Probability of midwives sharing & 0. \\ \hline
-\(w_{m}\) & Weight of shared information for midwives & 0. \\ \hline
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 10:1 \\ \hline
-\(\gamma\) & Probability weighting for gains  & 0.61 \\ \hline
-\(\delta\) & Probability weighting for losses &  0.69\\ \hline
-\(\alpha\) & Power for gains  & 0.88 \\ \hline
-\(\beta\) & Power for losses & 0.88 \\ \hline
-\(\lambda\) & Loss aversion &  2.25 \\ \hline
+\caption{Model parameters.} 
+\label{tab:qt_params}
+\begin{tabular} {llc}
+\hline\noalign{\smallskip}
+Name & Description & Value \\
+\noalign{\smallskip}\svhline\noalign{\smallskip}
+\(n_{w}\) & Number of women & 1000 \\ 
+\(n_{m}\) & Number of midwives & 100 \\ 
+\(r_{m}\) & Number of appointments per midwife & 1000 \\ 
+\(r_{w}\) & Maximum number of appointments per woman & 12 \\ 
+Runs & Simulation runs & 1000 \\ 
+\(p_{w}(h)\) & Proportion of heavy drinkers & \(1/3\) \\ 
+\(p_{w}(m)\) & Proportion of moderate drinkers & \(1/3\) \\ 
+\(p_{w}(l)\) & Proportion of light drinkers & \(1/3\) \\ 
+\(p_{m}(h)\) & Proportion of harsh midwives & \(5/100\) \\ 
+\(p_{m}(m)\) & Proportion of moderate midwives & \(10/100\) \\ 
+\(p_{m}(l)\) & Proportion of non-judgemental midwives & \(85/100\) \\ 
+\(q_{w}\) & Probability of women sharing & 0. \\ 
+\(w_{w}\) & Weight of shared information for women & 0. \\ 
+\(q_{m}\) & Probability of midwives sharing & 0. \\ 
+\(w_{m}\) & Weight of shared information for midwives & 0. \\ 
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 10:1 \\ 
+\(\gamma\) & Probability weighting for gains  & 0.61 \\ 
+\(\delta\) & Probability weighting for losses &  0.69\\ 
+\(\alpha\) & Power for gains  & 0.88 \\ 
+\(\beta\) & Power for losses & 0.88 \\ 
+\(\lambda\) & Loss aversion &  2.25 \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
 \end{tabular}
-\caption[Table caption text]{Model parameters. \label{tab:qt_params}}
 \end{table}
@@
 \begin{table}
-\center
-\begin{tabular} {|l | l | l| l|}
-\hline
-Name & Description & Min & Max \\ \hline
-\(p_{w}(m)\) & Proportion of moderate drinkers & 0 & 1 \\ \hline
-\(p_{w}(l)\) & Proportion of light drinkers & 0 & 1 \\ \hline
-\(p_{m}(m)\) & Proportion of moderate midwives & 0 & 1 \\ \hline
-\(p_{m}(l)\) & Proportion of non-judgemental midwives & 0 & 1 \\ \hline
-\(q_{w}\) & Probability of women sharing & 0 & 1 \\ \hline
-\(w_{w}\) & Weight of shared information for women & 0 & 1 \\ \hline
-\(q_{m}\) & Probability of midwives sharing & 0 & 1 \\ \hline
-\(w_{m}\) & Weight of shared information for midwives & 0 & 1 \\ \hline
-\(x_{h}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
-\(x_{r}\) & Cost for referral & \multicolumn{2}{l|}{\(-(x_{h} - 1)\)} \\ \hline
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 1:1 & 100:1 \\ \hline
+\caption{Parameter ranges.}
+\label{tab:sa_params}
+\begin{tabular} {llll}
+\hline\noalign{\smallskip}
+Name & Description & Min & Max \\
+\noalign{\smallskip}\svhline\noalign{\smallskip}
+\(p_{w}(m)\) & Proportion of moderate drinkers & 0 & 1 \\ 
+\(p_{w}(l)\) & Proportion of light drinkers & 0 & 1 \\ 
+\(p_{m}(m)\) & Proportion of moderate midwives & 0 & 1 \\ 
+\(p_{m}(l)\) & Proportion of non-judgemental midwives & 0 & 1 \\ 
+\(q_{w}\) & Probability of women sharing & 0 & 1 \\ 
+\(w_{w}\) & Weight of shared information for women & 0 & 1 \\ 
+\(q_{m}\) & Probability of midwives sharing & 0 & 1 \\ 
+\(w_{m}\) & Weight of shared information for midwives & 0 & 1 \\ 
+\(x_{h}\) & Health payoff for healthy delivery & 1 & 100 \\ 
+\(x_{r}\) & Cost for referral & \multicolumn{2}{l}{\(-(x_{h} - 1)\)} \\ 
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 1:1 & 100:1 \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
 \end{tabular}
-\caption[Table caption text]{Parameter ranges. \label{tab:sa_params}}
 \end{table}

### 2015-07-13 Model.tex
Finally fixed the tables
Table formatting

@@
 In order to translate the scenario sketched above into a more abstract, tractable form, we cast it as a signalling game, and assume that women's disclosures (or not), are signals.
-We also make the simplifying assumption that a woman may have one of only three drinking patterns - light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy.
+We also impose a discretisation on the continuum of alcohol use, and use three types of behaviour - light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy.
 Correspondingly, they are limited in what signals they may send when claiming to be one of these three types.
@@
 \begin{table}
-\center
+\caption{Payoff matrices}
+\label{tab:Payoff-matrix}
 \subfloat[Social cost, \(X_{s}\), for women, given their signal, and the midwife's type\label{tab:Social-cost-matrix}]{%
@@
 }
-
-\caption{Payoff matrices\label{tab:Payoff-matrix}}
 \end{table}
@@
 In reality, learning is not exclusively from personal experience, and social learning plays an important role.
+This social dynamic fits naturally into an agent framework, but is difficult to address without using an approach concerned with process, so we take advantage of this to show a na{\"\i}ve take on it here.
+
 In the disclosure game model, this takes the form of having each agent recount their play history to their colleagues with some probability \(q\).

### 2015-07-13 SensitivityAnalysis.tex
Finally fixed the tables
Build errors
Table formatting

@@
 \begin{table}[H]
-\center
-\begin{tabular} {|l | l | l | l | l | l |}
-\hline
-Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\ \hline
-\(p_{w}(m)\) & Proportion of moderate drinkers & 0.367 & 1.145 & 0.801 & 0.614 \\ \hline
-\(p_{w}(l)\) & Proportion of light drinkers & 10.080 & 37.750 & 23.968  & 5.137\\ \hline
-\(p_{m}(m)\) & Proportion of moderate midwives & 6.715 & 13.017 & 0.894 & 1.485\\ \hline
-\(p_{m}(l)\) & Proportion of non-judgemental midwives & 43.942 & 1.655 & 1.602 & 2.618 \\ \hline
-\(q_{w}\) & Probability of women sharing & 0.198 & 5.527 & 4.460 & 1.159 \\ \hline
-\(w_{w}\) & Weight of shared information for women & 0.355 & 13.025 & 2.716 & 0.888 \\ \hline
-\(q_{m}\) & Probability of midwives sharing & 0.145 & 0.667 & 0.368 & 0.157 \\ \hline
-\(w_{m}\) & Weight of shared information for midwives & 0.118 & 0.376 & 0.176 & 0.200 \\ \hline
-\(x_{h}\) & Health payoff for healthy delivery & 0.457 & 9.618 & 1.912 & 15.355 \\ \hline
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.140 & 7.537 & 10.427 & 7.795 \\ \hline
-Total & All parameters and two way interactions & 86.777 & 96.527 & 85.529 & 74.123 \\ \hline
+\caption{Median moderate drinker signalling parameter sensitivity \label{tab:sa_results_sig}}
+\begin{tabular} {llllll}
+\hline\noalign{\smallskip}
+Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
+\(p_{w}(m)\) & Proportion of moderate drinkers & 0.367 & 1.145 & 0.801 & 0.614 \\
+\(p_{w}(l)\) & Proportion of light drinkers & 10.080 & 37.750 & 23.968  & 5.137\\
+\(p_{m}(m)\) & Proportion of moderate midwives & 6.715 & 13.017 & 0.894 & 1.485\\
+\(p_{m}(l)\) & Proportion of non-judgemental midwives & 43.942 & 1.655 & 1.602 & 2.618 \\
+\(q_{w}\) & Probability of women sharing & 0.198 & 5.527 & 4.460 & 1.159 \\
+\(w_{w}\) & Weight of shared information for women & 0.355 & 13.025 & 2.716 & 0.888 \\
+\(q_{m}\) & Probability of midwives sharing & 0.145 & 0.667 & 0.368 & 0.157 \\
+\(w_{m}\) & Weight of shared information for midwives & 0.118 & 0.376 & 0.176 & 0.200 \\
+\(x_{h}\) & Health payoff for healthy delivery & 0.457 & 9.618 & 1.912 & 15.355 \\
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.140 & 7.537 & 10.427 & 7.795 \\
+Total & All parameters and two way interactions & 86.777 & 96.527 & 85.529 & 74.123 \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
 \end{tabular}
-\caption{Median moderate drinker signalling parameter sensitivity \label{tab:sa_results_sig}}
 \end{table}
@@
 \begin{table}[H]
-\center
-\begin{tabular} {|l | l | l | l | l | l | l |}
-\hline
-Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
-Lexicographic & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\ \hline
-Bayesian Payoff & 1.667 & 0.475 &  0.662 & 0.003 & 0.181 & 3.12 \\ \hline
-Bayesian & 3.352 & 0.534 & 1.160 & 0.001 & 0.068 & 2.423 \\ \hline
-\ac{CPT} & 1.503 & 0.331 & 1.241 & 0.002 & 0.101 & 1.842 \\ \hline
+\caption{Median moderate drinker signalling emulator statistics \label{tab:sa_emulator_sig}}
+\begin{tabular} {lllllll}
+\hline\noalign{\smallskip}
+Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\
+\noalign{\smallskip}\svhline\noalign{\smallskip}
+Lexicographic & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\
+Bayesian Payoff & 1.667 & 0.475 &  0.662 & 0.003 & 0.181 & 3.12 \\
+Bayesian & 3.352 & 0.534 & 1.160 & 0.001 & 0.068 & 2.423 \\
+\ac{CPT} & 1.503 & 0.331 & 1.241 & 0.002 & 0.101 & 1.842 \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
 \end{tabular}
-\caption{Median moderate drinker signalling emulator statistics \label{tab:sa_emulator_sig}}
 \end{table}
@@
 \begin{table}[H]
-\center
-\begin{tabular} {|l | l | l | l | l | l |}
-\hline
-Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\ \hline
-\(p_{w}(m)\) & Proportion of moderate drinkers & 0.327 & 0.688 & 0.457 & 0.586 \\ \hline
-\(p_{w}(l)\) & Proportion of light drinkers & 11.223 & 20.123 & 11.046 & 4.081 \\ \hline
-\(p_{m}(m)\) & Proportion of moderate midwives & 36.630 & 1.160 & 0.364 & 1.945 \\ \hline
-\(p_{m}(l)\) & Proportion of non-judgemental midwives & 6.228 & 4.487 & 0.0964 & 2.627\\ \hline
-\(q_{w}\) & Probability of women sharing & 0.498 & 0.235 & 2.537 & 1.812 \\ \hline
-\(w_{w}\) & Weight of shared information for women & 1.018 & 2.307 & 1.889 & 0.740 \\ \hline
-\(q_{m}\) & Probability of midwives sharing & 0.158 & 0.343 & 0.387 & 0.156 \\ \hline
-\(w_{m}\) & Weight of shared information for midwives & 0.076 & 0.973 & 0.125 & 0.213 \\ \hline
-\(x_{h}\) & Health payoff for healthy delivery & 0.317 & 10.960 & 3.305 & 16.493 \\ \hline
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 1.107 & 8.411 & 2.890 & 6.729 \\ \hline
-Total & All parameters and two way interactions & 81.702 & 83.693 & 47.449 & 71.032 \\ \hline
+\caption{Median between groups IQR parameter sensitivity \label{tab:sa_results_iqr}}
+\begin{tabular} {llllll}
+\hline\noalign{\smallskip}
+Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
+\noalign{\smallskip}\svhline\noalign{\smallskip}
+\(p_{w}(m)\) & Proportion of moderate drinkers & 0.327 & 0.688 & 0.457 & 0.586 \\
+\(p_{w}(l)\) & Proportion of light drinkers & 11.223 & 20.123 & 11.046 & 4.081 \\
+\(p_{m}(m)\) & Proportion of moderate midwives & 36.630 & 1.160 & 0.364 & 1.945 \\
+\(p_{m}(l)\) & Proportion of non-judgemental midwives & 6.228 & 4.487 & 0.0964 & 2.627\\
+\(q_{w}\) & Probability of women sharing & 0.498 & 0.235 & 2.537 & 1.812 \\
+\(w_{w}\) & Weight of shared information for women & 1.018 & 2.307 & 1.889 & 0.740 \\
+\(q_{m}\) & Probability of midwives sharing & 0.158 & 0.343 & 0.387 & 0.156 \\
+\(w_{m}\) & Weight of shared information for midwives & 0.076 & 0.973 & 0.125 & 0.213 \\
+\(x_{h}\) & Health payoff for healthy delivery & 0.317 & 10.960 & 3.305 & 16.493 \\
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 1.107 & 8.411 & 2.890 & 6.729 \\
+Total & All parameters and two way interactions & 81.702 & 83.693 & 47.449 & 71.032 \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
 \end{tabular}
-\caption{Median between groups IQR parameter sensitivity \label{tab:sa_results_iqr}}
 \end{table}
@@
 \begin{table}[H]
-\center
-\begin{tabular} {|l | l | l | l | l | l | l |}
-\hline
-Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
-Lexicographic & 0.930 & 0.240 & 0.249 & 0.002 & 0.040 & 1.832 \\ \hline
-Bayesian Payoff & 1.242 & 0.417 & 0.232 & 0.001 & 0.0034 & 2.308 \\ \hline
-Bayesian & 1.254 & 0.131 & 0.644 & 0.000 & 0.019 & 1.167 \\ \hline
-\ac{CPT} & 1.190 & 0.313 & 0.659 & 0.000 & 0.024 & 1.701 \\ \hline
+\caption{Median between groups IQR emulator statistics \label{tab:sa_emulator_iqr}}
+\begin{tabular} {lllllll}
+\hline\noalign{\smallskip}
+Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\
+\noalign{\smallskip}\svhline\noalign{\smallskip}
+Lexicographic & 0.930 & 0.240 & 0.249 & 0.002 & 0.040 & 1.832 \\
+Bayesian Payoff & 1.242 & 0.417 & 0.232 & 0.001 & 0.0034 & 2.308 \\
+Bayesian & 1.254 & 0.131 & 0.644 & 0.000 & 0.019 & 1.167 \\
+\ac{CPT} & 1.190 & 0.313 & 0.659 & 0.000 & 0.024 & 1.701 \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
 \end{tabular}
-\caption{Median between groups IQR emulator statistics \label{tab:sa_emulator_iqr}}
 \end{table}
@@
 \begin{table}[H]
-\center
-\begin{tabular} {|l | l | l | l | l | l |}
-\hline
-Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\ \hline
-\(p_{w}(m)\) & Proportion of moderate drinkers & 0.428 & 9.828 & 3.816 & 2.068 \\ \hline
-\(p_{w}(l)\) & Proportion of light drinkers & 8.369 & 13.791 & 4.045 & 2.400 \\ \hline
-\(p_{m}(m)\) & Proportion of moderate midwives & 13.416 & 0.712 & 0.676 & 0.583 \\ \hline
-\(p_{m}(l)\) & Proportion of non-judgemental midwives & 21.079 & 0.648 & 0.659 & 0.373 \\ \hline
-\(q_{w}\) & Probability of women sharing & 2.307 & 3.481 & 0.891 & 0.600 \\ \hline
-\(w_{w}\) & Weight of shared information for women & 6.021 & 6.009 & 0.562 & 0.937 \\ \hline
-\(q_{m}\) & Probability of midwives sharing & 0.315 & 1.829 & 0.114 & 0.117 \\ \hline
-\(w_{m}\) & Weight of shared information for midwives & 1.652 & 1.354 & 0.260 & 0.0.139 \\ \hline
-\(x_{h}\) & Health payoff for healthy delivery & 0.253 & 0.612 & 4.889 & 15.146 \\ \hline
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.504 & 3.096 & 19.863 & 25.999 \\ \hline
-Total & All parameters and two way interactions & 84.9968 & 77.413 & 57.125 & 83.322 \\ \hline
+\caption{IQR of median moderate drinker signalling parameter sensitivity \label{tab:sa_results_sig_iqr}}
+\begin{tabular} {llllll}
+\hline\noalign{\smallskip}
+Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
+\noalign{\smallskip}\svhline\noalign{\smallskip}
+\(p_{w}(m)\) & Proportion of moderate drinkers & 0.428 & 9.828 & 3.816 & 2.068 \\
+\(p_{w}(l)\) & Proportion of light drinkers & 8.369 & 13.791 & 4.045 & 2.400 \\
+\(p_{m}(m)\) & Proportion of moderate midwives & 13.416 & 0.712 & 0.676 & 0.583 \\
+\(p_{m}(l)\) & Proportion of non-judgemental midwives & 21.079 & 0.648 & 0.659 & 0.373 \\
+\(q_{w}\) & Probability of women sharing & 2.307 & 3.481 & 0.891 & 0.600 \\
+\(w_{w}\) & Weight of shared information for women & 6.021 & 6.009 & 0.562 & 0.937 \\
+\(q_{m}\) & Probability of midwives sharing & 0.315 & 1.829 & 0.114 & 0.117 \\
+\(w_{m}\) & Weight of shared information for midwives & 1.652 & 1.354 & 0.260 & 0.0.139 \\
+\(x_{h}\) & Health payoff for healthy delivery & 0.253 & 0.612 & 4.889 & 15.146 \\
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.504 & 3.096 & 19.863 & 25.999 \\
+Total & All parameters and two way interactions & 84.9968 & 77.413 & 57.125 & 83.322 \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
 \end{tabular}
-\caption{IQR of median moderate drinker signalling parameter sensitivity \label{tab:sa_results_sig_iqr}}
 \end{table}
@@
 \begin{table}[H]
-\center
-\begin{tabular} {|l | l | l | l | l | l | l |}
-\hline
-Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
-Lexicographic & 1.425 & 0.436 & 0.549 & 0.008 & 0.114 & 2.719 \\ \hline
-Bayesian Payoff & 1.223 & 0.496 & 0.747 & 0.012 & 0.207 & 2.034 \\ \hline
-Bayesian &  1.065 & 0.000 & 0.230 & 0.002 & 0.088 & 1.015 \\ \hline
-\ac{CPT} & 0.874 & 0.213 & 0.233 & 0.001 & 0.066 & 1.806 \\ \hline
+\caption{IQR of median between groups IQR emulator statistics \label{tab:sa_emulator_sig_iqr}}
+\begin{tabular} {lllllll}
+\hline\noalign{\smallskip}
+Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\
+\noalign{\smallskip}\svhline\noalign{\smallskip}
+Lexicographic & 1.425 & 0.436 & 0.549 & 0.008 & 0.114 & 2.719 \\
+Bayesian Payoff & 1.223 & 0.496 & 0.747 & 0.012 & 0.207 & 2.034 \\
+Bayesian &  1.065 & 0.000 & 0.230 & 0.002 & 0.088 & 1.015 \\
+\ac{CPT} & 0.874 & 0.213 & 0.233 & 0.001 & 0.066 & 1.806 \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
 \end{tabular}
-\caption{IQR of median between groups IQR emulator statistics \label{tab:sa_emulator_sig_iqr}}
 \end{table}
@@
 \begin{table}[H]
-\center
-\begin{tabular} {|l | l | l | l | l | l |}
-\hline
-Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\ \hline
-\(p_{w}(m)\) & Proportion of moderate drinkers & 0.691 & 5.926 & 1.053 & 1.265 \\ \hline
-\(p_{w}(l)\) & Proportion of light drinkers & 3.664 & 17.047 & 4.877 & 3.656 \\ \hline
-\(p_{m}(m)\) & Proportion of moderate midwives & 41.369 & 1.124 & 0.814 & 0.591 \\ \hline
-\(p_{m}(l)\) & Proportion of non-judgemental midwives & 7.109 & 0.739 & 0.496 & 0.378 \\ \hline
-\(q_{w}\) & Probability of women sharing & 1.963 & 2.038 & 0.733 & 0.589 \\ \hline
-\(w_{w}\) & Weight of shared information for women & 7.932 & 11.193 & 2.289 & 1.960 \\ \hline
-\(q_{m}\) & Probability of midwives sharing & 0.413 & 1.972 & 0.267 & 0.069\\ \hline
-\(w_{m}\) & Weight of shared information for midwives & 0.120 & 2.902 & 0.150 & 0.123 \\ \hline
-\(x_{h}\) & Health payoff for healthy delivery & 0.228 & 3.190 & 6.308 & 14.777 \\ \hline
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.673 & 10.411 & 22.901 & 26.340 \\ \hline
-Total & All parameters and two way interactions & 85.740 & 88.611 & 68.640 & 84.210 \\ \hline
+\caption{IQR of median between groups IQR parameter sensitivity \label{tab:sa_results_iqr_iqr}}
+\begin{tabular} {llllll}
+\hline\noalign{\smallskip}
+Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
+\noalign{\smallskip}\svhline\noalign{\smallskip}
+\(p_{w}(m)\) & Proportion of moderate drinkers & 0.691 & 5.926 & 1.053 & 1.265 \\
+\(p_{w}(l)\) & Proportion of light drinkers & 3.664 & 17.047 & 4.877 & 3.656 \\
+\(p_{m}(m)\) & Proportion of moderate midwives & 41.369 & 1.124 & 0.814 & 0.591 \\
+\(p_{m}(l)\) & Proportion of non-judgemental midwives & 7.109 & 0.739 & 0.496 & 0.378 \\
+\(q_{w}\) & Probability of women sharing & 1.963 & 2.038 & 0.733 & 0.589 \\
+\(w_{w}\) & Weight of shared information for women & 7.932 & 11.193 & 2.289 & 1.960 \\
+\(q_{m}\) & Probability of midwives sharing & 0.413 & 1.972 & 0.267 & 0.069\\
+\(w_{m}\) & Weight of shared information for midwives & 0.120 & 2.902 & 0.150 & 0.123 \\
+\(x_{h}\) & Health payoff for healthy delivery & 0.228 & 3.190 & 6.308 & 14.777 \\
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.673 & 10.411 & 22.901 & 26.340 \\
+Total & All parameters and two way interactions & 85.740 & 88.611 & 68.640 & 84.210 \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
 \end{tabular}
-\caption{IQR of median between groups IQR parameter sensitivity \label{tab:sa_results_iqr_iqr}}
 \end{table}
@@
 \begin{table}[H]
-\center
-\begin{tabular} {|l | l | l | l | l | l | l |}
-\hline
-Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\ \hline
-Lexicographic & 0.826 & 0.409 & 0.259 & 0.002 & 0.034 & 2.364 \\ \hline
-Bayesian Payoff & 3.202 & 0.520 & 0.328 & 0.002 & 0.032 & 2.452 \\ \hline
-Bayesian & 1.177 & 0.041 & 0.133 & 0.000 & 0.018 & 1.152 \\ \hline
-\ac{CPT} & 0.874 & 0.118 & 0.126 & 0.000 & 0.017 & 1.570 \\ \hline
+\caption{IQR of median between groups IQR emulator statistics \label{tab:sa_emulator_iqr_iqr}}
+\begin{tabular} {lllllll}
+\hline\noalign{\smallskip}
+Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\
+\noalign{\smallskip}\svhline\noalign{\smallskip}
+Lexicographic & 0.826 & 0.409 & 0.259 & 0.002 & 0.034 & 2.364 \\
+Bayesian Payoff & 3.202 & 0.520 & 0.328 & 0.002 & 0.032 & 2.452 \\
+Bayesian & 1.177 & 0.041 & 0.133 & 0.000 & 0.018 & 1.152 \\
+\ac{CPT} & 0.874 & 0.118 & 0.126 & 0.000 & 0.017 & 1.570 \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
 \end{tabular}
-\caption{IQR of median between groups IQR emulator statistics \label{tab:sa_emulator_iqr_iqr}}
 \end{table}

### 2015-07-13 model_description.tex
Table formatting

@@
 
-To resolve this, we can do exactly that, and cast it as a signalling game (fig \ref{fig:less_simple}).
-We make the simplifying assumption that a woman may have one of only three drinking patterns - light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy.
+To resolve this, we can do exactly that, and cast it as a signalling game (fig \ref{fig:less_simple}), with three types of player, corresponding to categories of drinking behaviour (light, moderate, and heavy).
 Each of these types of player, will play a different game.

### 2015-09-14 simulation_schedule.tex
More reorganisation
More trimming
Finish sim schedule
Motivation & methods mini lit review
+ finish sim schedule
twiddling

@@
 
-\begin{itemize}
+\begin{enumerate}
 \item Generate 1000 women, and place them in a queue
@@
 \item For each round of the game
-\begin{itemize}
+\begin{enumerate}
 	\item Take 100 women from the queue
@@
 	\item For each pair
-\begin{itemize}
-\item Woman sends a signal
-\item Midwife refers or not based on the signal
-\item Woman is informed of their payoff, the midwife's type, and whether they are referred
+	\begin{enumerate}
+		\item The woman sends a signal
+		\item The midwife refers or not based on the signal
+		\item The woman is informed of their payoff, the midwife's type, and whether they are referred
+		\item The woman updates her beliefs
+		\item The midwife stores the game in their memory
 		\item If the woman is referred
-\begin{itemize}
+		\begin{enumerate}
 			\item The midwife is informed of the woman's true type
@@
 			\item The midwife is now eligible to share their memories of games with this woman
-\end{itemize}
-\end{itemize}
-\item Women who have not been referred, or had their baby join the back of the queue
-\item Generate new women to replace those referred, or delivered
-\item Add new women to the back of the queue
+		\end{enumerate}
+	\end{enumerate}
+	\item Women who have not been referred or had their baby, join the back of the queue
+	\item New women are generated to replace those referred, or delivered
+	\item The new women are added to the back of the queue
 	\item For each referred or birthed woman
-\begin{itemize}
+	\begin{enumerate}
 		\item With probability p, their memory of games is shared with the active women
 		\item They are removed from simulation
-\end{itemize}
+	\end{enumerate}
+	\item The active women update their beliefs
 	\item For each midwife with information to share
-\begin{itemize}
+	\begin{enumerate}
 		\item With probability p, their memory of games with the referred woman is shared
 		\item The memory is no longer eligible to be shared
-\end{itemize}
-\end{itemize}
-\end{itemize}
+	\end{enumerate}
+	\item The midwives update their beliefs
+\end{enumerate}
+\end{enumerate}

### 2015-09-14 Introduction.tex
Changed process is opaque
to where the process is obscured

@@
 
-The resulting scenario is of substantial independent interest, and shows the potential utility of a simulation approach in domains where process is opaque, here both because of the interest in concealment, and obvious ethical concerns.
+The resulting scenario is of substantial independent interest, and shows the potential utility of a simulation approach in domains where the process is obscured, here both because of the interest in concealment, and obvious ethical concerns.
 With this said, the lack of a strong quantitative evidence base against which to validate the behaviour of the model augers for caution in interpreting the results, and a necessary reminder that in this instance the model is primarily a tool for formalisation of the thought process \citep{epstein2008}, rather than a machine for predicting.

### 2015-09-14 Model.tex
s/it/
Remove singular

@@
 To model a scenario, we take the approach of first creating a formal game to represent it, capturing the key features as far as possible in the structure of that game.
-This game is in essence a conjecture about the real data generating process, which can be played out it in simulation.
+This game is in essence a conjecture about the real data generating process, which can be played out in simulation.
 
@@
 
-Typically in the UK, a women will have 12 appointments with a midwife during the antenatal period, and in the majority of cases will encounter several different midwives \citep{Redshaw2014} in the course of their care.
+Typically in the UK, women have 12 appointments with a midwife during the antenatal period, and in the majority of cases will encounter several different midwives \citep{Redshaw2014} in the course of their care.
 In the UK, and unlike most healthcare scenarios, maternity notes are held by the patient, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously.

### 2015-09-14 Model.tex
scenarios - contexts
clarify that we mean ‘decisions’ by same outputs

@@
 Typically in the UK, women have 12 appointments with a midwife during the antenatal period, and in the majority of cases will encounter several different midwives \citep{Redshaw2014} in the course of their care.
-In the UK, and unlike most healthcare scenarios, maternity notes are held by the patient, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously.
+In the UK, and unlike most healthcare contexts, maternity notes are held by the patient, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously.
 Maternity notes are not generally linked to extra-departmental records, meaning that a history of alcohol related admissions to another service may remain unknown unless revealed by the woman.

### 2015-09-14 agent_models.tex
scenarios - contexts
clarify that we mean ‘decisions’ by same outputs

@@
 
-While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same outputs, we limit ourselves here to four.
+While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same output - a decision, we limit ourselves here to four.
 The simplest is a lexicographic rule (1), in the spirit of a \acl{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}.

### 2015-09-14 Methods.tex
Align
Add random seed footnote

@@
 
-Two key measures were used: the fraction of the subpopulation who had ever signalled honestly, and the proportion referred.
+Two key measures were used: the fraction of the subpopulation who had ever signalled honestly, and the proportion of the population who were referred.
 Both measures were taken after every round of play, and were taken relative to the agent's position in their sequence of appointments giving the probability of signalling honestly, or being referred having had a given number of appointments.
@@
 \label{tab:qt_params}
-\begin{tabular} {llc}
+\begin{tabular} {lll}
 \hline\noalign{\smallskip}
@@
 Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each, with emulator quality assessed by leave-one-out cross validation.
-A fixed set of 100 random seeds was used, such that each parameter set was run once with each seed, for every decision rule.
+A fixed set of 100 random seeds was used\footnote{Fixed random seeds were used to allow simulation results to be reproducible, since the combination of a parameter set and a random seed yields a deterministic process.}, such that each parameter set was run once with each seed, for every decision rule.
 

### 2015-09-14 Methods.tex
IQR

@@
 
-To capture the response characteristics for the model, we measured four outcome variables - (1) the interquartile range of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3, 4) the interquartile range of the average signal, and \ac{IQR} between simulation runs.
+To capture the response characteristics for the model, we measured four outcome variables - (1) the \ac{IQR} of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3, 4) the \ac{IQR} of 1 \& 2 between simulation runs.
 Together these four metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the variability in the system in response to changes to the parameters (3 \& 4).

### 2015-09-14 Results.tex
Tweaking results language

@@
 While there are small contributions to variance in interaction with other parameters (e.g.
-4\% to between groups IQR, for the interaction with the proportion of light drinkers under the Bayesian rule), this may suggest that the implementation is lacking, which we touch on in section \ref{sec:conclusion}.
+4\% to between groups IQR, for the interaction with the proportion of light drinkers under the Bayesian rule), this may suggest that the model is lacking in this area, which we touch on in section \ref{sec:conclusion}.
 
@@
 \includegraphics[width=119mm]{figures/sharing_emulated_simulated}
-\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules}
+\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules, with signals coded as 0 = light, 1 = moderate, and 2 = heavy.}
 \label{fig:outcome_plots}

### 2015-09-14 model_description.tex
Remove 'this'
Nash footnote

@@
 
-A game, in the game theoretic sense, this can be any interaction where the result for one person is dependent on the actions of another.
+A game, in the game theoretic sense, can be any interaction where the result for one person is dependent on the actions of another.
 In this scenario, the result for the woman would seem dependent on whether the midwife chooses to refer them for specialist support (although naturally the reality can only be thought of in terms of risk mitigation), and conversely, the right choice for the midwife is somewhat contingent on what the woman is willing to tell them.
@@
 The only time things in this very restricted world obviously end poorly, is if the woman asks for help but does not get any.
-This implies that a rational player would always refer if asked for help, and is indifferent otherwise - in other words, there are three possible Nash equilibriums.}
+This implies that a rational player would always refer if asked for help, and is indifferent otherwise - in other words, there are three possible Nash equilibriums\footnote{A Nash equilibrium is a solution to a game between two or more players, where no player can gain from changing their move.}.}
 \label{fig:simplest_game}

### 2015-09-15 Model.tex
Fix footnote
And add note to explain verbal example

@@
 The best move depends on the type, and beliefs of the midwife.
-For example, a particularly unlucky scenario might be for the midwife to not only be of a harshly judgemental disposition, but to believe that no women really need to be referred.
+For example, a particularly unlucky scenario might be for the midwife to not only be of a harshly judgemental disposition, but to believe that no women really need to be referred (i.e.
+that all women are light drinkers).
 Even a relatively weak belief in this possibility can make the honest signal look like an unwarranted risk.

### 2015-09-15 model_description.tex
Fix footnote
And add note to explain verbal example

@@
 The only time things in this very restricted world obviously end poorly, is if the woman asks for help but does not get any.
-This implies that a rational player would always refer if asked for help, and is indifferent otherwise - in other words, there are three possible Nash equilibriums\footnote{A Nash equilibrium is a solution to a game between two or more players, where no player can gain from changing their move.}.}
+This implies that a rational player would always refer if asked for help, and is indifferent otherwise - in other words, there are three possible Nash equilibriums\protect\footnotemark.}
 \label{fig:simplest_game}
 \end{figure}
+
+\footnotetext{A Nash equilibrium is a solution to a game between two or more players, where no player can gain from changing their move.}
 

### 2015-09-15 Results.tex
Clarifying what info is shared matters
Change caption for fig 1 & 2

@@
 \includegraphics[width=119mm]{figures/honesty_plot}
-\caption{Average fraction of population ever signalled honestly after 1000 rounds, mean with 95\% confidence limit over 1000 runs\label{fig:honest_signals}}
+\caption{Average fraction of population ever signalled honestly by each appointment, after 1000 rounds, mean with 95\% confidence limit over 1000 runs.
+Note that the large number of runs leads to very tight confidence intervals.\label{fig:honest_signals}}
 \end{figure}
@@
 \includegraphics[width=119mm]{figures/honesty_sharing}
-\caption{Impact of social learning on trends in honest signalling after 1000 rounds, mean with 95\% confidence interval over 100 runs}
+\caption{Impact of social learning on trends in the average fraction of population ever signalled honestly by their final appointment, after 1000 rounds, mean with 95\% confidence interval over 100 runs}
 \label{fig:honest_sharing}
@@
 They also suggest that the Bayesian decision rule is less stable under conditions where the weight of shared information is substantially higher than the probability of sharing.
-This suggests, perhaps unsurprisingly, that what information is shared is significant to outcomes.
+This indicates that placing a high weight on information from limited sources leads to greater variability, i.e.
+what information shared, matters.
 

### 2015-09-15 Conclusion.tex
Inter-intra distinction

@@
 
-From a pragmatic perspective, the differing response characteristics of the decision rules are substantial and significant.
+From a pragmatic perspective, the differing response characteristics of the classes decision rules are substantial and significant.
 The lack of a mechanism of homophily in the very simple rules leads to a high level of uncertainty in the overall dynamics, since even irrelevant information is taken at face value and to be equally valuable.
@@
 
-One of the notable features of the results is the similarity in behaviour of the two classes of decision rule.
+One of the notable features of the results is that the behaviour of rules within a class is very similar.
 To some extent this reflects poorly on the most complex rule, \ac{CPT}, which diverges only minimally in behaviour from the Bayesian model.
@@
 This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared and more sophisticated model of information transmission in general.
-This also highlights an advantage of the \ac{BACCO} approach, in diagnosing issues with model design by giving insight into parameters which are contributing inappropriately to variance in output.
+This also highlights an advantage of the \ac{BACCO} approach (which we describe in section \ref{sub:sensitivity}), in diagnosing issues with model design by giving insight into parameters which are contributing inappropriately to variance in output.
 Coupled with the ability of emulators to rapidly explore parameter space, this clearly suggests that statistical emulation is a powerful tool to support simulation based approaches.

### 2015-09-15 Conclusion.tex
Payoffs

@@
 To some extent this reflects poorly on the most complex rule, \ac{CPT}, which diverges only minimally in behaviour from the Bayesian model.
-This might be to a degree anticipated, in that the payoffs are unrealistic, which limits the utility of the \ac{CPT} approach.
+This might be to a degree anticipated since we have not elicited payoffs for obvious practical and ethical reasons, and they may be unrealistic, which limits the utility of the \ac{CPT} approach.
 Additionally, work by \citet{Glockner2012} has shown that there is considerable variation in individual parameters for the decision model, whereas we have let them remain homogeneous here.

### 2015-09-15 Conclusion.tex
Explain the homophily situation better

@@
 From a pragmatic perspective, the differing response characteristics of the classes decision rules are substantial and significant.
-The lack of a mechanism of homophily in the very simple rules leads to a high level of uncertainty in the overall dynamics, since even irrelevant information is taken at face value and to be equally valuable.
-By contrast, the belief structure of the \ac{CPT}, and Bayesian models represents a useful abstraction which allows the use of the relevant aspects of the information.
-Naturally, incorporating homophily, by, for example weighting shared information by the type of the sharer, would represent a trivial modification to the heuristic models.
+There is a high level of uncertainty in the overall dynamics with the model free rules.
+This does not arise with the more complex rules, because they reframe information from others in the context of their own experiences, as what would happen to them in that situation.
+By contrast, the simpler rules treat the experiences as having literally happened to them, and since there is no mechanism of homophily, no way to listen only to accounts of agents similar to themselves, they can come to believe unreasonable things.Naturally, incorporating homophily, by, for example weighting shared information by the type of the sharer, would represent a trivial modification to the heuristic models.
 While to some extent this highlights the flexibility of the decision rule approach, it would of course sacrifice the parsimony of the model.

### 2015-09-15 Conclusion.tex
We mean midwives with the example

@@
 This does not arise with the more complex rules, because they reframe information from others in the context of their own experiences, as what would happen to them in that situation.
-By contrast, the simpler rules treat the experiences as having literally happened to them, and since there is no mechanism of homophily, no way to listen only to accounts of agents similar to themselves, they can come to believe unreasonable things.Naturally, incorporating homophily, by, for example weighting shared information by the type of the sharer, would represent a trivial modification to the heuristic models.
+By contrast, the simpler rules treat the experiences as having literally happened to them, and since there is no mechanism of homophily, no way to listen only to accounts of agents similar to themselves, they can come to believe unreasonable things.
+Naturally, incorporating homophily, by, for example weighting shared information by the type of the sharer, would represent a trivial modification to the heuristic models.
 While to some extent this highlights the flexibility of the decision rule approach, it would of course sacrifice the parsimony of the model.

### 2015-09-15 Model.tex
We mean midwives with the example

@@
 In the disclosure game model, this takes the form of having each agent recount their play history to their colleagues with some probability \(q\).
-Individuals then incorporate shared information into their beliefs using weighted updates, such that a shared observation of a low type signal contributes to their beliefs by \(w\), and \(0\leq w\leq 1\) (i.e.
+Individuals then incorporate shared information into their beliefs using weighted updates, e.g.
+for a midwife a shared observation of a low type signal contributes to their beliefs by \(w\), and \(0\leq w\leq 1\) (i.e.
 \(n_{j} = n_{j} + w\)).

### 2015-09-15 Results.tex
Make it more obvious
That heavy & moderate pool because it is low risk for both

@@
 For these decision models, this is because social learning exacerbates the existing tendency of heavy drinkers to impersonate moderate drinkers, who behave more honestly as heavy drinkers become less so.
+This arises because both classes of agent learn that the moderate signal is the lower risk option as it is both a reliable indicator of need, and does not attract strongly negative judgement.
+The reliability of the signal is self reinforcing, since the more the agents use it and get referred, the more confident midwives become that it indicates need.
 

### 2015-09-15 Introduction.tex
Revised figures
Rewrite game theory -> decision theory bit

@@
 While scenarios may map to a number of games, exploring one candidate game still allows for a principled comparison between interpretations, and enforces explicit assumptions.
-Relating this to decision theory shifts the emphasis away from analytical equilibrium-seeking, and heightens the importance of behaviour change.
-This is clearly desirable where the focus is on the behavioural processes driving a system in motion, and how they change in response to that movement.
-Fundamentally, the shift of emphasis is from the process of acquiring and inferring the information needed to make choices, to the process of decision.
+But equilibrium is the sine qua non of game theory, and we wish to see the system in motion rather than just at rest, even if it does eventually settle to some stable point.
+We choose to focus instead on the behavioural processes driving a system in motion, a system out of equilibrium, to understand how these processes interact with the movement.
+Introducing decision theory takes a step down the ladder of abstraction from the mental chess of game theory.
+Dealing instead in the mechanics of decision making, and the calculus of choice allows us to explore not only paths that arrive at the destinations we might consider in game theory, but also avenues not accessible where we constrain ourselves to a sometimes implausible degree of rationality.
+
 This does not preclude a strategic dimension, since decision rules are to a great extent modular, and as demonstrated in this paper can be exchanged without altering the decision problem.
-In addition, rules are agnostic as to where the source of information, suggesting room for multi-stage processes.
+In addition, rules are agnostic as to the source of information, suggesting room for multi-stage processes - for example, a more game theoretic mental model approach could act as information source for a decision rule.
 As a corollary, the decision problem agents attempt to answer can change, allowing behaviour in novel problems to be informed by beliefs derived under other conditions.

### 2015-09-15 Model.tex
Make it more obvious
That heavy & moderate pool because it is low risk for both
Rewrite game theory -> decision theory bit

@@
 By the same rationale, midwives share only their history with the most recent woman they referred.
-Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{More precisely, memories of games remain, but it is assumed that only the most current information is relevant enough to be shared.}
+Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{More precisely, memories of games remain, but it is assumed that only the most current information is relevant enough to be shared.} Accounts are shared with some probability, to all fellow players.
+For example, a heavy drinker finishes play having claimed to be a light drinker, without ever being referred, and their account is selected to be shared with some probability $q_{w}$.
 
@@
 
+A payoff based agent, who is a light drinker, hears the account of the heavy drinker.
+They take the account as literally happening to them, and update their beliefs to include the possibility that there is a negative outcome attached to claiming to be a light drinker.
+
 By contrast, representing the problem in terms of the probabilities of the individual lotteries imposes a model that abstracts the new information from payoffs, and allows the agent to discard implausible outcomes.
 This stronger assumption as to the static and known qualities of payoffs does however reduce the flexibility of the decision rule.
+
+Returning to our example, a light drinker using this decision rule would follow the account through from their position in the game tree, correctly inferring that the outcome in their case would be positive.

### 2015-09-16 Introduction.tex
equilibrium

--- 2015-09-14 Introduction.tex
@@
 While scenarios may map to a number of games, exploring one candidate game still allows for a principled comparison between interpretations, and enforces explicit assumptions.
-Relating this to decision theory shifts the emphasis away from analytical equilibrium-seeking, and heightens the importance of behaviour change.
-This is clearly desirable where the focus is on the behavioural processes driving a system in motion, and how they change in response to that movement.
-Fundamentally, the shift of emphasis is from the process of acquiring and inferring the information needed to make choices, to the process of decision.
+But equilibrium is the sine qua non of game theory, which is concerned with the stable outcome of an infinite contest of second guesses.
+We wish to see the system in motion rather than just at rest, even if it does eventually settle to some stable point.
+Instead, we choose to focus instead on the behavioural processes driving a system in motion, a system out of equilibrium, to understand how these processes interact with the movement.
+Introducing decision theory takes a step down the ladder of abstraction from the mental chess of game theory.
+Dealing instead in the mechanics of decision making, and the calculus of choice, allows us to explore not only paths that arrive at the destinations we might consider in game theory, but also avenues not accessible where we constrain ourselves to a sometimes implausible degree of rationality.
+
 This does not preclude a strategic dimension, since decision rules are to a great extent modular, and as demonstrated in this paper can be exchanged without altering the decision problem.
-In addition, rules are agnostic as to where the source of information, suggesting room for multi-stage processes.
+In addition, rules are agnostic as to the source of information, suggesting room for multi-stage processes - for example, a more game theoretic, model of the opponent's mind, type approach could act as an information source for a decision rule.
 As a corollary, the decision problem agents attempt to answer can change, allowing behaviour in novel problems to be informed by beliefs derived under other conditions.
@@
 Given these features, the application of decision, and game theory to \ac{ABM} is an attractive approach to computational social science, where the locus of interest is process, and decision making.
-Taking a balance between models focused on replication of low level neurological mechanics, and those with a higher level emphasis where individual behaviours are abstracted away yields a computationally tractable approach.
+Taking a balance between models focused on replication of low level neurological mechanics, and those with a higher level emphasis where individual behaviours are abstracted away, yields a computationally tractable approach.
 Despite the relative simplicity, it nonetheless captures some of the nuance and sophistication of human decisions.

### 2015-09-17 Results.tex
the same, rather than single, signal

@@
 Figure \ref{fig:emulated_payoff_group_iqr} shows better separation, close to partial pooling\footnote{Pooling occurs when signallers of different types `pool' their signals, and one adopts the signals of another.} at high payoff distinction, with relatively modest honesty bias, which is reflected by the variance contributions of 11\% and 8\% respectively.
-For the more complex rules, the general tendency is towards less pooling for higher values of both, but with pockets where full pooling\footnote{Indicating that all signaller types are using a single signal.} occurs.
+For the more complex rules, the general tendency is towards less pooling for higher values of both, but with pockets where full pooling\footnote{Indicating that all signaller types are using a the same signal.} occurs.
 The plots also suggest that the sensitivity of the \ac{CPT} rule is marginally greater, which is supported by the significant contribution to variance of close to 15\% for all measures of \(x_{h}\).

### 2015-09-18 Methods.tex
s/in/of

@@
 To capture the response characteristics for the model, we measured four outcome variables - (1) the \ac{IQR} of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3, 4) the \ac{IQR} of 1 \& 2 between simulation runs.
-Together these four metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the variability in the system in response to changes to the parameters (3 \& 4).
+Together these four metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the variability of the system in response to changes to the parameters (3 \& 4).
 

### 2015-09-26 Conclusion.tex
Additional figs

@@
 
-From a pragmatic perspective, the differing response characteristics of the classes decision rules are substantial and significant.
+From a pragmatic perspective, the differing response characteristics of the classes decision rules are substantial and significant, particularly when social learning is considered.
 There is a high level of uncertainty in the overall dynamics with the model free rules.
@@
 While to some extent this highlights the flexibility of the decision rule approach, it would of course sacrifice the parsimony of the model.
-This is an important consideration, given that part of the argument in favour of a decision theoretic approach lies in the minimal nature of the behavioural rules, which can be seen as occupying a middle ground between parameter and model.
+This is an important consideration, given that part of the argument in favour of a decision theoretic approach lies in the minimal nature of the behavioural rules.
 
@@
 In reality it might be anticipated that midwives would not withhold judgement, and would pass on concerns about specific women to their colleagues, or that particularly dramatic stories would persist and be passed.
-This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared and more sophisticated model of information transmission in general.
+This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared and more sophisticated model of information flow in general.
 This also highlights an advantage of the \ac{BACCO} approach (which we describe in section \ref{sub:sensitivity}), in diagnosing issues with model design by giving insight into parameters which are contributing inappropriately to variance in output.
 Coupled with the ability of emulators to rapidly explore parameter space, this clearly suggests that statistical emulation is a powerful tool to support simulation based approaches.
+This is not without caveats however, since as noted in section \ref{sub:sa_results} the emulators here are indicative, but not definitive.
+Amongst the reasons this may arise are heteroskedasticity associated with social learning, the stochastic nature of the simulation, and a lack of precision.
+The latter could be improved through iterative fitting procedures, where the simulation is sampled more heavily in plausible regions of parameter space, a procedure not possible here given the dearth of data.
+The former issues could be addressed by a more comprehensive approach to setting the nugget, which explicitly incorporates point variance.
 

### 2015-09-26 Methods.tex
Additional figs

@@
 
-Measurements were taken at the end of 1000 rounds of play, and emulators were built against the median, and \ac{IQR} of each measure to assess both the overall trend, and the extent to which the parameters contribute to variance between runs.
+Measurements were taken at the end of 1000 rounds of play, and emulators were built against 400 sample points from the full set of simulation results (1 \& 2), and \ac{IQR} at each point (3 \& 4) to assess both the overall trend, and the extent to which the parameters contribute to variance between runs.
 

### 2015-09-26 Results.tex
is
Rearrange payoff tables
To save some space
Additional figs

@@
 Trends for all four rules are broadly similar, exhibiting a gradual increase across appointments which subsequently levels off.
-This levelling can in part be explained by the referral results, which show that the majority of drinkers are referred, even with substantial concealment.
+This levelling can in part be explained by the referral results (see figure \ref{fig:ref_plot} in appendix \ref{app:additional_figures}), which show that the majority of drinkers are referred, even with substantial concealment.
 Referrals continue to occur, in the absence of honest signals, because drinkers are able to achieve a referral by masquerading as higher or lower types, dependent on how their initial beliefs are biased.
@@
 
-\begin{figure}[h]
-\includegraphics[width=119mm]{figures/honesty_plot}
-\caption{Average fraction of population ever signalled honestly by each appointment, after 1000 rounds, mean with 95\% confidence limit over 1000 runs.
-Note that the large number of runs leads to very tight confidence intervals.\label{fig:honest_signals}}
-\end{figure}
-
 \subsection{Social Learning}
@@
 
-Introducing social learning amongst women leads the behaviour of the decision rules to diverge markedly.
+Introducing social learning amongst women leads the behaviour of the decision rules to diverge markedly, which we explore possible reasons for in section \ref{sec:discussion}.
 Figure \ref{fig:honest_sharing} shows the proportion of women who have signalled honestly at least once by their final appointment, under four sharing conditions.
 
-\begin{figure}
-\includegraphics[width=119mm]{figures/honesty_sharing}
+\begin{figure}[H]
+\includegraphics[width=100mm]{figures/honesty_sharing}
 \caption{Impact of social learning on trends in the average fraction of population ever signalled honestly by their final appointment, after 1000 rounds, mean with 95\% confidence interval over 100 runs}
@@
 
+\begin{figure}[H]
+\includegraphics[width=100mm]{figures/sharing_emulated_simulated}
+\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules, with signals coded as 0 = light, 1 = moderate, and 2 = heavy.}
+\label{fig:outcome_plots}
+\end{figure}
+
 Perhaps surprisingly, variance attributable to social learning between midwives is relatively low, with neither the weight nor probability accounting for more than 5\% of variance in any measure.
@@
 
-\begin{figure}[h]
-\includegraphics[width=119mm]{figures/sharing_emulated_simulated}
-\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules, with signals coded as 0 = light, 1 = moderate, and 2 = heavy.}
-\label{fig:outcome_plots}
-\end{figure}
-
 Figure \ref{fig:outcome_plots} gives a qualitative picture of both emulator quality, and the divergent response surfaces of the decision rules in response to variations in social learning parameters.
@@
 
-\begin{figure}[h]
-\includegraphics[width=119mm]{figures/unfixed_emu_sig_iqr}
+\begin{figure}[H]
+\includegraphics[width=100mm]{figures/unfixed_emu_sig_iqr}
 \caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\)}
@@
 This indicates that placing a high weight on information from limited sources leads to greater variability, i.e.
-what information shared, matters.
+what information is shared, matters.
+
+\begin{figure}[H]
+\includegraphics[width=100mm]{figures/unfixed_emu_payoff_honesty_group_iqr}
+\caption{Emulated between groups IQR in response to varying \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\), and \(x_{h}\)}
+\label{fig:emulated_payoff_group_iqr}
+\end{figure}
 
@@
 The plots also suggest that the sensitivity of the \ac{CPT} rule is marginally greater, which is supported by the significant contribution to variance of close to 15\% for all measures of \(x_{h}\).
-
-\begin{figure}[H]
-\includegraphics[width=119mm]{figures/unfixed_emu_payoff_honesty_group_iqr}
-\caption{Emulated between groups IQR in response to varying \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\), and \(x_{h}\)}
-\label{fig:emulated_payoff_group_iqr}
-\end{figure}

### 2015-09-26 Results.tex
Tweaks
Tweaking figure placement

@@
 Under these parameters, light drinkers always signal honestly and are never referred since there is no perceived advantage in doing so, and the evidence of deceptive signalling is insufficient to outweigh the biased priors of the midwives.
+
+\begin{figure}[H]
+\includegraphics[width=100mm]{figures/honesty_plot}
+\caption{Average fraction of population ever signalled honestly by each appointment, after 1000 rounds, mean with 95\% confidence limit over 1000 runs.
+Note that the large number of runs leads to very tight confidence intervals.\label{fig:honest_signals}}
+\end{figure}
 
@@
 
+\begin{figure}[H]
+\includegraphics[width=90mm]{figures/sharing_emulated_simulated}
+\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules, with signals coded as 0 = light, 1 = moderate, and 2 = heavy.}
+\label{fig:outcome_plots}
+\end{figure}
+
 For the median signal choice of moderate drinkers, the results of the sensitivity analysis suggest that the proportion of light drinkers has a significant effect for all decision rules, accounting for 10\%, 38\%, 24\%, and 5\% of the variance in output for the Lexicographic, Bayesian Payoff, Bayesian, and \ac{CPT} rules respectively.
@@
 The proportions of midwives are also key drivers in group separation, and the between run IQR of both measures for this rule.
-
-\begin{figure}[H]
-\includegraphics[width=100mm]{figures/sharing_emulated_simulated}
-\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules, with signals coded as 0 = light, 1 = moderate, and 2 = heavy.}
-\label{fig:outcome_plots}
-\end{figure}
 

### 2015-09-26 Conclusion.tex
Pronouns

@@
 Coupled with the ability of emulators to rapidly explore parameter space, this clearly suggests that statistical emulation is a powerful tool to support simulation based approaches.
-This is not without caveats however, since as noted in section \ref{sub:sa_results} the emulators here are indicative, but not definitive.
-Amongst the reasons this may arise are heteroskedasticity associated with social learning, the stochastic nature of the simulation, and a lack of precision.
-The latter could be improved through iterative fitting procedures, where the simulation is sampled more heavily in plausible regions of parameter space, a procedure not possible here given the dearth of data.
+As noted in section \ref{sub:sa_results} the emulators here are indicative, but not definitive.
+Amongst the reasons discrepancy arises here are heteroskedasticity associated with social learning, the stochastic nature of the simulation, and a lack of precision given the large parameter range.
 The former issues could be addressed by a more comprehensive approach to setting the nugget, which explicitly incorporates point variance.
+The latter could be improved through iterative fitting procedures, where the simulation is sampled more heavily in plausible regions of parameter space, a procedure not possible here given the dearth of data to evaluate plausibility.
+That the discrepancy exists is not prohibitive in this instance, since we are not using the emulator for prediction, only to achieve a broad strokes picture of the behaviour of the simulator.
 

### 2015-09-26 article.tex
Pronouns

\documentclass[graybox]{svmult}
\usepackage[hyperfootnotes=false]{hyperref}
\hypersetup{bookmarksdepth=3}

\usepackage{mathptmx}       \usepackage{helvet}         \usepackage{courier}        \usepackage{type1cm}                                    \usepackage{makeidx}         \usepackage{graphicx}                                     \usepackage{multicol}        \usepackage[bottom]{footmisc} \usepackage{adjustbox}
 \usepackage{multirow}
 \usepackage{algorithm}
 \usepackage{algpseudocode}
 \usepackage{ifthen}
 \usepackage{csquotes}
 \usepackage{amsmath}

\usepackage{comment}
 \usepackage{natbib}
 \setcitestyle{numbers,square}
 \usepackage[subrefformat=parens,labelformat=simple,caption=false,labelfont={bf}]{subfig}
 \usepackage[nolist,smaller]{acronym}
\allowdisplaybreaks
\makeindex

\begin{document}
\begin{acronym}[ALSPAC]
  \acro{FAS}{Foetal Alcohol Syndrome}
  \acro{CPT}{Cumulative Prospect Theory}
  \acro{PT}{Prospect Theory}
  \acro{NICE}{the National Institute for Health and Care Excellence}
  \acro{IAPT}{Improving Access to Psychological Therapies}
  \acro{CMACE}{Centre for Maternal and Child Enquiries}
  \acroindefinite{CMACE}{the}{the}
  \acro{AUDIT}{Alcohol Use Disorders Identification Test}
  \acro{T-ACE}{Tolerance, Annoyance, Cut down, Eye-opener}
  \acro{RCOG}{Royal College of Obstetricians and Gynecologists}
  \acroindefinite{RCOG}{the}{the}
  \acro{AML}{acute myeloid leukemia}
  \acro{ADHD}{Attention Defecit Hyperactivity Disorder}
  \acro{PND}{Postnatal Depression}
  \acro{RCT}{randomised control trial}
  \acro{WHO}{the World Health Organisation}
  \acro{ESS}{Evolutionarily Stable Strategy}
  \acrodefplural{ESS}[ESS]{Evolutionarily Stable Strategies}
  \acro{MCMC}{Markov chain monte carlo methods}
  \acro{DU}{Discounted Utility}
  \acro{AIC}{Akaike information criterion}
  \acro{ANOVA}{analysis of variance}
  \acro{ALSPAC}{the Avon Longitudinal Study of Parents and Children}
  \acro{GEM}{Gaussian Emulation Machine}
  \acrodefplural{GEM}{Gaussian Emulation Machines}
  \acro{GEM-SA}{Gaussian Emulation Machine for Sensitivity Analysis}
  \acro{JIT}{Just-in-time}
  \acro{ABM}{Agent Based Modelling}
  \acro{ABMs}{Agent Based Models}
  \acro{CPT}{Cumulative Prospect Theory}
  \acro{FFH}{Fast and Frugal Heuristic}
  \acro{OFC}{orbito-frontal cortex}
  \acro{BACCO}{Bayesian Analysis of Computer Code Outputs}
  \acro{IQR}{interquartile range}
\end{acronym}

\title*{Deciding to Disclose}
\subtitle{A Decision Theoretic Agent Model of Pregnancy and Alcohol Misuse}

\author{Jonathan Gray, Jakub Bijak, and Seth Bullock}
\institute{Jonathan Gray \at University of Southampton, Southampton, United Kingdom \email{j.gray@soton.ac.uk}
\and Jakub Bijak \at University of Southampton, Southampton, United Kingdom \email{j.bijak@soton.ac.uk}
\and Seth Bullock \at University of Southampton, Southampton, United Kingdom \email{sgb@ecs.soton.ac.uk}}

\maketitle

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax

\section*{Abstract}

We draw together methodologies from game theory, agent based modelling, decision theory, and uncertainty analysis to explore the process of decision making in the context of pregnant women disclosing their drinking behaviour to their midwives.

We employ a game theoretic framework to define a signalling game. The game represents a scenario where pregnant women decide the extent to which they disclose their drinking behaviours to their midwives, and midwives employ the information provided to decide whether to refer their patients for costly specialist treatment. This game is then recast as two games played against \enquote{nature}, to permit the use of a decision theoretic approach where both classes of agent use simple rules to decide their moves.
Four decision rules are explored - a lexicographic heuristic which considers only the link between moves and payoffs, a Bayesian risk minimisation agent that uses the same information, a more complex Bayesian risk minimiser with full access to the structure of the decision problem, and a \ac{CPT} rule.

In simulation, we recreate two key qualitative trends described in the midwifery literature for all the decision models, and investigate the impact of introducing a simple form of social learning within agent groups.
Finally a global sensitivity analysis using \acp{GEM} is conducted, to compare the response surfaces of the different decision rules in the game. \acresetall

\section{Introduction}
\label{sec:intro}

The case in favour of \ac{ABM} as a general analytical approach has been made numerously, and elegantly (e.g. \cite{epstein1994growing,Resnick,Axelrod1997,gilbert1999simulation,Macy2002a,Silverman2011,Silverman2013,epstein2014agent_zero}, amongst others). As such we will not belabour the point, and instead turn to addressing some of the concerns expressed about the approach. In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, reflecting the assumptions of the modeller rather than empirically or theoretically grounded \citep{Waldherr2013}. To ameliorate this concern, we draw on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game\footnote{In a signalling game, one player (the signaller), has some piece of information that is known only to them which affects the outcome of the game for both players. The signaller has a choice as to what they tell the other player about this hidden information, and the responding player as to what they believe the information to be.} \citep{Kreps1987} with a basic form of intragroup social learning. Four decision models of varying complexity, and behavioural plausibility are contrasted, by way of demonstrating the significance of the operationalisation of decision making in \ac{ABM}.

This exercise is framed in the context of disclosure decisions, taking drinking patterns in pregnant women as a motivating example. Alcohol consumption in the antenatal period is a significant issue in itself, although there is not a clear consensus on associated risk. In terms of official guidance in the UK, \ac{NICE} acknowledge that evidence of harm to the fetus is less than conclusive, but advise not drinking at all, or significant moderation \citep{NICE2010a}, with similar advice from the UK \cite{DepartmentofHealth2008}.

Turning more specifically to disclosure of alcohol use by women to healthcare professionals during their pregnancy, research is relatively sparse, although qualitative trends are reported by \citet{Phillips2007} and \citet{Alvik2006}. The former explored factors impacting disclosure through a small case study, highlighting the need to build up rapport between woman and midwife over several appointments; the latter compared post partum reports of consumption with contemporaneous accounts, finding apparent underreporting during pregnancy which was amplified by increased drinking. The simulation model described in this paper is able to replicate both qualitative trends, i.e. an increase in disclosure over appointments, and more honest behaviour by moderate as compared to heavier drinkers.

The resulting scenario is of substantial independent interest, and shows the potential utility of a simulation approach in domains where the process is obscured, here both because of the interest in concealment, and obvious ethical concerns. With this said, the lack of a strong quantitative evidence base against which to validate the behaviour of the model augers for caution in interpreting the results, and a necessary reminder that in this instance the model is primarily a tool for formalisation of the thought process \citep{epstein2008}, rather than a machine for predicting.

A game theoretic approach to generating an abstract form of the problem gives a convenient, and well known framework to reason about the processes involved in the scenario. While scenarios may map to a number of games, exploring one candidate game still allows for a principled comparison between interpretations, and enforces explicit assumptions. But equilibrium is the sine qua non of game theory, which is concerned with the stable outcome of an infinite contest of second guesses.
We wish to see the system in motion rather than just at rest, even if it does eventually settle to some stable point. Instead, we choose to focus instead on the behavioural processes driving a system in motion, a system out of equilibrium, to understand how these processes interact with the movement.
Introducing decision theory takes a step down the ladder of abstraction from the mental chess of game theory. Dealing instead in the mechanics of decision making, and the calculus of choice, allows us to explore not only paths that arrive at the destinations we might consider in game theory, but also avenues not accessible where we constrain ourselves to a sometimes implausible degree of rationality.

This does not preclude a strategic dimension, since decision rules are to a great extent modular, and as demonstrated in this paper can be exchanged without altering the decision problem. In addition, rules are agnostic as to the source of information, suggesting room for multi-stage processes - for example, a more game theoretic, model of the opponent's mind, type approach could act as an information source for a decision rule.  As a corollary, the decision problem agents attempt to answer can change, allowing behaviour in novel problems to be informed by beliefs derived under other conditions. This is also indicative of the broader benefits to \ac{ABM} as an approach. Embedding these abstract rules in a simulated environment allows for mechanics which cannot be readily explored using purely analytic, or predictive approaches, for example, the social learning dynamic of the disclosure game model.

While there is no universal theory of human behaviour to sit at the centre of \ac{ABM} as a method, a key motivation for decision rules is their claim to provide an account of decision making that is behaviourally and cognitively plausible. Their mooted capability in this regard is to some extent supported by work from neuroeconomics, which aims to empirically test theories of decision making \citep{Rustichini2009}. Many key aspects common to decision rules, for example the idea that a common currency is used by the brain to compare outcomes \citep{Padoa-Schioppa2006,Padoa-Schioppa2008}, are supported by neurological findings. In addition, a single decision rule represents a parsimonious alternative to numerous case specific production rules.

Given these features, the application of decision, and game theory to \ac{ABM} is an attractive approach to computational social science, where the locus of interest is process, and decision making. Taking a balance between models focused on replication of low level neurological mechanics, and those with a higher level emphasis where individual behaviours are abstracted away, yields a computationally tractable approach. Despite the relative simplicity, it nonetheless captures some of the nuance and sophistication of human decisions.

The remainder of this paper proceeds to outline the proposed approach to model development (section \ref{sec:model}), and experiments (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}). 
\section{Disclosure Game Model}
\label{sec:model}

In this section we sketch\footnote{A complete example of this for the alcohol misuse in pregnancy model is given in appendix \ref{app:model_description}, with a schedule of simulation provided in appendix \ref{app:sim_schedule}} the process of moving from a real world scenario to a minimal game which sufficiently captures reality, expressing the result as a decision problem representation, and translating this to a simulation model. We then outline four possible decision rules, and as an example of additional flexibility of process models and simulation in contrast to purely predictive or analytical approaches, extend the model to allow a simple form of social learning.

\subsection{Modelling Approach}
\label{sec:model_design}

To model a scenario, we take the approach of first creating a formal game to represent it, capturing the key features as far as possible in the structure of that game. This game is in essence a conjecture about the real data generating process, which can be played out in simulation.

The appropriate game representative of the scenario of interest, which captures the desired strategic dynamics may not be immediately obvious. We suggest that an iterative process is beneficial, beginning from the simplest possible game, and progressively augmenting it.

Transitioning from the resulting game, to a set of decision problems is a relatively simple task. We treat the $n$ player game as $n$ one-player games \citep{RiosInsua2009}, where the moves of other players are drawn from a probability distribution - nature, in game theoretic parlance. As with the game, the decision problem representation admits a degree of variation, and may need to be adjusted to reflect the decision rules that will be used.

These decision problems may then form the basis of an agent model, where agents use learning, and decision rules to play out the game. Simulation can then support features which are not readily representable within an analytic framework, for example, populations of heterogeneous players, individual and social learning, or network effects. In addition, the ability to observe the system in a state of flux rather than at equilibrium is desirable, since even where a social system reaches a stable state, the process by which we arrive at it is significant.

\subsection{Scenario}
\label{sec:scenario}

Typically in the UK, women have 12 appointments with a midwife during the antenatal period, and in the majority of cases will encounter several different midwives \citep{Redshaw2014} in the course of their care. In the UK, and unlike most healthcare contexts, maternity notes are held by the patient, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously. Maternity notes are not generally linked to extra-departmental records, meaning that a history of alcohol related admissions to another service may remain unknown unless revealed by the woman.

According to NICE guidance \citep{NICE2010a,NICE2010} the issue of substance misuse should be raised at the initial booking appointment, followed by subsequent action if a concern is raised is at the discretion of the midwife. This may take the form of specific guidance to reduce intake, or if deemed necessary a referral to a specialist midwife and relevant interdisciplinary team. On alcohol consumption, policy regarding how to determine the level of consumption is at the time of writing generally at the level of local health authority, hospital trust, or according to the best judgement of the individual midwife, with no guidance provided by NICE. This commonly takes the form of average units per week, but may include \ac{T-ACE}\footnote{The \ac{T-ACE} is a four question screening test for alcohol misuse intended specifically for use with pregnant women.} \citep{Sokol1989863} and similar measures.

Beyond the \enquote{booking} appointment, the onus is on women to raise concerns about their drinking behaviour, or the midwife to probe further if they feel it is warranted. In either case, once a concern has been raised the midwife must respond clinically, and inevitably personally, to the information.

In an ideal world, all interactions with healthcare providers would be immediately and fully disclosive, with no repercussions for the patient. However, alcohol misuse by women is known to attract stigma \citep{Gomberg1988}, and is a recognised barrier to appropriate treatment in the maternity context \citep{NICE2010,Radcliffe2011}.

\subsection{Disclosure Game}
\label{sub:the_game}

In order to translate the scenario sketched above into a more abstract, tractable form, we cast it as a signalling game, and assume that women's disclosures (or not), are signals. We also impose a discretisation on the continuum of alcohol use, and use three types of behaviour - light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy. Correspondingly, they are limited in what signals they may send when claiming to be one of these three types.

Midwives are treated in a similar fashion, where their type corresponds to how negatively they regard a drinking pattern - non-judgemental, moderately judgemental, and harshly judgemental. The expression of this judgement is not a matter of choice on their part, and is assumed to have no impact on their clinical response, which is to either refer the woman for specialist treatment, or do nothing.

At the end of a game, each player receives a payoff dependent on the actions and types of both players. Because both women and midwives have an interest in the outcome of the pregnancy, and would prefer a healthy baby, the payoff has a common interest component. Hence, both players receive a payoff based on the outcome of pregnancy, but women bear a social cost dependent on the signal they sent and the midwife's reaction to it. Similarly, midwives pay a cost if they refer to a specialist, mirroring the organisational cost of non-routine care. Table \ref{tab:Payoff-matrix} shows the three payoff matrices which together describe the game.

\begin{table}
\caption{Payoff matrices}
\label{tab:Payoff-matrix}
\subfloat[Social cost, \(X_{s}\), for women, given their signal, and the midwife's type\label{tab:Social-cost-matrix}]{\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

\hline
\multirow{4}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Harsh & -2 & -1 & 0\tabularnewline
\cline{2-5} 
 & Moderate & -1 & 0 & 0\tabularnewline
\cline{2-5} 
 & Non & 0 & 0 & 0\tabularnewline
\hline 
\end{tabular}

}\qquad
\subfloat[Health outcome, \(X_{h}\), for women and midwives, given the midwife's action, and woman's type\label{tab:Referral-payoff-matrix}]{\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

\hline 
\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Refer & 10 & 10 & 10\tabularnewline
\cline{2-5} 
 & Don't refer & -2 & -1 & 10\tabularnewline
\hline 
\end{tabular}

}

\subfloat[Referral cost, \(X_{c}\), for midwife, given their action and the woman's type\label{tab:inst_cost_matrix}]{\begin{tabular}{|c|c|c|c|c|}
\cline{3-5}  
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
\hline 
\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Refer & -9 & -9 & -9 \tabularnewline
\cline{2-5} 
 & Don't refer & 0 & 0 & 0\tabularnewline
\hline 
\end{tabular}

}
\end{table}

As an example, consider the challenge faced by an agent of the heavy drinking type. In order to get the best health outcome, they must be referred and would ideally achieve this without paying any social cost at all. The best move depends on the type, and beliefs of the midwife. For example, a particularly unlucky scenario might be for the midwife to not only be of a harshly judgemental disposition, but to believe that no women really need to be referred (i.e. that all women are light drinkers). Even a relatively weak belief in this possibility can make the honest signal look like an unwarranted risk.

To formally define the game, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\). Here, \(\{l, m, h\}\) correspond to light, moderate, and heavy alcohol consumption for women, and non-judgemental, moderately judgemental, and harshly judgemental for midwives. Midwives' pure strategies \(\{r,n\}\) are to refer, or do nothing, and those for women are to signal that they have one of the possible drinking patterns.
Additionally define two utility functions - 
\begin{equation}
u_{w}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}}
\end{equation} 
\begin{equation}
u_{m}(s_{w}, s_{m}, \theta_{w})=X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}},
\end{equation} with $X_{c}$, $X_{h}$, and $X_{s}$ being the payoff matrices as in table \ref{tab:Payoff-matrix}, $s_{w}$ and $s_{m}$ denoting a specific signal by a woman, and referral response by a midwife. Lastly let \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\) be distributions over types of women, and midwives respectively.

As noted, rather than solve the game, we allow populations of agents to play it, and hence stipulate further that women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)). They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred, and a new player is drawn from the same distribution that produced the original players to replace them. If they are not referred, they rejoin the back of the queue after their appointment. In either case, they are informed of their payoff after each round and update their beliefs accordingly using one of the rules described in section \ref{sub:the_agents}.

Midwives play for \(r_{m}\) rounds (\(r_{m}=1000\) in all experiments), and conduct appointments in parallel, i.e. if there are 5 midwives, then five women are drawn from the queue and assigned at random to the midwives. 
Unlike women, midwives are only informed of their payoff if they choose to make a referral. Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.

\subsection{Social Learning}
\label{sub:info_sharing}

In reality, learning is not exclusively from personal experience, and social learning plays an important role. This social dynamic fits naturally into an agent framework, but is difficult to address without using an approach concerned with process, so we take advantage of this to show a na{\"\i}ve take on it here.

In the disclosure game model, this takes the form of having each agent recount their play history to their colleagues with some probability \(q\). Individuals then incorporate shared information into their beliefs using weighted updates, e.g. for a midwife a shared observation of a low type signal contributes to their beliefs by \(w\), and \(0\leq w\leq 1\) (i.e. \(n_{j} = n_{j} + w\)).
Women share only when they have finished play, and provide their complete history of games, because they have accurate information about the outcomes. By the same rationale, midwives share only their history with the most recent woman they referred. Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{More precisely, memories of games remain, but it is assumed that only the most current information is relevant enough to be shared.} Accounts are shared with some probability, to all fellow players. For example, a heavy drinker finishes play having claimed to be a light drinker, without ever being referred, and their account is selected to be shared with some probability $q_{w}$.

Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this exogenous information differently. The simple payoff based rule relies on a belief structure relating actions directly to rewards which is essentially model free. Because payoffs differ by the agent's private type, the information shared may not correspond to the experience of the listening agent in the same scenario. As a result, payoff reasoners have a belief bias towards the most common player type, and can believe in outcomes that are, for them, impossible.

A payoff based agent, who is a light drinker, hears the account of the heavy drinker. They take the account as literally happening to them, and update their beliefs to include the possibility that there is a negative outcome attached to claiming to be a light drinker.

By contrast, representing the problem in terms of the probabilities of the individual lotteries imposes a model that abstracts the new information from payoffs, and allows the agent to discard implausible outcomes. This stronger assumption as to the static and known qualities of payoffs does however reduce the flexibility of the decision rule.

Returning to our example, a light drinker using this decision rule would follow the account through from their position in the game tree, correctly inferring that the outcome in their case would be positive. \subsection{Agent Models}
\label{sub:the_agents}

While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same output - a decision, we limit ourselves here to four. The simplest is a lexicographic rule (1), in the spirit of a \acl{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}. Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-output characteristics.

Agents have perfect recall, midwives recognise women if they repeatedly encounter them, making use of new information for retrospective updates. However, all four agent models make decisions `as-if' they were always facing a new \enquote{opponent}.

A simplifying assumption is made that all midwives have just qualified after receiving identical training. As a result, they have homogeneous beliefs about  women and assume to some extent that they are honest.
Women have heterogeneous beliefs, which correspond to experiencing \(k\) randomly chosen paths through the game, and following each path at least once.

\subsubsection{Lexicographic Heuristic}
\label{sub:lexico}

The lexicographic heuristic (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified problem representation, where an action is a choice between combined lotteries. Functionally, the heuristic maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e. one reason decision making. Where there is no clear best action, but one or more is evidently worse, a choice must be made as to whether to discard the poorer action; in this case we have elected to retain it.
This approach requires minimal computation, and does not assume that \(u_{i}\) is static, or known.

Women resolve this by approximating the utility function, as a function \(f(s_{w}, \sigma)\) on their choice of signal and an unknown distribution $\sigma$, which maps to \(u_{w}\) - i.e. \(s_{w}\) is a choice between simple lotteries. The algorithm maintains a count, \(n\), of the number of occurrences of each outcome given the choice from \(s_{w}\).

Midwives solve a slightly different problem with more information, where \(s_{w}\) is known, and \(s_{m}\) is the lottery choice - \(f(s_{w}, s_{m},\sigma)\). This is resolved by maintaining a separate count for each signal (i.e. \(n_{s_{w},s_{m}}\)), and otherwise following the same algorithm (\ref{alg:lexico}).

\begin{algorithm}
\begin{algorithmic}
\State $n \gets 1, action \gets none$
\While{$action = none$}
\State Calculate the $n$th most common outcome following each action.
\State Sort actions by the value of the $n$th most common outcome.
\If{clear winner} \State $action \gets best$ \EndIf
\State $n \gets n + 1$
\EndWhile
\State \Return action
\end{algorithmic}
\caption{Lexicographic heuristic\label{alg:lexico}}
\end{algorithm}

\subsubsection{Bayesian Payoff}

The Bayesian payoff agent uses the same subset of information as the lexicographic method, but updates beliefs on the link between actions and payoffs using the Bayes rule, and attempts to choose the action which minimises risk.

Given the discrete nature of actions and payoffs, coupled with a desire for tractability of the
simulation, the Dirichlet distribution is employed as a prior to represent these beliefs. 
The distribution is particularly convenient, in that to infer the
probability of a signal implying a payoff is
simply -

\begin{equation}
p(x=j|D,\alpha)=\frac{\alpha_{j}+n_{j}}{\sum_{j}(\alpha_{j}+n_{j})}\label{eq:posterior}
\end{equation}

Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), and \(\alpha_{i}\) is the pseudo-count of prior observations\footnote{Psuedo-counts are related to, but distinct from prior beliefs. Here, the psuedo-count is a parameter to the prior belief distribution and is nothing more than a hypothetical count of prior observations.} for a pair \(i\). Hence,
the belief that a signal will lead to a payoff is the number
of times that pairing has been observed (including the pseudo-count),
over the total number of observations thus far. This makes computation
of beliefs fast and simple, since all that must be maintained is
a count of observations.
As before, midwives follow a similar pattern but maintain \(n_{s_{w}}\) independent counts of pairings between referral choice and payoff, updating their beliefs about the relationship between the choice to refer and payoff given the signal they have received.

Agents then choose the strategy $s_{i}$ to minimise risk $R_{i}$, which is simply defined as - 
\begin{equation}
R_{w}(s_{w}) = \sum_{x \in X} -xp(x | s_{w})
\end{equation}
\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{x \in X} -xp(x | s_{w}\wedge s_{m}),
\end{equation}

where $X$ is the set of payoffs the agent has observed to follow $s_{i}$.

\subsubsection{Bayesian Risk Minimisation}

The second Bayesian agent augments the reasoning of the simple payoff model, making the stronger assumption that the utility function is static, and known. Women maintain two sets of beliefs, corresponding respectively to \(p_{m}\), and the probability of referral given signal choice. This leads to the risk function, minimised with respect to \(s_{w}\) -

\begin{equation}
R_{w}(s_{w}, \theta_{w}) = \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, \theta_{w}, j)p(j)p(i | s_{w}),
\end{equation}

so that the risk of a signal is the sum of the products of all payoffs with the probabilities of their entailed midwife types and responses.

Midwives reasoning centres on determining the meaning of signals, since given the knowledge of what some signal \(s_{w}\) conveys about the true type of the sender, the payoff for an action is known. As such, their inference process is the same as for the simple Bayesian agent but over signal-type pairs, and they attempt to minimise the following risk function, minimised with respect to \(s_{m}\) -

\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{m}(s_{w}, s_{m}, i)p(i | s_{w})
\end{equation}

\subsubsection{Descriptive Decision Theory}

The most complex decision rule used is \ac{CPT}, which attempts to reproduce a number of systematic deviations from rationality observed in humans. Rather than risk, `prospects', the sequence of payoff-probability pairings in ascending order of payoff, associated with an action  are used as decision criteria. While \ac{CPT} has primarily been applied in the context of decisions from description, it has been modified to deal with decisions from experience by incorporating a first stage where probabilities are estimates from observations \cite{FoxCPT}. In this instance the Bayesian inference process fills the first stage role.

\ac{CPT} uses transformed probabilities, underweighting small probabilities, and overweighting large ones. This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and contrastingly low probabilities as impossible. The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains (eqn \ref{eqn:cpt_p_pos}) and losses (eqn \ref{eqn:cpt_p_neg}) -

\begin{align}
w^{+}(p) & = \frac{p^{\gamma}}{(p^{\gamma}+(1-p)^{\gamma})^{\frac{1}{\gamma}}}\label{eqn:cpt_p_pos}\\
w^{-}(p) & = \frac{p^{\delta}}{(p^{\delta}+(1-p)^{\delta})^{\frac{1}{\delta}}}\label{eqn:cpt_p_neg},
\end{align}

where $p$ is the unweighted probability, and $\gamma$ and $\delta$
are the weights for gain and loss probabilities respectively. Along similar lines, the values of losses and gains are transformed to reflect a tendency to regard a loss as more significant than a gain  -

\begin{equation}
v(u_{i})=\begin{cases}
f(u_{i}),& \text{if}\, u_{i}>0\\
0,& \text{if}\, u_{i}=0\\
\lambda g(u_{i}),& \text{if}\, u_{i}<0
\end{cases},
\end{equation}

where,

\begin{equation}
f(u_{i})=\begin{cases}
u_{i}^{\alpha},& \text{if}\,\alpha>0\\
\ln(u_{i}),& \text{if}\,\alpha=0\\
1-(1+u_{i})^{\alpha},& \text{if}\,\alpha<0
\end{cases}
\end{equation}
\begin{equation}
g(u_{i})=\begin{cases}
-(-u_{i})^{\beta},& \text{if}\,\beta>0\\
-\ln(-u_{i}),& \text{if}\,\beta=0\\
(1-u_{i})^{\beta}-1,& \text{if}\,\beta<0
\end{cases},
\end{equation}

and $\alpha$, and $\beta$ are respectively the power of a gain,
and a loss, and \(\lambda\) is a multiplier giving the aversion to loss.

Finally, the transformed probabilities are used to construct decision weights, \(\pi^{+},\pi^{-}\) for losses and gains, where,

\begin{equation}
\pi_{n}^{+}=w^{+}(p_{n})
\end{equation}
\begin{equation}
\pi_{-m}^{-}=w^{-}(p_{-m})
\end{equation}
\begin{equation}
\pi_{i}^{+}=w^{+}(p_{i}+\ldots+p_{n}) - w^{+}(p_{i+1}+\ldots+p_{n}),0\leq i \leq n - 1
\end{equation}
\begin{equation}
\pi_{i}^{-}=w^{-}(p_{-m}+\ldots+p_{i}) - w^{-}(p_{-m}+\ldots+p_{i-1}),1-m\leq i \leq 0
\end{equation}

The \ac{CPT} value of a single outcome prospect \(f=(u_{i};p_{i})\), is $v(u_{i})\pi^{+}(p_{i})$
if $u_{i}\geq0$, and $v(u_{i})\pi^{-}(p_{i})$ otherwise. For any given action the \ac{CPT}
value, \(V\) is the sum of the value of the prospects of that action, as
in the Bayesian risk model, and the agent chooses the option which maximises this quantity. 
\section{Method}
\label{sec:method}

This section provides details of experiments conducted to examine the ability of the model to reproduce qualitative trends reported in the midwifery literature by \citet{Alvik2006}, and \citet{Phillips2007}; as well as a global sensitivity analysis and construction of statistical emulators to explore, and contrast the response surfaces of the four decision rules.

\subsection{Qualitative Trends}
\label{sub:qt}

Throughout this paper, parameters for the \ac{CPT} model were as used in \cite{Tversky1992} (table \ref{tab:qt_params}). While there has been significant work on determining appropriate parametrisation for the model (e.g. \cite{Neilson2002,Nilsson2011,Glockner2012}, and particularly \citet{Byrnes1999} and \citet{Booij2009} addressing risk aversion and gender), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work. For simplicity, it was assumed that all three drinking types are equally prevalent within the population, although results derived from \acl{ALSPAC} suggest that the reality is far more positive\footnote{95.5\% of women in the sample reported consumption at, or below, \ac{NICE} recommended safe levels.} \citep{Humphriss2013}. The scenario was biased towards disclosure as the better option by presuming a distribution of midwives strongly skewed towards non-judgemental types, with beliefs initially favouring honesty. Payoffs were as in table \ref{tab:Payoff-matrix}, which ensure that it is always strictly preferable to refer drinkers, and together with the initial belief that signals will be honest, not refer those claiming otherwise.

Two key measures were used: the fraction of the subpopulation who had ever signalled honestly, and the proportion of the population who were referred. Both measures were taken after every round of play, and were taken relative to the agent's position in their sequence of appointments giving the probability of signalling honestly, or being referred having had a given number of appointments.

\begin{table}[h!]
\caption{Model parameters.} 
\label{tab:qt_params}
\begin{tabular} {lll}
\hline\noalign{\smallskip}
Name & Description & Value \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(n_{w}\) & Number of women & 1000 \\ 
\(n_{m}\) & Number of midwives & 100 \\ 
\(r_{m}\) & Number of appointments per midwife & 1000 \\ 
\(r_{w}\) & Maximum number of appointments per woman & 12 \\ 
Runs & Simulation runs & 1000 \\ 
\(p_{w}(h)\) & Proportion of heavy drinkers & \(1/3\) \\ 
\(p_{w}(m)\) & Proportion of moderate drinkers & \(1/3\) \\ 
\(p_{w}(l)\) & Proportion of light drinkers & \(1/3\) \\ 
\(p_{m}(h)\) & Proportion of harsh midwives & \(5/100\) \\ 
\(p_{m}(m)\) & Proportion of moderate midwives & \(10/100\) \\ 
\(p_{m}(l)\) & Proportion of non-judgemental midwives & \(85/100\) \\ 
\(q_{w}\) & Probability of women sharing & 0. \\ 
\(w_{w}\) & Weight of shared information for women & 0. \\ 
\(q_{m}\) & Probability of midwives sharing & 0. \\ 
\(w_{m}\) & Weight of shared information for midwives & 0. \\ 
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 10:1 \\ 
\(\gamma\) & Probability weighting for gains  & 0.61 \\ 
\(\delta\) & Probability weighting for losses &  0.69\\ 
\(\alpha\) & Power for gains  & 0.88 \\ 
\(\beta\) & Power for losses & 0.88 \\ 
\(\lambda\) & Loss aversion &  2.25 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examined the impact of simple social learning within the population of women (section \ref{sub:info_sharing}) on the robustness of these trends. The original experiment was repeated at \(q_{w},w_{w}\in \{0.25, 0.5, 0.75, 1 | q_{w}=w_{w}\}\), with 100 runs under each condition.

\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}

In general, we have followed the example of \cite{Bijak2013b} for global sensitivity analysis of stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques. For this purpose the \ac{GEM-SA} software \citep{Kennedy} was used, which implements the \ac{BACCO} method developed by \citeauthor{Oakley2004} \citep{Oakley2002,Oakley2004,Dorresteijn2010}. This is a form of variance-based sensitivity analysis, which assumes that the model output is an unknown, smooth function of the inputs. The unknown function can then be approximated as a Gaussian Process, which is fitted to the training data using Bayes' Theorem and then serves as an emulator for the simulator. The emulator is then able to provide an indication about the extent to which uncertainty in a parameter propagates to uncertainty in the output, and how sharply the output responds to change in each parameter.

\begin{comment}

Justification for doing SA, point out the wide variety of places this gets used. Talk about uncertainty, briefly raise model discrepancy.

\end{comment}

Parameters for training were generated in R \citep{RTeam2014} using and appropriately transformed Latin Hypercube Sample \citep{Carnell2012} over the space of parameters given in table \ref{tab:sa_params}, giving eleven free parameters which were treated as uniformly distributed in the range given.  Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each, with emulator quality assessed by leave-one-out cross validation. A fixed set of 100 random seeds was used\footnote{Fixed random seeds were used to allow simulation results to be reproducible, since the combination of a parameter set and a random seed yields a deterministic process.}, such that each parameter set was run once with each seed, for every decision rule.

\begin{table}
\caption{Parameter ranges.}
\label{tab:sa_params}
\begin{tabular} {llll}
\hline\noalign{\smallskip}
Name & Description & Min & Max \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{w}(m)\) & Proportion of moderate drinkers & 0 & 1 \\ 
\(p_{w}(l)\) & Proportion of light drinkers & 0 & 1 \\ 
\(p_{m}(m)\) & Proportion of moderate midwives & 0 & 1 \\ 
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 0 & 1 \\ 
\(q_{w}\) & Probability of women sharing & 0 & 1 \\ 
\(w_{w}\) & Weight of shared information for women & 0 & 1 \\ 
\(q_{m}\) & Probability of midwives sharing & 0 & 1 \\ 
\(w_{m}\) & Weight of shared information for midwives & 0 & 1 \\ 
\(x_{h}\) & Health payoff for healthy delivery & 1 & 100 \\ 
\(x_{r}\) & Cost for referral & \multicolumn{2}{l}{\(-(x_{h} - 1)\)} \\ 
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 1:1 & 100:1 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

To capture the response characteristics for the model, we measured four outcome variables - (1) the \ac{IQR} of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3, 4) the \ac{IQR} of 1 \& 2 between simulation runs. Together these four metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the variability of the system in response to changes to the parameters (3 \& 4).

Measurements were taken at the end of 1000 rounds of play, and emulators were built against 400 sample points from the full set of simulation results (1 \& 2), and \ac{IQR} at each point (3 \& 4) to assess both the overall trend, and the extent to which the parameters contribute to variance between runs.

Sixteen emulators were built, covering each of the four outputs on all decision models and used to conduct a probabilistic sensitivity analysis to assess the impact of parameters and interactions.

In addition to the sensitivity analysis, we also employed the resulting emulators to rapidly\footnote{Once constructed, the emulator has an analytical solution conditional on the roughness parameters, which obviates the need to use MCMC.} explore the parameter space. While emulated results are subject to inaccuracy, they do provide an indication of the interest, and plausibility, of regions of the parameter space. Results for the outcomes of the interactions of \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) with \(x_{h}\), and \(q_{w}\) with \(w_{w}\) are given in section \ref{sub:sa_results}. 
\section{Results}
\label{sec:results}

\subsection{Qualitative Trends}
\label{sub:qt_results}

As shown in figure \ref{fig:honest_signals}, all four decision rules were able to reproduce both qualitative trends towards more disclosure as women experience more appointments \citep{Phillips2007}, and a greater tendency towards underreporting of consumption by heavier drinkers \citep{Alvik2006}.  
Trends for all four rules are broadly similar, exhibiting a gradual increase across appointments which subsequently levels off. This levelling can in part be explained by the referral results (see figure \ref{fig:ref_plot} in appendix \ref{app:additional_figures}), which show that the majority of drinkers are referred, even with substantial concealment. Referrals continue to occur, in the absence of honest signals, because drinkers are able to achieve a referral by masquerading as higher or lower types, dependent on how their initial beliefs are biased. Despite this the results suggest that a minority of risky drinkers will evade detection altogether, with no notable distinction between heavy and moderate types. Under these parameters, light drinkers always signal honestly and are never referred since there is no perceived advantage in doing so, and the evidence of deceptive signalling is insufficient to outweigh the biased priors of the midwives.

\begin{figure}[H]
\includegraphics[width=100mm]{figures/honesty_plot}
\caption{Average fraction of population ever signalled honestly by each appointment, after 1000 rounds, mean with 95\% confidence limit over 1000 runs. Note that the large number of runs leads to very tight confidence intervals.\label{fig:honest_signals}}
\end{figure}

\subsection{Social Learning}
\label{sub:sharing_results}

Introducing social learning amongst women leads the behaviour of the decision rules to diverge markedly, which we explore possible reasons for in section \ref{sec:discussion}. Figure \ref{fig:honest_sharing} shows the proportion of women who have signalled honestly at least once by their final appointment, under four sharing conditions.

\begin{figure}[H]
\includegraphics[width=100mm]{figures/honesty_sharing}
\caption{Impact of social learning on trends in the average fraction of population ever signalled honestly by their final appointment, after 1000 rounds, mean with 95\% confidence interval over 100 runs}
\label{fig:honest_sharing}
\end{figure}

Aside from the lexicographic decision rule, the general tendency is towards less honest signalling by heavy drinkers, which is accompanied by a slight increase in referrals for the Bayesian, and \ac{CPT} rules. For these decision models, this is because social learning exacerbates the existing tendency of heavy drinkers to impersonate moderate drinkers, who behave more honestly as heavy drinkers become less so. This arises because both classes of agent learn that the moderate signal is the lower risk option as it is both a reliable indicator of need, and does not attract strongly negative judgement. The reliability of the signal is self reinforcing, since the more the agents use it and get referred, the more confident midwives become that it indicates need.

Particularly notable, is the decline in honest signalling by light drinkers visible in both heuristic type rules at the 0.25 level of \(q_{w}\) \& \(w_{w}\), which is associated with an increase in false positives. This arises because of the lack of homophily in social learning, as light drinkers become informed about negative outcomes associated with concealment, despite having nothing to conceal. The relatively high referral rates of drinkers heighten the effect further, because shared information becomes dominated by their experiences.

The relationship is not, however, entirely straightforward, in that increasing social learning leads to greater variance between runs. A linear model was used to predict the between-runs interquartile range of the average signal sent by moderate drinkers. The predictors used were decision rule, and level of social learning, together with the interaction between the two. The regression results were significant (\(F_{7,12}=25,p<2.9\times10^{-6}\)) with \(R^2=94\%\), and intercept 0.07. The only significant coefficients were for the interaction terms, which were 0.44 (\(p<0.05\)) for the Bayesian payoff rule, and 0.69 (\(p<0.005\)) for the lexicographic. This suggests that social learning, for the heuristic style decision rules introduces considerable uncertainty to the model, which is explored further in the sensitivity analysis below.

\subsection{Sensitivity Analysis}
\label{sub:sa_results}

In this section we present a brief overview of the sensitivity analysis, followed by selected results highlighting the global effect of changes to perceived payoffs and degree of bias towards honesty, as well as social learning within women. The full results for the sensitivity analysis covering all sixteen emulators are available in appendix \ref{app:sensitivity_results}.

\begin{figure}[H]
\includegraphics[width=90mm]{figures/sharing_emulated_simulated}
\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules, with signals coded as 0 = light, 1 = moderate, and 2 = heavy.}
\label{fig:outcome_plots}
\end{figure}

For the median signal choice of moderate drinkers, the results of the sensitivity analysis suggest that the proportion of light drinkers has a significant effect for all decision rules, accounting for 10\%, 38\%, 24\%, and 5\% of the variance in output for the Lexicographic, Bayesian Payoff, Bayesian, and \ac{CPT} rules respectively. For the Lexicographic rule, the overwhelming majority of variance in signalling behaviour is reflective of the prevalence of stigmatisation by midwives (44\% \(p_{m}(m)\), 7\% \(p_{l}(m)\), and a further 15\% for their interaction).  The proportions of midwives are also key drivers in group separation, and the between run IQR of both measures for this rule.

Perhaps surprisingly, variance attributable to social learning between midwives is relatively low, with neither the weight nor probability accounting for more than 5\% of variance in any measure. While there are small contributions to variance in interaction with other parameters (e.g. 4\% to between groups IQR, for the interaction with the proportion of light drinkers under the Bayesian rule), this may suggest that the model is lacking in this area, which we touch on in section \ref{sec:conclusion}.

Figure \ref{fig:outcome_plots} gives a qualitative picture of both emulator quality, and the divergent response surfaces of the decision rules in response to variations in social learning parameters. Emulator fit is clearly imperfect, but overall behaviour is qualitatively similar, with both emulated and simulated plots demonstrating separation in outcome space for the decision rules.

\begin{figure}[H]
\includegraphics[width=100mm]{figures/unfixed_emu_sig_iqr}
\caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\)}
\label{fig:emulated_sharing_iqr}
\end{figure}

Following from the suggestive results for social learning introducing uncertainty (section \ref{sub:sharing_results}), figure \ref{fig:emulated_sharing_iqr} shows emulated points covering the parameter space in high resolution. These plots reflect the increase in uncertainty of outcome shown for the heuristic type rules, which is especially severe for the Bayesian payoff rule. They also suggest that the Bayesian decision rule is less stable under conditions where the weight of shared information is substantially higher than the probability of sharing. This indicates that placing a high weight on information from limited sources leads to greater variability, i.e. what information is shared, matters.

\begin{figure}[H]
\includegraphics[width=100mm]{figures/unfixed_emu_payoff_honesty_group_iqr}
\caption{Emulated between groups IQR in response to varying \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\), and \(x_{h}\)}
\label{fig:emulated_payoff_group_iqr}
\end{figure}

For the \ac{CPT}, and Bayesian decision models, the interaction of bias towards honesty, and distinction between payoffs has a significant, and non-linear effect on instability, and separability of groups. Figure \ref{fig:emulated_payoff_group_iqr} shows the effects, and also highlights the tendency towards poor separability of groups for both the heuristic type decision rules. The response surface of the Bayesian payoff rule is slightly more nuanced than the simple Lexicographic rule. Figure \ref{fig:emulated_payoff_group_iqr} shows better separation, close to partial pooling\footnote{Pooling occurs when signallers of different types `pool' their signals, and one adopts the signals of another.} at high payoff distinction, with relatively modest honesty bias, which is reflected by the variance contributions of 11\% and 8\% respectively.  For the more complex rules, the general tendency is towards less pooling for higher values of both, but with pockets where full pooling\footnote{Indicating that all signaller types are using a the same signal.} occurs.  The plots also suggest that the sensitivity of the \ac{CPT} rule is marginally greater, which is supported by the significant contribution to variance of close to 15\% for all measures of \(x_{h}\).

\section{Discussion}
\label{sec:discussion}

From a pragmatic perspective, the differing response characteristics of the classes decision rules are substantial and significant, particularly when social learning is considered. There is a high level of uncertainty in the overall dynamics with the model free rules. This does not arise with the more complex rules, because they reframe information from others in the context of their own experiences, as what would happen to them in that situation. By contrast, the simpler rules treat the experiences as having literally happened to them, and since there is no mechanism of homophily, no way to listen only to accounts of agents similar to themselves, they can come to believe unreasonable things. Naturally, incorporating homophily, by, for example weighting shared information by the type of the sharer, would represent a trivial modification to the heuristic models. While to some extent this highlights the flexibility of the decision rule approach, it would of course sacrifice the parsimony of the model. This is an important consideration, given that part of the argument in favour of a decision theoretic approach lies in the minimal nature of the behavioural rules.

One of the notable features of the results is that the behaviour of rules within a class is very similar. To some extent this reflects poorly on the most complex rule, \ac{CPT}, which diverges only minimally in behaviour from the Bayesian model. This might be to a degree anticipated since we have not elicited payoffs for obvious practical and ethical reasons, and they may be unrealistic, which limits the utility of the \ac{CPT} approach.  Additionally, work by \citet{Glockner2012} has shown that there is considerable variation in individual parameters for the decision model, whereas we have let them remain homogeneous here. In the same vein, utility functions should arguably vary between individual agents, which could potentially be addressed by replacing the fixed payoffs used here with a distribution.  With this said, the significant increase in complexity, which entails both additional parameters and increases to simulation time may auger for a middle ground, particularly where elicitation of payoffs is impractical.  This, together with the variability associated with the heuristic type decision rules speaks to a trade off between capturing reality, and replicating it.

Continuing the discussion of the issues raised by the representation of payoffs, the temporal aspect is significant, in that there is a timing difference in payoffs, since while the potential social pain of disclosure is immediate, the health outcome comes only later. In light of this, that there is a known impact of time on perceived utility \citet{Thaler1981} suggests that incorporating some form of temporal discounting (e.g. exponential \citep{Samuelson1937}, or hyperbolic \citep{Ainslie1991}), or a decision model which explicitly treats intertemporal choice, such as the \ac{CPT}-like model of \citet{Loewenstein1992}, is warranted.

As noted in section \ref{sub:sensitivity}, the impact of social learning in midwives is surprisingly minimal, where it might be expected to play a more significant role in reality. A possible explanation for this lies in the implementation, which may place an excessive constraint on how much information midwives can share. The restriction to sharing only after a referral, together with the disparity in population sizes, and random allocation of appointments leads to midwives rarely having more than a single interaction with woman to pass on to their colleagues. Furthermore, because midwives are only informed of the true type if a referral occurs, they have an inherent myopia since until they have evidence of deception they will not refer, with said evidence difficult to obtain without a referral.

In reality it might be anticipated that midwives would not withhold judgement, and would pass on concerns about specific women to their colleagues, or that particularly dramatic stories would persist and be passed. This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared and more sophisticated model of information flow in general. This also highlights an advantage of the \ac{BACCO} approach (which we describe in section \ref{sub:sensitivity}), in diagnosing issues with model design by giving insight into parameters which are contributing inappropriately to variance in output. Coupled with the ability of emulators to rapidly explore parameter space, this clearly suggests that statistical emulation is a powerful tool to support simulation based approaches.
As noted in section \ref{sub:sa_results} the emulators here are indicative, but not definitive. Amongst the reasons discrepancy arises here are heteroskedasticity associated with social learning, the stochastic nature of the simulation, and a lack of precision given the large parameter range. The former issues could be addressed by a more comprehensive approach to setting the nugget, which explicitly incorporates point variance.  The latter could be improved through iterative fitting procedures, where the simulation is sampled more heavily in plausible regions of parameter space, a procedure not possible here given the dearth of data to evaluate plausibility. That the discrepancy exists is not prohibitive in this instance, since we are not using the emulator for prediction, only to achieve a broad strokes picture of the behaviour of the simulator.

\section{Conclusion}
\label{sec:conclusion}

The conclusions that can be drawn about the behaviours of real life women, and their midwives, are necessarily limited by the paucity of data available to validate the model. While qualitative trends offer some indication, they are limited in scope, and do not permit strong claims about the drivers of disclosure.  As such, further work will focus on applying the model to domains where validation data is more available, which will support a more comprehensive evaluation of the model discrepancy. 
With this said, the trends reported by \citet{Alvik2006}, and \citet{Phillips2007} are borne out by the model, and predictions from the two more complex rules suggest that encouraging information sharing between women may encourage disclosure, but at the expense of reducing accuracy. By contrast, if one takes the view that a Lexicographic model is a better approximation of real behaviour, then outcomes can best be influenced by controlling how far midwives punish their women socially. We would however suggest that there are better reasons than the outputs of a simulation for doing so.

More broadly, the results demonstrate the logistical feasibility, and its utility as a `tool for thinking', of an agent model grounded in decision theory. The results also make clear that deciding the operationalisation of the decision making is of key significance.

 % Disclosure is a widely applicable issue in health and social care and beyond, with examples ranging from a lack of help seeking behaviour noted in older men \citep{Smith2007a}, to the inverse scenario of innapropriate disclosure in social media \citep{christofides2009information}.
 \section*{Acknowledgements}
\label{sec:acknowledgements}

This work was supported by the Engineering and Physical Sciences Research Council 
(EPSRC) grant EP/H021698/1 Care Life Cycle, funded within the Complexity 
Science in the Real World theme. The authors also gratefully acknowledge the use of the IRIDIS High Performance Computing Facility, and associated support services at the University of Southampton, in the completion of this work. 
\bibliography{library,library_addendum}
\bibliographystyle{spbasic}
\section{Disclosure Game Model Development}
\label{app:model_description}

This appendix provides a more in depth exploration of the model development process, beginning by deriving a game to serve as the basis for the model, and decision problems.

A game, in the game theoretic sense, can be any interaction where the result for one person is dependent on the actions of another. In this scenario, the result for the woman would seem dependent on whether the midwife chooses to refer her for specialist support (although naturally the reality can only be thought of in terms of risk mitigation), and conversely, the right choice for the midwife is somewhat contingent on what the woman is willing to tell them.

A very simple way to represent this would be a game with two players, who both have two possible moves - ask for help, or not; and refer, or not (fig \ref{fig:simplest_game}). Since both parties are invested in the outcome of the pregnancy, we might allow them to share the same payoff if everything ends well.

\begin{figure}[H]
\sidecaption
\includegraphics[width=7cm]{figures/simplest_game}
\caption{A very simple two player game. The only time things in this very restricted world obviously end poorly, is if the woman asks for help but does not get any. This implies that a rational player would always refer if asked for help, and is indifferent otherwise - in other words, there are three possible Nash equilibriums\protect\footnotemark.}
\label{fig:simplest_game}
\end{figure}

\footnotetext{A Nash equilibrium is a solution to a game between two or more players, where no player can gain from changing their move.}

The first complication, is that there should be differentiation between referring, and doing nothing because specialist treatment incurs a cost. We can modify the payoffs to reflect this, by reducing the midwife's payoffs when they refer. If the cost of referring is less than the value of a good outcome, then the effect of this is to make the only rational choice when not asked for help is to do nothing.

This simple game is however not very informative, and clearly neglects much of the nuance of the scenario. The wider difficulty here is that the real outcome depends on an attribute of one of the players, rather than their moves. In this case, we would expect the right choices to depend on the alcohol consumption of the woman, rather than entirely on what she has claimed about it.
To reflect this, we would need different variations on the same game to reflect this attribute.

To resolve this, we can do exactly that, and cast it as a signalling game (fig \ref{fig:less_simple}), with three types of player, corresponding to categories of drinking behaviour (light, moderate, and heavy). Each of these types of player, will play a different game. This also introduces a third player, who we will call nature. Nature takes the first move, and decides the type of the woman according to some probability distribution; in this case we will allow the probability of types to be uniform. 
This changes the dynamics of play substantially, since the midwife can no longer be certain of which game they are playing, and hence which move yields the best outcome. We must also amend the moves, and payoffs slightly. The woman now claims to be one of the types, and may send a signal to say, for example, that she a heavy drinker. We will also modify the common payoffs to allow light drinkers to get the best outcome no matter what, and moderate and heavy types to get the best outcome only if referred. We can also differentiate between the consequences of not getting help for these types by letting heavy drinkers have a very negative outcome, and moderate drinkers a slight one.

\begin{figure}[H]
\includegraphics[width=\textwidth]{figures/less_simplest_game}
\caption{A less simple two player signalling game. }

\label{fig:less_simple}
\end{figure}

At this point, the game becomes challenging to analyse from a Nash equilibrium perspective (there are several hundred). But, having raised to issue of stigma, we would also like incorporate this in the game. A possible approach to this is similar to the drinking behaviour of the women, and lets midwives have a type as well, corresponding to how judgemental they are when receiving signals: non-judgemental, moderately judgemental, and harshly judgemental. The expression of this judgement is not a matter of choice on their part, and is assumed to have no impact on their clinical response. Nature now has an additional move, to choose the type of the midwife, and we add costs for sending moderate and heavy signals. A heavy signal to a harshly judgemental midwife adds a heavy cost, and a moderate cost from a moderate midwife. The resulting game might reasonably be said to be intractable.

At this juncture, we do not gain much further from the game representation, and instead separate it into multiple decision problems.

Breaking the game down into separate decision problems can be achieved by treating the moves of the other players as a chance node, and omitting moves by nature that are known to them. For women, there are two such nodes, corresponding to the move by nature determining the type of midwife they play against, and the midwife's action. Midwives have simpler problem with only a single chance node, because the woman's move is known to them. Figure \ref{fig:decision_problems} shows the structure of the resulting decision problems. Note that there are in fact three distinct decision problems for the three types of woman, since the move by nature determining their type is known to them.

\begin{figure}[H]
\subfloat[Women (heavy drinkers)]{\includegraphics[width=11.9cm]{figures/women_influence}}
\vskip\baselineskip
\subfloat[Midwives]{\includegraphics[width=11.9cm]{figures/mw_influence}}
\caption{Influence diagrams, showing the game broken into two decision problems. Squares indicate a decision node, while circles are (from the perspective of the agent) chance nodes}

\label{fig:decision_problems}
\end{figure}

The precise structure of the decision problem is to some extent dependent on the decision rule in use, for example the Lexicographic heuristic rule is concerned only with a direct relationship between action and consequence. However, the literal translation from game to decision problem for women yields two chance nodes. As a result, solving this using the heuristic approach requires that the nodes be combined. By the same token, an arbitrarily complex problem could be resolved by rules without this limitation. This is significant, in that the decision problem is an individual agent's model of the situation, which might not be expected to correspond perfectly with the true sequence of events.

From this position, simulating play, and augmenting the basic conjecture is easily achievable, since together the game, and the decision rules specify the basis for a simulation model. In the disclosure game case, we make additional stipulations on how many games agents play, order of play, the circumstances under which agents observe true types, and the structure of agent populations amongst others.  
\section{Simulation Schedule}
\label{app:sim_schedule}

In this section we give the step by step process for a single run of the disclosure game simulation.

\begin{enumerate}
\item Generate 1000 women, and place them in a queue
\item Generate 100 midwives.
\item For each round of the game
\begin{enumerate}
	\item Take 100 women from the queue
	\item Pair each one with a random midwife
	\item For each pair
	\begin{enumerate}
		\item The woman sends a signal
		\item The midwife refers or not based on the signal
		\item The woman is informed of her payoff, the midwife's type, and whether she is referred
		\item The woman updates her beliefs
		\item The midwife stores the game in their memory
		\item If the woman is referred
		\begin{enumerate}
			\item The midwife is informed of the woman's true type
			\item The midwife retrospectively updates their beliefs using the true type, and memories of any games with this woman
			\item The midwife is now eligible to share their memories of games with this woman
		\end{enumerate}
	\end{enumerate}
	\item Women who have not been referred or had their baby, join the back of the queue
	\item New women are generated to replace those referred, or delivered
	\item The new women are added to the back of the queue
	\item For each referred or birthed woman
	\begin{enumerate}
		\item With probability p, her memory of games is shared with the active women
		\item She is removed from simulation
	\end{enumerate}
	\item The active women update their beliefs
	\item For each midwife with information to share
	\begin{enumerate}
		\item With probability p, their memory of games with the referred woman is shared
		\item The memory is no longer eligible to be shared
	\end{enumerate}
	\item The midwives update their beliefs
\end{enumerate}
\end{enumerate} \section{Agent Examples}
\label{sec:agent_eg}

This section provides a worked example for the learning and decision process of each agent model, focusing on the behaviour of the signalling agent.

\subsection{Lexicographic Heuristic}
\label{sub:lexico_eg}

As an example, take a light drinker who has played three rounds with a succession of particularly judgemental midwives, signalling honestly in two and claiming to be a moderate drinker in one. The most common outcome of the honest signal was a payoff of 10, which is clearly preferable to the 9 gained by claiming to be moderate. On that basis, they choose to signal honestly.

\subsection{Bayesian Payoff}
\label{sub:payoff_eg}

If we take our light drinker from the lexicographic case, and assume that they began with an uninformative prior. The 6 possible signal-payoffs pairings are then \([(l,10),(m,10),(h,10),(m,9),(h,9),(h,8)]\), with \(\alpha_{i}=1\) for all \(i\). After playing the three rounds, \(n_{l,10}=2\), and \(n_{m,9}=1\).

The agent then evaluates \(R_{w}\) for each signal, e.g. for the light signal:

\begin{equation*}
\begin{aligned}
X &= \{10\}\\
R_{w}(l) &= \sum_{x \in X} -xp(x | l) = -10p(10 | l)\\
R_{w}(l) &= -10(\frac{\alpha_{l,10}+n_{l,10}}{\sum_{j}(\alpha_{j}+n_{j})}) = -10(\frac{1+2}{1+2})\\
R_{w}(l) &= -10(\frac{3}{3}) = -10
\end{aligned}
\end{equation*}

and by the same method, \(R_{w}(m)=-9\frac{1}{3}\), and \(R_{w}(h)=-9\), concluding that signalling honestly is the best move.

\subsection{Bayesian Risk Minimisation}
\label{sub:bayes_eg}

Returning to our example agent, under this model the type of the midwife becomes salient, hence \(n_{h}=3\), and \(n_{l,n}=2\), \(n_{m,n}=1\). Their prior beliefs remain uninformative, i.e. \(\alpha_{j} = 1, j \in \{l,m,h\}\), \(\alpha_{i,j}=1,i \in \{r,n\}, j \in \{l,m,h\}\). As before, the agent evaluates \(R_{w}\) for the three signals, and the process for the light signal is given below.

\begin{equation*}
\begin{aligned}
R_{w}(l, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(l, i, l, j)p(j)p(i | l)\\
R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l)\\
&\phantom{{}=1}- u_{w}(l, r, l, m)p(m)p(r | l)- u_{w}(l, n, l, m)p(m)p(n | l)\\
&\phantom{{}=1}- u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
u_{w}(l, i, l, j) &= 10\\
R_{w}(l, l) &= -10p(l)p(r | l) - 10p(l)p(n | l) - 10p(m)p(r | l) - 10p(m)p(n | l)\\
&\phantom{{}=1} - 10p(h)p(r | l) - 10p(h)p(n | l)\\
p(l) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
p(m) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
p(h) &= \frac{1 + 3}{1 + 1 + 1 + 3} = \frac{2}{3}\\
p(r | l) &= \frac{1 + 0}{1 + 1 + 2} = \frac{1}{4}\\
p(n | l) &= \frac{1 + 2}{1 + 1 + 2} = \frac{3}{4}\\
R_{w}(l, l) &= -10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{2}{3} \cdot \frac{1}{4} - 10\cdot \frac{2}{3} \cdot \frac{3}{4}\\
&= -10
\end{aligned}
\end{equation*}

and similarly for moderate (\(R_{w}(m,l)=-9\frac{1}{3}\)), and heavy (\(R_{w}(h,l)=-8\frac{1}{2}\)) signals, once again concluding that honesty is the better option.

\subsection{Descriptive Decision Theory}
\label{sub:cpt_eg}

Once again, we return to the light drinker example.  The inferential aspects are identical with the more complex Bayesian risk minimisation algorithm, hence \(p(j)p(i | l)\), and \(u_{w}(l, i, l, j)\) remain the same, but the agent additionally calculates $v(u_{w}(l, i, l, j))w^{+}(p(j))w^{+}(p(i | l))$. For the \ac{CPT} parameters, the values are those originally given by \citet{Tversky1992} and used in the actual simulations which are given in table \ref{tab:cpt_params}.

\begin{table}[H]
\caption{\ac{CPT} parameters. \label{tab:cpt_params}}
\begin{tabular}{llc}
\hline
Name & Description & Value \\ \hline
\(\gamma\) & Probability weighting for gains  & 0.61 \\ \hline
\(\delta\) & Probability weighting for losses &  0.69\\ \hline
\(\alpha\) & Power for gains  & 0.88 \\ \hline
\(\beta\) & Power for losses & 0.88 \\ \hline
\(\lambda\) & Loss aversion &  2.25 \\ \hline
\end{tabular}
\end{table}

\begin{align*}
\alpha &= 0.88\\
\gamma &= 0.61\\
p(l) &= \frac{1}{6}\\
p(m) &= \frac{1}{6}\\
p(h) &= \frac{2}{3}\\
p(r | l) &= \frac{1}{4}\\
p(n | l) &= \frac{3}{4}\\
u_{w}(l, i, l, j) &= 10\\
f&=(10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{6},10;\frac{1}{2})\\
f^{+}&=f,f^{-}=()\\
n &= 5\\
v(u_{w}) &= f(u_{w}) = u_{w}^\alpha\\
v(u_{w}) &= 10^{0.88} = 7.59\\
\pi_{0}^{+}&=w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})\\
&=w^{+}(1) - w^{+}(\frac{23}{24})\\
&=0.19\\
\pi_{1}^{+}&=w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})\\
&=w^{+}(\frac{23}{24}) - w^{+}(\frac{5}{6})\\
&= 0.17\\
\pi_{2}^{+}&=w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(\frac{5}{6}) - w^{+}(\frac{19}{24})\\
&= 0.04\\
\pi_{3}^{+}&=w^{+}(\frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{6} + \frac{1}{2})=w^{+}(\frac{19}{24}) - w^{+}(\frac{2}{3})\\
&= 0.09\\
\pi_{4}^{+}&=w^{+}(\frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{2})=w^{+}(\frac{2}{3}) - w^{+}(\frac{1}{2})\\
&= 0.09\\
\pi_{5}^{+}&=w^{+}(\frac{1}{2})\\
&= 0.42\\
V(f) &= V(f^{+}) + V(f^{-}) = V(f^{+}) + 0\\
V(f^{+}) &= \sum_{i}^{n}\pi_{i}^{+}(f^{+})v_{i}^{+}(f^{+}) = 7.59
\end{align*}

And as before, following the same process for moderate, and heavy signals which yields respectively 7.14, and 6.22, the agent chooses the higher valued action and sends an honest signal. 
\section{Supplementary Figures}
\label{app:additional_figures}

\begin{figure}[H]
\includegraphics[width=100mm]{figures/ref_plot}
\caption{Average fraction of population referred by each appointment, after 1000 rounds, mean with 95\% confidence limit over 1000 runs. Note that the large number of runs leads to very tight confidence intervals.\label{fig:ref_plot}}
\end{figure} \section{Sensitivity Analysis}
\label{app:sensitivity_results}

This section provides complete variance based sensitivity analysis results for the disclosure game model. Each subsection gives results for one simulation output under all four decision rules, with tables providing the percentage of overall variance attributable to the individual parameters, emulator quality statistics, and the 5 most significant interaction contributions to variance in the output.

\subsection{Median Moderate Drinker Signalling}

\begin{table}[H]
\caption{Median moderate drinker signalling parameter sensitivity \label{tab:sa_results_sig}}
\begin{tabular} {llllll}
\hline\noalign{\smallskip}
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.367 & 1.145 & 0.801 & 0.614 \\
\(p_{w}(l)\) & Proportion of light drinkers & 10.080 & 37.750 & 23.968  & 5.137\\
\(p_{m}(m)\) & Proportion of moderate midwives & 6.715 & 13.017 & 0.894 & 1.485\\
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 43.942 & 1.655 & 1.602 & 2.618 \\
\(q_{w}\) & Probability of women sharing & 0.198 & 5.527 & 4.460 & 1.159 \\
\(w_{w}\) & Weight of shared information for women & 0.355 & 13.025 & 2.716 & 0.888 \\
\(q_{m}\) & Probability of midwives sharing & 0.145 & 0.667 & 0.368 & 0.157 \\
\(w_{m}\) & Weight of shared information for midwives & 0.118 & 0.376 & 0.176 & 0.200 \\
\(x_{h}\) & Health payoff for healthy delivery & 0.457 & 9.618 & 1.912 & 15.355 \\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.140 & 7.537 & 10.427 & 7.795 \\
Total & All parameters and two way interactions & 86.777 & 96.527 & 85.529 & 74.123 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Median moderate drinker signalling emulator statistics \label{tab:sa_emulator_sig}}
\begin{tabular} {lllllll}
\hline\noalign{\smallskip}
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
Lexicographic & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\
Bayesian Payoff & 1.667 & 0.475 &  0.662 & 0.003 & 0.181 & 3.12 \\
Bayesian & 3.352 & 0.534 & 1.160 & 0.001 & 0.068 & 2.423 \\
\ac{CPT} & 1.503 & 0.331 & 1.241 & 0.002 & 0.101 & 1.842 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Top 5 Interaction terms for \ac{CPT} decision rule. \label{tab:sa_interaction_prospect_sig}}
\begin{tabular} {ll}
\hline\noalign{\smallskip}
Parameter & Variance \\ 
\noalign{\smallskip}\svhline\noalign{\smallskip}

\(x_{h}\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 20.814\\
\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 5.698\\
\(p_{w}(l)\)*\(x_{h}\) & 2.895\\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(w_{w}\) & 2.799\\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(q_{m}\) & 1.686\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Top 5 Interaction terms for Bayesian decision rule. \label{tab:sa_interaction_sharing_sig}}
\begin{tabular} {ll}
\hline\noalign{\smallskip}
Parameter & Variance \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 17.270\\
\(p_{w}(l)\)*\(q_{m}\) & 6.054\\
\(q_{m}\)*\(w_{w}\) & 3.814\\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(q_{m}\) & 3.538\\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(w_{w}\) & 3.084\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Top 5 Interaction terms for Lexicographic decision rule. \label{tab:sa_interaction_lexic_sig}}
\begin{tabular} {ll}
\hline\noalign{\smallskip}
Parameter & Variance \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{m}(l)\)*\(p_{m}(m)\) & 15.331\\
\(p_{m}(m)\)*\(p_{w}(l)\) & 3.682\\
\(p_{m}(l)\)*\(p_{w}(l)\) & 3.581\\
\(p_{m}(m)\)*\(q_{m}\) & 0.349\\
\(p_{m}(l)\)*\(q_{m}\) & 0.279\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Top 5 Interaction terms for Bayesian Payoff decision rule. \label{tab:sa_interaction_payoff_sig}}
\begin{tabular} {ll}
\hline\noalign{\smallskip}
Parameter & Variance \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{w}(l)\)*\(w_{w}\) & 4.045\\
\(x_{h}\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 1.856\\
\(p_{w}(l)\)*\(q_{m}\) & 1.231\\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(q_{m}\) & 0.997\\
\(q_{m}\)*\(w_{w}\) & 0.929\\ 
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\subsection{Median Between Groups IQR}

\begin{table}[H]
\caption{Median between groups IQR parameter sensitivity \label{tab:sa_results_iqr}}
\begin{tabular} {llllll}
\hline\noalign{\smallskip}
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.327 & 0.688 & 0.457 & 0.586 \\
\(p_{w}(l)\) & Proportion of light drinkers & 11.223 & 20.123 & 11.046 & 4.081 \\
\(p_{m}(m)\) & Proportion of moderate midwives & 36.630 & 1.160 & 0.364 & 1.945 \\
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 6.228 & 4.487 & 0.0964 & 2.627\\
\(q_{w}\) & Probability of women sharing & 0.498 & 0.235 & 2.537 & 1.812 \\
\(w_{w}\) & Weight of shared information for women & 1.018 & 2.307 & 1.889 & 0.740 \\
\(q_{m}\) & Probability of midwives sharing & 0.158 & 0.343 & 0.387 & 0.156 \\
\(w_{m}\) & Weight of shared information for midwives & 0.076 & 0.973 & 0.125 & 0.213 \\
\(x_{h}\) & Health payoff for healthy delivery & 0.317 & 10.960 & 3.305 & 16.493 \\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 1.107 & 8.411 & 2.890 & 6.729 \\
Total & All parameters and two way interactions & 81.702 & 83.693 & 47.449 & 71.032 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Median between groups IQR emulator statistics \label{tab:sa_emulator_iqr}}
\begin{tabular} {lllllll}
\hline\noalign{\smallskip}
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
Lexicographic & 0.930 & 0.240 & 0.249 & 0.002 & 0.040 & 1.832 \\
Bayesian Payoff & 1.242 & 0.417 & 0.232 & 0.001 & 0.0034 & 2.308 \\
Bayesian & 1.254 & 0.131 & 0.644 & 0.000 & 0.019 & 1.167 \\
\ac{CPT} & 1.190 & 0.313 & 0.659 & 0.000 & 0.024 & 1.701 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[h]
\caption{Top 5 Interaction terms for \ac{CPT} decision rule.}
\label{tab:sa_interaction_prospect_group_iqr}
\begin{tabular} {ll}
\hline\noalign{\smallskip}
Parameter & Variance \\ 
\noalign{\smallskip}\svhline\noalign{\smallskip}

\(x_{h}\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 19.551\\
\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 3.838\\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(w_{w}\) & 2.450\\
\(p_{w}(l)\)*\(x_{h}\) & 2.337\\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(q_{m}\) & 2.046\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Top 5 Interaction terms for Bayesian decision rule. \label{tab:sa_interaction_sharing_group_iqr}}
\begin{tabular} {ll}
\hline\noalign{\smallskip}
Parameter & Variance \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(q_{m}\) & 4.284\\
\(p_{w}(l)\)*\(q_{m}\) & 3.866\\
\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 2.943\\
\(x_{h}\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 2.680\\
\(q_{m}\)*\(w_{w}\) & 2.282\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Top 5 Interaction terms for Lexicographic decision rule. \label{tab:sa_interaction_lexic_group_iqr}}
\begin{tabular} {ll}
\hline\noalign{\smallskip}
Parameter & Variance \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{m}(l)\)*\(p_{m}(m)\) & 12.046\\
\(p_{m}(m)\)*\(p_{w}(l)\) & 5.054\\
\(p_{m}(l)\)*\(p_{w}(l)\) & 3.005\\
\(p_{m}(l)\)*\(w_{w}\) & 0.819\\
\(p_{m}(m)\)*\(w_{w}\) & 0.757\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Top 5 Interaction terms for Bayesian Payoff decision rule. \label{tab:sa_interaction_payoff_group_iqr}}
\begin{tabular} {ll}
\hline\noalign{\smallskip}
Parameter & Variance \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 12.883\\
\(p_{w}(l)\)*\(w_{w}\) & 5.667\\
\(p_{w}(l)\)*\(x_{h}\) & 2.447\\
\(x_{h}\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 2.360\\
\(p_{m}(m)\)*\(p_{w}(l)\) & 1.919\\ 
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\subsection{Median Moderate Drinker Signalling IQR}

\begin{table}[H]
\caption{IQR of median moderate drinker signalling parameter sensitivity \label{tab:sa_results_sig_iqr}}
\begin{tabular} {llllll}
\hline\noalign{\smallskip}
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.428 & 9.828 & 3.816 & 2.068 \\
\(p_{w}(l)\) & Proportion of light drinkers & 8.369 & 13.791 & 4.045 & 2.400 \\
\(p_{m}(m)\) & Proportion of moderate midwives & 13.416 & 0.712 & 0.676 & 0.583 \\
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 21.079 & 0.648 & 0.659 & 0.373 \\
\(q_{w}\) & Probability of women sharing & 2.307 & 3.481 & 0.891 & 0.600 \\
\(w_{w}\) & Weight of shared information for women & 6.021 & 6.009 & 0.562 & 0.937 \\
\(q_{m}\) & Probability of midwives sharing & 0.315 & 1.829 & 0.114 & 0.117 \\
\(w_{m}\) & Weight of shared information for midwives & 1.652 & 1.354 & 0.260 & 0.0.139 \\
\(x_{h}\) & Health payoff for healthy delivery & 0.253 & 0.612 & 4.889 & 15.146 \\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.504 & 3.096 & 19.863 & 25.999 \\
Total & All parameters and two way interactions & 84.9968 & 77.413 & 57.125 & 83.322 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{IQR of median between groups IQR emulator statistics \label{tab:sa_emulator_sig_iqr}}
\begin{tabular} {lllllll}
\hline\noalign{\smallskip}
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
Lexicographic & 1.425 & 0.436 & 0.549 & 0.008 & 0.114 & 2.719 \\
Bayesian Payoff & 1.223 & 0.496 & 0.747 & 0.012 & 0.207 & 2.034 \\
Bayesian &  1.065 & 0.000 & 0.230 & 0.002 & 0.088 & 1.015 \\
\ac{CPT} & 0.874 & 0.213 & 0.233 & 0.001 & 0.066 & 1.806 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Top 5 Interaction terms for \ac{CPT} decision rule. \label{tab:sa_interaction_prospect_sig_iqr}}
\begin{tabular} {ll}
\hline\noalign{\smallskip}
Parameter & Variance \\ 
\noalign{\smallskip}\svhline\noalign{\smallskip}

\(x_{h}\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 17.377\\
\(p_{w}(m)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 3.356\\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(w_{w}\) & 3.036\\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(q_{m}\) & 2.067\\
\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 1.721\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Top 5 Interaction terms for Bayesian decision rule. \label{tab:sa_interaction_sharing_sig_iqr}}
\begin{tabular} {ll}
\hline\noalign{\smallskip}
Parameter & Variance \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{w}(m)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 4.188\\
\(x_{h}\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 3.120\\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(q_{m}\) & 2.423\\
\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 2.279\\
\(p_{w}(l)\)*\(q_{m}\) & 1.489\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Top 5 Interaction terms for Lexicographic decision rule. \label{tab:sa_interaction_lexic_sig_iqr}}
\begin{tabular} {ll}
\hline\noalign{\smallskip}
Parameter & Variance \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{m}(m)\)*\(p_{w}(l)\) & 12.068\\
\(p_{m}(l)\)*\(p_{w}(l)\) & 6.794\\
\(p_{m}(l)\)*\(p_{m}(m)\) & 5.567\\
\(p_{m}(m)\)*\(q_{m}\) & 0.886\\
\(p_{m}(l)\)*\(q_{m}\) & 0.692\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Top 5 Interaction terms for Bayesian Payoff decision rule. \label{tab:sa_interaction_payoff_sig_iqr}}
\begin{tabular} {ll}
\hline\noalign{\smallskip}
Parameter & Variance \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{w}(l)\)*\(p_{w}(m)\) & 8.357\\
\(p_{w}(l)\)*\(w_{w}\) & 7.431\\
\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 4.882\\
\(p_{w}(l)\)*\(q_{m}\) & 2.346\\
\(p_{w}(l)\)*\(w_{m}\) & 2.025\\ 
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\subsection{Between Groups IQR IQR}

\begin{table}[H]
\caption{IQR of median between groups IQR parameter sensitivity \label{tab:sa_results_iqr_iqr}}
\begin{tabular} {llllll}
\hline\noalign{\smallskip}
Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{w}(m)\) & Proportion of moderate drinkers & 0.691 & 5.926 & 1.053 & 1.265 \\
\(p_{w}(l)\) & Proportion of light drinkers & 3.664 & 17.047 & 4.877 & 3.656 \\
\(p_{m}(m)\) & Proportion of moderate midwives & 41.369 & 1.124 & 0.814 & 0.591 \\
\(p_{m}(l)\) & Proportion of non-judgemental midwives & 7.109 & 0.739 & 0.496 & 0.378 \\
\(q_{w}\) & Probability of women sharing & 1.963 & 2.038 & 0.733 & 0.589 \\
\(w_{w}\) & Weight of shared information for women & 7.932 & 11.193 & 2.289 & 1.960 \\
\(q_{m}\) & Probability of midwives sharing & 0.413 & 1.972 & 0.267 & 0.069\\
\(w_{m}\) & Weight of shared information for midwives & 0.120 & 2.902 & 0.150 & 0.123 \\
\(x_{h}\) & Health payoff for healthy delivery & 0.228 & 3.190 & 6.308 & 14.777 \\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.673 & 10.411 & 22.901 & 26.340 \\
Total & All parameters and two way interactions & 85.740 & 88.611 & 68.640 & 84.210 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{IQR of median between groups IQR emulator statistics \label{tab:sa_emulator_iqr_iqr}}
\begin{tabular} {lllllll}
\hline\noalign{\smallskip}
Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
Lexicographic & 0.826 & 0.409 & 0.259 & 0.002 & 0.034 & 2.364 \\
Bayesian Payoff & 3.202 & 0.520 & 0.328 & 0.002 & 0.032 & 2.452 \\
Bayesian & 1.177 & 0.041 & 0.133 & 0.000 & 0.018 & 1.152 \\
\ac{CPT} & 0.874 & 0.118 & 0.126 & 0.000 & 0.017 & 1.570 \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Top 5 Interaction terms for \ac{CPT} decision rule. \label{tab:sa_interaction_prospect_group_iqr_iqr}}
\begin{tabular} {ll}
\hline\noalign{\smallskip}
Parameter & Variance \\ 
\noalign{\smallskip}\svhline\noalign{\smallskip}

\(x_{h}\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 18.626\\
\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 3.312\\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(w_{w}\) & 2.823\\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(q_{m}\) & 2.694\\
\(x_{h}\)*\(q_{m}\) & 1.022\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Top 5 Interaction terms for Bayesian decision rule. \label{tab:sa_interaction_sharing_group_iqr_iqr}}
\begin{tabular} {ll}
\hline\noalign{\smallskip}
Parameter & Variance \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 7.947\\
\(x_{h}\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 4.048\\
\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(q_{m}\) & 3.134\\
\(p_{w}(l)\)*\(q_{m}\) & 2.307\\
\(p_{m}(m)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 2.232\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Top 5 Interaction terms for Lexicographic decision rule. \label{tab:sa_interaction_lexic_group_iqr_iqr}}
\begin{tabular} {ll}
\hline\noalign{\smallskip}
Parameter & Variance \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(p_{m}(l)\)*\(p_{m}(m)\) & 8.659\\
\(p_{m}(m)\)*\(p_{w}(l)\) & 3.726\\
\(p_{m}(l)\)*\(p_{w}(l)\) & 3.237\\
\(p_{m}(l)\)*\(w_{w}\) & 1.564\\
\(p_{m}(m)\)*\(w_{w}\) & 1.558\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Top 5 Interaction terms for Bayesian Payoff decision rule. \label{tab:sa_interaction_payoff_group_iqr_iqr}}
\begin{tabular} {ll}
\hline\noalign{\smallskip}
Parameter & Variance \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
\(q_{m}\)*\(w_{w}\) & 3.830\\
\(p_{w}(l)\)*\(p_{w}(m)\) & 3.808\\
\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 3.401\\
\(p_{w}(l)\)*\(q_{m}\) & 2.385\\
\(x_{h}\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 2.294\\ 
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

  \end{document}

### 2015-09-26 model_description.tex
Pronouns

@@
 A game, in the game theoretic sense, can be any interaction where the result for one person is dependent on the actions of another.
-In this scenario, the result for the woman would seem dependent on whether the midwife chooses to refer them for specialist support (although naturally the reality can only be thought of in terms of risk mitigation), and conversely, the right choice for the midwife is somewhat contingent on what the woman is willing to tell them.
+In this scenario, the result for the woman would seem dependent on whether the midwife chooses to refer her for specialist support (although naturally the reality can only be thought of in terms of risk mitigation), and conversely, the right choice for the midwife is somewhat contingent on what the woman is willing to tell them.
 
@@
 The wider difficulty here is that the real outcome depends on an attribute of one of the players, rather than their moves.
-In this case, we would expect the right choices to depend on the alcohol consumption of the woman, rather than entirely on what they have claimed about it.
+In this case, we would expect the right choices to depend on the alcohol consumption of the woman, rather than entirely on what she has claimed about it.
 To reflect this, we would need different variations on the same game to reflect this attribute.
@@
 We must also amend the moves, and payoffs slightly.
-The woman now claims to be one of the types, and may send a signal to say, for example, that they are a heavy drinker.
+The woman now claims to be one of the types, and may send a signal to say, for example, that she a heavy drinker.
 We will also modify the common payoffs to allow light drinkers to get the best outcome no matter what, and moderate and heavy types to get the best outcome only if referred.

### 2015-09-26 simulation_schedule.tex
Pronouns

@@
 		\item The midwife refers or not based on the signal
-		\item The woman is informed of their payoff, the midwife's type, and whether they are referred
+		\item The woman is informed of her payoff, the midwife's type, and whether she is referred
 		\item The woman updates her beliefs
@@
 	\begin{enumerate}
-		\item With probability p, their memory of games is shared with the active women
-		\item They are removed from simulation
+		\item With probability p, her memory of games is shared with the active women
+		\item She is removed from simulation
 	\end{enumerate}

### 2015-09-27 article.tex
Fix conf intervals in eps

@@
 This does not preclude a strategic dimension, since decision rules are to a great extent modular, and as demonstrated in this paper can be exchanged without altering the decision problem.
-In addition, rules are agnostic as to the source of information, suggesting room for multi-stage processes - for example, a more game theoretic, model of the opponent's mind, type approach could act as an information source for a decision rule.
+In addition, rules are agnostic as to the source of information, suggesting room for multi-stage processes - for example, a game theoretic, model of the opponent's mind, approach could act as an information source for a decision rule.
 As a corollary, the decision problem agents attempt to answer can change, allowing behaviour in novel problems to be informed by beliefs derived under other conditions.
@@
 While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same output - a decision, we limit ourselves here to four.
-The simplest is a lexicographic rule (1), in the spirit of a \acl{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}.
+The simplest is a lexicographic rule (1), in the spirit of a \acl{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule \cite{Tversky1992}.
 Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-output characteristics.
@@
 
-Measurements were taken at the end of 1000 rounds of play, and emulators were built against 400 sample points from the full set of simulation results (1 \& 2), and \ac{IQR} at each point (3 \& 4) to assess both the overall trend, and the extent to which the parameters contribute to variance between runs.
+Measurements were taken at the end of 1000 rounds of play, and emulators were built against 400 sample points from the full set of simulation results (1 \& 2), and the \ac{IQR} at each point (3 \& 4) to assess both the overall trend, and the extent to which the parameters contribute to variance between runs.
 

### 2015-11-10 acronyms.tex
acronyms to own file

--- 2015-09-27 article.tex
@@
-\documentclass[graybox]{svmult}
-\usepackage[hyperfootnotes=false]{hyperref}
-\hypersetup{bookmarksdepth=3}
-
-\usepackage{mathptmx}       \usepackage{helvet}         \usepackage{courier}        \usepackage{type1cm}                                    \usepackage{makeidx}         \usepackage{graphicx}                                     \usepackage{multicol}        \usepackage[bottom]{footmisc} \usepackage{adjustbox}
- \usepackage{multirow}
- \usepackage{algorithm}
- \usepackage{algpseudocode}
- \usepackage{ifthen}
- \usepackage{csquotes}
- \usepackage{amsmath}
-
-\usepackage{comment}
- \usepackage{natbib}
- \setcitestyle{numbers,square}
- \usepackage[subrefformat=parens,labelformat=simple,caption=false,labelfont={bf}]{subfig}
- \usepackage[nolist,smaller]{acronym}
-\allowdisplaybreaks
-\makeindex
-
-\begin{document}
-\begin{acronym}[ALSPAC]
 \acro{FAS}{Foetal Alcohol Syndrome}
@@
   \acro{IQR}{interquartile range}
-\end{acronym}
-
-\title*{Deciding to Disclose}
-\subtitle{A Decision Theoretic Agent Model of Pregnancy and Alcohol Misuse}
-
-\author{Jonathan Gray, Jakub Bijak, and Seth Bullock}
-\institute{Jonathan Gray \at University of Southampton, Southampton, United Kingdom \email{j.gray@soton.ac.uk}
-\and Jakub Bijak \at University of Southampton, Southampton, United Kingdom \email{j.bijak@soton.ac.uk}
-\and Seth Bullock \at University of Southampton, Southampton, United Kingdom \email{sgb@ecs.soton.ac.uk}}
-
-\maketitle
-
-\begingroup
-\let\clearpage\relax
-\let\cleardoublepage\relax
-
-\section*{Abstract}
-
-We draw together methodologies from game theory, agent based modelling, decision theory, and uncertainty analysis to explore the process of decision making in the context of pregnant women disclosing their drinking behaviour to their midwives.
-
-We employ a game theoretic framework to define a signalling game.
-The game represents a scenario where pregnant women decide the extent to which they disclose their drinking behaviours to their midwives, and midwives employ the information provided to decide whether to refer their patients for costly specialist treatment.
-This game is then recast as two games played against \enquote{nature}, to permit the use of a decision theoretic approach where both classes of agent use simple rules to decide their moves.
-Four decision rules are explored - a lexicographic heuristic which considers only the link between moves and payoffs, a Bayesian risk minimisation agent that uses the same information, a more complex Bayesian risk minimiser with full access to the structure of the decision problem, and a \ac{CPT} rule.
-
-In simulation, we recreate two key qualitative trends described in the midwifery literature for all the decision models, and investigate the impact of introducing a simple form of social learning within agent groups.
-Finally a global sensitivity analysis using \acp{GEM} is conducted, to compare the response surfaces of the different decision rules in the game. \acresetall
-
-\section{Introduction}
-\label{sec:intro}
-
-The case in favour of \ac{ABM} as a general analytical approach has been made numerously, and elegantly (e.g.
-\cite{epstein1994growing,Resnick,Axelrod1997,gilbert1999simulation,Macy2002a,Silverman2011,Silverman2013,epstein2014agent_zero}, amongst others).
-As such we will not belabour the point, and instead turn to addressing some of the concerns expressed about the approach.
-In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, reflecting the assumptions of the modeller rather than empirically or theoretically grounded \citep{Waldherr2013}.
-To ameliorate this concern, we draw on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game\footnote{In a signalling game, one player (the signaller), has some piece of information that is known only to them which affects the outcome of the game for both players.
-The signaller has a choice as to what they tell the other player about this hidden information, and the responding player as to what they believe the information to be.} \citep{Kreps1987} with a basic form of intragroup social learning.
-Four decision models of varying complexity, and behavioural plausibility are contrasted, by way of demonstrating the significance of the operationalisation of decision making in \ac{ABM}.
-
-This exercise is framed in the context of disclosure decisions, taking drinking patterns in pregnant women as a motivating example.
-Alcohol consumption in the antenatal period is a significant issue in itself, although there is not a clear consensus on associated risk.
-In terms of official guidance in the UK, \ac{NICE} acknowledge that evidence of harm to the fetus is less than conclusive, but advise not drinking at all, or significant moderation \citep{NICE2010a}, with similar advice from the UK \cite{DepartmentofHealth2008}.
-
-Turning more specifically to disclosure of alcohol use by women to healthcare professionals during their pregnancy, research is relatively sparse, although qualitative trends are reported by \citet{Phillips2007} and \citet{Alvik2006}.
-The former explored factors impacting disclosure through a small case study, highlighting the need to build up rapport between woman and midwife over several appointments; the latter compared post partum reports of consumption with contemporaneous accounts, finding apparent underreporting during pregnancy which was amplified by increased drinking.
-The simulation model described in this paper is able to replicate both qualitative trends, i.e.
-an increase in disclosure over appointments, and more honest behaviour by moderate as compared to heavier drinkers.
-
-The resulting scenario is of substantial independent interest, and shows the potential utility of a simulation approach in domains where the process is obscured, here both because of the interest in concealment, and obvious ethical concerns.
-With this said, the lack of a strong quantitative evidence base against which to validate the behaviour of the model augers for caution in interpreting the results, and a necessary reminder that in this instance the model is primarily a tool for formalisation of the thought process \citep{epstein2008}, rather than a machine for predicting.
-
-A game theoretic approach to generating an abstract form of the problem gives a convenient, and well known framework to reason about the processes involved in the scenario.
-While scenarios may map to a number of games, exploring one candidate game still allows for a principled comparison between interpretations, and enforces explicit assumptions.
-But equilibrium is the sine qua non of game theory, which is concerned with the stable outcome of an infinite contest of second guesses.
-We wish to see the system in motion rather than just at rest, even if it does eventually settle to some stable point.
-Instead, we choose to focus instead on the behavioural processes driving a system in motion, a system out of equilibrium, to understand how these processes interact with the movement.
-Introducing decision theory takes a step down the ladder of abstraction from the mental chess of game theory.
-Dealing instead in the mechanics of decision making, and the calculus of choice, allows us to explore not only paths that arrive at the destinations we might consider in game theory, but also avenues not accessible where we constrain ourselves to a sometimes implausible degree of rationality.
-
-This does not preclude a strategic dimension, since decision rules are to a great extent modular, and as demonstrated in this paper can be exchanged without altering the decision problem.
-In addition, rules are agnostic as to the source of information, suggesting room for multi-stage processes - for example, a game theoretic, model of the opponent's mind, approach could act as an information source for a decision rule.
-As a corollary, the decision problem agents attempt to answer can change, allowing behaviour in novel problems to be informed by beliefs derived under other conditions.
-This is also indicative of the broader benefits to \ac{ABM} as an approach.
-Embedding these abstract rules in a simulated environment allows for mechanics which cannot be readily explored using purely analytic, or predictive approaches, for example, the social learning dynamic of the disclosure game model.
-
-While there is no universal theory of human behaviour to sit at the centre of \ac{ABM} as a method, a key motivation for decision rules is their claim to provide an account of decision making that is behaviourally and cognitively plausible.
-Their mooted capability in this regard is to some extent supported by work from neuroeconomics, which aims to empirically test theories of decision making \citep{Rustichini2009}.
-Many key aspects common to decision rules, for example the idea that a common currency is used by the brain to compare outcomes \citep{Padoa-Schioppa2006,Padoa-Schioppa2008}, are supported by neurological findings.
-In addition, a single decision rule represents a parsimonious alternative to numerous case specific production rules.
-
-Given these features, the application of decision, and game theory to \ac{ABM} is an attractive approach to computational social science, where the locus of interest is process, and decision making.
-Taking a balance between models focused on replication of low level neurological mechanics, and those with a higher level emphasis where individual behaviours are abstracted away, yields a computationally tractable approach.
-Despite the relative simplicity, it nonetheless captures some of the nuance and sophistication of human decisions.
-
-The remainder of this paper proceeds to outline the proposed approach to model development (section \ref{sec:model}), and experiments (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}).
-\section{Disclosure Game Model}
-\label{sec:model}
-
-In this section we sketch\footnote{A complete example of this for the alcohol misuse in pregnancy model is given in appendix \ref{app:model_description}, with a schedule of simulation provided in appendix \ref{app:sim_schedule}} the process of moving from a real world scenario to a minimal game which sufficiently captures reality, expressing the result as a decision problem representation, and translating this to a simulation model.
-We then outline four possible decision rules, and as an example of additional flexibility of process models and simulation in contrast to purely predictive or analytical approaches, extend the model to allow a simple form of social learning.
-
-\subsection{Modelling Approach}
-\label{sec:model_design}
-
-To model a scenario, we take the approach of first creating a formal game to represent it, capturing the key features as far as possible in the structure of that game.
-This game is in essence a conjecture about the real data generating process, which can be played out in simulation.
-
-The appropriate game representative of the scenario of interest, which captures the desired strategic dynamics may not be immediately obvious.
-We suggest that an iterative process is beneficial, beginning from the simplest possible game, and progressively augmenting it.
-
-Transitioning from the resulting game, to a set of decision problems is a relatively simple task.
-We treat the $n$ player game as $n$ one-player games \citep{RiosInsua2009}, where the moves of other players are drawn from a probability distribution - nature, in game theoretic parlance.
-As with the game, the decision problem representation admits a degree of variation, and may need to be adjusted to reflect the decision rules that will be used.
-
-These decision problems may then form the basis of an agent model, where agents use learning, and decision rules to play out the game.
-Simulation can then support features which are not readily representable within an analytic framework, for example, populations of heterogeneous players, individual and social learning, or network effects.
-In addition, the ability to observe the system in a state of flux rather than at equilibrium is desirable, since even where a social system reaches a stable state, the process by which we arrive at it is significant.
-
-\subsection{Scenario}
-\label{sec:scenario}
-
-Typically in the UK, women have 12 appointments with a midwife during the antenatal period, and in the majority of cases will encounter several different midwives \citep{Redshaw2014} in the course of their care.
-In the UK, and unlike most healthcare contexts, maternity notes are held by the patient, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously.
-Maternity notes are not generally linked to extra-departmental records, meaning that a history of alcohol related admissions to another service may remain unknown unless revealed by the woman.
-
-According to NICE guidance \citep{NICE2010a,NICE2010} the issue of substance misuse should be raised at the initial booking appointment, followed by subsequent action if a concern is raised is at the discretion of the midwife.
-This may take the form of specific guidance to reduce intake, or if deemed necessary a referral to a specialist midwife and relevant interdisciplinary team.
-On alcohol consumption, policy regarding how to determine the level of consumption is at the time of writing generally at the level of local health authority, hospital trust, or according to the best judgement of the individual midwife, with no guidance provided by NICE.
-This commonly takes the form of average units per week, but may include \ac{T-ACE}\footnote{The \ac{T-ACE} is a four question screening test for alcohol misuse intended specifically for use with pregnant women.} \citep{Sokol1989863} and similar measures.
-
-Beyond the \enquote{booking} appointment, the onus is on women to raise concerns about their drinking behaviour, or the midwife to probe further if they feel it is warranted.
-In either case, once a concern has been raised the midwife must respond clinically, and inevitably personally, to the information.
-
-In an ideal world, all interactions with healthcare providers would be immediately and fully disclosive, with no repercussions for the patient.
-However, alcohol misuse by women is known to attract stigma \citep{Gomberg1988}, and is a recognised barrier to appropriate treatment in the maternity context \citep{NICE2010,Radcliffe2011}.
-
-\subsection{Disclosure Game}
-\label{sub:the_game}
-
-In order to translate the scenario sketched above into a more abstract, tractable form, we cast it as a signalling game, and assume that women's disclosures (or not), are signals.
-We also impose a discretisation on the continuum of alcohol use, and use three types of behaviour - light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy.
-Correspondingly, they are limited in what signals they may send when claiming to be one of these three types.
-
-Midwives are treated in a similar fashion, where their type corresponds to how negatively they regard a drinking pattern - non-judgemental, moderately judgemental, and harshly judgemental.
-The expression of this judgement is not a matter of choice on their part, and is assumed to have no impact on their clinical response, which is to either refer the woman for specialist treatment, or do nothing.
-
-At the end of a game, each player receives a payoff dependent on the actions and types of both players.
-Because both women and midwives have an interest in the outcome of the pregnancy, and would prefer a healthy baby, the payoff has a common interest component.
-Hence, both players receive a payoff based on the outcome of pregnancy, but women bear a social cost dependent on the signal they sent and the midwife's reaction to it.
-Similarly, midwives pay a cost if they refer to a specialist, mirroring the organisational cost of non-routine care.
-Table \ref{tab:Payoff-matrix} shows the three payoff matrices which together describe the game.
-
-\begin{table}
-\caption{Payoff matrices}
-\label{tab:Payoff-matrix}
-\subfloat[Social cost, \(X_{s}\), for women, given their signal, and the midwife's type\label{tab:Social-cost-matrix}]{\begin{tabular}{|c|c|c|c|c|}
-\cline{3-5} 
-\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
-
-\hline
-\multirow{4}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
-\cline{2-5} 
- & Harsh & -2 & -1 & 0\tabularnewline
-\cline{2-5} 
- & Moderate & -1 & 0 & 0\tabularnewline
-\cline{2-5} 
- & Non & 0 & 0 & 0\tabularnewline
-\hline 
-\end{tabular}
-
-}\qquad
-\subfloat[Health outcome, \(X_{h}\), for women and midwives, given the midwife's action, and woman's type\label{tab:Referral-payoff-matrix}]{\begin{tabular}{|c|c|c|c|c|}
-\cline{3-5} 
-\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
-
-\hline 
-\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
-\cline{2-5} 
- & Refer & 10 & 10 & 10\tabularnewline
-\cline{2-5} 
- & Don't refer & -2 & -1 & 10\tabularnewline
-\hline 
-\end{tabular}
-
-}
-
-\subfloat[Referral cost, \(X_{c}\), for midwife, given their action and the woman's type\label{tab:inst_cost_matrix}]{\begin{tabular}{|c|c|c|c|c|}
-\cline{3-5}  
-\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
-\hline 
-\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
-\cline{2-5} 
- & Refer & -9 & -9 & -9 \tabularnewline
-\cline{2-5} 
- & Don't refer & 0 & 0 & 0\tabularnewline
-\hline 
-\end{tabular}
-
-}
-\end{table}
-
-As an example, consider the challenge faced by an agent of the heavy drinking type.
-In order to get the best health outcome, they must be referred and would ideally achieve this without paying any social cost at all.
-The best move depends on the type, and beliefs of the midwife.
-For example, a particularly unlucky scenario might be for the midwife to not only be of a harshly judgemental disposition, but to believe that no women really need to be referred (i.e.
-that all women are light drinkers).
-Even a relatively weak belief in this possibility can make the honest signal look like an unwarranted risk.
-
-To formally define the game, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\).
-Here, \(\{l, m, h\}\) correspond to light, moderate, and heavy alcohol consumption for women, and non-judgemental, moderately judgemental, and harshly judgemental for midwives.
-Midwives' pure strategies \(\{r,n\}\) are to refer, or do nothing, and those for women are to signal that they have one of the possible drinking patterns.
-Additionally define two utility functions - 
-\begin{equation}
-u_{w}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}}
-\end{equation} 
-\begin{equation}
-u_{m}(s_{w}, s_{m}, \theta_{w})=X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}},
-\end{equation} with $X_{c}$, $X_{h}$, and $X_{s}$ being the payoff matrices as in table \ref{tab:Payoff-matrix}, $s_{w}$ and $s_{m}$ denoting a specific signal by a woman, and referral response by a midwife.
-Lastly let \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\) be distributions over types of women, and midwives respectively.
-
-As noted, rather than solve the game, we allow populations of agents to play it, and hence stipulate further that women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)).
-They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred, and a new player is drawn from the same distribution that produced the original players to replace them.
-If they are not referred, they rejoin the back of the queue after their appointment.
-In either case, they are informed of their payoff after each round and update their beliefs accordingly using one of the rules described in section \ref{sub:the_agents}.
-
-Midwives play for \(r_{m}\) rounds (\(r_{m}=1000\) in all experiments), and conduct appointments in parallel, i.e.
-if there are 5 midwives, then five women are drawn from the queue and assigned at random to the midwives.
-Unlike women, midwives are only informed of their payoff if they choose to make a referral.
-Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.
-
-\subsection{Social Learning}
-\label{sub:info_sharing}
-
-In reality, learning is not exclusively from personal experience, and social learning plays an important role.
-This social dynamic fits naturally into an agent framework, but is difficult to address without using an approach concerned with process, so we take advantage of this to show a na{\"\i}ve take on it here.
-
-In the disclosure game model, this takes the form of having each agent recount their play history to their colleagues with some probability \(q\).
-Individuals then incorporate shared information into their beliefs using weighted updates, e.g.
-for a midwife a shared observation of a low type signal contributes to their beliefs by \(w\), and \(0\leq w\leq 1\) (i.e.
-\(n_{j} = n_{j} + w\)).
-Women share only when they have finished play, and provide their complete history of games, because they have accurate information about the outcomes.
-By the same rationale, midwives share only their history with the most recent woman they referred.
-Sharing occurs simultaneously for all players at the end of each round, and all memories are either shared immediately or discarded.\footnote{More precisely, memories of games remain, but it is assumed that only the most current information is relevant enough to be shared.} Accounts are shared with some probability, to all fellow players.
-For example, a heavy drinker finishes play having claimed to be a light drinker, without ever being referred, and their account is selected to be shared with some probability $q_{w}$.
-
-Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this exogenous information differently.
-The simple payoff based rule relies on a belief structure relating actions directly to rewards which is essentially model free.
-Because payoffs differ by the agent's private type, the information shared may not correspond to the experience of the listening agent in the same scenario.
-As a result, payoff reasoners have a belief bias towards the most common player type, and can believe in outcomes that are, for them, impossible.
-
-A payoff based agent, who is a light drinker, hears the account of the heavy drinker.
-They take the account as literally happening to them, and update their beliefs to include the possibility that there is a negative outcome attached to claiming to be a light drinker.
-
-By contrast, representing the problem in terms of the probabilities of the individual lotteries imposes a model that abstracts the new information from payoffs, and allows the agent to discard implausible outcomes.
-This stronger assumption as to the static and known qualities of payoffs does however reduce the flexibility of the decision rule.
-
-Returning to our example, a light drinker using this decision rule would follow the account through from their position in the game tree, correctly inferring that the outcome in their case would be positive.
-\subsection{Agent Models}
-\label{sub:the_agents}
-
-While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same output - a decision, we limit ourselves here to four.
-The simplest is a lexicographic rule (1), in the spirit of a \acl{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule \cite{Tversky1992}.
-Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-output characteristics.
-
-Agents have perfect recall, midwives recognise women if they repeatedly encounter them, making use of new information for retrospective updates.
-However, all four agent models make decisions `as-if' they were always facing a new \enquote{opponent}.
-
-A simplifying assumption is made that all midwives have just qualified after receiving identical training.
-As a result, they have homogeneous beliefs about  women and assume to some extent that they are honest.
-Women have heterogeneous beliefs, which correspond to experiencing \(k\) randomly chosen paths through the game, and following each path at least once.
-
-\subsubsection{Lexicographic Heuristic}
-\label{sub:lexico}
-
-The lexicographic heuristic (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified problem representation, where an action is a choice between combined lotteries.
-Functionally, the heuristic maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e.
-one reason decision making.
-Where there is no clear best action, but one or more is evidently worse, a choice must be made as to whether to discard the poorer action; in this case we have elected to retain it.
-This approach requires minimal computation, and does not assume that \(u_{i}\) is static, or known.
-
-Women resolve this by approximating the utility function, as a function \(f(s_{w}, \sigma)\) on their choice of signal and an unknown distribution $\sigma$, which maps to \(u_{w}\) - i.e.
-\(s_{w}\) is a choice between simple lotteries.
-The algorithm maintains a count, \(n\), of the number of occurrences of each outcome given the choice from \(s_{w}\).
-
-Midwives solve a slightly different problem with more information, where \(s_{w}\) is known, and \(s_{m}\) is the lottery choice - \(f(s_{w}, s_{m},\sigma)\).
-This is resolved by maintaining a separate count for each signal (i.e.
-\(n_{s_{w},s_{m}}\)), and otherwise following the same algorithm (\ref{alg:lexico}).
-
-\begin{algorithm}
-\begin{algorithmic}
-\State $n \gets 1, action \gets none$
-\While{$action = none$}
-\State Calculate the $n$th most common outcome following each action.
-\State Sort actions by the value of the $n$th most common outcome.
-\If{clear winner} \State $action \gets best$ \EndIf
-\State $n \gets n + 1$
-\EndWhile
-\State \Return action
-\end{algorithmic}
-\caption{Lexicographic heuristic\label{alg:lexico}}
-\end{algorithm}
-
-\subsubsection{Bayesian Payoff}
-
-The Bayesian payoff agent uses the same subset of information as the lexicographic method, but updates beliefs on the link between actions and payoffs using the Bayes rule, and attempts to choose the action which minimises risk.
-
-Given the discrete nature of actions and payoffs, coupled with a desire for tractability of the
-simulation, the Dirichlet distribution is employed as a prior to represent these beliefs. 
-The distribution is particularly convenient, in that to infer the
-probability of a signal implying a payoff is
-simply -
-
-\begin{equation}
-p(x=j|D,\alpha)=\frac{\alpha_{j}+n_{j}}{\sum_{j}(\alpha_{j}+n_{j})}\label{eq:posterior}
-\end{equation}
-
-Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), and \(\alpha_{i}\) is the pseudo-count of prior observations\footnote{Psuedo-counts are related to, but distinct from prior beliefs.
-Here, the psuedo-count is a parameter to the prior belief distribution and is nothing more than a hypothetical count of prior observations.} for a pair \(i\).
-Hence,
-the belief that a signal will lead to a payoff is the number
-of times that pairing has been observed (including the pseudo-count),
-over the total number of observations thus far. This makes computation
-of beliefs fast and simple, since all that must be maintained is
-a count of observations.
-As before, midwives follow a similar pattern but maintain \(n_{s_{w}}\) independent counts of pairings between referral choice and payoff, updating their beliefs about the relationship between the choice to refer and payoff given the signal they have received.
-
-Agents then choose the strategy $s_{i}$ to minimise risk $R_{i}$, which is simply defined as - 
-\begin{equation}
-R_{w}(s_{w}) = \sum_{x \in X} -xp(x | s_{w})
-\end{equation}
-\begin{equation}
-R_{m}(s_{w}, s_{m}) = \sum_{x \in X} -xp(x | s_{w}\wedge s_{m}),
-\end{equation}
-
-where $X$ is the set of payoffs the agent has observed to follow $s_{i}$.
-
-\subsubsection{Bayesian Risk Minimisation}
-
-The second Bayesian agent augments the reasoning of the simple payoff model, making the stronger assumption that the utility function is static, and known.
-Women maintain two sets of beliefs, corresponding respectively to \(p_{m}\), and the probability of referral given signal choice.
-This leads to the risk function, minimised with respect to \(s_{w}\) -
-
-\begin{equation}
-R_{w}(s_{w}, \theta_{w}) = \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, \theta_{w}, j)p(j)p(i | s_{w}),
-\end{equation}
-
-so that the risk of a signal is the sum of the products of all payoffs with the probabilities of their entailed midwife types and responses.
-
-Midwives reasoning centres on determining the meaning of signals, since given the knowledge of what some signal \(s_{w}\) conveys about the true type of the sender, the payoff for an action is known.
-As such, their inference process is the same as for the simple Bayesian agent but over signal-type pairs, and they attempt to minimise the following risk function, minimised with respect to \(s_{m}\) -
-
-\begin{equation}
-R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{m}(s_{w}, s_{m}, i)p(i | s_{w})
-\end{equation}
-
-\subsubsection{Descriptive Decision Theory}
-
-The most complex decision rule used is \ac{CPT}, which attempts to reproduce a number of systematic deviations from rationality observed in humans.
-Rather than risk, `prospects', the sequence of payoff-probability pairings in ascending order of payoff, associated with an action  are used as decision criteria.
-While \ac{CPT} has primarily been applied in the context of decisions from description, it has been modified to deal with decisions from experience by incorporating a first stage where probabilities are estimates from observations \cite{FoxCPT}.
-In this instance the Bayesian inference process fills the first stage role.
-
-\ac{CPT} uses transformed probabilities, underweighting small probabilities, and overweighting large ones.
-This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and contrastingly low probabilities as impossible.
-The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains (eqn \ref{eqn:cpt_p_pos}) and losses (eqn \ref{eqn:cpt_p_neg}) -
-
-\begin{align}
-w^{+}(p) & = \frac{p^{\gamma}}{(p^{\gamma}+(1-p)^{\gamma})^{\frac{1}{\gamma}}}\label{eqn:cpt_p_pos}\\
-w^{-}(p) & = \frac{p^{\delta}}{(p^{\delta}+(1-p)^{\delta})^{\frac{1}{\delta}}}\label{eqn:cpt_p_neg},
-\end{align}
-
-where $p$ is the unweighted probability, and $\gamma$ and $\delta$
-are the weights for gain and loss probabilities respectively.
-Along similar lines, the values of losses and gains are transformed to reflect a tendency to regard a loss as more significant than a gain  -
-
-\begin{equation}
-v(u_{i})=\begin{cases}
-f(u_{i}),& \text{if}\, u_{i}>0\\
-0,& \text{if}\, u_{i}=0\\
-\lambda g(u_{i}),& \text{if}\, u_{i}<0
-\end{cases},
-\end{equation}
-
-where,
-
-\begin{equation}
-f(u_{i})=\begin{cases}
-u_{i}^{\alpha},& \text{if}\,\alpha>0\\
-\ln(u_{i}),& \text{if}\,\alpha=0\\
-1-(1+u_{i})^{\alpha},& \text{if}\,\alpha<0
-\end{cases}
-\end{equation}
-\begin{equation}
-g(u_{i})=\begin{cases}
--(-u_{i})^{\beta},& \text{if}\,\beta>0\\
--\ln(-u_{i}),& \text{if}\,\beta=0\\
-(1-u_{i})^{\beta}-1,& \text{if}\,\beta<0
-\end{cases},
-\end{equation}
-
-and $\alpha$, and $\beta$ are respectively the power of a gain,
-and a loss, and \(\lambda\) is a multiplier giving the aversion to loss.
-
-Finally, the transformed probabilities are used to construct decision weights, \(\pi^{+},\pi^{-}\) for losses and gains, where,
-
-\begin{equation}
-\pi_{n}^{+}=w^{+}(p_{n})
-\end{equation}
-\begin{equation}
-\pi_{-m}^{-}=w^{-}(p_{-m})
-\end{equation}
-\begin{equation}
-\pi_{i}^{+}=w^{+}(p_{i}+\ldots+p_{n}) - w^{+}(p_{i+1}+\ldots+p_{n}),0\leq i \leq n - 1
-\end{equation}
-\begin{equation}
-\pi_{i}^{-}=w^{-}(p_{-m}+\ldots+p_{i}) - w^{-}(p_{-m}+\ldots+p_{i-1}),1-m\leq i \leq 0
-\end{equation}
-
-The \ac{CPT} value of a single outcome prospect \(f=(u_{i};p_{i})\), is $v(u_{i})\pi^{+}(p_{i})$
-if $u_{i}\geq0$, and $v(u_{i})\pi^{-}(p_{i})$ otherwise. For any given action the \ac{CPT}
-value, \(V\) is the sum of the value of the prospects of that action, as
-in the Bayesian risk model, and the agent chooses the option which maximises this quantity. 
-\section{Method}
-\label{sec:method}
-
-This section provides details of experiments conducted to examine the ability of the model to reproduce qualitative trends reported in the midwifery literature by \citet{Alvik2006}, and \citet{Phillips2007}; as well as a global sensitivity analysis and construction of statistical emulators to explore, and contrast the response surfaces of the four decision rules.
-
-\subsection{Qualitative Trends}
-\label{sub:qt}
-
-Throughout this paper, parameters for the \ac{CPT} model were as used in \cite{Tversky1992} (table \ref{tab:qt_params}).
-While there has been significant work on determining appropriate parametrisation for the model (e.g.
-\cite{Neilson2002,Nilsson2011,Glockner2012}, and particularly \citet{Byrnes1999} and \citet{Booij2009} addressing risk aversion and gender), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work.
-For simplicity, it was assumed that all three drinking types are equally prevalent within the population, although results derived from \acl{ALSPAC} suggest that the reality is far more positive\footnote{95.5\% of women in the sample reported consumption at, or below, \ac{NICE} recommended safe levels.} \citep{Humphriss2013}.
-The scenario was biased towards disclosure as the better option by presuming a distribution of midwives strongly skewed towards non-judgemental types, with beliefs initially favouring honesty.
-Payoffs were as in table \ref{tab:Payoff-matrix}, which ensure that it is always strictly preferable to refer drinkers, and together with the initial belief that signals will be honest, not refer those claiming otherwise.
-
-Two key measures were used: the fraction of the subpopulation who had ever signalled honestly, and the proportion of the population who were referred.
-Both measures were taken after every round of play, and were taken relative to the agent's position in their sequence of appointments giving the probability of signalling honestly, or being referred having had a given number of appointments.
-
-\begin{table}[h!]
-\caption{Model parameters.} 
-\label{tab:qt_params}
-\begin{tabular} {lll}
-\hline\noalign{\smallskip}
-Name & Description & Value \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-\(n_{w}\) & Number of women & 1000 \\ 
-\(n_{m}\) & Number of midwives & 100 \\ 
-\(r_{m}\) & Number of appointments per midwife & 1000 \\ 
-\(r_{w}\) & Maximum number of appointments per woman & 12 \\ 
-Runs & Simulation runs & 1000 \\ 
-\(p_{w}(h)\) & Proportion of heavy drinkers & \(1/3\) \\ 
-\(p_{w}(m)\) & Proportion of moderate drinkers & \(1/3\) \\ 
-\(p_{w}(l)\) & Proportion of light drinkers & \(1/3\) \\ 
-\(p_{m}(h)\) & Proportion of harsh midwives & \(5/100\) \\ 
-\(p_{m}(m)\) & Proportion of moderate midwives & \(10/100\) \\ 
-\(p_{m}(l)\) & Proportion of non-judgemental midwives & \(85/100\) \\ 
-\(q_{w}\) & Probability of women sharing & 0. \\ 
-\(w_{w}\) & Weight of shared information for women & 0. \\ 
-\(q_{m}\) & Probability of midwives sharing & 0. \\ 
-\(w_{m}\) & Weight of shared information for midwives & 0. \\ 
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 10:1 \\ 
-\(\gamma\) & Probability weighting for gains  & 0.61 \\ 
-\(\delta\) & Probability weighting for losses &  0.69\\ 
-\(\alpha\) & Power for gains  & 0.88 \\ 
-\(\beta\) & Power for losses & 0.88 \\ 
-\(\lambda\) & Loss aversion &  2.25 \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examined the impact of simple social learning within the population of women (section \ref{sub:info_sharing}) on the robustness of these trends.
-The original experiment was repeated at \(q_{w},w_{w}\in \{0.25, 0.5, 0.75, 1 | q_{w}=w_{w}\}\), with 100 runs under each condition.
-
-\subsection{Global Sensitivity Analysis}
-\label{sub:sensitivity}
-
-In general, we have followed the example of \cite{Bijak2013b} for global sensitivity analysis of stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques.
-For this purpose the \ac{GEM-SA} software \citep{Kennedy} was used, which implements the \ac{BACCO} method developed by \citeauthor{Oakley2004} \citep{Oakley2002,Oakley2004,Dorresteijn2010}.
-This is a form of variance-based sensitivity analysis, which assumes that the model output is an unknown, smooth function of the inputs.
-The unknown function can then be approximated as a Gaussian Process, which is fitted to the training data using Bayes' Theorem and then serves as an emulator for the simulator.
-The emulator is then able to provide an indication about the extent to which uncertainty in a parameter propagates to uncertainty in the output, and how sharply the output responds to change in each parameter.
-
-\begin{comment}
-
-Justification for doing SA, point out the wide variety of places this gets used. Talk about uncertainty, briefly raise model discrepancy.
-
-\end{comment}
-
-Parameters for training were generated in R \citep{RTeam2014} using and appropriately transformed Latin Hypercube Sample \citep{Carnell2012} over the space of parameters given in table \ref{tab:sa_params}, giving eleven free parameters which were treated as uniformly distributed in the range given.
-Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each, with emulator quality assessed by leave-one-out cross validation.
-A fixed set of 100 random seeds was used\footnote{Fixed random seeds were used to allow simulation results to be reproducible, since the combination of a parameter set and a random seed yields a deterministic process.}, such that each parameter set was run once with each seed, for every decision rule.
-
-\begin{table}
-\caption{Parameter ranges.}
-\label{tab:sa_params}
-\begin{tabular} {llll}
-\hline\noalign{\smallskip}
-Name & Description & Min & Max \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-\(p_{w}(m)\) & Proportion of moderate drinkers & 0 & 1 \\ 
-\(p_{w}(l)\) & Proportion of light drinkers & 0 & 1 \\ 
-\(p_{m}(m)\) & Proportion of moderate midwives & 0 & 1 \\ 
-\(p_{m}(l)\) & Proportion of non-judgemental midwives & 0 & 1 \\ 
-\(q_{w}\) & Probability of women sharing & 0 & 1 \\ 
-\(w_{w}\) & Weight of shared information for women & 0 & 1 \\ 
-\(q_{m}\) & Probability of midwives sharing & 0 & 1 \\ 
-\(w_{m}\) & Weight of shared information for midwives & 0 & 1 \\ 
-\(x_{h}\) & Health payoff for healthy delivery & 1 & 100 \\ 
-\(x_{r}\) & Cost for referral & \multicolumn{2}{l}{\(-(x_{h} - 1)\)} \\ 
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 1:1 & 100:1 \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-To capture the response characteristics for the model, we measured four outcome variables - (1) the \ac{IQR} of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3, 4) the \ac{IQR} of 1 \& 2 between simulation runs.
-Together these four metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the variability of the system in response to changes to the parameters (3 \& 4).
-
-Measurements were taken at the end of 1000 rounds of play, and emulators were built against 400 sample points from the full set of simulation results (1 \& 2), and the \ac{IQR} at each point (3 \& 4) to assess both the overall trend, and the extent to which the parameters contribute to variance between runs.
-
-Sixteen emulators were built, covering each of the four outputs on all decision models and used to conduct a probabilistic sensitivity analysis to assess the impact of parameters and interactions.
-
-In addition to the sensitivity analysis, we also employed the resulting emulators to rapidly\footnote{Once constructed, the emulator has an analytical solution conditional on the roughness parameters, which obviates the need to use MCMC.} explore the parameter space.
-While emulated results are subject to inaccuracy, they do provide an indication of the interest, and plausibility, of regions of the parameter space.
-Results for the outcomes of the interactions of \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) with \(x_{h}\), and \(q_{w}\) with \(w_{w}\) are given in section \ref{sub:sa_results}.
-\section{Results}
-\label{sec:results}
-
-\subsection{Qualitative Trends}
-\label{sub:qt_results}
-
-As shown in figure \ref{fig:honest_signals}, all four decision rules were able to reproduce both qualitative trends towards more disclosure as women experience more appointments \citep{Phillips2007}, and a greater tendency towards underreporting of consumption by heavier drinkers \citep{Alvik2006}.
-Trends for all four rules are broadly similar, exhibiting a gradual increase across appointments which subsequently levels off.
-This levelling can in part be explained by the referral results (see figure \ref{fig:ref_plot} in appendix \ref{app:additional_figures}), which show that the majority of drinkers are referred, even with substantial concealment.
-Referrals continue to occur, in the absence of honest signals, because drinkers are able to achieve a referral by masquerading as higher or lower types, dependent on how their initial beliefs are biased.
-Despite this the results suggest that a minority of risky drinkers will evade detection altogether, with no notable distinction between heavy and moderate types.
-Under these parameters, light drinkers always signal honestly and are never referred since there is no perceived advantage in doing so, and the evidence of deceptive signalling is insufficient to outweigh the biased priors of the midwives.
-
-\begin{figure}[H]
-\includegraphics[width=100mm]{figures/honesty_plot}
-\caption{Average fraction of population ever signalled honestly by each appointment, after 1000 rounds, mean with 95\% confidence limit over 1000 runs.
-Note that the large number of runs leads to very tight confidence intervals.\label{fig:honest_signals}}
-\end{figure}
-
-\subsection{Social Learning}
-\label{sub:sharing_results}
-
-Introducing social learning amongst women leads the behaviour of the decision rules to diverge markedly, which we explore possible reasons for in section \ref{sec:discussion}.
-Figure \ref{fig:honest_sharing} shows the proportion of women who have signalled honestly at least once by their final appointment, under four sharing conditions.
-
-\begin{figure}[H]
-\includegraphics[width=100mm]{figures/honesty_sharing}
-\caption{Impact of social learning on trends in the average fraction of population ever signalled honestly by their final appointment, after 1000 rounds, mean with 95\% confidence interval over 100 runs}
-\label{fig:honest_sharing}
-\end{figure}
-
-Aside from the lexicographic decision rule, the general tendency is towards less honest signalling by heavy drinkers, which is accompanied by a slight increase in referrals for the Bayesian, and \ac{CPT} rules.
-For these decision models, this is because social learning exacerbates the existing tendency of heavy drinkers to impersonate moderate drinkers, who behave more honestly as heavy drinkers become less so.
-This arises because both classes of agent learn that the moderate signal is the lower risk option as it is both a reliable indicator of need, and does not attract strongly negative judgement.
-The reliability of the signal is self reinforcing, since the more the agents use it and get referred, the more confident midwives become that it indicates need.
-
-Particularly notable, is the decline in honest signalling by light drinkers visible in both heuristic type rules at the 0.25 level of \(q_{w}\) \& \(w_{w}\), which is associated with an increase in false positives.
-This arises because of the lack of homophily in social learning, as light drinkers become informed about negative outcomes associated with concealment, despite having nothing to conceal.
-The relatively high referral rates of drinkers heighten the effect further, because shared information becomes dominated by their experiences.
-
-The relationship is not, however, entirely straightforward, in that increasing social learning leads to greater variance between runs.
-A linear model was used to predict the between-runs interquartile range of the average signal sent by moderate drinkers.
-The predictors used were decision rule, and level of social learning, together with the interaction between the two.
-The regression results were significant (\(F_{7,12}=25,p<2.9\times10^{-6}\)) with \(R^2=94\%\), and intercept 0.07.
-The only significant coefficients were for the interaction terms, which were 0.44 (\(p<0.05\)) for the Bayesian payoff rule, and 0.69 (\(p<0.005\)) for the lexicographic.
-This suggests that social learning, for the heuristic style decision rules introduces considerable uncertainty to the model, which is explored further in the sensitivity analysis below.
-
-\subsection{Sensitivity Analysis}
-\label{sub:sa_results}
-
-In this section we present a brief overview of the sensitivity analysis, followed by selected results highlighting the global effect of changes to perceived payoffs and degree of bias towards honesty, as well as social learning within women.
-The full results for the sensitivity analysis covering all sixteen emulators are available in appendix \ref{app:sensitivity_results}.
-
-\begin{figure}[H]
-\includegraphics[width=90mm]{figures/sharing_emulated_simulated}
-\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules, with signals coded as 0 = light, 1 = moderate, and 2 = heavy.}
-\label{fig:outcome_plots}
-\end{figure}
-
-For the median signal choice of moderate drinkers, the results of the sensitivity analysis suggest that the proportion of light drinkers has a significant effect for all decision rules, accounting for 10\%, 38\%, 24\%, and 5\% of the variance in output for the Lexicographic, Bayesian Payoff, Bayesian, and \ac{CPT} rules respectively.
-For the Lexicographic rule, the overwhelming majority of variance in signalling behaviour is reflective of the prevalence of stigmatisation by midwives (44\% \(p_{m}(m)\), 7\% \(p_{l}(m)\), and a further 15\% for their interaction).
-The proportions of midwives are also key drivers in group separation, and the between run IQR of both measures for this rule.
-
-Perhaps surprisingly, variance attributable to social learning between midwives is relatively low, with neither the weight nor probability accounting for more than 5\% of variance in any measure.
-While there are small contributions to variance in interaction with other parameters (e.g.
-4\% to between groups IQR, for the interaction with the proportion of light drinkers under the Bayesian rule), this may suggest that the model is lacking in this area, which we touch on in section \ref{sec:conclusion}.
-
-Figure \ref{fig:outcome_plots} gives a qualitative picture of both emulator quality, and the divergent response surfaces of the decision rules in response to variations in social learning parameters.
-Emulator fit is clearly imperfect, but overall behaviour is qualitatively similar, with both emulated and simulated plots demonstrating separation in outcome space for the decision rules.
-
-\begin{figure}[H]
-\includegraphics[width=100mm]{figures/unfixed_emu_sig_iqr}
-\caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\)}
-\label{fig:emulated_sharing_iqr}
-\end{figure}
-
-Following from the suggestive results for social learning introducing uncertainty (section \ref{sub:sharing_results}), figure \ref{fig:emulated_sharing_iqr} shows emulated points covering the parameter space in high resolution.
-These plots reflect the increase in uncertainty of outcome shown for the heuristic type rules, which is especially severe for the Bayesian payoff rule.
-They also suggest that the Bayesian decision rule is less stable under conditions where the weight of shared information is substantially higher than the probability of sharing.
-This indicates that placing a high weight on information from limited sources leads to greater variability, i.e.
-what information is shared, matters.
-
-\begin{figure}[H]
-\includegraphics[width=100mm]{figures/unfixed_emu_payoff_honesty_group_iqr}
-\caption{Emulated between groups IQR in response to varying \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\), and \(x_{h}\)}
-\label{fig:emulated_payoff_group_iqr}
-\end{figure}
-
-For the \ac{CPT}, and Bayesian decision models, the interaction of bias towards honesty, and distinction between payoffs has a significant, and non-linear effect on instability, and separability of groups.
-Figure \ref{fig:emulated_payoff_group_iqr} shows the effects, and also highlights the tendency towards poor separability of groups for both the heuristic type decision rules.
-The response surface of the Bayesian payoff rule is slightly more nuanced than the simple Lexicographic rule.
-Figure \ref{fig:emulated_payoff_group_iqr} shows better separation, close to partial pooling\footnote{Pooling occurs when signallers of different types `pool' their signals, and one adopts the signals of another.} at high payoff distinction, with relatively modest honesty bias, which is reflected by the variance contributions of 11\% and 8\% respectively.
-For the more complex rules, the general tendency is towards less pooling for higher values of both, but with pockets where full pooling\footnote{Indicating that all signaller types are using a the same signal.} occurs.
-The plots also suggest that the sensitivity of the \ac{CPT} rule is marginally greater, which is supported by the significant contribution to variance of close to 15\% for all measures of \(x_{h}\).
-
-\section{Discussion}
-\label{sec:discussion}
-
-From a pragmatic perspective, the differing response characteristics of the classes decision rules are substantial and significant, particularly when social learning is considered.
-There is a high level of uncertainty in the overall dynamics with the model free rules.
-This does not arise with the more complex rules, because they reframe information from others in the context of their own experiences, as what would happen to them in that situation.
-By contrast, the simpler rules treat the experiences as having literally happened to them, and since there is no mechanism of homophily, no way to listen only to accounts of agents similar to themselves, they can come to believe unreasonable things.
-Naturally, incorporating homophily, by, for example weighting shared information by the type of the sharer, would represent a trivial modification to the heuristic models.
-While to some extent this highlights the flexibility of the decision rule approach, it would of course sacrifice the parsimony of the model.
-This is an important consideration, given that part of the argument in favour of a decision theoretic approach lies in the minimal nature of the behavioural rules.
-
-One of the notable features of the results is that the behaviour of rules within a class is very similar.
-To some extent this reflects poorly on the most complex rule, \ac{CPT}, which diverges only minimally in behaviour from the Bayesian model.
-This might be to a degree anticipated since we have not elicited payoffs for obvious practical and ethical reasons, and they may be unrealistic, which limits the utility of the \ac{CPT} approach.
-Additionally, work by \citet{Glockner2012} has shown that there is considerable variation in individual parameters for the decision model, whereas we have let them remain homogeneous here.
-In the same vein, utility functions should arguably vary between individual agents, which could potentially be addressed by replacing the fixed payoffs used here with a distribution.
-With this said, the significant increase in complexity, which entails both additional parameters and increases to simulation time may auger for a middle ground, particularly where elicitation of payoffs is impractical.
-This, together with the variability associated with the heuristic type decision rules speaks to a trade off between capturing reality, and replicating it.
-
-Continuing the discussion of the issues raised by the representation of payoffs, the temporal aspect is significant, in that there is a timing difference in payoffs, since while the potential social pain of disclosure is immediate, the health outcome comes only later.
-In light of this, that there is a known impact of time on perceived utility \citet{Thaler1981} suggests that incorporating some form of temporal discounting (e.g.
-exponential \citep{Samuelson1937}, or hyperbolic \citep{Ainslie1991}), or a decision model which explicitly treats intertemporal choice, such as the \ac{CPT}-like model of \citet{Loewenstein1992}, is warranted.
-
-As noted in section \ref{sub:sensitivity}, the impact of social learning in midwives is surprisingly minimal, where it might be expected to play a more significant role in reality.
-A possible explanation for this lies in the implementation, which may place an excessive constraint on how much information midwives can share.
-The restriction to sharing only after a referral, together with the disparity in population sizes, and random allocation of appointments leads to midwives rarely having more than a single interaction with woman to pass on to their colleagues.
-Furthermore, because midwives are only informed of the true type if a referral occurs, they have an inherent myopia since until they have evidence of deception they will not refer, with said evidence difficult to obtain without a referral.
-
-In reality it might be anticipated that midwives would not withhold judgement, and would pass on concerns about specific women to their colleagues, or that particularly dramatic stories would persist and be passed.
-This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared and more sophisticated model of information flow in general.
-This also highlights an advantage of the \ac{BACCO} approach (which we describe in section \ref{sub:sensitivity}), in diagnosing issues with model design by giving insight into parameters which are contributing inappropriately to variance in output.
-Coupled with the ability of emulators to rapidly explore parameter space, this clearly suggests that statistical emulation is a powerful tool to support simulation based approaches.
-As noted in section \ref{sub:sa_results} the emulators here are indicative, but not definitive.
-Amongst the reasons discrepancy arises here are heteroskedasticity associated with social learning, the stochastic nature of the simulation, and a lack of precision given the large parameter range.
-The former issues could be addressed by a more comprehensive approach to setting the nugget, which explicitly incorporates point variance.
-The latter could be improved through iterative fitting procedures, where the simulation is sampled more heavily in plausible regions of parameter space, a procedure not possible here given the dearth of data to evaluate plausibility.
-That the discrepancy exists is not prohibitive in this instance, since we are not using the emulator for prediction, only to achieve a broad strokes picture of the behaviour of the simulator.
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-The conclusions that can be drawn about the behaviours of real life women, and their midwives, are necessarily limited by the paucity of data available to validate the model.
-While qualitative trends offer some indication, they are limited in scope, and do not permit strong claims about the drivers of disclosure.
-As such, further work will focus on applying the model to domains where validation data is more available, which will support a more comprehensive evaluation of the model discrepancy.
-With this said, the trends reported by \citet{Alvik2006}, and \citet{Phillips2007} are borne out by the model, and predictions from the two more complex rules suggest that encouraging information sharing between women may encourage disclosure, but at the expense of reducing accuracy.
-By contrast, if one takes the view that a Lexicographic model is a better approximation of real behaviour, then outcomes can best be influenced by controlling how far midwives punish their women socially.
-We would however suggest that there are better reasons than the outputs of a simulation for doing so.
-
-More broadly, the results demonstrate the logistical feasibility, and its utility as a `tool for thinking', of an agent model grounded in decision theory.
-The results also make clear that deciding the operationalisation of the decision making is of key significance.
-
- % Disclosure is a widely applicable issue in health and social care and beyond, with examples ranging from a lack of help seeking behaviour noted in older men \citep{Smith2007a}, to the inverse scenario of innapropriate disclosure in social media \citep{christofides2009information}.
- \section*{Acknowledgements}
-\label{sec:acknowledgements}
-
-This work was supported by the Engineering and Physical Sciences Research Council 
-(EPSRC) grant EP/H021698/1 Care Life Cycle, funded within the Complexity 
-Science in the Real World theme.
-The authors also gratefully acknowledge the use of the IRIDIS High Performance Computing Facility, and associated support services at the University of Southampton, in the completion of this work.
-\bibliography{library,library_addendum}
-\bibliographystyle{spbasic}
-\section{Disclosure Game Model Development}
-\label{app:model_description}
-
-This appendix provides a more in depth exploration of the model development process, beginning by deriving a game to serve as the basis for the model, and decision problems.
-
-A game, in the game theoretic sense, can be any interaction where the result for one person is dependent on the actions of another.
-In this scenario, the result for the woman would seem dependent on whether the midwife chooses to refer her for specialist support (although naturally the reality can only be thought of in terms of risk mitigation), and conversely, the right choice for the midwife is somewhat contingent on what the woman is willing to tell them.
-
-A very simple way to represent this would be a game with two players, who both have two possible moves - ask for help, or not; and refer, or not (fig \ref{fig:simplest_game}).
-Since both parties are invested in the outcome of the pregnancy, we might allow them to share the same payoff if everything ends well.
-
-\begin{figure}[H]
-\sidecaption
-\includegraphics[width=7cm]{figures/simplest_game}
-\caption{A very simple two player game.
-The only time things in this very restricted world obviously end poorly, is if the woman asks for help but does not get any.
-This implies that a rational player would always refer if asked for help, and is indifferent otherwise - in other words, there are three possible Nash equilibriums\protect\footnotemark.}
-\label{fig:simplest_game}
-\end{figure}
-
-\footnotetext{A Nash equilibrium is a solution to a game between two or more players, where no player can gain from changing their move.}
-
-The first complication, is that there should be differentiation between referring, and doing nothing because specialist treatment incurs a cost.
-We can modify the payoffs to reflect this, by reducing the midwife's payoffs when they refer.
-If the cost of referring is less than the value of a good outcome, then the effect of this is to make the only rational choice when not asked for help is to do nothing.
-
-This simple game is however not very informative, and clearly neglects much of the nuance of the scenario.
-The wider difficulty here is that the real outcome depends on an attribute of one of the players, rather than their moves.
-In this case, we would expect the right choices to depend on the alcohol consumption of the woman, rather than entirely on what she has claimed about it.
-To reflect this, we would need different variations on the same game to reflect this attribute.
-
-To resolve this, we can do exactly that, and cast it as a signalling game (fig \ref{fig:less_simple}), with three types of player, corresponding to categories of drinking behaviour (light, moderate, and heavy).
-Each of these types of player, will play a different game.
-This also introduces a third player, who we will call nature.
-Nature takes the first move, and decides the type of the woman according to some probability distribution; in this case we will allow the probability of types to be uniform.
-This changes the dynamics of play substantially, since the midwife can no longer be certain of which game they are playing, and hence which move yields the best outcome.
-We must also amend the moves, and payoffs slightly.
-The woman now claims to be one of the types, and may send a signal to say, for example, that she a heavy drinker.
-We will also modify the common payoffs to allow light drinkers to get the best outcome no matter what, and moderate and heavy types to get the best outcome only if referred.
-We can also differentiate between the consequences of not getting help for these types by letting heavy drinkers have a very negative outcome, and moderate drinkers a slight one.
-
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{figures/less_simplest_game}
-\caption{A less simple two player signalling game. }
-
-\label{fig:less_simple}
-\end{figure}
-
-At this point, the game becomes challenging to analyse from a Nash equilibrium perspective (there are several hundred).
-But, having raised to issue of stigma, we would also like incorporate this in the game.
-A possible approach to this is similar to the drinking behaviour of the women, and lets midwives have a type as well, corresponding to how judgemental they are when receiving signals: non-judgemental, moderately judgemental, and harshly judgemental.
-The expression of this judgement is not a matter of choice on their part, and is assumed to have no impact on their clinical response.
-Nature now has an additional move, to choose the type of the midwife, and we add costs for sending moderate and heavy signals.
-A heavy signal to a harshly judgemental midwife adds a heavy cost, and a moderate cost from a moderate midwife.
-The resulting game might reasonably be said to be intractable.
-
-At this juncture, we do not gain much further from the game representation, and instead separate it into multiple decision problems.
-
-Breaking the game down into separate decision problems can be achieved by treating the moves of the other players as a chance node, and omitting moves by nature that are known to them.
-For women, there are two such nodes, corresponding to the move by nature determining the type of midwife they play against, and the midwife's action.
-Midwives have simpler problem with only a single chance node, because the woman's move is known to them.
-Figure \ref{fig:decision_problems} shows the structure of the resulting decision problems.
-Note that there are in fact three distinct decision problems for the three types of woman, since the move by nature determining their type is known to them.
-
-\begin{figure}[H]
-\subfloat[Women (heavy drinkers)]{\includegraphics[width=11.9cm]{figures/women_influence}}
-\vskip\baselineskip
-\subfloat[Midwives]{\includegraphics[width=11.9cm]{figures/mw_influence}}
-\caption{Influence diagrams, showing the game broken into two decision problems. Squares indicate a decision node, while circles are (from the perspective of the agent) chance nodes}
-
-\label{fig:decision_problems}
-\end{figure}
-
-The precise structure of the decision problem is to some extent dependent on the decision rule in use, for example the Lexicographic heuristic rule is concerned only with a direct relationship between action and consequence.
-However, the literal translation from game to decision problem for women yields two chance nodes.
-As a result, solving this using the heuristic approach requires that the nodes be combined.
-By the same token, an arbitrarily complex problem could be resolved by rules without this limitation.
-This is significant, in that the decision problem is an individual agent's model of the situation, which might not be expected to correspond perfectly with the true sequence of events.
-
-From this position, simulating play, and augmenting the basic conjecture is easily achievable, since together the game, and the decision rules specify the basis for a simulation model.
-In the disclosure game case, we make additional stipulations on how many games agents play, order of play, the circumstances under which agents observe true types, and the structure of agent populations amongst others.
-\section{Simulation Schedule}
-\label{app:sim_schedule}
-
-In this section we give the step by step process for a single run of the disclosure game simulation.
-
-\begin{enumerate}
-\item Generate 1000 women, and place them in a queue
-\item Generate 100 midwives.
-\item For each round of the game
-\begin{enumerate}
-	\item Take 100 women from the queue
-	\item Pair each one with a random midwife
-	\item For each pair
-	\begin{enumerate}
-		\item The woman sends a signal
-		\item The midwife refers or not based on the signal
-		\item The woman is informed of her payoff, the midwife's type, and whether she is referred
-		\item The woman updates her beliefs
-		\item The midwife stores the game in their memory
-		\item If the woman is referred
-		\begin{enumerate}
-			\item The midwife is informed of the woman's true type
-			\item The midwife retrospectively updates their beliefs using the true type, and memories of any games with this woman
-			\item The midwife is now eligible to share their memories of games with this woman
-		\end{enumerate}
-	\end{enumerate}
-	\item Women who have not been referred or had their baby, join the back of the queue
-	\item New women are generated to replace those referred, or delivered
-	\item The new women are added to the back of the queue
-	\item For each referred or birthed woman
-	\begin{enumerate}
-		\item With probability p, her memory of games is shared with the active women
-		\item She is removed from simulation
-	\end{enumerate}
-	\item The active women update their beliefs
-	\item For each midwife with information to share
-	\begin{enumerate}
-		\item With probability p, their memory of games with the referred woman is shared
-		\item The memory is no longer eligible to be shared
-	\end{enumerate}
-	\item The midwives update their beliefs
-\end{enumerate}
-\end{enumerate} \section{Agent Examples}
-\label{sec:agent_eg}
-
-This section provides a worked example for the learning and decision process of each agent model, focusing on the behaviour of the signalling agent.
-
-\subsection{Lexicographic Heuristic}
-\label{sub:lexico_eg}
-
-As an example, take a light drinker who has played three rounds with a succession of particularly judgemental midwives, signalling honestly in two and claiming to be a moderate drinker in one.
-The most common outcome of the honest signal was a payoff of 10, which is clearly preferable to the 9 gained by claiming to be moderate.
-On that basis, they choose to signal honestly.
-
-\subsection{Bayesian Payoff}
-\label{sub:payoff_eg}
-
-If we take our light drinker from the lexicographic case, and assume that they began with an uninformative prior.
-The 6 possible signal-payoffs pairings are then \([(l,10),(m,10),(h,10),(m,9),(h,9),(h,8)]\), with \(\alpha_{i}=1\) for all \(i\).
-After playing the three rounds, \(n_{l,10}=2\), and \(n_{m,9}=1\).
-
-The agent then evaluates \(R_{w}\) for each signal, e.g. for the light signal:
-
-\begin{equation*}
-\begin{aligned}
-X &= \{10\}\\
-R_{w}(l) &= \sum_{x \in X} -xp(x | l) = -10p(10 | l)\\
-R_{w}(l) &= -10(\frac{\alpha_{l,10}+n_{l,10}}{\sum_{j}(\alpha_{j}+n_{j})}) = -10(\frac{1+2}{1+2})\\
-R_{w}(l) &= -10(\frac{3}{3}) = -10
-\end{aligned}
-\end{equation*}
-
-and by the same method, \(R_{w}(m)=-9\frac{1}{3}\), and \(R_{w}(h)=-9\), concluding that signalling honestly is the best move.
-
-\subsection{Bayesian Risk Minimisation}
-\label{sub:bayes_eg}
-
-Returning to our example agent, under this model the type of the midwife becomes salient, hence \(n_{h}=3\), and \(n_{l,n}=2\), \(n_{m,n}=1\).
-Their prior beliefs remain uninformative, i.e.
-\(\alpha_{j} = 1, j \in \{l,m,h\}\), \(\alpha_{i,j}=1,i \in \{r,n\}, j \in \{l,m,h\}\).
-As before, the agent evaluates \(R_{w}\) for the three signals, and the process for the light signal is given below.
-
-\begin{equation*}
-\begin{aligned}
-R_{w}(l, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(l, i, l, j)p(j)p(i | l)\\
-R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l)\\
-&\phantom{{}=1}- u_{w}(l, r, l, m)p(m)p(r | l)- u_{w}(l, n, l, m)p(m)p(n | l)\\
-&\phantom{{}=1}- u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
-u_{w}(l, i, l, j) &= 10\\
-R_{w}(l, l) &= -10p(l)p(r | l) - 10p(l)p(n | l) - 10p(m)p(r | l) - 10p(m)p(n | l)\\
-&\phantom{{}=1} - 10p(h)p(r | l) - 10p(h)p(n | l)\\
-p(l) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
-p(m) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
-p(h) &= \frac{1 + 3}{1 + 1 + 1 + 3} = \frac{2}{3}\\
-p(r | l) &= \frac{1 + 0}{1 + 1 + 2} = \frac{1}{4}\\
-p(n | l) &= \frac{1 + 2}{1 + 1 + 2} = \frac{3}{4}\\
-R_{w}(l, l) &= -10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{2}{3} \cdot \frac{1}{4} - 10\cdot \frac{2}{3} \cdot \frac{3}{4}\\
-&= -10
-\end{aligned}
-\end{equation*}
-
-and similarly for moderate (\(R_{w}(m,l)=-9\frac{1}{3}\)), and heavy (\(R_{w}(h,l)=-8\frac{1}{2}\)) signals, once again concluding that honesty is the better option.
-
-\subsection{Descriptive Decision Theory}
-\label{sub:cpt_eg}
-
-Once again, we return to the light drinker example.
-The inferential aspects are identical with the more complex Bayesian risk minimisation algorithm, hence \(p(j)p(i | l)\), and \(u_{w}(l, i, l, j)\) remain the same, but the agent additionally calculates $v(u_{w}(l, i, l, j))w^{+}(p(j))w^{+}(p(i | l))$.
-For the \ac{CPT} parameters, the values are those originally given by \citet{Tversky1992} and used in the actual simulations which are given in table \ref{tab:cpt_params}.
-
-\begin{table}[H]
-\caption{\ac{CPT} parameters. \label{tab:cpt_params}}
-\begin{tabular}{llc}
-\hline
-Name & Description & Value \\ \hline
-\(\gamma\) & Probability weighting for gains  & 0.61 \\ \hline
-\(\delta\) & Probability weighting for losses &  0.69\\ \hline
-\(\alpha\) & Power for gains  & 0.88 \\ \hline
-\(\beta\) & Power for losses & 0.88 \\ \hline
-\(\lambda\) & Loss aversion &  2.25 \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{align*}
-\alpha &= 0.88\\
-\gamma &= 0.61\\
-p(l) &= \frac{1}{6}\\
-p(m) &= \frac{1}{6}\\
-p(h) &= \frac{2}{3}\\
-p(r | l) &= \frac{1}{4}\\
-p(n | l) &= \frac{3}{4}\\
-u_{w}(l, i, l, j) &= 10\\
-f&=(10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{6},10;\frac{1}{2})\\
-f^{+}&=f,f^{-}=()\\
-n &= 5\\
-v(u_{w}) &= f(u_{w}) = u_{w}^\alpha\\
-v(u_{w}) &= 10^{0.88} = 7.59\\
-\pi_{0}^{+}&=w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})\\
-&=w^{+}(1) - w^{+}(\frac{23}{24})\\
-&=0.19\\
-\pi_{1}^{+}&=w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})\\
-&=w^{+}(\frac{23}{24}) - w^{+}(\frac{5}{6})\\
-&= 0.17\\
-\pi_{2}^{+}&=w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(\frac{5}{6}) - w^{+}(\frac{19}{24})\\
-&= 0.04\\
-\pi_{3}^{+}&=w^{+}(\frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{6} + \frac{1}{2})=w^{+}(\frac{19}{24}) - w^{+}(\frac{2}{3})\\
-&= 0.09\\
-\pi_{4}^{+}&=w^{+}(\frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{2})=w^{+}(\frac{2}{3}) - w^{+}(\frac{1}{2})\\
-&= 0.09\\
-\pi_{5}^{+}&=w^{+}(\frac{1}{2})\\
-&= 0.42\\
-V(f) &= V(f^{+}) + V(f^{-}) = V(f^{+}) + 0\\
-V(f^{+}) &= \sum_{i}^{n}\pi_{i}^{+}(f^{+})v_{i}^{+}(f^{+}) = 7.59
-\end{align*}
-
-And as before, following the same process for moderate, and heavy signals which yields respectively 7.14, and 6.22, the agent chooses the higher valued action and sends an honest signal. 
-\section{Supplementary Figures}
-\label{app:additional_figures}
-
-\begin{figure}[H]
-\includegraphics[width=100mm]{figures/ref_plot}
-\caption{Average fraction of population referred by each appointment, after 1000 rounds, mean with 95\% confidence limit over 1000 runs.
-Note that the large number of runs leads to very tight confidence intervals.\label{fig:ref_plot}}
-\end{figure} \section{Sensitivity Analysis}
-\label{app:sensitivity_results}
-
-This section provides complete variance based sensitivity analysis results for the disclosure game model.
-Each subsection gives results for one simulation output under all four decision rules, with tables providing the percentage of overall variance attributable to the individual parameters, emulator quality statistics, and the 5 most significant interaction contributions to variance in the output.
-
-\subsection{Median Moderate Drinker Signalling}
-
-\begin{table}[H]
-\caption{Median moderate drinker signalling parameter sensitivity \label{tab:sa_results_sig}}
-\begin{tabular} {llllll}
-\hline\noalign{\smallskip}
-Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-\(p_{w}(m)\) & Proportion of moderate drinkers & 0.367 & 1.145 & 0.801 & 0.614 \\
-\(p_{w}(l)\) & Proportion of light drinkers & 10.080 & 37.750 & 23.968  & 5.137\\
-\(p_{m}(m)\) & Proportion of moderate midwives & 6.715 & 13.017 & 0.894 & 1.485\\
-\(p_{m}(l)\) & Proportion of non-judgemental midwives & 43.942 & 1.655 & 1.602 & 2.618 \\
-\(q_{w}\) & Probability of women sharing & 0.198 & 5.527 & 4.460 & 1.159 \\
-\(w_{w}\) & Weight of shared information for women & 0.355 & 13.025 & 2.716 & 0.888 \\
-\(q_{m}\) & Probability of midwives sharing & 0.145 & 0.667 & 0.368 & 0.157 \\
-\(w_{m}\) & Weight of shared information for midwives & 0.118 & 0.376 & 0.176 & 0.200 \\
-\(x_{h}\) & Health payoff for healthy delivery & 0.457 & 9.618 & 1.912 & 15.355 \\
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.140 & 7.537 & 10.427 & 7.795 \\
-Total & All parameters and two way interactions & 86.777 & 96.527 & 85.529 & 74.123 \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{Median moderate drinker signalling emulator statistics \label{tab:sa_emulator_sig}}
-\begin{tabular} {lllllll}
-\hline\noalign{\smallskip}
-Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-Lexicographic & 0.834 & 0.131 &  0.817 & 0.012 & 0.252 & 1.746 \\
-Bayesian Payoff & 1.667 & 0.475 &  0.662 & 0.003 & 0.181 & 3.12 \\
-Bayesian & 3.352 & 0.534 & 1.160 & 0.001 & 0.068 & 2.423 \\
-\ac{CPT} & 1.503 & 0.331 & 1.241 & 0.002 & 0.101 & 1.842 \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{Top 5 Interaction terms for \ac{CPT} decision rule. \label{tab:sa_interaction_prospect_sig}}
-\begin{tabular} {ll}
-\hline\noalign{\smallskip}
-Parameter & Variance \\ 
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-
-\(x_{h}\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 20.814\\
-\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 5.698\\
-\(p_{w}(l)\)*\(x_{h}\) & 2.895\\
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(w_{w}\) & 2.799\\
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(q_{m}\) & 1.686\\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{Top 5 Interaction terms for Bayesian decision rule. \label{tab:sa_interaction_sharing_sig}}
-\begin{tabular} {ll}
-\hline\noalign{\smallskip}
-Parameter & Variance \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 17.270\\
-\(p_{w}(l)\)*\(q_{m}\) & 6.054\\
-\(q_{m}\)*\(w_{w}\) & 3.814\\
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(q_{m}\) & 3.538\\
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(w_{w}\) & 3.084\\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{Top 5 Interaction terms for Lexicographic decision rule. \label{tab:sa_interaction_lexic_sig}}
-\begin{tabular} {ll}
-\hline\noalign{\smallskip}
-Parameter & Variance \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-\(p_{m}(l)\)*\(p_{m}(m)\) & 15.331\\
-\(p_{m}(m)\)*\(p_{w}(l)\) & 3.682\\
-\(p_{m}(l)\)*\(p_{w}(l)\) & 3.581\\
-\(p_{m}(m)\)*\(q_{m}\) & 0.349\\
-\(p_{m}(l)\)*\(q_{m}\) & 0.279\\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{Top 5 Interaction terms for Bayesian Payoff decision rule. \label{tab:sa_interaction_payoff_sig}}
-\begin{tabular} {ll}
-\hline\noalign{\smallskip}
-Parameter & Variance \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-\(p_{w}(l)\)*\(w_{w}\) & 4.045\\
-\(x_{h}\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 1.856\\
-\(p_{w}(l)\)*\(q_{m}\) & 1.231\\
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(q_{m}\) & 0.997\\
-\(q_{m}\)*\(w_{w}\) & 0.929\\ 
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\subsection{Median Between Groups IQR}
-
-\begin{table}[H]
-\caption{Median between groups IQR parameter sensitivity \label{tab:sa_results_iqr}}
-\begin{tabular} {llllll}
-\hline\noalign{\smallskip}
-Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-\(p_{w}(m)\) & Proportion of moderate drinkers & 0.327 & 0.688 & 0.457 & 0.586 \\
-\(p_{w}(l)\) & Proportion of light drinkers & 11.223 & 20.123 & 11.046 & 4.081 \\
-\(p_{m}(m)\) & Proportion of moderate midwives & 36.630 & 1.160 & 0.364 & 1.945 \\
-\(p_{m}(l)\) & Proportion of non-judgemental midwives & 6.228 & 4.487 & 0.0964 & 2.627\\
-\(q_{w}\) & Probability of women sharing & 0.498 & 0.235 & 2.537 & 1.812 \\
-\(w_{w}\) & Weight of shared information for women & 1.018 & 2.307 & 1.889 & 0.740 \\
-\(q_{m}\) & Probability of midwives sharing & 0.158 & 0.343 & 0.387 & 0.156 \\
-\(w_{m}\) & Weight of shared information for midwives & 0.076 & 0.973 & 0.125 & 0.213 \\
-\(x_{h}\) & Health payoff for healthy delivery & 0.317 & 10.960 & 3.305 & 16.493 \\
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 1.107 & 8.411 & 2.890 & 6.729 \\
-Total & All parameters and two way interactions & 81.702 & 83.693 & 47.449 & 71.032 \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{Median between groups IQR emulator statistics \label{tab:sa_emulator_iqr}}
-\begin{tabular} {lllllll}
-\hline\noalign{\smallskip}
-Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-Lexicographic & 0.930 & 0.240 & 0.249 & 0.002 & 0.040 & 1.832 \\
-Bayesian Payoff & 1.242 & 0.417 & 0.232 & 0.001 & 0.0034 & 2.308 \\
-Bayesian & 1.254 & 0.131 & 0.644 & 0.000 & 0.019 & 1.167 \\
-\ac{CPT} & 1.190 & 0.313 & 0.659 & 0.000 & 0.024 & 1.701 \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\begin{table}[h]
-\caption{Top 5 Interaction terms for \ac{CPT} decision rule.}
-\label{tab:sa_interaction_prospect_group_iqr}
-\begin{tabular} {ll}
-\hline\noalign{\smallskip}
-Parameter & Variance \\ 
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-
-\(x_{h}\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 19.551\\
-\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 3.838\\
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(w_{w}\) & 2.450\\
-\(p_{w}(l)\)*\(x_{h}\) & 2.337\\
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(q_{m}\) & 2.046\\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{Top 5 Interaction terms for Bayesian decision rule. \label{tab:sa_interaction_sharing_group_iqr}}
-\begin{tabular} {ll}
-\hline\noalign{\smallskip}
-Parameter & Variance \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(q_{m}\) & 4.284\\
-\(p_{w}(l)\)*\(q_{m}\) & 3.866\\
-\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 2.943\\
-\(x_{h}\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 2.680\\
-\(q_{m}\)*\(w_{w}\) & 2.282\\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{Top 5 Interaction terms for Lexicographic decision rule. \label{tab:sa_interaction_lexic_group_iqr}}
-\begin{tabular} {ll}
-\hline\noalign{\smallskip}
-Parameter & Variance \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-\(p_{m}(l)\)*\(p_{m}(m)\) & 12.046\\
-\(p_{m}(m)\)*\(p_{w}(l)\) & 5.054\\
-\(p_{m}(l)\)*\(p_{w}(l)\) & 3.005\\
-\(p_{m}(l)\)*\(w_{w}\) & 0.819\\
-\(p_{m}(m)\)*\(w_{w}\) & 0.757\\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{Top 5 Interaction terms for Bayesian Payoff decision rule. \label{tab:sa_interaction_payoff_group_iqr}}
-\begin{tabular} {ll}
-\hline\noalign{\smallskip}
-Parameter & Variance \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 12.883\\
-\(p_{w}(l)\)*\(w_{w}\) & 5.667\\
-\(p_{w}(l)\)*\(x_{h}\) & 2.447\\
-\(x_{h}\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 2.360\\
-\(p_{m}(m)\)*\(p_{w}(l)\) & 1.919\\ 
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\subsection{Median Moderate Drinker Signalling IQR}
-
-\begin{table}[H]
-\caption{IQR of median moderate drinker signalling parameter sensitivity \label{tab:sa_results_sig_iqr}}
-\begin{tabular} {llllll}
-\hline\noalign{\smallskip}
-Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-\(p_{w}(m)\) & Proportion of moderate drinkers & 0.428 & 9.828 & 3.816 & 2.068 \\
-\(p_{w}(l)\) & Proportion of light drinkers & 8.369 & 13.791 & 4.045 & 2.400 \\
-\(p_{m}(m)\) & Proportion of moderate midwives & 13.416 & 0.712 & 0.676 & 0.583 \\
-\(p_{m}(l)\) & Proportion of non-judgemental midwives & 21.079 & 0.648 & 0.659 & 0.373 \\
-\(q_{w}\) & Probability of women sharing & 2.307 & 3.481 & 0.891 & 0.600 \\
-\(w_{w}\) & Weight of shared information for women & 6.021 & 6.009 & 0.562 & 0.937 \\
-\(q_{m}\) & Probability of midwives sharing & 0.315 & 1.829 & 0.114 & 0.117 \\
-\(w_{m}\) & Weight of shared information for midwives & 1.652 & 1.354 & 0.260 & 0.0.139 \\
-\(x_{h}\) & Health payoff for healthy delivery & 0.253 & 0.612 & 4.889 & 15.146 \\
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.504 & 3.096 & 19.863 & 25.999 \\
-Total & All parameters and two way interactions & 84.9968 & 77.413 & 57.125 & 83.322 \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{IQR of median between groups IQR emulator statistics \label{tab:sa_emulator_sig_iqr}}
-\begin{tabular} {lllllll}
-\hline\noalign{\smallskip}
-Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-Lexicographic & 1.425 & 0.436 & 0.549 & 0.008 & 0.114 & 2.719 \\
-Bayesian Payoff & 1.223 & 0.496 & 0.747 & 0.012 & 0.207 & 2.034 \\
-Bayesian &  1.065 & 0.000 & 0.230 & 0.002 & 0.088 & 1.015 \\
-\ac{CPT} & 0.874 & 0.213 & 0.233 & 0.001 & 0.066 & 1.806 \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{Top 5 Interaction terms for \ac{CPT} decision rule. \label{tab:sa_interaction_prospect_sig_iqr}}
-\begin{tabular} {ll}
-\hline\noalign{\smallskip}
-Parameter & Variance \\ 
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-
-\(x_{h}\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 17.377\\
-\(p_{w}(m)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 3.356\\
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(w_{w}\) & 3.036\\
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(q_{m}\) & 2.067\\
-\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 1.721\\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{Top 5 Interaction terms for Bayesian decision rule. \label{tab:sa_interaction_sharing_sig_iqr}}
-\begin{tabular} {ll}
-\hline\noalign{\smallskip}
-Parameter & Variance \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-\(p_{w}(m)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 4.188\\
-\(x_{h}\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 3.120\\
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(q_{m}\) & 2.423\\
-\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 2.279\\
-\(p_{w}(l)\)*\(q_{m}\) & 1.489\\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{Top 5 Interaction terms for Lexicographic decision rule. \label{tab:sa_interaction_lexic_sig_iqr}}
-\begin{tabular} {ll}
-\hline\noalign{\smallskip}
-Parameter & Variance \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-\(p_{m}(m)\)*\(p_{w}(l)\) & 12.068\\
-\(p_{m}(l)\)*\(p_{w}(l)\) & 6.794\\
-\(p_{m}(l)\)*\(p_{m}(m)\) & 5.567\\
-\(p_{m}(m)\)*\(q_{m}\) & 0.886\\
-\(p_{m}(l)\)*\(q_{m}\) & 0.692\\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{Top 5 Interaction terms for Bayesian Payoff decision rule. \label{tab:sa_interaction_payoff_sig_iqr}}
-\begin{tabular} {ll}
-\hline\noalign{\smallskip}
-Parameter & Variance \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-\(p_{w}(l)\)*\(p_{w}(m)\) & 8.357\\
-\(p_{w}(l)\)*\(w_{w}\) & 7.431\\
-\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 4.882\\
-\(p_{w}(l)\)*\(q_{m}\) & 2.346\\
-\(p_{w}(l)\)*\(w_{m}\) & 2.025\\ 
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\subsection{Between Groups IQR IQR}
-
-\begin{table}[H]
-\caption{IQR of median between groups IQR parameter sensitivity \label{tab:sa_results_iqr_iqr}}
-\begin{tabular} {llllll}
-\hline\noalign{\smallskip}
-Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-\(p_{w}(m)\) & Proportion of moderate drinkers & 0.691 & 5.926 & 1.053 & 1.265 \\
-\(p_{w}(l)\) & Proportion of light drinkers & 3.664 & 17.047 & 4.877 & 3.656 \\
-\(p_{m}(m)\) & Proportion of moderate midwives & 41.369 & 1.124 & 0.814 & 0.591 \\
-\(p_{m}(l)\) & Proportion of non-judgemental midwives & 7.109 & 0.739 & 0.496 & 0.378 \\
-\(q_{w}\) & Probability of women sharing & 1.963 & 2.038 & 0.733 & 0.589 \\
-\(w_{w}\) & Weight of shared information for women & 7.932 & 11.193 & 2.289 & 1.960 \\
-\(q_{m}\) & Probability of midwives sharing & 0.413 & 1.972 & 0.267 & 0.069\\
-\(w_{m}\) & Weight of shared information for midwives & 0.120 & 2.902 & 0.150 & 0.123 \\
-\(x_{h}\) & Health payoff for healthy delivery & 0.228 & 3.190 & 6.308 & 14.777 \\
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 0.673 & 10.411 & 22.901 & 26.340 \\
-Total & All parameters and two way interactions & 85.740 & 88.611 & 68.640 & 84.210 \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{IQR of median between groups IQR emulator statistics \label{tab:sa_emulator_iqr_iqr}}
-\begin{tabular} {lllllll}
-\hline\noalign{\smallskip}
-Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-Lexicographic & 0.826 & 0.409 & 0.259 & 0.002 & 0.034 & 2.364 \\
-Bayesian Payoff & 3.202 & 0.520 & 0.328 & 0.002 & 0.032 & 2.452 \\
-Bayesian & 1.177 & 0.041 & 0.133 & 0.000 & 0.018 & 1.152 \\
-\ac{CPT} & 0.874 & 0.118 & 0.126 & 0.000 & 0.017 & 1.570 \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{Top 5 Interaction terms for \ac{CPT} decision rule. \label{tab:sa_interaction_prospect_group_iqr_iqr}}
-\begin{tabular} {ll}
-\hline\noalign{\smallskip}
-Parameter & Variance \\ 
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-
-\(x_{h}\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 18.626\\
-\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 3.312\\
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(w_{w}\) & 2.823\\
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(q_{m}\) & 2.694\\
-\(x_{h}\)*\(q_{m}\) & 1.022\\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{Top 5 Interaction terms for Bayesian decision rule. \label{tab:sa_interaction_sharing_group_iqr_iqr}}
-\begin{tabular} {ll}
-\hline\noalign{\smallskip}
-Parameter & Variance \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 7.947\\
-\(x_{h}\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 4.048\\
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\)*\(q_{m}\) & 3.134\\
-\(p_{w}(l)\)*\(q_{m}\) & 2.307\\
-\(p_{m}(m)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 2.232\\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{Top 5 Interaction terms for Lexicographic decision rule. \label{tab:sa_interaction_lexic_group_iqr_iqr}}
-\begin{tabular} {ll}
-\hline\noalign{\smallskip}
-Parameter & Variance \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-\(p_{m}(l)\)*\(p_{m}(m)\) & 8.659\\
-\(p_{m}(m)\)*\(p_{w}(l)\) & 3.726\\
-\(p_{m}(l)\)*\(p_{w}(l)\) & 3.237\\
-\(p_{m}(l)\)*\(w_{w}\) & 1.564\\
-\(p_{m}(m)\)*\(w_{w}\) & 1.558\\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-\begin{table}[H]
-\caption{Top 5 Interaction terms for Bayesian Payoff decision rule. \label{tab:sa_interaction_payoff_group_iqr_iqr}}
-\begin{tabular} {ll}
-\hline\noalign{\smallskip}
-Parameter & Variance \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-\(q_{m}\)*\(w_{w}\) & 3.830\\
-\(p_{w}(l)\)*\(p_{w}(m)\) & 3.808\\
-\(p_{w}(l)\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 3.401\\
-\(p_{w}(l)\)*\(q_{m}\) & 2.385\\
-\(x_{h}\)*\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & 2.294\\ 
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-\end{table}
-
-  \end{document}

### 2015-11-10 disclosure_game.tex
Cleaning up
Moving table caps
Finally fixed the tables
Build errors
Correct NICE acronym
Rewrite game theory -> decision theory bit
Rearrange payoff tables
To save some space
Additional figs
Tweaks
acronyms to own file

@@
 % \usepackage{hyperref}
- \usepackage{graphicx}
  \usepackage[subrefformat=parens,labelformat=simple,caption=false,labelfont={bf}]{subfig}
+%\usepackage{floatrow}
  \usepackage[nolist,smaller]{acronym}
- \usepackage{sidecap}
 % \usepackage{nomencl}
+\allowdisplaybreaks
 \makeindex
@@
 \begin{acronym}[ALSPAC]
-  \acro{FAS}{Foetal Alcohol Syndrome}
-  \acro{CPT}{Cumulative Prospect Theory}
-  \acro{PT}{Prospect Theory}
-  \acro{NICE}{National Institute for Health and Care Excellence}
-  \acro{IAPT}{Improving Access to Psychological Therapies}
-  \acro{CMACE}{Centre for Maternal and Child Enquiries}
-  \acroindefinite{CMACE}{the}{the}
-  \acro{AUDIT}{Alcohol Use Disorders Identification Test}
-  \acro{T-ACE}{Tolerance, Annoyance, Cut down, Eye-opener}
-  \acro{RCOG}{Royal College of Obstetricians and Gynecologists}
-  \acroindefinite{RCOG}{the}{the}
-  \acro{AML}{acute myeloid leukemia}
-  \acro{ADHD}{Attention Defecit Hyperactivity Disorder}
-  \acro{PND}{Postnatal Depression}
-  \acro{RCT}{randomised control trial}
-  \acro{WHO}{the World Health Organisation}
-  \acro{ESS}{Evolutionarily Stable Strategy}
-  \acrodefplural{ESS}[ESS]{Evolutionarily Stable Strategies}
-  \acro{MCMC}{Markov chain monte carlo methods}
-  \acro{DU}{Discounted Utility}
-  \acro{AIC}{Akaike information criterion}
-  \acro{ANOVA}{analysis of variance}
-  \acro{ALSPAC}{the Avon Longitudinal Study of Parents and Children}
-  \acro{GEM}{Gaussian Emulation Machine}
-  \acrodefplural{GEM}{Gaussian Emulation Machines}
-  \acro{GEM-SA}{Gaussian Emulation Machine for Sensitivity Analysis}
-  \acro{JIT}{Just-in-time}
-  \acro{ABM}{Agent Based Modelling}
-  \acro{ABMs}{Agent Based Models}
-  \acro{CPT}{Cumulative Prospect Theory}
-  \acro{FFH}{Fast and Frugal Heuristic}
-  \acro{OFC}{orbito-frontal cortex}
-  \acro{BACCO}{Bayesian Analysis of Computer Code Outputs}
-  \acro{IQR}{interquartile range}
+  \input{acronyms}
 \end{acronym}
@@
 
-%Assuming this is for JASSS.. Need to make background shorter.
-%Aim for ~ 7-8,000 words overall.
-
 \input{abstract_short}
@@
 %\input{Background}
-
+%\input{motivation}
 \input{Model}
@@
 \bibliographystyle{spbasic}
-\input{SensitivityAnalysis}
 \input{model_description}
@@
 \input{agent_examples}
+\input{add_figures}
+\input{SensitivityAnalysis}
 \end{document}

### 2015-11-10 Results.tex
Figures path

@@
 \begin{figure}[H]
-\includegraphics[width=100mm]{figures/honesty_plot}
+\includegraphics[width=100mm]{honesty_plot}
 \caption{Average fraction of population ever signalled honestly by each appointment, after 1000 rounds, mean with 95\% confidence limit over 1000 runs.
@@
 \begin{figure}[H]
-\includegraphics[width=100mm]{figures/honesty_sharing}
+\includegraphics[width=100mm]{honesty_sharing}
 \caption{Impact of social learning on trends in the average fraction of population ever signalled honestly by their final appointment, after 1000 rounds, mean with 95\% confidence interval over 100 runs}
@@
 \begin{figure}[H]
-\includegraphics[width=90mm]{figures/sharing_emulated_simulated}
+\includegraphics[width=90mm]{sharing_emulated_simulated}
 \caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules, with signals coded as 0 = light, 1 = moderate, and 2 = heavy.}
@@
 \begin{figure}[H]
-\includegraphics[width=100mm]{figures/unfixed_emu_sig_iqr}
+\includegraphics[width=100mm]{unfixed_emu_sig_iqr}
 \caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\)}
@@
 \begin{figure}[H]
-\includegraphics[width=100mm]{figures/unfixed_emu_payoff_honesty_group_iqr}
+\includegraphics[width=100mm]{unfixed_emu_payoff_honesty_group_iqr}
 \caption{Emulated between groups IQR in response to varying \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\), and \(x_{h}\)}

### 2015-11-12 Background.tex
Substantive background back in

--- 2015-06-04 Background.tex
@@
 %!TEX root = disclosure_game.tex
-%Rewrite all of this, ditch the alcohol stuff altogether. Any really key can be woven in elsewhere (discussion)
 \section{Previous Research}
@@
 
-This section presents a brief overview of previous work relating to the theoretical backdrop to this approach, addressing in turn signalling games, normative decision theory, heuristic decision making, and descriptive decision theory.
+This section presents a brief overview of literature focusing on the impact
+of drinking behaviour in pregnancy, and factors affecting disclosure
+behaviour in the midwifery context.
 
-\subsection{Signalling Games}
+\subsection{Alcohol, and Disclosure in the Maternity Setting}
+\label{sub:alcohol_disclosure}
 
-The majority of classical game theory focuses on strategic decision making, in scenarios where all players have complete information about all aspects of the game.
-An alternative, perhaps more common situation, is that players have incomplete information, i.e.
-their knowledge of the state of the world is in some way deficient.
-\citet{Harsanyi1967} introduced the concept of a Bayesian game, resolving the problems introduced by the incomplete information scenario by allowing the possible variations on the rules to be treated as subgames.
-This adds an additional player - nature, to the game, where nature takes the first move thereby deciding which subgame is played.
-Nature is assumed to make their move by lottery, and where the probability distribution governing the lottery is known to all players this permits the game to be formulated as one of complete information.
+\subsubsection{Impact of Alcohol\label{sub:Impact-of-Alcohol}}
 
-Here, we are specifically interested in signalling games \citep{Spence1973,Kreps1987}, where one player holds some private information which may be communicated (or not) by means of a signal.
-This basic form has been widely applied, with substantial interest in what conditions permit honest signalling as Nash equilibria or \acp{ESS}.
-\citet{Grafen1990}, following from a suggestion by \citet{Zahavi1975}, proposed that if signals intended to indicate mate quality exacted a cost on the signaller (e.g.
-peacock tail feathers), then honest signalling would constitute an \ac{ESS}.
-Similar results have also been demonstrated in a game of job market signalling, where signal cost was differentiated by type \citep{Spence1973}.
-Costly signalling has also been suggested as an explanation of behaviour that at first glance appears counter intuitive, for example \citet{Godfray1991} applied the idea to the food solicitation behaviour of chicks, where a stronger signal (i.e.
-more, or louder chirping) carries a risk of being eaten by predators.
-Moving beyond animal behaviour, \citet{Sosis2003} considered the implications of ritual behaviour, in the context of religion, representing a costly signal, an idea subsequently extended by \citet{Henrich2009} to include cultural transmission, and \citet{Wildman2011} to introduce group differentiation.
+Distinct from stigma attached to alcohol consumption in pregnancy,
+is the question of the real impact on woman and baby both in the \gls{antenatal}
+period, and beyond. While the canonical example of alcohol linked
+disorders is \ac{FAS}, and others on that spectrum, heavy drinking
+during pregnancy has been mooted as a factor in a variety of negative
+health outcomes.
 
-Other work augments the signalling game model, for example \citet{Austen-Smith2005} add a second `peer group' audience signalling game to the original \citeauthor{Spence1973} game in an effort to explain poor academic performance in some social groups, with some subsequent empirical support for the idea from \citet{Jr2010}.
-On a similar tack, \citet{Feltovich2002} introduce additional noisy type information, finding that this effectively explained counter-intuitive observed behaviour where actors with every right to boast of their quality fail to do so.
+The impact of moderate alcohol consumption in pregnancy is more contested.
+For example, \citet{Andersen2012} examined moderate drinking in a
+large Danish cohort study, finding a significant increase in the risk
+of spontaneous abortion at low levels of consumption early in pregnancy.
+\citet{Savitz2012} questioned the extent to which this can be interpreted
+as a causal connection, noting that there is a known relationship
+between absence of morning sickness, and spontaneous abortion, and
+suggesting that this may explain much of the difference in risk. \citet{Kesmodel2002}
+examined the relationship between alcohol consumption and still-birth,
+finding that increased consumption lead to an increase in risk to
+the baby, but in contrast to \citet{Andersen2012} this was significant
+at \gls{term}.
 
-\subsection{Normative Decision Theory}
+Considering longer term negative outcomes, a metastudy by \citet{Latino-Martel2010}
+examined the potential for maternal alcohol consumption in pregnancy
+to feature as a risk factor for onset of childhood leukaemia, finding
+that any alcohol consumption was associated with an increased risk
+of childhood \ac{AML}, but note the rarity of the condition as a
+limitation.
 
-While game theory addresses rational \emph{strategic} decision making, decision theory deals instead with rational decision making \citep{Peterson2009}.
-Taken literally, this leads to normative decision theory, where the focus is on giving the rational answer to a decision problem.
-A complementary view - descriptive, or behavioural decision theory, holds that the focus should instead be on giving an account of human decision making performance, complete with observed deviations from perfect rationality, which we address in section \ref{sub:descriptive_theories}.
-Finally a third perspective, which to some extent overlaps this division, suggests that decisions are heuristic in nature and rational in ecological context \citep{Gigerenzer1996} (section \ref{sub:heuristic_theories}).
+\citet{Huizink2006} reviewed literature looking at the impact of
+moderate consumption on neurodevelopmental and cognitive outcomes,
+concluding that maternal consumption can be a contributing factor
+to \ac{ADHD}, and impairments to learning and memory. They subsequently
+suggest that the underlying mechanism is not specific to alcohol consumption,
+but a more general phenomena arising from perturbations to foetal
+conditions \citep{Huizink2009}, but caution that methodological issues
+in many of the studies reviewed may undermine this hypothesis.
 
-The conceptual underpinning of all of these is the central idea of expected utility, originated by \citet{Bernoulli1954} and later formalised by \citet{Neumann1953}, which simply put, states that the worth of an action is the probability of each outcome, multiplied by the subjective gain or loss it delivers.
+Contrary to this, a meta-study by \citet{Gray2006} found there was
+insufficient evidence to suggest any harm arising from moderate (under
+1.5 UK units per day) alcohol consumption. This ties to the current
+guidance from the \ac{NICE} \citep{NICE2010a}, advising that women
+should avoid drinking at all in at least the first three months of
+pregnancy, and no more than 1-2 units once or twice a week if they
+do. In giving this advice, \ac{NICE} acknowledge that the risks to
+the foetus from alcohol are a somewhat contentious subject, concluding
+that the evidence of harm is inconclusive, but that this is not sufficient
+to rule out the risk of negative outcomes. This tension is reflected
+by earlier guidance from the \ac{RCOG} \citep{Gynecologists1996}
+suggesting no evidence of harm below 15 units per week, and subsequent
+criticism by \citet{Guerri1999}, who suggest that this might be interpreted
+as legitimising \gls{binge}, while noting several studies indicating
+adverse affects linked to even a single drink per day (e.g. \citet{Day1990}).
+A subsequent \ac{RCOG} statement \citep{RoyalCollegeofObstetriciansandGynaecologists2006}
+revised the recommendations to incorporate newer findings, advising
+that there is no known safe threshold for drinking in pregnancy, and
+highlighting binge drinking as of particular concern.
 
-Recently, several studies have explored biological correlates to aspects of expected utility.
-The fundamental concept, that all outcomes are comparable in a universal currency has been supported by evidence of neural correlates of decision variables \citep{Platt1999}, and following from this results from \citet{Padoa-Schioppa2006,Padoa-Schioppa2008} showing neuronal firing in the \ac{OFC} corresponding to revealed preferences in monkeys.
-Additionally, some support for neural representation of value, and risk aversion was found by \citet{Christopoulos2009}.
-The model presented in this paper makes an explicit assumption that social decisions utilise the same process, and while this is less well supported there is some evidence to suggest involvement by the same brain region, since damage to the \ac{OFC} has been shown to impair social judgements in both primates \citep{Watson2012}, and humans \citep{Willis2010}.
+There has recently been an increased interest in the impact of binge
+drinking, as a distinct pattern of consumption, with a wide variety
+of negative outcomes reported by \citet{Maier2001}, although a significant
+portion of their evidence base is drawn from animal studies which
+augers for caution in generalising findings to humans. \citet{Strandberg-larsen2008}
+explored links between binge drinking, and stillbirth, reporting a
+statistically significant increase in risk associated with more than
+three antenatal binge episodes. \citet{Sun2009} looked at seizure
+disorders in children whose mothers binged during pregnancy. They
+reported significantly greater risk of both neonatal seizures (\textasciitilde{}3
+fold) and epilepsy (1.81 fold) associated with binge drinking between
+11 and 16 weeks, but emphasised the exploratory nature of the results,
+and need for replication. In terms of neurodevelopmental outcomes,
+\citet{Streissguth1994} found a dose dependent association with scores
+on timed word, and arithmetic tests in fourteen year olds with a stronger
+association where bingeing occurred. A review by \citet{Henderson2007}
+cautiously supports the contention that binge drinking has a neurodevelopmental
+impact, but found no consistent support for adverse outcomes in pregnancy
+(e.g. stillbirth, miscarriage, etc.) and note a paucity of studies
+in the area. \citet{Meyer-Leu2011} considered the neonatal period,
+finding that both moderate and binge drinking were associated with
+an increased trend towards neonatal asphyxia. They also noted a large
+number of contradictory findings and raising methodological concerns
+about the studies reviewed by \citeauthor{Henderson2007}. \citet{Barr2006}
+contend that binge drinking may also contribute to psychiatric issues
+in the later life of offspring, although in this case their findings
+are confined to individuals with \ac{FAS}, which may in itself be
+a confounding factor, rather than indicating a directly causative
+relationship between antenatal binge drinking and subsequent psychiatric
+disorder in offspring.
 
-An alternative normative model of decision making is Bayesian decision theory, proposed by \citet{Robbins1964}, which is essentially the application of Bayesian style probabilities to the expected utility model.
-This allows probabilities used in reasoning to be subjective, which may allow for a better account of decisions from experience (see \citet{Hertwig2004,Hau2008} for results elucidating the distinction, and comparing the performance of several non-Bayesian models).
-This model has seen notable successes in practical problems \citep{McNamara1980,Kristensen1997,Survey2003}, but suggestions by several authors  that it could constitute an effective (top-down) model of learning \citep{Tenenbaum2006,Griffiths2010}, or induction \citep{Gallistel2012} in the brain have attracted substantial criticism\footnote{For example \citet{Bowers2012} responding to \citet{Tenenbaum2006}, and \citet{Griffiths2010}; and \citet{Miller2012} addressing \citet{Gallistel2012}.}.
+Overall, there is a distinct lack of consensus on what, and how extensive,
+the effects of drinking on the immediate and long term health outcomes
+are for the child.
 
-\subsection{Heuristic Decision Making}\label{sub:heuristic_theories}
+\subsubsection{Disclosure}
 
-As noted, heuristic decision making stems from a contention that \citeauthor{Neumann1953} type rationality ignores the context of decision making, and a lack of correspondence between predicted and actual human decisions (see, for example the Allais paradox \citep{Society2013}, and subsequent empirical support from \citet{Burke1996} and \citet{Oliver2003}).
-Arguably, this notion begins with \citet{Simon1956}, who suggested that humans do not attempt to make optimal choices, but to satisfice and choose the first `good enough' option.
-While noting that this will often achieve the same result, the claim is that humans exhibit bounded rationality \citep{Simon2000} arising from inherent limits to cognition.
+The issue of disclosure is central to the model presented here, in
+particular self-report by women of information that might disadvantage
+them, or be expected to do so in the immediate term. In general, the
+consensus is that alcohol self-reports have acceptable validity in
+the research context \citep{DelBoca2000}, but do not correspond perfectly
+to alternative methods. \citet{DelBoca2003} claim that the validity
+is generally accepted, and suggest that the current focus lies on
+what factors and processes underlie the discrepancies rather than
+questioning determining their existence. In this instance, the conjecture
+is that the information is in some way stigmatising; that, following
+\citet{Goffman1999}, disclosure equates to revelation of the mark.
+This is not immediately contentious, for example \citet{Gomberg1988}
+identified stigma surrounding alcohol abusing women in particular,
+an issue also highlighted by \ac{IAPT} guidance \citep{IAPT2012},
+as well as a number of other studies relating response effects to
+perceived negative consequences \citep{Langenbucher2001,DelBoca2000,Blair1977}.
+In the maternity context, \citet{Radcliffe2011} identifies stigma
+pertaining to substance misusing women amongst staff, and suggests
+that this may represent a barrier to appropriate treatment; similarly,
+\ac{NICE} guidance on pregnancy and complex social factors \citep{NICE2010}
+recognises concern about the attitude of staff as a source of anxiety
+in pregnant women who misuse substances.
 
-\citet{Gigerenzer1996} take the concept of bounded rationality further, and argue for what they term \acp{FFH}.
-This recasts rationality as bound to the context of the behaviour: a rational approach to choosing the right mate might well require checking every possible partner, but given finite time, memory, and so on rapidly becomes unachievable.
-On this basis, they contend that the rationality of any given decision rule can only be determined in the context of the environment \citep{Todd2003}, which implies that heuristics are task specific.
-They provide a number of heuristics for varying decision problems, e.g.
-recognition \citep{Goldstein2002}, cue ordering \citep{Gigerenzer1999,Todd2004}, and binary decisions \citep{Brandstatter2006}.
+Stigma, or fear of a judgemental response on the part of the practitioner
+should not however be taken uncritically to explain inaccurate reporting
+by patients. While recent \ac{NICE} public health guidance advocates
+routine alcohol misuse screening as a part of all practice \citep{NationalInstituteforHealthandCareExcellence2010},
+there is no specific policy for routine antenatal care beyond providing
+information on possible impacts of alcohol consumption \citep{NICE2010a}.
+\ac{NICE} guidance on pregnancy and complex social factors \citep{NICE2010}
+does specifically address women who misuse alcohol, but presupposes
+knowledge of the problem through medical history, or via other services.
+Taken in concert with the potential for harm from even moderate alcohol
+use (section \ref{sub:Impact-of-Alcohol}), this suggests that much
+of the onus is on the patient to volunteer information.
 
-\subsection{Descriptive Decision Theory}\label{sub:descriptive_theories}
+Where screening is used, \citet{Kaskutas2000} note that the most
+basic method, i.e. number of standard drinks consumed, can lead to
+inaccurate estimates of consumption arising from inability to relate
+the concept of a standard drink, to actual consumption. This is compounded
+by the impact of memory effects on recall over a number of days \citep{Stockwell2004},
+and a lack of consistency in the standard drink measure \citep{Turner1990}.
+Alternative screening tools, for example \acs{AUDIT}, and \acs{T-ACE}
+are available and have been shown to perform well in identifying problematic
+levels of drinking \citep{Piccinelli1997,Bradley1998,Russell1994,Russell1996},
+although the emphasis in these cases is on consumption at disordered
+levels.
 
-While heuristic theories arguably fall under the purview of the descriptive, the wider tendency is towards what are in essence \enquote{patches} to normative models.
-The most influential models in this class derive from \ac{PT} \citep{Kahneman1979}, which combines a set of heuristics based on observed decision behaviour \citep{Tversky1974}, with distortions to the perception of probability, and the value of outcomes \citep{Kahneman1984,Tversky1986}.
-\citet{Tversky1992} subsequently addressed issues present in their original formulation by introducing \ac{CPT}, which allows for non-binary decisions, but dispenses with the heuristic aspects of the original formulation.
-The essence then, is that high and low probabilities are treated differently, and the subjective value of a loss differs from the equivalent gain (losing your shirt is perceived as more of a loss than winning a shirt is a gain).
-This last effect, known as the framing effect is particularly significant, see for example work by \citet{Toll2007} examining the relationship between loss and gain framings and success rates in giving up smoking, and \ac{NICE} guidance on framing of treatment options \citep{NICE2007}.
+\citet{Prior2003} considered a different health arena (mental health
+problems and GPs), with similar characteristics in terms of concealment
+of medically relevant information. The central finding in this case
+is that non-disclosure is not a result of stigma, but of mismatched
+ontologies surrounding mental illness. Work by \citet{Alvik2005},
+where the relationship between anonymity and reporting of alcohol
+consumption by pregnant women was investigated, found no significant
+relationship, suggesting that a fear of social judgement may not be
+a dominant factor. This draws an interesting contrast with a study
+by \citet{Alvik2006}, which found that contemporaneous reports of
+consumption were significantly lower than those postpartum. Logistic
+regression results suggest that this trend is amplified by a number
+of factors, including level of alcohol consumption preceding conception,
+while anxiety about foetal wellbeing during pregnancy was associated
+with lower retrospective reports. Taken together with \citep{Alvik2005},
+these results could be seen as conflicting, but may suggest self-stigmatisation
+\citep{Watson2007}, or reflect a lack of distinction between anonymity,
+and confidentiality \citep{Malvin1983}.
 
-\ac{CPT} has been successful in explaining a number of anomalous results in decision tasks (see \citet{Camerer2004a} for a review), and \citet{Thaler2000} comments to the effect that the theory is promising, albeit incomplete, lacking for example any explanation of how frames are constructed.
-While remaining an effective account of decision behaviour under risk, the theory does not attempt to resolve apparent inconsistencies that arise when outcomes are delayed, i.e.
-in situations of intertemporal choice.
-Historically, \ac{DU} \citep{Samuelson1937}, which effectively claims that the value of a thing now is exponentially greater than the promise of the same thing at some future date, has been applied to explain this.
-More recently, \citet{Ainslie1991} has suggested that discounting of future outcomes is hyperbolic, rather than exponential.
-However neither model is complete, in that both fail to account for results from \citet{Thaler1981} showing differing temporal discounting rates for losses and gains.
-\citet{Loewenstein1992} report additional failings in classic \ac{DU} models, and propose a modified form of \ac{CPT} which they suggest is able to handle both immediate, and intertemporal choice.
+In summation then, there is a consensus that alcohol consumption is
+generally underreported in the pregnant population, with some support
+for the idea that concern about social judgement associated with stigmatisation
+may be a contributing factor. Of particular interest in the wider
+context of this work, is the relationship between underreporting and
+consumption, i.e. that heavier drinking is associated with a greater
+tendency to understate intake.
+
+\subsubsection{Practice Implications}
+
+Given that alcohol consumption is thought to be underreported some
+consideration must be given to the implications for midwifery practice,
+in terms of eliciting more accurate self-reporting. \citet{Phillips2007}
+present a qualitative account of factors influencing the disclosure
+of substance misuse to midwives, identifying particularly the need
+to build up a rapport, potentially over a number of appointments.
+This was related to continuity of care, seen as necessary by both
+midwives and women for building up a trust relationship, itself a
+key component of facilitating disclosure. \citet{Stevens2002} looked
+specifically at the process of transitioning to a caseloading model
+of care provision in one midwifery practice, reporting that both practitioners
+and women felt that this offered advantages in terms of long term
+relationship building. Relationship building was also highlighted
+by \citet{Kennedy2004} in a narrative investigation of midwifery
+practice, where the subjects interpreted the midwife-woman dynamic
+as about mutuality. \citeauthor{Kennedy2004} suggest that this arises
+from a recognition that interactions in this context are about information
+exchange, with the knowledge base of the woman as significant as that
+of the midwife, rather than simply a unidirectionally didactic relationship.
+
+\citet{Hunter2006} also focuses on much of midwifery as about relationship
+building, suggesting that there is an insufficiently recognised emotional
+labour component to practice. Observation and interview of a number
+of midwives as they practiced suggested that many midwives effectively
+took a mother type role to their patients, with implications around
+the nature of information exchange that was able to take place. The
+emotional labour component was also reported by \citeauthor{Stevens2002},
+who suggest that this is more evident under a caseloading system, particularly
+with challenging patients with complex needs. \citet{Todd1998} surveyed
+midwives working in a hospital environment, as well as those working
+in the community in a caseloading context, finding that community
+practice appeared to provide more job satisfaction, but was challenging
+to implement effectively because of limited resources. Community midwives
+suggested that larger team sizes, and smaller caseloads would contribute
+to a better realisation of the model. \citet{Farquhar2000} approached
+the same question from the perspective of women, also finding that
+faulty implementation hampered the expected benefits. They found that
+those cared for under a team scheme, with much higher continuity of
+care, reported that they had a better relationship with their midwives,
+but were not more satisfied in general with their care. In contrast,
+\citet{Biro2003} looked at a \ac{RCT} of team midwifery care versus
+hospital care in Australia, finding a significantly higher level of
+satisfaction under the team model, the distinction in this case may
+lie in the different balance of team size to caseload size.
+
+In terms of the impact of continuity of care on health, rather than
+experiential outcomes, research is relatively sparse. \citet{Marks2003}
+examined the impact of continuity of care on \ac{PND}, which has
+similar features to alcohol in that it carries an associated stigma
+that can act as a barrier to help seeking \citep{Dennis2006}. Based
+on the results of a \ac{RCT}, they conclude that continuity of care
+is not protective, in the sense of reducing rates or impacting onset,
+but was very successful in supporting engagement with treatment. Echoing
+this, a 2009 Cochrane Review by \citet{Hatem2009} found no significant
+difference in incidence of \ac{PND}, but reported benefits in terms
+of lower rates of \gls{episiotomies}, anaesthesia, and shorter hospital
+stays, with higher satisfaction as found by \citeauthor{Biro2003}.
+While research in this area does not specifically pertain to disclosure,
+the general trend in results are suggestive when taken in concert
+with studies emphasising the importance of relationship building as
+key in fostering a disclosure friendly environment. Continuity of
+care is generally regarded as improving patient experience, and leading
+to better health outcomes in the wider medical arena \citep{VanWalraven2010},
+but is clearly not a cost free endeavour, with particular concern
+arising from the emotional cost \citep{Todd1998}, and increased rates
+of `\gls{burnout}' in practitioners \citep{Sandall1997}.

### 2015-11-13 agent_models.tex
eq 10
FFH acronym

@@
 While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same output - a decision, we limit ourselves here to four.
-The simplest is a lexicographic rule (1), in the spirit of a \acl{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}.
+The simplest is a lexicographic rule (1), in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}.
 Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-output characteristics.
@@
 0,& \text{if}\, u_{i}=0\\
-\lambda g(u_{i}),& \text{if}\, x<0
+\lambda g(u_{i}),& \text{if}\, u_{i}<0
 \end{cases},

### 2015-11-16 article.tex
Renaming sections

@@
 
-The remainder of this paper proceeds to outline the proposed approach to model development (section \ref{sec:model}), and experiments (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}).
+The remainder of this paper proceeds to outline the proposed approach to model development (section \ref{sec:midwives_model}), and experiments (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}).
 \section{Disclosure Game Model}
-\label{sec:model}
+\label{sec:midwives_model}
 

### 2015-11-16 Results.tex
Jiggling to fit

@@
 Trends for all four rules are broadly similar, exhibiting a gradual increase across appointments which subsequently levels off.
-This levelling can in part be explained by the referral results (see figure \ref{fig:ref_plot} in appendix \ref{app:additional_figures}), which show that the majority of drinkers are referred, even with substantial concealment.
+This levelling can in part be explained by the referral results shown in figure \ref{fig:ref_plot}, which show that the majority of drinkers are referred, even with substantial concealment.
+
+\begin{figure}[H]
+\includegraphics[width=100mm]{ref_plot}
+\caption{Average fraction of population referred by each appointment, after 1000 rounds, mean with 95\% confidence limit over 1000 runs.
+Note that the large number of runs leads to very tight confidence intervals.\label{fig:ref_plot}}
+\end{figure}
+
 Referrals continue to occur, in the absence of honest signals, because drinkers are able to achieve a referral by masquerading as higher or lower types, dependent on how their initial beliefs are biased.

### 2015-11-16 model_description.tex
Figures path
Substantive background back in
Jiggling to fit

@@
 %!TEX root = disclosure_game.tex
-\section{Disclosure Game Model Development}
+\chapter{Disclosure Game Model Development}
 \label{app:model_description}
@@
 \begin{figure}[H]
-\sidecaption
-\includegraphics[width=7cm]{figures/simplest_game}
-\caption{A very simple two player game.
+%\sidecaption
+\includegraphics[width=7cm]{simplest_game}
+\caption[Simplest form of the disclosure game]{A very simple two player game.
 The only time things in this very restricted world obviously end poorly, is if the woman asks for help but does not get any.
@@
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{figures/less_simplest_game}
+\includegraphics[width=\textwidth]{less_simplest_game}
 \caption{A less simple two player signalling game. }
@@
 \begin{figure}[H]
-\subfloat[Women (heavy drinkers)]{\includegraphics[width=11.9cm]{figures/women_influence}}
+\subfloat[Women (heavy drinkers)]{\includegraphics[width=11.9cm]{women_influence}}
 \vskip\baselineskip
-\subfloat[Midwives]{\includegraphics[width=11.9cm]{figures/mw_influence}}
+\subfloat[Midwives]{\includegraphics[width=11.9cm]{mw_influence}}
 \caption{Influence diagrams, showing the game broken into two decision problems. Squares indicate a decision node, while circles are (from the perspective of the agent) chance nodes}

### 2016-09-30 Model.tex
Rearrange payoff tables
To save some space
Renaming sections
Jiggling to fit

@@
 \section{Disclosure Game Model}
-\label{sec:model}
+\label{sec:midwives_model}
 
@@
 \begin{table}
+\centering
 \caption{Payoff matrices}
 \label{tab:Payoff-matrix}
-\subfloat[Social cost, \(X_{s}\), for women, given their signal, and the midwife's type\label{tab:Social-cost-matrix}]{%
+\begin{subtable}[]{\textwidth}
 \begin{tabular}{|c|c|c|c|c|}
@@
 \end{tabular}
+\caption{Social cost, \(X_{s}\), for women, given their signal, and the midwife's type}
+\label{tab:Social-cost-matrix}
 
-}
-
-\subfloat[Health outcome, \(X_{h}\), for women and midwives, given the midwife's action, and woman's type\label{tab:Referral-payoff-matrix}]{%
+\end{subtable}
+\begin{subtable}[]{\textwidth}
 \begin{tabular}{|c|c|c|c|c|}
@@
 \end{tabular}
-
-}
-
-\subfloat[Referral cost, \(X_{c}\), for midwife, given their action and the woman's type\label{tab:inst_cost_matrix}]{%
+\caption{Health outcome, \(X_{h}\), for women and midwives, given the midwife's action, and woman's type}
+\label{tab:Referral-payoff-matrix}
+\end{subtable}
+\begin{subtable}[]{\textwidth}
 \begin{tabular}{|c|c|c|c|c|}
@@
 \end{tabular}
-
-}
+\caption{Referral cost, \(X_{c}\), for midwife, given their action and the woman's type}
+\label{tab:inst_cost_matrix}
+\end{subtable}
 \end{table}

### 2016-09-30 Introduction.tex

@@
 
-The remainder of this paper proceeds to outline the proposed approach to model development (section \ref{sec:model}), and experiments (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}).
+The remainder of this paper proceeds to review the substantive context of alcohol use and disclosure in the maternity context (section \ref{sec:alcohol_disclosure}), then outlines the proposed approach to model development (section \ref{sec:midwives_model}), and experiments (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}).

### 2016-09-30 SensitivityAnalysis.tex
Missing table line
Renaming sections

@@
 %Include the descent into chaos bit
-\section{Sensitivity Analysis}
+\chapter{Sensitivity Analysis}
 \label{app:sensitivity_results}
@@
 
-\subsection{Median Moderate Drinker Signalling}
+\section{Median Moderate Drinker Signalling}
 
@@
 \caption{Median moderate drinker signalling parameter sensitivity \label{tab:sa_results_sig}}
+\rotatebox{90}{
 \begin{tabular} {llllll}
@@
 Parameter & Description & Lexicographic & Bayesian Payoff & Bayesian & \ac{CPT} \\
+\noalign{\smallskip}\svhline\noalign{\smallskip}
 \(p_{w}(m)\) & Proportion of moderate drinkers & 0.367 & 1.145 & 0.801 & 0.614 \\
@@
 \end{tabular}
+}
 \end{table}
@@
 \caption{Median moderate drinker signalling emulator statistics \label{tab:sa_emulator_sig}}
+\rotatebox{90}{
 \begin{tabular} {lllllll}
 \hline\noalign{\smallskip}
-Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\
+Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & $\mu$ & Total output variance & Code uncertainty & RMSSE \\
 \noalign{\smallskip}\svhline\noalign{\smallskip}
@@
 \end{tabular}
+}
 \end{table}
 
-\input{top_5_table_sig}
+\input{midwives/top_5_table_sig}
 
-\subsection{Median Between Groups IQR}
+\section{Median Between Groups IQR}
 
@@
 \caption{Median between groups IQR parameter sensitivity \label{tab:sa_results_iqr}}
+\rotatebox{90}{
 \begin{tabular} {llllll}
@@
 \hline\noalign{\smallskip}
-Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & Mean output & Total output variance & Code uncertainty & RMSSE \\
+Rule & \(\sigma^2\) & Nugget \(\sigma^2\) & $\mu$ & Total output variance & Code uncertainty & RMSSE \\
 \noalign{\smallskip}\svhline\noalign{\smallskip}
@@
 
-\input{top_5_table_group_iqr}
+\input{midwives/top_5_table_group_iqr}
 
-\subsection{Median Moderate Drinker Signalling IQR}
+\section{Median Moderate Drinker Signalling IQR}
 
@@
 \caption{IQR of median moderate drinker signalling parameter sensitivity \label{tab:sa_results_sig_iqr}}
+\rotatebox{90}{
 \begin{tabular} {llllll}
@@
 
-\input{top_5_table_sig_iqr}
+\input{midwives/top_5_table_sig_iqr}
 
-\subsection{Between Groups IQR IQR}
+\section{Between Groups IQR IQR}
 
@@
 \caption{IQR of median between groups IQR parameter sensitivity \label{tab:sa_results_iqr_iqr}}
+\rotatebox{90}{
 \begin{tabular} {llllll}
@@
 
-\input{top_5_table_group_iqr_iqr}
+\input{midwives/top_5_table_group_iqr_iqr}

### 2016-09-30 Introduction.tex
Caps

@@
 The resulting scenario is of substantial independent interest, and shows the potential utility of a simulation approach in domains where the process is obscured, here both because of the interest in concealment, and obvious ethical concerns.
-With this said, the lack of a strong quantitative evidence base against which to validate the behaviour of the model augers for caution in interpreting the results, and a necessary reminder that in this instance the model is primarily a tool for formalisation of the thought process \citep{epstein2008}, rather than a machine for predicting.
+With this said, the lack of a strong quantitative evidence base against which to validate the behaviour of the model augers for caution in interpreting the results, and a necessary reminder that in this instance the model is primarily a tool for formalisation of the thought process \citep{Epstein2008}, rather than a machine for predicting.
 

### 2016-11-12 Background.tex
Renaming sections
Spellchecking

@@
 %!TEX root = disclosure_game.tex
-\section{Previous Research}
-
-\label{sec:lit_review}
+\section{Alcohol, and Disclosure in the Maternity Setting}
+\label{sec:alcohol_disclosure}
 
@@
 
-\subsection{Alcohol, and Disclosure in the Maternity Setting}
-\label{sub:alcohol_disclosure}
-
-\subsubsection{Impact of Alcohol\label{sub:Impact-of-Alcohol}}
+\subsection{Impact of Alcohol\label{sub:Impact-of-Alcohol}}
 
@@
 
-Considering longer term negative outcomes, a metastudy by \citet{Latino-Martel2010}
+Considering longer term negative outcomes, a meta-analysis by \citet{Latino-Martel2010}
 examined the potential for maternal alcohol consumption in pregnancy
@@
 
-\subsubsection{Disclosure}
+\subsection{Disclosure}
 
@@
 \citet{Prior2003} considered a different health arena (mental health
-problems and GPs), with similar characteristics in terms of concealment
+problems and general practionioners), with similar characteristics in terms of concealment
 of medically relevant information. The central finding in this case
@@
 of factors, including level of alcohol consumption preceding conception,
-while anxiety about foetal wellbeing during pregnancy was associated
+while anxiety about foetal well-being during pregnancy was associated
 with lower retrospective reports. Taken together with \citep{Alvik2005},
@@
 In summation then, there is a consensus that alcohol consumption is
-generally underreported in the pregnant population, with some support
+generally under reported in the pregnant population, with some support
 for the idea that concern about social judgement associated with stigmatisation
 may be a contributing factor. Of particular interest in the wider
-context of this work, is the relationship between underreporting and
+context of this work, is the relationship between under reporting and
 consumption, i.e. that heavier drinking is associated with a greater
@@
 
-\subsubsection{Practice Implications}
+\subsection{Practice Implications}
 
-Given that alcohol consumption is thought to be underreported some
+Given that alcohol consumption is thought to be under reported some
 consideration must be given to the implications for midwifery practice,
@@
 exchange, with the knowledge base of the woman as significant as that
-of the midwife, rather than simply a unidirectionally didactic relationship.
+of the midwife, rather than simply a one directional didactic relationship.
 

### 2016-11-12 Model.tex
Spellchecking

@@
 These decision problems may then form the basis of an agent model, where agents use learning, and decision rules to play out the game.
-Simulation can then support features which are not readily representable within an analytic framework, for example, populations of heterogeneous players, individual and social learning, or network effects.
+Simulation can then support features which are cannot be readily represented within an analytic framework, for example, populations of heterogeneous players, individual and social learning, or network effects.
 In addition, the ability to observe the system in a state of flux rather than at equilibrium is desirable, since even where a social system reaches a stable state, the process by which we arrive at it is significant.

### 2016-11-12 Results.tex
Spellchecking

@@
 
-As shown in figure \ref{fig:honest_signals}, all four decision rules were able to reproduce both qualitative trends towards more disclosure as women experience more appointments \citep{Phillips2007}, and a greater tendency towards underreporting of consumption by heavier drinkers \citep{Alvik2006}.
+As shown in figure \ref{fig:honest_signals}, all four decision rules were able to reproduce both qualitative trends towards more disclosure as women experience more appointments \citep{Phillips2007}, and a greater tendency towards under reporting of consumption by heavier drinkers \citep{Alvik2006}.
 Trends for all four rules are broadly similar, exhibiting a gradual increase across appointments which subsequently levels off.

### 2016-11-12 agent_models.tex
Spellchecking

@@
 %Maybe cut this bit and make explanation richer?
-\ac{CPT} uses transformed probabilities, underweighting small probabilities, and overweighting large ones.
-This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and contrastingly low probabilities as impossible.
+\ac{CPT} uses transformed probabilities, under weighting small probabilities, and over weighting large ones.
+This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and in contrast, low probabilities as impossible.
 The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains (eqn \ref{eqn:cpt_p_pos}) and losses (eqn \ref{eqn:cpt_p_neg}) -

### 2016-11-12 article.tex
Spellchecking

@@
   \acro{T-ACE}{Tolerance, Annoyance, Cut down, Eye-opener}
-  \acro{RCOG}{Royal College of Obstetricians and Gynecologists}
+  \acro{RCOG}{Royal College of Obstetricians and Gynaecologists}
   \acroindefinite{RCOG}{the}{the}
-  \acro{AML}{acute myeloid leukemia}
-  \acro{ADHD}{Attention Defecit Hyperactivity Disorder}
+  \acro{AML}{acute myeloid leukaemia}
+  \acro{ADHD}{Attention Deficit Hyperactivity Disorder}
   \acro{PND}{Postnatal Depression}
@@
 Turning more specifically to disclosure of alcohol use by women to healthcare professionals during their pregnancy, research is relatively sparse, although qualitative trends are reported by \citet{Phillips2007} and \citet{Alvik2006}.
-The former explored factors impacting disclosure through a small case study, highlighting the need to build up rapport between woman and midwife over several appointments; the latter compared post partum reports of consumption with contemporaneous accounts, finding apparent underreporting during pregnancy which was amplified by increased drinking.
+The former explored factors impacting disclosure through a small case study, highlighting the need to build up rapport between woman and midwife over several appointments; the latter compared post partum reports of consumption with contemporaneous accounts, finding apparent under reporting during pregnancy which was amplified by increased drinking.
 The simulation model described in this paper is able to replicate both qualitative trends, i.e.
@@
 
-\ac{CPT} uses transformed probabilities, underweighting small probabilities, and overweighting large ones.
+\ac{CPT} uses transformed probabilities, under weighting small probabilities, and over weighting large ones.
 This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and contrastingly low probabilities as impossible.

### 2016-11-16 Introduction.tex
Proofing

@@
 The case in favour of \ac{ABM} as a general analytical approach has been made numerously, and elegantly (e.g.
-\cite{epstein1994growing,Resnick,Axelrod1997,gilbert1999simulation,Macy2002a,Silverman2011,Silverman2013,epstein2014agent_zero}, amongst others).
+\cite{epstein1994growing,Resnick,Axelrod1997,gilbert1999simulation,Macy2002a,Silverman2011,Silverman2013}, and \cite{epstein2014agent_zero}, amongst others).
 As such we will not belabour the point, and instead turn to addressing some of the concerns expressed about the approach.
@@
 We wish to see the system in motion rather than just at rest, even if it does eventually settle to some stable point.
-Instead, we choose to focus instead on the behavioural processes driving a system in motion, a system out of equilibrium, to understand how these processes interact with the movement.
+Instead, we choose to focus on the behavioural processes driving a system in motion - a system \texit{out} of equilibrium - to understand how these processes interact with the movement.
 Introducing decision theory takes a step down the ladder of abstraction from the mental chess of game theory.

### 2016-11-18 agent_models.tex
Proofing

@@
 
-The lexicographic heuristic (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified problem representation, where an action is a choice between combined lotteries.
+The lexicographic heuristic \citep{Luce1956,Fishburn1974} (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified problem representation, where an action is a choice between combined lotteries.
 Functionally, the heuristic maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e.

### 2017-01-16 Background.tex
Jakub1

@@
 insufficient evidence to suggest any harm arising from moderate (under
-1.5 UK units per day) alcohol consumption. This ties to the current
+1.5 UK units\footnote{10ml, or 8g of pure alcohol.} per day) alcohol consumption. This ties to the current
 guidance from the \ac{NICE} \citep{NICE2010a}, advising that women
@@
 disorders in children whose mothers binged during pregnancy. They
-reported significantly greater risk of both neonatal seizures (\textasciitilde{}3
-fold) and epilepsy (1.81 fold) associated with binge drinking between
+reported significantly greater risk of both neonatal seizures (ca. three-fold) and epilepsy (1.81-fold) associated with binge drinking between
 11 and 16 weeks, but emphasised the exploratory nature of the results,
@@
 by patients. While recent \ac{NICE} public health guidance advocates
-routine alcohol misuse screening as a part of all practice \citep{NationalInstituteforHealthandCareExcellence2010},
+routine alcohol misuse screening as a part of all practice,
 there is no specific policy for routine antenatal care beyond providing
-information on possible impacts of alcohol consumption \citep{NICE2010a}.
+information on possible impacts of alcohol consumption \citep{NationalInstituteforHealthandCareExcellence2010,NICE2010a}.
 \ac{NICE} guidance on pregnancy and complex social factors \citep{NICE2010}
@@
 
-In summation then, there is a consensus that alcohol consumption is
+In summary then, there is a consensus that alcohol consumption is
 generally under reported in the pregnant population, with some support
@@
 
-\subsection{Practice Implications}
+\subsection{Implications for Clinical Practice}
 
@@
 of lower rates of \gls{episiotomies}, anaesthesia, and shorter hospital
-stays, with higher satisfaction as found by \citeauthor{Biro2003}.
+stays, with higher satisfaction as found by \citet{Biro2003}.
 While research in this area does not specifically pertain to disclosure,

### 2017-01-16 Introduction.tex
Jakub1

@@
 Turning more specifically to disclosure of alcohol use by women to healthcare professionals during their pregnancy, research is relatively sparse, although qualitative trends are reported by \citet{Phillips2007} and \citet{Alvik2006}.
-The former explored factors impacting disclosure through a small case study, highlighting the need to build up rapport between woman and midwife over several appointments; the latter compared post partum reports of consumption with contemporaneous accounts, finding apparent underreporting during pregnancy which was amplified by increased drinking.
+The former explored factors impacting disclosure through a small case study, highlighting the need to build up rapport between woman and midwife over several appointments; the latter compared post-partum reports of consumption with contemporaneous accounts, finding apparent underreporting during pregnancy which was amplified by increased drinking.
 The simulation model described in this paper is able to replicate both qualitative trends, i.e.
@@
 While scenarios may map to a number of games, exploring one candidate game still allows for a principled comparison between interpretations, and enforces explicit assumptions.
-But equilibrium is the sine qua non of game theory, which is concerned with the stable outcome of an infinite contest of second guesses.
+But equilibrium is the \emph{sine qua non} of game theory, which is concerned with the stable outcome of an infinite contest of second guesses.
 We wish to see the system in motion rather than just at rest, even if it does eventually settle to some stable point.
-Instead, we choose to focus on the behavioural processes driving a system in motion - a system \texit{out} of equilibrium - to understand how these processes interact with the movement.
+Instead, we choose to focus on the behavioural processes driving a system in motion - a system \textit{out} of equilibrium - to understand how these processes interact with the movement.
 Introducing decision theory takes a step down the ladder of abstraction from the mental chess of game theory.
@@
 
-The remainder of this paper proceeds to review the substantive context of alcohol use and disclosure in the maternity context (section \ref{sec:alcohol_disclosure}), then outlines the proposed approach to model development (section \ref{sec:midwives_model}), and experiments (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}).
+The remainder of this paper proceeds to review the substantive context of alcohol use and disclosure in the maternity context (section \ref{sec:alcohol_disclosure}), then outlines the proposed approach to model development (section \ref{sec:midwives_model}), and simulation experiments examining the abiility of the model to replicate qualitative trends in disclosure (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}).

### 2017-01-16 Methods.tex
Tweaking figure placement
Spellchecking
Jakub1

@@
 
-This section provides details of experiments conducted to examine the ability of the model to reproduce qualitative trends reported in the midwifery literature by \citet{Alvik2006}, and \citet{Phillips2007}; as well as a global sensitivity analysis and construction of statistical emulators to explore, and contrast the response surfaces of the four decision rules.
+This section provides details of simulation experiments conducted to examine the ability of the model to reproduce qualitative trends reported in the midwifery literature by \citet{Alvik2006}, and \citet{Phillips2007}; as well as a global sensitivity analysis and construction of statistical emulators to explore, and contrast the response surfaces of the four decision rules.
 
@@
 Throughout this paper, parameters for the \ac{CPT} model were as used in \cite{Tversky1992} (table \ref{tab:qt_params}).
-While there has been significant work on determining appropriate parametrisation for the model (e.g.
+While there has been significant work on determining appropriate parameterisation for the model (e.g.
 \cite{Neilson2002,Nilsson2011,Glockner2012}, and particularly \citet{Byrnes1999} and \citet{Booij2009} addressing risk aversion and gender), a full exploration of the impact of these parameters, or heterogeneous values within populations is beyond the scope of this work.
-For simplicity, it was assumed that all three drinking types are equally prevalent within the population, although results derived from \acl{ALSPAC} suggest that the reality is far more positive\footnote{95.5\% of women in the sample reported consumption at, or below, \ac{NICE} recommended safe levels.} \citep{Humphriss2013}.
+For simplicity, it was assumed that all three drinking types are equally prevalent within the population, although results derived from \acl{ALSPAC} suggest that the reality is far more positive\footnote{In this study 95.5\% of women in the sample reported consumption at, or below, \ac{NICE} recommended safe levels.} \citep{Humphriss2013}.
 The scenario was biased towards disclosure as the better option by presuming a distribution of midwives strongly skewed towards non-judgemental types, with beliefs initially favouring honesty.
-Payoffs were as in table \ref{tab:Payoff-matrix}, which ensure that it is always strictly preferable to refer drinkers, and together with the initial belief that signals will be honest, not refer those claiming otherwise.
-
-Two key measures were used: the fraction of the subpopulation who had ever signalled honestly, and the proportion of the population who were referred.
-Both measures were taken after every round of play, and were taken relative to the agent's position in their sequence of appointments giving the probability of signalling honestly, or being referred having had a given number of appointments.
-
+Payoffs were assumed as in table \ref{tab:Payoff-matrix}, which ensure that it is always strictly preferable to refer drinkers, and together with the initial belief that signals will be honest, not refer those claiming otherwise.
 \begin{table}[h!]
-\caption{Model parameters.} 
+\caption[Midwives and women disclosure game model parameters]{Model parameters.} 
 \label{tab:qt_params}
@@
 
+Two key measures were used: the fraction of the subpopulation of women who had ever signalled honestly, and the proportion of the population who were referred for specialist treatment.
+Both measures were taken after every round of play, and were taken relative to the agent's position in their sequence of appointments giving the probability of signalling honestly, or being referred having had a given number of appointments.
+
 In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examined the impact of simple social learning within the population of women (section \ref{sub:info_sharing}) on the robustness of these trends.
-The original experiment was repeated at \(q_{w},w_{w}\in \{0.25, 0.5, 0.75, 1 | q_{w}=w_{w}\}\), with 100 runs under each condition.
+The original experiment was repeated for different values of $q_{w}$ \(\{0.25, 0.5, 0.75, 1 | q_{w}=w_{w}\}\), with 100 runs under each condition.
 
@@
 
-In general, we have followed the example of \cite{Bijak2013b} for global sensitivity analysis of stochastic agent based models, although see \citet{Thiele2014} for a review of alternative techniques.
+In general, we have followed the example of \cite{Bijak2013b} for global sensitivity analysis of stochastic agent-based models, although see \citet{Thiele2014} for a review of alternative techniques.
 For this purpose the \ac{GEM-SA} software \citep{Kennedy} was used, which implements the \ac{BACCO} method developed by \citeauthor{Oakley2004} \citep{Oakley2002,Oakley2004,Dorresteijn2010}.
@@
 The unknown function can then be approximated as a Gaussian Process, which is fitted to the training data using Bayes' Theorem and then serves as an emulator for the simulator.
-The emulator is then able to provide an indication about the extent to which uncertainty in a parameter propagates to uncertainty in the output, and how sharply the output responds to change in each parameter.
+The meta-model is then able to provide an indication about the extent to which uncertainty in a parameter propagates to uncertainty in the output, and how sharply the output responds to change in each parameter.
 
@@
 
-To capture the response characteristics for the model, we measured four outcome variables - (1) the \ac{IQR} of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3, 4) the \ac{IQR} of 1 \& 2 between simulation runs.
-Together these four metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the variability of the system in response to changes to the parameters (3 \& 4).
-
-Measurements were taken at the end of 1000 rounds of play, and emulators were built against 400 sample points from the full set of simulation results (1 \& 2), and \ac{IQR} at each point (3 \& 4) to assess both the overall trend, and the extent to which the parameters contribute to variance between runs.
-
-Sixteen emulators were built, covering each of the four outputs on all decision models and used to conduct a probabilistic sensitivity analysis to assess the impact of parameters and interactions.
-
-In addition to the sensitivity analysis, we also employed the resulting emulators to rapidly\footnote{Once constructed, the emulator has an analytical solution conditional on the roughness parameters, which obviates the need to use MCMC.} explore the parameter space.
-While emulated results are subject to inaccuracy, they do provide an indication of the interest, and plausibility, of regions of the parameter space.
-Results for the outcomes of the interactions of \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) with \(x_{h}\), and \(q_{w}\) with \(w_{w}\) are given in section \ref{sub:sa_results}.
-
 \begin{table}
-\caption{Parameter ranges.}
+\caption[Parameter ranges for sensitivity analysis of the midwives and women disclosure game model]{Parameter ranges.}
 \label{tab:sa_params}
@@
 \end{table}
+
+To capture the response characteristics for the model, we measured four outcome variables - (1) the \ac{IQR} of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3, 4) the \ac{IQR} of 1 \& 2 between simulation runs.
+Together these four metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the variability of the system in response to changes to the parameters (3 \& 4).
+
+Measurements were taken at the end of 1000 rounds of play, and emulators were built against 400 sample points from the full set of simulation results (1 \& 2), and \ac{IQR} at each point (3 \& 4) to assess both the overall trend, and the extent to which the parameters contribute to variance between runs.
+
+Sixteen emulators were built, covering each of the four outputs on all decision models and used to conduct a probabilistic sensitivity analysis to assess the impact of parameters and interactions.
+
+In addition to the sensitivity analysis, we also employed the resulting emulators to rapidly\footnote{Once constructed, the emulator has an analytical solution conditional on the roughness parameters, which obviates the need to use MCMC.} explore the parameter space.
+While emulated results are subject to inaccuracy, they do provide an indication of the interest, and plausibility, of regions of the parameter space.
+Results for the outcomes of the interactions of \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) with \(x_{h}\), and \(q_{w}\) with \(w_{w}\) are given in section \ref{sub:sa_results}.

### 2017-01-16 Model.tex
Jakub1

@@
 In order to translate the scenario sketched above into a more abstract, tractable form, we cast it as a signalling game, and assume that women's disclosures (or not), are signals.
-We also impose a discretisation on the continuum of alcohol use, and use three types of behaviour - light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy.
+We also impose a discretisation on the continuum of alcohol use, and use three types of behaviour --- light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy.
 Correspondingly, they are limited in what signals they may send when claiming to be one of these three types.
 
-Midwives are treated in a similar fashion, where their type corresponds to how negatively they regard a drinking pattern - non-judgemental, moderately judgemental, and harshly judgemental.
+Midwives are treated in a similar fashion, where their type corresponds to how negatively they regard a drinking pattern --- non-judgemental, moderately judgemental, and harshly judgemental.
 The expression of this judgement is not a matter of choice on their part, and is assumed to have no impact on their clinical response, which is to either refer the woman for specialist treatment, or do nothing.
@@
 \begin{table}
-\centering
-\caption{Payoff matrices}
+\centering%!
+\caption[Payoff matrices for midwives, and women in the disclosure game]{Payoff matrices}
 \label{tab:Payoff-matrix}
-\begin{subtable}[]{\textwidth}
+\begin{subtable}[]{\textwidth}\centering%!
 \begin{tabular}{|c|c|c|c|c|}
@@
 \cline{2-5} 
- & Non & 0 & 0 & 0\tabularnewline
+ & Nonjudgemental & 0 & 0 & 0\tabularnewline
 \hline 
@@
 \end{subtable}
-\begin{subtable}[]{\textwidth}
+\begin{subtable}[]{\textwidth}\centering%!
 \begin{tabular}{|c|c|c|c|c|}
@@
 \label{tab:inst_cost_matrix}
-\end{subtable}
+\end{subtable}\par% !
 \end{table}
@@
 As noted, rather than solve the game, we allow populations of agents to play it, and hence stipulate further that women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)).
-They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred, and a new player is drawn from the same distribution that produced the original players to replace them.
+They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred for specialist treatment, and a new player is drawn from the same distribution that produced the original players to replace them.
 If they are not referred, they rejoin the back of the queue after their appointment.
@@
 Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this exogenous information differently.
-The simple payoff based rule relies on a belief structure relating actions directly to rewards which is essentially model free.
+The simple payoff-based rule relies on a belief structure relating actions directly to rewards which is essentially model free.
 Because payoffs differ by the agent's private type, the information shared may not correspond to the experience of the listening agent in the same scenario.
@@
 
-A payoff based agent, who is a light drinker, hears the account of the heavy drinker.
+A payoff-based agent, who is a light drinker, hears the account of the heavy drinker.
 They take the account as literally happening to them, and update their beliefs to include the possibility that there is a negative outcome attached to claiming to be a light drinker.

### 2017-01-16 Results.tex
Jakub1

@@
 \begin{figure}[H]
-\includegraphics[width=100mm]{ref_plot}
+\includegraphics[width=\textwidth]{ref_plot}
 \caption{Average fraction of population referred by each appointment, after 1000 rounds, mean with 95\% confidence limit over 1000 runs.
@@
 \begin{figure}[H]
-\includegraphics[width=100mm]{honesty_plot}
+\includegraphics[width=\textwidth]{honesty_plot}
 \caption{Average fraction of population ever signalled honestly by each appointment, after 1000 rounds, mean with 95\% confidence limit over 1000 runs.
@@
 \begin{figure}[H]
-\includegraphics[width=100mm]{honesty_sharing}
+\includegraphics[width=\textwidth]{honesty_sharing}
 \caption{Impact of social learning on trends in the average fraction of population ever signalled honestly by their final appointment, after 1000 rounds, mean with 95\% confidence interval over 100 runs}
@@
 This arises because both classes of agent learn that the moderate signal is the lower risk option as it is both a reliable indicator of need, and does not attract strongly negative judgement.
-The reliability of the signal is self reinforcing, since the more the agents use it and get referred, the more confident midwives become that it indicates need.
+The reliability of the signal is self-reinforcing, since the more the agents use it and get referred, the more confident midwives become that it indicates need.
 
-Particularly notable, is the decline in honest signalling by light drinkers visible in both heuristic type rules at the 0.25 level of \(q_{w}\) \& \(w_{w}\), which is associated with an increase in false positives.
+Particularly notable, is the decline in honest signalling by light drinkers visible in both heuristic type rules at the 0.25 level of \(q_{w}\) and \(w_{w}\), which is associated with an increase in false positives.
 This arises because of the lack of homophily in social learning, as light drinkers become informed about negative outcomes associated with concealment, despite having nothing to conceal.

### 2017-01-16 SensitivityAnalysis.tex
Jakub1

@@
 %Include the descent into chaos bit
-\chapter{Sensitivity Analysis}
+\chapter{Disclosure Game Model Sensitivity Analysis}
 \label{app:sensitivity_results}
@@
 This section provides complete variance based sensitivity analysis results for the disclosure game model.
-Each subsection gives results for one simulation output under all four decision rules, with tables providing the percentage of overall variance attributable to the individual parameters, emulator quality statistics, and the 5 most significant interaction contributions to variance in the output.
+Each subsection gives results for one simulation output under all four decision rules, with tables providing the percentage of overall variance attributable to the individual parameters, emulator quality statistics, and the five most important interaction contributions to variance in the output.
 
@@
 \caption{Median moderate drinker signalling emulator statistics \label{tab:sa_emulator_sig}}
-\rotatebox{90}{
 \begin{tabular} {lllllll}
@@
 \end{tabular}
-}
 \end{table}

### 2017-01-16 agent_examples.tex
Table captions
Table formatting
Equations and page widths
Tweaks
Jakub1

@@
 %!TEX root = disclosure_game.tex
-\section{Agent Examples}
+\chapter{Agent Examples}
 \label{sec:agent_eg}
@@
 
-\subsection{Lexicographic Heuristic}
+\section{Lexicographic Heuristic}
 \label{sub:lexico_eg}
@@
 
-\subsection{Bayesian Payoff}
+\section{Bayesian Payoff}
 \label{sub:payoff_eg}
 
-If we take our light drinker from the lexicographic case, and assume that they began with an uninformative prior.
-The 6 possible signal-payoffs pairings are then \([(l,10),(m,10),(h,10),(m,9),(h,9),(h,8)]\), with \(\alpha_{i}=1\) for all \(i\).
+If we take our light drinker from the lexicographic case, and assume that they began with an uninformative prior the 6 possible signal-payoffs pairings are then \([(l,10),(m,10),(h,10),(m,9),(h,9),(h,8)]\), with \(\alpha_{i}=1\) for all \(i\).
 After playing the three rounds, \(n_{l,10}=2\), and \(n_{m,9}=1\).
@@
 
-\subsection{Bayesian Risk Minimisation}
+\section{Bayesian Risk Minimisation}
 \label{sub:bayes_eg}
@@
 R_{w}(l, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(l, i, l, j)p(j)p(i | l)\\
-R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l) - u_{w}(l, r, l, m)p(m)p(r | l)\\
-&\phantom{{}=1}- u_{w}(l, n, l, m)p(m)p(n | l) - u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
+R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l)\\
+&\phantom{{}=1}- u_{w}(l, r, l, m)p(m)p(r | l)- u_{w}(l, n, l, m)p(m)p(n | l)\\
+&\phantom{{}=1}- u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
 u_{w}(l, i, l, j) &= 10\\
@@
 
-\subsection{Descriptive Decision Theory}
+\section{Descriptive Decision Theory}
 \label{sub:cpt_eg}
@@
 
-\begin{table}
-\begin{tabular}{|l | l | c|}
+\begin{table}[H]\centering
+\caption[\ac{CPT} parameters used in exemplar agent caclculations]{\ac{CPT} parameters. \label{tab:cpt_params}}
+\begin{tabular}{llc}
 \hline
@@
 \end{tabular}
-\caption[Table caption text]{\ac{CPT} parameters. \label{tab:cpt_params}}
 \end{table}
 
-\begin{equation*}
-\begin{aligned}
+%\begin{equation*}
+\begin{align*}
 \alpha &= 0.88\\
@@
 u_{w}(l, i, l, j) &= 10\\
-f&=(10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{6},10;\frac{1}{2})\\
-f^{+}&=f,f^{-}=()\\
+f^{+}&=(10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{6},10;\frac{1}{2})\\
+f^{+}&=f,f^{-}\equiv0\\
 n &= 5\\
@@
 v(u_{w}) &= 10^{0.88} = 7.59\\
-\pi_{0}^{+}&=w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(1) - w^{+}(\frac{23}{24})\\
+\pi_{0}^{+}&=w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})\\
+&=w^{+}(1) - w^{+}(\frac{23}{24})\\
 &=0.19\\
-\pi_{1}^{+}&=w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(\frac{23}{24}) - w^{+}(\frac{5}{6})\\
+\pi_{1}^{+}&=w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})\\
+&=w^{+}(\frac{23}{24}) - w^{+}(\frac{5}{6})\\
 &= 0.17\\
@@
 V(f^{+}) &= \sum_{i}^{n}\pi_{i}^{+}(f^{+})v_{i}^{+}(f^{+}) = 7.59
-\end{aligned}
-\end{equation*}
+\end{align*}
+%\end{equation*}
 

### 2017-01-16 agent_models.tex
Jakub1

@@
 
-Women resolve this by approximating the utility function, as a function \(f(s_{w}, \sigma)\) on their choice of signal and an unknown distribution $\sigma$, which maps to \(u_{w}\) - i.e.
+Women resolve this by approximating the utility function, as a function \(f(s_{w}, \sigma)\) on their choice of signal and an unknown distribution $\sigma$, which maps to \(u_{w}\) -- i.e.
 \(s_{w}\) is a choice between simple lotteries.
@@
 
-Midwives solve a slightly different problem with more information, where \(s_{w}\) is known, and \(s_{m}\) is the lottery choice - \(f(s_{w}, s_{m},\sigma)\).
+Midwives solve a slightly different problem with more information, where \(s_{w}\) is known, and \(s_{m}\) is the lottery choice -- \(f(s_{w}, s_{m},\sigma)\).
 This is resolved by maintaining a separate count for each signal (i.e.
@@
 \end{algorithmic}
-\caption{Lexicographic heuristic\label{alg:lexico}}
+\caption{Psuedocode for the Lexicographic heuristic\label{alg:lexico}}
 \end{algorithm}
@@
 Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), and \(\alpha_{i}\) is the pseudo-count of prior observations\footnote{Psuedo-counts are related to, but distinct from prior beliefs.
-Here, the psuedo-count is a parameter to the prior belief distribution and is nothing more than a hypothetical count of prior observations.} for a pair \(i\).
+Here, the pseudo-count is a parameter of the prior Dirichlet distribution and is nothing more than a hypothetical count of prior observations.
+The outcome is a result of the relationship between $\alpha$, and $n$, which is increasingly driven by the priors as fir higher values of $alpha$.} for a pair \(i\).
 Hence,
@@
 R_{w}(s_{w}) = \sum_{x \in X} -xp(x | s_{w})
+\label{eq:women_asker_risk}
 \end{equation}
@@
 R_{m}(s_{w}, s_{m}) = \sum_{x \in X} -xp(x | s_{w}\wedge s_{m}),
+\label{eq:mw_decider_risk}
 \end{equation}
 
-where $X$ is the set of payoffs the agent has observed to follow $s_{i}$.
+where $X$ is the set of payoffs, $x$, the agent has observed to follow $s_{i}$.
 
@@
 Women maintain two sets of beliefs, corresponding respectively to \(p_{m}\), and the probability of referral given signal choice.
-This leads to the risk function, minimised with respect to \(s_{w}\) -
+This leads to the risk function $R_{w}$, minimised with respect to \(s_{w}\) -
 
@@
 Midwives reasoning centres on determining the meaning of signals, since given the knowledge of what some signal \(s_{w}\) conveys about the true type of the sender, the payoff for an action is known.
-As such, their inference process is the same as for the simple Bayesian agent but over signal-type pairs, and they attempt to minimise the following risk function, minimised with respect to \(s_{m}\) -
+As such, their inference process is the same as for the simple Bayesian agent but over signal-type pairs, and they attempt to minimise the following risk function $R_{m}$, minimised with respect to \(s_{m}\) -
 
@@
 This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and in contrast, low probabilities as impossible.
-The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains (eqn \ref{eqn:cpt_p_pos}) and losses (eqn \ref{eqn:cpt_p_neg}) -
+The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains (\ref{eqn:cpt_p_pos}) and losses (\ref{eqn:cpt_p_neg}):
 
@@
 are the weights for gain and loss probabilities respectively.
-Along similar lines, the values of losses and gains are transformed to reflect a tendency to regard a loss as more significant than a gain  -
+Along similar lines, the values of losses and gains are transformed to reflect a tendency to regard a loss as more significant than a gain, such that -
 
@@
 
-where,
+where
 
@@
 
-and $\alpha$, and $\beta$ are respectively the power of a gain,
+and $\alpha$ and $\beta$ are respectively the power of a gain
 and a loss, and \(\lambda\) is a multiplier giving the aversion to loss.
 
-Finally, the transformed probabilities are used to construct decision weights, \(\pi^{+},\pi^{-}\) for losses and gains, where,
+Finally, the transformed probabilities are used to construct decision weights, \(\pi^{+},\pi^{-}\) for losses and gains, where
 

### 2017-01-16 article.tex
Jakub1

@@
 Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), and \(\alpha_{i}\) is the pseudo-count of prior observations\footnote{Psuedo-counts are related to, but distinct from prior beliefs.
-Here, the psuedo-count is a parameter to the prior belief distribution and is nothing more than a hypothetical count of prior observations.} for a pair \(i\).
+Here, the pseudo-count is a parameter to the prior belief distribution and is nothing more than a hypothetical count of prior observations.} for a pair \(i\).
 Hence,

### 2017-01-16 model_description.tex
Subcaps
Jakub1

@@
 \includegraphics[width=7cm]{simplest_game}
-\caption[Simplest form of the disclosure game]{A very simple two player game.
+\caption[Simplest form of the disclosure game]{A very simple two-player game.
 The only time things in this very restricted world obviously end poorly, is if the woman asks for help but does not get any.
@@
 We can modify the payoffs to reflect this, by reducing the midwife's payoffs when they refer.
-If the cost of referring is less than the value of a good outcome, then the effect of this is to make the only rational choice when not asked for help is to do nothing.
+If the cost of referring is less than the value of a good outcome, then the effect of this is to make the only rational choice when not asked for help to do nothing.
 
 This simple game is however not very informative, and clearly neglects much of the nuance of the scenario.
-The wider difficulty here is that the real outcome depends on an attribute of one of the players, rather than their moves.
+The wider difficulty here is that the real outcome depends on an attribute of one of the players, rather than their actions.
 In this case, we would expect the right choices to depend on the alcohol consumption of the woman, rather than entirely on what she has claimed about it.
@@
 We must also amend the moves, and payoffs slightly.
-The woman now claims to be one of the types, and may send a signal to say, for example, that she a heavy drinker.
+The woman now claims to be one of the types, and may send a signal to say that, for example, she is a heavy drinker.
 We will also modify the common payoffs to allow light drinkers to get the best outcome no matter what, and moderate and heavy types to get the best outcome only if referred.
@@
 
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{less_simplest_game}
-\caption{A less simple two player signalling game. }
-
-\label{fig:less_simple}
-\end{figure}
-
 At this point, the game becomes challenging to analyse from a Nash equilibrium perspective (there are several hundred).
-But, having raised to issue of stigma, we would also like incorporate this in the game.
+But, having raised the issue of stigma, we would also like incorporate this in the game.
 A possible approach to this is similar to the drinking behaviour of the women, and lets midwives have a type as well, corresponding to how judgemental they are when receiving signals: non-judgemental, moderately judgemental, and harshly judgemental.
@@
 At this juncture, we do not gain much further from the game representation, and instead separate it into multiple decision problems.
-
-Breaking the game down into separate decision problems can be achieved by treating the moves of the other players as a chance node, and omitting moves by nature that are known to them.
+This can be achieved by treating the moves of the other players as a chance node, and omitting moves by nature that are known to the player.
 For women, there are two such nodes, corresponding to the move by nature determining the type of midwife they play against, and the midwife's action.
@@
 \begin{figure}[H]
-\subfloat[Women (heavy drinkers)]{\includegraphics[width=11.9cm]{women_influence}}
-\vskip\baselineskip
-\subfloat[Midwives]{\includegraphics[width=11.9cm]{mw_influence}}
+\includegraphics[height=\textheight]{less_simplest_game}
+\caption{A less simple two player signalling game. }
+
+\label{fig:less_simple}
+\end{figure}
+
+\begin{figure}[H]
+
+\begin{subfigure}[]{\textwidth}
+\includegraphics[width=\textwidth]{women_influence}
+\caption{Women (heavy drinkers)}
+\end{subfigure}
+
+\begin{subfigure}[]{\textwidth}
+\includegraphics[width=\textwidth]{mw_influence}
+\caption{Midwives}
+\end{subfigure}
+
 \caption{Influence diagrams, showing the game broken into two decision problems. Squares indicate a decision node, while circles are (from the perspective of the agent) chance nodes}

### 2017-04-08 Conclusion.tex
viva version

@@
 
-From a pragmatic perspective, the differing response characteristics of the classes decision rules are substantial and significant, particularly when social learning is considered.
-There is a high level of uncertainty in the overall dynamics with the model free rules.
+From a pragmatic perspective, the differing response characteristics of the classes of decision rules are substantial and significant, particularly when social learning is considered.
+There is a high level of uncertainty in the overall dynamics with the Lexicographic, and Bayesian Payoff rules.
 This does not arise with the more complex rules, because they reframe information from others in the context of their own experiences, as what would happen to them in that situation.
-By contrast, the simpler rules treat the experiences as having literally happened to them, and since there is no mechanism of homophily, no way to listen only to accounts of agents similar to themselves, they can come to believe unreasonable things.
+By contrast, the simpler rules treat the experiences as equivalent to their own, and since there is no mechanism of homophily, no way to listen only to accounts of agents similar to themselves, they can come to believe unreasonable things.
 Naturally, incorporating homophily, by, for example weighting shared information by the type of the sharer, would represent a trivial modification to the heuristic models.
@@
 To some extent this reflects poorly on the most complex rule, \ac{CPT}, which diverges only minimally in behaviour from the Bayesian model.
-This might be to a degree anticipated since we have not elicited payoffs for obvious practical and ethical reasons, and they may be unrealistic, which limits the utility of the \ac{CPT} approach.
-Additionally, work by \citet{Glockner2012} has shown that there is considerable variation in individual parameters for the decision model, whereas we have let them remain homogeneous here.
+This might be to a degree anticipated since I have not elicited payoffs for obvious practical and ethical reasons, and they may be unrealistic, which limits the utility of the \ac{CPT} approach.
+Additionally, work by \citet{Glockner2012} has shown that there is considerable variation in individual parameters for the decision model, whereas I have let them remain homogeneous here.
 In the same vein, utility functions should arguably vary between individual agents, which could potentially be addressed by replacing the fixed payoffs used here with a distribution.
@@
 This might be addressed by incorporating noisy type information \citep{Feltovich2002}, capturing the unintentional information transmitted during appointments, together with a relaxation of the assumptions about when information may be shared and more sophisticated model of information flow in general.
-This also highlights an advantage of the \ac{BACCO} approach (which we describe in section \ref{sub:sensitivity}), in diagnosing issues with model design by giving insight into parameters which are contributing inappropriately to variance in output.
+This also highlights an advantage of the \ac{BACCO} approach (which I describe in section \ref{sub:sensitivity}), in diagnosing issues with model design by giving insight into parameters which are contributing inappropriately to variance in output.
 Coupled with the ability of emulators to rapidly explore parameter space, this clearly suggests that statistical emulation is a powerful tool to support simulation based approaches.
@@
 Amongst the reasons discrepancy arises here are heteroskedasticity associated with social learning, the stochastic nature of the simulation, and a lack of precision given the large parameter range.
-The former issues could be addressed by a more comprehensive approach to setting the nugget, which explicitly incorporates point variance.
+The former issues could be addressed by a more comprehensive approach, which explicitly incorporates point variance, to setting the `nugget' term, which weakens the presumed correlation of points very close together in parameter space.
 The latter could be improved through iterative fitting procedures, where the simulation is sampled more heavily in plausible regions of parameter space, a procedure not possible here given the dearth of data to evaluate plausibility.
-That the discrepancy exists is not prohibitive in this instance, since we are not using the emulator for prediction, only to achieve a broad strokes picture of the behaviour of the simulator.
+That the discrepancy exists is not prohibitive in this instance, since I am not using the emulator for prediction, only to achieve a broad strokes picture of the behaviour of the simulator.
 
@@
 By contrast, if one takes the view that a Lexicographic model is a better approximation of real behaviour, then outcomes can best be influenced by controlling how far midwives punish their women socially.
-We would however suggest that there are better reasons than the outputs of a simulation for doing so.
+I would however suggest that there are better reasons than the outputs of a simulation for doing so.
 
@@
 The results also make clear that deciding the operationalisation of the decision making is of key significance.
+In the following chapter, I address the significant weakness of this model by applying it to older adult care, where more empirical data is available to assess plausibility, before addressing the equivalent lack of empirical grounding in the decision models, in Chapter five.
 

### 2017-04-08 Introduction.tex
viva version

@@
 \cite{epstein1994growing,Resnick,Axelrod1997,gilbert1999simulation,Macy2002a,Silverman2011,Silverman2013}, and \cite{epstein2014agent_zero}, amongst others).
-As such we will not belabour the point, and instead turn to addressing some of the concerns expressed about the approach.
-In this instance we focus on the perception of \ac{ABM} as ad hoc in nature, reflecting the assumptions of the modeller rather than empirically or theoretically grounded \citep{Waldherr2013}.
-To ameliorate this concern, we draw on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game\footnote{In a signalling game, one player (the signaller), has some piece of information that is known only to them which affects the outcome of the game for both players.
+As such I will not belabour the point, and instead turn to addressing some of the concerns expressed about the approach.
+In this instance I focus on the perception of \ac{ABM} as ad hoc in nature, reflecting the assumptions of the modeller rather than empirically or theoretically grounded \citep{Waldherr2013}.
+To ameliorate this concern, I draw on decision theory to produce simple rule based, learning, decision making agents and show that they are able to play a form of signalling game\footnote{In a signalling game, one player (the signaller), has some piece of information that is known only to them which affects the outcome of the game for both players.
 The signaller has a choice as to what they tell the other player about this hidden information, and the responding player as to what they believe the information to be.} \citep{Kreps1987} with a basic form of intragroup social learning.

### 2017-04-08 Methods.tex
viva version

@@
 \(w_{m}\) & Weight of shared information for midwives & 0. \\ 
-\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty & 10:1 \\ 
+\(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\) & Pseudo-count favouring honesty\footnotemark & 10:1 \\ 
 \(\gamma\) & Probability weighting for gains  & 0.61 \\ 
@@
 \end{table}
+\footnotetext{This is the ratio by which the Dirichlet hyperparameters favour assuming a signal is accurate.
+In the case of the Lexicographic rule, this equates to setting the starting count of payoffs following an action to ten, where ${s_w=s_m}$.}
 
@@
 
-In addition to assessing the adequacy of the rules in capturing qualitative trends, we also examined the impact of simple social learning within the population of women (section \ref{sub:info_sharing}) on the robustness of these trends.
+In addition to assessing the adequacy of the rules in capturing qualitative trends, I also examined the impact of simple social learning within the population of women (section \ref{sub:info_sharing}) on the robustness of these trends.
 The original experiment was repeated for different values of $q_{w}$ \(\{0.25, 0.5, 0.75, 1 | q_{w}=w_{w}\}\), with 100 runs under each condition.
@@
 
-In general, we have followed the example of \cite{Bijak2013b} for global sensitivity analysis of stochastic agent-based models, although see \citet{Thiele2014} for a review of alternative techniques.
-For this purpose the \ac{GEM-SA} software \citep{Kennedy} was used, which implements the \ac{BACCO} method developed by \citeauthor{Oakley2004} \citep{Oakley2002,Oakley2004,Dorresteijn2010}.
+In general, I have followed the example of \cite{Bijak2013b} for global sensitivity analysis of stochastic agent-based models, although see \citet{Thiele2014} for a review of alternative techniques.
+For this purpose the \ac{GEM-SA} software \citep{Kennedy} was used, which implements the \ac{BACCO} method developed by \citeauthor{Oakley2004} \citeyear{Oakley2002,Oakley2004}.
 This is a form of variance-based sensitivity analysis, which assumes that the model output is an unknown, smooth function of the inputs.
@@
 Parameters for training were generated in R \citep{RTeam2014} using and appropriately transformed Latin Hypercube Sample \citep{Carnell2012} over the space of parameters given in table \ref{tab:sa_params}, giving eleven free parameters which were treated as uniformly distributed in the range given.
-Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each, with emulator quality assessed by leave-one-out cross validation.
+Given the limitation of 400 design points for the \ac{GEM-SA} software, I produced exactly that many parameter combinations and collected results for 100 runs of each, with emulator quality assessed by leave-one-out cross validation.
 A fixed set of 100 random seeds was used\footnote{Fixed random seeds were used to allow simulation results to be reproducible, since the combination of a parameter set and a random seed yields a deterministic process.}, such that each parameter set was run once with each seed, for every decision rule.
@@
 
-To capture the response characteristics for the model, we measured four outcome variables - (1) the \ac{IQR} of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3, 4) the \ac{IQR} of 1 \& 2 between simulation runs.
+To capture the response characteristics for the model, I measured four outcome variables - (1) the \ac{IQR} of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3, 4) the \ac{IQR} of 1 \& 2 between simulation runs.
 Together these four metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the variability of the system in response to changes to the parameters (3 \& 4).
@@
 
-In addition to the sensitivity analysis, we also employed the resulting emulators to rapidly\footnote{Once constructed, the emulator has an analytical solution conditional on the roughness parameters, which obviates the need to use MCMC.} explore the parameter space.
+In addition to the sensitivity analysis, I also employed the resulting emulators to rapidly\footnote{Once constructed, the emulator has an analytical solution conditional on the roughness parameters \citep{Oakley2002}, which obviates the need to use MCMC \citep{Oakley2004}.} explore the parameter space.
 While emulated results are subject to inaccuracy, they do provide an indication of the interest, and plausibility, of regions of the parameter space.

### 2017-04-08 Model.tex
viva version

@@
 
-In this section we sketch\footnote{A complete example of this for the alcohol misuse in pregnancy model is given in appendix \ref{app:model_description}, with a schedule of simulation provided in appendix \ref{app:sim_schedule}} the process of moving from a real world scenario to a minimal game which sufficiently captures reality, expressing the result as a decision problem representation, and translating this to a simulation model.
-We then outline four possible decision rules, and as an example of additional flexibility of process models and simulation in contrast to purely predictive or analytical approaches, extend the model to allow a simple form of social learning.
+In this section I sketch\footnote{A complete example of this for the alcohol misuse in pregnancy model is given in appendix \ref{app:model_description}, with a schedule of simulation provided in appendix \ref{app:sim_schedule}} the process of moving from a real world scenario to a minimal game which sufficiently captures reality, expressing the result as a decision problem representation, and translating this to a simulation model.
+I then outline four possible decision rules, and as an example of additional flexibility of process models and simulation in contrast to purely predictive or analytical approaches, extend the model to allow a simple form of social learning.
 
@@
 
-To model a scenario, we take the approach of first creating a formal game to represent it, capturing the key features as far as possible in the structure of that game.
+To model a scenario, I have taken the approach of first creating a formal game to represent it, capturing the key features as far as possible in the structure of that game.
 This game is in essence a conjecture about the real data generating process, which can be played out in simulation.
@@
 The appropriate game representative of the scenario of interest, which captures the desired strategic dynamics may not be immediately obvious.
-We suggest that an iterative process is beneficial, beginning from the simplest possible game, and progressively augmenting it.
+I would suggest that an iterative process is beneficial, beginning from the simplest possible game, and progressively augmenting it.
 
 Transitioning from the resulting game, to a set of decision problems is a relatively simple task.
-We treat the $n$ player game as $n$ one-player games \citep{RiosInsua2009}, where the moves of other players are drawn from a probability distribution - nature, in game theoretic parlance.
+I have treated the $n$ player game as $n$ one-player games \citep{RiosInsua2009}, where the moves of other players are drawn from a probability distribution - nature, in game theoretic parlance.
 As with the game, the decision problem representation admits a degree of variation, and may need to be adjusted to reflect the decision rules that will be used.
@@
 
-In order to translate the scenario sketched above into a more abstract, tractable form, we cast it as a signalling game, and assume that women's disclosures (or not), are signals.
-We also impose a discretisation on the continuum of alcohol use, and use three types of behaviour --- light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy.
+In order to translate the scenario sketched above into a more abstract, tractable form, I have cast it as a signalling game, and assume that women's disclosures (or not), are signals.
+I have also impose a discretisation on the continuum of alcohol use, and use three types of behaviour --- light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy.
 Correspondingly, they are limited in what signals they may send when claiming to be one of these three types.
@@
 
-As noted, rather than solve the game, we allow populations of agents to play it, and hence stipulate further that women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)).
+As noted, rather than solve the game, I have allow populations of agents to play it, and hence stipulate further that women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)).
 They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred for specialist treatment, and a new player is drawn from the same distribution that produced the original players to replace them.
@@
 In reality, learning is not exclusively from personal experience, and social learning plays an important role.
-This social dynamic fits naturally into an agent framework, but is difficult to address without using an approach concerned with process, so we take advantage of this to show a na{\"\i}ve take on it here.
+This social dynamic fits naturally into an agent framework, but is difficult to address without using an approach concerned with process, so I take advantage of this to show a na{\"\i}ve take on it here.
 

### 2017-04-08 Results.tex
viva version

@@
 
-Introducing social learning amongst women leads the behaviour of the decision rules to diverge markedly, which we explore possible reasons for in section \ref{sec:discussion}.
+Introducing social learning amongst women leads the behaviour of the decision rules to diverge markedly, possible reasons for which I explore in section \ref{sec:discussion}.
 Figure \ref{fig:honest_sharing} shows the proportion of women who have signalled honestly at least once by their final appointment, under four sharing conditions.
@@
 The relationship is not, however, entirely straightforward, in that increasing social learning leads to greater variance between runs.
-A linear model was used to predict the between-runs interquartile range of the average signal sent by moderate drinkers.
+As a preminary investigation of this, linear model was used to predict the between-runs interquartile range of the average signal sent by moderate drinkers.
 The predictors used were decision rule, and level of social learning, together with the interaction between the two.
@@
 
-In this section we present a brief overview of the sensitivity analysis, followed by selected results highlighting the global effect of changes to perceived payoffs and degree of bias towards honesty, as well as social learning within women.
+In this section I present a brief overview of the sensitivity analysis, followed by selected results highlighting the global effect of changes to perceived payoffs and degree of bias towards honesty, as well as social learning within women.
 The full results for the sensitivity analysis covering all sixteen emulators are available in appendix \ref{app:sensitivity_results}.
-
-\begin{figure}[H]
-\includegraphics[width=90mm]{sharing_emulated_simulated}
-\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules, with signals coded as 0 = light, 1 = moderate, and 2 = heavy.}
-\label{fig:outcome_plots}
-\end{figure}
 
@@
 While there are small contributions to variance in interaction with other parameters (e.g.
-4\% to between groups IQR, for the interaction with the proportion of light drinkers under the Bayesian rule), this may suggest that the model is lacking in this area, which we touch on in section \ref{sec:conclusion}.
+4\% to between groups IQR, for the interaction with the proportion of light drinkers under the Bayesian rule), this may suggest that the model is lacking in this area, which I touch on in section \ref{sec:conclusion}.
 
 Figure \ref{fig:outcome_plots} gives a qualitative picture of both emulator quality, and the divergent response surfaces of the decision rules in response to variations in social learning parameters.
+The figure shows the median signal by moderate drinkers versus the median IQR of the signal by all the drinking types.
+A higher IQR implies more separation in signalling behaviour between the groups, which in principle makes it less challenging to decide how to respond to a signal.
+The right hand side of the plot shows results from simulation for the four decision rules, at a variety of sharing parameters.
+The left hand side shows the output predicted by the emulator.
 Emulator fit is clearly imperfect, but overall behaviour is qualitatively similar, with both emulated and simulated plots demonstrating separation in outcome space for the decision rules.
@@
 \begin{figure}[H]
-\includegraphics[width=100mm]{unfixed_emu_sig_iqr}
-\caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\)}
-\label{fig:emulated_sharing_iqr}
+\includegraphics[width=0.8\textwidth]{sharing_emulated_simulated}
+\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules, with signals coded as 0 = light, 1 = moderate, and 2 = heavy.}
+\label{fig:outcome_plots}
 \end{figure}
@@
 \begin{figure}[H]
-\includegraphics[width=100mm]{unfixed_emu_payoff_honesty_group_iqr}
+\includegraphics[width=\textwidth]{unfixed_emu_sig_iqr}
+\caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\)}
+\label{fig:emulated_sharing_iqr}
+\end{figure}
+
+For the \ac{CPT}, and Bayesian decision models, the interaction of bias towards honesty, and distinction between payoffs has a significant, and non-linear effect on instability, and separability of groups.
+Figure \ref{fig:emulated_payoff_group_iqr} shows the effects, and also highlights the tendency towards poor separability of groups for both the heuristic type decision rules.
+The response surface of the Bayesian payoff rule is slightly more nuanced than the simple Lexicographic rule.
+Figure \ref{fig:emulated_payoff_group_iqr} shows better separation, close to partial pooling\footnote{Pooling occurs when signallers of different types `pool' their signals, and one adopts the signals of another.} at high payoff distinction, with relatively modest honesty bias, which is reflected by the variance contributions of 11\% and 8\% respectively.
+For the more complex rules, the general tendency is towards less pooling for higher values of both, but with pockets where full pooling\footnote{Indicating that all signaller types are using a the same signal.} occurs.
+The plots also suggest that the sensitivity of the \ac{CPT} rule is marginally greater, which is supported by the significant contribution to variance of close to 15\% for all measures of \(x_{h}\).
+
+\begin{figure}[H]
+\includegraphics[width=\textwidth]{unfixed_emu_payoff_honesty_group_iqr}
 \caption{Emulated between groups IQR in response to varying \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\), and \(x_{h}\)}

### 2017-04-08 abstract_short.tex
viva version

@@
 
-We draw together methodologies from game theory, agent based modelling, decision theory, and uncertainty analysis to explore the process of decision making in the context of pregnant women disclosing their drinking behaviour to their midwives.
+I draw together methodologies from game theory, agent based modelling, decision theory, and uncertainty analysis to explore the process of decision making in the context of pregnant women disclosing their drinking behaviour to their midwives.
 
-We employ a game theoretic framework to define a signalling game.
+I employ a game theoretic framework to define a signalling game.
 The game represents a scenario where pregnant women decide the extent to which they disclose their drinking behaviours to their midwives, and midwives employ the information provided to decide whether to refer their patients for costly specialist treatment.
@@
 
-In simulation, we recreate two key qualitative trends described in the midwifery literature for all the decision models, and investigate the impact of introducing a simple form of social learning within agent groups.
+In simulation, I recreate two key qualitative trends described in the midwifery literature for all the decision models, and investigate the impact of introducing a simple form of social learning within agent groups.
 Finally a global sensitivity analysis using \acp{GEM} is conducted, to compare the response surfaces of the different decision rules in the game.

### 2017-04-08 agent_models.tex
viva version

@@
 
-While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same output - a decision, we limit ourselves here to four.
+While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same output - a decision, I have limited myself here to four.
 The simplest is a lexicographic rule (1), in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}.
@@
 one reason decision making.
-Where there is no clear best action, but one or more is evidently worse, a choice must be made as to whether to discard the poorer action; in this case we have elected to retain it.
+Where there is no clear best action, but one or more is evidently worse, a choice must be made as to whether to discard the poorer action; in this case I have elected to retain it.
 This approach requires minimal computation, and does not assume that \(u_{i}\) is static, or known.
@@
 Given the discrete nature of actions and payoffs, coupled with a desire for tractability of the
-simulation, the Dirichlet distribution is employed as a prior to represent these beliefs. 
+simulation, the Dirichlet distribution is employed as a prior to represent these beliefs \citep{Agresti2005}. 
 The distribution is particularly convenient, in that to infer the
@@
 Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), and \(\alpha_{i}\) is the pseudo-count of prior observations\footnote{Psuedo-counts are related to, but distinct from prior beliefs.
-Here, the pseudo-count is a parameter of the prior Dirichlet distribution and is nothing more than a hypothetical count of prior observations.
-The outcome is a result of the relationship between $\alpha$, and $n$, which is increasingly driven by the priors as fir higher values of $alpha$.} for a pair \(i\).
+Here, the pseudo-count is a hyperparameter of the prior Dirichlet distribution and is nothing more than a hypothetical count of prior observations.
+The outcome is a result of the relationship between $\alpha$, and $n$, which is increasingly driven by the priors as for higher values of $\alpha$.} for a pair \(i\).
 Hence,
@@
 \begin{equation}
-R_{w}(s_{w}, \theta_{w}) = \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, \theta_{w}, j)p(j)p(i | s_{w}),
+R_{w}(s_{w}, \theta_{w}) = \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, \theta_{w}, j)p(j)p(i | s_{w})\label{eq:w_brm},
 \end{equation}
@@
 \begin{equation}
-R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{m}(s_{w}, s_{m}, i)p(i | s_{w})
+R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{m}(s_{w}, s_{m}, i)p(i | s_{w})\label{eq:mw_brm}
 \end{equation}
@@
 This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and in contrast, low probabilities as impossible.
-The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains (\ref{eqn:cpt_p_pos}) and losses (\ref{eqn:cpt_p_neg}):
+The correct weighting function is subject to some debate, but here I have used that of \citet{Tversky1992}, which treats probabilities differently for gains (\ref{eqn:cpt_p_pos}) and losses (\ref{eqn:cpt_p_neg}):
 
@@
 \begin{equation}
-\pi_{i}^{-}=w^{-}(p_{-m}+\ldots+p_{i}) - w^{-}(p_{-m}+\ldots+p_{i-1}),1-m\leq i \leq 0
+\pi_{i}^{-}=w^{-}(p_{-m}+\ldots+p_{i}) - w^{-}(p_{-m}+\ldots+p_{i-1}),1-m\leq i \leq 0\label{eq:cpt_end}
 \end{equation}

### 2017-04-08 motivation.tex
Cleaning up
viva version

@@
-\section{Methods and Motivation}
+\section{Approach and Motivation}
 \label{sec:model_design}
@@
 There will almost invariably be many possible alternatives, of which some are isomorphisms, and others fundamentally different conjectures about the data generating process.
-We suggest that an iterative process is beneficial, beginning from the simplest possible game, and progressively augmenting it.
+I would suggest that an iterative process is beneficial, beginning from the simplest possible game, and progressively augmenting it.
 
 Transitioning from the resulting game, to a set of decision problems is a relatively simple task.
-We treat the $n$ player game as $n$ one-player games \citep{RiosInsua2009}, where the moves of other players are drawn from a probability distribution - nature, in game theoretic parlance.
+I have treated the $n$ player game as $n$ one-player games \citep{RiosInsua2009}, where the moves of other players are drawn from a probability distribution - nature, in game theoretic parlance.
 As with the game, the decision problem representation admits a degree of variation, and may need to be adjusted to reflect the decision rules that will be used.

### 2017-04-08 Introduction.tex
Typo 9

@@
 
-The remainder of this paper proceeds to review the substantive context of alcohol use and disclosure in the maternity context (section \ref{sec:alcohol_disclosure}), then outlines the proposed approach to model development (section \ref{sec:midwives_model}), and simulation experiments examining the abiility of the model to replicate qualitative trends in disclosure (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}).
+The remainder of this paper proceeds to review the substantive context of alcohol use and disclosure in the maternity context (section \ref{sec:alcohol_disclosure}), then outlines the proposed approach to model development (section \ref{sec:midwives_model}), and simulation experiments examining the ability of the model to replicate qualitative trends in disclosure (section \ref{sec:method}), with selected results (section \ref{sec:results}), followed by a discussion contrasting the decision models (section \ref{sec:discussion}), and conclusions (section \ref{sec:conclusion}).

### 2017-04-08 Model.tex
Typo 10

@@
 These decision problems may then form the basis of an agent model, where agents use learning, and decision rules to play out the game.
-Simulation can then support features which are cannot be readily represented within an analytic framework, for example, populations of heterogeneous players, individual and social learning, or network effects.
+Simulation can then support features which cannot be readily represented within an analytic framework, for example, populations of heterogeneous players, individual and social learning, or network effects.
 In addition, the ability to observe the system in a state of flux rather than at equilibrium is desirable, since even where a social system reaches a stable state, the process by which we arrive at it is significant.

### 2017-04-08 Model.tex
Typo 11

@@
 
-As noted, rather than solve the game, I have allow populations of agents to play it, and hence stipulate further that women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)).
+As noted, rather than solve the game, I have allowed populations of agents to play it, and hence stipulate further that women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)).
 They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred for specialist treatment, and a new player is drawn from the same distribution that produced the original players to replace them.

### 2017-04-08 agent_models.tex
Typo 12

@@
 
-Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), and \(\alpha_{i}\) is the pseudo-count of prior observations\footnote{Psuedo-counts are related to, but distinct from prior beliefs.
+Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), and \(\alpha_{j}\) is the pseudo-count of prior observations\footnote{Psuedo-counts are related to, but distinct from prior beliefs.
 Here, the pseudo-count is a hyperparameter of the prior Dirichlet distribution and is nothing more than a hypothetical count of prior observations.
-The outcome is a result of the relationship between $\alpha$, and $n$, which is increasingly driven by the priors as for higher values of $\alpha$.} for a pair \(i\).
+The outcome is a result of the relationship between $\alpha$, and $n$, which is increasingly driven by the priors as for higher values of $\alpha$.} for a pair \(j\).
 Hence,
